\begin{abstract}
We work in the formal-local mixed holomorphic-topological string field
theory on
\[
  X=\R^2_{\mathrm{top}}\times\C^2_{\mathrm{hol}},
  \qquad
  L=\R_{\mathrm{brane}}\times\{s=z_1=z_2=0\},
\]
completed at the mixed Dirac brane whose holomorphic normal disk is
\((\operatorname{Spf}\C[[z_1,z_2]],dz_1\wedge dz_2)\).  The theorem
package proved in this local model has three cores: the Dirac brane
probe, the Hamiltonian BF closed sector, and the reduced Hamiltonian
CE/PV central-operation theorem, together with Matlis principal parts and
the Weyl/Moyal--Capelli quantum coefficient surface, finite radial/Weyl
certificates, and a finite-window non-scalar Costello/QME obstruction
criterion.

On a stack of \(N\) probes the holomorphic coordinates become
\(\phi_1,\phi_2\in\mathfrak{gl}_N\).  The open sector is the
Dirac-normalized first-order system
\[
  S_\partial
  =
  \int_\R\operatorname{Tr}\bigl(\phi_1\,d\phi_2
  +A[\phi_1,\phi_2]\bigr),
  \qquad
  Q\psi=[\phi_1,\phi_2].
\]
The closed sector is Hamiltonian BF theory for the shifted cotangent Lie
algebra
\[
  \mathfrak h=\C[[z_1,z_2]]/\C\cdot1,
  \qquad
  \mathfrak g=\mathfrak h\ltimes
  \mathfrak h^\vee_{\mathrm{cont}}[1],
\]
with the Hamiltonian bracket induced by \(dz_1\wedge dz_2\), the local BV
pairing supplied by continuous evaluation
\(\mathfrak h^\vee_{\mathrm{cont}}\otimes\mathfrak h\to\C\), and the
BF action
\[
  S_{\mathrm{BF}}
  =
  \int_{\R^2\times\C^2}
  \bigl\langle \beta,\,
  (d_{\R^2}+\bar\partial)\alpha+\tfrac12\{\alpha,\alpha\}
  \bigr\rangle\,dz_1dz_2 .
\]
The classical master equation is the Jacobi identity for
\(\mathfrak h\) plus the coadjoint-module identity.

The native holomorphic object is not a curve vertex algebra.  It is the
two-complex-dimensional Hamiltonian holomorphic factorization algebra
\[
  \mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}(B)
  =
  C^\bullet_{\mathrm{CE},\mathrm{cont}}
  \bigl(\Omega_c^{0,\bullet}(B)\widehat\otimes\mathfrak g\bigr)
\]
on holomorphic polydisks \(B\subset\C^2\), with mixed enhancement
\[
  \mathcal F_{\mathrm{Ham}}^{\mathrm{mix}}(U\times B)
  =
  C^\bullet_{\mathrm{CE},\mathrm{cont}}
  \bigl(
  \Omega_c^\bullet(U)\widehat\otimes
  \Omega_c^{0,\bullet}(B)\widehat\otimes\mathfrak g
  \bigr)
\]
for \(U\subset\R^2_{\mathrm{top}}\).  This is the manuscript's native
holomorphic \(E_2\)-type/factorization object.  Its brane avatars are the
Weyl/Moyal open-string algebra, matrix or supermatrix cyclic trace
models, and support-local principal-part currents on brane intervals.

The inner CE/PV theorem is a reduced Hamiltonian central-operation
statement.  For a finite-dimensional Lie algebra \(\mathfrak l\),
\[
  C^\bullet_{\mathrm{CE}}
  (\mathfrak l\ltimes\mathfrak l^{\vee}[1])
  \simeq \mathrm{PV}(\mathbf S(\mathfrak l)),
  \qquad
  c^I\mapsto\theta^I,\quad u_I\mapsto O_I .
\]
For the formal disk this becomes the coordinate completed map
\[
  \Phi_{\mathrm{coord}}\colon
  C^\bullet_{\mathrm{CE},\mathrm{coord}}(\mathfrak g)
  \xrightarrow{\sim}
  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}}).
\]
It is a dg coordinate theorem.  The bracketed \(P_0\) form is asserted
only after a bracket-admissible completion
\(B\subset\mathrm{PV}_{\mathrm{coord}}\) is chosen; the Maurer--Cartan
kernel \(\Theta_B\) is asserted only when the diagonal tensor converges
in a kernel-admissible product.  This is not the unreduced
factorization-centre theorem.

The cotangent coefficients are Grothendieck--Matlis principal parts,
not polynomial one-\(\psi\) descendants:
\[
  \begin{aligned}
  \mathcal P
  &=
  \operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
  \subset
  H^2_{\mathfrak m}(\C[[z_1,z_2]])\,dz_1dz_2,\\
  \rho_{a,b}
  &=
  z_1^{-a-1}z_2^{-b-1}dz_1dz_2,
  \qquad a,b\ge0,\ a+b>0 .
  \end{aligned}
\]
Their coadjoint action is
\[
  z_1^pz_2^q\cdot\rho_{a,b}
  =
  -(pb-qa+p-q)\rho_{a-p+1,b-q+1},
\]
with negative targets zero.
The PBW one-\(\psi\) classes \(\Psi_{a,b}\) share bidegree labels with
\(\rho_{a,b}\) but live in a different Hamiltonian module.  The
\(\mathcal D_\hbar\) Fourier--Rees bridge
\[
  z_1^az_2^b\mapsto
  \partial_1^a\partial_2^be_0
  \mapsto
  (-1)^{a+b}\hbar^{a+b}a!b!\rho_{a,b}
\]
is a polarization comparison; the same-action obstruction forbids a flat
polynomial realization of \(\mathcal P\) with the original action.

The quantum target uses the Weyl/Moyal convention
\[
  f*g=m\exp\!\left(\frac{\hbar}{2}
  (\partial_{z_1}\otimes\partial_{z_2}
  -\partial_{z_2}\otimes\partial_{z_1})\right)(f\otimes g),
  \qquad
  \{f,g\}_\hbar=\hbar^{-1}[f,g]_* .
\]
The raw commutator has first and third coefficients \(1\) and \(1/24\).
At finite \(N\) the normal-ordered quantum comoment carries the
Capelli contact term
\[
  \widehat\mu_\epsilon
  =
  \operatorname{Tr}\bigl(\epsilon(YX-XY+\hbar N I)\bigr),
\]
and the scalar QME obstruction in the ordinary scalar-reduced
\(\mathfrak{gl}_N\) branch is
\[
  \operatorname{Ob}_{\mathrm{sc}}
  =
  \hbar N\,\omega(f,g)
  \int_\R a(t)b(t)\gamma_{\mathbf 1}(t)\,dt,
  \qquad
  [\operatorname{Ob}_{\mathrm{sc}}]=\hbar N[\bar c].
\]
The central-character and balanced-supertrace branches cancel this scalar
class by changing the source or open model before the reduced class
forms; any other cancellation must supply an explicit null-homotopy with
leading class \(-\hbar N[\bar c]\).

The proved quantum surface is componentwise.  For an admissible weight
and interval \(I\),
\[
  \mathfrak S_{\hbar,w}(I)=
  \mathcal K_{\mathrm{BV}}^w
  \times\{0_{\mathrm{sc}}\}
  \times A^{\mathrm{pp},w}_{\partial,\hbar}(I)
  \times T_{\mathrm{Ham},\hbar}.
\]
Its factors are weighted coefficient/BV-kernel convergence,
balanced-supertrace scalar QME cancellation, reduced weighted
Moyal principal-part current brackets, and the degree-zero Hamiltonian
trace comparison relative to the radial/Weyl normal-form gate.  The
finite certificates now close the edge families \((2,b),(b,2)\) through
\(b=12\), the balanced diagonal through \((6,6)\), and all non-edge
bidegrees of total degree at most \(12\).  The missing all-bidegree
theorem is the uniform splitting of the free normal-diagram correction
map \(\mathcal C_{a,b}\); the first balanced case outside the current
certificate range is \((7,7)\), which is open rather than obstructed.

The non-scalar Costello graph/QME surface is now a finite-window
criterion.  After constructing the scalar-contact lift
\(\widehat\sigma_{\mathrm{sc}}\), one must kill
\[
  [\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]
  \in H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})
\]
with finite-window counterterms, a curved bulk-to-defect kernel, and
compatible centrality homotopies.  The closed rows
\(\alpha_{\mathrm{sc}}\) and \(\alpha_{11}\) vanish in the constructed
finite-window habitat.  The first exposed larger source-face row is
\(\theta_3\):
\[
  \mathsf E_{\theta_3,M}
  =
  -K^M_{\Theta_3}(\zeta_{M,\nu_3}),\qquad
  \ell_{\theta_3}(\mathsf E_{\theta_3,M})=1.
\]
It is not solved by naming a counterterm.  It is solved only by a CE
ancestor, a scalar-zero Costello local counterterm, or a complete
companion-face table whose differential gives
\(d_MC_{\theta_3,M}=-\mathsf E_{\theta_3,M}\) with Roos-compatible
finite-window projections.

Curve chiral and Zhu objects are reduced surfaces, not native objects.
A \(\C\times\R\) reduction must specify the projection, the retained
\(z_2\)-mode or principal-part coefficient system, the image of the
brane, the pushed-forward bracket, the BV pairing, the anomaly matching,
and the Dirac BRST differential before any \(Q_{\mathrm{BRST}}^2=0\) or
Zhu comparison is asserted.  The normal \(\Omega\)-background is likewise
a theorem surface, not a consequence of the preceding constructions:
one must use the brane-preserving normal torus on
\[
  N_LX=\R_s\oplus\C_{z_1}\oplus\C_{z_2},
  \qquad
  T_\Omega=
  \C^*_{\epsilon_s}\times
  \C^*_{\epsilon_1}\times
  \C^*_{\epsilon_2},
  \qquad t\ \text{fixed},
\]
construct
\[
  Q_\Omega=Q+\iota_{V_\Omega},\qquad
  Q_\Omega^2=L_{V_\Omega},
\]
invert the moving normal weights, and use a line-valued or
\(\hbar_\omega\)-weighted Hamiltonian bracket off the self-dual locus
\(\epsilon_1+\epsilon_2=0\).  It must also state the
residue/Euler normalization and build the resulting stratified
factorization algebra on \((X,L)\).
A protected stratified trace or physical \(\Omega\)-large-\(N\) trace
requires, in addition, the brane-defect QME, trace-state normalization,
and the same non-scalar obstruction vanishing.

No compact Calabi--Yau, global BCOV, CoHA, quintic, HKQ/CDGP/GV/OSV,
Abel--Jacobi, MNOP/chiral-volume, Vol III, Igusa, Borcherds/BKM, or
sister-volume consequence follows from this local theorem.  Such a target
requires a matched-conventions descent theorem and vanishing, with
specified null-homotopies, of the corresponding period, anomaly, QME,
convergence, hyperdescent, six-relation, and operadic obstruction
classes.
\end{abstract}
