\section{Factorization Current Conventions for the CE/PV Interface}
\label{sec:app-factorization-current-conventions}

This appendix fixes the algebraic source/target interface carried by
the factorization-current theorem.  The interface is used before the
admissible bar-cobar/enveloping criterion: interval Hamiltonian
currents form the CE source, distributional Matlis principal parts form
the cotangent current target, and the CE/PV generator dictionary is
\[
  c_\lambda\longmapsto\theta_\lambda,\qquad
  u_{a(t)dt\otimes f}\longmapsto B_f(a).
\]
The proved content is the reduced algebraic current model after
de Rham-current contraction.  The unreduced BV/QME current lift and the
Costello brane-defect graph theorem are separate obstruction problems,
recorded in Remark~\ref{rmk:unreduced-lift-status},
Appendix~\ref{sec:app-unreduced-bv-qme}, and
Problem~\ref{prob:analytic-graph-realization}.
All completed symmetric algebras in this appendix are interpreted
degreewise in the chosen current category; finite symmetric powers are
formed before completion, and brackets extend continuously from the
displayed length-one current formulas.
The geometry throughout is the formal-local mixed HT model on
\(\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\).  The
interval \(I\) is an oriented topological current interval in the brane
line, while the Hamiltonian labels live on the formal holomorphic
symplectic disk with
\[
  \Omega_{\mathrm{loc}}=dz_1\wedge dz_2,\qquad
  \{f,g\}=\partial_{z_1}f\,\partial_{z_2}g
    -\partial_{z_2}f\,\partial_{z_1}g .
\]
No compact Calabi--Yau target, global BCOV moduli space, CoHA, quintic,
OSV/GV, Abel--Jacobi, Igusa, or BKM datum is part of this appendix.

\begin{defn}[Interval Hamiltonian current algebra]
\label{def:app-factorization-current-source}
  For an open interval \(I\subset\R\), set
  \[
    \mathfrak h_I
      =\Omega^\bullet_c(I)\widehat\otimes\mathfrak h ,
  \]
  with differential \(d_I=d_{\mathrm{dR}}\otimes1\).  Here
  \[
    \mathfrak h=\C[[z_1,z_2]]/\C\cdot1
  \]
  is the Hamiltonian Lie algebra of the formal holomorphic symplectic
  disk \((\widehat{\C^2}_0,\Omega_{\mathrm{loc}})\), concentrated in
  degree \(0\).  The graded bracket is
  \[
    [\alpha\otimes f,\beta\otimes g]
      =\alpha\wedge\beta\otimes\{f,g\},
      \qquad
      \alpha,\beta\in\Omega^\bullet_c(I),\ f,g\in\mathfrak h .
  \]
  For degree-zero test functions \(a,b\in\Omega^0_c(I)\),
  \[
    [a\otimes f,b\otimes g]=ab\otimes\{f,g\}.
  \]
  The cosheaf structure for inclusions of intervals is extension by
  zero on \(\Omega^\bullet_c\), tensored with the identity on
  \(\mathfrak h\).  Polynomial formulas use the dense scalar-reduced
  subalgebra \(\bar A=\C[z_1,z_2]/\C\cdot1\subset\mathfrak h\).
  For \(j:I\hookrightarrow J\), extension by zero is smooth because
  every element of \(\Omega_c^\bullet(I)\) has support compactly
  contained in \(I\).  On CE cochains the induced map is the dual
  coproduct/pullback; the covariant factorization structure belongs to
  the compact-support current target, not to a restriction map on raw
  CE cochains.

  The notation \(a(t)dt\otimes f\) is the oriented density label paired
  with distributional cotangent currents.  It does not convert
  \(a\in\Omega^0_c(I)\) into a degree-one Hamiltonian generator of
  \(\mathfrak h_I\).
\end{defn}

\begin{defn}[Distributional Matlis current dual]
\label{def:app-factorization-current-dual}
  Let
  \[
    \mc P=\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
      \cong\mathfrak h^\vee_{\mathrm{cont}}
  \]
  be the reduced Matlis principal-part module of
  Section~\ref{sec:app-matlis-principal-parts}.  Its interval current
  form is
  \[
    \mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mc P .
  \]
  This is the selected support-local current dual used after
  contraction, not an assertion that the full strong dual of
  \(\Omega_c^\bullet(I)\widehat\otimes\mathfrak h\) has been imported.
  The pairing with degree-zero Hamiltonian currents is
  \[
    \langle B\otimes\rho,\;a\otimes f\rangle
      =B(a)\operatorname{Res}(\rho f),
      \qquad
      B\in\mathcal D'_c(I),\ \rho\in\mc P.
  \]
  The residue is the formal residue determined by
  \(dz_1\wedge dz_2\) on \(\widehat{\C^2}_0\); it is not integration
  over a compact target.
  If \(B=b(t)dt\) is a regular compactly supported density, then
  \[
    B(a)=\int_Ia(t)b(t)\,dt .
  \]

  The shifted cotangent interval Lie algebra is
  \[
    \mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1],
  \]
  where \(\mathfrak h_I\) acts on \(\mathcal P_I\) by the product of
  the \(C_c^\infty(I)\)-module operation \(B\mapsto aB\) on compactly
  supported currents and the Matlis coadjoint action
  on \(\mc P\).  On degree-zero labels this action is
  \[
    (a\otimes f)\cdot(B\otimes\rho)
      =(aB)\otimes(f\cdot\rho).
  \]
\end{defn}

\begin{prop}[Local unimodular input to the current kernels]
\label{prop:app-local-unimodular-current-kernel-input}
  The current and kernel constructions in this appendix use the
  Calabi--Yau datum only in the following formal-local sense:
  \[
    \left(\widehat{\C^2}_0,\Omega_{\mathrm{loc}}=dz_1\wedge dz_2\right).
  \]
  This datum supplies:
  \begin{enumerate}
    \item the Poisson bracket on
    \(\mathfrak h=\C[[z_1,z_2]]/\C\cdot1\);
    \item the Hamiltonian vector-field convention
    \[
      \iota_{X_f}\Omega_{\mathrm{loc}}=-df,\qquad
      X_f=(\partial_{z_1}f)\partial_{z_2}
        -(\partial_{z_2}f)\partial_{z_1};
    \]
    \item the divergence-free identity
    \(\operatorname{div}_{\Omega_{\mathrm{loc}}}X_f=0\), hence the
    residue integration-by-parts formula defining the Matlis coadjoint
    action;
    \item the principal-part residue pairing
    \[
      \operatorname{Res}_0
      \left(z_1^{-i-1}z_2^{-j-1}dz_1dz_2\;z_1^mz_2^n\right)
      =\delta_{i,m}\delta_{j,n}.
    \]
  \end{enumerate}
  At the reduced current-interface level the topological factor
  contributes the compactly supported de Rham current direction
  \(I\subset\R_{\mathrm{brane}}\), the operation \(B\mapsto aB\), and
  extension by zero.  In the graph layer it also contributes the local
  heat-kernel variables on \(\R^2_{\mathrm{top}}\).  Finite-window and
  weighted kernels are completions of the formal Hamiltonian coefficient
  system.  Compactness of a Calabi--Yau manifold is irrelevant to these
  constructions.
\end{prop}

\begin{proof}
  The bracket in
  Definition~\ref{def:app-factorization-current-source} is the inverse
  bivector of \(dz_1\wedge dz_2\), and constants are quotiented because
  they give the zero Hamiltonian vector field.  The displayed
  \(X_f\) satisfies \(X_f(g)=\{f,g\}\), and
  \[
    \operatorname{div}_{\Omega_{\mathrm{loc}}}X_f
      =-\partial_{z_1}\partial_{z_2}f
        +\partial_{z_2}\partial_{z_1}f=0.
  \]
  Thus Hamiltonian fields preserve the residue density.  The transpose
  of this action under
  \(\operatorname{Res}(\rho f)\) is exactly the Matlis coadjoint action
  used in
  Definition~\ref{def:app-factorization-current-dual} and
  Corollary~\ref{cor:app-factorization-principal-part-current-brackets}.

  The interval variable is independent of the holomorphic disk.  In the
  reduced current interface its operations are the de Rham differential,
  multiplication of a current by a smooth compactly supported test
  function, and extension by zero.  In the graph layer the additional
  topological variables enter only through the local heat-kernel
  calculus on \(\R^2_{\mathrm{top}}\).  The finite-window constructions
  truncate only the Hamiltonian degree in the formal disk and then pass
  through the weighted Mittag--Leffler inverse limit.  None of these
  operations uses compact Hodge theory, periods, worldsheet instantons,
  or global BCOV integration data.
\end{proof}

\begin{lem}[Multiplication of a current by a test function]
\label{lem:app-factorization-current-product}
  For \(a\in C^\infty_c(I)\) and \(B\in\mathcal D'_c(I)\), define
  \[
    (aB)(\varphi)=B(a\varphi),
    \qquad \varphi\in C^\infty_c(I).
  \]
  Then \(aB\in\mathcal D'_c(I)\),
  \[
    \operatorname{supp}(aB)\subset
    \operatorname{supp}(a)\cap\operatorname{supp}(B),
  \]
  and \(a(bB)=(ab)B\).  If \(B=b(t)dt\) is regular, then
  \(aB=(ab)(t)dt\).  No product of two distributions occurs in the
  reduced current model.
\end{lem}

\begin{proof}
  The function \(a\varphi\) is a compactly supported smooth test
  function, so precomposition by \(\varphi\mapsto a\varphi\) defines a
  compactly supported distribution.  If \(\varphi\) is supported away
  from \(\operatorname{supp}(a)\cap\operatorname{supp}(B)\), then
  \(a\varphi\) is supported away from \(\operatorname{supp}(B)\), hence
  \(B(a\varphi)=0\).  Associativity follows from
  \(a(b\varphi)=(ab)\varphi\).  The regular-density formula is the
  displayed integral identity.
\end{proof}

\begin{defn}[Current CE/PV coordinates]
\label{def:app-factorization-current-coordinates}
  Let \(\lambda=B\otimes\rho\in\mathcal P_I\).  The Hamiltonian CE
  coordinate dual to the Hamiltonian current through \(\lambda\) is
  written
  \[
    c_\lambda,\qquad |c_\lambda|=1 .
  \]
  Its PV/current target coordinate is
  \[
    \theta_\lambda=\theta_{B\otimes\rho}:=\Theta_\rho(B).
  \]

  The label \(a(t)dt\otimes f\) denotes the functional on
  \(\mathcal P_I\)
  \[
    B\otimes\rho\longmapsto B(a)\operatorname{Res}(\rho f).
  \]
  The CE coordinate dual to the shifted cotangent generator through this
  functional is
  \[
    u_{a(t)dt\otimes f},\qquad |u_{a(t)dt\otimes f}|=0.
  \]
  Its PV/current target coordinate is the smeared Hamiltonian boundary
  observable
  \[
    O_{a,f}=B_f(a).
  \]
  In the brane realization,
  \[
    B_f(a)=
      \int_I a(t)\,
      \overline{\operatorname{Tr}f(\phi_1(t),\phi_2(t))}\,dt .
  \]
\end{defn}

\begin{defn}[Enlarged reduced defect-current target]
\label{def:app-factorization-enlarged-current-target}
  The reduced defect-current target attached to \(I\) is
  \[
    A_\partial^{\mathrm{cur}}(I)
      =
      \widehat{\mathbf S}(\mathfrak h_I)
      \widehat\otimes
      \widehat{\mathbf S}(\mathcal P_I[1]).
  \]
  This is the same reduced principal-part target denoted
  \(A_\partial^{\mathrm{pp}}(I)\) in the main text; the superscript
  \(\mathrm{cur}\) records the current-interface role in this appendix.
  It enlarges the Hamiltonian target
  \(A_\partial^{\mathrm{Ham}}(I)=\widehat{\mathbf S}(\mathfrak h_I)\)
  by adjoining the odd principal-part current generators
  \(\theta_\lambda=\Theta_\rho(B)\).  The structure maps for
  inclusions of intervals are extension by zero on
  \(\Omega^\bullet_c(I)\) and on \(\mathcal D'_c(I)\).  The
  factorization product on disjoint intervals is the completed
  graded-commutative product after extension by zero.
\end{defn}

\begin{thm}[Universal algebraic current interface]
\label{thm:app-factorization-universal-current-interface}
  For each interval \(I\), the generator assignment
  \[
    \Phi_I^{\mathrm{cur}}(c_\lambda)=\theta_\lambda,\qquad
    \Phi_I^{\mathrm{cur}}(u_{a(t)dt\otimes f})=B_f(a)
  \]
  extends uniquely to a continuous morphism of completed
  graded-commutative algebras from the interval CE cofactorization source
  \(C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_I)\) to the
  reduced defect-current central-operation target
  \(A_\partial^{\mathrm{cur}}(I)\).  On length-one current generators
  the target open-current \(P_0\) brackets are
  \[
  \begin{aligned}
    \{B_f(a),B_g(b)\}
      &=B_{\{f,g\}}(ab),\\
    \{B_f(a),\theta_{B\otimes\rho}\}
      &=\theta_{aB\otimes(f\cdot\rho)}
        =\Theta_{f\cdot\rho}(aB),\\
    \{\theta_{B\otimes\rho},\theta_{C\otimes\sigma}\}
      &=0 .
  \end{aligned}
  \]
  The factorization product and the reduced current source-target
  \(P_0\)-equivariance defects in this reduced current target are strict:
  \[
    H_{\mathrm{fact}}=0,\qquad H_{P_0}=0.
  \]
  This is not a zero Poisson-centre statement for overlapping supports;
  the nonzero Hamiltonian current bracket is the moment-map bracket
  displayed above.  Thus \(u_{a(t)dt\otimes f}\mapsto B_f(a)\) and
  \(c_\lambda\mapsto\theta_\lambda\) form the current-level
  source/target interface used before the admissible bar-cobar/enveloping
  criterion.
\end{thm}

\begin{proof}
  The CE algebra of
  \(\mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1]\) is the
  completed symmetric algebra on the continuous dual shifted by
  \([-1]\).  The coordinate \(c_\lambda\) has degree \(1\), and the
  coordinate \(u_{a(t)dt\otimes f}\) has degree \(0\).  The target
  \(A_\partial^{\mathrm{cur}}(I)\) is the completed symmetric algebra on
  the corresponding current coordinates \(\theta_\lambda\) and
  \(B_f(a)\).  Hence the displayed assignment extends uniquely and
  continuously to the completed graded-commutative algebras.

  The CE differential and the target current brackets use the same
  semidirect Lie structure constants.  The Hamiltonian-current bracket
  in Definition~\ref{def:app-factorization-current-source} gives
  \[
    [a\otimes f,b\otimes g]=ab\otimes\{f,g\},
  \]
  and the boundary realization gives the first displayed bracket.  The
  action of \(a\otimes f\) on \(B\otimes\rho\) is
  \((aB)\otimes(f\cdot\rho)\), giving the second displayed bracket by
  negative transpose under the product pairing
  \[
    \langle B\otimes\rho,\;a\otimes f\rangle
      =B(a)\operatorname{Res}(\rho f).
  \]
  The shifted cotangent current ideal is abelian, giving the third
  bracket.  These three identities are exactly the current form of the
  CE/PV generator identities \(c_\lambda\mapsto\theta_\lambda\) and
  \(u\mapsto O\).  Since the CE differential is a derivation and the
  target bracket is a biderivation, the generator identities determine
  the full completed current interface.

  Factorization compatibility is strict in the cofactorization-source
  convention.  Extension by zero on current Lie algebras induces the CE
  coproduct, and the target product is compatible with pointwise
  products \(ab\) and with the \(C_c^\infty(I)\)-module operation
  \(B\mapsto aB\).
  If two intervals are disjoint, the products have empty support and
  the mixed brackets vanish.  The target product is graded
  commutative, so multiplication by an image generator has zero
  Hochschild product-centrality defect.

  For reduced current \(P_0\)-equivariance, let \(x\) be a length-one source generator and
  let \(Y\) be a homogeneous monomial in the CE source.  The defect
  \[
    D_x(Y)=
    \{\Phi_I^{\mathrm{cur}}(x),\Phi_I^{\mathrm{cur}}(Y)\}
      -\Phi_I^{\mathrm{cur}}(\operatorname{ad}_xY)
  \]
  is a derivation in \(Y\).  The three generator bracket identities
  give \(D_x(Y)=0\) for every length-one \(Y\).  The Leibniz rule gives
  \(D_x(Y)=0\) for every monomial, and continuity extends this to the
  completed algebra.  Thus \(H_{\mathrm{fact}}\) and \(H_{P_0}\) are
  zero equivariance-defect homotopies in the reduced current model.
\end{proof}

\begin{cor}[Principal-part current brackets in monomial coordinates]
\label{cor:app-factorization-principal-part-current-brackets}
\label{prop:app-factorization-principal-part-bracket}
  For \(f=z_1^p z_2^q\), \(a\in C^\infty_c(I)\),
  \(B\in\mathcal D'_c(I)\), and
  \(\rho_{i,j}=z_1^{-i-1}z_2^{-j-1}dz_1dz_2\), one has
  \[
    \{B_{z_1^p z_2^q}(a),\Theta_{\rho_{i,j}}(B)\}
      =
      -(pj-qi+p-q)
      \Theta_{\rho_{i-p+1,j-q+1}}(aB),
  \]
  with negative-index targets equal to zero.  If \(B=b(t)dt\) is
  regular, then the interval factor is \((ab)(t)dt\).
\end{cor}

\begin{proof}
  Proposition~\ref{prop:app-matlis-coadjoint-action} gives
  \[
    z_1^p z_2^q\cdot\rho_{i,j}
      =-(pj-qi+p-q)\rho_{i-p+1,j-q+1},
  \]
  with negative-index terms projected to zero in the principal-part
  module.  Substituting this action into the second bracket of
  Theorem~\ref{thm:app-factorization-universal-current-interface} gives
  the displayed formula.  The regular-current statement is
  Lemma~\ref{lem:app-factorization-current-product}.
\end{proof}

\begin{thm}[BMK current data and finite-window obstruction vector]
\label{thm:app-finite-window-bmk-current-transfer}
  Let
  \(B_0\Subset B_1\Subset B_2\Subset B\subset\C^2\) be nested
  polydisks around the collision point, and choose
  \(\chi\in C_c^\infty(B_2)\) with \(\chi=1\) on \(B_1\).  Put
  \[
    \mc P_{\leq N}
      =
      \bigoplus_{\substack{a,b\geq0\\0<a+b\leq N}}\C\rho_{a,b},
      \qquad
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2 .
  \]
  On \((B_\zeta\times B_z)\setminus\Delta\), set
  \[
    \eta=\zeta-z,\qquad
    r^2=|\eta_1|^2+|\eta_2|^2,\qquad
    d\bar\eta_j=d\bar\zeta_j-d\bar z_j .
  \]
  The Dolbeault homotopy kernel is the
  Bochner--Martinelli--Koppelman current
  \[
    K_{\mathrm{BM}}(\zeta,z)
    =
    \frac{1}{(2\pi i)^2}
    \frac{
      \overline{\eta_1}\,d\bar\eta_2
      -
      \overline{\eta_2}\,d\bar\eta_1
    }{r^4}
    \wedge d\zeta_1\wedge d\zeta_2 .
  \]
  The \(d\bar z_j\)-terms are part of the Koppelman current.  The
  scalar \(d\bar z=0\) component is not enough for the Dolbeault
  homotopy.

  Choose a radial cutoff \(\vartheta_\epsilon(r)\), equal to \(0\) for
  \(r\leq\epsilon\) and to \(1\) for \(r\geq2\epsilon\), and put
  \[
    K_{\chi,\epsilon}
      =
      \chi(\zeta)\chi(z)\vartheta_\epsilon(|\zeta-z|)
      K_{\mathrm{BM}}(\zeta,z).
  \]
  The current limit
  \[
    H_\chi\alpha(z)
      =
      \lim_{\epsilon\to0}
      \int_{\zeta\in B}K_{\chi,\epsilon}(\zeta,z)\wedge\alpha(\zeta)
  \]
  exists on every fixed finite configuration stratum.  For separated
  supports it satisfies
  \[
    |\nabla^kK_{\mathrm{BM}}(\zeta,z)|
      \leq C_k|\zeta-z|^{-3-k}.
  \]

  Let \(i_N:\mc P_{\leq N}\to\mathcal D'_0{}^{0,2}(B)\) be
  \[
    i_N(\rho_{a,b})=\Delta_{a,b}
      =
      \frac{(-1)^{a+b}}{a!\,b!}
      \partial_{z_1}^a\partial_{z_2}^b
      \delta_0\,d\bar z_1\wedge d\bar z_2,
  \]
  normalized by
  \[
    \langle\Delta_{a,b},f\rangle
      =
      \operatorname{Res}_0(\rho_{a,b}f).
  \]
  Define the finite principal-part moment projection on top Dolbeault
  degree by
  \[
    p_N(\alpha)
      =
      \sum_{0<a+b\leq N}
      \left(
        \int_B z_1^az_2^b\,
        \alpha^{0,2}\wedge dz_1\wedge dz_2
      \right)\rho_{a,b}.
  \]
  The data above construct \(H_\chi\), \(p_N\), and \(i_N\), but not a
  native finite-window homotopy on the full compact-support/current
  complex.  The desired identity
  \[
    \bar\partial H_{\chi,N}
    +H_{\chi,N}\bar\partial
    =
    \operatorname{id}-i_Np_N+E_{\chi,N}
  \tag{\(\ast_N^{\mathrm{BMK}}\)}
  \]
  is blocked by
  \[
    \operatorname{Ob}^{\mathrm{BMK\mbox{-}curr}}_N
    =
    \left(
      \operatorname{ob}_{\mathrm{diag}},
      \operatorname{ob}_{\mathrm{an}/\mathrm{fin},N},
      \operatorname{ob}_{\mathfrak h,N},
      \operatorname{ob}_{\mathrm{collar\mbox{-}fact},N}
    \right).
  \]
  The first entry is the annular diagonal sign and scalar of
  \(\bar\partial\vartheta_\epsilon\wedge K_{\mathrm{BM}}\) relative to
  the derivative-delta Matlis convention.  With the displayed kernel and
  real outward boundary orientation the angular mass is \(-1\).  The
  second entry is the gap between the full analytic moment kernel
  \(\ker(\mathcal O(B_1)^\vee\to\mc P_{\le N})\) and the smaller
  support-at-zero span generated by the scalar and high derivative-delta
  currents.  The third entry is
  \[
    \operatorname{ob}_{\mathfrak h,N}
      =
    \pi_N(\mathfrak h\cdot\ker\pi_N),
  \]
  which is nonzero because
  \[
    z_1^{N+2}\cdot\rho_{N+1,0}=-(N+2)\rho_{0,1}.
  \]
  Thus a strict finite support-local quotient killing high modes while
  retaining \(\mc P_{\le N}\) is not compatible with the full Hamiltonian
  action.  The fourth entry is the missing cosheaf/factorization
  compatibility of the collar relation with extension by zero, disjoint
  products, and the BMK homotopy.

  A normalized finite-window identity is available only after changing
  habitat.  If the full analytic BMK contraction is supplied and the
  relative complex is quotiented by representatives of
  \(\ker(\mathcal O(B_1)^\vee\to\mc P_{\le N})\), then the normalized
  homotopy
  \[
    (1-I_{\mathrm{an}}P_{\mathrm{an}})H_\chi
    (1-I_{\mathrm{an}}P_{\mathrm{an}})
  \]
  descends and gives
  \[
    \bar\partial H_{\mathrm{BM},N}
    +H_{\mathrm{BM},N}\bar\partial
    =
    \operatorname{id}-i_Np_N .
  \]
  This is a one-pair analytic quotient, not a native support-local
  factorization-current quotient.

  Keeping the full Taylor tower gives the positive one-pair pro-Matlis
  retract.  Put
  \[
    \widehat{\mc P}_{\Pi}
      =
      \prod_{\substack{a,b\geq0\\a+b>0}}\C\rho_{a,b},
    \qquad
    \mc P_{\mathrm{an}}(B_1)
      =
      \tau\bigl(\mathcal O(B_1)^\vee_{\mathrm{red}}\bigr)
      \subset\widehat{\mc P}_{\Pi},
  \]
  where
  \[
    \tau(\lambda)
      =
      \bigl(\lambda(z_1^az_2^b)\bigr)_{a+b>0}.
  \]
  After the diagonal orientation is fixed and the collar quotient kills
  the cutoff error, the normalized analytic contraction
  \(H_\chi^0=(1-I_{\mathrm{an}}P_{\mathrm{an}})
  H_\chi(1-I_{\mathrm{an}}P_{\mathrm{an}})\) satisfies
  \[
    \bar\partial H_\chi^0+H_\chi^0\bar\partial
    =
    \operatorname{id}-I_{\mathrm{an}}P_{\mathrm{an}}.
  \]
  The pro-analytic moment map
  \(P_{\Pi}^{\mathrm{an}}=\tau P_{\mathrm{an}}\) has compatible finite
  projections
  \[
    \pi_NP_{\Pi}^{\mathrm{an}}=p_N,\qquad
    \pi_{M,N}p_M=p_N .
  \]
  This is a one-pair analytic pro-Matlis statement, not a native
  support-local factorization-current transfer.

  The binary coefficient operation
  \[
    \ell^{\mathrm{BM},N}_2(x,y)=p_N[ix,iy]
  \]
  is retained as the Hamiltonian/Matlis arity-two comparison, read in the
  output window \(\mc P_{\leq N}\), not as a consequence of a native
  finite-window homotopy.  For monomials,
  \[
    \ell^{\mathrm{BM},N}_2
    (z_1^pz_2^q,z_1^rz_2^s)
      =
      (ps-qr)\,
      \operatorname{pr}_{\leq N}
      (z_1^{p+r-1}z_2^{q+s-1})
      \pmod{\C},
  \]
  and
  \[
    \ell^{\mathrm{BM},N}_2(z_1^pz_2^q,\rho_{i,j})
      =
      -(pj-qi+p-q)\,
      \operatorname{pr}_{\leq N}
      \rho_{i-p+1,j-q+1},
  \]
  with negative-index targets equal to zero, while
  \[
    \ell^{\mathrm{BM},N}_2(\rho,\sigma)=0 .
  \]
  Thus the arity-two cotangent coefficient comparison is the Matlis
  coadjoint action of
  Proposition~\ref{prop:app-matlis-coadjoint-action}.

  Only after the finite-current gate
  \(\operatorname{Ob}^{\mathrm{BMK\mbox{-}curr}}_N\) is killed, or
  replaced by a genuine native factorization-current habitat, does the
  strict all-window and arity-three extension become the following
  obstruction vector.  Set
  \[
    Q_{\oplus}=\widehat{\mc P}_{\Pi}/\mc P .
  \]
  For \(\alpha\in\Omega_c^{0,2}(B)\), put
  \[
    \operatorname{mom}_{\infty}(\alpha)
      =
      \left(
        \int_B z_1^az_2^b\,
        \alpha^{0,2}\wedge dz_1\wedge dz_2
      \right)_{a+b>0}
      \in\widehat{\mc P}_{\Pi},
  \]
  and
  \[
    \operatorname{ob}_{\oplus}(\alpha)
      =
      [\operatorname{mom}_{\infty}(\alpha)]
      \in Q_{\oplus} .
  \]
  This class is zero exactly when the all-window moment sequence lands in
  the direct-sum Matlis module \(\mc P\).

  The pro-product tower does not repair the native current problem by
  itself.  There is no support-local compact-current section
  \[
    i_\Pi:\widehat{\mc P}_{\Pi}\to\mathcal D'_0{}^{0,2}(B)
  \]
  extending the finite derivative-delta sections \(i_N\): a distribution
  supported at one point has finite order.  This is
  \(\operatorname{ob}_{I_\Pi}\).  The full formal Hamiltonian algebra also
  fails to act on \(\widehat{\mc P}_{\Pi}\).  For
  \(f=\sum_{p\ge2}z_1^p\) and
  \(\lambda=\sum_{p\ge2}\rho_{p-1,0}\), the
  \(\rho_{0,1}\)-coefficient of \(f\cdot\lambda\) would be
  \(-\sum_{p\ge2}p\).  This undefined coefficient is
  \(\operatorname{ob}_{\mathfrak h,\Pi}\).

  The collar part is the finite-window family
  \[
    \operatorname{ob}_{\mathrm{collar},\Pi,N}
      =
      E_{\chi,N}
      \in
      \operatorname{Hom}\!
      \left(\Omega_c^{0,\bullet}(B),
      \mathcal D'{}^{0,\bullet}(B)\right)_{\operatorname{supp}d\chi}.
  \]
  The first arity-three obstruction is
  \[
    \operatorname{ob}^{\chi}_{3,\Pi,N}(x,y,z)
      =
      p_N[H_{\mathrm{BM},N}([ix,iy]-i\ell^{\mathrm{BM},N}_2(x,y)),iz]
      +\operatorname{cyc}_{x,y,z}.
  \]
  It vanishes on separated-support strata by the displayed estimates.
  On the coefficient collision stratum its non-collar part is the
  Jacobiator of \(\mathfrak h\ltimes\mc P[1]\), hence zero.  The
  remaining part is supported on the small diagonal and on the cutoff
  collar.

  Finally, let \(C_{s,N}\) be the optimal constants for the chosen
  finite-window seminorm estimates of
  \(H_{\chi,N}\), \(p_N\), \(E_{\chi,N}\), and
  \(\operatorname{ob}^{\chi}_{3,\Pi,N}\).  The uniformity obstruction is
  \[
    \operatorname{ob}_{\mathrm{unif},\Pi}
      =
      \left(\left[(C_{s,N})_{N\geq1}\right]\right)_s
      \in
      \prod_s
      \left(
        \prod_{N\geq1}\R_{\geq0}\big/\ell^\infty_N
      \right).
  \]
  Thus the all-window obstruction vector is
  \[
    \operatorname{Ob}^{\Pi}_{\mathrm{BM}}
      =
      \left(
      \operatorname{ob}_{\oplus},
      \operatorname{ob}_{I_\Pi},
      \operatorname{ob}_{\mathfrak h,\Pi},
      (\operatorname{ob}_{\mathrm{collar},\Pi,N})_N,
      (\operatorname{ob}^{\chi}_{3,\Pi,N})_N,
      \operatorname{ob}_{\mathrm{unif},\Pi}
      \right).
  \]
  Any strict native all-window current \(E_2\) transfer extending the
  displayed binary coefficient comparison forces this vector to vanish.
  The first, second, third, and sixth entries are nonzero in the native
  current topology; the collar and ternary entries are exact primitive
  construction targets.  The proved theorem here is the BMK current data,
  the finite-window obstruction vector, the positive one-pair analytic
  pro-Matlis retract, and the arity-two Hamiltonian/Matlis comparison.

  The principal-part face remains two-variable:
  \[
    \frac{1}{(2\pi i)^2}
    \frac{d\zeta_1\wedge d\zeta_2}
         {(\zeta_1-z_1)(\zeta_2-z_2)}
    =
    \sum_{a,b\geq0}z_1^az_2^b\rho_{a,b}(\zeta).
  \]
  Killing \(z_2\) kills the Hamiltonian bracket, and the \(b=0\)
  principal-part line is not stable since
  \(z_1\cdot\rho_{a,0}=-\rho_{a,1}\).  No curve VOA, Zhu algebra, or
  one-variable transfer follows from this theorem.
\end{thm}

\begin{proof}
  The Bochner--Martinelli--Koppelman identity gives the Dolbeault
  homotopy on the punctured product \(B_\zeta\times B_z\setminus\Delta\).
  Multiplication by the cutoff gives the exact derivative split
  \[
    \bar\partial(\chi(\zeta)\chi(z)
      \vartheta_\epsilon K_{\mathrm{BM}})
    =
    \chi\chi\,\vartheta_\epsilon\,\bar\partial K_{\mathrm{BM}}
    +\bar\partial(\chi\chi)\,\vartheta_\epsilon K_{\mathrm{BM}}
    +\chi\chi\,\bar\partial\vartheta_\epsilon\wedge K_{\mathrm{BM}} .
  \]
  The middle term is collar-supported.  The last term is the annular
  diagonal current, not a collar term; its sign and scalar are exactly
  \(\operatorname{ob}_{\mathrm{diag}}\).  Since \(K_{\mathrm{BM}}\) has
  size \(r^{-3}\) in real dimension four, the cutoff current has a limit
  on every fixed finite configuration stratum.  This proves the current
  data, not the finite-window identity on the full current complex.

  The formula for \(i_N\) is fixed by integration by parts:
  \[
    \left\langle
      \frac{(-1)^{a+b}}{a!\,b!}
      \partial_{z_1}^a\partial_{z_2}^b\delta_0,\,
      f
    \right\rangle
    =
    [z_1^az_2^b]f
    =
    \operatorname{Res}_0(\rho_{a,b}f).
  \]
  Hence \(i_Np_N\) is the finite support-at-collision projector with the
  Matlis residue normalization, after the diagonal-current orientation is
  tied to that convention.

  The native finite-window identity is obstructed already on closed top
  currents in the kernel of the finite moment map.  If
  \(T=\Delta_{N+1,0}\), then \(p_N(T)=0\) but
  \(\langle T,z_1^{N+1}\rangle=1\).  A putative identity
  \(T=\bar\partial S\) would give
  \(\langle T,z_1^{N+1}\rangle=0\) by Stokes.  The scalar
  \(\Delta_{0,0}\) is the same obstruction for the removed reduced
  principal-part line.  More strongly, a strict support-local quotient
  must be an \(\mathfrak h\)-submodule quotient; the calculation
  \(z_1^{N+2}\cdot\rho_{N+1,0}=-(N+2)\rho_{0,1}\) contradicts killing
  \(\rho_{N+1,0}\) while retaining \(\rho_{0,1}\).

  The one-pair analytic quotient works for the reason stated in the
  theorem: after choosing the full analytic projector \(I_{\mathrm{an}}
  P_{\mathrm{an}}\), the normalized homotopy kills representatives of
  \(\ker\pi_N\), descends to the quotient, and identifies the analytic
  projector with \(i_Np_N\).  Keeping the Taylor tower instead gives the
  pro-analytic map \(P_{\Pi}^{\mathrm{an}}=\tau P_{\mathrm{an}}\), and
  the equality \(\pi_NP_{\Pi}^{\mathrm{an}}=p_N\) is just functoriality
  of Taylor moments under finite truncation.  Its dependence on analytic
  representatives and on the chosen pair prevents it from being a native
  factorization quotient.

  The arity-two coefficient comparison is the residue transpose.  For
  Hamiltonian labels it is the Poisson bracket modulo constants,
  truncated only after the output coefficient is computed.  For cotangent
  principal parts, Proposition~\ref{prop:app-matlis-coadjoint-action}
  gives
  \[
    \operatorname{Res}_0((f\cdot\rho)g)
      =
      -\operatorname{Res}_0(\rho\,\{f,g\}),
  \]
  which is the displayed coadjoint formula.  The shifted cotangent ideal
  is abelian, so the \((\rho,\sigma)\)-operation is zero.

  The displayed ternary expression is only the next obstruction after the
  finite-current gate has been crossed.  The separated-support estimate
  makes it vanish away from collisions.  On the coefficient collision
  stratum the semidirect Lie algebra \(\mathfrak h\ltimes\mc P[1]\)
  satisfies Jacobi.  Therefore any surviving term is a collar,
  small-diagonal, or completed-window transfer residue, recorded as the
  finite-window representative \(\operatorname{ob}^{\chi}_{3,\Pi,N}\)
  of the \(\Pi\)-tower class only after the finite-current
  obstruction has been removed.

  A strict native all-window current transfer would have to replace the
  compatible family \(p_N\) by a single moment map landing in
  \(\mc P\), construct a compact-current section of the pro-product
  tower, define the full formal Hamiltonian action on that tower, remove
  \(E_{\chi,N}\) compatibly with extension by zero, kill the ternary
  collar residue by compatible primitives, and supply uniform estimates
  in the completed window topology.  These six requirements are
  precisely the six entries of \(\operatorname{Ob}^{\Pi}_{\mathrm{BM}}\).
  The all-window theorem target is a changed native habitat where these
  six witnesses exist, or the displayed obstruction theorem.  It is not
  asserted from the finite-window calculation alone and does not bypass
  \(\operatorname{Ob}^{\mathrm{BMK\mbox{-}curr}}_N\).

  The Cauchy expansion is the Laurent expansion in the two holomorphic
  variables and records the same residue basis.  The calculation
  \(z_1\cdot\rho_{a,0}=-\rho_{a,1}\), from
  Proposition~\ref{prop:app-matlis-coadjoint-action}, rules out the
  \(b=0\) principal-part truncation as a native submodule.
\end{proof}

\begin{thm}[Normal \(\Omega\)-weighted brane-current brackets]
\label{thm:app-omega-weighted-current-brackets}
  Use the normal brane-preserving equivariant parameters of the local
  dictionary:
  \(t\) has weight \(0\),
  \(z_1,z_2\) have weights \(\epsilon_1,\epsilon_2\), and
  \[
    \chi_\omega=\epsilon_1+\epsilon_2,\qquad
    \operatorname{wt}_\Omega(\hbar_\omega)=\chi_\omega .
  \]
  Put
  \[
    B_{p,q}(a):=B_{z_1^p z_2^q}(a),\qquad
    \Theta_{r,s}(B):=\Theta_{\rho_{r,s}}(B),
  \]
  with \(p,q,r,s\geq0\), \(p+q>0\), \(r+s>0\), and
  \(\rho_{r,s}=z_1^{-r-1}z_2^{-s-1}dz_1dz_2\).
  The compactly supported test function \(a\) and compactly supported
  current \(B\) live on the fixed brane line and have weight \(0\).  Hence
  \[
    \operatorname{wt}_\Omega B_{p,q}(a)=p\epsilon_1+q\epsilon_2,
    \qquad
    \operatorname{wt}_\Omega \Theta_{r,s}(B)
      =-r\epsilon_1-s\epsilon_2 .
  \]

  Off the self-dual locus the Hamiltonian current bracket is not a scalar
  bracket unless one either keeps the inverse symplectic-character line or
  adjoins \(\hbar_\omega\).  In the scalarized convention the
  length-one current brackets are
  \[
  \begin{aligned}
    \{B_{p,q}(a),B_{r,s}(b)\}_{\Omega}
      &=
      \hbar_\omega(ps-qr)\,
      B_{p+r-1,q+s-1}(ab),\\
    \{B_{p,q}(a),\Theta_{r,s}(B)\}_{\Omega}
      &=
      -\hbar_\omega(ps-qr+p-q)\,
      \Theta_{r-p+1,s-q+1}(aB),\\
    \{\Theta_{r,s}(B),\Theta_{u,v}(C)\}_{\Omega}
      &=0 .
  \end{aligned}
  \]
  Here \(B_{\alpha,\beta}=0\) if \(\alpha<0\), \(\beta<0\), or
  \((\alpha,\beta)=(0,0)\), and
  \(\Theta_{\alpha,\beta}=0\) if \(\alpha<0\), \(\beta<0\), or
  \((\alpha,\beta)=(0,0)\).  The last convention only records the reduced
  scalar-annihilator target; when the coadjoint formula lands at
  \(\rho_{0,0}\) its coefficient is already zero.

  Equivalently, before adjoining \(\hbar_\omega\), remove the displayed
  factor \(\hbar_\omega\) and read the first two brackets as valued in the
  inverse symplectic-character line
  \(\mathbb L_\omega^{-1}\), where
  \(\operatorname{wt}_\Omega(\mathbb L_\omega)=\chi_\omega\).
  On the self-dual specialization
  \(\epsilon_1+\epsilon_2=0\), the line is trivial.  After choosing the
  trivialization \(\hbar_\omega=1\), the formulas reduce to the
  non-equivariant brackets of
  Theorem~\ref{thm:app-factorization-universal-current-interface} and
  Corollary~\ref{cor:app-factorization-principal-part-current-brackets}.
  This specialization is a separate branch; it is not obtained by
  inverting \(\chi_\omega\) and then setting \(\chi_\omega=0\).

  For an inclusion of intervals \(j:I\hookrightarrow J\), extension by zero
  has weight \(0\) and satisfies
  \[
    j_!B_{p,q,I}(a)=B_{p,q,J}(j_!a),\qquad
    j_!\Theta_{r,s,I}(B)=\Theta_{r,s,J}(j_!B),
  \]
  together with
  \[
    j_!\{x,y\}_{\Omega,I}
      =
    \{j_!x,j_!y\}_{\Omega,J}
  \]
  for the displayed length-one generators.  For disjoint intervals the
  mixed brackets vanish after extension to a common interval.

  These statements are algebraic current identities.  They hold for all
  \(B,C\in\mathcal D'_c(I)\) because the only distributional operation is
  multiplication of a current by a smooth compactly supported function.
  They do not assert a normal-\(\Omega\) Costello graph theorem for
  arbitrary distributional labels.  A graph-level lift must still restrict
  cotangent labels to regular densities or to graphwise
  wavefront-admissible tuples as in
  Propositions~\ref{prop:app-regular-density-costello-graph-kernel} and
  \ref{prop:app-wavefront-admissible-costello-graph-kernel}, and must add
  the \(Q_\Omega\)-Cartan package, normal-weight contraction,
  residue/Euler normalization choice, equivariant counterterms, and the
  scalar/non-scalar QME obstruction classes.
\end{thm}

\begin{proof}
  The weight assignments are forced by the normal torus action:
  \(z_1^pz_2^q\) has character \(p\epsilon_1+q\epsilon_2\), while
  \[
    z_1^{-r-1}z_2^{-s-1}dz_1dz_2
  \]
  has character
  \(-(r+1)\epsilon_1-(s+1)\epsilon_2+\chi_\omega
  =-r\epsilon_1-s\epsilon_2\).  The brane-line variables and currents are
  in the fixed \(t\)-direction, so they add no equivariant character.

  The Poisson bivector
  \(\partial_{z_1}\wedge\partial_{z_2}\) has character
  \(-\chi_\omega\).  Thus the ordinary Hamiltonian bracket has weight
  \(\operatorname{wt}(f)+\operatorname{wt}(g)-\chi_\omega\).  Multiplying by
  \(\hbar_\omega\) makes the bracket scalar and weight-preserving.  On
  monomials this gives
  \[
    [z_1^pz_2^q,z_1^rz_2^s]_\Omega
      =
      \hbar_\omega(ps-qr)z_1^{p+r-1}z_2^{q+s-1},
  \]
  followed by the quotient by constants.  Substitution in the first
  bracket of
  Theorem~\ref{thm:app-factorization-universal-current-interface} gives
  the displayed \(B\)-\(B\) formula.

  For the cotangent current, the coadjoint action of
  Proposition~\ref{prop:app-matlis-coadjoint-action} gives
  \[
    z_1^pz_2^q\cdot\rho_{r,s}
      =
      -(ps-qr+p-q)\rho_{r-p+1,s-q+1}.
  \]
  Scalarizing the Hamiltonian action by the same \(\hbar_\omega\) gives
  the \(B\)-\(\Theta\) formula, and the shifted cotangent current ideal is
  abelian.  Each right-hand side has total weight equal to the sum of the
  weights of the two inputs, so the formulas are
  \(T_\Omega\)-homogeneous.

  Extension by zero commutes with multiplication of compactly supported
  test functions and currents:
  \(j_!(ab)=(j_!a)(j_!b)\) and
  \(j_!(aB)=(j_!a)(j_!B)\).  Hence it commutes with all three displayed
  brackets.  If two intervals are disjoint inside a common interval, these
  products are zero, so the mixed brackets vanish.

  Finally, no singular product of two compactly supported distributions is
  used in the algebraic current formulas.  Costello graph weights are
  different: after pushing current labels through graph incidence maps one
  must multiply them by singular propagator boundary values and extend
  across collision diagonals.  The wavefront and scaling-degree hypotheses
  in
  Propositions~\ref{prop:app-wavefront-admissible-costello-graph-kernel}
  and~\ref{prop:app-current-compatible-Dprimec-theorem-surface} are exactly
  the missing analytic conditions.  The \(\Omega\)-weights and the factor
  \(\hbar_\omega\) do not remove those microlocal conditions.
\end{proof}

\begin{cor}[Smeared Hamiltonian source convention]
\label{cor:app-factorization-source-of-B}
\label{prop:app-factorization-source-of-B}
  The smeared boundary Hamiltonian observable is sourced by the
  shifted-cotangent CE coordinate:
  \[
    u_{a(t)dt\otimes f}\longmapsto
    B_f(a)
      =\int_I a(t)\,
        \overline{\operatorname{Tr}
        f(\phi_1(t),\phi_2(t))}\,dt .
  \]
  The Hamiltonian CE coordinate \(c_\lambda\) maps to the PV/current
  vector \(\theta_\lambda\), not to \(B_f(a)\).  Consequently
  \[
    \{B_f(a),B_g(b)\}=B_{\{f,g\}}(ab)
  \]
  is the degree-zero moment-map shadow of the CE/PV identity
  \(c_\lambda\mapsto\theta_\lambda,\ u\mapsto O\).
\end{cor}

\begin{proof}
  The coordinate \(u_{a(t)dt\otimes f}\) is dual to the shifted
  cotangent generator through the pairing with
  \(\mathcal P_I\).  Under the CE/PV isomorphism it maps to the
  function coordinate \(O_{a,f}\), realized on the brane by the
  displayed trace integral.  The coordinate \(c_\lambda\) is dual to a
  Hamiltonian current and maps to the vector/current coordinate
  \(\theta_\lambda\).  The bracket identity is the first bracket of
  Theorem~\ref{thm:app-factorization-universal-current-interface};
  equivalently, it is the equal-time Poisson bracket smeared against
  \(a(t)b(s)\delta(t-s)\), which produces the pointwise product \(ab\).
\end{proof}

\begin{rmk}[Orientation reversal]
\label{rmk:app-factorization-orientation-reversal}
  The orientation convention is the ordinary convention for oriented
  one-forms and current one-forms.  The labels \(a(t)dt\) and regular
  currents \(B=b(t)dt\) transform by pullback,
  \(a(\psi(s))\psi'(s)\,ds\) and \(b(\psi(s))\psi'(s)\,ds\).  No
  additional sign is inserted from
  \(u_{a(t)dt\otimes f}\), \(c_\lambda\), \(\theta_\lambda\), or the
  principal-part label \(\rho\).  If the written one-form is held fixed
  while only the chosen orientation is reversed, the sign is exactly the
  sign of \(dt\).
\end{rmk}

\begin{rmk}[Boundary of the algebraic current theorem]
\label{rmk:app-factorization-residual}
  Theorem~\ref{thm:app-factorization-universal-current-interface}
  proves the algebraic distributional-current interface.  It does not
  identify \(\Theta_\rho(B)\) with a finite polynomial BV observable,
  construct the primitive cumulant projection before reduction, solve
  the full de Rham-current BV differential, or prove the mixed
  brane-defect QME.  It also does not supply Costello renormalized
  graph weights.  Those statements require the unreduced current
  complex, scalar cancellation data, Tate/weighted coefficient kernel,
  and brane-defect propagator specified in
  Appendix~\ref{sec:app-unreduced-bv-qme} and
  Problem~\ref{prob:analytic-graph-realization}.
\end{rmk}

\begin{defn}[Unreduced non-scalar current lift datum]
\label{def:app-unreduced-nonscalar-current-lift-datum}
  Fix an oriented interval
  \(I\subset\R_{\mathrm{brane}}\subset\R^2_{\mathrm{top}}\), an
  admissible weight \(w\) on the Hamiltonian degree of
  \(\widehat{\C^2}_{0,\mathrm{hol}}\), and the Moyal parameter
  \(\hbar\).  A non-scalar Costello current lift of the reduced interface
  for the local mixed HT model consists of the following data.
  \begin{enumerate}
    \item A source current complex
    \[
      \mathfrak g^{w,\mathrm{cur}}_{\hbar,I}
        =
        \bigl(\Omega^\bullet_c(I)\widehat\otimes
        \mathfrak h_{w,\hbar}\bigr)
        \ltimes
        \bigl(\mathcal D'_c(I)\widehat\otimes
        \mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}\bigr)[1],
    \]
    or, before scalar reduction, the corresponding central-character
    replacement of
    Definition~\ref{def:app-central-character-principal-part-current-algebra}.
    \item A target defect local-functional complex
    \[
      \mathfrak Q^\bullet_{w,\partial,\hbar}(I)
        =
        \left(
        \mathcal O_{\mathrm{loc}}^{\mathrm{bd}}\bigl(
          \mathcal E_w|_I;\,
          A^{\mathrm{pp},w}_{\partial,\hbar}(I)\bigr),
        d_{\mathrm{QME}}=Q+\{I_0^w,-\}_{\hbar}
        \right),
    \]
    together with the finite-scale BV Laplacian and propagator whenever
    the Costello scale-\(L\) QME has not been absorbed into
    \(d_{\mathrm{QME}}\).
    Here \(\mathcal E_w\) is the weighted local mixed HT field complex on
    \(\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\),
    restricted to the brane-defect interval \(I\); the coefficient
    algebra is the weighted Hamiltonian/Moyal algebra of the same formal
    holomorphic symplectic disk.
    \item A continuous bulk-to-defect kernel, equivalently a Maurer--Cartan
    candidate in the completed convolution Lie algebra,
    \[
      \kappa_{\hbar,w,I}\colon
      C^\bullet_{\mathrm{CE},\mathrm{cont}}
      (\mathfrak g^{w,\mathrm{cur}}_{\hbar,I})
      \longrightarrow
      \mathfrak Q^\bullet_{w,\partial,\hbar}(I),
    \]
    whose generator values are representatives
    \[
      u_{a(t)dt\otimes f}\longmapsto B_f^{\mathrm{BV}}(a),
      \qquad
      c_{B,\rho}\longmapsto\Theta_\rho^{\mathrm{BV}}(B).
    \]
    \item A \(d_{\mathrm{QME}}\)-stable scalar-contact filtration and a
    filtered chain projection
    \[
      \widehat\sigma_{\mathrm{sc}}\colon
      \mathfrak Q^\bullet_{w,\partial,\hbar}(I)
      \longrightarrow
      C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]]
    \]
    whose associated graded is the scalar-symbol map of
    Definition~\ref{def:app-scalar-obstruction-complex}.
    \item Product centrality homotopies and \(P_0\)-bracket homotopies
    against arbitrary unreduced open observables, not only against the
    freely adjoined current generators of the reduced target.
  \end{enumerate}
  The reduced algebraic theorem supplies only the image of this datum
  after scalar reduction, de Rham-current contraction, and passage to the
  added principal-part current target.
\end{defn}

\begin{defn}[Bulk-to-defect convolution habitat]
\label{def:app-bulk-defect-convolution-habitat}
  With \(I,w,\hbar\) as in
  Definition~\ref{def:app-unreduced-nonscalar-current-lift-datum}, and
  with all Hamiltonian coefficients taken from the local formal
  holomorphic disk of
  Proposition~\ref{prop:app-local-unimodular-current-kernel-input}, put
  \[
    \mathbf K^\bullet_{w,\partial,\hbar}(I)
      =
      \operatorname{Hom}_{\mathrm{cont}}\!\left(
      C^\bullet_{\mathrm{CE},\mathrm{cont}}
      (\mathfrak g^{w,\mathrm{cur}}_{\hbar,I}),
      \mathfrak Q^\bullet_{w,\partial,\hbar}(I)\right).
  \]
  The topology is the complete filtration topology generated by the
  \(\hbar\)-adic filtration, the scalar-contact filtration, and the
  finite-window Mittag--Leffler filtration.  Thus a sequence of kernels
  converges exactly when all of its finite-window, scalar-contact, and
  \(\hbar\)-adic projections converge.  The differential and bracket are
  the completed convolution operations
  \[
    d_{\mathbf K}T=d_{\mathrm{QME}}T-(-1)^{|T|}T\,d_{\mathrm{CE}},
    \qquad
    [T_1,T_2]_{\mathbf K}
      =[-,-]_{\hbar}\circ(T_1\widehat\otimes T_2)\circ\Delta_{\mathrm{CE}},
  \]
  where \(\Delta_{\mathrm{CE}}\) is the completed CE coproduct and
  \([-,-]_{\hbar}\) is the target \(P_{0,\hbar}\)/BV bracket.  For a
  degree-zero kernel candidate \(\kappa\), its curvature is
  \[
    \operatorname{Curv}_{\mathbf K}(\kappa)
      =
      d_{\mathbf K}\kappa
      +\frac12[\kappa,\kappa]_{\mathbf K}
      \in \mathbf K^1_{w,\partial,\hbar}(I).
  \]
  On generators, the term \(-\kappa d_{\mathrm{CE}}\) is exactly the
  source-bracket subtraction appearing in the bracket-defect formulas
  below.
\end{defn}

\begin{prop}[Bulk-to-defect coefficient-current kernel layer]
\label{prop:app-bulk-defect-kernel-layer}
  In the local mixed HT model on
  \(\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\), there is
  a canonical degree-zero continuous coefficient-current kernel
  \[
    \kappa^{\mathrm{coef}}_{\hbar,w,I}
      \in \mathbf K^0_{w,\partial,\hbar}(I)
  \]
  whose generator values are
  \[
    \kappa^{\mathrm{coef}}_{\hbar,w,I}
      (u_{a(t)dt\otimes f})
      =\iota_I\bigl(B^w_f(a)\bigr),
    \qquad
    \kappa^{\mathrm{coef}}_{\hbar,w,I}(c_{B,\rho})
      =\iota_I\bigl(\Theta^w_\rho(B)\bigr).
  \]
  Here
  \(a\in C^\infty_c(I)\), \(f\in\mathfrak h_{w,\hbar}\),
  \(B\in\mathcal D'_c(I)\), and
  \(\rho\in\mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}\).  The map
  \(\iota_I\) is the coefficient inclusion of
  \(A^{\mathrm{pp},w}_{\partial,\hbar}(I)\) as field-independent
  defect-local functionals in
  \(\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\).  The degrees are
  \[
    |u_{a(t)dt\otimes f}|=|B^w_f(a)|=0,\qquad
    |c_{B,\rho}|=|\Theta^w_\rho(B)|=1.
  \]
  The kernel has the following proved properties.
  \begin{enumerate}
    \item For each finite Hamiltonian window \(M\) in the formal
    holomorphic Hamiltonian degree, its restriction
    \(\kappa^{\mathrm{coef},M}_{\hbar,w,I}\) lands in
    \[
      \mathcal O_{\mathrm{loc}}^{\mathrm{bd}}\bigl(
        \mathcal E_w^M|_I;\,
        A_{\partial,\hbar}^{\mathrm{pp},w,M}(I)\bigr)
    \]
    and the finite-window maps satisfy
    \[
      \pi_{M,N}\kappa^{\mathrm{coef},M}_{\hbar,w,I}
        =
      \kappa^{\mathrm{coef},N}_{\hbar,w,I}\pi_{M,N}^{\mathrm{CE}},
      \qquad M\geq N.
    \]
    For admissible weights \(w,w'\), the diagonal transport maps satisfy
    \[
      R^M_{w,w'}\kappa^{\mathrm{coef},M}_{\hbar,w,I}
        =
      \kappa^{\mathrm{coef},M}_{\hbar,w',I}R^{M,\mathrm{CE}}_{w,w'}.
    \]
    Hence the displayed finite-window kernels determine the unique
    strict Mittag--Leffler inverse-limit kernel
    \(\kappa^{\mathrm{coef}}_{\hbar,w,I}\).
    \item After setting \(\hbar=0\), applying scalar reduction and the
    de Rham-current contraction, the kernel is exactly
    \(\Phi_I^{\mathrm{cur}}\) of
    Theorem~\ref{thm:app-factorization-universal-current-interface}.
    \item Inside the freely adjoined coefficient-current subalgebra, the
    generator \(P_{0,\hbar}\)-defects vanish:
    \[
      \{B^w_f(a),B^w_g(b)\}_{\hbar}
        =B^w_{\{f,g\}_{\hbar}}(ab),
    \]
    \[
      \{B^w_f(a),\Theta^w_\rho(B)\}_{\hbar}
        =
      \Theta^w_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}(aB),
      \qquad
      \{\Theta^w_\rho(B),\Theta^w_\sigma(C)\}_{\hbar}=0.
    \]
    \item Let \(\kappa_{\hbar,w,I}\) be any Costello-local-functional lift
    of this coefficient kernel.  If its curved Maurer--Cartan equation has
    been solved through order \(\hbar^{n-1}\), then the order-\(n\)
    component of
    \(\operatorname{Curv}_{\mathbf K}(\kappa_{\hbar,w,I})\) is
    \(d_{\mathrm{QME}}\)-closed modulo the already solved lower-order
    terms.  If the filtered scalar projection exists and its scalar image
    is zero, each fixed source-arity or graph component gives, by
    evaluation, a residual class in
    \[
      H^1\!\left(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}}\right).
    \]
    Equivalently, the assembled curvature coefficient is a class in the
    corresponding Hom-valued obstruction complex; this is the class denoted
    \([\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]\) in
    Problem~\ref{prob:quantum-p0-operation-realization}.
    Its compatible finite-window counterterm obstruction is precisely the
    inverse-limit \(H^1\) class together with the
    \(\varprojlim^1H^0\) primitive-compatibility class of
    Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.
  \end{enumerate}
  This proposition constructs only the local coefficient-current kernel
  layer.  It does not construct a Costello graph kernel for arbitrary
  \(B\in\mathcal D'_c(I)\).  The missing analytic theorem is the following:
  for every finite window and every defect-current-labelled graph, the
  products of the finite-scale propagators with the pushed-forward compactly
  supported currents must satisfy H\"ormander wavefront transversality, admit
  local extensions across the relevant small diagonals, and produce
  counterterms compatible with interval extension, finite-window
  truncation, and admissible weight transport.  Without that theorem the
  graph-level lift is proved only after restricting the cotangent labels to
  regular compactly supported densities or to a wavefront-admissible class,
  or else remains an obstruction problem.  No compact target or global
  BCOV theorem is invoked.
\end{prop}

\begin{proof}
  By
  Proposition~\ref{prop:app-local-unimodular-current-kernel-input}, the
  source Lie brackets and principal-part pairings are the formal-disk
  Hamiltonian brackets and residues tensored with interval currents.  The
  continuous CE cochain algebra is the completed graded-symmetric
  algebra on the continuous dual of
  \(\mathfrak g^{w,\mathrm{cur}}_{\hbar,I}[1]\).  The target coefficient
  algebra \(A^{\mathrm{pp},w}_{\partial,\hbar}(I)\) is the completed
  graded-symmetric algebra on the matching Hamiltonian-current generators
  \(B^w_f(a)\) and cotangent-current generators \(\Theta^w_\rho(B)\).
  The displayed assignment therefore extends uniquely to a continuous
  completed graded-commutative algebra map.  Since the source and target
  generators have the displayed equal degrees, the resulting element of the
  convolution habitat has degree \(0\).

  Windowwise, the same construction is finite-dimensional in the coefficient
  direction, with \(D_{w,\leq M}\) and
  \(A_{\partial,\hbar}^{\mathrm{pp},w,M}(I)\) as in
  Definition~\ref{defn:wt-nonscalar-qme-tower}.  Truncation merely discards
  coefficient degrees \(d>N\), while \(R^M_{w,w'}\) rescales each surviving
  degree-\(d\) basis vector and its dual by inverse factors.  The formulas
  for \(B^w_f(a)\) and \(\Theta^w_\rho(B)\) are degreewise identities, so
  they commute with truncation and with weight transport.  The strict
  Mittag--Leffler universal property gives the inverse-limit kernel.

  The reduction statement follows by forgetting the Moyal deformation,
  applying the scalar quotient, and contracting the de Rham current
  direction.  The two generator formulas become
  \(u_{a(t)dt\otimes f}\mapsto B_f(a)\) and
  \(c_{B,\rho}\mapsto\Theta_\rho(B)\), which are precisely the generators
  of Theorem~\ref{thm:app-factorization-universal-current-interface}.

  The three displayed bracket identities are the weighted Moyal version of
  the semidirect-product calculation in
  Theorem~\ref{thm:app-factorization-universal-current-interface}: the
  Hamiltonian-current bracket gives the pointwise product \(ab\), the
  cotangent action is multiplication \(B\mapsto aB\) together with the
  Moyal coadjoint action, and the shifted cotangent current ideal is
  abelian.  By biderivation, the identities extend from generators to the
  completed coefficient-current subalgebra.

  Finally, the convolution habitat is a filtered dg Lie algebra.  The
  Bianchi identity
  \[
    d_{\mathbf K}\operatorname{Curv}_{\mathbf K}(\kappa)
      +[\kappa,\operatorname{Curv}_{\mathbf K}(\kappa)]_{\mathbf K}=0
  \]
  implies, order by order in \(\hbar\), that the first unsolved curvature
  coefficient is closed for the linearized differential.  Under the chosen
  scalar projection, zero scalar image places every evaluated component in
  \(\ker\widehat\sigma_{\mathrm{sc}}\), equivalently places the assembled
  coefficient in the Hom-valued kernel.  Adding a degree-zero local
  counterterm changes the first unsolved coefficient by the corresponding
  \(d_{\mathrm{QME}}\)-boundary, and the finite-window compatibility of
  such primitives is exactly the Milnor obstruction measured in
  Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.  This proves the
  stated obstruction class and leaves only the analytic distributional
  graph-extension theorem named in the statement.
\end{proof}

\begin{prop}[Regular-density Costello graph kernel layer]
\label{prop:app-regular-density-costello-graph-kernel}
  Let
  \[
    \mathcal D^{\mathrm{reg}}_c(I)
      =\{\,b(t)dt\mid b\in C^\infty_c(I)\,\}
      \subset \mathcal D'_c(I)
  \]
  and let
  \[
    \mathfrak g^{w,\mathrm{reg}}_{\hbar,I}
      =
      \bigl(\Omega^\bullet_c(I)\widehat\otimes
      \mathfrak h_{w,\hbar}\bigr)
      \ltimes
      \bigl(\mathcal D^{\mathrm{reg}}_c(I)\widehat\otimes
      \mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}\bigr)[1]
      \subset
      \mathfrak g^{w,\mathrm{cur}}_{\hbar,I}.
  \]
  Put \(\mathbf K^{\bullet,\mathrm{reg}}_{w,\partial,\hbar}(I)\) for the
  corresponding completed convolution Hom obtained from
  Definition~\ref{def:app-bulk-defect-convolution-habitat} by restricting
  the source to
  \(C^\bullet_{\mathrm{CE},\mathrm{cont}}
  (\mathfrak g^{w,\mathrm{reg}}_{\hbar,I})\).
  Assume that, on every finite Hamiltonian window \(M\) of the local
  formal holomorphic Hamiltonian sector, the target
  \(\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\) is equipped with the
  regulator-admissible finite-scale Costello brane-defect graph calculus
  for
  \(\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\):
  the weighted propagator \(P_{\epsilon,L}^{w,M}\), regularized BV
  Laplacian, local interaction \(I_{0,M}^{w}\), interval extension by
  zero, truncation maps \(\pi_{M,N}\), and admissible weight transports
  \(R^M_{w,w'}\), satisfying the acceptance gate of
  Statement~\ref{stmt:weighted-rg-acceptance-gate} and the graphwise
  Hadamard/Mittag--Leffler control of
  Theorem~\ref{thm:hadamard-mittag-leffler}.

  Then the restriction of
  \(\kappa^{\mathrm{coef}}_{\hbar,w,I}\) to regular density labels has a
  graphwise Costello-local lift
  \[
    \kappa^{\mathrm{graph,reg}}_{\hbar,w,I}
      \in
      \mathbf K^{0,\mathrm{reg}}_{w,\partial,\hbar}(I)
  \]
  in the following precise sense.
  For every fixed connected Costello graph \(\Gamma\), finite CE input,
  finite window \(M\), and external cotangent labels
  \(B_j=b_j(t)dt\in\mathcal D^{\mathrm{reg}}_c(I)\), the finite-scale graph
  contribution
  \[
    W^{\mathrm{reg},M}_{\Gamma,\epsilon,L}
      (a_\bullet,b_\bullet;f_\bullet,\rho_\bullet)
      \in
      \mathcal O_{\mathrm{loc}}^{\mathrm{bd}}\bigl(
        \mathcal E_w^M|_I;\,
        A_{\partial,\hbar}^{\mathrm{pp},w,M}(I)\bigr)
  \]
  is a well-defined smooth local-functional kernel for
  \(0<\epsilon\leq L<\infty\).  Its small-\(\epsilon\) expansion admits
  Costello local counterterms
  \(C_{\Gamma,w}^{\mathrm{reg},M}(\epsilon;b_\bullet)\), and the
  renormalized graph
  \[
    W^{R,\mathrm{reg},M}_{\Gamma,L,w}
      =
      \lim_{\epsilon\to0}
      \bigl(
        W^{\mathrm{reg},M}_{\Gamma,\epsilon,L}
        -
        C_{\Gamma,w}^{\mathrm{reg},M}(\epsilon;b_\bullet)
      \bigr)
  \]
  is again a brane-defect local functional with regular density
  coefficient labels.  These graph kernels are compatible with interval
  extension by zero, finite-window truncation, and admissible weight
  transport:
  \[
    \pi_{M,N}W^{R,\mathrm{reg},M}_{\Gamma,L,w}
      =
      W^{R,\mathrm{reg},N}_{\Gamma,L,w}\pi^{\mathrm{CE}}_{M,N},
    \qquad
    R^M_{w,w'}W^{R,\mathrm{reg},M}_{\Gamma,L,w}
      =
      W^{R,\mathrm{reg},M}_{\Gamma,L,w'}R^{M,\mathrm{CE}}_{w,w'} .
  \]
  On the zero-internal-edge part, and after scalar reduction and
  de Rham-current contraction, the lifted kernel is
  \(\Phi_I^{\mathrm{cur}}\).

  Consequently, wherever a filtered scalar projection
  \(\widehat\sigma_{\mathrm{sc}}\) has been constructed on the chosen
  regular-density graph/counterterm subhabitat, the curvature
  \[
    \operatorname{Curv}_{\mathbf K}
      (\kappa^{\mathrm{graph,reg}}_{\hbar,w,I})
  \]
  defines the same finite-window non-scalar obstruction system as in
  Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.  Thus the
  regular-density theorem removes the analytic wavefront/counterterm gap
  attached to the cotangent labels, but it does not prove the filtered
  scalar projection outside its stated habitat and does not prove
  vanishing of
  \[
    [\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]
      \in
      H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}}).
  \]

  No extension from \(\mathcal D^{\mathrm{reg}}_c(I)\) to
  \(\mathcal D'_c(I)\) is asserted.  The exact remaining analytic theorem
  is: for every finite window \(M\), every Costello graph \(\Gamma\), and
  every compactly supported distributional label
  \(B_j\in\mathcal D'_c(I)\), the product of the finite-scale
  brane-defect propagator kernels with the pushed-forward current labels
  must satisfy H\"ormander wavefront transversality, admit local
  extensions across all graph small diagonals, and admit counterterms
  compatible with interval extension, \(\pi_{M,N}\), and \(R^M_{w,w'}\).
  This is a local brane-defect microlocal condition, not a compactness
  condition on the holomorphic target.
\end{prop}

\begin{proof}
  The regular subspace is stable under the current operations used in the
  source.  Indeed, if \(B=b(t)dt\) and \(a\in C^\infty_c(I)\), then
  Lemma~\ref{lem:app-factorization-current-product} gives
  \(aB=(ab)(t)dt\), again a compactly supported smooth density.  Extension
  by zero along \(I\hookrightarrow J\) is smooth because the support is
  compactly contained in \(I\).  Thus the regular labels define the stated
  source subcomplex and the restriction of the convolution habitat.

  Fix a finite window \(M\), a graph \(\Gamma\), and
  \(0<\epsilon\leq L<\infty\).  In this window the coefficient part of
  the propagator is finite rank, and the spacetime part of
  \(P_{\epsilon,L}^{w,M}\) is the finite-scale heat-kernel propagator of
  Costello's elliptic BV calculus.  It is smooth at positive scale.  After
  restriction to the brane line, multiplication by the smooth compactly
  supported functions \(a_i\) and densities \(b_j(t)dt\) produces a smooth
  compactly supported graph integrand on the relevant configuration space
  and edge-parameter domain.  Hence no product of singular distributions is
  formed at finite scale, and the graph integral is a well-defined element
  of the displayed brane-defect local-functional target.

  As \(\epsilon\to0\), the only singularities are the usual heat-kernel
  singularities along graph diagonals.  Multiplication by smooth compact
  densities does not enlarge wavefront sets and does not change the
  Hadamard singular order.  Therefore the local asymptotic expansion and
  local counterterm construction are exactly the windowwise Costello
  construction, tensored with the finite coefficient kernel and multiplied
  by smooth density coefficients.  Theorem~\ref{thm:hadamard-mittag-leffler}
  supplies the graphwise Hadamard estimates and strict Mittag--Leffler
  passage in the weighted coefficient direction.  The counterterms remain
  local on the brane line; their coefficients are differential expressions
  in smooth compactly supported labels, hence regular density labels.

  The compatibility identities are degreewise.  The maps \(\pi_{M,N}\)
  discard coefficient degrees above \(N\), while \(R^M_{w,w'}\) rescales
  the surviving weighted Hamiltonian and cotangent bases.  The regular
  density factors live in the interval variable and are untouched by these
  coefficient maps.  The strict Mittag--Leffler compatibility of the
  finite-window propagators and counterterms in
  Statement~\ref{stmt:weighted-rg-acceptance-gate} therefore gives the two
  displayed identities.  Interval extension compatibility is the same
  locality statement: all labels and counterterms are extended by zero, and
  local graph weights are supported on the same brane diagonals after
  extension.

  The zero-internal-edge graph is the generator assignment of
  Proposition~\ref{prop:app-bulk-defect-kernel-layer}.  After forgetting
  the Moyal deformation, applying scalar reduction, and contracting the
  de Rham-current direction, it is
  Theorem~\ref{thm:app-factorization-universal-current-interface}.

  The curvature assertion is formal in the filtered convolution dg Lie
  algebra.  The Bianchi identity used in the proof of
  Proposition~\ref{prop:app-bulk-defect-kernel-layer} applies to the
  regular restricted habitat.  Once a filtered scalar projection is
  available, the first unsolved curvature coefficient lands in
  \(\ker\widehat\sigma_{\mathrm{sc}}\), and compatible counterterms change
  it by \(d_{\mathrm{QME}}\)-boundaries.  The finite-window obstruction is
  exactly the inverse-limit \(H^1\) class and the
  \(\varprojlim^1H^0\) primitive-compatibility class of
  Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.

  If \(B\) is an arbitrary compactly supported distribution, the preceding
  smooth-multiplier argument fails at the point where the pushed-forward
  brane current is multiplied with propagator boundary values and then
  extended across graph diagonals.  The needed H\"ormander
  transversality, extension, and compatible counterterm theorem is
  therefore exactly the residual theorem stated above.
\end{proof}

\begin{defn}[Wavefront-admissible defect-current labels]
\label{def:app-wavefront-admissible-defect-labels}
  Fix a finite Hamiltonian window \(M\), a connected Costello graph
  \(\Gamma\), and a finite list of external cotangent-current labels
  \(B_\bullet=(B_1,\ldots,B_r)\), \(B_j\in\mathcal D'_c(I)\).  Let
  \(X=\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\) and
  \(L_I=I\times\{0\}\times\{p\}\subset X\).  If
  \(V_{\mathrm{bulk}}(\Gamma)\) and \(V_{\partial}(\Gamma)\) are the bulk
  and defect vertices, set
  \[
    X^0_\Gamma(I)=
    X^{V_{\mathrm{bulk}}(\Gamma)}
    \times L_I^{V_{\partial}(\Gamma)}
    \times E_{\Gamma,M},
  \]
  where \(E_{\Gamma,M}\) is the finite-dimensional coefficient and edge
  parameter space in the window \(M\).  The final graph space
  \(X_\Gamma(I)\) is the open complement of the graph collision
  diagonals in \(X^0_\Gamma(I)\) before local extension across those
  diagonals.  Choose an attachment map
  \(\ell:\{1,\ldots,r\}\to V_{\partial}(\Gamma)\) for the current labels
  and define the incidence map
  \[
    e_\Gamma:X^0_\Gamma(I)\longrightarrow I^r,\qquad
    e_{\Gamma,j}(x)=t_{\ell(j)} .
  \]
  Repeated labels at one defect vertex are therefore diagonal pullbacks
  by \(e_\Gamma\).  For
  \(B^\boxtimes=B_1\boxtimes\cdots\boxtimes B_r\), write
  \(B_\Gamma=e_\Gamma^*B^\boxtimes\) only when this pullback is defined.
  Let
  \(\operatorname{Diag}(\Gamma)\) be the finite set of graph collision
  diagonals on which the small-\(\epsilon\) Hadamard coefficients may be
  singular.

  The tuple \(B_\bullet\) is called
  \((\Gamma,M)\)-wavefront-admissible if the following four operations are
  defined by the usual H\"ormander calculus
  \cite{hormander-vol1}*{Ch.~8} and by the Costello finite-window graph
  package \cite{costello-renormalization}*{Chs.~5--7}.
  \begin{enumerate}
    \item The incidence pullback is non-characteristic:
    \[
      N_{e_\Gamma}\cap\mathrm{WF}(B^\boxtimes)=\emptyset,\qquad
      N_{e_\Gamma}=
      \{(e_\Gamma(x),\xi)\mid de_{\Gamma,x}^{\,t}\xi=0\}.
    \]
    Then
    \[
      \mathrm{WF}(B_\Gamma)\subset
      e_\Gamma^\#\mathrm{WF}(B^\boxtimes)
      =
      \{(x,de_{\Gamma,x}^{\,t}\xi)\mid
      (e_\Gamma(x),\xi)\in\mathrm{WF}(B^\boxtimes)\}.
    \]
    The resulting support is proper over the graph integration variables.
    \item For every Hadamard coefficient
    \(K^M_{\Gamma,\alpha}\) appearing in the small-\(\epsilon\) expansion
    of the finite-window graph kernel,
    \[
      \bigl(
      \mathrm{WF}(K^M_{\Gamma,\alpha})
      +\mathrm{WF}(B_\Gamma)
      \bigr)
      \cap T^*_{X_\Gamma(I)}X_\Gamma(I)=\emptyset .
    \]
    Equivalently, no covector in
    \(\mathrm{WF}(B_\Gamma)\) is the negative of a graph-kernel covector.
    Thus the product \(K^M_{\Gamma,\alpha}B_\Gamma\) is a canonical
    distribution.
    \item For each collision diagonal
    \(\Delta\in\operatorname{Diag}(\Gamma)\), the products
    \(K^M_{\Gamma,\alpha}B_\Gamma\) have finite scaling degree along
    \(\Delta\).  Their allowed extensions across \(\Delta\) differ by
    distributions supported on
    \(\Delta\cap\operatorname{supp}(B_\Gamma)\), hence by brane-defect
    local counterterms with distributional current coefficients.
    \item The final graph pushforward has wavefront contained in the
    brane-defect local-functional wavefront class already used in
    Theorem~\ref{thm:hadamard-mittag-leffler}, after tensoring with the
    finite coefficient kernel.
  \end{enumerate}
  Denote the resulting multilinear relation by
  \[
    \mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)
      \subset \bigl(\mathcal D'_c(I)\bigr)^r .
  \]
  The universal wavefront-admissible relation is the intersection of
  these relations over the finite windows, graphs, and finite CE inputs
  under consideration.  This is a relation on finite tuples.  A linear
  subspace \(\mathcal V\subset\mathcal D'_c(I)\) gives an honest
  restricted CE source only when every finite tuple from \(\mathcal V\)
  lies in the corresponding relation.

  A useful source of such subspaces is a diagonal-admissible conic set
  \(\Lambda\subset T^*I\setminus0\): for every \(n\geq1\),
  \[
    \xi_1,\ldots,\xi_n\in\Lambda
    \quad\Longrightarrow\quad
    \xi_1+\cdots+\xi_n\neq0 .
  \]
  Then
  \[
    \mathcal D'_{c,\Lambda,\mathrm{fs}}(I)
      =
      \{\,B\in\mathcal D'_c(I)\mid
      \mathrm{WF}(B)\subset\Lambda,\ B
      \text{ has finite scaling degree along its singular support}\,\}
  \]
  is the finite-scaling one-sided wavefront class.  On an oriented
  interval, either open half-cone
  \(\Lambda_+=\{(t,\xi)\mid \xi>0\}\) or
  \(\Lambda_-=\{(t,\xi)\mid \xi<0\}\) is diagonal-admissible.
  These two half-cones are maximal among sign-conic diagonal-admissible
  linear habitats for ordinary collision-conormal kernels: any conic
  subset of \(T^*I\setminus0\) containing both signs admits, after
  positive rescaling, a finite nonempty covector sum equal to zero, so it
  can cancel a collision conormal.
  Compactly supported one-sided conormal boundary values, for example
  cutoffs of \((t-t_0-i0)^{-m}\) after choosing the Fourier sign
  convention, lie in one of these classes and are not regular densities.
\end{defn}

\begin{prop}[Wavefront-admissible distributional graph kernel layer]
\label{prop:app-wavefront-admissible-costello-graph-kernel}
  Assume the same regulator-admissible finite-window Costello
  brane-defect graph calculus as in
  Proposition~\ref{prop:app-regular-density-costello-graph-kernel}.  Let
  \(\Gamma\) be a fixed connected graph, \(M\) a finite Hamiltonian window,
  and \(B_\bullet\in
  \mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)\).  Then the graph contribution
  with external cotangent labels \(B_\bullet\) has the following
  distributional extension.
  \begin{enumerate}
    \item For every \(0<\epsilon\leq L<\infty\), the finite-scale graph
    weight
    \[
      W^{\mathrm{WF},M}_{\Gamma,\epsilon,L}
        (a_\bullet,B_\bullet;f_\bullet,\rho_\bullet)
    \]
    is a well-defined brane-defect local-functional kernel with compactly
    supported distributional current coefficients.  At this positive
    scale the propagator is smooth, so the only distributional operation
    is multiplication of smooth kernels by the pushed-forward currents.
    \item The small-\(\epsilon\) expansion admits local counterterms
    \[
      C_{\Gamma,w}^{\mathrm{WF},M}(\epsilon;B_\bullet)
    \]
    supported on
    \[
      \bigcup_{\Delta\in\operatorname{Diag}(\Gamma)}
      \Delta\cap\operatorname{supp}(B_\Gamma).
    \]
    The renormalized graph
    \[
      W^{R,\mathrm{WF},M}_{\Gamma,L,w}
        =
        \lim_{\epsilon\to0}
        \bigl(
          W^{\mathrm{WF},M}_{\Gamma,\epsilon,L}
          -
          C_{\Gamma,w}^{\mathrm{WF},M}(\epsilon;B_\bullet)
        \bigr)
    \]
    is a brane-defect local functional with coefficients in the
    distributional current target
    \(A_{\partial,\hbar}^{\mathrm{pp},w,M}(I)\).
    \item The construction is compatible with interval extension by zero,
    finite-window truncation, and admissible weight transport whenever
    the chosen tuple remains wavefront-admissible after applying the
    corresponding incidence maps:
    \[
      \pi_{M,N}W^{R,\mathrm{WF},M}_{\Gamma,L,w}
        =
      W^{R,\mathrm{WF},N}_{\Gamma,L,w}\pi^{\mathrm{CE}}_{M,N},
      \qquad
      R^M_{w,w'}W^{R,\mathrm{WF},M}_{\Gamma,L,w}
        =
      W^{R,\mathrm{WF},M}_{\Gamma,L,w'}R^{M,\mathrm{CE}}_{w,w'} .
    \]
  \end{enumerate}
  In particular, every finite tuple of labels in
  \(\mathcal D'_{c,\Lambda,\mathrm{fs}}(I)\) for a diagonal-admissible
  cone \(\Lambda\) is wavefront-admissible for graph kernels whose
  singular wavefronts are conormal to ordinary graph collision
  diagonals.  This gives a non-regular distributional extension of
  Proposition~\ref{prop:app-regular-density-costello-graph-kernel}.

  This is the exact extension asserted here from the present Costello
  graph products: outside the relation
  \(\mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)\), at least one of the
  multiplication, extension, or graph-pushforward operations above is not
  defined by the cited wavefront calculus.  No theorem for all of
  \(\mathcal D'_c(I)\) follows.  The obstruction and the admitted
  extension are entirely local on the brane interval and on the
  finite-window formal disk coefficient sector.
\end{prop}

\begin{proof}
  At positive scale the heat-kernel propagator
  \(P_{\epsilon,L}^{w,M}\) is smooth in the spacetime and defect
  variables.  Multiplication of a compactly supported distribution by a
  smooth function is always defined, and the incidence maps are proper on
  the supports by Definition~\ref{def:app-wavefront-admissible-defect-labels}.
  This proves the finite-scale graph weight.

  As \(\epsilon\to0\), Theorem~\ref{thm:hadamard-mittag-leffler} gives
  graphwise Hadamard coefficients with wavefront contained in the union of
  conormals to graph collision diagonals.  The second condition in
  Definition~\ref{def:app-wavefront-admissible-defect-labels} is exactly
  H\"ormander's product criterion
  \cite{hormander-vol1}*{Ch.~8}, so
  \(K^M_{\Gamma,\alpha}B_\Gamma\) is a canonical distribution for every
  coefficient.  The finite-scaling condition then gives the standard
  local extension across each collision diagonal.  Its ambiguity is
  supported on the collision locus meeting the support of \(B_\Gamma\);
  this is precisely a brane-defect local counterterm with distributional
  current coefficient.  Subtracting these local counterterms gives the
  displayed renormalized graph.

  The two compatibility identities are inherited degreewise from the
  finite-window Costello graph calculus.  The maps \(\pi_{M,N}\) and
  \(R^M_{w,w'}\) act on the weighted Hamiltonian coefficient factors and
  do not change the interval wavefront cone.  Interval extension by zero
  is allowed exactly when the extended incidence tuple satisfies the same
  non-characteristic and proper-support conditions.  Hence compatibility
  holds on the stated wavefront-admissible relation.

  For the one-sided conic classes, let
  \(\Lambda\) be diagonal-admissible and let
  \(B_j\in\mathcal D'_{c,\Lambda,\mathrm{fs}}(I)\).  A conormal covector
  to an \(n\)-fold collision diagonal has components
  \((\eta_1,\ldots,\eta_n)\) whose sum is zero on each collision block.
  If this covector were cancelled by covectors from the external labels,
  then a finite nonempty sum of elements of \(\Lambda\) would be zero,
  contradicting diagonal-admissibility.  Thus the product criterion holds.
  The finite-scaling hypothesis gives the extension condition, and the
  remaining pushforward condition is the same proper-support condition as
  above.

  Finally, the full compactly supported distribution space is too large.
  In the one-edge boundary graph take two external labels
  \(B_1=B_2=\delta_{t_0}\).  The singular boundary propagator has
  wavefront containing the conormal directions
  \((t_0,t_0;\tau,-\tau)\) to the diagonal \(t=s\), while
  \(\mathrm{WF}(\delta_{t_0}\boxtimes\delta_{t_0})\) contains the
  opposite directions \((t_0,t_0;-\tau,\tau)\).  H\"ormander's product
  criterion therefore fails.  Equivalently, the graph asks for the value
  of the singular propagator on the diagonal against
  \(\delta_{t_0}\boxtimes\delta_{t_0}\), which is not a canonical
  distributional operation without an additional renormalization rule.
  Thus arbitrary \(\mathcal D'_c(I)\)-labels are not supported by the
  current Costello graph products.
\end{proof}

\begin{prop}[Current-compatible \(D'_c\) theorem surface]
\label{prop:app-current-compatible-Dprimec-theorem-surface}
  Assume the regulator-admissible finite-window Costello brane-defect
  graph package of
  Proposition~\ref{prop:app-regular-density-costello-graph-kernel}.  The
  theorem surface compatible with compactly supported distributional
  cotangent labels is the following.
  \begin{enumerate}
    \item For arbitrary \(B\in\mathcal D'_c(I)\), the constructed object
    is the coefficient-current kernel
    \[
      \kappa^{\mathrm{coef}}_{\hbar,w,I}
        (u_{a(t)dt\otimes f})=\iota_I(B^w_f(a)),
      \qquad
      \kappa^{\mathrm{coef}}_{\hbar,w,I}(c_{B,\rho})
        =\iota_I(\Theta^w_\rho(B)).
    \]
    This is an algebraic current kernel.  It is not a Costello
    graph-kernel theorem for all \(B\in\mathcal D'_c(I)\).
    \item For a fixed graph \(\Gamma\), finite window \(M\), and
    admissible tuple
    \(B_\bullet\in\mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)\), put
    \[
      T^M_{\Gamma,\alpha}(B_\bullet)
        =K^M_{\Gamma,\alpha}B_\Gamma .
    \]
    Its wavefront is bounded by the H\"ormander product formula
    \[
    \begin{aligned}
      \mathrm{WF}\!\left(T^M_{\Gamma,\alpha}(B_\bullet)\right)
      \subset&
      \mathrm{WF}(K^M_{\Gamma,\alpha})
      \cup \mathrm{WF}(B_\Gamma)  \\
      &\cup
      \bigl(\mathrm{WF}(K^M_{\Gamma,\alpha})
        +\mathrm{WF}(B_\Gamma)\bigr),
    \end{aligned}
    \]
    with the fibrewise sum taken over the same base point in
    \(X_\Gamma(I)\).  For the final graph projection
    \(p_\Gamma:X_\Gamma(I)\to Y_\Gamma(I)\), proper on support, the
    pushed-forward graph has
    \[
      \mathrm{WF}\bigl(p_{\Gamma,*}T^M_{\Gamma,\alpha}\bigr)
      \subset
      \{(y,\eta)\mid
      \exists x\in p_\Gamma^{-1}(y),\
      (x,dp_{\Gamma,x}^{\,t}\eta)\in
      \mathrm{WF}(T^M_{\Gamma,\alpha})\}.
    \]
    These are the only wavefront bounds used by the distributional
    graph layer.
    \item Let \(\Delta\in\operatorname{Diag}(\Gamma)\), let
    \(c_\Delta=\operatorname{codim}\Delta\), and suppose
    \[
      s_{\Gamma,\alpha,\Delta}
        =\operatorname{sd}_\Delta
        \left(T^M_{\Gamma,\alpha}(B_\bullet)\right)<\infty .
    \]
    Set
    \[
      N_{\Gamma,\alpha,\Delta}
        =
      \max\{-1,\,
      \lfloor s_{\Gamma,\alpha,\Delta}-c_\Delta\rfloor\}.
    \]
    If \(\widetilde T\) and \(\widetilde T'\) are two local extensions
    of \(T^M_{\Gamma,\alpha}(B_\bullet)\) across \(\Delta\), then locally
    in normal coordinates to \(\Delta\)
    \[
      \widetilde T'-\widetilde T
        =
      \sum_{|\beta|\leq N_{\Gamma,\alpha,\Delta}}
      \partial_\nu^\beta\delta_\Delta\otimes
      S_{\Delta,\beta},
    \]
    with no summand when \(N_{\Gamma,\alpha,\Delta}=-1\).  Here
    \(S_{\Delta,\beta}\in\mathcal D'(\Delta)\) is supported in
    \(\Delta\cap\operatorname{supp}(B_\Gamma)\) and carries the same
    finite-window Hamiltonian coefficient label.  Thus the allowed
    counterterm ambiguity belongs to
    \[
      \sum_{\Delta,\alpha}
      \sum_{|\beta|\leq N_{\Gamma,\alpha,\Delta}}
      \partial_\nu^\beta\delta_\Delta\,
      \mathcal D'_{\Delta\cap\operatorname{supp}(B_\Gamma)}(\Delta)
      \widehat\otimes
      A_{\partial,\hbar}^{\mathrm{pp},w,M}(I).
    \]
    \item The finite-window counterterms are compatible precisely when
    the chosen extensions satisfy
    \[
      j_*C_{\Gamma,I}^{\mathrm{WF},M}(\epsilon;B_\bullet)
        =
      C_{\Gamma,J}^{\mathrm{WF},M}(\epsilon;j_*B_\bullet),
    \]
    for interval inclusions \(j:I\hookrightarrow J\) for which the
    extended tuple remains admissible, and
    \[
      \pi_{M,N}C_{\Gamma,w}^{\mathrm{WF},M}(\epsilon;B_\bullet)
        =
      C_{\Gamma,w}^{\mathrm{WF},N}(\epsilon;B_\bullet)
        \pi^{\mathrm{CE}}_{M,N},
    \]
    \[
      R^M_{w,w'}C_{\Gamma,w}^{\mathrm{WF},M}(\epsilon;B_\bullet)
        =
      C_{\Gamma,w'}^{\mathrm{WF},M}(\epsilon;B_\bullet)
        R^{M,\mathrm{CE}}_{w,w'} .
    \]
    Failure of the interval identity is a factorization-compatibility
    residual.  Failure of the last two identities is exactly the
    finite-window primitive compatibility obstruction measured by
    Theorem~\ref{thm:wt-nonscalar-counterterm-criterion} after passing to
    the relevant graph/counterterm habitat.
    \item There is no present theorem for all of
    \(\mathcal D'_c(I)\).  In particular, the coincident-current
    boundary graph with
    \(B_1=B_2=\delta_{t_0}\) violates the product condition because
    conormal covectors \((\tau,-\tau)\) to \(t=s\) can be cancelled by
    \(\mathrm{WF}(\delta_{t_0}\boxtimes\delta_{t_0})\).  Thus the
    arbitrary-\(D'_c\) graph theorem would require extra renormalization
    data not supplied by Costello's general finite-scale package or by
    the Costello--Gwilliam factorization vocabulary.
  \end{enumerate}
  Hence the manuscript has a theorem-grade graph layer on
  \(\mathcal D^{\mathrm{reg}}_c(I)\), on finite graphwise
  wavefront-admissible tuples, and on the sign-conic finite-scaling
  habitats \(\mathcal D'_{c,\Lambda_\pm,\mathrm{fs}}(I)\) for ordinary
  collision-conormal graph kernels.  The full distributional space
  \(\mathcal D'_c(I)\) remains a named obstruction problem.
\end{prop}

\begin{proof}
  Item (1) is
  Proposition~\ref{prop:app-bulk-defect-kernel-layer}: the assignment is
  degreewise algebraic in the compactly supported current \(B\) and uses
  only multiplication of a current by a smooth test function.  No
  singular graph product is formed there.

  Items (2) and (3) are the standard H\"ormander product, pushforward,
  and finite-scaling extension calculus applied to
  Definition~\ref{def:app-wavefront-admissible-defect-labels}.  The
  product transversality condition makes
  \(K^M_{\Gamma,\alpha}B_\Gamma\) canonical.  Properness of the graph
  projection gives the displayed pushforward wavefront bound.  Finite
  scaling degree along \(\Delta\) gives extensions across \(\Delta\);
  the structure theorem for distributions supported on a submanifold
  gives the finite normal-derivative formula for the difference of two
  extensions.  The support statement follows because all extensions
  agree off
  \(\Delta\cap\operatorname{supp}(B_\Gamma)\).

  Item (4) is the compatibility condition needed for the counterterms to
  define one interval-local element of the completed finite-window and
  weight-transport tower rather than unrelated graphwise choices.  When
  the identities hold, the Bianchi argument of
  Proposition~\ref{prop:app-bulk-defect-kernel-layer} produces the
  Hom-valued obstruction class and the Milnor
  \(\varprojlim^1H^0\) primitive obstruction.  Failure of interval
  extension compatibility is a failure of the factorization current
  structure itself; failure of finite-window or weight compatibility is
  precisely a primitive-compatibility obstruction.

  Item (5) is the counterexample in the proof of
  Proposition~\ref{prop:app-wavefront-admissible-costello-graph-kernel}.
  It also matches the source audit: the local Costello sources support
  finite-scale BV/RG/QME graph calculus, local functionals, and local
  counterterms under their hypotheses, but they do not prove a
  current-valued arbitrary-\(\mathcal D'_c\) brane-defect theorem.
\end{proof}

\begin{prop}[Obstruction maps for the non-scalar current lift]
\label{prop:app-nonscalar-current-lift-obstructions}
  The datum of
  Definition~\ref{def:app-unreduced-nonscalar-current-lift-datum} can
  realize the non-scalar Costello graph/QME theorem for the local mixed HT
  brane-defect model only if the following obstruction maps vanish, with
  the stated homotopies.
  \begin{enumerate}
    \item The scalar projection of the curvature must vanish in the
    chosen scalar branch:
    \[
      \widehat\sigma_{\mathrm{sc}}\!\left(
      \operatorname{Curv}_{\mathbf K}(\kappa_{\hbar,w,I})
      \right)=0.
    \]
    In the ordinary scalar-reduced \(\lie{gl}_N\) branch this condition is
    exactly the requirement that the Capelli contact class
    \(\hbar N[\bar c]\) be cancelled by a closed-exchange term and a local
    counterterm.  In the balanced supertrace branch it is the condition
    \(\widehat\sigma_{\mathrm{sc}}
    (\operatorname{Ob}_{w,\partial,\hbar})=0\).
    \item After scalar reduction and de Rham-current contraction, the
    kernel must recover the reduced current interface:
    \[
      \overline{\kappa}_{\hbar,w,I}
      (u_{a(t)dt\otimes f})=B_f(a),\qquad
      \overline{\kappa}_{\hbar,w,I}(c_{B,\rho})=\Theta_\rho(B),
    \]
    with brackets
    \[
      \{B_f(a),B_g(b)\}_\hbar=B_{\{f,g\}_\hbar}(ab),\qquad
      \{B_f(a),\Theta_\rho(B)\}_\hbar
        =\Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}(aB),
    \]
    and \(\{\Theta_\rho(B),\Theta_\sigma(C)\}_\hbar=0\).
    At \(\hbar=0\) this is
    Theorem~\ref{thm:app-factorization-universal-current-interface}.
    \item The unreduced bracket defects
    \[
      D_{f,g}(a,b)=
      \{B_f^{\mathrm{BV}}(a),B_g^{\mathrm{BV}}(b)\}_\hbar
        -B_{\{f,g\}_\hbar}^{\mathrm{BV}}(ab),
    \]
    \[
      D_{f,\rho}(a,B)=
      \{B_f^{\mathrm{BV}}(a),\Theta_\rho^{\mathrm{BV}}(B)\}_\hbar
        -\Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}^{\mathrm{BV}}(aB),
    \]
    and
    \[
      D_{\rho,\sigma}(B,C)=
      \{\Theta_\rho^{\mathrm{BV}}(B),
        \Theta_\sigma^{\mathrm{BV}}(C)\}_\hbar
    \]
    must be \(d_{\mathrm{QME}}\)-exact by homotopies compatible with
    inclusions of intervals, disjoint factorization products, and the
    finite-window regulator maps.
    \item After evaluation on each fixed finite CE input \(\xi\), equivalently
    on each fixed graph/source-arity component, the residual non-scalar
    curvature class
    \[
      \left[
      \operatorname{Curv}_{\mathbf K}(\kappa_{\hbar,w,I})(\xi)
      \right]
      \in
      H^1\!\left(
        \ker\widehat\sigma_{\mathrm{sc}},
        d_{\mathrm{QME}}
      \right)
    \]
    must vanish after the compatible finite-window counterterms
    \(C_{\Gamma,w}^{w_0}(\epsilon)\) have been inserted.
  \end{enumerate}
  These conditions are necessary.  They are also sufficient for the
  stated local graph/QME realization once the Costello finite-scale BV
  propagator, BV Laplacian, locality estimates, and counterterm system in
  the chosen coefficient category have been constructed.  They do not
  assert a compact Calabi--Yau, CoHA, global BCOV, or cross-volume
  comparison theorem.
\end{prop}

\begin{proof}
  The source and target in
  Definition~\ref{def:app-unreduced-nonscalar-current-lift-datum} are the
  current versions of the weighted cotangent Hamiltonian source and the
  mixed brane-defect obstruction complex of
  Problem~\ref{prob:quantum-p0-operation-realization}.  A Costello graph
  realization is a solution of the QME in this local-functional complex,
  hence its curvature has zero scalar projection and zero residual class
  in \(\ker\widehat\sigma_{\mathrm{sc}}\).  This gives the first and
  fourth obstruction maps.

  The second condition is forced by compatibility with the already proved
  reduced current theorem.  After contraction and scalar reduction the
  only allowed target brackets are the Moyal principal-part current
  brackets of Theorem~\ref{thm:quantum-coefficient-surface}; at
  \(\hbar=0\) these reduce to the three brackets of
  Theorem~\ref{thm:app-factorization-universal-current-interface}.  Any
  different reduction would change the theorem already proved.

  The three defects in the third condition are the generator-level
  failures of the source semidirect Lie brackets to match the target
  \(P_0\)-brackets.  Since the CE differential and the target bracket are
  derivations, exactness of these generator defects, with homotopies
  compatible with factorization products and finite-window transition
  maps, is precisely the condition that the generator assignment extend
  to the desired homotopy \(P_0\)-central operation.  The reduced algebraic
  target has zero defects by
  Theorem~\ref{thm:app-factorization-universal-current-interface}; the
  unreduced polynomial BV target does not, by
  Theorem~\ref{thm:app-unreduced-polynomial-centrality-no-go}.  Therefore
  the missing theorem must construct these homotopies in a larger
  current-compatible Costello local-functional category.
\end{proof}

\begin{thm}[Curved kernel centrality homotopy criterion]
\label{thm:app-curved-kernel-centrality-homotopy-criterion}
  Fix the local mixed HT brane-defect model on
  \(\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\), a
  weighted current source
  \(\mathfrak g^{w,\mathrm{cur}}_{\hbar,I}\), and a Costello
  local-functional target
  \(\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\) as in
  Definition~\ref{def:app-unreduced-nonscalar-current-lift-datum}.  Let
  \(\kappa_M\) be a finite-window component of a degree-zero continuous
  kernel in the convolution habitat
  \(\mathbf K^\bullet_{w,\partial,\hbar}(I)\), and assume that the chosen
  scalar-contact projection is a chain map on the habitat under
  discussion.

  For source generators
  \[
    x\in\{u_{a(t)dt\otimes f},\,c_{B,\rho}\},\qquad
    y\in\{u_{b(t)dt\otimes g},\,c_{C,\sigma}\},
  \]
  define the binary closed-open curvature component by
  \[
    \mathfrak D^M_\kappa(x,y)
      =
    \operatorname{Curv}_{\mathbf K,M}(\kappa_M)(x\wedge y).
  \]
  When no binary Taylor component has already been inserted, these are the
  three generator defects
  \[
    D^M_{f,g}(a,b),\qquad
    D^M_{f,\rho}(a,B),\qquad
    D^M_{\rho,\sigma}(B,C)
  \]
  displayed in
  Proposition~\ref{prop:app-nonscalar-current-lift-obstructions}.

  A compatible unreduced binary centrality homotopy for this kernel is
  exactly a family of cochains
  \[
    H^M_{x,y}\in
    \mathcal K^{|x|+|y|-1}_{\mathrm{ns},M}(I)
      =
    \ker\widehat\sigma_{\mathrm{sc},M}
      \cap
    \mathfrak Q^{|x|+|y|-1}_{w,M,\partial,\hbar}(I)
  \]
  satisfying
  \begin{equation}
    \mathfrak D^M_\kappa(x,y)+d_M H^M_{x,y}=0
    \label{eq:app-centrality-homotopy-equation}
  \end{equation}
  for every such pair, together with the compatibility identities
  \[
    j_*H^M_{I;x,y}
      =
    H^M_{J;j_*x,j_*y},
  \]
  for interval inclusions \(j:I\hookrightarrow J\) for which the labels
  remain admissible, and
  \[
    \pi_{M,N}H^M_{x,y}=H^N_{\pi x,\pi y},
    \qquad
    R^M_{w,w'}H^M_{w;x,y}=H^M_{w';Rx,Ry}.
  \]
  Equivalently, for every pair \((x,y)\), the inverse-system cohomology
  class
  \[
    \bigl([\mathfrak D^M_\kappa(x,y)]\bigr)_M
    \in
    \varprojlim_M
    H^{|x|+|y|}\!
    \left(\mathcal K^\bullet_{\mathrm{ns},M}(I),d_M\right)
  \]
  and the Milnor primitive-compatibility class represented by
  \[
    \left[
      \pi_{M,N}h^M_{x,y}-h^N_{\pi x,\pi y}
    \right]
    \in
    H^{|x|+|y|-1}
    \left(\mathcal K^\bullet_{\mathrm{ns},N}(I),d_N\right)
  \]
  must both vanish, where \(h^M_{x,y}\) is any windowwise primitive
  solving
  \(\mathfrak D^M_\kappa(x,y)+d_M h^M_{x,y}=0\).

  For the algebraic coefficient-current kernel
  \(\kappa^{\mathrm{coef}}_{\hbar,w,I}\) of
  Proposition~\ref{prop:app-bulk-defect-kernel-layer}, all
  \(\mathfrak D^M_\kappa(x,y)\) vanish in the freely adjoined current
  target, and one may take \(H^M_{x,y}=0\).  This is the strict
  homotopy of
  Theorem~\ref{thm:app-algebraic-factorization-centre-zero-homotopies}.
  For a genuine unreduced Costello local-functional target, the same
  conclusion is not supplied by the coefficient-current formula.  It
  requires the finite-window graph row representing
  \(\mathfrak D^M_\kappa(x,y)\), a scalar-zero gate for that row, and a
  local counterterm or binary Taylor cochain \(H^M_{x,y}\) satisfying
  equation~\eqref{eq:app-centrality-homotopy-equation} with the displayed
  interval, window, and weight compatibilities.
\end{thm}

\begin{proof}
  The arity-two part of the curved Maurer--Cartan equation in the
  convolution dg Lie algebra is precisely
  \[
    \operatorname{Curv}_{\mathbf K,M}(\kappa_M)(x\wedge y)=0.
  \]
  Expanding this identity before choosing a binary component gives the
  target bracket of the two generator images minus the image of the source
  semidirect bracket, with the source term supplied by
  \(-\kappa d_{\mathrm{CE}}\).  These are exactly the three defects
  \(D_{f,g}\), \(D_{f,\rho}\), and \(D_{\rho,\sigma}\) of
  Proposition~\ref{prop:app-nonscalar-current-lift-obstructions}.

  A binary homotopy is, by definition, a degree
  \(|x|+|y|-1\) primitive for this curvature component in the
  scalar-zero kernel complex.  This gives
  equation~\eqref{eq:app-centrality-homotopy-equation}.  Compatibility with
  extension by zero, finite-window truncation, and admissible weight
  transport is exactly the statement that these primitives assemble to a
  homotopy in the completed local factorization target rather than to
  unrelated windowwise choices.  The inverse-limit obstruction and the
  Milnor class are the usual Roos obstruction for choosing compatible
  primitives, in the same form as
  Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.

  In the algebraic coefficient-current target the three brackets are
  identities, hence the curvature components vanish and the zero
  primitive is compatible with every structural map.  In a Costello
  local-functional target the terms are graph weights, source faces,
  collision/contact terms, and counterterms.  Unless those rows and their
  primitive are supplied in the chosen finite-window package, the displayed
  equation is only an obstruction equation, not a constructed homotopy.
\end{proof}
