\section{Radial Parts and the Moyal Normalization}
\label{sec:app-radial-parts-moyal}

This appendix records the proof spine for
Theorem~\ref{thm:lane-moyal-degree-zero}.  The stable core is the
scalar-reduced Weyl/Moyal normalization, the Capelli change of basis,
the stable connected trace bracket, and the reduced open-line Wick
graph expansion with midpoint propagator
\(\frac12\operatorname{sgn}(t-s)\).  The finite-\(N\) radial-parts
comparison is isolated as the explicit input package stated below.
Once that package is assumed, the radial argument is algebraic:
Vandermonde conjugation removes the Dunkl--Calogero connection terms,
injectivity detects the reduced quotient, and the stable connected
cumulant projection extracts the single-trace Moyal bracket.

\begin{defn}[Formal Weyl/Moyal convention]
\label{def:app-radial-moyal-convention}
  Let
  \[
    P=\partial_{z_1}\otimes\partial_{z_2}
      -\partial_{z_2}\otimes\partial_{z_1}.
  \]
  The formal Weyl product on \(\C[[z_1,z_2]][[\hbar]]\) is
  \[
    f*g=m\circ\exp\left(\frac{\hbar}{2}P\right)(f\otimes g),
  \]
  and
  \[
    [f,g]_{\mathrm{raw}}=f*g-g*f,\qquad
    \{f,g\}_\hbar=\hbar^{-1}[f,g]_{\mathrm{raw}}.
  \]
  The reduced quantum Hamiltonian Lie algebra is the scalar quotient
  \[
    \bar A_\hbar=\C[[z_1,z_2]][[\hbar]]/\C[[\hbar]]
  \]
  as a Lie algebra.  It is not used as an associative quotient.
\end{defn}

\begin{thm}[Exact formal Weyl/Moyal coefficients]
\label{thm:app-radial-moyal-coefficients}
  For \(f=z_1^kz_2^l\) and \(g=z_1^mz_2^n\),
  \[
    P^r(f,g)=
    \sum_{a=0}^r(-1)^a\binom ra
      (k)_{r-a}(l)_a(m)_a(n)_{r-a}
      z_1^{k+m-r}z_2^{l+n-r}.
  \]
  Consequently
  \[
    [f,g]_{\mathrm{raw}}
      =\sum_{\substack{r\geq1\\r\ \mathrm{odd}}}
        \frac{2}{2^r r!}\hbar^rP^r(f,g),
  \]
  equivalently, for \(s\geq0\), the raw coefficient of
  \(\hbar^{2s+1}\) is
  \[
    \frac{1}{2^{2s}(2s+1)!}\,P^{2s+1}(f,g),
  \]
  and the normalized Hamiltonian bracket has coefficient
  \[
    \frac{\hbar^{2s}}{2^{2s}(2s+1)!}\,P^{2s+1}(f,g).
  \]
  The first and third raw commutator coefficients are
  \[
    \hbar P(f,g),\qquad \frac{\hbar^3}{24}P^3(f,g),
  \]
  and all even raw commutator coefficients vanish.  This is a theorem
  inside the formal Weyl algebra of the constant symplectic plane.  It
  uses no finite-\(N\) radial-parts theorem and no Costello graph
  specialization.
\end{thm}

\begin{proof}
  The two summands in
  \(P=\partial_{z_1}\otimes\partial_{z_2}
     -\partial_{z_2}\otimes\partial_{z_1}\)
  commute as differential operators on the tensor product.  The
  binomial theorem gives
  \[
    P^r=\sum_{a=0}^r(-1)^a\binom ra
      \partial_{z_1}^{r-a}\partial_{z_2}^{a}
      \otimes
      \partial_{z_1}^{a}\partial_{z_2}^{r-a}.
  \]
  Applying this to the two monomials gives the falling-factorial
  formula.  Interchanging \(f\) and \(g\) changes \(P^r(f,g)\) by
  \((-1)^r\), so the commutator retains exactly the odd powers and
  contributes the coefficient \(2/(2^r r!)\) in order \(r\).
\end{proof}

\begin{cor}[All odd Moyal coefficients]
\label{cor:app-radial-all-odd-moyal-coefficients}
  The Weyl/Moyal commutator has no even raw powers of \(\hbar\).  Its
  odd raw and normalized coefficients are
  \[
    [f,g]_{\mathrm{raw}}^{(2s+1)}
      =
      \frac{\hbar^{2s+1}}{2^{2s}(2s+1)!}P^{2s+1}(f,g),
    \qquad
    \{f,g\}_\hbar^{(2s)}
      =
      \frac{\hbar^{2s}}{2^{2s}(2s+1)!}P^{2s+1}(f,g).
  \]
  In particular the next two raw coefficients after the third-order
  term are
  \[
    \frac{\hbar^5}{1920}P^5(f,g),\qquad
    \frac{\hbar^7}{322560}P^7(f,g).
  \]
\end{cor}

\begin{proof}
  Put \(r=2s+1\) in
  Theorem~\ref{thm:app-radial-moyal-coefficients}.  Then
  \(2/(2^{2s+1}(2s+1)!)=1/(2^{2s}(2s+1)!)\).  Dividing by \(\hbar\)
  gives the normalized coefficient.
\end{proof}

\begin{cor}[First and third formal graph weights]
\label{cor:app-formal-first-third-weights}
  In the ordered formal product
  \(m\circ\exp(\hbar P/2)\), the one-cross-contraction term has weight
  \(\hbar P(f,g)/2\), and the three-cross-contraction term has weight
  \(\hbar^3P^3(f,g)/48\).  After antisymmetrising the ordered product,
  the commutator weights are
  \[
    \hbar P(f,g),\qquad \frac{\hbar^3}{24}P^3(f,g).
  \]
\end{cor}

\begin{proof}
  The ordered exponential contributes
  \[
    \frac{1}{r!}\left(\frac{\hbar}{2}\right)^r P^r(f,g)
  \]
  in order \(r\).  For \(r=1\) this is \(\hbar P(f,g)/2\); for \(r=3\)
  it is \(\hbar^3P^3(f,g)/(3!\,2^3)=\hbar^3P^3(f,g)/48\).  Since
  \(P(g,f)=-P(f,g)\) and \(P^3(g,f)=-P^3(f,g)\), subtracting the reverse
  ordered product doubles these two ordered contributions.
\end{proof}

\begin{ex}[A higher-order coefficient check]
\label{ex:app-radial-higher-moyal-check}
  For
  \[
    f=z_1^4z_2^2,\qquad g=z_1^2z_2^4,
  \]
  the first nonzero odd contractions are
  \[
    P(f,g)=12z_1^5z_2^5,\qquad
    P^3(f,g)=-960z_1^3z_2^3,\qquad
    P^5(f,g)=11520z_1z_2 .
  \]
  Hence
  \[
    [f,g]_{\mathrm{raw}}
      =
      12\hbar z_1^5z_2^5
      -40\hbar^3 z_1^3z_2^3
      +6\hbar^5 z_1z_2 .
  \]
  The third coefficient is \(-960/24=-40\).  The fifth coefficient is
  \(11520/1920=6\).  This example checks the numerical normalization
  beyond the first nontrivial term without using radial parts.
\end{ex}

\begin{proof}
  Apply the falling-factorial formula of
  Theorem~\ref{thm:app-radial-moyal-coefficients}.  For \(r=1\),
  \[
    4\cdot4-2\cdot2=12.
  \]
  For \(r=3\),
  \[
  \begin{aligned}
    P^3(f,g)
    &=
      \bigl(24\cdot24
      -3\cdot12\cdot2\cdot2\cdot12
      +3\cdot4\cdot2\cdot2\cdot4\bigr)z_1^3z_2^3  \\
    &=-960z_1^3z_2^3 .
  \end{aligned}
  \]
  For \(r=5\), only the \(a=1\) and \(a=2\) summands survive, and they
  give
  \[
    \bigl(-5\cdot24\cdot2\cdot2\cdot24
      +10\cdot24\cdot2\cdot2\cdot24\bigr)z_1z_2
    =
    11520z_1z_2 .
  \]
  Substituting the odd Moyal coefficients
  \(1\), \(1/24\), and \(1/1920\) gives the displayed raw commutator.
\end{proof}

\begin{defn}[Matrix Weyl algebra and Weyl traces]
\label{def:app-radial-matrix-weyl}
  Let \(\mathcal W_N\) be the completed Weyl algebra generated by
  entries of two \(N\times N\) matrices \(X,Y\) with
  \[
    [X^i{}_j,Y^k{}_l]=\hbar\,\delta^i_l\delta^k_j,\qquad
    [X^i{}_j,X^k{}_l]=[Y^i{}_j,Y^k{}_l]=0.
  \]
  The normal-ordered quantum comoment for conjugation is
  \[
    \widehat\mu_\epsilon=-\operatorname{Tr}([\epsilon,X]Y),
    \qquad
    \hbar^{-1}[\widehat\mu_\epsilon,a]=\epsilon\cdot a.
  \]
  For \(f\in\C[z_1,z_2][[\hbar]]\), define the Weyl-ordered trace
  \[
    J_N(f)=\operatorname{Tr}\operatorname{Op}_{\mathrm W}(f)(X,Y).
  \]
  The degree-zero quantum Hamiltonian reduction uses the effective
  traceless comoment ideal
  \[
    \mathrm N_{\mathcal W_N}
      (\mathcal W_N\widehat\mu(\lie{sl}_N))/
    \mathcal W_N\widehat\mu(\lie{sl}_N).
  \]
  The scalar Hamiltonian line is not killed by this moment ideal itself;
  below it is removed by quotienting the empty trace before connected
  large-\(N\) extraction.
\end{defn}

\begin{lem}[Capelli--Weyl triangular normalization]
\label{lem:app-radial-capelli-triangular}
  Let \(T_{a,b}=\operatorname{Tr}(X^aY^b)\) be the normal-ordered trace.
  In the quantum Hamiltonian reduction, the locally proved
  Weyl-normal-ordering formula is
  \[
    J_N(z_1^az_2^b)\equiv
      \sum_{r=0}^{\min(a,b)}
        \left(-\frac{\hbar N}{2}\right)^r
        r!\binom ar\binom br\,T_{a-r,b-r}.
  \]
  The inverse triangular system is
  \[
    T_{a,b}\equiv
      \sum_{r=0}^{\min(a,b)}
        \left(\frac{\hbar N}{2}\right)^r
        r!\binom ar\binom br\,J_N(z_1^{a-r}z_2^{b-r}).
  \]
\end{lem}

\begin{proof}
  Total Weyl symmetrisation is obtained from normal ordering by
  commuting \(Y\)'s past \(X\)'s.  Each contraction contributes the
  Capelli contact term coming from
  \[
    YX-XY+\hbar N I\equiv0
      \pmod{\mathcal W_N\widehat\mu(\lie{sl}_N)}.
  \]
  Choosing \(r\) contracted \(X\)-slots and \(r\) contracted \(Y\)-slots
  gives \(\binom ar\binom br\), pairing them gives \(r!\), and Weyl
  ordering contributes \(2^{-r}\).  The sign is negative because the
  displayed moment relation rewrites a normal-ordering swap as the
  lower triangular term \(-\hbar N\).  The diagonal term is \(r=0\),
  hence the system is unipotent over \(\C[[\hbar N]]\); inversion
  changes \(-\hbar N/2\) to \(+\hbar N/2\).

  The cited Capelli literature supplies the standard source for the
  Capelli contact phenomenon, and the displayed contraction count fixes
  the bivariate trace normalization used here.
\end{proof}

\begin{stmt}[Radial-parts input package]
\label{stmt:app-radial-external-input}
  The finite-\(N\) radial-parts step uses the following
  Harish-Chandra radial-parts theorem for invariant differential
  operators, in the form refined by Wallach and by
  Levasseur--Stafford
  \cites{harish-chandra-invariant-differential-operators,
  wallach-reductive-invariant-differential,
  levasseur-stafford-harish-chandra,
  levasseur-stafford-kernel-harish-chandra}.  After identifying
  \(\mathcal W_N\simeq\mathcal D_\hbar(\mathfrak{gl}_N)\), this package
  uses the Harish-Chandra map on invariants whose kernel is the quantum
  moment-map ideal and hence injects the quantum Hamiltonian reduction
  by conjugation into Weyl-invariant differential operators on the
  regular Cartan.  With
  \(\lambda_1,\ldots,\lambda_N\) the Cartan coordinates and
  \(\Delta=\prod_{i<j}(\lambda_i-\lambda_j)\), the radial-part map is
  conjugated by \(\Delta\).

  The cited radial-parts literature sources the Harish-Chandra
  homomorphism, regular-Cartan landing, and kernel statement.  The
  exact Weyl-trace image in item~(3) is the matched normalization datum
  used in the formal-local comparison.  It is not supplied by the cited radial-parts
  sources in this exact Weyl/Capelli convention.  The finite exact checks
  below attack it in ranks \(2\) and \(3\), but they do not replace the
  all-\(N\) radial-parts input.

  The input consists of the following three assertions.
  \begin{enumerate}
    \item The Vandermonde-conjugated radial map is a homomorphism from
      the invariant quantum Hamiltonian reduction by conjugation to
      Weyl-invariant differential operators on the regular Cartan.
    \item Its kernel is precisely the quantum moment-map ideal; hence it
      is injective on the reduced quotient.
    \item The Weyl trace generators used here have image
  \[
    \operatorname{Rad}_0(J_N(f))
      =\Delta^{-1}\left(\sum_{i=1}^N
        \operatorname{Op}_{\mathrm W}
        (f)(\lambda_i,-\hbar\partial_{\lambda_i})\right)\Delta.
  \]
  \end{enumerate}
  The nonlinear-shear test in
  Lemma~\ref{lem:app-radial-nonlinear-shear-obstruction} shows that
  pure \(z_1\)- and \(z_2\)-power images together with classical
  symbol-level shear compatibility do not determine item~(3).  A smaller
  source package would need a genuine quantum-corrected Egorov theorem in
  the Weyl algebra.
\end{stmt}

\begin{defn}[Radially normalized Weyl trace class]
Assume only the homomorphism and injectivity clauses of
Statement~\ref{stmt:app-radial-external-input}.  For
\(f\in\C[z_1,z_2][[\hbar]]\), a class \(J_N^{\mathrm{rad}}(f)\) in the
degree-zero quantum Hamiltonian reduction is called radially normalized
if
\[
  \operatorname{Rad}_0(J_N^{\mathrm{rad}}(f))
  =\Delta^{-1}S_N(f)\Delta .
\]
Existence is a normalization hypothesis; uniqueness follows from radial
injectivity.  Statement~\ref{stmt:app-radial-external-input}(3) is
exactly the assertion that the ordinary Weyl trace \(J_N(f)\) equals
\(J_N^{\mathrm{rad}}(f)\).
\end{defn}

\begin{defn}[Vandermonde gauge variables]
\label{def:app-radial-vandermonde-gauge-variables}
  Set
  \[
    \nabla_i^\Delta
      =
      \Delta^{-1}(-\hbar\partial_{\lambda_i})\Delta
      =
      -\hbar\partial_{\lambda_i}
      -\hbar\sum_{j\neq i}\frac{1}{\lambda_i-\lambda_j}.
  \]
  The logarithmic summand is the type \(A\) Dunkl--Calogero correction
  in the Vandermonde gauge.  For \(f\in\C[z_1,z_2][[\hbar]]\), put
  \[
    S_N(f)=\sum_{i=1}^N
      \operatorname{Op}_{\mathrm W}
      (f)(\lambda_i,-\hbar\partial_{\lambda_i})
  \]
  and
  \[
    R_N(f)=
      \sum_{i=1}^N
      \operatorname{Op}_{\mathrm W}
      (f)(\lambda_i,\nabla_i^\Delta)
      =
      \Delta^{-1}S_N(f)\Delta .
  \]
\end{defn}

\begin{lem}[Dunkl--Calogero correction cancellation]
\label{lem:app-radial-dunkl-calogero-cancellation}
  The Vandermonde-gauge variables satisfy
  \[
    [\lambda_i,\lambda_j]=0,\qquad
    [\nabla_i^\Delta,\nabla_j^\Delta]=0,\qquad
    [\lambda_i,\nabla_j^\Delta]=\hbar\,\delta_{ij}.
  \]
  Consequently
  \[
    \hbar^{-1}[R_N(f),R_N(g)]=R_N(\{f,g\}_\hbar)
  \]
  for all \(f,g\).  In particular, all logarithmic
  Dunkl--Calogero terms introduced by expanding
  \(\Delta^{-1}S_N(-)\Delta\) cancel in the commutator identity.
\end{lem}

\begin{proof}
  The operator \(\nabla_i^\Delta\) is conjugate to
  \(-\hbar\partial_{\lambda_i}\) by multiplication by \(\Delta\).
  The three displayed commutation relations are therefore the ordinary
  Weyl relations for
  \((\lambda_i,-\hbar\partial_{\lambda_i})\), conjugated by
  \(\Delta\).  The correction terms are a pure gauge connection:
  their curvature is zero because the unconjugated partial derivatives
  commute.  Hence the \(i\)-th summand is again a one-particle Weyl
  representation of the formal Moyal algebra, and different summands
  commute.  This gives the displayed commutator identity.  No separate
  Calogero potential remains after the computation is kept in
  Vandermonde-conjugated form.
\end{proof}

\begin{lem}[Radial-map injectivity on the reduced quotient]
\label{lem:app-radial-map-injectivity}
  Under Statement~\ref{stmt:app-radial-external-input}, if an invariant
  Weyl operator \(D\) in the normalizer of the quantum moment-map ideal
  satisfies
  \[
    \operatorname{Rad}_0(D)=0,
  \]
  then \(D\) is zero in the degree-zero quantum Hamiltonian reduction.
\end{lem}

\begin{proof}
  Statement~\ref{stmt:app-radial-external-input} identifies the kernel
  of the Vandermonde-conjugated Harish-Chandra radial map with the
  quantum moment-map ideal.  Passing to the normalizer quotient by that
  ideal gives an injective map into Weyl-invariant differential
  operators on the regular Cartan.  Thus an element with zero radial
  image represents the zero class in the reduced quotient.
\end{proof}

\begin{lem}[Nonlinear shear obstruction to a smaller radial package]
\label{lem:app-radial-nonlinear-shear-obstruction}
  Pure-power radial images plus classical symbol-level compatibility
  with nonlinear shears do not determine the mixed Weyl-trace image
  normalization.  In the one-particle Weyl algebra
  \([\lambda,y]=\hbar\), the coefficient of \(t\) in
  \[
    (y+t\lambda^2)^4
  \]
  is
  \[
    4\lambda^2y^3-12\hbar\lambda y^2+8\hbar^2 y,
  \]
  whereas
  \[
    4\operatorname{Op}_{\mathrm W}(z_1^2z_2^3)
    =
    4\lambda^2y^3-12\hbar\lambda y^2+6\hbar^2 y.
  \]
  The difference \(2\hbar^2y\) is non-scalar.  Thus a proof of
  Statement~\ref{stmt:app-radial-external-input}(3) cannot be reduced to
  classical nonlinear shear covariance without adding the missing
  quantum Egorov correction.
\end{lem}

\begin{proof}
  Expand to first order in \(t\):
  \[
    (y+t\lambda^2)^4
    =
    y^4+t\sum_{j=0}^3 y^j\lambda^2y^{3-j}+O(t^2).
  \]
  Using \(y\lambda=\lambda y-\hbar\), the sum normal-orders to
  \(4\lambda^2y^3-12\hbar\lambda y^2+8\hbar^2y\).
  Weyl symmetrisation of \(z_1^2z_2^3\) gives
  \(\lambda^2y^3-3\hbar\lambda y^2+\frac32\hbar^2y\), hence the
  displayed value after multiplication by \(4\).  The discrepancy is a
  nonconstant one-particle operator, so it cannot be removed by the
  scalar Hamiltonian quotient.
\end{proof}

\begin{prop}[Quantum shear congruence suffices for the all-\(N\) image]\label{prop:app-quantum-shear-suffices-radial-image}
  Assume the homomorphism and injectivity clauses of
  Statement~\ref{stmt:app-radial-external-input}, and assume the pure
  power images
  \[
    \operatorname{Rad}_0(J_N(z_1^r))=\Delta^{-1}S_N(z_1^r)\Delta,
    \qquad
    \operatorname{Rad}_0(J_N(z_2^r))=\Delta^{-1}S_N(z_2^r)\Delta
  \]
  for all \(r\geq0\).  Suppose moreover that, for all \(a,b\geq0\), the
  quantum shear congruence
  \[
    \hbar^{-1}\bigl[
      J_N(z_1^{a+1}/(a+1)),J_N(z_2^{b+1})
    \bigr]
    \equiv
    J_N\!\left(
      \{z_1^{a+1}/(a+1),z_2^{b+1}\}_\hbar
    \right)
    \pmod {I_N}
  \]
  holds in the degree-zero quantum Hamiltonian reduction, where \(I_N\)
  is the quantum moment-map ideal.  Then the exact Weyl-trace image in
  Statement~\ref{stmt:app-radial-external-input}(3) holds for every
  monomial \(z_1^az_2^b\), hence for every polynomial \(f\).
\end{prop}

\begin{proof}
  The normalized Moyal bracket gives
  \[
    \{z_1^{a+1}/(a+1),z_2^{b+1}\}_\hbar
    =
    (b+1)z_1^az_2^b
    +\sum_{s\ge1}
      \frac{\hbar^{2s}(a+1)_{2s+1}(b+1)_{2s+1}}
      {(a+1)2^{2s}(2s+1)!}
      z_1^{a-2s}z_2^{b-2s}.
  \]
  Every summand after the leading term has lower total degree.  The pure
  power cases start the induction.  Assume the asserted radial image is
  known in all total degrees \(<a+b\).  Applying the radial homomorphism
  to the quantum shear congruence identifies the radial image of the
  left-hand commutator with the Moyal commutator of the already known
  pure-power radial images.  Lemma~\ref{lem:app-radial-cartan-moyal-representation}
  computes this as the Vandermonde-conjugated Weyl quantization of the
  displayed Moyal bracket.  By the induction hypothesis all lower-degree
  terms have the required images, so the leading coefficient
  \((b+1)\) determines the image of \(J_N(z_1^az_2^b)\).  Radial
  injectivity then identifies the class in the reduced quotient.
\end{proof}

\begin{lem}[Moment-ideal primitive form of the quantum shear input]
\label{lem:app-quantum-shear-primitive-obstruction}
  In the notation of
  Proposition~\ref{prop:app-quantum-shear-suffices-radial-image}, the
  quantum shear congruence is equivalent to the following explicit
  left-ideal membership problem.  Put
  \[
    E_{a,b,N}
    =
    \sum_{j=0}^b\operatorname{Tr}(Y^jX^aY^{b-j})
    -
    J_N\!\left(
      \{z_1^{a+1}/(a+1),z_2^{b+1}\}_\hbar
    \right).
  \]
  Then the congruence holds if and only if
  \(E_{a,b,N}\in\mathcal W_N\widehat\mu(\lie{sl}_N)\).  Equivalently,
  after choosing normal-ordered matrix generators
  \(\widehat\mu^i{}_j\) for the traceless quantum moment-map ideal, one
  must construct coefficients \(A^j{}_i(a,b,N)\in\mathcal W_N\) such
  that
  \[
    E_{a,b,N}=\sum_{i,j}A^j{}_i(a,b,N)\widehat\mu^i{}_j .
  \]
\end{lem}

\begin{proof}
  Since the pure powers are already Weyl ordered,
  \(J_N(z_1^{a+1}/(a+1))=\operatorname{Tr}(X^{a+1})/(a+1)\) and
  \(J_N(z_2^{b+1})=\operatorname{Tr}(Y^{b+1})\).  The Weyl relations give
  \[
    \hbar^{-1}
    \bigl[\operatorname{Tr}(X^{a+1})/(a+1),Y\bigr]
    =X^a .
  \]
  Applying the Leibniz rule to \(Y^{b+1}\) gives
  \[
    \hbar^{-1}
    \bigl[
      J_N(z_1^{a+1}/(a+1)),J_N(z_2^{b+1})
    \bigr]
    =
    \sum_{j=0}^b\operatorname{Tr}(Y^jX^aY^{b-j}).
  \]
  Subtracting the \(J_N\)-image of the normalized Moyal bracket gives
  exactly \(E_{a,b,N}\).  Reduction modulo \(I_N\) is reduction modulo
  the left ideal
  \(\mathcal W_N\widehat\mu(\lie{sl}_N)\), so the displayed congruence
  is precisely the asserted membership.  The coefficient formula is the
  same membership written after a choice of generators for that left
  ideal.
\end{proof}

\begin{stmt}[Free trace-diagram quantum-lift obstruction]
\label{stmt:app-quantum-shear-trace-diagram-obstruction}
  Put \(M=YX-XY+\hbar N I\), and interpret
  \[
    \operatorname{Tr}(W M)=\sum_{i,j}W^j{}_iM^i{}_j
  \]
  as a left-ideal expression.  Let \(\mathsf C_{a,b}\) be the rational
  vector space spanned by words \(W\) with \(a-1\) letters \(X\) and
  \(b-1\) letters \(Y\), and let \(\mathsf{Cyc}_{a,b}\) be the cyclic
  word space with \(a\) letters \(X\) and \(b\) letters \(Y\).  The
  leading term of the desired primitive is the cyclic boundary equation
  \[
    \partial c=
    \sum_{j=0}^b[Y^jX^aY^{b-j}]
    -\frac{b+1}{\binom{a+b}{a}}
      \sum_{U\in \operatorname{Sh}(a,b)}[U],
    \qquad
    \partial W=[WYX]-[WXY].
  \]
  An all-\(N\) primitive is stronger.  It requires equality after free
  indexed normal ordering, including every contraction term which splits
  a trace into multi-traces:
  \[
    \mathcal N_{\mathrm{free}}\!\left(
      \sum_W c_W\operatorname{Tr}(W M)\right)
    =
    \mathcal N_{\mathrm{free}}(E_{a,b,N}).
  \]
  The cyclic equation alone does not imply this quantum equation.

  In bidegree \((a,b)=(4,4)\), the lexicographic pivot solution of the
  cyclic equation is
  \[
  \begin{aligned}
    C^{\mathrm{cl}}_{4,4}
    &=
      \frac{31}{7}\operatorname{Tr}(XXXYYY\,M)
      -\frac{4}{7}\operatorname{Tr}(XXYXYY\,M)
      -\frac{4}{7}\operatorname{Tr}(XXYYXY\,M)\\
    &\quad
      +\frac{27}{7}\operatorname{Tr}(XXYYYX\,M)
      +\frac{23}{7}\operatorname{Tr}(XYXXYY\,M)
      +\frac{1}{7}\operatorname{Tr}(XYXYXY\,M)\\
    &\quad
      +\operatorname{Tr}(XYXYYX\,M)
      -\frac{2}{7}\operatorname{Tr}(XYYXXY\,M)
      +\frac{15}{7}\operatorname{Tr}(XYYXYX\,M).
  \end{aligned}
  \]
  Its quantum residual is nonzero.  In rank \(N=2\), exact normal
  ordering gives
  \[
  \begin{aligned}
    R^{\mathrm{cl}}_{4,4,2}
    &:=
      E_{4,4,2}-C^{\mathrm{cl}}_{4,4}\\
    &=
      \frac{43}{70}\hbar^2\bigl(
        4\operatorname{Tr}(XXYY)-5\operatorname{Tr}(XYXY)
        +2\operatorname{Tr}(XYYX)\\
    &\hspace{4.6cm}
        -5\operatorname{Tr}(YXYX)
        +4\operatorname{Tr}(YYXX)
      \bigr)\neq0 .
  \end{aligned}
  \]
  After expanding the displayed traces into normal-ordered matrix
  entries, the coefficient of
  \(\hbar^2X^1{}_1X^1{}_1Y^1{}_2Y^2{}_1\) is \(43/7\).

  The residual is killed by the classical-kernel correction
  \[
  \begin{aligned}
    K_{4,4}
    &=
    \frac{43}{14}\bigl(
      \operatorname{Tr}(XXYXYY\,M)
      -\operatorname{Tr}(XYXXYY\,M)
      \\
    &\qquad
      -\operatorname{Tr}(XYYXYX\,M)
      +\operatorname{Tr}(XYYYXX\,M)
    \bigr),
  \end{aligned}
  \]
  whose cyclic boundary is zero.  The free normal-form computation below
  proves that this correction cancels the \((4,4)\) residual before any
  finite-rank trace identity is imposed.  The remaining theorem
  obligation is the decorated PBW Stokes identity: prove, for every
  bidegree, that
  \[
    \Omega^{\mathrm{rad}}_{a,b}=0
    \quad\Longleftrightarrow\quad
    D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b},
    \qquad
    D^\square_{a,b}=C^+_{a,b}\partial_2 .
  \]
  If this fails, the certificate is not a timed-out finite computation
  but a normalized signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})=1\).
\end{stmt}

\begin{proof}
  The leading \(\hbar^0\) component of
  \(\operatorname{Tr}(W M)\) is
  \([WYX]-[WXY]\) in the cyclic trace quotient; comparing it with the
  leading term of \(E_{a,b,N}\) gives the displayed cyclic equation.
  Normal ordering in the indexed Weyl algebra contracts every occurrence
  of a \(Y\)-entry moved past an \(X\)-entry.  These contractions identify
  matrix indices and may split one cyclic trace into a product of cyclic
  traces.  Hence equality in the cyclic quotient is only the associated
  graded condition.

  The \((4,4)\) coefficients displayed above solve the cyclic equation
  in the stated pivot gauge.  Direct exact normal ordering in
  \(\mathcal W_2\) gives the displayed residual.  Its nonvanishing follows
  from the indicated normal monomial coefficient.  Applying \(\partial\)
  to the four words in \(K_{4,4}\) gives two copies of each resulting
  cyclic word with opposite signs, so \(K_{4,4}\in\ker\partial\).  The
  finite computation proves the obstruction to the uncorrected cyclic
  lift.  The all-\(N\) status of \(K_{4,4}\) is supplied by the free
  trace-diagram normal form below, not by finite-rank specialization.
\end{proof}

\begin{defn}[Free indexed normal diagrams]
\label{def:app-free-indexed-normal-diagrams}
  Let \(u=L_1\cdots L_m\) be a word in \(X,Y\).  Write the trace
  \(\operatorname{Tr}(u)\) as the directed \(m\)-gon with vertices
  \(v_0,\ldots,v_{m-1}\) and edge \(e_r:v_r\to v_{r+1}\), labelled
  \(L_r\), with indices read modulo \(m\).  A contraction matching
  \(\Gamma\) is a partial matching of pairs
  \[
    p<q,\qquad L_p=Y,\qquad L_q=X .
  \]
  For each pair \((p,q)\in\Gamma\), delete the two edges \(e_p,e_q\)
  and identify
  \[
    v_q\sim v_{p+1},\qquad v_p\sim v_{q+1}.
  \]
  Let \(e(u,\Gamma)\) be the number of isolated vertices left after
  these deletions and identifications.  Let
  \(\mathsf D(u,\Gamma)\) be the remaining directed labelled graph,
  with all \(X\)-edges placed before all \(Y\)-edges in the ambient
  commutative normal-ordered algebra of matrix entries.  Disconnected
  components are retained; they are the split-trace terms.  The empty
  graph is denoted \(1\).
\end{defn}

\begin{thm}[Free indexed normal-ordering formula]
\label{thm:app-free-indexed-normal-ordering}
  In the universal indexed matrix Weyl algebra with
  \[
    Y^k{}_lX^i{}_j=X^i{}_jY^k{}_l-\hbar\,\delta^i_l\delta^k_j,
  \]
  the normal-ordered trace word is
  \[
    \mathcal N_{\mathrm{free}}\operatorname{Tr}(u)
    =
    \sum_{\Gamma}
      (-\hbar)^{|\Gamma|}
      N^{e(u,\Gamma)}
      \mathsf D(u,\Gamma),
  \]
  where the sum runs over all contraction matchings
  \(\Gamma\) of \(Y\)-before-\(X\) inversions in \(u\).  Consequently
  \[
  \begin{aligned}
    \mathcal N_{\mathrm{free}}\operatorname{Tr}(W M)
    &=
      \mathcal N_{\mathrm{free}}\operatorname{Tr}(WYX)
      -\mathcal N_{\mathrm{free}}\operatorname{Tr}(WXY)\\
    &\quad
      +\hbar N\,\mathcal N_{\mathrm{free}}\operatorname{Tr}(W),
  \end{aligned}
  \]
  with \(M=YX-XY+\hbar N I\), interpreted as the left-ideal expression
  \(\operatorname{Tr}(W M)=\sum_{i,j}W^j{}_iM^i{}_j\).
\end{thm}

\begin{proof}
  Move the \(X\)-entries leftward through the \(Y\)-entries by the PBW
  relation displayed above.  Choosing the commutator summand at a swap
  selects one pair \(Y_p,X_q\), contributes the factor \(-\hbar\), and
  imposes exactly the two Kronecker identifications
  \(v_q\sim v_{p+1}\) and \(v_p\sim v_{q+1}\).  Choosing the ordered
  summand leaves both edges and continues the PBW ordering.  Since a
  generator can be contracted only once, the possible choices are
  precisely the partial matchings of original inversions.  After all
  \(X\)-entries have been moved left, the uncontracted entries form the
  normal diagram \(\mathsf D(u,\Gamma)\).  Each isolated index loop
  contributes a free summation over \(1,\ldots,N\), hence \(N\).  This
  proves the formula for trace words.  The formula for
  \(\operatorname{Tr}(W M)\) is the defining expansion of \(M\), with the
  scalar matrix term contributing \(\hbar N\operatorname{Tr}(W)\).
\end{proof}

\begin{lem}[Stable injectivity for normal trace diagrams]
\label{lem:app-free-trace-diagram-stable-injectivity}
  Fix \(d\).  Let \(\mathsf{Diag}_{\le d}\) be the rational span of free
  indexed normal diagrams with at most \(d\) labelled nonempty edges,
  with coefficients in \(\Q[\hbar,N]\).  The joint specialization map
  to \(N\times N\) matrices for all ranks \(N\ge d\) is injective.  Thus
  a free normal-form equality in \(\mathsf{Diag}_{\le d}\) is an all-\(N\)
  matrix Weyl identity, and a nonzero free residual cannot be killed by
  a theorem which only checks finitely many ranks below the stable
  Procesi--Razmyslov range.
\end{lem}

\begin{proof}
  Polarize in the labelled edges.  A linear relation among polarized
  closed directed trace diagrams of edge degree at most \(d\) is a trace
  identity for generic matrices of degree at most \(d\).  The
  Procesi--Razmyslov second fundamental theorem says that the trace
  identities are generated by the fundamental antisymmetrizer on
  \(N+1\) index lines.  Hence no nonzero identity of degree at most
  \(d\) exists in ranks \(N\ge d\).  Since the coefficients are
  polynomials in the formal scalar \(N\), vanishing in every rank
  \(N\ge d\) forces each coefficient polynomial to vanish.  Depolarizing
  gives the stated injectivity.
\end{proof}

\begin{prop}[First free residual and its kernel correction]
\label{prop:app-free-trace-diagram-K44}
  Use the normal-diagram notation of
  Definition~\ref{def:app-free-indexed-normal-diagrams}; for instance
  \(\mathsf D(X_{0\to1}Y_{1\to0})\) denotes the directed two-edge
  normal diagram with one \(X\)-edge and one \(Y\)-edge.  Then
  \[
  \begin{aligned}
    \mathcal N_{\mathrm{free}}
      (E_{4,4,N}-C^{\mathrm{cl}}_{4,4})
    &=
      \frac{43}{7}\hbar^2\Bigl(
      \mathsf D(X_{0\to1}X_{1\to2}Y_{2\to3}Y_{3\to0})\\
    &\quad
      -\mathsf D(X_{0\to1}X_{2\to3}Y_{1\to2}Y_{3\to0})\\
    &\quad
      -\hbar\,\mathsf D(X_{0\to0}\mid Y_{0\to0})
      +\hbar N\,\mathsf D(X_{0\to1}Y_{1\to0})
      \Bigr).
  \end{aligned}
  \]
  Moreover
  \[
    \mathcal N_{\mathrm{free}}(K_{4,4})
    =
    \mathcal N_{\mathrm{free}}
      (E_{4,4,N}-C^{\mathrm{cl}}_{4,4}),
  \]
  and therefore
  \[
    \mathcal N_{\mathrm{free}}
      (E_{4,4,N}-C^{\mathrm{cl}}_{4,4}-K_{4,4})=0.
  \]
  This is an all-\(N\) identity in the free indexed normal-diagram
  algebra.  It is not inferred from ranks \(2\) and \(3\).
\end{prop}

\begin{proof}
  Apply Theorem~\ref{thm:app-free-indexed-normal-ordering} to the nine
  trace words in \(C^{\mathrm{cl}}_{4,4}\) and to the Weyl-trace
  expression defining \(E_{4,4,N}\).  The finite matching enumeration is
  rational and contains no finite-rank specialization.  It leaves exactly
  the four displayed normal diagrams.  Applying the same formula to the
  four trace words in \(K_{4,4}\) gives the same four-diagram vector.
  The script
  \[
    \texttt{scripts/quantum\_shear\_trace\_diagram\_normal\_form.py}
  \]
  is the reproducible enumeration: with
  \(\texttt{--case 4,4 --classical-only}\) it prints the four-term
  residual above, and with \(\texttt{--case 4,4}\) it verifies zero
  residual after adding \(K_{4,4}\).
\end{proof}

\begin{defn}[Kernel-correction residual and decorated necklace complex]
\label{def:app-free-kernel-correction-obstruction}
  Let \(\mathsf W_{a,b}\) be the rational span of words with \(a-1\)
  letters \(X\) and \(b-1\) letters \(Y\), and let
  \(\mathsf V_{a,b}=\mathsf{Cyc}_{a,b}\) be the rational span of cyclic
  words with \(a\) letters \(X\) and \(b\) letters \(Y\).  Define the
  two-colour necklace multigraph \(G_{a,b}\) by taking
  \(\mathsf V_{a,b}\) as its vertex span and by assigning to
  \(W\in\mathsf W_{a,b}\) the oriented edge
  \[
    e_W:[WXY]\longrightarrow[WYX].
  \]
  Its incidence map is
  \[
    \partial\colon\mathsf W_{a,b}\to\mathsf V_{a,b},\qquad
    \partial W=[WYX]-[WXY],
  \]
  and \(Z_{a,b}:=\ker\partial\) is the cycle space.

  Let \(\mathsf{Diag}_{a,b}\) denote the positive free indexed
  normal-diagram target in bidegree \((a,b)\): the uncontracted
  \(\hbar^0\) cyclic component is removed and all PBW contraction,
  split-trace, and Capelli \(\hbar N\)-terms are retained.  Write
  \(\pi_+\) for this projection.  Define the decorated contraction
  cochain by
  \[
    C^+_{a,b}(W)
    =
    \pi_+\mathcal N_{\mathrm{free}}\operatorname{Tr}(WM),
    \qquad
    M=YX-XY+\hbar NI.
  \]
  The correction map is
  \[
    \mathcal C_{a,b}=A_{a,b}:=
    C^+_{a,b}|_{Z_{a,b}}\colon
    Z_{a,b}\longrightarrow\mathsf{Diag}_{a,b}.
  \]

  Put
  \[
    T_{a,b}=
    \sum_{j=0}^b[Y^jX^aY^{b-j}]
    -\frac{b+1}{\binom{a+b}{a}}
      \sum_{U\in\operatorname{Sh}(a,b)}[U].
  \]
  For any solution \(c^{\mathrm{cl}}_{a,b}\) of
  \(\partial c=T_{a,b}\), define
  \[
    E^+_{a,b}
    =
    \pi_+\mathcal N_{\mathrm{free}}(E_{a,b,N})
  \]
  and put
  \[
    R_{a,b}^{\mathrm{free}}
    =
    E^+_{a,b}-C^+_{a,b}(c^{\mathrm{cl}}_{a,b})
  \]
  and define
  \[
    \mathfrak o_{a,b}
    =
    [R_{a,b}^{\mathrm{free}}]\in
    \operatorname{coker}\mathcal C_{a,b}.
  \]
  This is the kernel-correction class after a choice of classical lift.
  The radial obstruction itself is the lift-independent class
  \(\Omega^{\mathrm{rad}}_{a,b}\) and the signed-row criterion of
  Proposition~\ref{prop:app-radial-dual-potential-obstruction}.
\end{defn}

\begin{stmt}[Decorated kernel-correction Hodge criterion]
\label{stmt:app-free-kernel-homotopy-obstruction}
  Give \(Z_{a,b}\) and \(\mathsf{Diag}_{a,b}\) the inner products for
  which the chosen word-cycle and free normal-diagram bases are
  orthonormal.  Let \(A=A_{a,b}\) and define
  \[
    \Delta^{\mathrm{dec}}_{a,b}=AA^*,\qquad
    \mathsf H^{\mathrm{dec}}_{a,b}=\ker A^*
      =(\operatorname{im}A)^\perp .
  \]
  Let
  \[
    \Pi^{\mathrm{harm}}_{a,b}\colon
    \mathsf{Diag}_{a,b}\to\mathsf H^{\mathrm{dec}}_{a,b}
  \]
  be the orthogonal projection.  For every \(a,b\geq1\), the following
  conditions are equivalent.
  \begin{enumerate}
    \item There exists \(K_{a,b}\in Z_{a,b}\) such that
      \[
        C^+_{a,b}(K_{a,b})=R^{\mathrm{free}}_{a,b}.
      \]
    \item The kernel-correction class \(\mathfrak o_{a,b}\) vanishes.
    \item The decorated harmonic projection vanishes:
      \[
        \Pi^{\mathrm{harm}}_{a,b}R^{\mathrm{free}}_{a,b}=0.
      \]
    \item Every functional
      \(\lambda\in\mathsf{Diag}_{a,b}^{*}\) with
      \[
        \lambda C^+_{a,b}(K)=0\qquad(K\in Z_{a,b})
      \]
      also satisfies \(\lambda(R^{\mathrm{free}}_{a,b})=0\).
  \end{enumerate}
  When these equivalent conditions hold, the canonical Hodge correction is
  \[
    K_{a,b}=
    A_{a,b}^{*}(\Delta^{\mathrm{dec}}_{a,b})^{-1}
    R^{\mathrm{free}}_{a,b},
  \]
  with the inverse taken on \(\operatorname{im}A_{a,b}\).  Thus the
  fixed-lift kernel-correction problem is equivalent to
  \[
    \Pi^{\mathrm{harm}}_{a,b}R^{\mathrm{free}}_{a,b}=0
    \qquad\text{in the chosen bidegree.}
  \]
  This is an intermediate Hodge form.  The lift-independent exact
  obstruction theorem is the
  \(\Omega^{\mathrm{rad}}_{a,b}\), \(D^\square_{a,b}\), and normalized
  signed-row formulation in
  Proposition~\ref{prop:app-radial-dual-potential-obstruction}.
  Proposition~\ref{prop:app-free-trace-diagram-K44} supplies the first
  nonzero lift; the statement above does not prove the all-bidegree
  vanishing.
\end{stmt}

\begin{proof}
  If \(c\) and \(c'\) solve the cyclic equation, then
  \(c-c'\in Z_{a,b}\).  Hence
  \(R(c')-R(c)=-A_{a,b}(c'-c)\), so the class in
  \(\operatorname{coker}A_{a,b}\), and its harmonic projection, are
  independent of the chosen cyclic lift.

  The finite-dimensional Hodge decomposition for \(A\) gives
  \[
    \mathsf{Diag}_{a,b}=\operatorname{im}A\oplus\ker A^* .
  \]
  Therefore \(R^{\mathrm{free}}_{a,b}\in\operatorname{im}A\) if and
  only if its projection to \(\ker A^*\) is zero.  This proves the
  equivalence of the correction equation, the intermediate cokernel
  class, and the harmonic projection.  The functional criterion is the
  annihilator form of the same statement:
  \(R\in\operatorname{im}A\) if and only if every
  \(\lambda\in(\operatorname{im}A)^\perp=\ker A^*\) vanishes on \(R\).
  If \(R\in\operatorname{im}A\), then
  \(AA^*(AA^*)^{-1}R=R\) on \(\operatorname{im}A\), so the displayed
  \(K_{a,b}\) is a correction.  Conversely, any correction places
  \(R^{\mathrm{free}}_{a,b}\) in \(\operatorname{im}A\).
\end{proof}

\begin{defn}[Square-cell PBW Stokes complex]
\label{def:app-square-cell-pbw-stokes-complex}
  Let \(\mathsf S_{a,b}\) be the rational span of square cells obtained
  from two commuting adjacent swaps in a cyclic word with \(a\) letters
  \(X\) and \(b\) letters \(Y\).  A based representative has the form
  \[
    uXYvXYw,
  \]
  and its oriented square is
  \[
    uXYvXYw\to uYXvXYw\to uYXvYXw\to
    uXYvYXw\to uXYvXYw .
  \]
  Each side is read as the corresponding edge
  \(e_W:[WXY]\to[WYX]\) of the necklace graph.  This defines
  \[
    \partial_2\colon \mathsf S_{a,b}\longrightarrow\mathsf W_{a,b}.
  \]
  The decorated PBW Stokes map is
  \[
    D^\square_{a,b}
      =
      C^+_{a,b}\partial_2\colon
      \mathsf S_{a,b}\longrightarrow\mathsf{Diag}_{a,b}.
  \]
\end{defn}

\begin{lem}[Ordinary necklace Stokes theorem]
\label{lem:app-ordinary-necklace-stokes}
  For \(a,b\geq1\),
  \[
    \operatorname{im}\partial_2=\ker\partial .
  \]
\end{lem}

\begin{proof}
  Work first with based words.  A binary word with \(a\) letters \(X\)
  and \(b\) letters \(Y\) is the same as an order ideal in the rectangle
  poset \([a]\times[b]\), via its inversion set.  An adjacent
  \(XY\leftrightarrow YX\) move toggles one extremal box.  The cubical
  complex of the distributive lattice of order ideals, with squares
  generated by commuting toggles, is contractible.  Hence its rational
  one-cycles are generated by square boundaries.  Passing to cyclic words
  is the quotient by a finite cellular rotation action; over \(\Q\),
  transfer identifies the quotient rational homology with the invariant
  rational homology upstairs.  Thus every necklace cycle is a rational
  sum of square boundaries.
\end{proof}

\begin{prop}[Dual-potential form of the radial obstruction]
\label{prop:app-radial-dual-potential-obstruction}
  Define the finite-dimensional map
  \[
    B_{a,b}\colon\mathsf W_{a,b}\longrightarrow
    \mathsf V_{a,b}\oplus\mathsf{Diag}_{a,b},
    \qquad
    B_{a,b}(W)=(\partial W,C^+_{a,b}(W)),
  \]
  and the target
  \[
    \eta_{a,b}=(T_{a,b},E^+_{a,b}).
  \]
  Let
  \[
    \Omega^{\mathrm{rad}}_{a,b}
    =
    [\eta_{a,b}]\in\operatorname{coker}B_{a,b}.
  \]
  For fixed \((a,b)\), the following are equivalent.
  \begin{enumerate}
    \item \(\Omega^{\mathrm{rad}}_{a,b}=0\).
    \item For one, equivalently every, classical lift
      \(c^{\mathrm{cl}}_{a,b}\) with
      \(\partial c^{\mathrm{cl}}_{a,b}=T_{a,b}\), there is an
      \(H_{a,b}\in\mathsf S_{a,b}\) such that
      \[
        D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b}.
      \]
    \item For one, equivalently every, classical lift
      \(c^{\mathrm{cl}}_{a,b}\), the residual
      \(R^{\mathrm{free}}_{a,b}\) lies in
      \(\operatorname{im}(C^+_{a,b}|_{\ker\partial})\).
    \item \(\Pi^{\mathrm{harm}}_{a,b}R^{\mathrm{free}}_{a,b}=0\).
    \item For every pair
      \[
        (\phi,\lambda)\in
        \mathsf V_{a,b}^*\oplus\mathsf{Diag}_{a,b}^*
      \]
      satisfying
      \[
        \lambda C^+_{a,b}(W)=\phi(\partial W)
        \qquad(W\in\mathsf W_{a,b}),
      \]
      one has
      \[
        \lambda(E^+_{a,b})=\phi(T_{a,b}).
      \]
  \end{enumerate}
  Thus
  \[
    \Omega^{\mathrm{rad}}_{a,b}=0
    \quad\Longleftrightarrow\quad
    D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b}
  \]
  for one, equivalently every, classical lift.  Failure in bidegree
  \((a,b)\) is exactly a signed dual row
  \[
    (\phi,-\lambda)\in\ker B_{a,b}^*
  \]
  with
  \[
    \lambda(E^+_{a,b})-\phi(T_{a,b})\ne0.
  \]
  Equivalently, after rescaling, it is a normalized row
  \[
    \lambda\in\ker(D^\square_{a,b})^*,
    \qquad
    \lambda(R^{\mathrm{free}}_{a,b})=1 .
  \]
\end{prop}

\begin{proof}
  The pair \((\phi,\lambda)\) in the statement corresponds to the signed
  dual row \((\phi,-\lambda)\) on
  \(\mathsf V_{a,b}\oplus\mathsf{Diag}_{a,b}\).  It annihilates
  \(B_{a,b}(W)\) precisely when
  \(\lambda C^+_{a,b}(W)=\phi(\partial W)\).  Since the spaces are finite
  dimensional,
  \[
    \eta_{a,b}\in\operatorname{im}B_{a,b}
    \quad\Longleftrightarrow\quad
    \ell(\eta_{a,b})=0
    \text{ for every }\ell\in\ker B_{a,b}^* .
  \]
  Evaluating \((\phi,-\lambda)\) on \(\eta_{a,b}\) gives
  \(\phi(T_{a,b})-\lambda(E^+_{a,b})\), proving the equivalence of
  \(\Omega^{\mathrm{rad}}_{a,b}=0\) with the signed-row condition.

  If \(c^{\mathrm{cl}}_{a,b}\) is a classical lift, then
  \[
    \eta_{a,b}-B_{a,b}(c^{\mathrm{cl}}_{a,b})
    =
    (0,R^{\mathrm{free}}_{a,b}).
  \]
  Adding \(B_{a,b}(K)\) with \(K\in\ker\partial\) changes only the
  decorated diagram component by \(C^+_{a,b}(K)\).  Hence
  \(\eta_{a,b}\in\operatorname{im}B_{a,b}\) if and only if
  \(R^{\mathrm{free}}_{a,b}\in
  \operatorname{im}(C^+_{a,b}|_{\ker\partial})\).  By
  Lemma~\ref{lem:app-ordinary-necklace-stokes},
  \(\ker\partial=\operatorname{im}\partial_2\), so this image is exactly
  \(\operatorname{im}D^\square_{a,b}\).  The Hodge equivalence is the
  decomposition of
  Statement~\ref{stmt:app-free-kernel-homotopy-obstruction}.

  Finally, finite-dimensional duality for \(D^\square_{a,b}\) says that
  \(R^{\mathrm{free}}_{a,b}\notin\operatorname{im}D^\square_{a,b}\) if
  and only if some \(\lambda\in\ker(D^\square_{a,b})^*\) has
  \(\lambda(R^{\mathrm{free}}_{a,b})\ne0\).  Rescale the row to make the
  value \(1\).  The equality
  \(\lambda C^+_{a,b}(W)=\phi(\partial W)\) identifies this row with the
  signed row \((\phi,-\lambda)\in\ker B_{a,b}^*\), and evaluating that
  signed row on \(\eta_{a,b}\) gives
  \(\phi(T_{a,b})-\lambda(E^+_{a,b})\).
\end{proof}

\begin{rmk}[Potential form and the failure of the bare graph Green operator]
\label{rmk:app-decorated-hodge-potential-form}
  A functional \(\lambda\in\mathsf{Diag}_{a,b}^{*}\) satisfies
  \(\lambda C^+_{a,b}|_{\ker\partial}=0\) precisely when the edge cochain
  \[
    W\longmapsto \lambda C^+_{a,b}(W)
  \]
  has zero periods on the necklace graph \(G_{a,b}\).  The graph is
  connected for \(a,b>0\), since adjacent \(XY\leftrightarrow YX\)
  moves connect all two-colour necklaces.  Hence this zero-period
  condition is equivalent to a vertex potential
  \(\phi_\lambda\in\mathsf V_{a,b}^{*}\), unique up to a constant, with
  \[
    \lambda C^+_{a,b}(W)
    =
    \phi_\lambda([WYX])-\phi_\lambda([WXY])
    =
    \phi_\lambda(\partial W).
  \]
  Because \(T_{a,b}\) has total coefficient zero, \(\phi_\lambda(T_{a,b})\)
  is independent of the additive constant.  The radial obstruction
  vanishes, equivalently \(\Omega^{\mathrm{rad}}_{a,b}=0\), if and only
  if every such \(\lambda\) satisfies the potential identity
  \[
    \lambda\pi_+\mathcal N_{\mathrm{free}}(E_{a,b,N})
    =
    \phi_\lambda(T_{a,b}).
  \]
  By Lemma~\ref{lem:app-ordinary-necklace-stokes}, the same row condition
  is \(\lambda D^\square_{a,b}=0\).
  Indeed,
  \[
    \lambda(R^{\mathrm{free}}_{a,b})
    =
    \lambda E^+_{a,b}
    -\lambda C^+_{a,b}(c^{\mathrm{cl}}_{a,b})
    =
    \lambda E^+_{a,b}
    -\phi_\lambda(T_{a,b}).
  \]

  The ordinary graph Green operator for the incidence map
  \(\partial\) is therefore insufficient.  It constructs a classical
  cyclic lift \(c^{\mathrm{cl}}_{a,b}\) of \(T_{a,b}\), i.e. it solves
  only the uncontracted \(\hbar^0\) incidence equation.  The quantum
  correction equation is instead
  \(A_{a,b}K_{a,b}=R^{\mathrm{free}}_{a,b}\), equivalently
  \(D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b}\), inside the positive
  PBW diagram target, where contraction diagrams, split traces, and the
  Capelli term are visible.  No canonical inverse from an arbitrary
  positive diagram residual to a necklace edge cochain has been
  constructed here.  The correct finite-dimensional Green operator is
  the decorated square-cell one attached to
  \(D^\square_{a,b}(D^\square_{a,b})^{*}\).
\end{rmk}

\begin{prop}[Edge PBW telescoping primitive]
\label{prop:app-edge-pbw-telescoping}
  For every \(b\geq2\), set
  \[
    C^{\mathrm{edge}}_{2,b}
    =
    \sum_{r=0}^{\lfloor(b-2)/2\rfloor}
      (b-1-2r)\operatorname{Tr}(Y^rXY^{b-1-r}M).
  \]
  For every \(a\geq2\), set
  \[
    C^{\mathrm{edge}}_{a,2}
    =
    \frac3{a+1}
    \sum_{r=0}^{\lfloor(a-2)/2\rfloor}
      (a-1-2r)\operatorname{Tr}(X^{a-1-r}YX^rM).
  \]
  Then the free indexed normal-diagram identities
  \[
    \mathcal N_{\mathrm{free}}
      (E_{2,b,N}-C^{\mathrm{edge}}_{2,b})=0,
    \qquad
    \mathcal N_{\mathrm{free}}
      (E_{a,2,N}-C^{\mathrm{edge}}_{a,2})=0
  \]
  hold for all displayed edge bidegrees.  Hence
  \[
    \mathfrak o_{2,b}=0,\qquad
    \mathfrak o_{a,2}=0
  \]
  with no separate kernel correction in this edge gauge.  This is only
  the one-moving-letter edge strip; for \(a,b\geq3\) the remaining
  theorem is the decorated PBW Stokes problem
  \(D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b}\), equivalently the
  normalized signed-row criterion of
  Proposition~\ref{prop:app-radial-dual-potential-obstruction}.
\end{prop}

\begin{proof}
  We prove the \((2,b)\) strip.  Put
  \[
    \Theta_s^{(b)}=\mathsf D(XY^sXY^{b-s}),
    \qquad 0\leq s\leq b,
  \]
  and
  \[
    \Phi_s^{(b)}
    =
    \mathsf D(XY^s)\mid\mathsf D(Y^{b-1-s}),
    \qquad 0\leq s\leq b-1,
  \]
  where the vertical bar denotes disjoint union and
  \(\mathsf D(Y^0)\) is the isolated index loop, hence contributes the
  scalar factor \(N\).  For
  \[
    W_r=Y^rXY^{b-1-r},\qquad 0\leq r\leq b-1,
  \]
  Theorem~\ref{thm:app-free-indexed-normal-ordering} gives the PBW
  column identity
  \[
    \mathcal N_{\mathrm{free}}\operatorname{Tr}(W_rM)
    =
    \Theta_r^{(b)}-\Theta_{r+1}^{(b)}
    -\hbar\Phi_r^{(b)}
    +\hbar\Phi_{b-1-r}^{(b)}.
  \]
  Indeed,
  \[
    \operatorname{Tr}(W_rM)
    =
    \operatorname{Tr}(W_rYX)
    -\operatorname{Tr}(W_rXY)
    +\hbar N\operatorname{Tr}(W_r).
  \]
  PBW matchings in the first two trace words which do not use the
  adjacent crossing supplied by \(M\) cancel in pairs.  The matchings
  using that adjacent crossing are cancelled, including their secondary
  contractions, by the scalar term \(\hbar N\operatorname{Tr}(W_r)\).
  The uncontracted part leaves the boundary
  \(\Theta_r^{(b)}-\Theta_{r+1}^{(b)}\).  The two endpoint contraction
  families are the left and reflected right blocks, giving
  \(-\hbar\Phi_r^{(b)}\) and \(+\hbar\Phi_{b-1-r}^{(b)}\).  No further
  term survives the pairing.

  The target \(E_{2,b,N}\) contains only the first and third Moyal
  terms:
  \[
    J_N\!\left(
      \{z_1^3/3,z_2^{b+1}\}_\hbar
    \right)
    =
    (b+1)J_N(z_1^2z_2^b)
    +\frac{(b+1)b(b-1)}{12}\hbar^2\operatorname{Tr}(Y^{b-2}).
  \]
  Counting PBW matchings in the shear sum and in the Weyl average gives
  \[
    \mathcal N_{\mathrm{free}}(E_{2,b,N})
    =
    \sum_{r=0}^{\lfloor(b-2)/2\rfloor}
      (b-1-2r)
      \left(
        \Theta_r^{(b)}-\Theta_{r+1}^{(b)}
        -\hbar\Phi_r^{(b)}
        +\hbar\Phi_{b-1-r}^{(b)}
      \right).
  \]
  In contraction degree \(0\), this is the discrete boundary coefficient
  of the two-\(X\) cyclic separation.  In contraction degree \(1\), the
  coefficient of \(\Phi_s^{(b)}\) is
  \(-(b+1)+2(s+1)=2s-(b-1)\), the antisymmetric half-sum above.  In
  contraction degree \(2\), the difference between the shear count and
  the first-Moyal Weyl count is exactly
  \[
    \frac{(b+1)b(b-1)}{12}\,
    \mathcal N_{\mathrm{free}}\operatorname{Tr}(Y^{b-2}),
  \]
  which is cancelled by the third Moyal term in the displayed target.
  Combining this target expansion with the column identity proves
  \(\mathcal N_{\mathrm{free}}(E_{2,b,N}-C^{\mathrm{edge}}_{2,b})=0\).

  The \((a,2)\) strip is the same one-moving-letter calculation with
  \(Y\) moving through an \(X\)-string.  For
  \(V_r=X^{a-1-r}YX^r\) one obtains
  \[
    \mathcal N_{\mathrm{free}}\operatorname{Tr}(V_rM)
    =
    \widetilde\Theta_r^{(a)}-\widetilde\Theta_{r+1}^{(a)}
    -\hbar\widetilde\Phi_r^{(a)}
    +\hbar\widetilde\Phi_{a-1-r}^{(a)}.
  \]
  Here
  \[
    \widetilde\Theta_s^{(a)}
      =\mathsf D(X^{a-s}YX^sY),
    \qquad
    \widetilde\Phi_s^{(a)}
      =\mathsf D(X^{a-1-s})\mid\mathsf D(X^sY),
  \]
  with \(\mathsf D(X^0)\) again interpreted as the isolated index loop.
  The first and third Moyal coefficients for
  \(\{z_1^{a+1}/(a+1),z_2^3\}_\hbar\) are
  \[
    3,\qquad \frac{a(a-1)}4,
  \]
  namely \(3/(a+1)\) times the corresponding \((2,a)\) coefficients.
  The same count therefore gives the stated
  \(C^{\mathrm{edge}}_{a,2}\) and proves the second identity.
\end{proof}

\begin{prop}[Free obstruction certificates beyond \((4,4)\)]
\label{prop:app-free-obstruction-certificates}
  In the free indexed normal-diagram algebra,
  \(\mathfrak o_{3,5}=\mathfrak o_{5,3}=0\), and the lexicographic
  cyclic lifts already have zero quantum residual.  Explicitly,
  \[
  \begin{aligned}
    E_{3,5,N}
    &=
      \frac{36}{7}\operatorname{Tr}(XXYYYY\,M)
      +\frac{24}{7}\operatorname{Tr}(XYXYYY\,M)\\
    &\quad
      -\frac{6}{7}\operatorname{Tr}(XYYXYY\,M)
      -\frac{6}{7}\operatorname{Tr}(XYYYXY\,M)\\
    &\quad
      +\frac{30}{7}\operatorname{Tr}(XYYYYX\,M)
      +\frac{12}{7}\operatorname{Tr}(YXYXYY\,M),
  \end{aligned}
  \]
  and
  \[
  \begin{aligned}
    E_{5,3,N}
    &=
      \frac{24}{7}\operatorname{Tr}(XXXXYY\,M)
      -\frac{4}{7}\operatorname{Tr}(XXXYXY\,M)\\
    &\quad
      +\frac{20}{7}\operatorname{Tr}(XXXYYX\,M)
      +\frac{12}{7}\operatorname{Tr}(XXYXXY\,M)\\
    &\quad
      -\frac{8}{7}\operatorname{Tr}(XXYXYX\,M)
      +\frac{16}{7}\operatorname{Tr}(XXYYXX\,M).
  \end{aligned}
  \]
  In total degree \(9\) the same free computation gives
  \(\mathfrak o_{3,6}=\mathfrak o_{6,3}=0\).  The cyclic lifts already
  have zero free residual:
  \[
  \begin{aligned}
    E_{3,6,N}
    &=
      \frac{25}{4}\operatorname{Tr}(XXYYYYY\,M)
      +\frac{19}{4}\operatorname{Tr}(XYXYYYY\,M)\\
    &\quad
      -\frac{3}{4}\operatorname{Tr}(XYYXYYY\,M)
      -\frac{3}{4}\operatorname{Tr}(XYYYXYY\,M)\\
    &\quad
      -\frac{3}{4}\operatorname{Tr}(XYYYYXY\,M)
      +\frac{11}{2}\operatorname{Tr}(XYYYYYX\,M)\\
    &\quad
      +\frac{13}{4}\operatorname{Tr}(YXYXYYY\,M)
      +\frac{1}{4}\operatorname{Tr}(YXYYXYY\,M)\\
    &\quad
      +\frac{7}{4}\operatorname{Tr}(YXYYYXY\,M),
  \end{aligned}
  \]
  and
  \[
  \begin{aligned}
    E_{6,3,N}
    &=
      \frac{25}{7}\operatorname{Tr}(XXXXXYY\,M)
      -\frac{3}{7}\operatorname{Tr}(XXXXYXY\,M)\\
    &\quad
      +\frac{22}{7}\operatorname{Tr}(XXXXYYX\,M)
      -\frac{3}{7}\operatorname{Tr}(XXXYXXY\,M)\\
    &\quad
      -\frac{6}{7}\operatorname{Tr}(XXXYXYX\,M)
      +\frac{19}{7}\operatorname{Tr}(XXXYYXX\,M)\\
    &\quad
      +\frac{16}{7}\operatorname{Tr}(XXYXXXY\,M)
      +\frac{1}{7}\operatorname{Tr}(XXYXXYX\,M)\\
    &\quad
      +\operatorname{Tr}(XXYXYXX\,M).
  \end{aligned}
  \]
  Edge strips are not part of this finite-certificate assertion:
  Proposition~\ref{prop:app-edge-pbw-telescoping} proves
  \(\mathfrak o_{2,b}=\mathfrak o_{a,2}=0\) for all \(a,b\geq2\).
\end{prop}

\begin{proof}
  Apply Theorem~\ref{thm:app-free-indexed-normal-ordering}.  For
  \((3,5)\) and \((5,3)\), the displayed coefficients solve the cyclic
  equation and the free normal-form residual has no terms.  The
  total-degree-\(9\) formulas for \((3,6)\) and \((6,3)\) are checked in
  the same way; their residual also has no terms, so \(K_{3,6}=K_{6,3}=0\)
  in this pivot gauge.  The normal-form script reproduces these
  rational enumerations, and separately regression-checks the edge
  theorem, in the modes
  \[
  \begin{gathered}
    \texttt{--case 3,5 --case 5,3}\quad \texttt{--solve-free},\\
    \texttt{--case 3,6 --case 6,3}\quad
      \texttt{--solve-classical},\\
    \texttt{--case 3,6}\quad \texttt{--kernel-correction},\qquad
    \texttt{--case 6,3}\quad \texttt{--kernel-correction},\\
    \texttt{--case 2,7 --case 7,2}\quad
      \texttt{--kernel-correction}.
  \end{gathered}
  \]
  The calculation is in the free diagram basis; finite-rank trace
  identities are not used.
\end{proof}

\begin{lem}[Cartan one-particle Moyal representation]
\label{lem:app-radial-cartan-moyal-representation}
  Put
  \[
    S_N(f)=\sum_{i=1}^N
      \operatorname{Op}_{\mathrm W}
      (f)(\lambda_i,-\hbar\partial_{\lambda_i}).
  \]
  Then, for all \(f,g\in\C[z_1,z_2][[\hbar]]\),
  \[
    \hbar^{-1}[S_N(f),S_N(g)]=S_N(\{f,g\}_\hbar).
  \]
\end{lem}

\begin{proof}
  The \(i\)-th summand of \(S_N(f)\) lies in the one-particle Weyl
  algebra generated by \(\lambda_i\) and
  \(-\hbar\partial_{\lambda_i}\).  Weyl quantization is an algebra
  isomorphism from the formal Moyal algebra of the constant Poisson
  plane to this one-particle Weyl algebra, so
  \[
    \hbar^{-1}[
      \operatorname{Op}_{\mathrm W}(f)_i,
      \operatorname{Op}_{\mathrm W}(g)_i]
    =
    \operatorname{Op}_{\mathrm W}(\{f,g\}_\hbar)_i .
  \]
  Summands with different \(i\) commute, because they use disjoint
  Cartan variables.  Summing over \(i\) gives the displayed identity.
\end{proof}

\begin{thm}[Finite-\(N\) radial-parts identity from the input package]
\label{thm:app-radial-finite-N}
  Under the radial-parts input of
  Statement~\ref{stmt:app-radial-external-input}, put
  \[
    S_N(f)=\sum_{i=1}^N
      \operatorname{Op}_{\mathrm W}
      (f)(\lambda_i,-\hbar\partial_{\lambda_i}).
  \]
  Then
  \[
    \operatorname{Rad}_0(J_N(f))=\Delta^{-1}S_N(f)\Delta,
  \]
  and for all \(f,g\)
  \[
    D_N(f,g)=
      \hbar^{-1}[J_N(f),J_N(g)]-J_N(\{f,g\}_\hbar)
  \]
  lies in the quantum moment-map ideal.  Equivalently, in the
  Vandermonde gauge,
  \[
    \operatorname{Rad}_0(D_N(f,g))
      =
      \hbar^{-1}[R_N(f),R_N(g)]-R_N(\{f,g\}_\hbar)
      =0 .
  \]
  Thus \(D_N(f,g)\) vanishes in degree-zero quantum Hamiltonian
  reduction.
\end{thm}

\begin{proof}
  The first displayed identity is the exact image normalization included
  in Statement~\ref{stmt:app-radial-external-input}.  The same
  radial-parts input makes the conjugated radial map injective on the
  reduced invariant quotient, so the commutator defect can be tested on
  the Cartan.

  Lemma~\ref{lem:app-radial-nonlinear-shear-obstruction} identifies the
  exact theorem target behind the full displayed formula: classical
  nonlinear shear covariance is not enough to recover mixed Weyl images
  in this convention.  One must instead construct the all-\(N\)
  moment-ideal primitives, equivalently prove
  \(\Omega^{\mathrm{rad}}_{a,b}=0\) or the decorated PBW Stokes identity
  \(D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b}\) in every bidegree.
  A genuine failure is a normalized signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\), not the absence of a finite
  computation.

  Finally
  Lemma~\ref{lem:app-radial-cartan-moyal-representation} gives
  \(\hbar^{-1}[S_N(f),S_N(g)]=S_N(\{f,g\}_\hbar)\).  Equivalently,
  Lemma~\ref{lem:app-radial-dunkl-calogero-cancellation} gives the
  same identity after Vandermonde conjugation:
  \[
    \hbar^{-1}[R_N(f),R_N(g)]=R_N(\{f,g\}_\hbar).
  \]
  Thus \(\operatorname{Rad}_0(D_N(f,g))=0\).  The radial-map
  injectivity of Lemma~\ref{lem:app-radial-map-injectivity} puts
  \(D_N(f,g)\) in the quantum moment-map ideal.
\end{proof}

\begin{defn}[Stable cumulant extraction]
\label{def:app-radial-stable-cumulant-extraction}
  Fix a total polynomial degree bound \(d\) and take \(N\geq d\).  Let
  \[
    \kappa_{N,d}
  \]
  denote the connected single-trace cumulant projection on the stable
  trace algebra in degrees \(\leq d\): it kills the empty trace and
  all decomposable multi-trace products, and it sends the
  Capelli-renormalized generator
  \[
    J_N(z_1^az_2^b),\qquad 0<a+b\leq d,
  \]
  to its single-trace indecomposable class.  The stable map
  \(\kappa_{\infty,d}\) is the stable-tail identification of these
  projections in the Procesi--Razmyslov stable range, after passing
  through the renormalized associated-graded \(J_N\)-basis transition
  system.
\end{defn}

\begin{lem}[Connected-trace projection after Capelli triangularization]
\label{lem:app-radial-connected-projection}
  Fix a polynomial degree bound \(d\).  In the stable range
  \(N\geq d\), the Capelli triangular system
  \[
    J_N(z_1^az_2^b)\equiv
      \sum_{r=0}^{\min(a,b)}
        \left(-\frac{\hbar N}{2}\right)^r
        r!\binom ar\binom br\,T_{a-r,b-r}
  \]
  identifies the span of nonempty Weyl traces \(J_N(z_1^az_2^b)\),
  \(a+b\leq d\), with the span of nonempty normal-ordered traces
  \(T_{a,b}\), modulo the empty trace and decomposable multi-traces.
  The cumulant projection
  \[
    \kappa_{N,d}\bigl(J_N(z_1^az_2^b)\bigr)
      \longmapsto z_1^az_2^b
  \]
  is therefore degreewise injective on the scalar-reduced connected
  single-trace quotient in the stable range.
\end{lem}

\begin{proof}
  The displayed Capelli formula is triangular for total degree:
  its \(r=0\) term is \(T_{a,b}\), and every \(r\geq1\) term has total
  degree \(a+b-2r\).  The diagonal coefficient is \(1\), hence the
  triangular matrix is unipotent and invertible over
  \(\C[[\hbar N]]\).  The only term which can become the empty trace is
  the term with \(a-r=b-r=0\), and the scalar-reduced connected quotient
  removes it.  Decomposable products are removed by the connected
  projection.  Stable Procesi--Razmyslov trace independence in degree
  \(d\) gives linear independence of the remaining connected trace
  generators for \(N\geq d\).  Thus the stated projection is injective
  degreewise in the stable range.
\end{proof}

\begin{thm}[Connected-trace bracket compatibility and stable cumulants]
\label{cor:app-radial-stable-connected}
  Under the same radial-parts input as
  Theorem~\ref{thm:app-radial-finite-N}, for each fixed polynomial
  degree the classes
  \[
    \overline{J_N(f)}
  \]
  have a stable connected large-\(N\) limit after removing the empty
  trace and disconnected products.  This limit is the renormalized
  associated-graded connected transition system, not a naive inverse
  limit of finite-rank normal-ordered trace algebras over
  \(\C[[\hbar]]\).  In that limit,
  \[
    \hbar^{-1}[\partial_{\mathrm{bb},\hbar}(f),
      \partial_{\mathrm{bb},\hbar}(g)]_{\mathrm{conn,raw}}
      =
      \partial_{\mathrm{bb},\hbar}(\{f,g\}_\hbar).
  \]
  More explicitly, for \(N\geq d\) and all \(f,g\) with all monomials
  in \(f,g,\{f,g\}_\hbar\) of total degree \(\leq d\),
  \[
    \kappa_{N,d}\!\left(
      \hbar^{-1}[J_N(f),J_N(g)]
    \right)
    =
    \kappa_{N,d}\!\left(
      J_N(\{f,g\}_\hbar)
    \right),
  \]
  and these identities are compatible under \(N\mapsto N+1\).
\end{thm}

\begin{proof}
  Lemma~\ref{lem:app-radial-connected-projection} gives the
  degreewise stable connected single-trace projection and its
  injectivity after removing the empty trace and decomposable products.
  The finite-\(N\) identity of
  Theorem~\ref{thm:app-radial-finite-N} gives equality in the reduced
  quantum Hamiltonian quotient.  Applying \(\kappa_{N,d}\) gives the
  displayed connected-trace identity, since the cumulant projection
  kills only the empty trace and decomposable products and is injective
  on the Capelli-renormalized single-trace span by
  Lemma~\ref{lem:app-radial-connected-projection}.  The identity is
  compatible with adjoining extra Cartan variables, because
  \(S_{N+k}(f)\) is obtained from \(S_N(f)\) by adding commuting
  one-particle summands.  Therefore the bracket identity stabilizes
  degreewise in \(N\).
\end{proof}

\begin{defn}[Reduced open-line Wick graph data]
\label{def:app-reduced-open-line-wick-graph-data}
  In the reduced first-order open-line model with action
  \[
    S_0=\int_\R\operatorname{Tr}(\phi_1\,d\phi_2),
  \]
  use Weyl-ordered boundary vertices \(f(\phi_1,\phi_2)\), and choose
  the zero-mode-removed midpoint propagator
  \[
    G(t,s)=\frac12\operatorname{sgn}(t-s),\qquad
    \langle\phi_1(t)\phi_2(s)\rangle=\hbar G(t,s),\qquad
    \langle\phi_2(t)\phi_1(s)\rangle=-\hbar G(t,s).
  \]
  Self-contractions at a Weyl vertex are set to zero.  The only
  connected two-vertex graphs are \(r\)-fold cross-contractions between
  the two boundary vertices.
\end{defn}

\begin{thm}[Reduced open-line Wick graph expansion]
\label{thm:app-reduced-open-line-moyal-product}
  With the graph data of
  Definition~\ref{def:app-reduced-open-line-wick-graph-data}, the
  ordered local product for two boundary Hamiltonians at \(t>s\) is
  the formal Moyal product
  \[
    F\star G=m\circ\exp\left(\frac{\hbar}{2}P\right)(F\otimes G).
  \]
  More precisely, the graph with exactly \(r\) cross-edges contributes
  \[
    W_r^{>}(f,g)
      =
    \frac{1}{r!}\left(\frac{\hbar}{2}\right)^rP^r(f,g),
  \]
  while the reversed ordering \(s>t\) contributes
  \[
    W_r^{<}(f,g)
      =
    \frac{1}{r!}\left(-\frac{\hbar}{2}\right)^rP^r(f,g).
  \]
  Hence the antisymmetrized factorization commutator is
  \[
    [f,g]_{\mathrm{graph}}
      =
    \sum_{r\geq0}
      \frac{1-(-1)^r}{2^r r!}\hbar^rP^r(f,g)
      =
    \sum_{\substack{r\geq1\\r\ \mathrm{odd}}}
      \frac{2}{2^r r!}\hbar^rP^r(f,g).
  \]
  The one-edge and three-edge commutator coefficients are exactly
  \[
    \hbar P(f,g),\qquad \frac{\hbar^3}{24}P^3(f,g).
  \]
  All even commutator orders vanish.
\end{thm}

\begin{proof}
  For ordered insertions with \(t>s\), the midpoint propagator gives
  \(G(t,s)=1/2\).  A single cross-contraction therefore contributes
  \[
    \frac{\hbar}{2}
    \left(\partial_{z_1}\otimes\partial_{z_2}
      -\partial_{z_2}\otimes\partial_{z_1}\right)
    =\frac{\hbar}{2}P.
  \]
  Wick expansion of the free first-order model exponentiates the
  cross-contraction operator.  With Weyl vertices there are no
  self-contractions; hence a connected two-vertex graph is determined
  by its number \(r\) of cross-edges.  The exponential supplies the
  symmetry factor \(1/r!\), and the ordered propagator supplies
  \((\hbar/2)^r\).  This proves the formula for \(W_r^{>}\).  Reversing
  the order changes the propagator from \(1/2\) to \(-1/2\), giving
  \(W_r^{<}\).  Subtracting the two orderings gives the displayed
  commutator series.  The coefficients in orders \(1\) and \(3\) are
  \(2/(2\cdot1!)=1\) and \(2/(2^3\cdot3!)=1/24\).
\end{proof}

\begin{cor}[All-order reduced Wick realization of Moyal]
\label{cor:app-reduced-graph-realizes-moyal}
  The reduced open-line Wick graph expansion of
  Theorem~\ref{thm:app-reduced-open-line-moyal-product} realizes the
  Weyl/Moyal Lie bracket of
  Definition~\ref{def:app-radial-moyal-convention} to all orders:
  \[
    [f,g]_{\mathrm{graph}}=[f,g]_{\mathrm{raw}},\qquad
    \hbar^{-1}[f,g]_{\mathrm{graph}}=\{f,g\}_\hbar .
  \]
\end{cor}

\begin{proof}
  Compare the graph commutator series in
  Theorem~\ref{thm:app-reduced-open-line-moyal-product} with the formal
  Weyl commutator series in
  Theorem~\ref{thm:app-radial-moyal-coefficients}.  The coefficient of
  \(P^r\) is \(2\hbar^r/(2^r r!)\) for odd \(r\) and \(0\) for even
  \(r\) in both series.
\end{proof}

\begin{rmk}[Finite exact arithmetic anchors]
\label{rmk:app-radial-finite-verification}
  The script \texttt{scripts/check\_moyal\_coefficients.py} is an
  exact rational-arithmetic falsification harness for the algebraic
  coefficients used above.  It checks:
  \[
  \begin{gathered}
    14641\text{ monomial pairs }(z_1^kz_2^l,z_1^mz_2^n),
      \quad 0\leq k,l,m,n\leq10,\\
    \text{Moyal commutator orders }0\leq r\leq11,\\
    121\text{ Capelli triangular round trips }J\to T\to J
      \text{ with }0\leq a,b\leq10,\\
    80\text{ direct }N=2\text{ radial restrictions and }
      80\text{ direct }N=3\text{ radial restrictions},\\
    [S_2(f),S_2(g)]=S_2([f,g]_{*})
      \text{ on the primary and higher-order Cartan test pairs},\\
    \text{the pre-quotient leading scalar Moyal coefficient,}\\
    \text{its \(U(1)\)-anomaly constant term, and}\\
    \text{the open-line }r=1,3\text{ graph weights.}
  \end{gathered}
  \]
  These checks verify the constants
  \[
    1,\qquad \frac1{24},\qquad
    \frac1{1920},\qquad \frac1{322560}
  \]
  in the tested Moyal orders, the Capelli signs
  \((-\hbar N/2)^r\) and \((+\hbar N/2)^r\), and the rank-two/rank-three
  shadows of the radial image formula.  They do not prove the
  all-\(N\) Harish-Chandra radial-parts theorem or the analytic
  Costello brane-defect graph specialization.

  The script
  \(\texttt{scripts/quantum\_shear\_trace\_diagram\_normal\_form.py}\)
  is separate from the finite-rank harness.  It enumerates the free
  indexed normal diagrams of
  Theorem~\ref{thm:app-free-indexed-normal-ordering}; finite matrices
  are used only in its optional PBW self-test.  Its default run verifies
  the displayed low bidegree primitive candidates, the low edge-family
  regressions for Proposition~\ref{prop:app-edge-pbw-telescoping}, and
  the free \(K_{4,4}\)-corrected residual.  The command with
  \(\texttt{--case 4,4 --classical-only}\) prints the four-term
  residual of Proposition~\ref{prop:app-free-trace-diagram-K44}.  The
  \(\texttt{--solve-free}\) and \(\texttt{--kernel-correction}\) modes
  compute the intermediate kernel-correction class
  \(\mathfrak o_{a,b}\) of
  Definition~\ref{def:app-free-kernel-correction-obstruction}; they
  give the additional finite certificates in
  Proposition~\ref{prop:app-free-obstruction-certificates}, including
  the total-degree-\(9\) cases \((3,6)\) and \((6,3)\).  The current
  exact obstruction theorem is the vanishing of
  \(\Omega^{\mathrm{rad}}_{a,b}\), equivalently the decorated PBW Stokes
  equation \(D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b}\), with
  normalized signed-row failure criterion.  The total-degree \(14\)
  bidegrees \((6,8)\), \((8,6)\), and \((7,7)\) are timeout frontiers
  for the present exact enumeration, not known obstruction rows.  The
  \(\texttt{--edge-family-max}\) mode checks any finite edge window
  against the closed PBW formula, but it is no longer the proof of the
  edge strip.  These computations do not prove the all-bidegree
  decorated PBW Stokes identity.
\end{rmk}

\begin{rmk}[Scalar quotient and the \(U(1)\) anomaly]
\label{rmk:app-radial-scalar-quotient}
  Constants are central in the Moyal Lie algebra and are killed in
  \(\bar A_\hbar\).  Before this scalar reduction the linear
  commutator carries the central term
  \([z_1,z_2]_*= \hbar\), and on the brane side the corresponding
  matrix trace is the Capelli shift \(\hbar N\).  The reduced theorem
  is the theorem after quotienting by this scalar line.
  The unreduced line is the \(U(1)\) anomaly class of
  Theorem~\ref{thm:u1-center-anomaly}.
\end{rmk}

\begin{prop}[Moyal--Capelli normalization and realization boundary]
\label{prop:app-moyal-capelli-realization-boundary}
  The following statements are the exact theorem surface used by the
  degree-zero Moyal sector.
  \begin{enumerate}
    \item The formal Weyl algebra on the constant symplectic plane gives
      the raw commutator coefficients
      \[
        [f,g]_{\mathrm{raw}}^{(2s+1)}
        =
        \frac{\hbar^{2s+1}}{2^{2s}(2s+1)!}P^{2s+1}(f,g),
        \qquad
        [f,g]_{\mathrm{raw}}^{(2s)}=0.
      \]
      In particular the third raw coefficient is
      \(\hbar^3P^3(f,g)/24\).
    \item The finite-rank brane algebra is the degree-zero normalizer
      quotient of the matrix Weyl algebra by the traceless quantum
      moment ideal.  With the normal-ordering convention of
      Definition~\ref{def:app-radial-matrix-weyl}, the contact relation
      is
      \[
        YX-XY+\hbar N I\equiv0
        \pmod{\mathcal W_N\widehat\mu(\lie{sl}_N)}.
      \]
      This scalar Capelli shift is absorbed by the triangular change of
      basis \(T_{a,b}\leftrightarrow J_N(z_1^az_2^b)\), and the remaining
      scalar Hamiltonian line is removed only after passing to
      \(\bar A_\hbar\) and to the empty-trace quotient.
    \item The equality
      \[
        \hbar^{-1}[J_N(f),J_N(g)]
        =
        J_N(\{f,g\}_\hbar)
      \]
      in degree-zero quantum Hamiltonian reduction is proved here
      relative to the radial-parts input of
      Statement~\ref{stmt:app-radial-external-input}.  Without that input,
      the exact algebraic obstruction theorem is
      \[
        \Omega^{\mathrm{rad}}_{a,b}=0
        \quad\Longleftrightarrow\quad
        D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b},
      \]
      with normalized signed-row failure criterion, as in
      Proposition~\ref{prop:app-radial-dual-potential-obstruction}.  The
      moment-ideal primitive
      \(E_{a,b,N}=\sum A^j{}_i(a,b,N)\widehat\mu^i{}_j\) of
      Lemma~\ref{lem:app-quantum-shear-primitive-obstruction} and the
      class \(\mathfrak o_{a,b}\) of
      Definition~\ref{def:app-free-kernel-correction-obstruction} are
      equivalent intermediate forms after choosing a classical lift.
    \item The quantum principal-part target is the continuous
      \(\bar A_\hbar\)-coadjoint module.  It is defined by
      \[
        (\operatorname{ad}^{\vee}_{f,\hbar}\rho)(g)
        =
        -\rho(\{f,g\}_\hbar).
      \]
      For \(f=z_1^pz_2^q\) and the principal-part basis
      \(\rho_{a,b}\), this gives the finite formula
      \[
        z_1^pz_2^q\cdot_\hbar\rho_{a,b}
        =
        -\sum_{\substack{r\geq1\\ r\ \mathrm{odd}}}
        \frac{\hbar^{r-1}}{2^{r-1}r!}\,
        C_r(p,q;a-p+r,b-q+r)\,
        \rho_{a-p+r,b-q+r},
      \]
      where
      \[
        C_r(p,q;m,n)=
        \sum_{\alpha=0}^{r}(-1)^\alpha\binom r\alpha
        (p)_{r-\alpha}(q)_\alpha(m)_\alpha(n)_{r-\alpha},
      \]
      and terms with negative indices or scalar target \((0,0)\) are
      zero.  The \(r=1\) part is the classical Matlis coadjoint action.
      The \(r\ge3\) terms are genuine Moyal corrections and are not the
      polynomial one-\(\psi\) PBW action.
    \item The reduced open-line Wick graph computation realizes the same
      formal Moyal product with midpoint propagator.  It does not prove
      an unreduced Costello graph/QME theorem.  Such a theorem would
      require the brane-defect propagator, counterterms, anomaly
      cancellation, and \(d_{\mathrm{QME}}\)-homotopies in the local BV
      complex; those data are outside the algebraic Weyl/Moyal target.
  \end{enumerate}
\end{prop}

\begin{proof}
  Item (1) is
  Theorem~\ref{thm:app-radial-moyal-coefficients}.  Example
  \ref{ex:app-radial-higher-moyal-check} gives a concrete nontrivial
  check of the coefficients \(1/24\) and \(1/1920\).

  Item (2) is the normal-ordered comoment calculation in
  Definition~\ref{def:app-radial-matrix-weyl} and
  Lemma~\ref{lem:app-radial-capelli-triangular}; the scalar quotient is
  exactly the quotient of
  Definition~\ref{def:app-radial-moyal-convention} and
  Remark~\ref{rmk:app-radial-scalar-quotient}.

  Item (3) is
  Theorem~\ref{thm:app-radial-finite-N}.  The primitive formulation is
  Lemma~\ref{lem:app-quantum-shear-primitive-obstruction}; the exact
  obstruction theorem is
  Proposition~\ref{prop:app-radial-dual-potential-obstruction}, with
  Statement~\ref{stmt:app-free-kernel-homotopy-obstruction} as its
  fixed-lift Hodge form.  The edge
  strip is proved by
  Proposition~\ref{prop:app-edge-pbw-telescoping}.  The finite
  interior certificates in
  Proposition~\ref{prop:app-free-trace-diagram-K44} and
  Proposition~\ref{prop:app-free-obstruction-certificates} do not supply
  the missing all-bidegree decorated PBW Stokes identity.

  Item (4) is the residue-dual definition of the Moyal coadjoint action,
  expanded with the same \(P^r\)-coefficient formula as in item (1).
  Finiteness follows because the falling factorials vanish for
  \(r>p+q\), and the scalar target is removed by the Hamiltonian scalar
  quotient.  Its special fibre is
  Proposition~\ref{prop:principal-part-coadjoint}; the quantum target is
  Construction~\ref{constr:quantum-principal-part-descendant-target}.

  Item (5) is
  Theorem~\ref{thm:app-reduced-open-line-moyal-product} together with
  Corollary~\ref{cor:app-reduced-graph-realizes-moyal}.  The separation
  from the Costello graph/QME realization is part of the hypothesis
  boundary in Theorem~\ref{thm:lane-moyal-degree-zero}.
\end{proof}
