\section*{Claim status and dependencies: coordinate CE/PV and admissible Koszul layers}
\addcontentsline{toc}{section}{Claim status and dependencies: coordinate CE/PV and admissible Koszul layers}

\begingroup
\small
\setlength{\parindent}{0pt}

\noindent\fbox{\begin{minipage}{0.96\textwidth}
\textbf{Formal-local theorem data.}
The formal-local interface is attached to
the shifted cotangent Hamiltonian Lie algebra
\[
  \mathfrak h=\C[[z_1,z_2]]/\C\cdot1,\qquad
  \mathfrak g=\mathfrak h\ltimes
    \mathfrak h^\vee_{\mathrm{cont}}[1].
\]
Its visible interface is stratified by proof strength:
\[
\begin{gathered}
  \text{finite cotangent CE/PV, proved}\\
  \Downarrow\\
  \text{coordinate formal-disk CE/PV, proved as dg algebra}\\
  \Downarrow\\
  \text{bracket-admissible \(P_0\) realizations, proved after \(B\)}\\
  \Downarrow\\
  \text{kernel-admissible MC kernels, proved after datum}\\
  \Downarrow\\
  \text{Tate bar-cobar, relative to the admissible envelope}.
\end{gathered}
\]
The reduced CE/PV central-operation generator map is fixed once and for all:
\[
  c^I\longmapsto\theta^I,\qquad u_I\longmapsto O_I .
\]
The admissible interface datum is
\[
  \mathfrak U_{\mathfrak h}
  =(\Phi_{\mathrm{coord}},\{\Phi^B_{P_0}\}_B,\{\Theta_B\}_B),
\]
where \(B\) ranges over bracket-admissible subalgebras in the second
component and kernel-admissible data in the third.  This is not a
categorical universal object unless a category of admissible completions
and a universal property are supplied.  The theory is
extended by the primitive higher-\(\psi\) extraction, the
\(\mathcal D_\hbar\) Fourier--Rees bridge, the weighted finite-window
regulator, the endpoint criteria, and the unreduced factorization-current
lift datum.

\smallskip
\textbf{Admissibility principle.}
A frontier extension is admissible only when a target theorem supplies
the matched-conventions datum and proves vanishing, with null-homotopies,
of the period, anomaly, QME, convergence, hyperdescent, six-relation,
descent, and operadic obstruction vector.

\smallskip
\textbf{External-comparison quarantine.}
CoHA, compact Calabi--Yau/quintic, OSV/GV, Abel--Jacobi, MNOP,
Igusa/BKM, and global BCOV data are external only.  Without a separate
matched-conventions theorem with comparison maps and vanishing
obstruction vector, they prove none of the local QME, Ext, cyclic,
Weyl/Moyal, radial-parts, or kernel claims; their gaps are external
source obligations, not core proof obligations.
\end{minipage}}

\medskip
\paragraph{Proof route.}
For the proof route read the local theorem dependencies, then the local theorem,
then the obstruction complexes in Section~\ref{sec:open-obligations}.
For theorem names read the status table below together with
Theorem~\ref{thm:witten-centrality-local-form}.  For residual
obligations read the admissible Tate, unreduced factorization-current,
one-antifield, componentwise quantum coefficient, non-scalar QME, and
descent rows.  For cross-volume
uses read only the firewall row: no CoHA, compact Calabi--Yau, quintic,
OSV/GV, Abel--Jacobi, MNOP, Vol III, Igusa/BKM, or global BCOV claim
supports or follows from the local QME, Ext, cyclic, Weyl/Moyal,
radial-parts, or kernel theorem surface without the named
matched-conventions descent theorem.

\medskip
\paragraph{Admissibility stages.}
Stage A0 is the finite cotangent CE/PV identity.  Stage A1 is the
coordinate formal-disk CE/PV identity \(\Phi_{\mathrm{coord}}\), proved
as a completed dg commutative algebra statement.  Stage A2 is a
bracket-admissible \(P_0\)-realization
\(\Phi^B_{P_0}\colon\Phi_{\mathrm{coord}}^{-1}(B)\to B\).  Here
\(B\) is an explicitly topologized complete Hausdorff subalgebra with
continuous inclusion in the coordinate product, continuous
multiplication, continuous \(d_\pi^{\mathrm{coord}}\), and a continuous
closed Schouten contraction bracket whose transport to
\(\Phi_{\mathrm{coord}}^{-1}(B)\) is again continuous.  Boundary
Hamiltonian uses also require \(B\) to contain the relevant \(O_f\)'s and
their forced differentials \(d_\pi^{\mathrm{coord}}O_f\).  Stage A3 is a
kernel-admissible Maurer--Cartan kernel \(\Theta_B\), proved after a
specified completed convolution dg Lie algebra \(\mathcal K_B\) in which
the diagonal sums converge; without that object there is no kernel
theorem.  Stage A4 is an admissible Tate or relative
bar-cobar/Quillen envelope: strict Mittag--Leffler exactness and kernel
existence are constructed in the finite-window habitat, while Quillen
equivalence remains relative to the stated admissible model-envelope
hypotheses.
Stage A5 is the stable scalar-reduced Dirac trace comparison.  Stage A6
splits.  Stage A6a is the componentwise quantum coefficient surface of
Theorem~\ref{thm:quantum-coefficient-surface}: weighted BV kernel
convergence, balanced-supertrace scalar QME cancellation, reduced
weighted Moyal principal-part current brackets, and the
finite-certificate-relative radial/Weyl trace comparison with its
dual-potential obstruction
\(\Omega^{\mathrm{rad}}_{a,b}\), decorated PBW Stokes gate
\(D^\square_{a,b}=C^+_{a,b}\partial_2\), and signed-row failure
criterion.  Stage A6b
has a proved minimal full-equivariant finite-window branch:
Theorem~\ref{thm:app-minimal-full-equivariant-all-order-vanishing}
kills \(R^{\mathrm{ns}}_{n,M}\),
\(\mathfrak o^{\mathrm{ns}}_{n,M}\), and \(C_{n,M}\) for every
\(n\geq1\) only in the named minimal marked habitat.  The larger
non-scalar Costello graph/QME construction problem of
Problem~\ref{prob:quantum-p0-operation-realization} is the exact
obstruction problem obtained before
the scalar-projection lift tower \(o_{\sigma,w}^{(r)}\) vanishes, the
filtered projection \(\widehat\sigma_{\mathrm{sc}}\) is constructed, the
named obstruction class in
\(H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})\) is killed by
compatible counterterms, and a curved bulk-to-defect kernel is built.
Stage A7 is any external matched-conventions descent problem.  Its rows
are quarantine gates, not prerequisites for the core local theorem; they
are not consequences of the local stages.

\paragraph{Koszul comparison layers.}
Layer 0 is the operadic Lie/coComm Koszul input
\(\mathrm{Lie}^{!}\simeq\mathrm{coComm}[-1]\).  Layer 1 is the
Tate CE/bar-cobar identity
\(\Omega C^{\mathrm{CE}}_*(\mathfrak g)\simeq U(\mathfrak g)\) only in an
admissible lower-central Tate-pronilpotent envelope whose strict
Mittag--Leffler exactness has been constructed.  Layer 2 is the
corresponding Tate Quillen equivalence, relative to the transferred
model-envelope hypotheses.  Layer 3 is the coordinate CE/PV reduced \(P_0\)
central-operation theorem with \(c^I\mapsto\theta^I\) and
\(u_I\mapsto O_I\).  Layer 4 is the PBW/Rees special-fibre shadow
\[
  U_\hbar(\mathfrak g)
  =
  T(\mathfrak g)[[\hbar]]/
  \langle xy-(-1)^{|x||y|}yx-\hbar[x,y]\rangle,\qquad
  U_\hbar(\mathfrak g)/(\hbar)\cong
  S(\mathfrak h\oplus\mathfrak h^\vee[1]).
\]
Layer 5 is the Matlis/Grothendieck cotangent module
\[
  \mathfrak h^\vee_{\mathrm{cont}}\cong
  \mathcal P=\bigoplus_{a+b>0}\C\rho_{a,b},\qquad
  z_1^pz_2^q\cdot\rho_{a,b}
  =-(pb-qa+p-q)\rho_{a-p+1,b-q+1}.
\]
Layer 6 is the brane-line factorization-current comparison
\[
  \mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h,\qquad
  u_{a(t)dt\otimes f}\longmapsto B_f(a).
\]
Layer 7 is the stable large-\(N\) bulk-boundary horizon; in this ledger it
is a trace-state construction surface, not evidence for the local
Hamiltonian BF/Moyal core.

\medskip
\paragraph{Status table.}

\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.35\textwidth}
  >{\raggedright\arraybackslash}p{0.18\textwidth}
  >{\raggedright\arraybackslash}p{0.37\textwidth}@{}}
\textbf{Claim surface} & \textbf{Status} & \textbf{Boundary}\\
\hline
Coordinate formal-disk CE/PV theorem & proved as dg coordinate
algebra &
\(\Phi_{\mathrm{coord}}\) is a finite-test/pro-window cochain theorem;
it is not a strict global \(P_0\) theorem\\
Bracket-admissible \(P_0\) realization & proved after \(B\) &
\(\Phi^B_{P_0}\) is asserted only for complete \(B\subset
\mathrm{PV}_{\mathrm{coord}}\) stable under the coordinate differential
\(d_\pi^{\mathrm{coord}}\), closed under
multiplication, and equipped with a continuous closed contraction bracket
whose transported source bracket is closed\\
Kernel-admissible MC kernel & proved after datum &
\(\Theta_B\) is a theorem inside a specified \((B,\mathcal K_B)\) where
the diagonal sums converge; \(\mathfrak o^{\mathrm{Cas}}\) proves that
the strict product/direct-sum endpoint has no such kernel\\
Full \(Z^{P_0}_{\mathrm{fact}}\) of the open BV algebra &
centrality/QME obstruction-vector problem &
construct product and \(P_0\)-centrality homotopies, stratified descent,
and a Costello brane-defect QME kernel; the exact obstruction vector is
\((\operatorname{ob}^{\mathrm{prod}}_{\mathrm{cent}},
\operatorname{ob}^{P_0}_{\mathrm{cent}},
\operatorname{ob}^{\mathrm{bd}}_{\mathrm{QME}},
\delta_{\mathrm{Weiss}}^{\check C/R})\)\\
Full open BV identification & reduced-sector theorem plus unreduced
kernel problem &
only the scalar-reduced connected Hamiltonian sector is used; the
unreduced identification requires the principal-part current lift datum,
coefficient kernel, brane-defect propagator, and compatible centrality
homotopies\\
Admissible formal conilpotent Koszul duality & relative theorem &
strict ML exactness and compatible kernels are constructed; bar-cobar
and module-category equivalences require the named finite-window
model-envelope, conilpotence, PBW, transfer, smallness, and cyclic trace
hypotheses; failure is the vector
\(\mathcal O_{\mathrm{AdmTate}}\) with window, topology, conilpotence,
MC, cobar, PBW, \(P_0\), and cyclic components\\
Matlis cotangent module & proved &
\(\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)\) is a residue-annihilator,
not a naive \(R\)-submodule quotient\\
Radial/Weyl trace comparison & finite certificates plus exact
dual-potential obstruction &
formal Moyal coefficients, reduced open-line Wick weights, Capelli
triangular normalization, free normal ordering, stable trace-diagram
injectivity, and the supplied finite certificates are proved; the
all-bidegree theorem is
\(\Omega^{\mathrm{rad}}_{a,b}=0\), equivalently decorated PBW Stokes
\(D^\square_{a,b}=C^+_{a,b}\partial_2\); failure is exactly a signed row
\((\phi,-\lambda)\in\ker B_{a,b}^*\) with
\(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\)\\
Quantum coefficient surface & proved componentwise &
weighted BV kernel convergence, balanced-supertrace scalar zero,
reduced weighted Moyal principal-part current brackets, and the
finite-certificate-relative degree-zero trace comparison; not a graph/QME
construction\\
Minimal full-equivariant finite-window non-scalar QME branch & proved all
orders in named habitat &
in the minimal marked list generated by strict current-interface rows,
\(\alpha_{\mathrm{sc}}\), and its subset-deletion closure, with no added
positive-order seed, CE-source, graph-counterterm, or nonzero scalar-zero
row, \(R^{\mathrm{ns}}_{n,M}=\mathfrak o^{\mathrm{ns}}_{n,M}=C_{n,M}=0\)
for every \(n\geq1\); this is not a theorem about larger graph packages\\
Larger non-scalar Costello graph/QME construction & obstruction-class
problem &
first kill \(o_{\sigma,w}^{(r)}\), then kill
\([\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]\in
H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})\) and the
finite-window pair \(\mathfrak O_n^{\mathrm{ns}}\); the curved
bulk-to-defect kernel and homotopies are the exact construction target\\
QME cancellation mechanisms & exact scalar alternatives &
unreduced central-character, opposite central-extension, and
balanced-supertrace source/model replacements are proved; ordinary
scalar-reduced \(\mathfrak{gl}_N\) has first obstruction
\(\hbar N[\bar c]\), and a same-branch closed-exchange repair must supply
leading class \(-\hbar N[\bar c]\)\\
External compact-CY/CoHA frontier material & quarantined comparison, no
transfer theorem &
no support for the local QME, Ext, cyclic, Weyl/Moyal, radial-parts, or
kernel claims until
\(\operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}}\) vanishes with
null-homotopies and comparison morphisms; missing fixtures stay external
\end{longtable}

\medskip
\paragraph{Local graph/QME branch statuses.}

\begin{center}
\begin{tabular}{p{0.30\textwidth}p{0.20\textwidth}p{0.40\textwidth}}
\textbf{Branch} & \textbf{Status} & \textbf{Exact boundary}\\
\hline
Balanced scalar-contact projection & proved on named habitats &
\(\widehat\sigma_{\mathrm{bal,sc}}=0\) is a filtered chain map on
balanced scalar-contact habitats and on balanced graph/counterterm
subhabitats; outside these habitats the obstruction is the first
nonzero \(o_{\sigma,w}^{(r)}(I)\)\\
Full-equivariant scalar shadow & proved on finite marked habitats &
codimension-two closed finite-window marked Costello lists and
full-equivariant Brauer marker tensors have zero cyclic-supertrace
shadow for \(V=\C^{N|N}\); missing boundary entries, signs, marker
transports, or closure equations are the obstruction\\
Finite closed graph list & finite-window row-closure datum &
a finite seed set becomes a theorem-grade list exactly after all
field-differential, BV-edge, collision, counterterm, and source faces
close with compatible codimension-two signs and marker transports; until
then the package has no defined non-scalar \(H^1/\varprojlim^1\) class\\
Minimal full-equivariant finite-window array & proved all orders in named
habitat &
the order-\(0\) current row has \(R^{\mathrm{row}}_{0,M}=S_{0,M}=0\);
the full-equivariant one-cross scalar-contact row is zero as a local
functional for \(V=\C^{N|N}\); in the minimal subset-deletion closure
\(R^{\mathrm{ns}}_{n,M}=\mathfrak o^{\mathrm{ns}}_{n,M}=C_{n,M}=0\) for
all \(n\geq1\)\\
Larger finite-window graph packages & row-data obstruction problem &
after any added positive-order seed, CE-source face, graph-counterterm
face, nonzero scalar-zero row, or nonminimal lower counterterm, the
package must supply graph type, labels, marker tensor, incidence signs,
row values, scalar gates, and truncation coefficients before the
\(H^1/\varprojlim^1\) non-scalar class is defined\\
Regular-density curvature certificate & proved under certificate &
for a closed regular-density graph package with zero scalar projection
and compatible regular lower counterterms, the residual lies in
\(\mathcal X^{\mathrm{reg}}\) and
\(\eta^{\mathrm{reg}},\kappa^{\mathrm{reg}},\beta^{\mathrm{cl,reg}},
\mu^{\mathrm{cl}},\lambda^{\mathrm{cl}}\) vanish; absent certificate,
\(\eta^{\mathrm{reg}}_{n_0,M}\) and then
\(\kappa^{\mathrm{reg}}_{n_0}\) decide the branch\\
Wavefront eta branch & obstruction theorem &
non-smooth wavefront labels survive in
\(\mathcal S_c(I)=\mathcal D'_c(I)/\mathcal D^{\mathrm{reg}}_c(I)\);
the obstruction is
\(\eta^{\mathrm{reg}}_{n_0,M}
=[\mathfrak s^{\mathrm{WF}}_{n_0,M}]\), killed only by a degree-zero
distributional primitive in the original quotient complex\\
Radial trace-diagram branch & finite certificates plus exact cokernel
obstruction &
the moment-ideal primitive problem is sharpened to
\(\Omega^{\mathrm{rad}}_{a,b}
=[(T_{a,b},E^+_{a,b})]\in\operatorname{coker}B_{a,b}\);
known finite certificates vanish in the recorded range, while the
all-bidegree theorem is decorated PBW Stokes
\(D^\square_{a,b}=C^+_{a,b}\partial_2\), with failure a signed
\(B^*_{a,b}\)-row\\
\end{tabular}
\end{center}

\medskip
\paragraph{Failed-surface status ledger.}
The following frontier surfaces are not downgraded.  Each is either
proved theorem data already present, a construction target whose missing
datum is named, or an exact obstruction-theorem target.

\begin{enumerate}
  \item \emph{Native \(E_2\) all-window Bochner--Martinelli transfer.}
  Status: construction target.  The native \(\C^2\) factorization object
  plus BMK current-limit data, finite Matlis moment maps, and the
  arity-two output projection \(p_N[ix,iy]\) are proved data.  Strict
  finite-current transfer is obstructed by
  \(\operatorname{Ob}^{\mathrm{BMK\mbox{-}curr}}_N\), with boundary-mode
  obstruction
  \(z_1^{N+2}\cdot\rho_{N+1,0}=-(N+2)\rho_{0,1}\); the projected finite-window
  \(L_\infty\) escape repair has Jacobiator
  \((N+1)(N+2)\rho_{0,1}\).  The positive all-window theorem presently
  available is the one-pair analytic pro-Matlis retract
  \(P_{\Pi}^{\mathrm{an}}=\tau P_{\mathrm{an}}\) with
  \(\pi_NP_{\Pi}^{\mathrm{an}}=p_N\).  The strict native all-window
  current theorem would have to construct cutoff kernels, a direct-sum
  moment map, a compact-current section of the pro-product tower, a full
  formal Hamiltonian action, collar estimates, ternary homotopy, and
  inverse-limit control; failure is the exact obstruction theorem for
  \(\operatorname{Ob}^{\Pi}_{\mathrm{BM}}\).

  \item \emph{\(\C\times\R\), VOA, BRST, and Zhu gates.}
  Status: construction target.  The required interface is
  \[
    \mathfrak I_{\mathrm{ch}}
    =
    (\mathcal R_{\C\times\R},\mathcal F_{\mathrm{red}},
     V_{\mathrm{red}},Q_{\mathrm{BRST}},\mathbf 1,T,Y,
     \operatorname{wt},\zeta_{\hbar},H_{\mathrm{anom}})
  \]
  with a controlled \(\C\times\R\) reduction retaining the \(z_2\)-mode or
  full principal-part coefficient system, together with bracket,
  BV-pairing, brane, product, factorization-to-vertex, Zhu/Moyal, and
  stable Hochschild/HKR/CE-PV comparison and anomaly comparison.  Before
  that construction, any curve VOA or Zhu assertion is false transfer.
  Failure is the exact obstruction vector
  \[
    \operatorname{Ob}_{\mathfrak I_{\mathrm{ch}}}
    =
    (\operatorname{Ob}_{\mathrm{red}},
     \operatorname{Ob}_{\mathrm{vert}},
     \operatorname{Ob}_{\mathrm{Zhu}},
     \operatorname{Ob}_{\mathrm{nat}}).
  \]

  \item \emph{Strict product/direct-sum endpoints and Casimir kernels.}
  Status: exact obstruction-theorem target for the strict endpoint and
  construction target for admissible replacements.  The strict endpoint
  is governed by \(\mathfrak o^{\mathrm{Cas}}\); the stronger positive
  theorem must build a weighted coefficient habitat with convergent
  Casimir, continuous bracket, coevaluation, and bar-cobar compatibility.

  \item \emph{Equivariant CE/PV refined bracket and completion.}
  Status: construction target.  The target is a
  \(T_\Omega\)-graded completed habitat with diagonal kernel,
  \(Q_\Omega=Q+\iota_{V_\Omega}\), \(Q_\Omega^2=L_{V_\Omega}\),
  coefficient ring, continuous bracket, and normalization.  Failure is
  \(\operatorname{ob}_{\Omega,\mathrm{CE/PV}}\).

  \item \emph{Open \(A_\infty\) Koszul and cyclic acceptance.}
  Status: proved cyclic/Koszul trace core plus construction target for
  the admissible open \(A_\infty\) comparison.  The relative theorem
  requires the acceptance datum \(K1\)--\(K11\): finite-window cyclic
  source towers, reduced cyclic chains, the corrected finite-window
  Loday--Quillen--Tsygan single-cycle comparison, an admissible
  filtered open \(A_\infty\)-algebra,
  closed CE/PV target, twisting cochain, completed cobar morphism,
  exact cone/Roos obstruction complex, and cyclicity/BV-pairing
  conventions.  The raw PBW stable trace source does not satisfy this
  theorem: the full cyclic normal-ordering contraction fails, the
  \(\Psi_{a,b}\to\rho_{a,b}\) module bridge is obstructed, the strict
  Casimir endpoint is absent, and the full disk is not made
  lower-central pronilpotent by a naive split.  Failure is the exact
  obstruction tuple
  \[
    \mathcal O_{\mathrm{open}}
    =
    (\mathcal O_{\mathrm{cyc}},
     \mathcal O_{\Psi-\rho},
     \mathcal O_{\mathrm{Cas}},
     \mathcal O_{\mathrm{lc}},
     H^*(\operatorname{Cone}(\operatorname{gr}\kappa_{\tau})),
     \varprojlim\nolimits^1H(\Omega C_{\mathrm{op}}),
     \varprojlim\nolimits^1H(B_{\mathrm{CE/PV}}),
     H^*(\operatorname{Cone}\lambda_{\mathrm{LQT}})).
  \]
  The LQT component is now theorem-grade only on the Koszul-window
  quotient \(A_{\psi,K}=A_\psi/F^{>K}A_\psi\), the CE-length window
  \(\le L\), and on the stable
  single-cycle image
  \(\operatorname{Prim}^{1\mathrm{cyc}}_{N,K,L}
  =\operatorname{im}\Theta_{N,K,L}\),
  with
  \(\lambda_{\mathrm{LQT},K,L}
  =\Theta_{N,K,L}^{-1}P_{1\mathrm{cyc}}\).
  The accepted projection is the stable block-sum Hopf Eulerian
  idempotent
  \[
    P_{1\mathrm{cyc}}
    =
    \log^*(\operatorname{id})
    =
    \sum_{m=1}^{L}\frac{(-1)^{m-1}}{m}
    (\operatorname{id}-u\epsilon)^{*m},
  \]
  in the range \(N\geq\max(K,L+2)\), or \(N\geq W+2\) under one bound;
  in that specialization \(A_{\psi,W}\), \(\Theta_{N,W}\), and
  \(\lambda_{\mathrm{LQT},W}\) abbreviate \(K,L\le W\).
  The same-rank operation that deletes fixed-rank multicycles is false as
  a chain map because
  \(d_{\mathrm{CE}}(\Theta_1(a)\wedge\Theta_1(b))\) has a single-cycle
  commutator term while deletion before \(d_{\mathrm{CE}}\) gives zero.
  The finite-rank bridge uses the normalized signed average
  \(\beta_{M,K,L}\) over injections into the \(L\) labeled diagonal
  blocks and the read-back map \(\alpha_{M,K,L}\), with
  \(\alpha_{M,K,L}\beta_{M,K,L}=\operatorname{id}\); its idempotent is
  \[
    P^{\mathrm{sep}}_{M,K,L}
    =
    \beta_{M,K,L}P_{1\mathrm{cyc}}\alpha_{M,K,L},
    \qquad
    M=L\max(K,L+2),
  \]
  while the same-rank chain-homotopy bridge is blocked by
  \[
    \Gamma_N=d_{\mathrm{same}}F_N-F_Nd_{\oplus}.
  \]
  The unqualified finite-window primitive statement is blocked by
  \[
    \mathcal O_{\mathrm{LQT},K,L}
    =
    (\mathcal O_{\mathrm{win}},
     \mathcal O_{\mathrm{Prim}},
     \mathcal O_{\mathrm{stab}},
     \mathcal O_{\mathrm{scalar}},
     \mathcal O_{\mathrm{CC}},
     \mathcal O_{\mathrm{Roos}}),
  \]
  where \(\mathcal O_{\mathrm{scalar}}\) is the failure of killing
  \(\Theta_1(\psi)\) alone to define a chain quotient:
  \(d_{\mathrm{CE}}\Theta_1(\psi)=\Theta_1(xy-yx)\).

  \item \emph{Full open BV factorization center and unreduced cotangent
  lift.}
  Status: construction target with exact obstruction vector.  The missing
  theorem data are distributional principal-part currents, boundary
  representatives, product and \(P_0\)-centrality homotopies,
  coefficient kernel, brane-defect propagator, and QME solution.
  Failure is
  \((\operatorname{ob}^{\mathrm{prod}}_{\mathrm{cent}},
  \operatorname{ob}^{P_0}_{\mathrm{cent}},
  \operatorname{ob}^{\mathrm{bd}}_{\mathrm{QME}},
  \delta_{\mathrm{Weiss}}^{\check C/R})\), with the last entry the
  Cech-cone/Roos gluing class of the stratified factorization row.

  \item \emph{PBW/Rees source action and polynomial-descendant target.}
  Status: exact obstruction-theorem target for same-action polynomial
  descendants, and construction target for the changed
  principal-part quantum target.  A positive theorem must build the
  homotopical Rees action and naturality; failure is the categorical
  obstruction to a polynomial sub-bimodule with the same Hamiltonian
  action.

  \item \emph{Analytic Costello specialization and first/third graph
  normalization.}
  Status: construction target.  The reduced Wick/Moyal coefficients
  \(1\) and \(1/24\) are proved algebraic data.  The stronger theorem
  must construct the elliptic parent, reduction, propagator, measure,
  counterterms, anomaly cancellation, and graph-normalization rows;
  failure is the local anomaly/normalization obstruction theorem.

  \item \emph{Ordinary scalar-reduced \(\mathfrak{gl}_N\) QME.}
  Status: exact obstruction-theorem target.  The ordinary branch has first
  scalar class \(\hbar N[\bar c]\).  It is repaired only by the proved
  central-character or balanced-supertrace replacements, or by a
  closed-exchange term whose leading class is \(-\hbar N[\bar c]\);
  \(W_{\mathrm{ext}}=0\) or exact leading class leaves the branch
  obstructed.

  \item \emph{Non-scalar Costello/QME beyond the minimal marked branch.}
  Status: construction target with exact obstruction pair.  The minimal
  full-equivariant finite-window branch is proved only in its named
  habitat.  In that habitat the binary centrality row is the zero-row
  theorem
  \(A^M_{\min}:0\to0\), \(r^M_{\min}=0\), \(h^M_{\min}=0\), with zero
  Roos primitive class.  A larger theorem must construct
  \(\widehat\sigma_{\mathrm{sc}}\),
  closed row arrays, residual vectors, boundary matrices, truncation
  identities, and zero Roos class.  For an enlarged binary Costello row
  the local equation is \(A^Mh^M=-r^M\) after the scalar gate, row basis,
  primitive columns, and transition matrices have been supplied.  Failure is
  \((([\mathfrak o^{\mathrm{ns}}_M])_M,\lambda)\), with the
  closed-exchange refinement
  \((\beta^{\mathrm{cl}},\mu^{\mathrm{cl}},\lambda^{\mathrm{cl}})\).

  \item \emph{\(\theta_3\) primitive and companion-face table.}
  Status: exact obstruction-theorem target until one of the accepted
  constructive witnesses is supplied.  The present one-row scalar-zero
  complex has \(K^0=0\), \(K^1=\C\mathsf E_{\theta_3}\), \(d=0\), and
  \(\ell_{\theta_3}(\mathsf E_{\theta_3})=1\).  Thus there is no
  scalar-zero counterterm inside the supplied one-row complex.  In the
  tested two-\(u\), Hamiltonian-degree-\(\le3\) CE source envelope, a
  left-cokernel \(q\) satisfies \(qd_{\mathrm{CE}}=0\) and
  \(q(\zeta_{M,\nu_3})=1\), so no pure CE ancestor exists in that finite
  envelope.  The eight-face companion attempt has nonzero coordinate row
  \((2,-2,3,2,-1,1,-2,-3)\) and its diagonal transport to \(N=2\)
  leaves \(2E_{\nu_{02}}-2E_{\nu_{20}}\).  The canonical lower
  source-coordinate candidate
  \(D^2_{02,20}=K^2_{\Theta_3}
  (u_{a,H_{1,0}}u_{b,H_{0,1}})\) is source-exact because
  \(d_{\mathrm{CE}}(u_{a,H_{1,0}}u_{b,H_{0,1}})
  =2\zeta_{\nu_{02}}-2\zeta_{\nu_{20}}\), but it is not yet
  local-functional-exact.  In the Bianchi-exposed lower basis
  \((E^2_{\nu_{02}},E^2_{\nu_{20}},\mathfrak b^2_{02,20})\),
  \[
    A_D^2=(-2,2,1)^T,\qquad r_2=(2,-2,0)^T,
  \]
  and the cokernel
  \[
    \widetilde\lambda_{02,\mathfrak b}
    =
    \frac12(E^2_{\nu_{02}})^*
    +(\mathfrak b^2_{02,20})^*
  \]
  kills \(A_D^2\) and detects \(r_2\).  A repair must therefore leave
  the obstructed envelope by adding a controlled degree-zero local
  counterterm primitive killing \(\mathfrak b^2_{02,20}\), higher or
  marked CE-source rows, or a complete transport-compatible companion
  table with scalar-zero, signed residual zero, codimension-two closure,
  truncation cocycle, Bianchi transport, and zero Roos class.

  \item \emph{Larger finite-window graph packages and marked scalar
  shadow.}
  Status: construction target.  Scalar-contact and marked-shadow
  vanishing are proved only on named habitats.  Full packages require
  all boundary entries, incidence signs, marker transports, scalar gates,
  row bases, locality data, and truncation matrices; failure is the first
  undefined or nonzero finite-window cokernel row.

  \item \emph{Regular-density and wavefront-current graph branches.}
  Status: theorem-grade on named habitats, with exact wavefront
  obstruction outside them.  The positive branch is the regular-density
  graph calculus on
  \(\mathcal D^{\mathrm{reg}}_c(I)=C_c^\infty(I)dt\), the graphwise tuple
  relation \(\mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)\), and, for ordinary
  collision-conormal kernels, the two maximal sign-conic finite-scaling
  habitats \(\mathcal D'_{c,\Lambda_\pm,\mathrm{fs}}(I)\).  A theorem for
  arbitrary \(\mathcal D'_c(I)\) currents is absent because products of
  pushed-forward currents with Hadamard graph kernels are not canonical
  unless H\"ormander transversality, finite scaling degree, diagonal
  extension, counterterms, and pushforward wavefront bounds are supplied.
  Failure in the singular quotient is the class
  \[
    \eta^{\mathrm{reg}}_{n_0,M}\in
    H^1(\mathfrak Q^\bullet_{w,M}(I)/X^{\mathrm{reg}}_{w,M}(I)),
  \]
  and failure before cohomology is the microlocal
  no-canonical-graph-contraction obstruction for arbitrary
  \(\mathcal D'_c(I)\)-labels.

  \item \emph{Radial all-\(N\) image and signed-row obstruction surface.}
  Status: construction target with exact cokernel obstruction.  The
  finite certificates, edge strips, and free normal forms are proved
  data.  The all-bidegree theorem is the vanishing of
  \[
    \Omega^{\mathrm{rad}}_{a,b}
    =
    [(T_{a,b},E^+_{a,b})]\in\operatorname{coker}B_{a,b},
  \]
  equivalently decorated PBW Stokes
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\).  Failure is a signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) detecting
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\).  The \((7,7)\) row is open
  computation, not a proved nonzero class.

  \item \emph{Normal \(\Omega\) finite-window QME habitat.}
  Status: construction target.  Localization data are not QME data.  The
  positive theorem must build the \(R_\Omega^{N,M}\)-package with normal
  contraction, residue/Euler normalization, equivariant propagator,
  scalar projection, kernel counterterms, zero \(\varprojlim^1H^0\), and
  centrality homotopies.  Failure is the corresponding obstruction-class
  theorem.

  \item \emph{Stratified factorization on \((X,L)\).}
  Status: construction target.  The missing theorem is
  \(\mathcal F^{\mathrm{str}}_{\Omega,N}\) with branch choice, collar
  module, products, descent, centrality homotopies, and QME curvature.
  Failure is the exact obstruction vector
  \(\operatorname{Ob}^{\mathrm{int}}_{\mathrm{str},\Omega,N}\), with the
  source-primary class
  \(\operatorname{ob}^{\mathrm{src}}_{\mathrm{CFG}}\) kept as an external
  matched-conventions gate.

  \item \emph{Protected trace and physical \(\Omega\) large-\(N\) state.}
  Status: construction target.  Algebraic stable trace generators are not
  a protected state.  The theorem must construct \(\omega_{N,\Omega}\),
  topology \(\mathcal T_\Omega\), normalization \(\nu_{\Omega,N}\),
  kernels, counterterms, Ward identities, and large-\(N\) cumulant
  estimates; failure is
  \(\operatorname{Ob}_{\Omega,\mathrm{phys}}\).

  \item \emph{Global Weiss/Ran descent and external comparison firewalls.}
  Status: construction target for descent and matched-conventions
  comparisons, external quarantine otherwise.  The theorem must provide
  period, source comparison, cotangent boundary, \(P_0\)-center
  homotopies, descent data, comparison maps, and vanishing obstruction
  vector.  Failure is the descent or matched-conventions obstruction
  theorem.

  \item \emph{Full Hamiltonian finite-dimensional truncation and Tate
  kernel.}
  Status: construction target with exact Tate/Casimir obstruction.  A
  naive finite-dimensional truncation is not a Lie/BV kernel theorem.
  The positive theorem must build weighted finite-window coefficient
  kernels with coherent heat/gauge fixing, coevaluation, admissible
  weights, and endpoint control; failure is the finite-window/Tate
  Casimir obstruction.
\end{enumerate}

\medskip
\paragraph{Supremum controller classifications.}
The ledger is a theorem controller, not a weakening table.  Every
frontier claim below is admissible only in the strongest true form named
in the right-hand clause.  The controller statuses are:
\emph{proved}, \emph{theorem-surface-with-missing-construction},
\emph{exact obstruction}, \emph{false transfer}, and
\emph{external comparison}.

\begin{enumerate}
  \item \emph{Native holomorphic \(E_2\) / \(\C^2\) factorization.}
  Classification: \emph{proved} for the CE/factorization object and the
  semidirect Hamiltonian--cotangent collision algebra;
  \emph{proved BMK current-limit data, finite Matlis moments, and
  arity-two output projection}; and
  \emph{exact obstruction} for the all-window strict
  Bochner--Martinelli transfer.  The admissible object is
  \[
    \mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}(B)
    =
    C^\bullet_{\mathrm{CE},\mathrm{cont}}
    \bigl(\Omega_c^{0,\bullet}(B)\widehat\otimes
    (\mathfrak h\ltimes\mathcal P[1])\bigr),
  \]
  with \(\mathcal P=\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)\).
  The finite-window output projection \(p_N[ix,iy]\) identifies the
  arity-two operations with the Hamiltonian bracket and the Matlis
  coadjoint action; it is not a proved native finite-window homotopy.
  Strict support-local finite-current transfer is obstructed by
  \(\operatorname{Ob}^{\mathrm{BMK\mbox{-}curr}}_N\), and the projected
  finite-window \(L_\infty\) escape repair has nonzero Jacobiator
  \((N+1)(N+2)\rho_{0,1}\).  The positive all-window theorem currently
  proved is the one-pair analytic pro-Matlis retract.  The stronger
  strict native all-window current theorem is exactly the vanishing, or
  constructive replacement, of
  \[
    \operatorname{Ob}^{\Pi}_{\mathrm{BM}}
    =
    (\operatorname{ob}_{\oplus},
     \operatorname{ob}_{I_\Pi},
     \operatorname{ob}_{\mathfrak h,\Pi},
     \operatorname{ob}_{\mathrm{collar},\Pi},
     \operatorname{ob}_{3,\Pi},
     \operatorname{ob}_{\mathrm{unif},\Pi}),
  \]
  meaning uniform moment restriction to the direct-sum Matlis module,
  a compact-current section of the pro-product tower, a full formal
  Hamiltonian action on the chosen target, collar removal under
  extension-by-zero factorization, vanishing of the first transferred
  ternary obstruction, and uniform estimates in the \(m\)-adic window.
  The first, second, third, and sixth entries are nonzero in the native
  current/product topology; the collar and ternary entries are exact
  primitive construction targets.
  It is not a curve VOA theorem and not a Costello QME theorem.

  \item \emph{Controlled \(\C\times\R\) reduction.}
  Classification: \emph{theorem-surface-with-missing-construction}.
  A curve/topological shadow is admissible only after a reduction datum
  \[
    \mathcal R_{\C\times\R}
    =
    (\pi,\kappa_{\mathrm{top}},\kappa_{\mathrm{hol}},
     B_{z_2},\pi_!,L_{\mathrm{red}},
     \langle-,-\rangle_{\mathrm{red}},
     \{-,-\}_{\mathrm{red}},H_{\mathrm{anom}})
  \]
  is constructed.  Here \(\pi\) fixes the surviving \(t,z_1\)
  directions, \(\kappa_{\mathrm{top}}\) and
  \(\kappa_{\mathrm{hol}}\) are the topological and holomorphic kernels,
  \(B_{z_2}\) records the retained \(z_2\)-mode or principal-part
  coefficient system, \(\pi_!\) is the compact-support or residue
  pushforward, and the remaining entries prove the pushed-forward
  bracket, BV pairing, brane image, and anomaly comparison.  Without
  this datum, importing a \(\C\times\R\) chiral/topological theorem is a
  \emph{false transfer}.

  \item \emph{Reduced Dirac BRST curve algebra and Zhu bridge.}
  Classification: \emph{theorem-surface-with-missing-construction} after
  the controlled reduction, and \emph{false transfer} before it.  The
  strongest admissible theorem must construct a reduced BRST complex
  with \(Q_{\mathrm{BRST}}^2=0\), a one-complex-dimensional
  factorization-to-vertex package
  \[
    (V_L,\mathbf 1_L,T_L,Y_L),
    \qquad
    Y_L(a,w)b=\sum_{n\in\Z}(a_{(n)}b)w^{-n-1},
  \]
  finite singular orders, locality, and a continuous Zhu or zero-mode map
  \[
    \zeta_{L,\hbar}\colon(\bar A_\hbar,*)\to\operatorname{Zhu}(V_L)
  \]
  compatible with
  \([J_{f,(0)},\Theta_\rho]
  =\Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}\).  The existing
  Weyl/Moyal calculation supplies neither \(Y_L\) nor \(\zeta_{L,\hbar}\).
  In this manuscript such a generic \(V_L\) datum is admissible only after
  it factors through \(\mathcal R_{\C\times\R}\) and is identified with
  the retained-mode object \(V_{\mathrm{red}}\).
  Equivalently, an externally constructed chiral algebra enters only as
  \(V_{\mathrm{red}}\) in
  \(\mathfrak I_{\mathrm{ch}}\) after
  \(\mathcal R_{\C\times\R}\) has retained the \(z_2\)-coefficient or
  principal-part system and after
  \[
    \operatorname{Ob}_{\mathfrak I_{\mathrm{ch}}}
    =
    (\operatorname{Ob}_{\mathrm{red}},
     \operatorname{Ob}_{\mathrm{vert}},
     \operatorname{Ob}_{\mathrm{Zhu}},
     \operatorname{Ob}_{\mathrm{nat}})
  \]
  has been killed by the theorem or named as the obstruction-theorem
  target.  Before that reduction datum it is \emph{false transfer}, not
  native \(\C^2\)-factorization data.

  \item \emph{Normal \(\Omega\)-background.}
  Classification: \emph{theorem-surface-with-missing-construction}.
  The native deformation is normal scaling of
  \[
    N_LX=\R_s\oplus\C_{z_1}\oplus\C_{z_2},
    \qquad t\ \text{fixed},
  \]
  with
  \[
    V_\Omega=\epsilon_s s\partial_s+
    \epsilon_1z_1\partial_{z_1}+\epsilon_2z_2\partial_{z_2},
    \qquad
    Q_\Omega=Q+\iota_{V_\Omega},\quad
    Q_\Omega^2=L_{V_\Omega}.
  \]
  The strongest admissible theorem constructs the mixed Cartan model and
  the localized deformation retract
  \[
    \mathsf C_\Omega=(\pi_L,j_L,h_\Omega),\qquad
    Q_\Omega h_\Omega+h_\Omega Q_\Omega=\operatorname{id}-j_L\pi_L
  \]
  over the finite-window localization
  \[
    R_\Omega^{N,M}
    =
    \C[\epsilon_s,\epsilon_1,\epsilon_2,\hbar_\omega]
    [\chi^{-1}\mid\chi\in\mathsf X_{N,M}],
  \]
  where \(\mathsf X_{N,M}\) contains the nonzero moving characters
  \(n\epsilon_s+a\epsilon_1+b\epsilon_2\) and
  \(n\epsilon_s-a\epsilon_1-b\epsilon_2\) that occur in the chosen
  window.  The self-dual specialization is formed before further
  inversion.  The exact residuals are
  \(\operatorname{ob}_{\Omega,\mathrm{Cartan}}\) and
  \(\operatorname{ob}_{\Omega,\mathrm{contr}}\).

  \item \emph{Equivariant CE/PV and refined Hamiltonian bracket.}
  Classification: \emph{proved coordinate formula plus global-completion
  obstruction theorem surface}.
  The self-dual locus \(\epsilon_1+\epsilon_2=0\) has scalar
  Hamiltonian bracket.  Off that locus the Poisson tensor has weight
  \(-(\epsilon_1+\epsilon_2)\), so the scalar bracket exists only after
  adjoining the line parameter
  \[
    [f,g]_\Omega=\hbar_\omega\{f,g\},\qquad
    w(\hbar_\omega)=\epsilon_1+\epsilon_2.
  \]
  The stable coordinate theorem keeps
  \(c_{a,b}\mapsto\theta_{a,b}\) and \(u_{a,b}\mapsto O_{a,b}\), with
  \[
    d_{\mathrm{CE},\Omega}c^K
    =-\frac12\hbar_\omega C^K_{IJ}c^Ic^J,\qquad
    d_{\mathrm{CE},\Omega}u_K
    =\hbar_\omega C^L_{KJ}u_Lc^J,
  \]
  and the matching PV tensor
  \(\pi_\Omega=\frac12\hbar_\omega C^K_{IJ}O_K\theta^I\theta^J\).
  The stronger global theorem is a weighted basic-Cartan
  prefactorization comparison over finite normal windows, with
  bracket-admissible topology, diagonal kernel
  \(\Theta_{\Omega,w,B}\), resonance retention, normalization branch,
  and Weiss/Roos descent.  Its obstruction vector is
  \[
    \operatorname{Ob}^{\mathrm{glob}}_{\Omega,\mathrm{CE/PV}}
    =
    (\operatorname{ob}_{\Omega,\mathrm{Cartan}},
     \operatorname{ob}_{\Omega,\mathrm{top}},
     \operatorname{ob}_{\Omega,\mathrm{br}},
     \operatorname{ob}_{\Omega,\mathrm{diag}},
     \operatorname{ob}_{\Omega,\mathrm{res}},
     \operatorname{ob}_{\Omega,\mathrm{norm}},
     \operatorname{ob}_{\Omega,\mathrm{fact}},
     \operatorname{ob}_{\Omega,\mathrm{Roos}},
     \operatorname{ob}_{\Omega,\mathrm{QME}}).
  \]

  \item \emph{Omega quantum parameters.}
  Classification: \emph{notation gate, not a QME theorem}.  The ledger
  distinguishes
  \[
    \hbar_{\mathrm{QME}},\qquad
    \hbar_{\mathrm{W}},\qquad
    \hbar_\omega .
  \]
  The first is the Costello/BV graph loop parameter, the second is the
  Weyl/Moyal deformation parameter, and the third is the equivariant line
  parameter with \(w(\hbar_\omega)=\epsilon_1+\epsilon_2\).  A Weyl branch
  may set \(\hbar_{\mathrm{W}}=\hbar_\omega\); no branch sets
  \(\hbar_{\mathrm{QME}}\) equal to either parameter without an explicit
  convention and a separate QME obstruction calculation.

  \item \emph{Stratified factorization on \((X,L)\).}
  Classification: \emph{theorem-surface-with-missing-construction}.
  The stronger theorem is a functor
  \[
    \mathcal F^{\mathrm{str}}_{\Omega,N}\colon
    \operatorname{Disk}^{\mathrm{str}}_{X,L}
    \to
    \operatorname{Ch}_{R_\Omega^{N,M}[[\hbar_{\mathrm{QME}}]]}
  \]
  with bulk values, brane values
  \(A^q_{N,\Omega}\) over the Weyl parameter \(\hbar_{\mathrm{W}}\) or
  \(A^{\mathrm{pp},w}_{\partial,\Omega,\hbar_{\mathrm{W}}}\), a collar module
  \(\mathcal M_{\Omega,N}\), products \(\mu_{\mathrm{str}}\), and
  stratified Weiss descent.  Its exact internal obstruction vector is
  \[
    \operatorname{Ob}^{\mathrm{int}}_{\mathrm{str},\Omega,N}
    =
    (\delta_{\mathrm{pref}},
     \delta_{\mathrm{assoc}},
     \delta_{\mathrm{Weiss}}^{\check C/R},
     \operatorname{ob}_{\mathrm{collar}},
     \operatorname{ob}^{\mathrm{prod}}_{\mathrm{cent}},
     \operatorname{ob}^{P_0}_{\mathrm{cent}},
     \operatorname{ob}^{\mathrm{bd}}_{\mathrm{QME}},
     \operatorname{ob}_{\Omega\mathrm{-basic}},
     \operatorname{ob}_{\mathrm{tr}\mathrm{-top}}).
  \]
  where
  \[
    \delta_{\mathrm{Weiss}}^{\check C/R}
    =
    \left(
      \{H^\bullet(\Delta^{N,M}_{V,\mathcal U})\}_{V,\mathcal U,N,M},
      \mathfrak w^{\check C/R}_{V,\Omega,N,M}
    \right).
  \]
  The source-primary class
  \(\operatorname{ob}^{\mathrm{src}}_{\mathrm{CFG}}\) is external to this
  internal vector.  The Weiss component is not a holim slogan: for a
  collared stratified Weiss cover \(\mathcal U\) it is the cone
  \[
    \Delta^{N,M}_{V,\mathcal U}
    =
    \operatorname{Cone}\left(
      \mathcal F^{\mathrm{str}}_{\Omega,N,M}(V)
      \to
      \operatorname{Tot}\check C^\bullet
      (\mathcal U;\mathcal F^{\mathrm{str}}_{\Omega,N,M})
    \right),
  \]
  together with the Roos compatibility class
  \(\mathfrak w^{\check C/R}_{V,\Omega,N,M}\) for refinements, windows,
  interval inclusions, and weight transports.

  \item \emph{Protected stratified trace.}
  Classification: \emph{theorem-surface-with-missing-construction}.
  The algebraic stable trace theorem supplies candidate generators only.
  A protected trace requires a continuous state
  \[
    \omega_{N,\Omega}\colon
    \int_{L\subset X}\mathcal F^{\mathrm{str}}_{\Omega,N}
    \to
    R_\Omega^{N,M}[[\hbar_{\mathrm{QME}}]]
  \]
  together with normalization \(\nu_{\Omega,N}\), topology
  \(\mathcal T_\Omega\), brane-defect kernel and counterterms, product
  and \(P_0\)-centrality homotopies, and Ward identities for
  \(d_{\mathrm{QME}}\), \(Q_\Omega\), the moment map, and the brane
  curvature.  The residue branch has
  \(\nu_\Omega^{\mathrm{res}}=1\).  The Euler branch has
  \[
    \nu_\Omega^{\mathrm{Eu}}
    =
    \sigma_s(\epsilon_s\epsilon_1\epsilon_2)^{-1}.
  \]
  These are separate branches until a comparison theorem fixes the sign
  and factor.

  \item \emph{Costello graph/QME brane-defect package.}
  Classification: \emph{exact obstruction}.  The normal
  \(\Omega\)-background and the componentwise quantum coefficient surface
  do not construct the Costello propagator, counterterms, or
  brane-defect QME kernel.  The admissible theorem must produce
  \(K_{\Omega,N}\) with
  \[
    \operatorname{Curv}(K_{\Omega,N})
    =
    d_{\mathrm{QME}}K_{\Omega,N}
    +\frac12[K_{\Omega,N},K_{\Omega,N}]_{\hbar_{\mathrm{QME}}}=0,
  \]
  after the scalar projection tower \(o_{\sigma,w}^{(r)}\), the
  non-scalar class in
  \(H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})\), and the
  finite-window pairs \(\mathfrak O_n^{\mathrm{ns}}\) are killed by
  compatible counterterms and centrality homotopies.
  The certified \(\theta_3\) row is the model case for this rule:
  in the supplied one-row scalar-zero complex
  \[
    \mathcal Q^0_{\theta_3,M}=0,\qquad
    \mathcal Q^1_{\theta_3,M}=\C\mathsf E_{\theta_3,M},\qquad d_M=0,
  \]
  the functional \(\ell_{\theta_3}(\mathsf E_{\theta_3,M})=1\)
  proves a nonzero finite-row class.  The admissible upgrade is not to
  soften the non-scalar QME theorem, but to add one of the missing
  constructive witnesses:
  a CE ancestor \(\eta_{\theta_3,M}\) with
  \(d_{\mathrm{CE}}\eta_{\theta_3,M}=\zeta_{M,\nu_3}\) and
  \(d_MK^M_{\Theta_3}(\eta_{\theta_3,M})=-\mathsf E_{\theta_3,M}\);
  a scalar-zero Costello local counterterm
  \(C^{\mathrm{ct}}_{\theta_3,M}\) with
  \(d_MC^{\mathrm{ct}}_{\theta_3,M}=-\mathsf E_{\theta_3,M}\);
  or a complete companion-face table changing the row residual to zero.
  The lower source-coordinate candidate
  \(D^2_{02,20}=K^2_{\Theta_3}(\zeta^0_2)\) adds only source exactness
  until the Bianchi defect
  \[
    \mathfrak b^2_{02,20}
    =
    d_{\mathrm{ns},2}K^2_{\Theta_3}(\zeta^0_2)
    -
    K^2_{\Theta_3}(d_{\mathrm{CE}}\zeta^0_2)
  \]
  is killed.  In the exposed lower basis the obstruction is
  \(A_D^2=(-2,2,1)^T\), \(r_2=(2,-2,0)^T\), detected by
  \(\widetilde\lambda_{02,\mathfrak b}
  =\frac12(E^2_{\nu_{02}})^*
  +(\mathfrak b^2_{02,20})^*\).  The current habitat contains no
  \(B^2_{02,20}\) counterterm: the target
  \((0,0,-1)^T=-\mathfrak b^2_{02,20}\) is outside the image of
  \(A_D^2\), detected by
  \(\widetilde\lambda_{02,\mathfrak b}((0,0,-1)^T)=-1\).  The exact next
  target is a scalar-zero local-functional column
  \(A_B^2=(0,0,-1)^T\) with locality or wavefront admissibility and
  finite-window transport.  In a tower the named transport cocycle is
  \[
    \Delta^1_{M,N}
    =
    -\pi_{M,N}\mathfrak b^M+\mathfrak b^N,
  \]
  and a compatible family \(B^M\) kills it only when
  \[
    \Delta^1_{M,N}
    =
    d_{\mathrm{ns},N}(\pi_{M,N}B^M-B^N).
  \]
  These witnesses must therefore kill both the \(H^1\) class of
  \(\Delta^1_{M,N}\) and the secondary \(\varprojlim^1H^0\)
  primitive-compatibility class.  A named \(C_{\theta_3}\) without one of
  these differentials is not evidence.

  \item \emph{Radial/Weyl finite certificates and decorated Stokes gate.}
  Classification: \emph{proved finite certificates plus exact
  dual-potential obstruction theorem}.  The radial comparison is no longer a
  bare external input in the ledger.  The proved algebraic surface
  consists of the formal Weyl/Moyal coefficients, the reduced open-line
  Wick weights, the Capelli triangular normalization, the free indexed
  normal-ordering formula, stable trace-diagram injectivity, the all-\(N\)
  correction \(K_{4,4}\), and the finite certificate range recorded in
  Section~\ref{sec:open-obligations}.  For every bidegree put
  \[
    R^{\mathrm{free}}_{a,b}
    =
    \mathcal N_{\mathrm{free}}(E_{a,b,N})
    -
    \mathcal N_{\mathrm{free}}
    \left(\sum_W c^{\mathrm{cl}}_W\operatorname{Tr}(WM)\right),
  \]
  and
  \[
    \mathfrak o^{\mathrm{rad}}_{a,b}
    =
    [R^{\mathrm{free}}_{a,b}]
    \in
    \operatorname{coker}
    \left(
      \mathcal C_{a,b}\colon
      \ker\partial\to\mathsf{Diag}_{a,b}
    \right).
  \]
  A kernel splitting of \(\mathcal C_{a,b}\) is one presentation of the
  same problem, but the controlling theorem surface is the sharper
  dual-potential formulation.  With
  \(B_{a,b}(W)=(\partial W,C^+_{a,b}(W))\) and
  \(\eta_{a,b}=(T_{a,b},E^+_{a,b})\), this is
  \[
    \Omega^{\mathrm{rad}}_{a,b}
      =
    [\eta_{a,b}]\in\operatorname{coker}B_{a,b}.
  \]
  Failure is exactly a signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\).  The ordinary square-cell
  necklace cycle mechanism is proved; the current missing theorem is the
  decorated PBW Stokes identity for
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\).  The first unclosed
  certificate targets \((6,8)\), \((8,6)\), and \((7,7)\) are exact-basis
  frontier computations in the present solver, not nonzero obstruction
  rows.

  \item \emph{Physical \(\Omega\)-large-\(N\) trace-state theorem.}
  Classification: \emph{theorem-surface-with-missing-construction};
  external physical or factorization-homology analogies are
  \emph{external comparison} until matched to this local pair.  The
  strongest admissible theorem fixes the state and topology, defines
  connected cumulants by
  \[
    \langle F_1,\ldots,F_k\rangle^c_{N,\Omega}
    =
    [t_1\cdots t_k]\log\omega_{N,\Omega}
    \left(\exp\Bigl(\sum_i t_iF_i\Bigr)\right),
  \]
  and proves, in \(\mathcal T_\Omega\),
  \[
    \langle F_1,\ldots,F_k\rangle^c_{N,\Omega}
    \sim
    \sum_{g\ge0}N^{2-2g-k}
    F^\Omega_{g;k}(F_1,\ldots,F_k)
  \]
  with the chosen \(\hbar,N\)-scaling and Ward identities.  Degreewise
  stable invariant theory is not this theorem.
\end{enumerate}

\medskip
\paragraph{Theorem data.}

\begin{enumerate}
  \item \emph{Stage A0: finite cotangent CE/PV.}
  For each finite-dimensional Lie algebra \(\mathfrak l\),
  \[
    \Phi_{\mathfrak l}\colon
    C^\bullet_{\mathrm{CE}}
      (\mathfrak l\ltimes \mathfrak l^\vee[1])
    \xrightarrow{\sim}
    \mathrm{PV}(\mathbf S(\mathfrak l))
  \]
  with \(c\mapsto\theta\), \(u\mapsto O\).  The formal-disk coordinate
  comparison is reconstructed from admissible finite coordinate tests and
  pro-window coordinate cochains.  It becomes a completed bracketed
  statement only in a mixed or weighted topology where the contraction
  bracket is continuous.  The strict ambient product/direct-sum
  completion is obstructed by the infinite diagonal.

  \item \emph{Stage A1: coordinate formal disk CE/PV.}
  The completed formal-disk comparison is first a coordinate dg algebra
  isomorphism
  \[
    \Phi_{\mathrm{coord}}\colon
    C^\bullet_{\mathrm{CE},\mathrm{coord}}(\mathfrak g)
    \longrightarrow
    \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}}).
  \]
  It becomes a \(P_0\) comparison only after choosing a
  bracket-admissible subalgebra \(B\).  If \(B\) is kernel-admissible, the
  diagonal kernel \(\Theta_B\) is an additional theorem datum whose
  existence is exactly the convergence of the two diagonal sums in the
  chosen convolution habitat.
  Its coordinate transition obstruction terms are
  \[
    \mathfrak o^{\mathrm{br}}_{M,N},\qquad
    \mathfrak o^{\mathrm{coad}}_{M,N}.
	  \]
	  The separate strict-kernel and ambient-product bracket obstruction is
	  \(\mathfrak o^{\mathrm{Cas}}_{M,N}\).

  \item \emph{Stage A2: bracket-admissible \(P_0\) realization.}
  A bracket-admissible \(B\subset
  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) is complete,
  stable under \(d_\pi^{\mathrm{coord}}\), closed under multiplication, and closed under a
  continuous Schouten contraction bracket.  Its source
  \(\Phi_{\mathrm{coord}}^{-1}(B)\) must be closed under the transported
  bracket.  Under these hypotheses
  \[
    \Phi^B_{P_0}\colon\Phi_{\mathrm{coord}}^{-1}(B)
    \xrightarrow{\sim}B
  \]
  is the completed dg \(P_0\)-comparison.

  \item \emph{Stage A3: kernel-admissible Maurer--Cartan tensor.}
  A bracket-admissible \(B\) is kernel-admissible when the diagonal sums
  \[
    \Theta_B=\sum_I H_I\otimes\theta^I+\sum_I\eta^I\otimes O_I
  \]
  converge in the completed tensor product attached to \(B\).  Then
  \(\Theta_B\) is the corresponding Maurer--Cartan tensor, checked
  coefficientwise from the Jacobi and coadjoint identities in that
  completed convolution dg Lie algebra:
  \[
    d\Theta_B+\frac12[\Theta_B,\Theta_B]=0.
  \]
  The strict product/direct-sum endpoint has no such kernel:
  \(\mathfrak o^{\mathrm{Cas}}\) is the obstruction.  The weighted and
  strict ML habitats supply replacement coefficient categories; they are
  regulators, not universal endpoints for all tail-sensitive cohomology.

	  \item \emph{Stage A4: admissible Tate bar-cobar/Quillen envelope.}
  For an admissible Tate replacement
  \(\mathfrak g_{\mathrm{adm}}\),
  \[
    B_{\mathrm{adm}}=
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{adm}}),
    \qquad
    B_{\mathrm{adm}}^!\simeq
    \widehat U(\mathfrak g_{\mathrm{adm}}).
  \]
  The strict finite-window Mittag--Leffler habitat constructs exact
  inverse limits, \(\varprojlim^1=0\), paired-window tensor products,
  continuous duals, and compatible kernels.  The bar-cobar/Quillen
  theorem is then relative to an admissible model envelope: conilpotent
  CE coalgebra, PBW completeness, completed symmetric associated
  graded, transfer and smallness, and an admissible transferred
  \(P_0\)-algebra model structure.

  \item \emph{Reduced CE/PV central-operation generator map.}
  The Hamiltonian CE ghost \(c^I\) becomes the Schouten vector
  \(\theta^I\).  The shifted-cotangent CE coordinate \(u_I\) becomes the
  Hamiltonian boundary coordinate \(O_I\).  Boundary Hamiltonian
  observables come from \(u_I\).

  \item \emph{Dirac open Koszul model.}
  The brane stack is the derived commuting-pair locus:
  \[
    S_\partial=\int_\R\operatorname{Tr}
    (\phi_1\,d\phi_2+A[\phi_1,\phi_2]),\qquad
    Q\psi=[\phi_1,\phi_2].
  \]
  The displayed action is in the Dirac-normalized variables obtained from
  the raw shifted-Chern--Simons coefficient fields; the Koszul complex is
  the derived zero fibre of the commuting-pair equation, not an assertion
  that the finite-\(N\) moment-map components form a regular sequence.
  Stable trace invariants are taken degreewise; for total word degree
  \(d\), the stable range is \(N\ge d\).

  \item \emph{Primitive higher-\(\psi\) extraction.}
  The primitive Koszul complex has nonconstant Hamiltonian \(H_0\)
  classes and positive Hamiltonian one-\(\psi\) primitive \(H_1\)
  classes \(\Psi_{a,b}\) with \(a+b>0\).  The scalar
  \(\Psi_{0,0}=\operatorname{Tr}(\psi)\) is the removed odd scalar line,
  not a Matlis principal-part class.  The higher primitive sectors
  satisfy \(H_p=0\) for \(p\ge2\) in the stable finite-bidegree cyclic
  word model.  The
  one-\(\psi\) action is
  \[
    \{\overline{\operatorname{Tr}(\phi_1^p\phi_2^q)},
      \widetilde\Psi_{a,b}\}
    =(pb-qa)\widetilde\Psi_{a+p-1,b+q-1}.
  \]

  \item \emph{Matlis cotangent module.}
  The cotangent coefficient module is
  \[
    \mathcal P=
    \operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
    \subset H^2_{\mathfrak m}(R)\,dz_1dz_2,
    \qquad
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}dz_1dz_2 .
  \]
  Its coadjoint action is
  \[
    z_1^pz_2^q\cdot\rho_{a,b}
    =-(pb-qa+p-q)\rho_{a-p+1,b-q+1}.
  \]

  \item \emph{Polynomial-descendant obstruction.}
  Polynomial one-\(\psi\) representatives have locally nilpotent linear
  Hamiltonian action, while
  \[
    z_1\cdot\rho_{a,b}=-(b+1)\rho_{a,b+1},\qquad
    z_2\cdot\rho_{a,b}=(a+1)\rho_{a+1,b}
  \]
  is not locally nilpotent on principal parts.  Any polynomial
  realization of \(\mathcal P\) must therefore change the target, the
  action, or the category.

  \item \emph{\(\mathcal D_\hbar\) Fourier--Rees bridge.}
  With
  \[
    \mathcal D_\hbar=
    \C[[\hbar]]\langle z_i,\partial_i\rangle/
    ([\partial_i,z_j]=\hbar\delta_{ij}),
  \]
  the Fourier delta lattice gives
  \[
    z_1^az_2^b\mapsto\partial_1^a\partial_2^be_0
    \mapsto(-1)^{a+b}\hbar^{a+b}a!b!\rho_{a,b}.
  \]
  Before inverting \(\hbar\) the image is the Rees sublattice
  \(\bigoplus\hbar^{a+b}\C[[\hbar]]\rho_{a,b}\).  The bridge changes
  polarization; same-action Rees families from \(\Psi_{a,b}\) to
  \(\rho_{a,b}\) are obstructed.

  \item \emph{Quantum Hamiltonian and Moyal sector.}
  The Weyl convention is
  \[
    f*g=m\exp\!\left(\frac{\hbar}{2}P\right)(f\otimes g),
    \qquad
    \{f,g\}_\hbar=\hbar^{-1}[f,g]_* .
  \]
  The first and third raw commutator coefficients are \(1\) and
  \(1/24\).  These formal coefficients, the reduced open-line Wick
  midpoint weights, the Capelli triangular normalization, and the free
  trace-diagram normal-ordering formula are proved.  The all-\(N\)
  ordinary Weyl-trace comparison is controlled by the quantum shear
  congruence of
  Proposition~\ref{prop:app-quantum-shear-suffices-radial-image}.  In
  the matrix Weyl algebra this is first the explicit moment-ideal
  primitive problem of
  Lemma~\ref{lem:app-quantum-shear-primitive-obstruction}: construct
  \(A^j{}_i(a,b,N)\) with
  \(E_{a,b,N}=\sum_{i,j}A^j{}_i(a,b,N)\widehat\mu^i{}_j\).  The sharper
  free-diagram form is the dual-potential obstruction theorem
  \[
    \Omega^{\mathrm{rad}}_{a,b}
    =
    [(T_{a,b},E^+_{a,b})]\in\operatorname{coker}B_{a,b},
  \]
  equivalently the decorated PBW Stokes identity
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\); failure is a signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\).  Finite certificates prove
  vanishing in the recorded windows and exhibit the nontrivial
  correction \(K_{4,4}\).  The descendant sector is
  governed by the principal-part Moyal target and the
  no-\(\hbar\)-adic same-action intertwiner.

  \item \emph{Componentwise quantum coefficient surface.}
  The proved quantum surface is
  \[
    \mathfrak S_{\hbar,w}(I)
      =
      \mathcal K_{\mathrm{BV}}^w
      \times\{0_{\mathrm{sc}}\}
      \times A^{\mathrm{pp},w}_{\partial,\hbar}(I)
      \times T_{\mathrm{Ham},\hbar}.
  \]
  The first factor records weighted coefficient-kernel convergence and
  graphwise weighted boundedness.  The second records the balanced
  \(\mathfrak{gl}(N|N)\) supertrace scalar QME cancellation.  The third
  is the reduced weighted Moyal principal-part current target, with
  coadjoint action \(\operatorname{ad}^{\vee}_{f,\hbar}\) rather than the
  polynomial one-\(\psi\) PBW action.  The fourth is the degree-zero
  Hamiltonian trace comparison, relative to the finite-certificate
  radial/Weyl gate: the obstruction is
  \(\Omega^{\mathrm{rad}}_{a,b}\), equivalently decorated PBW Stokes
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\), with failure certified by a
  signed \(B_{a,b}^*\)-row.  This is a
  genuine theorem surface, not the non-scalar
  Costello graph/QME construction.

  The next theorem obligation first asks for the scalar-projection lift:
  for a complete \(d_{\mathrm{QME}}\)-stable scalar-contact filtration,
  the successive classes
  \[
    o_{\sigma,w}^{(r)}(I)\in
    H^1\!\left(
      \operatorname{Hom}\bigl(
        \operatorname{gr}_{F}
        \mathfrak Q^\bullet_{w,\partial,\hbar}(I),
        C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]]
      \bigr)_{-r}
    \right)
  \]
  must vanish.  In the ordinary scalar-reduced
  \(\mathfrak{gl}_N\) branch the first class evaluates on
  \(z_1,z_2\) as \(\hbar N\gamma_{\mathbf 1}\), so no filtered scalar
  projection exists without an external leading class
  \(-\hbar N[\bar c]\) or a source/model replacement.  The balanced
  supertrace branch has proved zero filtered projections on the balanced
  scalar-contact habitat, on balanced graph/counterterm subhabitats, and
  on codimension-two closed full-equivariant marked finite-window
  habitats.  For any larger graph/counterterm habitat not shown to lie in
  one of these classes, the scalar-contact extension remains the
  obstruction tower \(o_{\sigma,w}^{(r)}(I)\).  Only after
  the scalar lift is built does the next obstruction become the
  vanishing of
  \[
    [\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]
      \in
      H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})
  \]
  inside the filtered complex
  \(\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\) of
  Problem~\ref{prob:quantum-p0-operation-realization}.  Concretely, one
  must construct finite-window local counterterms whose obstruction pair
  \[
    \mathfrak O_n^{\mathrm{ns}}
      =
      \bigl(([\mathfrak o^{\mathrm{ns}}_{n,M}])_M,\lambda_n\bigr)
  \]
  vanishes at every \(\hbar\)-order, build the curved bulk-to-defect
  kernel, and prove that the non-scalar class vanishes with compatible
  centrality homotopies.  The minimal full-equivariant finite-window
  branch is already closed by
  Theorem~\ref{thm:app-minimal-full-equivariant-all-order-vanishing}: its
  positive-order row sums, non-scalar classes, and counterterms are all
  zero in the named minimal marked habitat.  This closure does not supply
  the row data or curved kernel for any larger graph package.

  \item \emph{Weighted finite-window regulator.}
  Admissible weights \(w,w'\) are related by diagonal finite-window
  transport \(R_{w,w'}^{w_0}\).  The regulator theorem identifies the
  Mittag-Leffler local-functional complexes and carries
  \(\mathrm{Ob}_w\) to \(\mathrm{Ob}_{w'}\).  Vanishing of the mixed
  brane-defect QME class is independent of the admissible weight.  Weight
  transport preserves the non-scalar obstruction pair
  \(\mathfrak O_n^{\mathrm{ns}}\); it does not kill a nonzero class.

  \item \emph{Endpoint criteria.}
  An endpoint for \(w_q(d)=q^d\) is admissible when conditions
  (E1)--(E5) hold.  The obstruction tuple is
  \[
    \mathfrak o_{\mathrm{BV,end}}=
    (\mathfrak o_{\mathrm{Cas}},
     \mathfrak o_{\mathrm{def}},
     \mathfrak o_{\mathrm{RG}},
     \mathfrak o_{\mathrm{QME}}).
  \]
  The strict product/direct-sum endpoint fails because no tensor
  projects to all finite-window Casimirs \(C_{\mathfrak h}^{w_0}\).

  \item \emph{Unreduced factorization-current lift.}
  Distributional principal-part currents give the target for cotangent
  boundary modes.  The lift datum consists of boundary representatives,
  product centrality homotopies, \(P_0\)-bracket homotopies, the
  coefficient kernel, the brane-defect propagator, and the QME solution.
  The scalar component is
  \[
    \operatorname{Ob}_{\mathrm{sc}}
    =\hbar N\,\omega(f,g)
      \int_\R a(t)b(t)\gamma_{\mathbf 1}(t)\,dt ,
	  \]
	  with associated graded formal class
	  \(\hbar N[\bar c]\in H^2_{\mathrm{Lie}}(\bar A;\C)[[\hbar]]\).
	  In the original scalar-reduced ordinary \(\mathfrak{gl}_N\) model,
	  the first scalar-lift obstruction is this class, detected already on
	  the linear Hamiltonian window.  Closed-exchange data can repair that
	  branch only if its leading scalar class is
	  \(-\hbar N[\bar c]\).  The minimal algebraic defect-supported
	  central-contact cone with generator \(e_M\),
	  \(\Xi_M(e_M)=-\hbar N\bar c_M\), \(W_M=e_M\), and \(C_M=0\)
	  kills the finite-window scalar classes only as a changed algebraic
	  source branch; it is not yet a Costello-local closed-exchange
	  realization.  The genuine ordinary branch is obstructed first by
	  \(o_{\sigma,M}^{(1),\mathrm{sc}}=\hbar N[\bar c_M]\), and then by
	  \(\beta^{\mathrm{sc}}_M\),
	  \(\beta^{\mathrm{sc}}_{\mathrm{cl}}\),
	  \(\mu^{\mathrm{sc}}_{\mathrm{cl}}\), and
	  \(\lambda^{\mathrm{sc}}_C\) for any supplied closed-exchange tower.
	  The central-character, opposite central-extension, and
	  balanced-supertrace mechanisms instead replace the source or open model
	  before the reduced scalar class forms.  In the opposite extension
	  \(J_{\mathrm{op}}=-k^\vee\) satisfies
	  \(d_{\mathrm{CE}}J_{\mathrm{op}}=-\hbar N\bar c\); after forgetting
	  \(K_{\mathrm{cl}}\), the class \(\hbar N[\bar c]\) returns on
	  \(\bar A\).  Outside the minimal
	  full-equivariant finite-window branch of
	  Theorem~\ref{thm:app-minimal-full-equivariant-all-order-vanishing},
	  the non-scalar lift still requires the curved kernel, product
	  centrality homotopies, \(P_0\)-bracket homotopies,
	  current-compatible Costello locality, and vanishing of the residual
	  class in
	  \(H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})\).

  \item \emph{Global and cross-volume descent.}
  A target theorem supplies a matched-conventions datum
  \(\mathfrak C_{\mathrm{tar}}\).  The admissibility vector is
  \[
    \operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}}
    =
	    (\operatorname{per}_{\mathrm{tar}},
	     \operatorname{ob}_{\mathrm{WR}},
	     \operatorname{ob}_{\mathrm{anom}},
	     \operatorname{ob}_{\mathrm{QME}},
	     \operatorname{ob}_{\mathrm{conv}},
	     \operatorname{ob}_{\mathrm{hyp}},
	     \operatorname{ob}_{6r},
	     \operatorname{ob}_{\mathrm{MD}}).
  \]
  It must vanish, with compatible null-homotopies and comparison
  morphisms, before any CoHA, compact BCOV, quintic, OSV/GV,
  Abel--Jacobi, MNOP, Vol III, Igusa/BKM, or global Calabi--Yau
  consequence is deduced from the formal-local theorem.  The compact-CY
  fixture split is a source-routing construction only: it separates CoHA
  vocabulary from HKQ, CDGP, GV, OSV, Abel--Jacobi, conifold, Stokes, and
  arithmetic fixtures.  It is not theorem support for a compact-CY
  transfer and supplies no evidence for the local QME, Ext, cyclic,
  Weyl/Moyal, radial-parts, or kernel theorem surfaces.
\end{enumerate}

\endgroup
