% frontier_mnop_framing_volume.tex
% Standalone frontier notes: MNOP/DT/PT source facts, E_2-centre
% conjecture, S^3-framing targets on the quintic, chiral-volume quintic
% evidence, and compact CY_3 categorical descent targets.
%
% Not bound into main.tex: the bound manuscript is the closed local
% mixed A/B theorem on R^2 x C^2. This file records the compact
% CY_3 frontier in the same voice (Chriss-Ginzburg / Russian school
% + math-physics elite: Maulik, Nekrasov, Okounkov, Pandharipande,
% Costello, Bridgeland, Kontsevich-Soibelman, Joyce, Kinjo-Park-Safronov).

\documentclass[12pt]{amsart}
\usepackage[localtheorems]{raeez-math-template}
\input{mathmacros.tex}

% amsthm setup (preamble.tex provides these, but we're standalone here).
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{remark}
\newtheorem{rmk}[thm]{Remark}
\renewcommand*{\theHthm}{\thesection.\arabic{thm}}
\renewcommand*{\theHprop}{\theHthm}
\renewcommand*{\theHconj}{\theHthm}
\renewcommand*{\theHrmk}{\theHthm}

% Local macros used only in this frontier file.
\providecommand{\E}{\mathrm{E}}
\providecommand{\PhiFA}{\Phi^{\mathrm{FA}}}
\providecommand{\DT}{\mathrm{DT}}
\providecommand{\PT}{\mathrm{PT}}
\providecommand{\GW}{\mathrm{GW}}
\providecommand{\Perf}{\mathrm{Perf}}
\providecommand{\Aut}{\mathrm{Aut}}
\providecommand{\End}{\mathrm{End}}
\providecommand{\cF}{\mathcal{F}}
\providecommand{\cO}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}

\title[Compact CY$_3$ frontier]{Conditional compact CY$_3$ frontier:
  MNOP substitution, $S^3$ framing, and quintic period evidence}

\begin{document}
\maketitle

\begin{rmk}[Frontier status]
This note records target data and compact CY\(_3\) frontier evidence.
It is not a consequence of the formal-local Hamiltonian BF/Moyal theorem.
Any use in the bound manuscript requires a matched-conventions descent
theorem and null-homotopies for the period, anomaly, QME, convergence,
hyperdescent, six-relation, and operadic obstruction classes.
\end{rmk}

\begin{rmk}[Source-fixture status]
The scalar MNOP/PT/DT source row is
\path{references/primary-sources/mnop-pt-dt-source-anchors-2026-04-30.md}.
The quintic BCOV/GV numerical-source row is
\path{references/primary-sources/quintic-bcov-gv-source-anchors-2026-04-30.md}.
The reconstructed CoHA/centre source-gap row is
\path{references/primary-sources/coha-center-source-anchors-2026-04-30.md}.
It supplies only Hall/CoHA/centre vocabulary and stable identifiers:
Lurie centre grammar, Joyce/Gross--Joyce--Tanaka Hall--vertex
structures, and Joyce--Upmeier and Kinjo--Park--Safronov
orientation/CoHA prerequisites. The non-CoHA compact-CY source-control
row is
\path{references/primary-sources/compact-cy-source-fixture-control-surface-2026-04-30.md}.
It is not a construction. Hence no compact-target \(\cF_X\), trace maps,
\(\sigma_Q\), \(\E_2\)-rigidity, \(N_{\AJ}\), or
\(\mathrm{Ob}_{\mathrm{UKD}}(C_{\mathrm{tar}})\)-null-homotopy is
imported as theorem-grade data here.

First-principles admission test: a CoHA is not produced by the
formal-local Hamiltonian BF/Moyal calculation.  It would require a
3CY category of brane objects, a derived moduli stack of objects,
extension or triangle correspondences giving Hall multiplication,
orientation data and vanishing-cycle cohomology, and then a separate
comparison from that Hall algebra to the relevant factorization centre.
The bound local theorem supplies instead a shifted cotangent Hamiltonian
Lie algebra, its CE/PV comparison, principal-part currents, and weighted
Moyal/BV coefficient identities.  Thus CoHA enters this note only as
compact-CY frontier target language, not as local theorem input.
\end{rmk}

\section{MNOP source facts and the $\E_2$-centre target}\label{sec:mnop}

Let $X$ be a smooth compact Calabi--Yau threefold. The present
source-backed datum is scalar: DT virtual counts, PT stable-pair counts,
GW virtual-class notation, the degree-zero MacMahon factor, and the
reduced DT/PT equality in the smooth projective CY$_3$ setup. The compact
target datum is separate:
\[
  C_{\mathrm{tar}}(X)=
  \bigl(\cF_X,\ M_{\DT},M_{\PT},M_{\GW},\
    \mathrm{Tr}_{\DT},\mathrm{Tr}_{\PT},\mathrm{Tr}_{\GW},\
    \sigma_X\bigr),
\]
where \(\cF_X\) would be the factorisation-algebra image
\(\PhiFA_3(\Perf(X))\), the \(M_\bullet\) would be dualisable
\(\cF_X\)-modules, the trace maps would recover scalar partition
functions, and
\(\sigma_X\in\Aut_{\E_2}(Z_{\E_2}(\cF_X))\) would implement the
MNOP/PT--GW substitution.  The fixture
\path{references/primary-sources/mnop-pt-dt-source-anchors-2026-04-30.md}
does not construct \(C_{\mathrm{tar}}(X)\). The CoHA/centre fixture
\path{references/primary-sources/coha-center-source-anchors-2026-04-30.md}
records the Lurie/Joyce/Kinjo--Park--Safronov source family only as
grammar and prerequisites for such a construction.

The scalar rows are:
\begin{itemize}
  \item Donaldson--Thomas virtual counts (Thomas; Behrend; Behrend--
    Fantechi), with
    partition function $Z_{\DT}(q) = \sum_n \DT_n(X) q^n$;
  \item Pandharipande--Thomas stable-pair counts, with
    $Z_{\PT}(q) = \sum_n \PT_n(X) q^n$;
  \item Gromov--Witten virtual-class notation (Behrend--Fantechi,
    Li--Tian, MNOP), with
    $Z_{\GW}(u) = \sum_g \GW_g(X) u^{2g-2}$.
\end{itemize}

\begin{thm}[DT/PT factorisation at the quintic]\label{thm:mnop-quintic}
  Let $Q \subset \P^4$ be a smooth quintic threefold, so that
  $\chi(Q) = -200$. The degree-zero DT generating function factors off
  as the MacMahon power, and the reduced DT partition function
  coincides with the PT partition function:
  $$Z_{\DT}(Q;\, q) \;=\; M(-q)^{\chi(Q)} \cdot Z_{\PT}(Q;\, q),
    \qquad M(q) = \prod_{n \geq 1}(1-q^n)^{-n}.$$
  The PT/GW leg with substitution \(-q=e^{iu}\) is conditional on the
  Katz--Klemm--Vafa integrality conjecture for \(Q\); it is finite-genus
  target evidence only after the Huang--Klemm--Quackenbush source row is
  supplied. The quintic fixture records HKQ as a missing local source
  obligation; the CoHA fixture is irrelevant to this numerical source
  row.
\end{thm}

\begin{proof}[Proof sketch]
  The DT/PT factorisation $Z_{\DT} = M(-q)^{\chi} \cdot Z_{\PT}$ is
  the scalar identity
  \[
    Z_{\DT}=Z_{\DT,0}Z'_{\DT},\qquad
    Z_{\DT,0}=M(-q)^{\chi(Q)},\qquad
    Z'_{\DT}=Z_{\PT}.
  \]
  The source fixture anchors the reduced equality in Bridgeland's
  Hall-algebra theorem, treats Toda as an auxiliary wall-crossing source,
  anchors the MacMahon factor in Behrend--Fantechi's Hilbert-scheme
  formula, and checks locally that \(\chi(Q)=-200\). This proves the
  displayed scalar identity. The reconstructed CoHA fixture does not lift
  it to \(\cF_Q\), construct trace maps, or supply a
  motivic/factorisation-algebra identity.

  MNOP I/II and Pandharipande--Thomas formulate the PT/GW substitution
  as conjectural target data. KKV, HKQ, and the compact BCOV/GV source
  rows needed to upgrade finite-genus evidence are outside the scalar
  fixture and are recorded as missing in
  \path{references/primary-sources/quintic-bcov-gv-source-anchors-2026-04-30.md}.
  \qed
\end{proof}

\begin{conj}[E2-centre MNOP package]\label{conj:e2-centre-mnop-package}
  The substitution $-q = e^{iu}$ is not a tautology. In the compact
  target datum \(C_{\mathrm{tar}}(Q)\), the three objects
  $M_{\DT}, M_{\PT}, M_{\GW}$ would be distinct dualisable objects with
  a priori independent partition functions.  The desired
  chain-level upgrade is a constructed automorphism
  \[
    \sigma_Q\in\Aut_{\E_2}\bigl(Z_{\E_2}(\cF_Q)\bigr)
  \]
  effecting \(-q=e^{iu}\), together with a rigidity theorem proving its
  uniqueness.  The CoHA/centre fixture supplies only the source grammar
  in which this sentence can be posed. This is target data: it neither
  constructs \(\sigma_Q\) nor proves \(\Aut_{\E_2}\)-rigidity.
\end{conj}

\begin{rmk}[Generic compact CY$_3$, via Joyce--KPS vertex algebra]
  The scalar DT/PT factorisation has a source-backed smooth projective
  CY$_3$ form. The CoHA/centre fixture
  \path{references/primary-sources/coha-center-source-anchors-2026-04-30.md}
  records Joyce's vertex algebra on moduli stacks, the
  Gross--Joyce--Tanaka Hall formalism, Kinjo--Park--Safronov
  orientation/CoHA input, and Lurie's centre formalism as source
  vocabulary. It also records the firewall: compact-target \(\cF_X\),
  trace maps, \(\sigma_X\), \(\E_2\)-rigidity, and
  \(\mathrm{Ob}_{\mathrm{UKD}}(C_{\mathrm{tar}})\) are unconstructed.
  Thus the Joyce--KPS line is a conditional target schema, not a theorem
  in this note and not a Vol III transfer.
\end{rmk}

\section{Chain-level $S^3$-framing on the quintic}

Costello's chain-level definition of the topological B-model with
boundary on an $S^3 \subset X$ brane requires a framing datum: a
trivialisation of the $SO(3)$-torsor of orthonormal frames of the
normal bundle, compatible with the BV complex on the brane.
At a Lagrangian $L \cong S^3 \hookrightarrow Q$ in the smooth
quintic --- e.g.\ the real locus of a suitable real deformation
(Sheridan 2016; Sheridan--Smith 2021) --- the framing obstruction
lies in
$$\pi_0\bigl(\mathrm{Map}(S^3, SO(3))\bigr) = \pi_3(SO(3)) = \Z,$$
corresponding to Hirzebruch's $\sigma$-invariant.

\begin{prop}[Normal-bundle orientation and topological triviality]
  \label{prop:s3-framing-quintic}
  For a Lagrangian $L \cong S^3 \subset Q$ in a smooth quintic
  threefold, the CY$_3$ structure orients \(N_{L/Q}\), and the oriented
  rank-three bundle \(N_{L/Q}\to S^3\) is topologically trivial.
  Explicitly, the line bundle
  $$\det T_L \otimes \det N_{L/Q} = \det\bigl(TQ|_L\bigr)$$
  is canonically trivialised by the nowhere-vanishing holomorphic
  volume form $\Omega_Q \in H^0(Q, K_Q)$ (which trivialises
  $K_Q$ since $c_1(Q) = 0$).
\end{prop}

\begin{proof}
  $Q$ has $K_Q = \cO_Q$ and $\Omega_Q$ is nowhere zero. Restriction
  to $L$ gives a nowhere-vanishing section of $\det(TQ|_L)$; the
  Lagrangian splitting $TQ|_L = TL \oplus N_{L/Q}$ as real bundles
  (under the complex structure) identifies
  $\det(TQ|_L)_\R = \det(T_L) \otimes \det(N_{L/Q})$. Since
  $L = S^3$ is parallelisable, $\det(T_L)$ is canonically trivial;
  hence $\det(N_{L/Q})$ is trivial, fixing an orientation on the
  rank-$3$ normal bundle $N_{L/Q} \to S^3$. Every oriented rank-$3$
  real bundle on $S^3$ is trivial: the classifying map lands in
  $BSO(3)$, and $\pi_3(BSO(3)) = \pi_2(SO(3)) = 0$. This proves
  orientation and topological trivializability.  It does not select the
  integer point of the framing torsor
  \(\pi_3(SO(3))=\Z\), nor a BV/$A_\infty$ chain homotopy.\qed
\end{proof}

\begin{conj}[Chain-level \(S^3\)-framing target]
  A chain-level framing requires a chosen integer framing class in the
  \(\Z\)-torsor of trivializations and a Costello-compatible homotopy on
  the brane BV complex.  The holomorphic volume form supplies the
  orientation/triviality input above, not the full chain-level datum.
\end{conj}

\section{Chiral-volume conjecture at small enumerative degree}

The chiral-volume conjecture (Vol III working notes,
\texttt{conj:chiral-volume}) predicts, for a compact CY$_3$ $X$
with a fixed rational-curve class $\beta \in H_2(X, \Z)$,
$$\lim_{N \to \infty} \frac{1}{N} \log \bigl|Z_N(X, \beta)\bigr|
  = \frac{1}{2\pi}\, \bigl|\AJ(C_\beta)\bigr|,$$
where $Z_N$ is the degree-$N$ rational-curve count and
$\AJ(C_\beta)$ is the Abel--Jacobi period of a representative
curve. For the quintic $Q$ and the hyperplane class $H \in H_2(Q)$,
the degree-$N$ genus-$0$ BPS invariant \(n_N\) is the scalar input. The
quintic fixture supports the displayed entries \(N\leq9\) from the local
BCOV table and checks the arithmetic below. It records the HKQ \(N=10\)
entry, CDGP period convention, OSV rate, and historical low-degree
source mirrors as missing local source obligations. The CoHA/centre
fixture
\path{references/primary-sources/coha-center-source-anchors-2026-04-30.md}
records only Hall/CoHA/centre vocabulary and its non-import firewall.
The non-CoHA compact-CY source-control row
\path{references/primary-sources/compact-cy-source-fixture-control-surface-2026-04-30.md}
routes the remaining domain fixtures. Thus the following table is a
conditional numerical input at \(N=10\), not a new theorem of this note:
$$\renewcommand{\arraystretch}{1.1}
\begin{array}{r@{\;=\;}l}
  n_1 & 2875 \\
  n_2 & 609\,250 \\
  n_3 & 317\,206\,375 \\
  n_4 & 242\,467\,530\,000 \\
  n_5 & 229\,305\,888\,887\,625 \\
  n_6 & 248\,249\,742\,118\,022\,000 \\
  n_7 & 295\,091\,050\,570\,845\,659\,250 \\
  n_8 & 375\,632\,160\,937\,476\,603\,550\,000 \\
  n_9 & 503\,840\,510\,416\,985\,243\,645\,106\,250 \\
  n_{10} & 704\,288\,164\,978\,454\,686\,113\,488\,249\,750.
\end{array}$$
The sequence $a_N := N^{-1} \log n_N$ attains its minimum at $N=3$:
$$
a_1 \approx 7.964,\;
a_2 \approx 6.660,\;
a_3 \approx 6.525,\;
a_4 \approx 6.554,\;
a_5 \approx 6.613,
$$
$$
a_6 \approx 6.676,\;
a_7 \approx 6.733,\;
a_8 \approx 6.785,\;
a_9 \approx 6.832,\;
a_{10} \approx 6.873.
$$
The sequence decreases sharply through $N = 3$, then increases
monotonically: $a_{N+1} - a_N > 0$ for $N \in \{3, \dots, 9\}$, with
increments
\[
\{+0.029,\ +0.060,\ +0.062,\ +0.058,\ +0.052,\ +0.046,\ +0.041\}.
\]

\begin{prop}[Conditional finite quintic chiral-volume evidence through $N = 10$]
  \label{prop:chiral-volume-quintic}
  Conditional on the displayed genus-zero quintic table through \(N=10\),
  the sequence $a_N = N^{-1} \log n_N$ on the quintic with hyperplane
  class $H$ has a minimum at $N = 3$ and, on the tail
  $N \in \{5, \dots, 10\}$, fits the three-parameter ansatz
  $$a_N \;=\; L \;+\; \alpha\, \frac{\log N}{N} \;+\; \frac{\beta}{N}$$
  to residuals below $5 \times 10^{-6}$ with
  $L = 7.593$, $\alpha = -3.32$, $\beta = 0.45$. The fitted
  parameter \(L\) is compatible, to three significant figures, with the
  raw mirror-period ratio $|t(z_c)|$ at the conifold point
  $z_c = 5^{-5}$ of the Candelas--de la Ossa--Green--Parkes mirror
  family:
  $$|t(z_c)| \;=\; \left|\frac{\omega_1}{\omega_0}(z_c)\right|
    \;=\; 7.5909,$$
  with $\omega_0 = \sum_n ((5n)!/(n!)^5)\, z^n$ the fundamental period
  and $\omega_1 = \omega_0(z) \log z + \sum_n ((5n)!/(n!)^5) \cdot
  5(H_{5n} - H_n)\, z^n$ the logarithmic period ($H_k$ the $k$-th
  harmonic number). Identifying this raw ratio with a Hodge-normalised
  Abel--Jacobi norm requires the missing \(N_{\AJ}\) normalisation. The
  OSV physical rate is a missing-source comparison value
  $5 \log 5 \approx 8.047$; the finite data $\{a_N\}$ rises monotonically
  from $N = 4$ in a way compatible with, but not proving, that
  asymptotic picture.
\end{prop}

\begin{proof}
  The fixture
  \path{references/primary-sources/quintic-bcov-gv-source-anchors-2026-04-30.md}
  supplies local BCOV anchors for \(N\leq9\) and records the HKQ
  \(N=10\) row and the historical low-degree mirrors as source gaps.
  Taking the displayed table as input, linear least-squares on the six equations
  $a_N = L + \alpha (\log N)/N + \beta / N$ for
  $N \in \{5, \dots, 10\}$ gives the stated coefficients with
  residuals bounded by $5 \times 10^{-6}$. The same fixture checks the
  raw period arithmetic from the displayed CDGP-formula input. The
  fundamental and logarithmic periods satisfy the Picard--Fuchs operator
  $\theta^4 - 5 z (5 \theta + 1)(5 \theta + 2)(5 \theta + 3)(5
  \theta + 4)$ with $\theta = z \partial_z$; evaluated at
  $z_c = 5^{-5}$ via the convergent power series (radius of
  convergence $5^{-5}$, boundary value by continuity from the
  interior),
  $$\omega_0(z_c) \approx 1.070725350970, \qquad
    \omega_1(z_c) \approx -8.127765022685,$$
  giving $|t(z_c)| \approx 7.590896223126$. The CDGP source row for the
  formula and the OSV source row for the entropy-rate interpretation are
  missing local fixtures. This is arithmetic evidence, not a theorem for
  fixed-class quintic counts.\qed
\end{proof}

\begin{rmk}
  The displayed data close only the arithmetic gap conditional on the
  \(N=10\) HKQ row. Three numerical paths are mutually compatible:
  direct tail extrapolation gives \(L\approx7.59\), the raw mirror-period
  ratio gives $|t(z_c)| \approx 7.5909$, and the OSV attractor comparison
  value is $5 \log 5 \approx 8.05$. The correction
  $\alpha = -3.32 < 0$ forces the approach to $L$ from below: the
  conjectural chiral-volume limit would therefore not be bounded above by
  $\{a_1, a_2, a_3\}$; those points lie on the
  Schubert--Katz--Ellingsrud--Str\o mme Fano-geometric branch, below
  the expected large-$N$ BPS regime. The source provenance of that
  historical branch remains open until the local mirrors named in the
  fixture are supplied.
\end{rmk}

\begin{rmk}[Abel--Jacobi normalisation gap]
  \label{rmk:hodge-normalisation-aj}
  The conjecture
  $\lim a_N = (2\pi)^{-1} |\AJ(C_H)|$ uses the Hodge metric on
  $J^2(Q)$. The raw mirror ratio
  \(t(z_c)=\omega_1(z_c)/\omega_0(z_c)\) is not an Abel--Jacobi norm by
  itself. A theorem-grade comparison requires a normalisation datum
  \(N_{\AJ}\) matching the CDGP period basis, the Hodge metric, and the
  \(2\pi i\)-monodromy convention. No local fixture supplies
  \(N_{\AJ}\). This is an Abel--Jacobi/period-normalisation gap, not a
  CoHA datum. The finite evidence \(L\approx |t(z_c)|\) is therefore a
  target normalisation check, not a proof of the \(N\to\infty\) limit.
\end{rmk}

\section{NCCR substitute at generic compact CY$_3$}

Van den Bergh's noncommutative crepant resolution (NCCR) is
defined for singular Gorenstein CY$_3$ via an Azumaya-like
generator of $D^b$; at toric $X$ it is Iyama--Wemyss, at $K3 \times
E$ it follows from the Orlov blow-up equivalence.

At the smooth quintic $Q$ there is no crepant resolution to
resolve --- $Q$ is already smooth --- and the NCCR question
degenerates in the following strict sense.

\begin{prop}[Serre pairing on smooth compact CY$_3$]
  \label{prop:serre-nccr-substitute}
  Let $X$ be a smooth compact Calabi--Yau threefold. The Serre
  functor $S_X : D^b(X) \to D^b(X)$ satisfies \(S_X=[3]\).  The CY$_3$
  structure gives the Serre pairing on \(\Perf(X)=D^b(X)\).  This is the
  categorical Calabi--Yau datum that any local quasi-NCCR descent must
  preserve; it is not by itself a Van den Bergh NCCR or a global
  quasi-NCCR construction.
\end{prop}

\begin{proof}
  Smoothness plus $K_X = \cO_X$ gives $S_X = \otimes K_X[3] = [3]$.
  The CY$_3$ structure provides the Calabi--Yau pairing
  $$\RHom(F, G) \otimes \RHom(G, F) \to \C[-3]$$
  which is the Serre duality pairing.  No sheaf of endomorphism algebras,
  local tilting object, or descent datum is constructed here.\qed
\end{proof}

\begin{rmk}
  Proposition~\ref{prop:serre-nccr-substitute} records the Serre
  structure that a compact-CY substitute must preserve.  The global
  quasi-NCCR descent problem remains target data: one still needs a local
  algebraic or dg model with finite-dimensionality, descent, and
  Serre-equivariance hypotheses checked.
\end{rmk}

\section{Fourier--Mukai partners for $K3 \times E$}

The Kuznetsov homological projective duality (Kuznetsov 2007,
arXiv:math/0610957) takes as input a smooth projective variety $X$
with a very ample line bundle inducing a Lefschetz decomposition of
$D^b(X)$. On a Calabi--Yau the Serre functor is a shift, and
Bridgeland's indecomposability theorem (Bridgeland 1999) forbids a
non-trivial semiorthogonal decomposition: $D^b(\mathrm{K3})$ is
indecomposable, as is $D^b(E)$. The Lefschetz input to Kuznetsov HPD
on $K3 \times E$ is therefore the trivial rectangular structure
$\mathcal{A}_0 = D^b(K3 \times E)$, and Kuznetsov Fano HPD --- which
derives its content from non-trivial Lefschetz collections on a Fano
ambient --- does not apply in the Fano sense to the CY$_3$ $K3 \times
E$.

The content that survives is a Fourier--Mukai partner construction,
not a Lefschetz HPD or an automatic self-duality statement.

\begin{thm}[Fourier--Mukai equivalence in the isotropic \(K3\times E\) case]
  \label{thm:fm-self-duality-k3e}
  Let $S$ be a projective $K3$ surface with primitive polarisation
  $H_S$, and let $E$ be a principally polarised elliptic curve. Fix a
  Mukai vector $v = (r, \ell, s) \in \widetilde{H}(S, \Z)$ with $\ell
  \in \mathrm{NS}(S)$, Mukai pairing \(\langle v,v\rangle=0\), and
  $H_S$ chosen $v$-generic. Assume the coprimality condition
  \begin{equation}\label{eq:coprimality-star}
    \gcd(r,\, \ell \cdot H_S,\, s) = 1. \tag{$\star$}
  \end{equation}
  Let $M := M_{H_S}(v)$ be the moduli space of $H_S$-stable sheaves
  with Mukai vector $v$. Then:
  \begin{enumerate}
    \item $M$ is a smooth projective $K3$ surface (Mukai 1987;
      O'Grady 1997);
    \item there is an equivalence of $\C$-linear triangulated
      categories
      $$\Phi_{\mathcal{U}} :\ D^b(S) \xrightarrow{\,\sim\,} D^b(M),$$
      given by Fourier--Mukai transform along the universal sheaf
      $\mathcal{U}$ on $S \times M$ (Bridgeland--Maciocia 2001,
      \emph{Complex surfaces with equivalent derived categories},
      Thm.\ 1.1);
    \item combined with the Poincar\'e--Mukai autoequivalence
      $\mathrm{FM}_{\mathcal{P}} : D^b(E) \xrightarrow{\,\sim\,}
      D^b(\hat{E}) = D^b(E)$ (Mukai 1981), the product transform
      $$\Phi_{\mathcal{U}} \boxtimes \mathrm{FM}_{\mathcal{P}} :\
        D^b(S \times E) \xrightarrow{\,\sim\,}
        D^b(M \times E)$$
      is an equivalence of CY$_3$ categories preserving the Serre
      structure $S_{X} = [3]$.  When \(M\simeq S\) this is an
      untwisted Fourier--Mukai self-equivalence; in general it is a
      derived equivalence to the partner \(M\times E\).
  \end{enumerate}
\end{thm}

\begin{proof}
  (1) Under $(\star)$ and $v$-genericity of $H_S$, every
  $H_S$-semistable sheaf with Mukai vector $v$ is stable
  (no strictly semistables); the moduli $M$ is then a smooth projective
  holomorphic symplectic variety of dimension
  \(\langle v,v\rangle+2=2\).  Hence \(M\) is a \(K3\) surface.  For
  positive Mukai square the moduli space is higher-dimensional
  hyperk\"ahler and the product with \(E\) is no longer a CY$_3$ of the
  form asserted here.

  (2) The universal sheaf $\mathcal{U}$ exists on $S \times M$ under
  $(\star)$: $\gcd(r, \ell \cdot H_S, s) = 1$ kills the Brauer
  obstruction to a universal family (C\u{a}ld\u{a}raru 2000,
  Thm.\ 1.3.2). The Fourier--Mukai kernel
  $\mathcal{U} \in D^b(S \times M)$ satisfies the
  Bridgeland--Maciocia orthogonality criterion
  (Bridgeland--Maciocia 2001, \S 1) and induces an equivalence.
  Without $(\star)$, $\mathcal{U}$ exists only as a
  $p_M^*\alpha$-twisted sheaf for a Brauer class $\alpha \in
  \mathrm{Br}(M)$, yielding instead $D^b(S) \simeq D^b(M, \alpha)$
  (Huybrechts--Stellari 2005).

  (3) On $E$ with principal polarisation, $\hat{E} \cong E$
  canonically; the Poincar\'e bundle $\mathcal{P} \in D^b(E \times E)$
  is the kernel of $\mathrm{FM}_{\mathcal{P}}$ (Mukai 1981, Thm.\
  2.2). Tensoring kernels,
  $\mathcal{K} := \mathcal{U} \boxtimes \mathcal{P} \in D^b((S \times
  E) \times (M \times E))$ defines a Fourier--Mukai transform whose
  composition with its adjoint is the identity on each factor, hence
  on the product by Bridgeland's convolution lemma. The Serre functor
  is preserved because both $\Phi_{\mathcal{U}}$ and
  $\mathrm{FM}_{\mathcal{P}}$ are exact equivalences between
  CY categories of the same dimension ($\dim_{\mathrm{CY}} = 2$ and
  $\dim_{\mathrm{CY}} = 1$ respectively), and Serre functors are
  preserved by any equivalence; the product Serre $S_X = [3]$
  survives.\qed
\end{proof}

\begin{prop}[Brauer-twisted dichotomy in the isotropic case]
  \label{prop:coprimality-dichotomy}
  Keep the isotropic hypothesis \(\langle v,v\rangle=0\) and drop
  $(\star)$ in Theorem~\ref{thm:fm-self-duality-k3e}. Then there
  exists a Brauer class $\alpha \in \mathrm{Br}(M)$, whose order
  divides $\gcd(r, \ell \cdot H_S, s)$, such that
  $$D^b(S \times E) \simeq D^b\bigl((M, \alpha) \times E\bigr),$$
  where the right-hand side denotes the derived category of
  $p_M^*\alpha$-twisted sheaves. The partner is
  \((M,\alpha)\times E\) with twisted \(K3\) factor; an untwisted
  kernel exists only under the coprimality hypothesis.
\end{prop}

\begin{proof}
  C\u{a}ld\u{a}raru 2000 Thm.\ 1.3.2 constructs the Brauer obstruction
  to the universal sheaf from the non-coprime Mukai vector; its order
  is the gcd. Huybrechts--Stellari 2005 (\emph{Equivalences of twisted
  K3 surfaces}) then identifies the derived equivalence as a twisted
  Fourier--Mukai. The elliptic factor contributes an untwisted
  $\mathrm{FM}_{\mathcal{P}}$.\qed
\end{proof}

\begin{rmk}[Why ``Kuznetsov Fano HPD'' is the wrong frame]
  The attempted ``Kuznetsov Fano HPD on $K3
  \times E$'' formulation requires a smooth Fano ambient
  with a non-trivial Lefschetz collection; $K3 \times E$ is CY$_3$,
  not Fano, and its $D^b$ is indecomposable. The correct replacement is
  the Fourier--Mukai partner construction
  (Theorem~\ref{thm:fm-self-duality-k3e}), in the isotropic
  Mukai-vector case and governed by coprimality $(\star)$, with the
  Brauer-twisted dichotomy
  (Proposition~\ref{prop:coprimality-dichotomy}) supplying the
  beyond-coprimality partner. The Kuznetsov--Perry 2019
  categorical-join / rectangular-HPD machinery does not upgrade
  Fourier--Mukai to Fano HPD here, precisely because neither
  $D^b(K3)$ nor $D^b(E)$ admits a non-trivial Lefschetz decomposition
  to feed into the rectangular construction.
\end{rmk}

\begin{rmk}[Alignment with Vol III]
  Coprimality $(\star)$ is the primitive Mukai-vector hypothesis that
  controls the untwisted Fourier--Mukai kernel.  The total-space
  categorical value is
  \(\kappa_{\mathrm{cat}}(K3\times E)=\chi(\cO)=0\) by K\"unneth.  The
  Vol III comparison keeps the other normalizations separate:
  \(\kappa_{\mathrm{ch}}^{\mathrm{Heis}}=3\),
  \(\kappa_{\mathrm{BKM}}(\Phi_1)=5\) in the paramodular
  \(\Delta_5\) row, \(\kappa_{\mathrm{fibre}}(K3)=2\), and
  \(\mathrm{rk}\,\widetilde H^*(K3)=24\).  The value \(2\) is fibre
  Euler data, and the value \(24\) is Mukai-rank data; neither is the
  compact CY$_3$ total-space invariant.
\end{rmk}

\section{Non-perturbative BCOV on the quintic: Gopakumar--Vafa closure}
\label{sec:bcov-np-closure}

Costello--Li 2012 (arXiv:1201.4501) construct the classical BCOV field
theory, define the perturbative BV quantisation problem, and prove the
elliptic-curve uniqueness/Virasoro results in their stated scope. That
paper is a framework and source theorem; it is not, by itself, a compact
CY$_3$ all-genus construction of the quintic amplitudes. The fixture
\path{references/primary-sources/quintic-bcov-gv-source-anchors-2026-04-30.md}
supports the BCOV/Costello--Li framework, BCOV conifold vocabulary, and
the BCOV degree \(1,\dots,9\) quintic table. It records HKQ, CDGP,
Gopakumar--Vafa, OSV, Strominger, Schwinger/Vafa, Shenker--Marino, and
Cecotti--Codesido--Marino source rows as missing local obligations. In
the conditional target below, write
$\{F_g^{\mathrm{BCOV}}(X,t)\}_{g\geq0}$ for a compact CY$_3$ solution of
the BCOV holomorphic anomaly equation with the standard large-radius and
conifold boundary data. The
perturbative series
\[
  F^{\mathrm{pert}}(\lambda, t) \;=\; \sum_{g \geq 0} \lambda^{2g - 2}\, F_g(X, t),
  \qquad \lambda = g_s,
\]
is expected in the resurgent compact-CY picture to be Gevrey-$1$ in
\(\lambda\): the Shenker--Marino factorial growth
$F_g \sim (2g - 3)! / A^{2g - 2}$ with $A = \oint_{\gamma_c} \Omega_X$
the vanishing-cycle period at the nearest conifold singularity forces
Borel non-summability on the physical ray. The local fixture does not
source this large-order theorem; it remains part of the compact target
datum. The residual obstruction at compact CY$_3$ is exactly this:
perturbative BCOV does not specify the trans-series completion.

The Gopakumar--Vafa formula is retained as the conditional
non-perturbative schema; local GV mirrors are absent in the fixture:
\begin{equation}\label{eq:gv-expansion}
  F^{\mathrm{GV}}(\lambda, t) \;=\; \sum_{\beta > 0}\, \sum_{g \geq 0}\, n_\beta^g
    \sum_{m \geq 1} \frac{1}{m}\,
    \bigl(2 \sin(m \lambda / 2)\bigr)^{2g - 2}\,
    e^{- m\, \beta \cdot t},
\end{equation}
with $n_\beta^g \in \Z$ the BPS invariants. Each fixed-$\beta$ summand
would resum infinitely many perturbative genera and produce Schwinger
poles at $\lambda = 2\pi k / m$ whose residues are electric--magnetic
pair-production amplitudes. This is the proposed trans-series completion
missing from perturbative BCOV, not a source-closed theorem in this note.

\begin{conj}[GV non-perturbative closure target on the quintic]
  \label{conj:bcov-np-quintic}
  Assume the HKQ, CDGP, GV, OSV, and conifold-resurgence source rows
  recorded as missing in the quintic fixture are supplied and their
  normalisations match the scalar DT/PT fixture.
  Let $Q \subset \P^4$ be the smooth quintic. Let
  $F^{\mathrm{BCOV}}_g(Q, t)$ be the genus-$g$ solution of the BCOV
  holomorphic anomaly recursion with the CDGP large-radius input and the
  standard conifold gap boundary condition. Let $F^{\mathrm{GV}}$ be the
  Gopakumar--Vafa resummation~\eqref{eq:gv-expansion}, with BPS
  invariants $n_\beta^g(Q)$ computed by Huang--Klemm--Quackenbush 2009
  through genus $22$. Then in the Kahler cone $\Re t > t_c$, where
  $t_c$ is the image of the conifold locus $\psi = 1$ on the
  complex-structure moduli space of the mirror quintic $\widetilde Q$:
  \begin{enumerate}
    \item[(i)] \emph{(Conditional finite-genus evidence.)} For every
      $0 \leq g \leq 22$,
      \[
        F^{\mathrm{BCOV}}_g(Q, t) \;=\; [\lambda^{2g - 2}]\, F^{\mathrm{GV}}(\lambda, t)
      \]
      as formal power series in $e^{-\beta \cdot t}$; equality holds in
      $\Z[[e^{-t}]]$ after the Katz--Klemm--Vafa integrality normalisation.
      This item is not source-grade until the HKQ and PT/GW rows are
      locally present.
    \item[(ii)] \emph{(Convergence target.)}
      The genus-$0$ BPS series $\sum_\beta n_\beta^0 e^{-\beta t}$ is
      expected to have a nonempty convergence domain controlled by the
      conifold/entropy scale.  No coefficient-growth theorem proving this
      convergence is supplied here.
    \item[(iii)] \emph{(Conditional local conifold Stokes target.)} The trans-series
      completion of $F^{\mathrm{pert}}$ produced by the GV resummation
      is compatible near the conifold point $\psi = 1$ with the
      Candelas--de la Ossa--Green--Parkes 1991 mirror-period monodromy:
      the local Stokes normalization is expected to have \(S_c=1\), and
      the instanton action is \(A=2\pi i\,\tau_c\), where \(\tau_c\) is the
      vanishing-cycle period $\oint_{\gamma_c} \Omega_{\widetilde Q}$.
  \end{enumerate}
\end{conj}

\begin{rmk}[Verification path]
  (i) would apply the Pandharipande--Thomas formulation of MNOP
  (Theorem~\ref{thm:mnop-quintic}) to BCOV genus-$g$ amplitudes
  determined by the holomorphic anomaly recursion and boundary data.
  This is not an invocation of a compact-CY$_3$ Costello--Li all-genus
  theorem. The fixture presently supports only BCOV/Costello--Li
  framework facts and the scalar DT/PT theorem. The CDGP prepotential,
  HKQ genus-\(22\) computation, GV sine expansion, and PT/GW matching
  remain missing source rows.

  (ii) Even after the HKQ row is supplied, finite-genus and finite-degree
  data would not by themselves prove convergence. Castelnuovo-type genus
  bounds do not bound the number \(n_\beta^0\) of rational curves.  The
  convergence domain of the genus-zero BPS series is therefore an open
  asymptotic input, outside the proved statements of the compact-CY
  frontier.

  (iii) Near the conifold, the target source chain would identify the
  leading factorial growth
  $F_g^{\mathrm{pert}}(Q, t) \sim (2g - 3)! / (2\pi i\, \tau_c)^{2g - 2}$
  in the Borel plane direction fixed by the vanishing cycle $\gamma_c$,
  with $\tau_c = \oint_{\gamma_c} \Omega_{\widetilde Q}$. The Strominger
  conifold mechanism would identify the residue at this Borel
  singularity with a single hypermultiplet of mass $|\tau_c|$; in the
  dual GV expansion~\eqref{eq:gv-expansion} it is the leading-$m$
  contribution of a single BPS hypermultiplet with
  $n_{\beta_c}^0 = 1$, where $\beta_c \in H_2(Q, \Z)$ is the A-model
  class that the Strominger mechanism pairs with $\gamma_c$ under
  mirror symmetry; on the quintic this identification is the
  Candelas--de la Ossa conifold match and is scoped to a neighbourhood
  of the conifold ray, not to the full moduli space. The
  local \'Ecalle--Borel resurgent sum should be compatible with the
  normalization \(S_c=1\) across the conifold ray. The fixture records the
  Strominger, Vafa/Schwinger, Shenker--Marino, and
  Cecotti--Codesido--Marino rows as missing; the statement is therefore a
  target path, not a global compact-CY closure theorem.
\end{rmk}

\begin{conj}[Conditional conifold trinity on the quintic]
  \label{conj:conifold-trinity-quintic}
  On the quintic $Q \subset \P^4$, the following three numerical data
  are expected to coincide as complex numbers (up to sign and overall
  $2\pi i$ normalisation), conditional on the missing conifold source
  rows and the cited resurgent normalization:
  \[
    A_{\mathrm{BCOV}} \;=\; A_{\mathrm{Schwinger}} \;=\; A_{\mathrm{period}},
  \]
  where
  $A_{\mathrm{BCOV}}$ is the Shenker--Marino instanton action of the
  perturbative BCOV series, read off as
  $|F_g| / |F_{g+1}| \sim |A|^2 / (2g-2)(2g-1)$;
  $A_{\mathrm{Schwinger}} = 2\pi i / m$ is the Schwinger-pole
  location of the Gopakumar--Vafa summand at multiplicity $m$,
  rescaled by the class $\beta_c \cdot t_c$;
  and
  $A_{\mathrm{period}} = \oint_{\gamma_c} \Omega_{\widetilde Q}$ is
  the vanishing-cycle period at the conifold locus $\psi = 1$ on
  the mirror quintic. Equality of all three reads the conifold
  Stokes normalization as \(S_c=1\) with a single BPS hypermultiplet
  $n_{\beta_c}^0 = 1$.
\end{conj}

\begin{rmk}[Evidence]
  The present fixture supports only BCOV conifold vocabulary: \(\psi=1\)
  and the pole behaviour near the conifold. The equality
  $A_{\mathrm{BCOV}} = A_{\mathrm{period}}$ requires a
  Huang--Klemm/Shenker--Marino large-order source row. The equality
  $A_{\mathrm{Schwinger}} = A_{\mathrm{period}}$ requires the
  Vafa/Schwinger and Strominger source rows. The normalization
  \(S_c=1\) requires the Cecotti--Codesido--Marino resurgent row. None is
  present locally; no global Stokes-sheaf construction is claimed.
\end{rmk}

\begin{rmk}[What (iii) does \emph{not} claim]
  The resurgent completion in (iii) would be Borel-summed along the
  physical ray and matched at one Stokes wall (the conifold). A full
  non-perturbative completion requires matching at every Stokes wall of
  the quintic moduli space: large complex structure, conifold, and
  Landau--Ginzburg / Gepner. At Gepner, the desired HKQ input is
  finite-genus bootstrap data; at large complex structure, the desired GV
  expansion~\eqref{eq:gv-expansion} is the target definition. The residual
  obstruction is the \emph{global} resurgent sheaf: a unique trans-series
  $F^{\mathrm{np}}(\lambda, t)$ on the full moduli space whose Stokes
  jumps match the BCOV monodromy representation on $H^3(\widetilde Q, \Z)$.
  This is open beyond the quintic and open globally on the quintic
  moduli space; the present fixtures do not check it locally at the
  special loci.
\end{rmk}

\begin{conj}[Mirror-period recovery from non-perturbative BCOV]
  \label{conj:mirror-period-recovery}
  Assume the missing CDGP and GV source rows are supplied with conventions
  matching the raw period formula in
  Proposition~\ref{prop:chiral-volume-quintic}.
  Let
  \[
    \varpi_0(\psi),\quad \varpi_1(\psi),\quad
    \varpi_2(\psi),\quad \varpi_3(\psi)
  \]
  be the CDGP 1991 fundamental periods of the mirror quintic
  $\widetilde Q$, solutions of the quintic Picard--Fuchs operator
  \[
    \mathcal{L}_{\mathrm{PF}} \;=\; (\psi \partial_\psi)^4
      - 5\psi\, \prod_{k = 1}^{4} (5 \psi \partial_\psi + k).
  \]
  The genus-zero prepotential extracted from
  $F^{\mathrm{GV}}(\lambda, t) = \lambda^{-2}\, \mathcal{F}_0(t) + O(\lambda^0)$
  with $t = \varpi_1 / \varpi_0$ the mirror map should satisfy
  \[
    \mathcal{F}_0(t) \;=\; \tfrac{1}{\varpi_0^2}\,
      \bigl(\varpi_0 \varpi_3 - \varpi_1 \varpi_2\bigr)
      + \text{(classical polynomial)}
  \]
  with no instanton corrections beyond those encoded in
  $\{n_\beta^0\}_\beta$. The fixture supports the small-\(\beta\) scalar
  values $n_1^0 = 2875$, $n_2^0 = 609250$, $n_3^0 = 317206375$ from the
  local BCOV table. The CDGP period/prepotential source and the
  Schubert--Katz--Ellingsrud--Str\o mme historical mirrors are still
  missing local source rows.
\end{conj}

\begin{rmk}[Relation to the chiral-volume conjecture]
  Conjecture~\ref{conj:mirror-period-recovery} would be the genus-zero
  shadow of the chiral-volume conjecture
  (Prop.~\ref{prop:chiral-volume-quintic}) after the missing
  \(N_{\AJ}\) normalisation identifies the Hodge-normalised
  Abel--Jacobi period with the mirror-coordinate modulus $|t(z_c)|$.
  Under that additional datum, the conjectural chiral-volume limit \(L\)
  would be the logarithmic period
  $|\varpi_1(z_c)/\varpi_0(z_c)|$ of the CDGP family evaluated at the
  conifold attractor. HKQ genus-\(22\) data would give finite evidence
  after its source row is supplied; higher genera require the resurgent
  completion of
  Conjecture~\ref{conj:bcov-np-quintic}(iii).
\end{rmk}

\section{Honest-status summary}

\begin{enumerate}
  \item MNOP source facts: the DT/PT MacMahon factorisation is theorem
    grade as a scalar partition-function identity, sourced by
    \path{references/primary-sources/mnop-pt-dt-source-anchors-2026-04-30.md}.
    The PT/GW leg is KKV-conditional; HKQ finite-genus evidence is a
    separate compact-CY source gap. The CoHA/\(\E_2\)-centre package is
    source-gap-ledgered target language via
    \path{references/primary-sources/coha-center-source-anchors-2026-04-30.md},
    with no constructed \(\cF_X\), trace maps, \(\sigma_Q\), rigidity
    theorem, or \(\mathrm{Ob}_{\mathrm{UKD}}\)-null-homotopy.
  \item \(S^3\)-framing on the quintic: the CY volume form orients the
    normal bundle and the oriented rank-three bundle is topologically
    trivial (Prop.~\ref{prop:s3-framing-quintic}).  The integer framing
    and Costello-compatible chain homotopy remain target data.
  \item Chiral-volume evidence on the quintic through $N = 10$:
    conditional on the displayed table, the sequence
    $a_N = N^{-1} \log n_N$ has a minimum at $N = 3$
    and increases monotonically thereafter; the three-parameter
    tail fit $a_N = L + \alpha (\log N)/N + \beta / N$ gives
    $L = 7.593$, compatible with the raw mirror-period ratio
    $|t(z_c)| = 7.5909$ to three significant figures. HKQ \(N=10\),
    CDGP normalisation, OSV rate, and \(N_{\AJ}\) remain missing-source
    obligations recorded by the quintic fixture and future
    compact-CY-domain fixtures, not by the CoHA fixture
    (Prop.~\ref{prop:chiral-volume-quintic}).
  \item Smooth compact CY$_3$ categorical input: theorem-grade statement is
    \(S_X=[3]\) and the Serre pairing
    (Prop.~\ref{prop:serre-nccr-substitute}).  A local
    Serre-equivariant quasi-NCCR descent object remains open target data.
  \item Fourier--Mukai equivalence on $K3 \times E$: theorem in the
    isotropic Mukai-vector case under coprimality $(\star)$
    (Theorem~\ref{thm:fm-self-duality-k3e}); dichotomy to twisted
    $K3$ partner beyond $(\star)$
    (Proposition~\ref{prop:coprimality-dichotomy}). Kuznetsov
    Fano HPD does not apply: $K3 \times E$ is CY$_3$, not Fano,
    and $D^b$ of each factor is Bridgeland-indecomposable.
  \item Non-perturbative closure of BCOV on the quintic: conjectural target.
    The fixture supports BCOV/Costello--Li framework and conifold
    vocabulary only; HKQ, GV, CDGP, and conifold-resurgence rows remain
    open. Residual obstruction: convergence of the GV/BPS series and the
    global resurgent sheaf across all Stokes walls simultaneously
    (Conjecture~\ref{conj:bcov-np-quintic} and the following remark).
  \item Mirror-period recovery from the GV resummation
    (Conjecture~\ref{conj:mirror-period-recovery}): conjectural identity
    between the normalised genus-zero prepotential and the CDGP 1991
    period integral $\varpi_0 \varpi_3 - \varpi_1 \varpi_2$; the local
    fixture supports only the first three scalar table entries, while the
    CDGP and historical source mirrors remain open.
\end{enumerate}

Theorem-grade statements are restricted to the DT/PT
factorisation, the normal-bundle orientation/triviality statement, the
Serre functor and pairing, and the isotropic Fourier--Mukai equivalence.
Item~(3) conditionally extends the quintic chiral-volume data through
$N = 10$ and exhibits finite numerical compatibility on
\[
  L \approx 7.59 \approx |t(z_c)|,
\]
against the raw CDGP-formula period ratio. The CDGP source convention,
OSV attractor rate, and Abel--Jacobi normalisation remain source/gap
obligations.
Items~(1)'s \(\E_2\)-centre package, (2)'s chain-level framing, (3)'s
large-\(N\) limit, (4)'s quasi-NCCR descent, (6), and~(7) remain
conjectural or target data, sharpened against the present fixtures but
not upgraded to compact CY/global transfer.

\end{document}
