\providecommand{\Prim}{\operatorname{Prim}}
\providecommand{\Conn}{\operatorname{Conn}}

\section*{Local dictionary}
\addcontentsline{toc}{section}{Local dictionary}

\begingroup
\small
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.15}

\paragraph{Local Calabi--Yau/unimodularity datum.}
In the core local theorem surface, ``Calabi--Yau'' means only the
following formal orientation/unimodularity datum.  It is a definition,
not a compact-target hypothesis.
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Datum} & \textbf{Definition and force}\\
\hline
\endfirsthead
\hline
\textbf{Datum} & \textbf{Definition and force}\\
\hline
\endhead
\(\Omega_{\mathrm{loc}}\) &
The fixed holomorphic volume and symplectic form on the formal disk
\[
  \widehat{\C^2}_0=\operatorname{Spf}\C[[z_1,z_2]],
  \qquad
  \Omega_{\mathrm{loc}}=dz_1\wedge dz_2 .
\]
It trivializes the local canonical line and fixes the residue
orientation.  No compact manifold, no global moduli space, and no
threefold Hodge theory are part of the datum.\\
\hline
Poisson tensor and bracket &
The inverse bivector is
\[
  P=\partial_{z_1}\otimes\partial_{z_2}
    -\partial_{z_2}\otimes\partial_{z_1},
  \qquad
  \{f,g\}=\partial_{z_1}f\,\partial_{z_2}g
    -\partial_{z_2}f\,\partial_{z_1}g .
\]
Polynomial calculations use \(\bar A=\C[z_1,z_2]/\C\cdot1\); completed
CE/PV calculations use
\(\mathfrak h=\C[[z_1,z_2]]/\C\cdot1\).  Constants are removed because
they generate the zero Hamiltonian vector field.\\
\hline
Hamiltonian vector field &
The convention is
\[
  \iota_{X_f}\Omega_{\mathrm{loc}}=-df,\qquad
  X_f=(\partial_{z_1}f)\partial_{z_2}
      -(\partial_{z_2}f)\partial_{z_1}.
\]
Thus \(X_f(g)=\{f,g\}\) and
\([X_f,X_g]=X_{\{f,g\}}\) after projecting constants.\\
\hline
Unimodularity / divergence-free condition &
For a holomorphic vector field
\(X=a_1\partial_{z_1}+a_2\partial_{z_2}\),
\[
  \mathcal L_X\Omega_{\mathrm{loc}}
    =(\operatorname{div}_{\Omega_{\mathrm{loc}}}X)\Omega_{\mathrm{loc}},
  \qquad
  \operatorname{div}_{\Omega_{\mathrm{loc}}}X
    =\partial_{z_1}a_1+\partial_{z_2}a_2 .
\]
Every Hamiltonian vector field is divergence-free:
\[
  \operatorname{div}_{\Omega_{\mathrm{loc}}}X_f
  =-\partial_{z_1}\partial_{z_2}f
    +\partial_{z_2}\partial_{z_1}f=0 .
\]
Conversely, on the formal disk the holomorphic Poincare lemma identifies
\(\Ker(\partial_{\Omega_{\mathrm{loc}}}\colon\mathrm{PV}^1\to
\mathrm{PV}^0)\) with Hamiltonians modulo constants.  This is the
unimodularity assertion used in the paper.\\
\hline
Closed BV pairing &
For the Hamiltonian BF fields
\[
  \Omega^\bullet(\R^2)\widehat\otimes\Omega^{0,\bullet}(\C^2)
  \widehat\otimes
  \bigl(\mathfrak h[1]\oplus
  \mathfrak h^\vee_{\mathrm{cont}}[2]\bigr),
\]
the BV pairing is the compactly supported local pairing obtained by
wedging the form factors, integrating against
\(\Omega_{\mathrm{loc}}\), and applying the continuous evaluation
\(\mathfrak h^\vee_{\mathrm{cont}}\otimes\mathfrak h\to\C\).  It has
degree \(-1\).  This abstract pairing is not a Costello coefficient
coevaluation kernel unless a Tate/weighted category makes the Casimir
converge.\\
\hline
Residue / cyclic trace density &
The same orientation fixes the principal-part residue pairing
\[
  \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2,\qquad
  \operatorname{Res}_0(\rho_{a,b}z_1^mz_2^n)
    =\delta_{a,m}\delta_{b,n},
\]
with \(a+b>0\) in the reduced cotangent module.  Hamiltonian vector
fields preserve \(dz_1dz_2\), so residue integration by parts gives the
coadjoint action.  On the open brane, the top Ext class is the residue
orientation dual to \(dz_1\wedge dz_2\), and the cyclic trace is
\[
  \operatorname{Tr}_{\mathrm{open}}(\eta\otimes u\otimes M)
  =\int_\R\eta\,[\varepsilon_1\varepsilon_2]u\,
    \operatorname{Tr}_N(M).
\]\\
\hline
Difference from compact CY\(_3\) BCOV &
BCOV supplies source conventions: Dolbeault polyvectors, divergence from
a volume form, and cotangent BV language.  It is not a theorem input for
the local \(2_{\R}+2_{\C}\) Hamiltonian surface model.  The local datum is
only \((\widehat{\C^2}_0,dz_1\wedge dz_2)\) with its Hamiltonian Lie
algebra, continuous cotangent module, BV pairing, and residue/cyclic
trace.\\
\hline
\end{longtable}

\paragraph{Admissible and inadmissible uses.}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Use} & \textbf{Status}\\
\hline
\endfirsthead
\hline
\textbf{Use} & \textbf{Status}\\
\hline
\endhead
Admissible &
Use \(\Omega_{\mathrm{loc}}\) to define
\(\partial_{\Omega_{\mathrm{loc}}}\), the Poisson bracket, Hamiltonian
vector fields modulo constants, the local BF action, the degree \(-1\)
BV pairing, residue principal parts, Ext orientation, cyclic traces, and
integration-by-parts/coadjoint formulas.\\
\hline
Admissible with proof &
Use a global holomorphic symplectic surface only after reducing to a
formal Darboux neighbourhood and recording the period obstruction to
global Hamiltonian primitives.  Use a Costello graph/QME theorem only
after supplying the elliptic parent, gauge fixing, convergent coefficient
kernel, counterterm scheme, and brane-defect wavefront rules.\\
\hline
Inadmissible &
Do not import compact Calabi--Yau threefold hypotheses, compact Hodge
theory, compact-CY chiral homology, unproved one-dimensional
vertex-algebra structure, period integrals, holomorphic anomaly equations,
Gromov--Witten or Gopakumar--Vafa expansions, MNOP/PT/DT comparisons,
quintic computations, OSV/GV, Abel--Jacobi or normal-function claims,
CoHA structures, Igusa products, Borcherds lifts, BKM algebras, or Vol
III comparison theorems into the core local SFT.\\
\hline
Inadmissible &
Do not infer a compact BCOV theorem, Costello--Li anomaly cancellation,
ordinary \(\lie{gl}_N\) QME cancellation, radial-parts theorem,
finite-\(N\) trace normalization, or non-scalar closed-open
factorization-centre morphism from the word ``Calabi--Yau''.  Each such
claim requires its own matched-conventions theorem and its own
obstruction calculation.\\
\hline
\end{longtable}

\paragraph{Local chiral/factorization taxonomy.}
In this manuscript the word ``chiral'', when it is used informally, means
the constructed local Hamiltonian chiral/factorization object below, or
one of its mixed, brane, or current avatars.  The construction is present;
the missing extra theorem, if desired, is only the extraction of a
one-complex-dimensional vertex/OPE algebra from it.  The word never means
a compact Calabi--Yau chiral homology object, a CoHA, a quintic/GV/OSV
structure, or a Borcherds--Kac--Moody denominator unless a separate
matched-conventions theorem supplies that target.
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Object} & \textbf{Definition and exclusions}\\
\hline
\endfirsthead
\hline
\textbf{Object} & \textbf{Definition and exclusions}\\
\hline
\endhead
Formal Hamiltonian holomorphic factorization algebra on \(\C^2\) &
The constructed local chiral/factorization algebra is
\[
  \mathcal F_{\mathrm{Ham}}^{\mathrm{hol}},
\]
the formal-disk Hamiltonian BF object on
\((\widehat{\C^2}_0,dz_1\wedge dz_2)\).  For a holomorphic polydisk
\(B\) its dg Lie input is
\[
  \Omega^{0,\bullet}_c(B)\widehat\otimes
  \mathfrak g,\qquad
  \mathfrak g=\mathfrak h\ltimes
  \mathfrak h^\vee_{\mathrm{cont}}[1],
  \quad
  \mathfrak h=\C[[z_1,z_2]]/\C\cdot1 ,
\]
with differential \(\bar\partial\) plus the Hamiltonian BF differential.
The formal stalk of observables is the completed CE/PV object
\[
  C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
  \simeq
  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})
\]
only in the coordinate/admissible sense recorded below.  This is a
two-complex-dimensional holomorphic factorization algebra in the
manuscript's local sense of ``chiral''.  It is not yet the
one-complex-dimensional vertex-algebra specialization.\\
\hline
Mixed topological-current enhancement over \(\R^2\) &
For a topological open \(U\subset\R^2_{\mathrm{top}}\) and holomorphic
polydisk \(B\subset\C^2_{\mathrm{hol}}\), the mixed current input is
\[
  \mathfrak g^{\mathrm{mix}}_{U,B}
  =
  \Omega^\bullet_c(U)\widehat\otimes
  \Omega^{0,\bullet}_c(B)\widehat\otimes
  (\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1]).
\]
Its observables are locally constant in \(U\) and holomorphic in \(B\).
The brane-line current algebras below are the support-local
one-real-dimensional restrictions of this mixed topological current
object.  They are not compact-CY chiral homology and not a VOA obtained
from a complex curve.\\
\hline
Weyl/Moyal open-string brane algebra and cyclic avatars &
The degree-zero quantum brane target is the Weyl/Moyal deformation of the
formal symplectic disk.  Put
\[
  P=\partial_{z_1}\otimes\partial_{z_2}
   -\partial_{z_2}\otimes\partial_{z_1}.
\]
Then
\[
  \begin{aligned}
  f*g&=m\circ\exp\!\left(\frac{\hbar}{2}P\right)(f\otimes g),\\
  \{f,g\}_\hbar&=\hbar^{-1}(f*g-g*f),
  \end{aligned}
\]
with constants quotiented in the Hamiltonian Lie algebra
\(\bar A_\hbar\).  At finite \(N\) the open avatar is the matrix Weyl
algebra generated by \((\phi_1)^i{}_j,(\phi_2)^k{}_l\) with
\[
  [(\phi_1)^i{}_j,(\phi_2)^k{}_l]
  =\hbar\,\delta^i_l\delta^k_j ,
\]
followed by the quantum moment-map reduction and the connected trace
projection.  Cyclic and supercyclic bar-cobar avatars are trace or
supertrace word complexes for matrix or supermatrix branes; they are not
CoHA objects, compact-CY chiral homology, or BKM denominator data.\\
\hline
Defect/principal-part current algebra &
For an interval \(I\subset\R_{\mathrm{brane}}\),
\[
  \mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h,\qquad
  \mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mathcal P,\qquad
  \mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1],
\]
where
\[
  \mathcal P=\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
  \subset H^2_{\mathfrak m}(\C[[z_1,z_2]])\,dz_1dz_2 .
\]
The reduced target is
\[
  A^{\mathrm{pp}}_\partial(I)=
  \widehat{\mathbf S}(\Omega_c^0(I)\widehat\otimes\bar A)
  \widehat\otimes
  \widehat{\mathbf S}(\mathcal D'_c(I)\widehat\otimes\mathcal P[1]),
\]
with brackets
\[
  \begin{aligned}
  \{B_f(a),B_g(b)\}&=B_{\{f,g\}}(ab),\\
  \{B_f(a),\Theta_\rho(B)\}&=\Theta_{f\cdot\rho}(aB),\\
  \{\Theta_\rho(B),\Theta_\sigma(C)\}&=0 .
  \end{aligned}
\]
This is a support-local real-current \(P_0\) algebra with Matlis
principal parts in two holomorphic variables.  It is not the singular OPE
algebra of a one-dimensional vertex algebra.\\
\hline
One-dimensional vertex/OPE restriction boundary &
The constructed local chiral/factorization algebra above does not require
the following data.  They are necessary only for the stronger assertion
that it has been restricted to a one-complex-dimensional vertex/OPE
algebra.  Such a restriction requires extra datum
\[
  \mathfrak R_L
  =
  (\iota_L,\mathcal B_\perp,\mathsf R_{L,\mathcal B_\perp},
   V_L,\mathbf 1_L,T_L,Y_L,\zeta_{L,\hbar}),
\]
where
\(\iota_L\colon L=\operatorname{Spf}\C[[w]]
\hookrightarrow\widehat{\C^2}_0\) is a chosen holomorphic line or defect
germ, \(\mathcal B_\perp\) is a transverse boundary condition or normal
vacuum, and \(\mathsf R_{L,\mathcal B_\perp}\) is a restriction functor
producing a
one-complex-dimensional holomorphic factorization algebra
\[
  \mathcal F_{L,\mathcal B_\perp}(D)
  =
  \mathsf R_{L,\mathcal B_\perp}(\mathcal F_{\C^2})(D)
\]
for disks \(D\subset L\).  The functor must be built from a specified
tubular-neighbourhood, shriek/star restriction, or defect-coupling
construction, and must prove independence of the auxiliary transverse
radius, functoriality for disjoint disks, and translation covariance along
the coordinate \(w\).  The tuple also includes the restricted state
space \(V_L\), vacuum, translation, state-field map, and Zhu/zero-mode
map.  In the \(\C\times\R\) interface used below, such a generic \(V_L\)
datum is admissible only when it factors through
\(\mathcal R_{\C\times\R}\) and is identified with
\(V_{\mathrm{red}}\) in \(\mathfrak I_{\mathrm{ch}}\).  The present
formal \(\C^2\) Hamiltonian data
construct \(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}\) and its mixed
current avatars, but they do not choose \(L\), \(\mathcal B_\perp\), or
\(\mathsf R_{L,\mathcal B_\perp}\).\\
\hline
OPE data for a restricted curve object &
After such a restriction one must construct
\[
  V_L=H^\bullet(\mathcal F_{L,\mathcal B_\perp}(\Delta_0)),
  \qquad
  Y_L(a,w)b=\sum_{n\in\Z}(a_{(n)}b)\,w^{-n-1}.
\]
The factorization product for two disks centered at \(w\) and \(0\) must
have a finite-pole expansion
\[
  \mu_{w,0}(a\boxtimes b)
  \sim
  \sum_{n\ge0}(a_{(n)}b)\,w^{-n-1}
  +\mu^{\mathrm{reg}}_{w,0}(a,b),
\]
with \(a_{(n)}b=0\) for \(n\gg0\), a vacuum
\(\mathbf 1_L\), translation
\([T_L,Y_L(a,w)]=\partial_wY_L(a,w)\), and locality
\[
  (w_1-w_2)^N
  [Y_L(a,w_1),Y_L(b,w_2)]=0
\]
for \(N\gg0\).  These Laurent modes and finite singular orders are not
part of the two-complex-dimensional holomorphic factorization algebra or
of the real interval current algebra.\\
\hline
Compatibility with the Weyl/Moyal brane algebra &
A one-dimensional vertex/OPE restriction must also specify how the
degree-zero brane algebra acts on the restricted object.  Equivalently it
must supply a continuous Zhu/zero-mode map
\[
  \zeta_{L,\hbar}\colon
  (\bar A_\hbar,*)\longrightarrow \operatorname{Zhu}(V_L)
\]
or fields \(J_f(w)\) satisfying
\[
  J_f(w)J_g(0)
  \sim
  \frac{\kappa_L(f,g)}{w^2}
  +
  \frac{J_{\{f,g\}_\hbar}(0)}{w},
\]
with the central level \(\kappa_L\) specified, and on the cotangent
current sector
\[
  [J_{f,(0)},\Theta_\rho]
  =
  \Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}.
\]
Equivalently,
\(\zeta_{L,\hbar}(f*g)=\zeta_{L,\hbar}(f)\zeta_{L,\hbar}(g)\).
The existing Weyl/Moyal calculation supplies \(f*g\) and the reduced
interval-current brackets only; it does not supply \(\zeta_{L,\hbar}\),
the fields \(J_f(w)\), the central level, or the OPE singular expansion.\\
\hline
Constructed chiral algebra interface tuple &
An externally constructed curve chiral algebra may enter this manuscript
only as the reduced vertex object \(V_{\mathrm{red}}\) in
\[
  \mathfrak I_{\mathrm{ch}}
  =
  (\mathcal R_{\C\times\R},
   \mathcal F_{\mathrm{red}},
   V_{\mathrm{red}},
   Q_{\mathrm{BRST}},
   \mathbf 1,T,Y,
   \operatorname{wt},
   \zeta_{\hbar},
   H_{\mathrm{anom}}).
\]
Here \(\mathcal R_{\C\times\R}\) is a controlled pushforward to
\(\R_t\times\C_{z_1}\) retaining the \(z_2\)-mode or the full two-index
principal-part coefficient system
\[
  \mathfrak h_{\mathrm{red}}=\C[[z_1]][[z_2]]/\C\cdot1,\qquad
  \mathcal P_{\mathrm{red}}\subset
  H^2_{(z_1,z_2)}(\C[[z_1,z_2]])\,dz_1dz_2 .
\]
\(\mathcal F_{\mathrm{red}}\) denotes the resulting pushed-forward
factorization algebra on \(\R_t\times\C_{z_1}\); until the reduction
obstruction vanishes it is a theorem target, not native \(\C^2\) data.
The interface must prove the pushed-forward bracket, BV pairing, brane
image, factorization-to-vertex package, BRST nilpotence, Zhu/zero-mode
map, Capelli normalization, Moyal multiplicativity, the completed stable
Hochschild/HKR/CE-PV comparison, and anomaly transport.  Its exact
obstruction vector is
\[
  \operatorname{Ob}_{\mathfrak I_{\mathrm{ch}}}
  =
  (\operatorname{Ob}_{\mathrm{red}},
   \operatorname{Ob}_{\mathrm{vert}},
   \operatorname{Ob}_{\mathrm{Zhu}},
   \operatorname{Ob}_{\mathrm{nat}}).
\]
Before this datum is supplied, a curve VOA or Zhu assertion is false
transfer.  After it is supplied, \(V_{\mathrm{red}}\) is still a reduced
shadow of \(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}\), not the native
\(\C^2\) holomorphic factorization algebra.\\
\hline
\end{longtable}

\paragraph{Normal \(\Omega\)-background theorem surface.}
This block is the dictionary for the brane-preserving equivariant
deformation.  It is a theorem surface: it records the objects and the
identities that must be constructed in the mixed de Rham/Dolbeault
coefficient category.  It is not a Costello graph/QME theorem and does
not produce physical trace-state asymptotics.
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Object or convention} & \textbf{Definition and force}\\
\hline
\endfirsthead
\hline
\textbf{Object or convention} & \textbf{Definition and force}\\
\hline
\endhead
Ambient pair and fixed stratum &
The local pair is
\[
  X=\R^2_{t,s}\times\C^2_{z_1,z_2},\qquad
  L=\R_t\times\{s=z_1=z_2=0\}.
\]
The normal bundle of the brane line is
\[
  N_LX=\R_s\oplus\C_{z_1}\oplus\C_{z_2}.
\]
The \(\Omega\)-background used here is normal scaling of this bundle with
\(t\) fixed.  A literal rotation in the \((t,s)\)-plane is not native to
this brane problem because it does not leave \(L\) as the fixed line.\\
\hline
Equivariant parameters &
Write
\[
  T_\Omega
  =\C^*_{\epsilon_s}\times
   \C^*_{\epsilon_1}\times
   \C^*_{\epsilon_2}.
\]
The parameters \(\epsilon_s,\epsilon_1,\epsilon_2\) are equivariant
weights.  They are not the Ext generators
\(\varepsilon_1,\varepsilon_2\) used in the open trace orientation.
The action is
\[
  (s,z_1,z_2)\mapsto
  (\lambda_s s,\lambda_1z_1,\lambda_2z_2),
  \qquad t\mapsto t .
\]
Its infinitesimal vector field is
\[
  V_\Omega
  =
  \epsilon_s s\partial_s
  +\epsilon_1 z_1\partial_{z_1}
  +\epsilon_2 z_2\partial_{z_2}.
\]\\
\hline
Equivariant differential &
The Cartan differential on the local mixed complex is
\[
  Q_\Omega=Q+\iota_{V_\Omega},\qquad
  Q_\Omega^2=L_{V_\Omega}.
\]
Thus \(Q_\Omega\) is an honest differential on the
\(T_\Omega\)-invariant subcomplex.  Away from invariants the correct
object is the \(T_\Omega\)-equivariant curved/Cartan package with
curvature \(L_{V_\Omega}\), not an ordinary dg complex with
\(Q_\Omega^2=0\).\\
\hline
Normal-weight localization ring &
For a finite \((N,M)\)-window let \(\mathsf X_{N,M}\) be the finite set
of nonzero moving characters that occur in that window.  It contains the
normal Hamiltonian and residue-dual characters
\[
  n\epsilon_s+a\epsilon_1+b\epsilon_2,\qquad
  n\epsilon_s-a\epsilon_1-b\epsilon_2
\]
whenever the corresponding moving summands occur.  The localized
coefficient ring is
\[
  R_\Omega^{N,M}
  =
  \C[\epsilon_s,\epsilon_1,\epsilon_2,\hbar_\omega]
  [\chi^{-1}\mid \chi\in\mathsf X_{N,M}].
\]
Equivalently, one inverts only the nonzero weights present in the finite
normal window.  This is the algebraic habitat in which moving normal
modes may be contracted.  There is no default inversion of
\(\epsilon_s\epsilon_1\epsilon_2\) unless the Euler-localization branch
has been declared.  The self-dual branch is a specialization with its own
allowed inversions; base-change first, then invert only the surviving
nonzero characters, so \(\epsilon_1+\epsilon_2\) is not inverted on the
self-dual branch.\\
\hline
Normal contraction datum &
The stronger theorem surface is the construction of a localized
deformation retract
\[
  \mathsf C_\Omega=(\pi_L,j_L,h_\Omega)
  \colon
  \mathcal E_\Omega(X)
  \rightleftarrows
  \mathcal E_\Omega(L)
\]
for the mixed de Rham/Dolbeault coefficient complex, with
\[
  \pi_Lj_L=\operatorname{id},
  \qquad
  Q_\Omega h_\Omega+h_\Omega Q_\Omega
  =\operatorname{id}-j_L\pi_L
\]
on the localized invariant normal complex.  On a homogeneous normal
summand of nonzero weight \(\lambda\), \(h_\Omega\) is the Euler/Koszul
homotopy divided by \(\lambda\), with signs fixed by the de Rham degree
in the \(s\)-direction and the Dolbeault degree in the \(z_i\)-directions.
The present dictionary records this contraction datum as required data;
it does not assert that the Costello propagator and counterterms have
already been transported through it.\\
\hline
Hamiltonian and cotangent weights &
For \(H_{a,b}=z_1^az_2^b\), \(a+b>0\),
\[
  w(H_{a,b})=a\epsilon_1+b\epsilon_2.
\]
For the principal-part residue basis,
\[
  \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2,
  \qquad
  w(\rho_{a,b})=-a\epsilon_1-b\epsilon_2 .
\]
The holomorphic symplectic character is
\[
  \chi_\omega=\epsilon_1+\epsilon_2,
  \qquad
  w(dz_1\wedge dz_2)=\chi_\omega,
  \qquad
  w(P)=-\chi_\omega .
\]
The Weyl/Moyal deformation parameter, when present, has
\[
  w(\hbar_{\mathrm{W}})=\chi_\omega.
\]\\
\hline
Three \(\hbar\)-parameters &
The Omega convention distinguishes three formal parameters:
\[
  \hbar_{\mathrm{QME}},\qquad
  \hbar_{\mathrm{W}},\qquad
  \hbar_\omega .
\]
Here \(\hbar_{\mathrm{QME}}\) is the Costello/BV loop-counting parameter
in graph and curvature equations; \(\hbar_{\mathrm{W}}\) is the
Weyl/Moyal deformation parameter in the open brane algebra; and
\(\hbar_\omega\) is the equivariant line parameter of weight
\(\chi_\omega\) used to scalarize the Poisson bracket.  A Weyl branch may
identify \(\hbar_{\mathrm{W}}=\hbar_\omega\).  No branch identifies
\(\hbar_{\mathrm{QME}}\) with either parameter unless the theorem states
that convention explicitly.\\
\hline
Self-dual bracket &
On the self-dual locus
\[
  \epsilon_1+\epsilon_2=0
\]
the Poisson tensor has weight \(0\).  The Hamiltonian bracket
\(\{f,g\}\) is then a scalar \(T_\Omega\)-equivariant Lie bracket on
\(\mathfrak h\) after quotienting constants.\\
\hline
Refined bracket off the self-dual locus &
Off the self-dual locus the ordinary Poisson bracket has weight
\[
  w(\{f,g\})=w(f)+w(g)-(\epsilon_1+\epsilon_2).
\]
It is therefore a bracket valued in the inverse symplectic-character
line.  The scalar refined bracket is obtained only after adjoining the
line parameter \(\hbar_\omega\) of weight
\(w(\hbar_\omega)=\epsilon_1+\epsilon_2\):
\[
  [f,g]_\Omega=\hbar_\omega\{f,g\}.
\]
In the Weyl/Moyal specialization one may identify
\(\hbar_\omega\) with the deformation parameter
\(\hbar_{\mathrm{W}}\).  Without this line or parameter, the refined
Hamiltonian algebra is line-valued, not the old scalar Hamiltonian Lie
algebra.\\
\hline
Equivariant CE/PV generator rule &
The equivariant CE/PV theorem surface keeps the same generator labels
\[
  c_{a,b}\mapsto\theta_{a,b},\qquad
  u_{a,b}\mapsto O_{a,b},
\]
but all differentials and brackets are read in the \(T_\Omega\)-graded
completed coordinate habitat.  In the refined convention the contraction
bracket and the \(d_\pi\)-terms carry the factor \(\hbar_\omega\).  In the
self-dual convention this factor has weight \(0\) and may be suppressed.\\
\hline
Equivariant quantum brane algebra &
The degree-zero open quantum brane target is the equivariant Hamiltonian
reduction
\[
  A^q_{N,\Omega}
  =
  \operatorname{Weyl}_{\hbar_{\mathrm{W}}}(\operatorname{Mat}_N^2)
  //_{\hbar_{\mathrm{W}}} GL_N,
  \qquad
  YX-XY+\hbar_{\mathrm{W}}NI=0,
\]
with
\[
  w(X)=\epsilon_1,\qquad
  w(Y)=\epsilon_2,\qquad
  w(\hbar_{\mathrm{W}})=\epsilon_1+\epsilon_2.
\]
The moment-map equation is weight homogeneous.  Its scalar \(U(1)\)
contact term is the same Capelli line as in the non-equivariant
dictionary, now graded by \(\epsilon_1+\epsilon_2\).\\
\hline
Residue normalization &
The residue convention uses the formal residue orientation
\[
  \operatorname{Res}_{z_1=z_2=0}
  \bigl(z_1^{-1}z_2^{-1}dz_1dz_2\bigr)=1
\]
and the open top Ext coefficient
\([\varepsilon_1\varepsilon_2]\).  Its normalization constant is
\[
  \nu_\Omega^{\mathrm{res}}=1.
\]
In this convention the brane trace is
normalized by the residue/cyclic density and no smooth normal Euler
denominator is silently inserted.  Any \(\epsilon_s\epsilon_1\epsilon_2\)
factor must be written explicitly as a comparison constant.\\
\hline
Euler-localization normalization &
The smooth equivariant localization convention pushes from \(X\) to \(L\)
with the inverse normal Euler class
\[
  e_{T_\Omega}(N_LX)^{-1}
  =
  (\epsilon_s\epsilon_1\epsilon_2)^{-1},
\]
up to the orientation sign \(\sigma_s\) fixed by the chosen real
\(s\)-density and the complex orientation \(dz_1\wedge dz_2\).  Its
normalization constant is
\[
  \nu_\Omega^{\mathrm{Eu}}
  =
  \sigma_s(\epsilon_s\epsilon_1\epsilon_2)^{-1}.
\]
A theorem comparing this
convention with the residue convention must state the sign and the exact
factor.  Until then the two normalizations are separate branches.\\
\hline
Stratified factorization datum &
The brane-localized object is a stratified mixed HT factorization datum
on the pair \((X,L)\),
\[
  \mathcal F^{\mathrm{str}}_\Omega(X,L)
  =
  \bigl(\mathcal F_{\Omega,X\setminus L},
        \mathcal F_{\Omega,L},
        \mathcal M_{\Omega,L},
        j^*,i^!,\mu_{\mathrm{str}}\bigr),
\]
where the open stratum is the \(T_\Omega\)-equivariant mixed bulk
factorization algebra, the closed stratum is the brane-line current
object, and \(\mathcal M_{\Omega,L}\) is the defect module.  Protected
observables become stratified factorization-homology traces only after
the brane-defect QME and the trace-state normalization are supplied.\\
\hline
Open obstruction vector &
The residual theorem obligations are recorded as
\[
  \begin{aligned}
  \operatorname{Ob}_\Omega
  &=
  \bigl(\operatorname{ob}_{\Omega,\mathrm{Cartan}},
        \operatorname{ob}_{\Omega,\mathrm{contr}},\\
  &\qquad
        \operatorname{ob}_{\Omega,\mathrm{CE/PV}},
        \operatorname{ob}_{\Omega,\mathrm{norm}},\\
  &\qquad
        \operatorname{ob}_{\Omega,\mathrm{strat}},
        \operatorname{ob}_{\Omega,\mathrm{QME}},\\
  &\qquad
        \operatorname{ob}_{\Omega,N\to\infty}\bigr).
  \end{aligned}
\]
These name, respectively, the mixed Cartan model, the localized normal
contraction, the equivariant CE/PV bracket comparison, the
residue-versus-Euler normalization theorem, the stratified factorization
structure, the Costello brane-defect graph/QME package, and the physical
large-\(N\) trace-state theorem.\\
\hline
\end{longtable}

\paragraph{Canonical maps and obstruction symbols.}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\endfirsthead
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\endhead
\(\Phi_{\mathfrak l}\) &
Finite-dimensional cotangent CE/PV map
\[
  C^\bullet_{\mathrm{CE}}
  (\mathfrak l\ltimes \mathfrak l^\vee[1])
  \to \mathrm{PV}(\mathbf S(\mathfrak l)),
  \qquad c\mapsto\theta,\quad u\mapsto O .
\]\\
\hline
\(\Phi_{\mathrm{coord}}\) &
Formal-disk coordinate CE/PV map reconstructed from admissible finite
coordinate tests and pro-window coordinate cochains for
\(\mathfrak h=\C[[z_1,z_2]]/\C\cdot1\) and
\(\mathfrak g=\mathfrak h\ltimes
\mathfrak h^\vee_{\mathrm{cont}}[1]\).  It is a completed coordinate dg
commutative algebra isomorphism before any \(P_0\) bracket is asserted.\\
\hline
\(\Phi^B_{P_0}\) &
Restriction of \(\Phi_{\mathrm{coord}}\) to a bracket-admissible
subalgebra \(B\subset
\mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\):
\[
  \Phi^B_{P_0}\colon\Phi_{\mathrm{coord}}^{-1}(B)\xrightarrow{\sim}B .
\]
This is the completed \(P_0\) comparison only because \(B\) carries a
specified complete Hausdorff topology, continuous inclusion in the
coordinate product, continuous multiplication, continuous
\(d_\pi^{\mathrm{coord}}\), and a continuous closed contraction bracket.
Boundary Hamiltonians inside this \(P_0\) comparison require the relevant
\(O_f\) and \(d_\pi^{\mathrm{coord}}O_f\) to lie in \(B\).\\
\hline
\(\Theta_B\) &
Kernel-admissible Maurer--Cartan tensor in a specified completed
convolution dg Lie algebra \(\mathcal K_B\)
\[
  \Theta_B=\sum_I H_I\otimes\theta^I+\sum_I\eta^I\otimes O_I
\]
attached to \(B\).  It is asserted only when the displayed diagonal sums
converge and the convolution differential and bracket are continuous in
\(\mathcal K_B\).\\
\hline
\(\eta^I\) &
Shifted cotangent generator
\(\eta^I=(H_I)^\vee[1]\in\mathfrak h^\vee_{\mathrm{cont}}[1]\), for
\(I=(a,b)\) and \(a+b>0\).  It is the source of the \(O_I\) coordinate in
the CE/PV map.\\
\hline
\(\mathfrak U_{\mathfrak h}\) &
Admissible formal-local interface datum, not a categorical universal
object unless a category of admissible completions and a universal
property are supplied,
\[
  \mathfrak U_{\mathfrak h}
  =(\Phi_{\mathrm{coord}},\{\Phi^B_{P_0}\}_B,\{\Theta_B\}_B),
\]
where \(B\) ranges over bracket-admissible subalgebras in the middle term
and kernel-admissible data in the last term.\\
\hline
\(B_{\mathrm{fin}},E_q\) &
Model admissibility tests.  \(B_{\mathrm{fin}}\) is the finite-support
coordinate subalgebra on a finite window.  \(E_q\), for \(q>1\), is the
weighted Köthe test target with seminorms
\[
  p_n(x)=\sup_{a,b}|x_{a,b}|q^{a+b}(1+a+b)^n .
\]
It is bracket-admissible only after the finite-word tensor convention
and the corresponding convolution estimate are fixed; it is
kernel-admissible only if the diagonal tensor converges.\\
\hline
\(\mathfrak o^{\mathrm{br}},
  \mathfrak o^{\mathrm{coad}}\) &
Transition obstruction terms for bracket and coadjoint compatibility in
the pro/mixed coordinate CE/PV comparison.\\
\hline
\(\mathfrak o^{\mathrm{Cas}}\) &
Strict product/direct-sum kernel obstruction for the Casimir,
propagator, and Costello endpoint problem. It is not part of the
coordinate CE/PV identity.\\
\hline
\(\mathfrak o_{\mathrm{BV,end}}\) &
Endpoint obstruction tuple
\((\mathfrak o_{\mathrm{Cas}},
  \mathfrak o_{\mathrm{def}},
  \mathfrak o_{\mathrm{RG}},
  \mathfrak o_{\mathrm{QME}})\) controlling a Costello-compatible
coefficient endpoint.\\
\hline
\(\operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}}\) &
Matched-conventions descent vector
\((\operatorname{per}_{\mathrm{tar}},
  \operatorname{ob}_{\mathrm{WR}},
  \operatorname{ob}_{\mathrm{anom}},
  \operatorname{ob}_{\mathrm{QME}},
  \operatorname{ob}_{\mathrm{conv}},
  \operatorname{ob}_{\mathrm{hyp}},
  \operatorname{ob}_{6r},
  \operatorname{ob}_{\mathrm{MD}})\), with target-specific Vol III,
Igusa/BKM, or sister-volume components appended when such a target is
claimed.\\
\hline
\end{longtable}

\paragraph{Non-scalar Costello/QME dictionary.}
The entries in this block are the local obstruction habitat for
Problem~\ref{prob:quantum-p0-operation-realization}.  A scalar-symbol
map is associated-graded data.  A scalar-contact projection is a
filtered chain map.  Reduced principal-part brackets live after
de Rham-current contraction.  A non-scalar Costello graph realization is
the unreduced QME equation below.
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol or datum} & \textbf{Meaning}\\
\hline
\endfirsthead
\hline
\textbf{Symbol or datum} & \textbf{Meaning}\\
\hline
\endhead
\(\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\) &
Filtered brane-defect local-functional complex
\[
  \varprojlim_M
  \left(
    \mathcal O_{\mathrm{loc}}^{\mathrm{bd}}\bigl(
      \mathcal E_w^M|_I;
      A_{\partial,\hbar}^{\mathrm{pp},w,M}(I)\bigr),
    d_M
  \right),
  \qquad d_M=Q+\{I^w_{0,M},-\}_{\hbar,M}.
\]
The inverse limit is taken over finite Hamiltonian windows with the
\(\hbar\)-adic, scalar-contact, and finite-window filtrations.  The
differential has degree \(+1\).  This is the target habitat for the
bulk-to-defect kernel and QME obstruction; it is not the reduced current
algebra \(A_{\partial,\hbar}^{\mathrm{pp},w}(I)\).\\
\hline
\(F^\bullet\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\) &
Complete decreasing closed scalar-contact filtration preserved by
\(d_{\mathrm{QME}}\).  In the ordinary scalar-reduced branch one may take
\(F^r=J_{\mathrm{sc}}^r\), where \(J_{\mathrm{sc}}\) is the closed ideal
of functionals with zero associated-graded scalar-contact symbol.  In the
balanced branch it is the closed filtration generated by
identity-endomorphism contractions inside the balanced scalar-contact
habitat.  Its role is to define the associated-graded scalar symbol and
the obstruction tower for lifting that symbol.\\
\hline
\(\sigma_{\mathrm{sc}}\) &
Associated-graded scalar-symbol extractor
\[
  \sigma_{\mathrm{sc}}\colon
  \operatorname{gr}_F\mathfrak Q^\bullet_{w,\partial,\hbar}(I)
  \longrightarrow
  C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]] .
\]
It has cochain degree \(0\), but it is not by itself a projection of the
filtered QME complex.  On a degree-one scalar contact with two
Hamiltonian inputs it records the Lie two-cocycle coefficient of
\(\gamma_{\mathbf 1}\).  In the ordinary branch this leading symbol is
\(\hbar N[\bar c]\).\\
\hline
\(\widehat\sigma_{\mathrm{sc}}\) &
Actual scalar-contact projection: a continuous filtered degree-\(0\)
cochain map
\[
  \widehat\sigma_{\mathrm{sc}}\colon
  \mathfrak Q^\bullet_{w,\partial,\hbar}(I)
  \to
  C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]]
\]
whose associated graded is \(\sigma_{\mathrm{sc}}\).  It exists exactly
when the scalar-lift obstruction classes
\(o_{\sigma,w}^{(r)}(I)\) vanish successively with compatible
finite-window choices.  The residual non-scalar complex is defined only
after this map has been chosen.  On a balanced scalar-contact habitat the
proved projection is the zero chain map
\(\widehat\sigma_{\mathrm{bal,sc}}=0\).\\
\hline
\(o_{\sigma,w}^{(r)}(I)\) &
Successive scalar-contact lift obstruction.  For a filtered linear lift
\(s\) of \(\sigma_{\mathrm{sc}}\), the chain defect
\(\delta_s=d_{\mathrm{CE}}s-sd_{\mathrm{QME}}\) lowers \(F^\bullet\).
Its first nonzero part gives
\[
  o_{\sigma,w}^{(r)}(I)\in
  H^1\!\left(
    \operatorname{Hom}\bigl(
      \operatorname{gr}_F\mathfrak Q^\bullet_{w,\partial,\hbar}(I),
      C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]]
    \bigr)_{-r}
  \right).
\]
In the ordinary scalar-reduced \(\lie{gl}_N\) branch the first
two-input evaluation is
\(\hbar N\,\omega(f,g)\gamma_{\mathbf 1}\), nonzero on
\((f,g)=(z_1,z_2)\).\\
\hline
\(\mathfrak g^{w,\mathrm{cur}}_{\hbar,I}\) &
Current source for the unreduced non-scalar lift,
\[
  \bigl(\Omega^\bullet_c(I)\widehat\otimes\mathfrak h_{w,\hbar}\bigr)
  \ltimes
  \bigl(\mathcal D'_c(I)\widehat\otimes
  \mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}\bigr)[1].
\]
The topology is the completed current topology with the weighted
finite-window and \(\hbar\)-adic completions.  On CE coordinates,
\(c_{B,\rho}\) has degree \(1\) and
\(u_{a(t)dt\otimes f}\) has degree \(0\).  Before scalar reduction one
may replace the Hamiltonian source by the central-character source.\\
\hline
\(\kappa_{\hbar,w,I}\) &
Continuous bulk-to-defect kernel, equivalently a degree-\(0\)
Maurer--Cartan candidate in the completed convolution Lie algebra,
\[
  \kappa_{\hbar,w,I}\colon
  C^\bullet_{\mathrm{CE},\mathrm{cont}}
  (\mathfrak g^{w,\mathrm{cur}}_{\hbar,I})
  \longrightarrow
  \mathfrak Q^\bullet_{w,\partial,\hbar}(I),
\]
with generator values
\[
  u_{a(t)dt\otimes f}\mapsto B_f^{\mathrm{BV}}(a),
  \qquad
  c_{B,\rho}\mapsto\Theta_\rho^{\mathrm{BV}}(B).
\]
Its reduced image must recover \(B_f(a)\) and \(\Theta_\rho(B)\), but the
kernel itself lives before scalar reduction, before de Rham-current
contraction, and before replacing unreduced open observables by freely
adjoined current generators.\\
\hline
\(\operatorname{Ob}_{w,\partial,\hbar}\) &
Curvature cocycle of the bulk-to-defect kernel,
\[
  \operatorname{Ob}_{w,\partial,\hbar}
    =
  d_{\mathrm{QME}}\kappa_{\hbar,w,I}
  +\frac12[\kappa_{\hbar,w,I},\kappa_{\hbar,w,I}]_\hbar .
\]
It has QME degree \(1\).  The scalar branch first requires
\(\widehat\sigma_{\mathrm{sc}}(\operatorname{Ob}_{w,\partial,\hbar})=0\).
Only then does its residual class lie in the non-scalar complex.\\
\hline
\(\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}\) &
Residual non-scalar obstruction after the scalar-contact projection has
been constructed and the scalar component has been killed:
\[
  [\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]
  \in
  H^1\!\left(
    \ker\widehat\sigma_{\mathrm{sc}},
    d_{\mathrm{QME}}
  \right).
\]
This class is not defined from the scalar-symbol map alone and is not
killed by the reduced principal-part bracket formulas.\\
\hline
\(\mathcal Q^\bullet_{w,M}(I)\) &
Finite-window residual complex
\[
  \mathcal Q^\bullet_{w,M}(I)
    =
  \ker(\widehat\sigma_{\mathrm{sc},M})
  \subset
  \left(
    \mathcal O_{\mathrm{loc}}^{\mathrm{bd}}\bigl(
      \mathcal E_w^M|_I;
      A_{\partial,\hbar}^{\mathrm{pp},w,M}(I)\bigr),
    d_M
  \right).
\]
The bracket, interaction, and differential are the transported
finite-window structures supplied by the acceptance gate, not naive
truncations of the unweighted Hamiltonian bracket.\\
\hline
\(C_{n,M}\), \(C_{\Gamma,w}^{w_0}(\epsilon)\) &
Finite-window counterterms.  At order \(\hbar^n\),
\(C_{n,M}\in\mathcal Q^0_{w,M}(I)\) must satisfy
\[
  d_MC_{n,M}=-\mathfrak o^{\mathrm{ns}}_{n,M},
  \qquad
  \pi_{M,N}C_{n,M}=C_{n,N}.
\]
Graph representatives \(C_{\Gamma,w}^{w_0}(\epsilon)\) must also commute
with window truncation and weight transport.  They are degree-zero local
functionals; they are not arbitrary finite changes of the reduced current
target.\\
\hline
\(\mathfrak O^{\mathrm{ns}}_n\) &
Order-\(n\) finite-window obstruction vector
\[
  \mathfrak O^{\mathrm{ns}}_n
  =
  \bigl(([\mathfrak o^{\mathrm{ns}}_{n,M}])_M,\lambda_n\bigr),
\]
where the first component lies in
\(\varprojlim_MH^1(\mathcal Q^\bullet_{w,M}(I))\), and
\(\lambda_n\in\varprojlim\nolimits^1_M
H^0(\mathcal Q^\bullet_{w,M}(I))\) is the primitive-compatibility class.
Its vanishing is exactly the finite-window criterion for compatible
order-\(n\) counterterms.\\
\hline
\(\mathsf E_{\theta_3,M}\), \(C_{\theta_3,M}\) &
First certified larger-row non-scalar obstruction and its permitted
primitive.  In the supplied one-row package,
\[
  \mathcal Q^0_{\theta_3,M}=0,\qquad
  \mathcal Q^1_{\theta_3,M}=\C\mathsf E_{\theta_3,M},\qquad
  d_M=0,
\]
and the residual is \(\mathfrak o^{\mathrm{ns}}_{\theta_3,M}
=\mathsf E_{\theta_3,M}\).  The covector
\(\ell_{\theta_3}(\mathsf E_{\theta_3,M})=1\) proves that this class is
nonzero in the supplied subcomplex.  A valid \(C_{\theta_3,M}\) is not a
formal name: it must be one of three explicit witnesses,
\[
  K^M_{\Theta_3}(\eta_{\theta_3,M}),\qquad
  C^{\mathrm{ct}}_{\theta_3,M},\qquad
  \text{or a companion-face primitive,}
\]
with differential \(d_MC_{\theta_3,M}=-\mathsf E_{\theta_3,M}\),
scalar-contact value zero, and vanishing Roos compatibility class under
finite-window projection.\\
\hline
\(I_N,\eta,\chi_N\) &
Moment-ideal and scalar primitive data.  The quantum Hamiltonian
reduction uses the left moment-map ideal
\(I_N=\mathcal W_N\widehat\mu(\lie{sl}_N)\) and then removes the scalar
empty trace.  The scalar primitive lives on the unreduced Hamiltonian
source \(A=\C[z_1,z_2]\):
\[
  \eta(f)=-[f]_0,\qquad d_{\mathrm{CE}}\eta=\omega,\qquad
  \chi_N(f)=N[f]_0=-N\eta(f).
\]
Thus
\(\hbar N\omega+d_{\mathrm{CE}}(\hbar\chi_N)=0\) before scalar
reduction.  This primitive does not descend to
\(\bar A=A/\C\cdot1\) and is not a counterterm in the original
scalar-reduced QME complex.\\
\hline
\(E_{a,b,N}\), \(A^j{}_i(a,b,N)\) &
Quantum shear moment-ideal primitive datum in the matrix Weyl algebra.
Put
\[
  E_{a,b,N}
  =
  \sum_{j=0}^b\operatorname{Tr}(Y^jX^aY^{b-j})
  -
  J_N\!\left(
    \{z_1^{a+1}/(a+1),z_2^{b+1}\}_\hbar
  \right).
\]
The all-\(N\) shear congruence required for the radial/Weyl image is
equivalent to
\[
  E_{a,b,N}\in I_N
  \quad\Longleftrightarrow\quad
  E_{a,b,N}
    =
  \sum_{i,j}A^j{}_i(a,b,N)\widehat\mu^i{}_j
\]
for coefficients \(A^j{}_i(a,b,N)\in\mathcal W_N\).  This is a
degree-zero left-ideal primitive problem in the quantum moment-map ideal,
not the scalar CE primitive \(\eta\), not a scalar-contact projection,
and not a Costello QME counterterm.\\
\hline
Reduced principal-part brackets &
Target-side brackets in
\(A_{\partial,\hbar}^{\mathrm{pp},w}(I)\) after scalar reduction and
de Rham-current contraction:
\[
  \{B_f(a),B_g(b)\}_\hbar=B_{\{f,g\}_\hbar}(ab),\quad
  \{B_f(a),\Theta_\rho(B)\}_\hbar
    =\Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}(aB),
\]
\[
  \{\Theta_\rho(B),\Theta_\sigma(C)\}_\hbar=0 .
\]
They use multiplication of a distribution by a smooth test function,
never a product of two distributions.  They prove the reduced current
interface and do not supply Costello wavefront estimates, unreduced
centrality homotopies, or the non-scalar QME.\\
\hline
Unreduced non-scalar QME realization &
The full graph theorem is the construction of
\(\kappa_{\hbar,w,I}\) and compatible counterterms
\(C_{\hbar,w}\).  Put
\(K_{\hbar,w,I}=\kappa_{\hbar,w,I}+C_{\hbar,w}\).  The equation is
\[
  \operatorname{Curv}(K_{\hbar,w,I})
  =
  d_{\mathrm{QME}}K_{\hbar,w,I}
  +\frac12[K_{\hbar,w,I},K_{\hbar,w,I}]_\hbar
  =0.
\]
It requires the Costello finite-scale BV propagator and Laplacian,
locality and counterterm estimates, scalar-contact chain projection,
vanishing of \(\mathfrak O^{\mathrm{ns}}_n\) for every order, and
unreduced product and \(P_0\)-bracket homotopies against arbitrary open
observables.\\
\hline
\end{longtable}

\paragraph{Common local rings and quotients.}
\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\(R=\C[[z_1,z_2]]\) &
Complete local ring of the formal symplectic disk.\\
\hline
\(\mathfrak m=(z_1,z_2)\) &
Maximal ideal of functions vanishing at the brane point.\\
\hline
\(\mathfrak h=R/\C\cdot1\) &
Reduced Hamiltonian Lie algebra of the formal disk. Constants are
removed because they generate the zero Hamiltonian vector field.\\
\hline
\(\mathfrak g_{\mathrm{str}}\) &
Strict shifted cotangent Hamiltonian Lie algebra
\[
  \mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1].
\]
Its Hamiltonian side is a product completion and its cotangent side is
continuous dual/direct-sum in residue coordinates.  This is the
formal-local CE/PV object, but not by itself a Costello coefficient
kernel.\\
\hline
\(\mathfrak g_w\) &
Weighted finite-window Tate replacement used as a regulator.  It carries
the same coordinate-window CE/PV formulas after passage through the
admissible tower, but its weight topology is auxiliary data and is not
the strict cotangent completion.\\
\hline
\(\bar A=\C[z_1,z_2]/\C\cdot1\) &
Polynomial Hamiltonian sector used in explicit trace and Moyal
calculations.\\
\hline
\(\bar A_{\mathrm{desc}}\) &
Abstract polynomial label space for PBW one-\(\psi\) descendants. It
is not the Matlis principal-part module.\\
\hline
\([\bar c]\) &
Distinguished scalar \(U(1)\) anomaly class in
\(H^2_{\mathrm{Lie}}(\bar A,\C)\), realized by the constant term of the
Poisson bracket and by the Capelli shift.\\
\hline
\(N\) &
Rank of the brane probe stack. Degreewise stable trace statements are
formed at fixed total word degree and then for \(N\) in the stable range.\\
\hline
\(D\) &
Taylor truncation degree when a finite quotient
\(\mathfrak m/\mathfrak m^{D+1}\) is used. It is not the brane rank
\(N\).\\
\hline
\end{tabular}
\end{center}

\paragraph{Large-\(N\) and quotient conventions.}
\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol or operation} & \textbf{Meaning}\\
\hline
\(\operatorname{Prim}_{\mathrm{st}}\) &
Degreewise stable primitive invariant sector. In total word degree
\(d\), the Procesi--Razmyslov stable range is \(N\geq d\).\\
\hline
\(\operatorname{Conn}_{N\to\infty}\) &
Connected single-trace cumulant extraction after finite-\(N\)
normalization and passage to the stable range. It removes disconnected
products.\\
\hline
Hamiltonian scalar quotient &
The closed scalar \(1\in\C[z_1,z_2]\) and the open empty trace
\(\operatorname{Tr}_N(1)=N\) are omitted as primitive Hamiltonian
generators. The unit of the symmetric algebra remains.\\
\hline
\end{tabular}
\end{center}

\paragraph{Separation rule.}
The next three blocks are disjoint.  PBW special-fibre labels
\(H_{a,b},O_{a,b},\Psi_{a,b}\), CE/PV labels \(c^I,u_I,\theta^I,O_I\),
and Matlis labels \(\rho_{a,b}\) live in different modules unless a
specific theorem supplies a comparison.  The Fourier--Rees theorem
matches associated-graded labels after Fourier normalization through
the Fourier delta Rees lattice
\(\mathcal D_\hbar/(z_1,z_2)\).  Its \v{C}ech realization carries the
factor \((-1)^{a+b}\hbar^{a+b}a!b!\), so before \(\hbar\) is inverted
it is the Rees sublattice, and as a module statement it uses a
Fourier-twisted polarization rather than the original Hamiltonian
coadjoint action.

\paragraph{Source--target status table.}
\begin{longtable}{@{}>{\raggedright\arraybackslash}p{0.22\textwidth}
  >{\raggedright\arraybackslash}p{0.22\textwidth}
  >{\raggedright\arraybackslash}p{0.18\textwidth}
  >{\raggedright\arraybackslash}p{0.28\textwidth}@{}}
\hline
\textbf{Source} & \textbf{Target} & \textbf{Status} &
\textbf{Forbidden identification}\\
\hline
\endfirsthead
\hline
\textbf{Source} & \textbf{Target} & \textbf{Status} &
\textbf{Forbidden identification}\\
\hline
\endhead
coordinate-window tower / mixed-continuous replacement attached to
\(\mathfrak g_{\mathrm{str}}\) &
\(\mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) &
coordinate dg identity; bracketed comparison only after choosing a
bracket-admissible \(B\) &
not the full unreduced factorization centre without additional centrality
and descent data\\
\hline
bracket-admissible \(B\subset\mathrm{PV}_{\mathrm{coord}}\) &
\(P_0\) realization \(\Phi^B_{P_0}\) &
proved after completeness, \(d_\pi^{\mathrm{coord}}\)-stability, product stability, and
continuous contraction bracket are part of \(B\)'s data &
not the strict product/direct-sum completion\\
\hline
kernel-admissible \(B\) &
Maurer--Cartan kernel \(\Theta_B\) &
accepted only after diagonal convergence in the chosen completed tensor
product is proved &
not a strict Casimir kernel for the ambient product completion\\
\hline
\(C^\bullet_{\mathrm{CE}}(\mathfrak g)\) / \(\mathrm{PV}(A)\) &
reduced \(P_0\) central-operation model &
local Poisson cochain model &
not the ordinary centre and not the unreduced
\(Z^{P_0}_{\mathrm{fact}}\) without centrality homotopies\\
\hline
\(U_\hbar(\mathfrak g)/(\hbar)\) PBW special fibre &
\(\mathbf S(\mathfrak h\oplus\mathfrak h^\vee[1])\) and then selected
\(\mathbf S(\bar A\oplus\bar A_{\mathrm{desc}}[1])\) labels &
associated-graded label comparison &
not a same-action identification of \(\Psi_{a,b}\) with
\(\rho_{a,b}\)\\
\hline
admissible Tate / relative bar-cobar envelope &
\(\widehat U(\mathfrak g_{\mathrm{adm}})\) &
accepted only after conilpotent CE chains, exact continuous duality, PBW
completeness, and strong convergence are supplied &
not available for the raw full formal disk without admissibility data\\
\hline
\(c^I\) &
\(\theta^I\) &
proved generator rule &
not a boundary Hamiltonian coordinate\\
\hline
\(u_I\) &
\(O_I\) and brane-line Hamiltonian coordinates \(B_f(a)\) &
proved generator rule &
not a Hamiltonian CE ghost\\
\hline
\(C^\bullet_{\mathrm{CE}}(\mathfrak g_I)\) on intervals &
reduced brane-line factorization target &
cofactorization/\allowbreak{}opposite-interval source; factorization only after the
CE coproduct is paired with target multiplication &
not a same-variance morphism of raw factorization algebras\\
\hline
\(\Psi_{a,b}\) &
stable primitive one-\(\psi\) PBW special-fibre class &
proved in the stable trace complex &
not \(\mathfrak h^\vee_{\mathrm{cont}}\), not \(\mathcal P\), and not a
principal-part current\\
\hline
\(\rho_{a,b}\) &
\(\mathcal P=\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)\) &
proved by residue/Matlis comparison &
not a polynomial descendant and not an \(R\)-submodule quotient\\
\hline
\(\mathsf F_{\mathrm{Rees}}\) &
\(\bigoplus\hbar^{a+b}\C[[\hbar]]\rho_{a,b}\) &
proved after Fourier polarization &
not a same-action bridge \(\Psi_{a,b}\cong\rho_{a,b}\)\\
\hline
\(\Omega_c^\bullet(I)\otimes\mathfrak h\) &
brane-line Hamiltonian currents &
proved reduced current model &
\(C_c^\infty(I)\) denotes only the degree-zero summand\\
\hline
\(\mathcal D'_c(I)\widehat\otimes\mathcal P[1]\) &
principal-part current sector \(\Theta_\rho(B)\) &
proved reduced post-contraction &
does not require a product of two distributions\\
\hline
formal Moyal algebra \(\bar A_\hbar\) &
degree-zero Weyl coefficient target &
proved algebraically in the reduced setting with raw weights \(1\) and
\(1/24\) &
not a finite-\(N\) radial-parts theorem by itself\\
\hline
finite-\(N\) radial-parts target &
stable connected trace realization of the Moyal coefficients &
finite-certificate-relative theorem datum: the formal coefficients,
Capelli normalization, free normal-diagram obstruction
\(\mathfrak o^{\mathrm{rad}}_{a,b}\), proved edge PBW strip, and the
remaining uniform splitting or left-cokernel theorem &
not supplied by formal Moyal coefficients or by the cited radial-parts
sources alone; not a Costello analytic graph/QME realization\\
\hline
Costello brane-defect kernel &
closed-open graph/QME specialization &
open obstruction datum &
not inferred from the formal Moyal or reduced open-line computation\\
\hline
scalar cocycle \([\bar c]\) &
\(U(1)\) anomaly / Capelli contact line &
proved distinguished class &
not an exhaustive classification of unreduced QME cancellation\\
\hline
External global bulk-boundary target &
compact BCOV / Calabi--Yau / Vol III / Igusa--BKM consequence &
open matched-conventions descent problem &
not a consequence of the local Koszul Layers 0--6\\
\hline
\end{longtable}

\paragraph{PBW special-fibre open trace labels.}
\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\(H_{a,b}=z_1^az_2^b\) &
Polynomial Hamiltonian label in \(\bar A\), with \(a+b>0\). In the
PBW special fibre it labels the scalar-reduced trace observable
\(O_{a,b}\).\\
\hline
\(O_{a,b}\) &
Open ghost-zero trace class
\(\overline{\operatorname{Tr}(\phi_1^a\phi_2^b)}\), with \(a+b>0\)
in the reduced Hamiltonian label set.\\
\hline
\(\Psi_{a,b}\) &
Primitive one-\(\psi\) stable open class, represented by the
symmetrised trace with one \(\psi\), \(a\) copies of \(\phi_1\), and
\(b\) copies of \(\phi_2\), with \(a+b>0\) after removing the scalar
descendant line. It lies in the PBW special-fibre open
shadow and carries the corresponding polynomial action. In the reduced
comparison it supplies the primitive indecomposable \(P_0\)-shadow
label.\\
\hline
\(\mathsf F_{\mathrm{Rees}}\) &
Fourier--Rees label bridge of
Theorem~\ref{thm:app-matlis-rees-fourier-bridge}. It sends the
polynomial label \(z_1^az_2^b\) to the Fourier-delta label
\(\partial_1^a\partial_2^be_0\), whose \v{C}ech realization is
\((-1)^{a+b}\hbar^{a+b}a!b!\rho_{a,b}\).  After inverting
\(\hbar\) one may divide by this Rees factor and read the
principal-part label \(\rho_{a,b}\).  It changes polarization and is
not an \(\mathfrak h\)-module identification between \(\Psi_{a,b}\)
and \(\rho_{a,b}\).\\
\hline
\end{tabular}
\end{center}

The shared indices on \(H_{a,b}\), \(\Psi_{a,b}\), and
\(\rho_{a,b}\) are labels, not an \(\mathfrak h\)-module
identification. The span of the \(\Psi_{a,b}\) is not
\(\mathfrak h^\vee_{\mathrm{cont}}\), not \(\mathcal P\), and not a
principal-part current module.

\paragraph{Closed CE/PV labels.}
\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\(\mathfrak g=\mathfrak h\ltimes
\mathfrak h^\vee_{\mathrm{cont}}[1]\) &
Shifted cotangent Lie algebra of Hamiltonian canonical transformations.\\
\hline
\(H_I\) &
Hamiltonian generator in \(\mathfrak h\).\\
\hline
\(\eta^I\) &
Shifted cotangent generator \((H_I)^\vee[1]\), with \(I=(a,b)\) and
\(a+b>0\).\\
\hline
\(c^I\) &
Chevalley--Eilenberg coordinate dual to a Hamiltonian generator
\(H_I\in\mathfrak h\). Under \(\Phi_{\mathrm{coord}}\),
\(c^I\mapsto\theta^I\).\\
\hline
\(u_I\) &
Chevalley--Eilenberg coordinate dual to the shifted cotangent generator.
Under \(\Phi_{\mathrm{coord}}\), \(u_I\mapsto O_I\). Boundary Hamiltonian observables
come from \(u_I\), not from \(c^I\).\\
\hline
\(\theta^I\) &
Polyvector coordinate corresponding to \(c^I\) under the coordinate CE/PV
isomorphism.\\
\hline
\(O_I\) &
Hamiltonian observable coordinate corresponding to \(u_I\) under the
coordinate CE/PV isomorphism.\\
\hline
\(\Phi_{\mathrm{coord}}\) &
Coordinate dg CE/PV map determined on generators by
\(c^I\mapsto\theta^I\) and \(u_I\mapsto O_I\).  Its \(P_0\) restriction
is \(\Phi^B_{P_0}\) only after a bracket-admissible \(B\) is chosen.\\
\hline
\end{tabular}
\end{center}

\paragraph{Matlis principal-part labels.}
\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\(\mathcal P\) &
Reduced principal-part module
\(\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)\subset
H^2_{\mathfrak m}(R)\,dz_1dz_2\), identified with
\(\mathfrak h^\vee_{\mathrm{cont}}\).\\
\hline
\(\rho_{a,b}\) &
Principal-part residue current
\(z_1^{-a-1}z_2^{-b-1}dz_1dz_2\), \(a+b>0\), with the Matlis
coadjoint action.\\
\hline
\(z_1^p z_2^q\cdot\rho_{a,b}\) &
Coadjoint action
\(-(pb-qa+p-q)\rho_{a-p+1,b-q+1}\). This is the Hamiltonian coadjoint
principal-part action, not the Matlis \(R\)-module action and not the
PBW action on \(\Psi_{a,b}\).\\
\hline
\(\mathcal P_I\) &
\(\mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mathcal P\), the
compactly supported distributional principal-part currents on an interval
\(I\).\\
\hline
\end{tabular}
\end{center}

Thus \(\Psi_{a,b}\) and \(\rho_{a,b}\) live in different modules:
\[
  \Psi_{a,b}\in\text{PBW special-fibre open homology},\qquad
  \rho_{a,b}\in
  \mathcal P\cong\mathfrak h^\vee_{\mathrm{cont}}.
\]
No ordinary \(\mathfrak h\)-module isomorphism between these two spans
is used or asserted.

\paragraph{Interval-current and boundary labels.}
\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.25\textwidth}
  >{\raggedright\arraybackslash}p{0.67\textwidth}@{}}
\hline
\textbf{Symbol} & \textbf{Meaning}\\
\hline
\(\mathfrak h_I\) &
\(\mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h\), the
compactly supported de Rham Hamiltonian currents on an interval
\(I\subset\R\). Degree-zero test functions appear only after taking the
explicit measurement notation.\\
\hline
\(\mathfrak g_I\) &
\(\mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1]\), the shifted
cotangent current algebra on \(I\), with principal-part currents in the
shifted cotangent direction.\\
\hline
\(B_f(a)\) &
Smeared boundary Hamiltonian observable
\(\int_I a(t)\overline{\operatorname{Tr}f(\phi_1(t),\phi_2(t))}\,dt\).
Its CE source is \(u_{a(t)dt\otimes f}\).\\
\hline
\(A^{\mathrm{Ham}}_\partial(I)\) &
Reduced Hamiltonian brane-line \(P_0\) factorization algebra
\(\widehat{\mathbf S}(\mathfrak h_I)\).\\
\hline
\(A^{\mathrm{pp}}_\partial(I)\) &
Reduced principal-part defect-current model after de Rham-current contraction
\(\widehat{\mathbf S}(\mathfrak h_I)\widehat\otimes
\widehat{\mathbf S}(\mathcal P_I[1])\).  An unreduced BV observable
algebra maps to it only after the centrality homotopies, coefficient
kernel, brane-defect propagator, descent data, and BV/QME solution are
supplied.\\
\hline
\(\Theta_\rho(B)\) &
Principal-part current observable with
\(B\in\mathcal D'_c(I)\) and \(\rho\in\mathcal P\). It is the boundary
notation for \(B\otimes\rho[1]\) in the reduced model and pairs with
smooth test functions by \(B(a)\operatorname{Res}(\rho f)\).\\
\hline
\(aB\) &
Multiplication of a compactly supported distribution \(B\) by a smooth
test function \(a\in\Omega^0_c(I)\). The reduced brackets use this
operation and never require multiplying two distributions.\\
\hline
\end{tabular}
\end{center}
\endgroup
