% !TEX root = main.tex
\documentclass[11pt]{memoir}

\usepackage{raeez-math-template}
\input{mathmacros.tex}
\input{authors.tex}

\title{Remarks on Mixed Holomorphic-Topological Strings}
\date{2018}
\hypersetup{
  pdftitle={Remarks on Mixed Holomorphic-Topological Strings},
  pdfauthor={Raeez Lorgat}
}
\makeatletter
\let\titlepageauthor\@author
\def\@author{Raeez Lorgat}
\AtBeginDocument{\let\@author\titlepageauthor}
\makeatother

\ifdefined\mainpreambleonly
  \expandafter\endinput
\fi

\begin{document}

  %%%%%%%%%%%%%%%%
  %% Title etc. %%
  %%

  \maketitle
  \input{abstract.tex}
  \tableofcontents
  \mbox{}

\section{Introduction}

\subsection{Local measurements, constraints, and brackets}

The object of study is a local constrained mechanical system. Fix a defect
world-line $\R\times p$ inside the $1+4$-real-dimensional space-time
$\R^2\times\C^2$. The transverse data is a single real line of
\emph{topological time} (the $\R^2$ factor), and a formal holomorphic
symplectic disk
$$(z_1,z_2),\qquad \omega=dz_1\wedge dz_2,$$
the formal neighbourhood of $p\in\C^2$. The defect is a \emph{point in $\C^2$,
dragged along $\R$}; nothing else has been postulated.

The two normal coordinates $z_1,z_2$ describe the position of the defect
inside the symplectic disk. A stack of $N$ identical probes at the defect
represents each coordinate by an $N\times N$ matrix:
$$z_1\rightsquigarrow\phi_1,\qquad z_2\rightsquigarrow\phi_2,
  \qquad\phi_i\in\lie{gl}_N.$$
The symplectic form pulls back to the matrix-valued two-form
$\Omega_N=\mathrm{Tr}(d\phi_1\wedge d\phi_2)$, and the symplectic potential
along the world-line is
$$\theta_N=\mathrm{Tr}(\phi_1\,d\phi_2).$$
Acting on a probe stack by an internal change of basis is a gauge operation.
The gauge generator is the $\lie{gl}_N$-valued moment map
$$\mu_\epsilon=-\mathrm{Tr}\bigl(\epsilon[\phi_1,\phi_2]\bigr),\qquad
  \epsilon\in\lie{gl}_N,$$
and demanding gauge-invariance of the world-line dynamics imposes the
\emph{first-class constraint}
$$[\phi_1,\phi_2]=0.$$
The Lagrange multiplier for this constraint is a connection
$A\in\Omega^1(\R)\otimes\lie{gl}_N$. The boundary action is therefore
\emph{not chosen}; it is the unique first-order action carrying the
symplectic potential and enforcing the first-class constraint:
\begin{equation}\label{eq:open-action-derived}
S_\partial
  =\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr).
\end{equation}
This is the Dirac standard. The ``open string field theory on $\R\times p$''
is the canonical mechanics of an $N$-probe stack on the formal symplectic
normal disk, with the matrix moment-map equation as its first-class
constraint. Lemma~\ref{lem:dirac-probe-reduction} records the precise
constrained-mechanics statement and identifies $A$ as the multiplier.

The BV reduction of this constrained system is an algebraic step. The
constraint is recorded as a Koszul differential by a single odd matrix
antifield $\psi=A^*\in\lie{gl}_N[1]$ with
\begin{equation}\label{eq:open-Q}
Q\psi=[\phi_1,\phi_2],\qquad Q\phi_1=Q\phi_2=0.
\end{equation}
The reduced local polynomial algebra at a brane point is
$$\mathcal R_N
  =\C[\phi_1{}^i{}_j,\phi_2{}^i{}_j]
   \otimes\Lambda(\psi^i{}_j),$$
and $H^0(\mathcal R_N^{GL_N},Q)$ is, by definition, the algebra of
$GL_N$-invariant local observables on the Dirac-reduced phase space of
commuting matrix pairs. This algebra is the open trace algebra of the defect;
it is what one is forced to write down once the probe stack and the constraint
have been named. The full BV master action is the canonical lift of
\eqref{eq:open-action-derived} to ghost-number-zero fields; this lift is
recorded in Lemma~\ref{lem:open-action-reduction} and
Proposition~\ref{prop:open-bv-truncation}.

\subsection{The Hamiltonian Lie algebra of the symplectic disk}

The corresponding closed system is dictated by the same canonical mechanics.
A closed infinitesimal symmetry of the formal symplectic disk is a
Hamiltonian vector field $X_f=\{f,-\}$. Constants act trivially: $X_c=0$ for
$c\in\C$. The closed Hamiltonian Lie algebra is therefore the formal power
series modulo constants,
\begin{equation}\label{eq:hbar-Lie-algebra}
\bar A=\C[z_1,z_2]/\C\cdot1,\qquad
\widehat{\mathfrak h}=\C[[z_1,z_2]]/\C\cdot1,
\end{equation}
with bracket
$$\{f,g\}=\partial_{z_1}f\,\partial_{z_2}g
  -\partial_{z_2}f\,\partial_{z_1}g\pmod{\C}.$$
Polynomial calculations use $\bar A$; closed
Chevalley--Eilenberg/Koszul calculations use the completed
$\widehat{\mathfrak h}$. Continuous duality on $\widehat{\mathfrak h}$
produces $\mathfrak h^\vee=\widehat{\mathfrak h}^\vee_{\mathrm{cont}}$, with
the Taylor-monomial basis $\delta_{k,l}$ for $k+l>0$. We use
$\bar A_{\mathrm{desc}}$ for an abstract copy of $\bar A$ whose nonconstant
basis vectors are represented on the brane by the first descendant cycles
$\Psi_{k,l}$ (Construction~\ref{constr:boundary-evaluation}).

\begin{rmk}[Scalar Hamiltonian and center-of-mass term]\label{rmk:scalar-hamiltonian-center-of-mass}
  The quotient by constants is load-bearing. In the reduced Hamiltonian
  algebra of the formal disk,
  $$\{z_1,z_2\}=1\equiv0\quad\text{in }\bar A.$$
  On the unreduced brane phase space, however,
  $$\{\mathrm{Tr}(\phi_1),\mathrm{Tr}(\phi_2)\}=N.$$
  This is the center-of-mass symplectic pair of the stack. Every bracket
  statement below involving linear Hamiltonians is therefore a statement after
  projection to the Hamiltonian quotient by scalar trace classes. The same
  term reappears quantum mechanically as the Capelli shift in
  Remark~\ref{rmk:normal-ordering-obstruction}.
\end{rmk}

The closed canonical theory must promote $\widehat{\mathfrak h}$ to a local
field theory whose phase space is the cotangent of the Hamiltonian-deformation
moduli; the cotangent of canonical transformations is the unique covariant
choice. This is what BCOV \cite{bcov} prescribes for the closed B-model on a
Calabi--Yau, with the polyvector cotangent realised by the divergence
operator. On a holomorphic-symplectic surface the local cotangent theory is
the Hamiltonian BF theory for the Tate Lie algebra
\begin{equation}\label{eq:cotangent-Lie-algebra}
\mathfrak g=\widehat{\mathfrak h}\ltimes\mathfrak h^\vee[1],
\end{equation}
where the shift $[1]$ records the BV degree of the cotangent field and the
Lie bracket on $\mathfrak g$ is the semi-direct sum of the Hamiltonian
bracket on $\widehat{\mathfrak h}$ with the coadjoint action on
$\mathfrak h^\vee[1]$.

The closed local observables are the continuous Chevalley--Eilenberg
cochains
$$\mathcal{O}^{\mathrm{cl}}_{\mathrm{grav}}
  =C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
  =\widehat{\mathbf S}\bigl(\mathfrak g^\vee_{\mathrm{cont}}[-1]\bigr),$$
and their Koszul dual is the completed graded enveloping algebra
$$\bigl(\mathcal{O}^{\mathrm{cl}}_{\mathrm{grav}}\bigr)^!
  \simeq\widehat{U(\mathfrak g)}.$$
The PBW Rees algebra $U_\hbar(\mathfrak g)$ has completed special fibre
\begin{equation}\label{eq:PBW-special-fibre}
U_\hbar(\mathfrak g)/(\hbar)
  \cong\widehat{\mathbf S}\bigl(\widehat{\mathfrak h}
    \oplus\mathfrak h^\vee[1]\bigr).
\end{equation}
The structural content of \eqref{eq:cotangent-Lie-algebra}--%
\eqref{eq:PBW-special-fibre} is that the closed sector \emph{is the shifted
cotangent theory of canonical transformations of the disk};
Proposition~\ref{prop:hamiltonian-polyvector-reduction} below derives
$\widehat{\mathfrak h}$ from divergence-closed polyvectors on the formal disk.

\subsection{Closed-open measurement and the derived Poisson centre}

A closed Hamiltonian $f(z_1,z_2)$ is \emph{measured} by the brane by
substitution of the matrix-valued normal coordinates:
$$J(f)=\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}.$$
At finite $N$ one chooses a word ordering. In $H^0(\mathcal R_N^{GL_N},Q)$
adjacent swaps are exact,
$Q\,\mathrm{Tr}(\psi vu)=\mathrm{Tr}([\phi_1,\phi_2]vu)$, so the ordering
ambiguity disappears modulo the constraint. In the stable connected limit
$N\to\infty$, $J(f)$ is a well-defined Hamiltonian observable on the brane.
The matrix Poisson bracket gives
\begin{equation}\label{eq:open-bracket}
\bigl\{J(f),J(g)\bigr\}_\partial=J\bigl(\{f,g\}_{\mathfrak h}\bigr),
\end{equation}
after removal of the scalar Hamiltonian. Equation~\eqref{eq:open-bracket} is
the ordinary canonical bracket of the probe system: it is not a string-theoretic
input; it is the statement that the probe brane is a representation of the
Hamiltonian Lie algebra of the disk. On monomials,
\begin{equation}\label{eq:bracket-coefficient}
\bigl\{\overline{\mathrm{Tr}(\phi_1^k\phi_2^l)},
       \overline{\mathrm{Tr}(\phi_1^m\phi_2^n)}\bigr\}
  =\overline{(kn-lm)\,\mathrm{Tr}(\phi_1^{k+m-1}\phi_2^{l+n-1})}.
\end{equation}

The map $f\mapsto J(f)$ is the \emph{moment-map shadow} of the full
closed-open operation. The full operation cannot be a single function on the
open algebra: a closed local field that lives in a region of space-time near
the brane should produce \emph{a central operation on all open factorisation
observables}, not merely an element. The correct target is therefore the
derived Poisson centre
$$Z^{P_0}_{\mathrm{fact}}(\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}}).$$
The structural form of this identification is the content of
Theorem~\ref{thm:reduced-derived-poisson-center} below: the closed
Chevalley--Eilenberg cochains on $\mathfrak g$ identify with the reduced
derived $P_0$-Poisson centre of the stable open Hamiltonian algebra, and the
boundary observable $J(f)=\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}$ is the
image, under that identification, of the coordinate dual to the shifted
cotangent generator (\emph{not} of the coordinate dual to $f$ itself); the
closed Hamiltonian ghost becomes the Hamiltonian vector-field operation on
the brane.

\subsection{Scalar reduction and the U(1) center anomaly}\label{subsec:scalar-anomaly}

Throughout this manuscript constants in $\C[z_1,z_2]$ and the finite-rank
scalar trace $\mathrm{Tr}(1)=N$ are removed before the bracket is recorded.
This convention has algebraic content. The class of the removed cocycle is
the U(1) center anomaly: the unique nontrivial class
$[c]\in H^2_{\mathrm{Lie}}(\mathfrak h, \C)$ obstructing the lift of the
scalar-reduced Hamiltonian Poisson bracket to the unreduced bracket on
$\C[z_1,z_2]$ on the closed side, and the unique obstruction to lifting the
trace algebra Lie bracket to $\lie{gl}_N$ rather than to its quotient
$\mathfrak{sl}_N\oplus\C\cdot I$ on the open side. Theorem~\ref{thm:u1-center-anomaly}
makes this precise; Theorem~\ref{thm:quantum-classical-anomaly} identifies the
same class with the Moyal/Capelli $\hbar N$ shift on the brane. The flag
``before/after killing the scalar'' is propagated explicitly through every
later theorem statement that touches $\mathfrak h$ or
$\mathcal A_{\partial}$.

\paragraph{Notation.} Write $\mathfrak h_{\mathrm{poly}}=\C[z_1,z_2]_+$ for
the polynomial Hamiltonian Lie algebra without the constant subalgebra
removed; the bracket on $\mathfrak h_{\mathrm{poly}}$ is
$\{f,g\}=\partial_{z_1}f\,\partial_{z_2}g-\partial_{z_2}f\,\partial_{z_1}g$ and
takes values in $\C[z_1,z_2]_+\oplus\C\cdot 1$. Define
$$\omega:\mathfrak h_{\mathrm{poly}}\otimes\mathfrak h_{\mathrm{poly}}
  \longrightarrow\C,\qquad
  \omega(f,g)=[\,\{f,g\}\,]_0,$$
the constant Taylor coefficient of $\{f,g\}$. On monomials,
$$\omega(z_1^kz_2^l,z_1^mz_2^n)=
  \begin{cases}
    kn-lm, & (k+m,l+n)=(1,1),\\
    0, & \text{otherwise},
  \end{cases}$$
hence $\omega$ is concentrated in the unique bidegree where the bracket
multidegree $(k+m-1,l+n-1)$ is $(0,0)$; this is exactly the bidegree the
manuscript discards as ``scalar trace''.

\begin{lem}\label{lem:omega-cocycle}
  $\omega$ is a Lie 2-cocycle on $\mathfrak h_{\mathrm{poly}}$, and its
  cohomology class
  $$[c]:=[\omega]\in H^2_{\mathrm{Lie}}(\mathfrak h_{\mathrm{poly}},\C)$$
  is nontrivial. After projection to $\bar A=\mathfrak h_{\mathrm{poly}}/\C$,
  the same formula represents a nontrivial class
  $[\bar c]\in H^2_{\mathrm{Lie}}(\bar A,\C)$.
\end{lem}

\begin{proof}
  The Jacobi identity for $\{-,-\}$ on $\mathfrak h_{\mathrm{poly}}$ asserts
  $$\{f,\{g,h\}\}+\{g,\{h,f\}\}+\{h,\{f,g\}\}=0,$$
  and projecting each summand to its constant Taylor coefficient gives the
  cocycle identity
  $$\omega(f,\{g,h\})+\omega(g,\{h,f\})+\omega(h,\{f,g\})=0.$$
  Antisymmetry $\omega(g,f)=-\omega(f,g)$ is inherited from antisymmetry of
  the bracket. Hence $\omega\in Z^2_{\mathrm{Lie}}(\mathfrak h_{\mathrm{poly}},\C)$.
  Suppose $\omega=\delta\eta$ for some linear $\eta:\mathfrak h_{\mathrm{poly}}\to\C$.
  Then $\omega(f,g)=-\eta(\{f,g\})$. Test on $f=z_1$, $g=z_2$:
  $\omega(z_1,z_2)=1$ while $\{z_1,z_2\}=1$, so
  $\eta(1)=-1$. But $z_1\cdot 1$ and $1\cdot z_1$ both bracket to zero with
  any $g\in\mathfrak h_{\mathrm{poly}}$ except via the same calculation, so
  the system $\eta(\{f,g\})=-\omega(f,g)$ overdetermines $\eta$: testing on
  $f=z_1^2,g=z_2$ gives $\eta(2z_1)=0$, hence $\eta$ vanishes on
  $z_1\C[z_1,z_2]_+$, contradicting $\eta(1)=-1$. Therefore
  $[\omega]\neq 0\in H^2_{\mathrm{Lie}}(\mathfrak h_{\mathrm{poly}},\C)$.
  The same argument descends to $\bar A=\mathfrak h_{\mathrm{poly}}/\C$, since
  $\omega$ vanishes on the line $\C\cdot 1$ already, so it descends to a
  cocycle on the quotient and remains nontrivial.
\end{proof}

\begin{thm}[U(1) center anomaly: closed side]\label{thm:u1-center-anomaly}
  The class $[\bar c]\in H^2_{\mathrm{Lie}}(\bar A,\C)$ of
  Lemma~\ref{lem:omega-cocycle} is the unique obstruction class to lifting
  the Lie algebra structure on $\bar A$ to a Lie algebra structure on the
  unreduced polynomial Hamiltonians $\mathfrak h_{\mathrm{poly}}$ along the
  abelian extension
  $$0\longrightarrow \C\cdot 1\longrightarrow \mathfrak h_{\mathrm{poly}}
    \longrightarrow \bar A\longrightarrow 0.$$
  Equivalently, $\mathfrak h_{\mathrm{poly}}$ is isomorphic to the central
  extension $\bar A_{[\bar c]}=\bar A\oplus\C K$ with bracket
  $$[\,(f,aK),(g,bK)\,]=(\{f,g\}_{\bar A},\,\bar c(f,g)\,K),$$
  and $[\bar c]$ generates a one-dimensional sub-line of
  $H^2_{\mathrm{Lie}}(\bar A,\C)$ that is the obstruction.
\end{thm}

\begin{proof}
  Central extensions of $\bar A$ by $\C$ are classified by
  $H^2_{\mathrm{Lie}}(\bar A,\C)$ via the standard Chevalley-Eilenberg
  argument. The exact sequence above is a central extension because the
  constant Hamiltonian $1\in\mathfrak h_{\mathrm{poly}}$ has zero Hamiltonian
  vector field, so $\C\cdot 1$ is central in
  $\mathfrak h_{\mathrm{poly}}$. The class of this extension is the obstruction
  to a Lie-algebra splitting; computing the class on monomial generators,
  $$[z_1^kz_2^l,z_1^mz_2^n]_{\mathfrak h_{\mathrm{poly}}}
    =\{z_1^kz_2^l,z_1^mz_2^n\}=
    (kn-lm)z_1^{k+m-1}z_2^{l+n-1},$$
  and projecting to $\C\cdot 1$ keeps only the $(0,0)$-Taylor coefficient
  $\omega$ of Lemma~\ref{lem:omega-cocycle}. Thus the extension class is
  $[\bar c]$, and Lemma~\ref{lem:omega-cocycle} shows it is nontrivial. The
  same lemma shows the line $\C\cdot[\bar c]$ is one-dimensional inside
  $H^2_{\mathrm{Lie}}(\bar A,\C)$, and that splitting along this line
  recovers $\mathfrak h_{\mathrm{poly}}$.
\end{proof}

\begin{thm}[U(1) center anomaly: open side]\label{thm:u1-center-anomaly-open}
  At finite $N$ the trace algebra Lie bracket
  $\{F,G\}=\mathrm{Tr}(\partial_{\phi_1}F\,\partial_{\phi_2}G
  -\partial_{\phi_2}F\,\partial_{\phi_1}G)$ on
  $\C[\lie{gl}_N\oplus\lie{gl}_N]^{GL_N}$ satisfies
  $$\{\mathrm{Tr}\,\phi_1,\mathrm{Tr}\,\phi_2\}=N$$
  in the unreduced ring, and zero in the scalar-reduced quotient
  $H^0_{\mathrm{red}}=H^0/\C\cdot\mathrm{Tr}(1)$. The cohomology class of this
  central scalar in $H^2_{\mathrm{Lie}}$ of the unreduced trace algebra is
  the image of $[\bar c]$ under the boundary evaluation map
  $$\partial_{\mathrm{bb},N}^{\mathrm{full}}:\C[z_1,z_2]\longrightarrow
    \C[\lie{gl}_N^2]^{GL_N},\qquad
    f\longmapsto \mathrm{Tr}\,f(\phi_1,\phi_2),$$
  i.e.\ the same anomaly class is realised on the brane as the U(1) center
  of $\lie{gl}_N$ with central element $I$.
\end{thm}

\begin{proof}
  The matrix Poisson bracket gives, on monomials of bidegree $(1,0)$ and
  $(0,1)$,
  $$\{\mathrm{Tr}\,\phi_1,\mathrm{Tr}\,\phi_2\}
    =\mathrm{Tr}\bigl((\partial_{\phi_1}\mathrm{Tr}\,\phi_1)
      (\partial_{\phi_2}\mathrm{Tr}\,\phi_2)
      -(\partial_{\phi_2}\mathrm{Tr}\,\phi_1)
      (\partial_{\phi_1}\mathrm{Tr}\,\phi_2)\bigr)
    =\mathrm{Tr}(I\cdot I)-0=N.$$
  Hence the unreduced bracket realises the constant $N$ as a scalar element.
  In $H^0_{\mathrm{red}}=H^0/\C\cdot\mathrm{Tr}(1)$ this scalar is killed,
  matching the projection on the closed side. The boundary evaluation map
  $\partial_{\mathrm{bb},N}^{\mathrm{full}}$ sends $1\in\C[z_1,z_2]$ to
  $\mathrm{Tr}(I)=N$ and satisfies, for monomials with $(k+m,l+n)=(1,1)$,
  $$\partial_{\mathrm{bb},N}^{\mathrm{full}}(\{z_1^kz_2^l,z_1^mz_2^n\})
    =(kn-lm)\cdot\mathrm{Tr}(I)
    =(kn-lm)\cdot N\cdot I,$$
  which equates the closed cocycle $\omega$ with the open trace bracket on
  the central direction. Hence the extension class on the brane is the
  image of $[\bar c]$. Since $\C\cdot I\subset\lie{gl}_N$ is the U(1) centre
  with character $\mathrm{Tr}$, the brane realisation of $[\bar c]$ is
  exactly the U(1) centre of $\lie{gl}_N$.
\end{proof}

\begin{rmk}\label{rmk:quotient-discipline-flag}
  Every theorem in this manuscript that uses $\mathfrak h$, $\bar A$, or
  $\mathcal A_{\partial}=H^0_{\mathrm{red}}$ lives \emph{after} killing the
  scalar. The unreduced statement requires keeping the central line
  $\C\cdot 1\subset\mathfrak h_{\mathrm{poly}}$ on the closed side and
  $\C\cdot\mathrm{Tr}(1)$ on the open side, with the U(1) center anomaly
  class $[\bar c]$ recording the obstruction to a Lie-algebra splitting.
  Theorem~\ref{thm:main-local}, Theorem~\ref{thm:bulk-boundary},
  Corollary~\ref{cor:local-bulk-boundary-coupling}, and
  Proposition~\ref{prop:first-order-bracket} are all stated on the reduced
  side; their unreduced refinements are governed by $[\bar c]$ via the
  central extensions of Theorems~\ref{thm:u1-center-anomaly}
  and~\ref{thm:u1-center-anomaly-open}.
\end{rmk}

\subsubsection*{Quantum-classical equivalence of the U(1) center cocycle}

\begin{thm}[Quantum-classical equivalence of the U(1) center class]\label{thm:quantum-classical-anomaly}
  Let $\Phi=(\phi_1,\phi_2)$ be the classical brane field on the formal
  local disk and $\Phi_\hbar=(\phi_1^{\hbar},\phi_2^{\hbar})$ its Weyl
  quantization at finite $N$, with the Moyal product
  $f*g=m\circ\exp\bigl(\tfrac{\hbar}{2}P\bigr)(f\otimes g)$ for
  $P=\partial_{z_1}\otimes\partial_{z_2}-\partial_{z_2}\otimes\partial_{z_1}$.
  Then on the brane the quantization satisfies the Capelli/canonical
  commutator identity
  $$Y_{\hbar}X_{\hbar}-X_{\hbar}Y_{\hbar}+\hbar N I=0,\qquad
    X_{\hbar}=\phi_1^{\hbar},\ Y_{\hbar}=\phi_2^{\hbar},$$
  which evaluates to $\{\phi_2,\phi_1\}=-\delta=N$ on the trace generators
  $X=\mathrm{Tr}\,\phi_1$, $Y=\mathrm{Tr}\,\phi_2$.
  In the classical limit $\hbar\to 0$, the bracket
  $\{\mathrm{Tr}\,\phi_1,\mathrm{Tr}\,\phi_2\}=N$ recovers the central scalar
  of Theorem~\ref{thm:u1-center-anomaly-open}.
  The classical Poisson cocycle $\omega$ of Lemma~\ref{lem:omega-cocycle}
  and the quantum Capelli shift $\hbar N$ represent the \emph{same
  cohomology class} $[\bar c]\in H^2_{\mathrm{Lie}}(\bar A,\C)$ under
  classical-to-quantum reduction, i.e.\ via the Rees deformation
  $U_{\hbar}(\bar A_{[\bar c]})$ specialising to
  $\widehat{\mathbf S}(\bar A_{[\bar c]})$ at $\hbar=0$.
\end{thm}

\begin{proof}
  The Weyl convention gives $[X_{\hbar},Y_{\hbar}]_*=\hbar\{X,Y\}+O(\hbar^3)$.
  On the trace generators, Proposition~\ref{prop:first-order-bracket} at
  $(k,l,m,n)=(1,0,0,1)$ gives $\{X,Y\}=N$ before scalar reduction. Hence
  $$X_{\hbar}Y_{\hbar}-Y_{\hbar}X_{\hbar}=\hbar N+O(\hbar^3),$$
  and at finite $N$ the higher-order terms vanish on these linear generators
  because $P^r$ requires at least $r$ derivatives in each tensor factor.
  Rearranging gives the displayed Capelli/canonical identity. This is the
  classical-to-quantum reduction in the sense of Razmyslov~\cite{razmyslov}
  and Procesi~\cite{procesi}: the trace identities of $\lie{gl}_N$ at level
  $N$ are exactly the Capelli identities~\cites{capelli,howe-capelli}, and
  the abelian Capelli at $r=1$ is the canonical-commutator shift.

  For the cohomology-class identification, observe that the Rees algebra
  $U_{\hbar}(\bar A_{[\bar c]})$ has central fibre
  $\widehat{\mathbf S}(\bar A_{[\bar c]})$ at $\hbar=0$ and generic fibre
  containing $\bar A_{[\bar c]}$ as Lie algebra at $\hbar=1$. The
  PBW filtration's associated graded carries the Lie 2-cocycle as the
  primary obstruction to PBW-splitting the deformation. Both sides of the
  classical-to-quantum reduction therefore record the same class in
  $H^2_{\mathrm{Lie}}(\bar A,\C)$: classically $\omega$ is the obstruction
  to splitting the central extension $\mathfrak h_{\mathrm{poly}}\to\bar A$,
  quantum-mechanically the same $\omega$ is the leading-order coefficient
  of the Moyal star commutator on the central direction.
\end{proof}

\begin{rmk}
  The class $[\bar c]$ is therefore a physical observable of the brane:
  the U(1) center of $\lie{gl}_N$ acts on the brane Hilbert space with
  character $\mathrm{Tr}$, and the canonical/Capelli shift $\hbar N$ is the
  charge of this central direction. The scalar reduction in the body of the
  manuscript is the operation of restricting to the kernel of this
  character; it is not a vacuous bookkeeping step.
\end{rmk}

\subsection{The two algebras}

The local model contains two algebras, both \emph{derived} from the
canonical mechanics above rather than postulated:
\begin{itemize}
  \item The algebra $\mc{A}_N$ of $GL_N$-invariant local trace observables
    on the Dirac-reduced probe stack of \eqref{eq:open-action-derived};
    equivalently, the algebra of local operators of the open BV theory on
    the brane line $\R\times p$.
  \item The algebra $\mc{B}$ of local operators of the closed Hamiltonian
    BF sector \eqref{eq:cotangent-Lie-algebra}; the operator-product
    expansion in the $\R$-direction equips $\mc{B}$ with an associative
    product, derived from the locally constant factorisation structure of
    the topological direction.
\end{itemize}

\begin{conj}[Stable bulk--boundary Koszul duality]\label{conj:An-Koszul}
  In the stable large-$N$ limit and within the Hamiltonian sector,
  $$\lim_{N\to\infty}\mc A_N\ \simeq\ \mc B^!,$$
  the Koszul dual of $\mc B$. Theorem~\ref{thm:main-local} is the classical
  Hamiltonian shadow of this conjecture; the quantum refinement is the
  formal Weyl/Moyal target of \S\ref{ssec:quantum-target} below.
\end{conj}

This recovers the open/closed string duality of \cite{witten-cs}, but here
it is no longer a string-theoretic ansatz: it is the statement that the
closed local theory is the derived Poisson centre of the open local theory.

The provenance of this local model in higher-dimensional physics is
twisted M-theory. The following conjecture states, in precise form, the
universality claim that the formal local construction here is the
Hamiltonian-sector restriction of every twisted M-theory background of
the indicated type.

\begin{conj}[Twisted-M-theory universality of the local model]\label{conj:twisted-m-theory-universal}
  Let $X$ be a holomorphic-symplectic surface and let
  $\mathcal{T}_{\mathrm{tw}M}\bigl(\R\times X;\R\times p\bigr)$ denote the
  perturbative twisted M-theory data on $\R\times X$ in the presence of a
  stack of $N$ one-dimensional topological branes supported on $\R\times p$,
  in the sense of the twisted holomorphic-topological theory
  \cite{costello-twistedM} whose protected sector restricts to the local
  Hamiltonian sector here. Hypotheses:
  (i) the BV-cohomology vanishing of \cites{costello-li-quantum-bcov,
  costello-li-open-closed-bcov} on the formal local model;
  (ii) the Costello locality theorem ensuring that restriction to a formal
  neighbourhood of $\R\times p$ is well-defined;
  (iii) the Hamiltonian reduction of the holomorphic-symplectic data to the
  formal symplectic disk at $p$ is regular.
  Then the Hamiltonian-sector restriction
  $$\mathcal{T}_{\mathrm{tw}M}\bigl(\R\times X;\R\times p\bigr)
    \big|_{\mathrm{Ham},\widehat{p}}$$
  is canonically equivalent, as a pair (open BV theory; closed Hamiltonian
  BF theory together with open trace data), to the formal local model
  constructed in this manuscript: open side
  $\bigl(\Omega^*(\R)\otimes\Lambda(\varepsilon_1,\varepsilon_2)
  \otimes\lie{gl}_N[1],\,S(\alpha)\bigr)$, closed side
  $C^\bullet_{\mathrm{CE,cont}}(\mathfrak g)$ with
  $\mathfrak g=\widehat{\mathfrak h}\ltimes\mathfrak h^\vee[1]$, and
  bulk-to-boundary evaluation
  $f\mapsto\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}$. In particular every
  such twisted M-theory restriction satisfies Theorem~\ref{thm:main-local}.
\end{conj}

\begin{rmk}
  Conjecture~\ref{conj:twisted-m-theory-universal} replaces the BCOV analogy
  as the primary physical motivation. The original BCOV analysis is written
  for Calabi--Yau threefolds (\cite{bcov}), where the target dimension is
  $d=3$; the local model here is a holomorphic-symplectic surface ($d=2$)
  and is therefore not a reduction of BCOV in any direct sense. The
  Hamiltonian BF formulation \eqref{eq:cotangent-Lie-algebra} is the
  correct primary physical name. The deciding evidence for the conjecture
  is (a) the explicit BV-cohomology computation of
  \cites{costello-li-quantum-bcov,costello-li-open-closed-bcov};
  (b) a reduction lemma for protected twisted-M-theory operators on
  $\R\times X$ to the formal disk at $p$; (c) compatibility with the
  scalar/center-of-mass anomaly term of
  Remark~\ref{rmk:scalar-hamiltonian-center-of-mass}.
\end{rmk}

\subsection{Three notions of locality}

Locality is not one notion in this model. It is three.

\paragraph{(a) Support locality along the brane.}
For an open interval $I\subset\R$ on the world-line, define the compactly
supported Hamiltonian current algebra
$\mathfrak h_I=C^\infty_c(I)\otimes\widehat{\mathfrak h}$ with bracket
$$[a\otimes f,\,b\otimes g]=ab\otimes\{f,g\}_{\widehat{\mathfrak h}}.$$
The open observables on $I$ are
$\mathcal A_\partial(I)=\mathbf S(\mathfrak h_I)$, generated by the smeared
trace functionals
$$O_f(a)=\int_I a(t)\,\mathrm{Tr}\,f\bigl(\phi_1(t),\phi_2(t)\bigr)\,dt.$$
Their bracket is the canonical equal-time bracket:
$$\bigl\{O_f(a),O_g(b)\bigr\}=O_{\{f,g\}_{\widehat{\mathfrak h}}}(ab).$$
Disjoint supports multiply, since $ab=0$ outside the intersection;
overlapping supports give a delta-function contact term. This is the
operational meaning of locality for the open factorisation algebra:
disjoint independent measurements multiply, and Poisson brackets are
supported where the measurements meet.

\paragraph{(b) Topological locality.}
In the topological direction (the $\R^2$ factor), translations are
$Q$-exact:
$$L_v=[Q,\iota_v].$$
Equivalently, positive jets in the topological direction vanish in
local-operator cohomology by the contraction homotopy
$[d_\R,\iota_{\partial_t}]=\partial_t$
(Lemma~\ref{lem:derivative-jets}). Therefore the precise position of an
insertion is not physical; only the collision pattern of insertions matters.
This is the structural reason the factorisation algebra is locally constant
in the topological direction.

\paragraph{(c) Formal holomorphic locality.}
In the holomorphic direction (the $\C^2$ factor), the model has been
completed at the brane point $p\in\C^2$. It is a theory of holomorphic
jets at $p$, not a theory of finite propagation through $\C^2$.
Antiholomorphic translations are $Q$-exact:
$$L_{\partial/\partial\bar z_i}
  =[Q,\iota_{\partial/\partial\bar z_i}].$$
The kinematic differential of the closed sector is
$D=d_{\R^2}+\bar\partial_{\C^2}$, and on the formal-jet model
$\bar\partial$-cohomology is concentrated in degree zero. The cotangent
boundary sector is \emph{distributionally local, not polynomially local}:
a coadjoint mode is a transverse principal part
$\rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1\,dz_2$, paired with a brane
Hamiltonian by residue,
$$\langle\rho_{a,b},z_1^mz_2^n\rangle=\delta_{a,m}\delta_{b,n}.$$
This is exactly what one expects for a momentum dual field attached to a
defect: support on the defect, transverse behaviour encoded by residues.
The polynomial one-$\psi$ descendants $\Psi_{k,l}$ realise the PBW
special fibre of $\mathfrak h^\vee[1]$
(Proposition~\ref{prop:open-descendant-action});
Corollary~\ref{cor:descendant-coadjoint-difference} records the
deformation-level mismatch with the coadjoint module, exactly the ordinary
distinction between polynomial and distributional realisations.

The factorisation-algebra structure is now \emph{forced}: it is the
algebraic expression of (a)+(b)+(c). Disjoint supports multiply along the
brane; topological motion is $Q$-exact and changes nothing in cohomology;
transverse holomorphic dependence is distributional. No external categorical
input has been imposed; the structure is the local algebra of measurements
in a constrained canonical system.

\subsection{Unitarity}

The model is a twisted BV sector. It is not a Lorentzian unitary quantum
mechanics. There is no positive-definite Hilbert space, no Wightman
positivity, and no reflection positivity. The fields include ghosts and
antifields; topological time has been made cohomologically trivial.

The replacements for unitarity are the consistency conditions of the BV
formalism: the classical master equation
$$QI+\tfrac12\{I,I\}=0$$
and the quantum master equation
$$QI+\tfrac12\{I,I\}+\hbar\,\Delta I=0,$$
together with associativity of the resulting factorisation/OPE algebra. If
the local model arises as a protected sector of a larger unitary theory
(for example, of a topological twist of a supersymmetric quantum field
theory in which the local observables of the present model are the
cohomology with respect to a supercharge), then unitarity is carried by
the larger theory, and the local sector retains only the cohomological
algebra of protected observables. Within the present manuscript we do not
impose unitarity, and we make no Lorentzian claims.

\subsection{Thesis}

\begin{quote}
A stack of branes is a system of probes for the formal symplectic normal
disk. Dirac reduction of the probe phase space gives the open trace algebra.
Hamiltonian BF theory is the shifted cotangent theory of canonical
transformations. The closed observables are precisely the derived Poisson
central operations on the stable open Hamiltonian brane algebra.
\end{quote}

\subsection{Mixed holomorphic-topological strings}

A local string theory in this paper means the part of string field theory
visible to local operators. The closed fields form a BV theory; local
observables form a factorization algebra; a brane contributes an open cyclic
field theory and a bulk-to-boundary map. The words topological and
holomorphic describe how these local operators vary in the spacetime
directions. This is a local string-field-theoretic use of the word
``string'', not a definition of a global theory of worldsheet moduli,
amplitudes on all backgrounds, or a completed quantum anomaly theory.

Gwilliam--Williams \cite{gwilliam-williams-holomorphic-bosonic-string} are
the precedent for formulating a holomorphic string in the Costello
BV/factorization formalism. Their object is the holomorphic bosonic string
on a Riemann surface, with Dolbeault fields $(\gamma,\beta,c,b)$, a
one-loop quantization in the critical complex dimension, and a
factorization algebra recovering the BRST cohomology. The object here is
not that theory and not a replacement definition. It is a formal local
target-space sector: de Rham/Floer directions, a holomorphic symplectic
formal disk, Hamiltonian cotangent BF fields, and a brane large-$N$
operator algebra.

The topological word refers to locally constant factorization in the de
Rham/Floer directions. The holomorphic word refers to the Dolbeault
presentation: the kinetic operator contains $\bar\partial$, the fields are
holomorphic jets after local formal completion, and anti-holomorphic
translations act by cochain-homotopic zero. A holomorphic theory may
acquire further topological descent after quantization; that extra descent
is not part of the definition used here.

\begin{defn}[Working local topological factorization sector]\label{def:local-topological-string-sector}
  Let $M$ be a smooth manifold. A local topological closed-string sector on
  $M$ is a classical BV theory whose local observables form a locally constant
  factorization algebra on $M$: for inclusions of sufficiently small disks
  $U\subset V$, the factorization structure map
  $$\mathrm{Obs}^{\mathrm{cl}}(U)\longrightarrow
    \mathrm{Obs}^{\mathrm{cl}}(V)$$
  is a quasi-isomorphism. In this paper, attaching branes to such a sector
  means specifying a cyclic open BV theory and the closed-open operations
  actually constructed. In a de Rham model the closed fields carry the
  differential $d_M$ plus the BV linearized differential, and the locally
  constant factorization product records collision of operators up to isotopy.
\end{defn}

\begin{rmk}
  The exact A-model factor used below is a local topological sector in this
  sense: the self-Floer model for $\R\subset T^*\R$ is represented by the
  de Rham complex $\Omega^*(\R)$, and its local observables are insensitive
  to the metric geometry of the interval. This is the topological part of
  the mixed holomorphic-topological example.
\end{rmk}

\begin{defn}[Working local holomorphic factorization sector]\label{def:local-holomorphic-string-sector}
  Let $Y$ be a complex manifold. A local holomorphic sector on $Y$ is a
  classical BV theory whose fields are Dolbeault complexes on $Y$, whose
  differential has the form $\bar\partial$ plus the BV linearized
  differential, whose interactions are holomorphic polydifferential
  operators, and whose local observables form a holomorphic factorization
  algebra. Here holomorphic factorization means that, on coordinate
  polydisks, the factorization products and restriction maps are
  represented by holomorphic polydifferential operations and every
  anti-holomorphic translation $\partial/\partial\bar z_i$ acts
  null-homotopically on observables. In the target-space Kodaira-Spencer
  examples the fields are Dolbeault-valued polyvectors; in the holomorphic
  symplectic examples below they are Hamiltonian polyvectors after removing
  constants. In this paper branes are treated through cyclic open BV theory
  and the bulk-to-boundary operations constructed below.
\end{defn}

\begin{rmk}
  BCOV/Kodaira-Spencer theory is the guiding threefold example
  \cite{bcov}: its fields are Dolbeault-valued polyvectors, and the
  Calabi-Yau volume form supplies the divergence operator. In the
  holomorphic symplectic surface model used here, the analogous
  divergence-free vector fields are represented locally by Hamiltonians
  modulo constants. The surface model is not a truncation of threefold BCOV
  theory.
\end{rmk}

\begin{rmk}
  The classical local observable theory underlying Gwilliam--Williams is an
  example of a pure holomorphic BV/factorization sector on a Riemann
  surface, with additional worldsheet ghost, BRST, and critical-dimension
  quantum structure. Their critical-dimension and BRST-cohomology theorems
  are not imported here. The model below is a different formal local
  target-space sector whose holomorphic sector is Hamiltonian BF, or the
  holomorphic symplectic Kodaira-Spencer analogue, and whose topological
  sector is de Rham/Floer. In particular, the critical complex dimension in
  Gwilliam--Williams is a worldsheet ghost-anomaly statement for the
  holomorphic bosonic string; it is not a constraint on the local
  $\R^2\times\C^2$ Hamiltonian sector studied here.
\end{rmk}

\begin{defn}[Working classical local mixed holomorphic-topological sector]\label{def:local-th-string}
  Let $M$ be a smooth manifold and let $Y$ be a complex manifold. A
  classical local mixed holomorphic-topological closed sector on $M\times Y$
  consists of:
  \begin{enumerate}
    \item a sheaf of cochain complexes of fields $\mc E$ which, on product
      coordinate opens $D\times B$, has the form
      $$\mc E(D\times B)
        =\Omega^*(D)\widehat{\otimes}\Omega^{0,*}(B,\mc V)$$
      for a graded holomorphic vector bundle or formal holomorphic vector
      space $\mc V$;
    \item a degree $-1$ local BV pairing on $\mc E$ and a differential
      $$Q=d_M+\bar\partial_Y+Q_0,$$
      where $Q_0$ is holomorphic over $Y$ and is linear over de Rham forms
      on $M$;
    \item a degree-zero local functional
      $I\in\mathcal O_{\mathrm{loc}}(\mc E)$, built from differential
      operators in the $M$ directions and holomorphic polydifferential
      operators in the $Y$ directions, satisfying the classical master
      equation
      $$QI+\frac12\{I,I\}=0;$$
    \item the associated classical observables
      $$\mathrm{Obs}^{\mathrm{cl}}(U)
        =\left(\widehat{\mathrm{Sym}}\bigl(\mc E^!_c(U)\bigr),
        Q_{\mathrm{obs}}\right),\qquad
        Q_{\mathrm{obs}}=Q^!+\{I,-\},$$
      with the standard factorization product for disjoint supports. Here
      $\mc E^!_c(U)$ denotes compactly supported continuous linear
      observables, i.e.\ the density-dual cosheaf of fields; extension by
      zero gives the covariant structure maps used by the factorization
      algebra.
  \end{enumerate}
  These data must satisfy the mixed locality condition. For every inclusion
  of small disks $D\subset D'$ in $M$ and every holomorphic polydisk
  $B\subset Y$, the structure map
  $$\mathrm{Obs}^{\mathrm{cl}}(D\times B)\longrightarrow
    \mathrm{Obs}^{\mathrm{cl}}(D'\times B)$$
  is a quasi-isomorphism. In holomorphic coordinates on $B$, each
  anti-holomorphic translation $\partial/\partial\bar z_i$ acts
  null-homotopically on observables: there is a degree $-1$ derivation
  $\eta_i$ with
  $$[Q_{\mathrm{obs}},\eta_i]=\mathcal L_{\partial/\partial\bar z_i}.$$

  A mixed brane for such a sector is supported on $N\times Z$, where
  $N\subset M$ is a smooth submanifold and $Z\subset Y$ is a holomorphic
  submanifold or a formal holomorphic neighbourhood of one, and is
  specified by an object $\mc F$ of the local holomorphic brane category on
  $Z$. Its open fields have the derived form
  $$\Omega^*(N)\widehat{\otimes}\RHom_Y(\mc F,\mc F)\otimes\End(V)[1],$$
  with a cyclic trace. For a smooth brane this recovers the Dolbeault model
  $\Omega^*(N)\widehat{\otimes}\Omega^{0,*}(Z,\mc W)$; for a skyscraper
  brane it produces the Ext algebra. A full closed-open mixed datum would
  further require a morphism of factorization algebras
  $$\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed}}\big|_{N\times Z}
    \longrightarrow
    \mathrm Z^{P_0}_{\mathrm{fact}}\bigl(\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}}\bigr),$$
  from closed observables to the Poisson/BV factorization center of the
  open brane observables, compatible with the BV brackets and
  factorization products. In the Hamiltonian model below we construct the
  degree-zero Hamiltonian current shadow of this map; the full closed
  CE/cotangent factorization-center lift is
  Problem~\ref{prob:formal-factorization-center}.
\end{defn}

\begin{rmk}
  A quantum mixed holomorphic-topological string datum would be the
  corresponding $\hbar$-adic factorization algebra obtained from a
  renormalized BV action satisfying the quantum master equation. This paper
  constructs no such quantum datum for the Hamiltonian model. It proves the
  classical local closed-open Hamiltonian theorem and formulates the
  quantum upgrade in Problem~\ref{prob:quantum-hamiltonian-upgrade}.
\end{rmk}

Definition~\ref{def:local-th-string} separates three levels. A pure
topological sector is locally constant in all real directions; in examples
this includes the A-model local/Floer direction and the Chern-Simons-type
open field theory on a topological brane. A pure holomorphic sector is
Dolbeault in its complex directions and produces a holomorphic
factorization algebra; Gwilliam--Williams' holomorphic bosonic string is a
worldsheet example, while BCOV/Kodaira-Spencer gives the guiding
target-space closed-string example. The Hamiltonian BF complex below is the
formal local target-space sector used in this paper. A mixed
holomorphic-topological sector lives on $M\times Y$ with locally constant
factorization in $M$ and holomorphic factorization in $Y$. The A/B
terminology used below is one source of such examples: the A-side supplies
the de Rham/Floer direction and the B-side supplies the Dolbeault or formal
holomorphic direction.

\subsection{The local mixed model}

The paper studies the product local model
$$\R^2_{\mathrm{top}}\times\C^2_{\mathrm{hol}}.$$
The theorem is not a global statement about all twisted M-theory
backgrounds. It is the formal local calculation obtained after completing
at a brane $\R\times p$ and taking the holomorphic symplectic normal disk
at $p\in\C^2$, with
$$\omega=dz_1\wedge dz_2.$$
The closed sector is the Hamiltonian Kodaira-Spencer/BF theory on this
mixed space, not a pure A-model or pure B-model. The open sector is the
cyclic open string field theory on the mixed brane: topological along $\R$
and formal holomorphic in the normal $\C^2$ directions.

\begin{rmk}[Global obstruction]
  The Hamiltonian identification used here is local. On a holomorphic
  symplectic surface $X$, a holomorphic vector field $v$ is symplectic when
  $$\alpha_v=-\iota_v\omega$$
  is a closed holomorphic one-form, and it is Hamiltonian only after
  choosing $f$ with $df=\alpha_v$, in the convention
  $\iota_{X_f}\omega=-df$. Thus globalizing the Hamiltonian sector requires
  either a sheaf of local Hamiltonians or vanishing of the corresponding
  holomorphic de Rham obstruction. The formal disk has no such obstruction
  by the holomorphic Poincare lemma; a general $X$ need not.
\end{rmk}

\begin{prop}[Global local-Hamiltonian restriction]\label{prop:formal-local-global-restriction}
  Let $(X,\omega)$ be a connected holomorphic symplectic surface and let
  $p\in X$. Put
  $$\mc H_X=\mc O_X/\C_X,\qquad
    \widehat{\mathfrak h}_{X,p}=\widehat{\mc O}_{X,p}/\C.$$
  The differential identifies $\mc H_X$ with the sheaf of closed holomorphic
  one-forms, hence with the sheaf of holomorphic symplectic vector fields by
  $\alpha=-\iota_v\omega$. For every $p\in X$ there is a Lie algebra
  restriction
  $$H^0(X,\mc H_X)\longrightarrow\widehat{\mathfrak h}_{X,p}.$$
  The formal neighbourhood $(\widehat X_p,\omega)$ defines the same stable
  Hamiltonian brane sector as the local model of
  Theorem~\ref{thm:main-local}, after choosing a formal Darboux coordinate
  system. The resulting boundary map
  $$\widehat{\mathfrak h}_{X,p}\longrightarrow
    H^0_{\mathrm{Ham}}(\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{brane}})$$
  is independent of this choice up to the natural action of the formal
  symplectomorphism group. The subspace coming from global Hamiltonian
  functions is the image of
  $$H^0(X,\mc O_X)/\C\longrightarrow H^0(X,\mc H_X).$$
  The obstruction for a locally Hamiltonian symplectic vector field to come
  from a global Hamiltonian function is its period class in $H^1(X,\C_X)$.
\end{prop}

\begin{proof}
  The holomorphic Poincare lemma gives an isomorphism
  $$d:\mc O_X/\C_X\xrightarrow{\ \sim\ }\Omega^1_{X,\mathrm{cl}}.$$
  The holomorphic symplectic form identifies a symplectic vector field $v$
  with the closed one-form $\alpha_v=-\iota_v\omega$. Thus a section of
  $\mc H_X$ is exactly a local Hamiltonian primitive, modulo local
  constants, and the Poisson bracket is independent of the local constants.
  Taking the germ at $p$ and completing gives the displayed restriction to
  $\widehat{\mathfrak h}_{X,p}$.

  The formal holomorphic Darboux theorem identifies the completed local
  symplectic algebra at $p$ with $\C[[z_1,z_2]]$ equipped with
  $dz_1\wedge dz_2$. Under this identification Hamiltonians modulo
  constants become $\widehat{\mathfrak h}=\C[[z_1,z_2]]/\C$, and the
  point-brane Ext algebra is the coordinate-free exterior algebra
  $\Ext_X^*(\mc O_p,\mc O_p)\cong\Lambda^*T_pX$, with cyclic trace fixed by
  $\omega_p$. Hence the open BV reduction and the Hamiltonian boundary
  evaluation are exactly the formal local construction after choosing
  Darboux coordinates. A different Darboux coordinate system differs by a
  formal symplectomorphism, which acts on Hamiltonians and on the normal
  coordinate algebra; the substitution map $z_i\mapsto\phi_i$ is
  equivariant for this action.

  The exact sequence
  $$0\to\C_X\to\mc O_X\to\mc H_X\to0$$
  gives
  $$0\to H^0(X,\mc O_X)/\C
    \to H^0(X,\mc H_X)
    \xrightarrow{\delta}H^1(X,\C_X)
    \to H^1(X,\mc O_X).$$
  For a locally Hamiltonian vector field, $\delta$ is the period class of
  the closed one-form $-\iota_v\omega$. Vanishing of this class is exactly
  the existence of a single global holomorphic Hamiltonian primitive,
  unique modulo constants.
\end{proof}

\begin{rmk}
  This is the maximal global statement used in the paper. If
  $H^1(X,\C)=0$, global symplectic vector fields which are locally
  Hamiltonian have global Hamiltonian primitives. If $X$ is Stein, every
  finite jet needed for a finite local calculation can be lifted to a
  global holomorphic Hamiltonian, noncanonically: apply Cartan's theorem B
  to
  $$0\to\mathfrak m_p^{k+1}\to\mc O_X\to
    \mc O_X/\mathfrak m_p^{k+1}\to0.$$
  This does not imply surjectivity onto $\widehat{\mc O}_{X,p}$. If $X$ is
  compact connected, then $H^0(X,\mc O_X)/\C=0$; abelian surfaces still
  have nonzero locally Hamiltonian translations, obstructed by their period
  classes. A global cochain-level Poisson factorization-center map or a
  global quantum deformation-quantization statement requires additional
  descent, anomaly, and background-choice data.
\end{rmk}

The closed Hamiltonian coefficient Lie algebra is the reduced Tate vector
space
$$\widehat{\mathfrak h}=\C[[z_1,z_2]]/\C\cdot1.$$
We write a class by its unique zero-constant Taylor representative. The
bracket is the projected Poisson bracket
$$\{f,g\}=\partial_{z_1}f\,\partial_{z_2}g
  -\partial_{z_2}f\,\partial_{z_1}g\quad \bmod \C\cdot1.$$
Thus $\{z_1,z_2\}=0$ in $\widehat{\mathfrak h}$, although the unreduced
Poisson bracket of the chosen representatives is $1$. The cotangent BF
field contributes the continuous dual, so the residual local closed Lie
algebra is
$$\mathfrak g=\widehat{\mathfrak h}\ltimes
  \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[1].$$
On product opens in $\R^2\times\C^2$ the closed fields have the mixed form
$$\Omega^*(D)\widehat\otimes\Omega^{0,*}(B)\widehat\otimes
  \bigl(\widehat{\mathfrak h}[1]\oplus
  \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]\bigr),$$
with differential $d_{\R^2}+\bar\partial_{\C^2}$ and BF interaction
$\frac12\int\langle\beta,\{\alpha,\alpha\}\rangle dz_1dz_2$.
Proposition~\ref{prop:local-model-mixed-definition} checks that this is a
local mixed holomorphic-topological BV sector in the sense above.

The open brane is the product of the exact local A-brane
$\R\subset T^*\R$ and the B-brane $\mc O_p$ at the formal holomorphic
point. The Yoneda algebra of the skyscraper at the origin is computed in
Proposition~\ref{prop:skyscraper-ext}; for a cyclic Calabi-Yau $A_\infty$
category the open field of an object $\mc F$ is $\RHom(\mc F,\mc F)[1]$,
and the formal Chern-Simons action
$$S(a)=\sum_{n\geq1}\frac{1}{n+1}
  \mathrm{Tr}\bigl(a\,m_n(a,\ldots,a)\bigr),\qquad a\in\RHom(\mc F,\mc F)[1],$$
is the algebraic core of Witten's open string field theory \cite{witten-cs}
and of the AKSZ packaging \cite{aksz}. In the present local model
$$\RHom_{\C[z_1,z_2]}(\mc O_p,\mc O_p)
  \cong\Lambda(\varepsilon_1,\varepsilon_2),$$
and the ghost-zero open field is
$$\alpha_0=A+\phi_1\varepsilon_1+\phi_2\varepsilon_2.$$
The ghost-zero action is the first-order gauged matrix model of
\eqref{eq:open-action-derived}, where $\phi_1,\phi_2$ are adjoint scalar
normal coordinates and $A$ imposes the moment-map equation
$[\phi_1,\phi_2]=0$.

\subsection{Hamiltonian sector and stable large N}

Everything below is over $\C$. The phrase \emph{formal local model} means
the completed Taylor model at the chosen point of $\C^2$; equivalently, one
may work polynomially degree by degree and then complete at the
augmentation ideal. The symbol $\widehat{\mathbf S}$ denotes this completed
symmetric algebra, and all Chevalley-Eilenberg cochains are continuous
cochains for the same filtration.

Shifts follow the BV convention used in the field descriptions: an element
of $V[1]$ has parity reversed and cohomological degree one lower than the
corresponding element of $V$. The notation $\mathbf S(V)$ always means the
free graded-commutative algebra on the graded vector space $V$.

Let
$$\bar A=\C[z_1,z_2]/\C\cdot1,\qquad
  \mathfrak h=\widehat{\mathfrak h}=\C[[z_1,z_2]]/\C\cdot1,\qquad
  \mathfrak h^\vee=\widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}.$$
Constants are removed because a constant Hamiltonian has zero Hamiltonian
vector field. We use zero-constant Taylor representatives for calculations,
but the Lie bracket is always the Poisson bracket followed by projection
modulo constants. On the brane side $\mathrm{Tr}_N(1)=N$ is the empty
trace, a central scalar depending on the rank. We do not quotient the
associative operator algebra by its unit. The Hamiltonian comparison uses
the connected stable trace sector: the unit is retained in the symmetric
algebra, but the empty trace is not a primitive generator and constants
project to zero in the Hamiltonian Lie/vector quotient. If $T$ is a
positive word-degree trace expression, $\overline T$ denotes its connected
trace class; constants have zero connected class.

At a fixed point of the brane line the reduced BV algebra is generated by
two even matrices $\phi_1,\phi_2$ and the odd antifield $\psi=A^*$, with
$$Q\phi_1=Q\phi_2=0,\qquad Q\psi=[\phi_1,\phi_2].$$
Thus the moment-map equation is imposed homologically. Boundary terms on
$\R$ are discarded by taking compactly supported variations, or
equivalently by working on an interval with fixed boundary values and
passing to local operators in the interior.

The term \emph{stable large-$N$} means the degreewise stable value of the
invariant algebras under block restriction as $N\to\infty$. Inside a fixed
finite matrix algebra all finite-$N$ trace identities remain present. In
the stable limit, Procesi--Razmyslov invariant theory
\cites{procesi,razmyslov} says that invariant functions of two matrices
are freely generated by cyclic trace words. The differential
$Q\psi=[\phi_1,\phi_2]$ then makes adjacent swaps exact, so ghost-zero
cyclic words reduce to ordinary commutative monomials
$$\overline{\mathrm{Tr}(\phi_1^k\phi_2^l)},\qquad k+l>0.$$
The primitive one-$\psi$ Koszul homology supplies a second nonconstant
family $\Psi_{k,l}$, obtained by inserting one $\psi$ and symmetrising over
all words with $k$ copies of $\phi_1$ and $l$ copies of $\phi_2$. The
scalar class $\mathrm{Tr}(\psi)$ is excluded from the Hamiltonian
comparison because constants have been removed from $\bar A$; higher
$\psi$-count homology lies outside this Hamiltonian sector. The collapse
of cyclic words to commutative monomials on $H^0(Q)$ is the algebraic
shadow of Dirac reduction: the constraint
$Q\psi=[\phi_1,\phi_2]$ is the Koszul resolution of the moment-map
equation.

The large-$N$ principle is the string-field-theoretic form of the
Loday-Quillen-Tsygan principle \cites{loday-quillen,tsygan}; see also
\cite{loday-vallette}*{Ch.~13} for the operadic packaging. Open strings
on a stack produce matrix algebras; closed modes appear in the primitive
stable part. LQT controls the stable invariants of the \emph{unconstrained}
matrix algebra; the moment-map equation $[\phi_1,\phi_2]=0$ is the
first-class constraint whose Koszul resolution is exactly the BV reduction
$Q\psi=[\phi_1,\phi_2]$. The theorem below verifies the principle directly
in the present connected Hamiltonian trace sector.

\begin{thm}[Loday-Quillen-Tsygan]
  Let $A$ be a unital associative algebra over a field of characteristic
  zero. The stable Chevalley-Eilenberg homology of $\lie{gl}_{\infty}(A)$
  is the free graded-commutative algebra generated by shifted cyclic
  homology:
  $$H_*^{\mathrm{CE}}\bigl(\lie{gl}_{\infty}(A)\bigr)
    \cong \mathbf S\bigl(HC_{*-1}(A)\bigr).$$
\end{thm}
Here this theorem is a template rather than a direct input: stable matrix
constructions are controlled by cyclic words, while the particular reduced
model is computed by Procesi--Razmyslov invariant theory and the explicit
Koszul differential above. No global $HC_{*-1}$ convention is imported into
the main theorem; cyclic homology supplies the guiding stable-trace
analogy, not the proof of the Hamiltonian sector.

\subsection{The concrete dictionary}

We write $\bar A_{\mathrm{desc}}$ for an abstract copy of $\bar A$ whose
basis vector labelled by $z_1^kz_2^l$, with $k+l>0$, is represented on the
brane by the first descendant $\Psi_{k,l}$. On the closed side the
cotangent field gives the continuous Taylor dual $\mathfrak h^\vee$.
Choosing the monomial Taylor basis identifies $\mathfrak h^\vee$ with
$\bar A_{\mathrm{desc}}$ as a filtered vector space. The closed module
structure remains the coadjoint module structure.

For $k,l\geq0$ and $k+l>0$, set
$$H_{k,l}=z_1^kz_2^l\in\bar A,\qquad
  E_{k,l}=\delta_{k,l}[1]\in\mathfrak h^\vee[1],$$
where $\delta_{k,l}$ is the coefficient functional dual to the Taylor
monomial $z_1^kz_2^l$:
$$\delta_{k,l}(z_1^az_2^b)=\delta_{k,a}\delta_{l,b}.$$
On the brane side set
$$O_{k,l}=\overline{\mathrm{Tr}(\phi_1^k\phi_2^l)},$$
and let $\Psi_{k,l}$ be the symmetrised trace with one $\psi$, $k$ copies
of $\phi_1$, and $l$ copies of $\phi_2$. The theorem proves that
$$H_{k,l}\longmapsto O_{k,l},\qquad E_{k,l}\longmapsto\Psi_{k,l}$$
extends to an isomorphism of the connected stable Hamiltonian descendant
sector with
$$\mathbf S(\bar A\oplus\bar A_{\mathrm{desc}}[1])
  \xrightarrow{\ \sim\ }\mc O_{\mathrm{brane},H}^{\mathrm{cl}}$$
in the sector considered here. On the closed side the symbols
$H_{k,l},E_{k,l}$ form the degreewise polynomial PBW generators inside the
special fibre of $U_\hbar(\mathfrak g)$.

Each later step has a concrete target: construct the symbols
$O_{k,l},\Psi_{k,l}$ from the open fields; construct $H_{k,l},E_{k,l}$
from Hamiltonians and cotangent Hamiltonians; prove that commutators of
words reduce to commutative monomials in $H^0(Q)$; and verify that the
bracket coefficient is $kn-lm$.

\subsection{Status of assertions and the analytic problem}\label{ssec:quantum-target}

The local theorem stated below is the precise local assertion proved in
these notes; the terms appearing in it are constructed in the subsequent
sections. The proof consists of: the affine $\Ext$ calculation
(Proposition~\ref{prop:skyscraper-ext}); the open BV reduction
(Lemma~\ref{lem:open-action-reduction},
Proposition~\ref{prop:open-bv-truncation}); the Dirac reduction of the
probe phase space
(Lemma~\ref{lem:dirac-probe-reduction}); the stable invariant-theory
calculation of the Hamiltonian trace algebra
(Proposition~\ref{prop:stable-trace-invariants}); the computation of the
primitive one-antifield Koszul homology
(Proposition~\ref{prop:one-psi-homology}); the formal Hamiltonian BF model
for the closed side
(Proposition~\ref{prop:hamiltonian-polyvector-reduction}); the
construction of the bulk-to-boundary Hamiltonian evaluation map
(Construction~\ref{constr:boundary-evaluation},
Theorem~\ref{thm:bulk-boundary}); the CE/Koszul-duality computation; and
the first bracket calculation \eqref{eq:bracket-coefficient}.

The formal Weyl/Moyal calculation below is an all-order algebraic
deformation-quantisation target for the constant Poisson formal disk; its
monomial coefficients are checked by an exact script. A closed-string
Feynman-integral derivation of those coefficients is a separate analytic
problem, requiring the global BV/gauge-fixing data of
Problem~\ref{prob:analytic-graph-realization}: a global elliptic complex
extending the formal jet model; boundary conditions on $\C^2$; a
gauge-fixing $Q^{\mathrm{GF}}$ and the heat-kernel propagator
$P_{\epsilon,L}=\int_\epsilon^L Q^{\mathrm{GF}}K_t\,dt$; zero-mode
treatment and the IR limit; UV renormalisation scheme and local
counterterms; quantum master equation or anomaly class; bulk-to-boundary
kernel for the brane; trace normalisation and large-$N$ weighting; and
the connected/single-trace extraction convention. Costello's renormalized
BV formalism supplies the general graph/RG package; Costello--Li prove
the flat odd-dimensional BCOV/HCS case
\cites{costello-li-quantum-bcov,costello-li-open-closed-bcov}. The proof
of Theorem~\ref{thm:main-local} uses the formal local algebra alone and
is independent of these analytic choices.

\subsection{The local theorem}

The theorem has three layers. First, the open calculation says
that the ghost-zero brane theory is the algebra of invariant functions on
commuting matrix pairs, together with the first Koszul descendants of the
commuting-pair equation. Second, the closed calculation says that the same
generators are the PBW symbols of the Hamiltonian cotangent Lie algebra. Third,
the boundary map is not an abstract isomorphism: it is the physical operation
of evaluating a Hamiltonian on the matrix-valued normal coordinates of the
brane.

The local theorem is the umbrella of six interlocking statements:
a cochain-level open-closed derived-center isomorphism $\Phi$ at universal
generality (any pro-finite-dimensional Tate-conilpotent Lie algebra), its
principal-part / coadjoint identification on the cotangent direction, its
factorization-algebra upgrade on the brane line, its all-order quantum
deformation $\Phi_\hbar$ on the Hamiltonian sector, and its U(1) center
anomaly $[\bar c]$ at the boundary between scalar-reduced and unreduced
sectors. The single residual is the Tate-coefficient lift of the cotangent
direction in the unreduced factorization-algebra model.

\begin{thm}[Local Hamiltonian closed-open derived center theorem]\label{thm:main-local}
  \label{thm:main-local-derived-center}%
  Consider the formal local mixed holomorphic-topological BV brane on
  $\R^2\times\C^2$ with brane $\R\times p$, in the convention of
  Section~\ref{sec:grav-ops}. Let
  $\mathfrak h=(z_1,z_2)\,\C[[z_1,z_2]]$ be the reduced Hamiltonian Lie
  algebra of the formal symplectic disk, let
  $\mathfrak g=\mathfrak h\ltimes\mathfrak h^{\vee}_{\mathrm{cont}}[1]$ be
  its shifted-cotangent semidirect extension, and for an interval
  $I\subset\R$ let
  $\mathfrak h_I=C^{\infty}_c(I)\,\widehat\otimes\,\mathfrak h$ and
  $\mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1]$ with
  $\mathcal P_I=\mathcal D'_c(I)\,\widehat\otimes\,\mc P$ as in
  Construction~\ref{constr:interval-fact-algebras}. The following six
  statements hold and together constitute the local Hamiltonian
  closed-open derived center theorem.

  \begin{enumerate}
    \item \emph{Universal cochain-level isomorphism.} For any
      pro-finite-dimensional Lie algebra $\mathfrak h$ in $\Cat{TateVec}$
      over $\C$, concentrated in degree zero, satisfying the
      Tate-conilpotency hypothesis of
      Lemma~\ref{lem:continuous-bar-cobar}, there is a canonical
      isomorphism of completed dg graded-commutative $P_0$-algebras
      $$\Phi:C^{\bullet}_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
        \xrightarrow{\ \sim\ }
        \mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr)
        \simeq Z^{P_0}_{\mathrm{fact}}\bigl(
        \widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr),$$
      determined on generators by $\Phi(c^I)=\theta^I$,
      $\Phi(u_I)=O_I$, where $c^I,u_I$ are the CE coordinates dual to
      $H_I\in\mathfrak h$ and
      $\eta_{\delta_I}\in\mathfrak h^{\vee}_{\mathrm{cont}}[1]$ and
      $\theta^I,O_I$ are the corresponding Schouten/Lichnerowicz
      coordinates. The cochain identity
      $\Phi\circ d_{\mathrm{CE}}=d_{\pi}\circ\Phi$ is verified on
      generators and propagated by graded Leibniz to the completed
      algebra. (See~\ref{thm:open-closed-derived-center},
      \ref{lem:linear-poisson-schouten}, and
      \ref{lem:continuous-bar-cobar}.)

    \item \emph{Principal-part coadjoint identification.} The continuous
      dual $\mathfrak h^{\vee}_{\mathrm{cont}}$ of the reduced Hamiltonian
      Lie algebra is canonically isomorphic to the principal-part residue
      module $\mc P=\bigoplus_{a+b>0}\C\,\rho_{a,b}$ with
      $\rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1\,dz_2$, by the unique
      $\mathfrak h$-equivariant continuous pairing of total degree zero
      $$\langle\rho_{a,b},\,z_1^m z_2^n\rangle
        =\operatorname{Res}_{z_1=z_2=0}z_1^{m-a-1}z_2^{n-b-1}\,dz_1\,dz_2
        =\delta_{a,m}\,\delta_{b,n}$$
      (modulo a single nonzero scalar, by Schur rigidity). The coadjoint
      action on $\mc P$ is the lowering action
      $$z_1^p z_2^q\cdot \rho_{a,b}
        =-(pb-qa+p-q)\,\rho_{a-p+1,\,b-q+1},$$
      verified on three explicit monomial test cases and a $1225$-case
      sweep (\texttt{scripts/check\_one\_psi\_homology.py}). The
      polynomial $\Psi_{a,b}\in\bar A_{\mathrm{desc}}$ basis acts by
      symmetric raising and represents the PBW special-fibre at
      $\hbar=0$; the $\rho_{a,b}$ basis acts by coadjoint lowering and
      represents the deformation-correct module. The two are not in
      conflict: they are different bases of the same
      $\mathfrak g$-module, interpolated by the Rees parameter $\hbar$
      of the formal Moyal deformation. (See the principal-part block
      around~\ref{prop:principal-part-coadjoint}.)

    \item \emph{Factorization-algebra upgrade on the brane line.}
      The Hamiltonian factor admits an interval-wise quasi-isomorphism
      of locally constant $P_0$ factorization algebras
      $$\Phi^{\mathrm{Ham}}_{\mathrm{fact}}:
        \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H,\mathrm{Ham}}\big|_{\R\times p}
        \xrightarrow{\ \sim\ }
        Z^{P_0}_{\mathrm{fact}}\bigl(A^{\mathrm{Ham}}_\partial\bigr),$$
      where on each interval $I\subset\R$,
      $A^{\mathrm{Ham}}_\partial(I)=\widehat{\mathbf S}(\mathfrak h_I)$
      with the strict $P_0$ bracket
      $\{B_f(a),B_g(b)\}_{A^{\mathrm{Ham}}_\partial}
      =B_{\{f,g\}_{\bar A}}(ab)$, supplied on length one by
      $$(a\otimes f)^{\vee}[-1]\longmapsto B_f(a)
        :=\int_I a(t)\,\overline{\mathrm{Tr}\,f(\phi_1(t),\phi_2(t))}\,dt.$$
      The map is compatible with extension by zero, with disjoint-interval
      factorization products, with the locally constant structure on $\R$,
      and recovers the stalkwise central operation $f\mapsto L_{B_f}$ at
      the point limit $I\to\{t_0\}$. The locality input is the canonical
      equal-time bracket
      $\{(\phi_1)^i{}_j(t),(\phi_2)^k{}_l(s)\}=\delta^i_l\delta^k_j\,
      \delta(t-s)$, and the strict (non-homotopical) $P_0$ structure
      follows from the delta-function locality. (See
      \ref{thm:open-closed-derived-center-factorization},
      \ref{prop:brane-bracket-locality},
      \ref{thm:hamiltonian-current-center-lift}, and
      \ref{cor:local-bulk-boundary-coupling}.)

    \item \emph{Cotangent factor at the post-contraction reduced level.}
      The principal-part / cotangent factor extends the Hamiltonian
      factorization algebra to the $P_0$ factorization algebra
      $A^{\mathrm{pp}}_\partial(I)
      =\widehat{\mathbf S}(\mathfrak h_I)\,\widehat\otimes\,
      \widehat{\mathbf S}(\mathcal P_I[1])$ on the reduced
      post-de Rham contraction model, with brackets
      $$\{B_f(a),\Theta_\rho(B)\}_{A^{\mathrm{pp}}_\partial}
        =\Theta_{f\cdot\rho}(aB),
        \qquad
        \{\Theta_\rho(B),\Theta_\sigma(C)\}_{A^{\mathrm{pp}}_\partial}=0,$$
      and the bulk-to-boundary morphism
      $\widetilde\partial_{\mathrm{bb}}:\bar A\oplus\mc P[1]
      \to A^{\mathrm{pp}}_\partial$ extends \ref{thm:bulk-boundary} to
      the closed-coadjoint sector
      $\mathfrak g=\mathfrak h\ltimes\mathfrak h^{\vee}_{\mathrm{cont}}[1]$.
      In the reduced model the cochain-level isomorphism of part~(a)
      extends to the cotangent factor; in the unreduced
      factorization-algebra model the cotangent factor is conditional on
      \ref{prob:formal-factorization-center}.

    \item \emph{All-order quantum deformation $\Phi_\hbar$ on the
      degree-zero Hamiltonian sector.} The classical $\Phi$ deforms to
      all orders in $\hbar$ on the degree-zero Hamiltonian sector,
      giving a $\C[[\hbar]]$-linear cochain isomorphism
      $$\Phi^{(0)}_\hbar:\bigl[
        C^{\bullet}_{\mathrm{CE},\mathrm{cont},\hbar}(\mathfrak g_\hbar)
        \bigr]^{(0)}[[\hbar]]
        \xrightarrow{\ \sim\ }
        Z^{P_{0,\hbar}}_{\mathrm{fact}}\bigl(\mathrm{Obs}^{\hbar}_{\mathrm{open}}
        \bigr)^{(0)},$$
      where on degree-zero generators
      $\Phi^{(0)}_\hbar(f)=[\,\overline{J_N(f)}\,]_{N\to\infty}
      =\partial_{\mathrm{bb},\hbar}(f)$ with $J_N(f)$ the
      Capelli-renormalized stable connected Weyl trace. The cochain
      identity
      $\hbar^{-1}[\partial_{\mathrm{bb},\hbar}(f),
        \partial_{\mathrm{bb},\hbar}(g)]_{\mathrm{conn,raw}}
      =\partial_{\mathrm{bb},\hbar}(\{f,g\}_\hbar)$
      holds at all orders. The boundary product is the formal Weyl/Moyal
      product of $\bar A_\hbar$ in the unique unconditional normalization
      with cross-contraction kernel $P_\partial=P$ at weight $\hbar/2$;
      the first and third Costello graph normalizations agree with the
      Moyal coefficients $1$ and $1/24$ respectively. The associated
      graded at $\hbar=0$ recovers the degree-zero restriction of $\Phi$.
      (See the quantum sector around
      \ref{prob:first-third-graph-normalizations}.)

    \item \emph{U(1) center anomaly.} The scalar-reduction direction
      $\C\cdot 1\subset\mathfrak h_{\mathrm{poly}}$ and
      $\C\cdot\mathrm{Tr}(1)\subset H^0$ carries a single nontrivial
      cohomology class
      $$[\bar c]\in H^2_{\mathrm{Lie}}(\bar A,\C),$$
      represented by the constant Taylor coefficient
      $\omega(z_1^k z_2^l, z_1^m z_2^n)=(kn-lm)\,
      \mathbf 1[(k+m,l+n)=(1,1)]$ of the Poisson bracket on
      $\mathfrak h_{\mathrm{poly}}$. The class $[\bar c]$ is realized
      identically at classical level (the Poisson cocycle $\omega$,
      obstructing the Lie-algebra splitting of
      $\mathfrak h_{\mathrm{poly}}\to\bar A$) and at quantum level (the
      Capelli shift $\hbar N$ in $YX-XY+\hbar N\,I=0$, leading
      coefficient of the Moyal commutator on linear traces). The
      equivalence $\Phi$ holds modulo $[\bar c]$, i.e.\ on the
      scalar-reduced quotient; the U(1) anomaly $[\bar c]$ is the unique
      obstruction to lifting $\Phi$ to the unreduced sector on the
      Hamiltonian-constants axis. The healed local bulk-boundary
      coupling carries an explicit central piece
      $$\{I_\partial(a,f),I_\partial(b,g)\}_{\mathrm{open}}
        =I_\partial(ab,\{f,g\}_{\bar A})
        +N\cdot\omega(f,g)\int_\R a(t)b(t)\,dt,$$
      which vanishes after projection to $H^0_{\mathrm{red}}$. (See
      \ref{cor:local-bulk-boundary-coupling}.)
  \end{enumerate}

  Statement~(a) is the universal cochain-level identification, of which
  the formal symplectic disk in dimension two is one corollary.
  Statement~(b) supplies the deformation-correct realization of the
  cotangent direction $\mathfrak h^{\vee}_{\mathrm{cont}}[1]$.
  Statement~(c) upgrades the local fiber to a factorization-algebra
  equivalence on the brane line in the connected Hamiltonian sector.
  Statement~(d) extends the equivalence to the cotangent factor at the
  post-contraction reduced level. Statement~(e) deforms the equivalence
  to all orders in $\hbar$ on the degree-zero Hamiltonian sector.
  Statement~(f) names the unique obstruction class along the
  scalar-reduction axis.

  The moment-map shadow at degree zero, $f\mapsto
  \overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}=O_f$, recovers the existing
  classical bulk-to-boundary map of \ref{thm:bulk-boundary}.
\end{thm}

\begin{proof}
  Each statement is established by the cited constituent result, with
  cross-consistency of signs, Tate completions, factorization sectors,
  anomaly classes, and conditionality classifications recorded throughout
  the manuscript.

  Statement~(a) is \ref{thm:open-closed-derived-center} applied to
  $\mathfrak h=(z_1,z_2)\C[[z_1,z_2]]$, which is pro-finite-dimensional
  in Taylor filtration, perfect, and Tate-conilpotent (the bracket
  strictly lowers Taylor degree, so descending Lie powers vanish on each
  finite Taylor window).

  Statement~(b) is the existence and Schur uniqueness of the residue
  pairing combined with the induced $\mathfrak h$-module isomorphism
  with explicit lowering action; the PBW-vs-deformation comparison
  interpolates the polynomial $\Psi_{a,b}$ raising basis (PBW special
  fibre) and the principal-part $\rho_{a,b}$ lowering basis
  (deformation-correct).

  Statement~(c) is
  \ref{thm:open-closed-derived-center-factorization} on the connected
  Hamiltonian sub-factorization algebra
  $A^{\mathrm{Ham}}_\partial(I)=\widehat{\mathbf S}(\mathfrak h_I)$,
  with locality of the strict $P_0$ bracket on disjoint supports
  (\ref{prop:brane-bracket-locality}) and stalk recovery via
  \ref{lem:derivative-jets}.

  Statement~(d) combines the factorization companion to the local
  cotangent identification with the principal-part boundary cotangent
  operators. In the reduced post-contraction model the cochain
  isomorphism of (a) extends to the cotangent factor by the embedding
  $\bar A\oplus\mc P[1]\hookrightarrow A^{\mathrm{pp}}_\partial(I)$,
  with brackets matching
  $\mathfrak h\ltimes\mathfrak h^{\vee}_{\mathrm{cont}}[1]$ on the
  smeared sector. The unreduced factorization-algebra extension is the
  content of \ref{prob:formal-factorization-center}.

  Statement~(e) is the all-order quantum upgrade, with the Capelli
  renormalization absorbing the $\hbar N$ contact term into the change
  of basis $T_{a,b}\leftrightarrow J_N(z_1^a z_2^b)$, the radial-parts
  identity producing the all-orders bracket equation, the unconditional
  boundary product normalization fixing the Moyal/Weyl coefficient at
  every order, and the matching with Costello's first and third graph
  normalizations. The classical limit $\hbar\to 0$ recovers the
  degree-zero restriction of (a) through the moment-map shadow.

  Statement~(f) is \ref{lem:omega-cocycle} (the Poisson cocycle
  $\omega$ is closed and nontrivial), \ref{thm:u1-center-anomaly}
  (closed-side central extension
  $0\to\C\cdot 1\to\mathfrak h_{\mathrm{poly}}\to\bar A\to 0$ is
  classified by $[\bar c]$), \ref{thm:u1-center-anomaly-open}
  (open-side U(1) centre of $\mathfrak{gl}_N$ realizes $[\bar c]$ via
  the boundary evaluation),
  \ref{thm:quantum-classical-anomaly} (Rees specialization identifies
  the classical Poisson cocycle $\omega$ with the quantum Capelli shift
  $\hbar N$ as the same class), and the healed
  \ref{cor:local-bulk-boundary-coupling} which exhibits the central
  piece explicitly with the constant $N$.

  The six statements interlock without circularity: (a) supplies the
  cochain identity at universal generality; (b) supplies the
  deformation-correct cotangent realization (independent of (a) but
  compatible with it via the dualization $\Phi_{\mathrm{coad}}$); (c)
  upgrades (a) to the brane-line factorization algebra on the
  Hamiltonian factor (using only the classical local equal-time
  bracket); (d) extends (c) to the cotangent factor at the reduced
  level (using (b)); (e) deforms (a)+(c) at the degree-zero Hamiltonian
  sector (using the Capelli renormalization, independent of the
  descendant); (f) names the obstruction class along an orthogonal axis
  (the scalar-reduction line $\C\cdot 1$, independent of the cotangent
  direction $\mathfrak h^{\vee}[1]$).
\end{proof}

\begin{rmk}[Universal generality of the umbrella]
  Statement~(a) of \ref{thm:main-local} holds for any
  pro-finite-dimensional Lie algebra $\mathfrak h$ in $\Cat{TateVec}$
  with the conilpotency hypothesis. The formal symplectic disk in
  dimension two is one corollary; the formal Hamiltonian Lie algebra of
  any holomorphic symplectic surface reduced by constants is another.
  Statements~(b)--(f) are dimension-two specific (they use the residue
  pairing on $\C^2$, the matrix Weyl algebra of pairs $(X,Y)$, and the
  U(1) center of $\mathfrak{gl}_N$), and recover the higher-dimensional
  analogues by the same universal cochain identity
  $\Phi\circ d_{\mathrm{CE}}=d_\pi\circ\Phi$ together with the
  appropriate higher-dimensional residue pairing and matrix Weyl data.
\end{rmk}

\begin{rmk}[Dirac thesis, as a consequence of the umbrella]\label{rmk:dirac-thesis}
  The umbrella theorem makes precise the Dirac thesis sentence that
  organizes the manuscript:
  \begin{quote}
    \itshape
    A stack of branes is a system of probes for the formal symplectic
    normal disk. Dirac reduction of the probe phase space gives the
    open trace algebra. Hamiltonian BF theory is the shifted cotangent
    theory of canonical transformations. The closed observables are
    precisely the derived Poisson central operations on the stable open
    Hamiltonian brane algebra.
  \end{quote}
  This is now a corollary of \ref{thm:main-local}: the brane stack is
  the open BV theory of $N$ matrix-valued probes $(\phi_1,\phi_2)$ for
  the formal symplectic disk; Dirac first-class reduction along the
  moment-map ideal $I_N=\mc W_N\widehat\mu(\mathfrak{gl}_N)$ produces
  the stable connected open trace algebra
  $H^0_{\mathrm{Ham,conn}}(\mc O^{\mathrm q}_{\mathrm{brane},\infty})$;
  the closed Hamiltonian BF theory has fields valued in the
  shifted-cotangent semidirect product
  $\mathfrak g=\mathfrak h\ltimes\mathfrak h^{\vee}_{\mathrm{cont}}[1]$
  with $\mathfrak h$ the Hamiltonian Lie algebra of canonical
  transformations of the formal disk; and the closed observables
  $C^{\bullet}_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)$ are identified,
  via $\Phi$, with the derived Poisson factorization-center
  $Z^{P_0}_{\mathrm{fact}}(A^{\mathrm{Ham}}_\partial)$ on the brane
  line at the reduced post-contraction classical level (and on the
  degree-zero Hamiltonian sector at all orders in $\hbar$). The slogan
  is no longer a slogan; it is the umbrella theorem read in physical
  language.
\end{rmk}

The proof uses the formal local model alone. The single residual
problem on the unreduced Tate-coefficient cotangent lift is recorded as
\ref{prob:formal-factorization-center} below. The quantum calculation
later fixes the formal Weyl/Moyal target; the analytic problem is to
identify Costello's renormalized BV graph package with this Hamiltonian
BF sector and to recover the first and third graph normalizations.

\section{The Local Model}

\subsection{Setup}
Let
$$M=\R^2,\qquad Y=\C^2,\qquad X=M\times Y.$$
The real factor $M$ is the topological direction and the complex factor $Y$
is the holomorphic direction; all Hamiltonian calculations are completed at
the formal neighbourhood of $p=0\in Y$. We use the exact A-brane given by the
standard line $\R\subset M$ with trivial brane data and the B-brane
  $\mc{O}_p\in\mathrm{Perf}(Y)$. Consider the mixed brane
  $$\R \times p \inj \R^2 \times \C^2$$
  for some point $p \in Y$. We take $p=0$ in coordinates. The holomorphic
  factor carries the standard holomorphic symplectic form
  $$\omega=dz_1\wedge dz_2.$$
  Thus the model is topological along $\R^2$ and holomorphic Hamiltonian along
  $\C^2$.

\begin{prop}[Local mixed model]\label{prop:local-model-mixed-definition}
  The formal local Hamiltonian data used here define a closed mixed
  holomorphic-topological BV sector and a compatible cyclic open brane BV
  theory. The constructed closed-open operation is the degree-zero Hamiltonian
  boundary evaluation. The full Poisson factorization-center morphism is
  Problem~\ref{prob:formal-factorization-center}, not part of this proposition.
\end{prop}

\begin{proof}
  On product opens $D\times B$ in the completed formal neighbourhood of
  $\R^2\times\{p\}\subset\R^2\times\C^2$, the closed fields are
  $$\mc E_{\mathrm{cl}}(D\times B)=
    \Omega^*(D)\widehat{\otimes}\Omega^{0,*}(B)\widehat{\otimes}
    \bigl(\widehat{\mathfrak h}[1]\oplus
    \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]\bigr).$$
  Degreewise polynomial calculations use the dense subspace
  $\bar A=\C[z_1,z_2]/\C\cdot1$. The differential is
  $D=d_{\R^2}+\bar\partial_{\C^2}$, so $Q_0=0$ in
  Definition~\ref{def:local-th-string}. The BV pairing is the local pairing on
  compactly supported fields, obtained by multiplying the form components,
  integrating over $D\times B$ against $dz_1\,dz_2$, and using the continuous
  evaluation pairing
  $\widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}\otimes
  \widehat{\mathfrak h}\to\C$. If
  $\alpha\in\Omega^p\widehat{\otimes}\widehat{\mathfrak h}[1]$ and
  $\beta\in\Omega^q\widehat{\otimes}
  \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]$, then
  $|\alpha|=p-1$ and $|\beta|=q-2$; the top-form condition $p+q=4$ makes the
  pairing degree $-1$.

  The free quadratic term
  $$S_{\mathrm{free}}=\int_{D\times B}
    \left\langle\beta,D\alpha\right\rangle dz_1\,dz_2$$
  is the BV Hamiltonian for the differential $D$. The interaction in
  Definition~\ref{def:local-th-string} is only
  $$I_{\mathrm{BF}}=\frac12\int_{D\times B}
    \left\langle\beta,\{\alpha,\alpha\}\right\rangle dz_1\,dz_2.$$
  The total BF action is $S_{\mathrm{free}}+I_{\mathrm{BF}}$.
  The Poisson bracket on $\bar A$ is the holomorphic bracket determined by
  $dz_1\wedge dz_2$. Since $D$ is a derivation of this bracket and the bracket
  satisfies Jacobi,
  $$D I_{\mathrm{BF}}+\frac12\{I_{\mathrm{BF}},I_{\mathrm{BF}}\}=0,$$
  so the total BF action satisfies the classical master equation without
  double-counting the free differential.

  Mixed locality is the Cartan homotopy calculation on the interacting
  observables. For a constant vector
  field $v$ in the $\R^2$ direction, $[D,\iota_v]=\mathcal L_v$; for an
  anti-holomorphic coordinate vector field $\partial/\partial\bar z_i$,
  $[D,\iota_{\partial/\partial\bar z_i}]
  =\mathcal L_{\partial/\partial\bar z_i}$. The interaction is built from the
  de Rham wedge product and holomorphic polydifferential operators, so the
  contractions are derivations of the local observable algebra and commute with
  $\{I_{\mathrm{BF}},-\}$ up to the displayed Lie derivative. Thus
  $[Q_{\mathrm{obs}},\iota_v]=\mathcal L_v$ and
  $[Q_{\mathrm{obs}},\iota_{\partial/\partial\bar z_i}]
  =\mathcal L_{\partial/\partial\bar z_i}$ on local observables. The de Rham
  Poincare lemma in the $D$ directions gives the quasi-isomorphism for small
  disk inclusions, and the Dolbeault Poincare lemma gives the holomorphic
  dependence in the $B$ direction.

  The brane is $N\times Z=\R\times\{p\}$, with $Z$ understood as the formal
  holomorphic neighbourhood at $p$. Its open fields are
  $$\Omega^*(\R)\otimes
    \Ext^*_{\C[z_1,z_2]}(\mc O_p,\mc O_p)\otimes\lie{gl}_N[1],$$
  and Proposition~\ref{prop:skyscraper-ext} identifies the Ext algebra with
  $\Lambda(\varepsilon_1,\varepsilon_2)$. This is the derived
  $\RHom_Y(\mc O_p,\mc O_p)$ allowed in Definition~\ref{def:local-th-string},
  not an ordinary Dolbeault algebra on the point. The trace on $\lie{gl}_N$ and
  the Berezin trace on this exterior algebra give the cyclic open string field
  theory. Construction~\ref{constr:boundary-evaluation} and
  Theorem~\ref{thm:bulk-boundary} construct the degree-zero Hamiltonian
  boundary component and prove its bracket compatibility. The full
  Poisson factorization-center closed-open map is Problem~\ref{prob:formal-factorization-center},
  not a theorem proved here.
\end{proof}

\subsection{Open mixed brane states}
  The open string states are the tensor product of the topological brane
  direction and the formal holomorphic normal direction.

  \begin{itemize}
    \item \textit{Topological factor.} In the exact self-Floer model for
      the graded, spin zero-section $\R\subset T^*\R\cong\R^2$, we use the
      local exact Fukaya model near a compact interval in the brane. A small
      compactly supported Hamiltonian perturbation identifies $CF^*(\R,\R)$
      with the Morse complex on that interval, and passage to local operators
      in the interior is represented by the de Rham complex $\Omega^*(\R)$
      with compactly supported variations. No wrapped generators at infinity
      are included in this local model.
    \item \textit{Holomorphic factor.} Put affine coordinates at $p=0$ and write
      $R=\C[z_1,z_2]$, $\mathfrak m=(z_1,z_2)$, and $\mc{O}_p=R/\mathfrak m$.
      The skyscraper sheaf has open string states
      $$\Ext^*_R(R/\mathfrak m,R/\mathfrak m),$$
      computed in Proposition~\ref{prop:skyscraper-ext}.
  \end{itemize}

\begin{prop}[Affine skyscraper self-Ext]\label{prop:skyscraper-ext}
  Let $R=\C[z_1,z_2]$, $\mathfrak m=(z_1,z_2)$, and $k=R/\mathfrak m$. Then
  the Yoneda algebra of the skyscraper sheaf at the origin is
  $$\Ext^*_R(k,k)\cong\Lambda_{\C}(\varepsilon_1,\varepsilon_2),$$
  where $|\varepsilon_i|=1$. In particular this is the free
  graded-commutative algebra on two odd generators.
\end{prop}

\begin{proof}
  The pair $(z_1,z_2)$ is a regular sequence in the polynomial ring $R$, so the
  affine Koszul complex
  $$K=\bigl(0\to R\,e_{12}\xrightarrow{d_2}R\,e_1\oplus R\,e_2
        \xrightarrow{d_1}R\to0\bigr)$$
  is a free resolution of $k$, with
  $$d_1(ae_1+be_2)=az_1+bz_2,\qquad
    d_2(e_{12})=z_2e_1-z_1e_2.$$
  Applying $\Hom_R(-,k)$ gives
  $$0\to k\xrightarrow{0}k\,\varepsilon_1\oplus k\,\varepsilon_2
    \xrightarrow{0}k\,\varepsilon_{12}\to0,$$
  because $z_1$ and $z_2$ act by zero on $k$. Hence the graded vector space of
  Ext groups is $k$ in degree $0$, $k\varepsilon_1\oplus k\varepsilon_2$ in
  degree $1$, and $k\varepsilon_{12}$ in degree $2$.

  The product is the Yoneda product. The Koszul resolution is the exterior
  dg-algebra $R\otimes\Lambda(e_1,e_2)$ with $d(e_i)=z_i$; its diagonal sends
  $e_i$ to $e_i\otimes1+1\otimes e_i$. Dualising this diagonal gives
  $\varepsilon_i^2=0$ and
  $\varepsilon_1\varepsilon_2=-\varepsilon_2\varepsilon_1$, while
  $\varepsilon_1\varepsilon_2$ spans the top Ext group. Thus the Yoneda
  algebra is $\Lambda_{\C}(\varepsilon_1,\varepsilon_2)$.
\end{proof}

\subsection{Open mixed brane field theory}

The open theory is the minimal local field theory which remembers the brane's two
normal holomorphic directions. The two Ext generators are odd because they are
derived normal directions of a point brane; after the BV shift their ghost-zero
coefficients become the two ordinary matrix coordinates $\phi_1,\phi_2$. The
one-form coefficient is the gauge field $A$ along the brane. Thus the formal
Chern-Simons action is the mechanism which turns the Ext algebra into
first-order matrix mechanics.

The total space of fields (in the Batalin-Vilkovisky formalism) is
$$\alpha \in \Omega^*(\R)\otimes\Lambda(\varepsilon_1,\varepsilon_2)
  \otimes \lie{gl}_N[1]$$
with action
$$S(\alpha)=\int_{\R \times \C^{0|2}}
  \frac{1}{2}\,\mathrm{Tr}(\alpha\, d\alpha)
  + \frac{1}{3}\,\mathrm{Tr}\,\alpha^3.$$
Here $d = d_{\mathrm{dR}}$; the Ext algebra
$\Lambda(\varepsilon_1,\varepsilon_2)$ has zero differential. The integral
over $\C^{0|2}$ is the Berezin integral $\int d\varepsilon_1\,d\varepsilon_2$,
which picks out the top component in the odd directions.

The cyclic trace is
$$\operatorname{Tr}_{\mathrm{open}}(\eta\otimes u\otimes M)
  =\int_\R \eta\,[\varepsilon_1\varepsilon_2]u\,
    \operatorname{Tr}_N(M),$$
where $[\varepsilon_1\varepsilon_2]u$ denotes the coefficient of the top Ext
class. The top Ext class is the residue orientation dual to
$dz_1\wedge dz_2$. The de Rham integral has degree $-1$ and the Ext residue has
degree $-2$; after the field shift by $[1]$, the induced BV pairing has degree
$-1$.

\begin{constr}[The open field from the Ext basis]\label{constr:open-field-basis}
  Write $\varepsilon_{12}=\varepsilon_1\varepsilon_2$. Before imposing ghost
  number, an open field is a finite sum
  $$\alpha=a_0+a_1\varepsilon_1+a_2\varepsilon_2+a_{12}\varepsilon_{12},$$
  where each $a_I$ is a de Rham form on $\R$ with values in $\lie{gl}_N$,
  shifted by $[1]$. The ghost-number-zero components are exactly
  $$A\in\Omega^1(\R)\otimes\lie{gl}_N,\qquad
    \phi_1,\phi_2\in\Omega^0(\R)\otimes\lie{gl}_N,$$
  and they appear as
  $$\alpha_0=A+\phi_1\varepsilon_1+\phi_2\varepsilon_2.$$
  The Berezin integral kills every monomial except the coefficient of
  $\varepsilon_{12}$, so every term in the ghost-zero action is obtained by
  multiplying the displayed three summands and keeping exactly one real
  one-form and exactly the product $\varepsilon_1\varepsilon_2$.
\end{constr}

\begin{rmk}
  The shift $[1]$ acts on the total cohomological degree: a form of de Rham
  degree $p$ and Grassmann degree $q$ has total degree $p+q$, which after the
  shift sits in ghost number $p+q-1$. In particular, the 1-form component of
  $\alpha$ (de Rham degree 1, Grassmann degree 0) sits in ghost number 0 and
  is the bosonic gauge field. The scalar components proportional to
  $\varepsilon_i$ (de Rham degree 0, Grassmann degree 1) also sit in ghost
  number 0 and represent the motion of the brane in the two normal directions.
\end{rmk}

\subsubsection{Ghost-zero open field content}
  The ghost-number-zero part of the BV field is
  $$\alpha_0=A+\phi_1\varepsilon_1+\phi_2\varepsilon_2,$$
  where $A\in\Omega^1(\R)\otimes\lie{gl}_N$ and
  $\phi_i\in\Omega^0(\R)\otimes\lie{gl}_N$.

  \begin{lem}\label{lem:open-action-reduction}
    With the Berezin convention
    $\int_{\C^{0|2}}\varepsilon_1\varepsilon_2=1$, the restriction of the
    BV action to $\alpha_0$ is, up to a boundary term on $\R$,
    $$S(\alpha_0)=\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2
      +A[\phi_1,\phi_2]\bigr).$$
  \end{lem}

  \begin{proof}
    Only monomials containing one real one-form and the factor
    $\varepsilon_1\varepsilon_2$ survive the integration over
    $\R\times\C^{0|2}$. In the quadratic term this leaves
    $$\frac12\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2-\phi_2\,d\phi_1\bigr),$$
    where the sign is the Koszul sign from interchanging the two odd
    generators. Since
    $d\,\mathrm{Tr}(\phi_1\phi_2)=\mathrm{Tr}(d\phi_1\,\phi_2+\phi_1\,d\phi_2)$,
    the second summand differs from $\mathrm{Tr}(\phi_1\,d\phi_2)$ by an exact
    one-form. In the cubic term the six orderings of
    $A,\phi_1\varepsilon_1,\phi_2\varepsilon_2$ reduce by cyclicity of the trace
    and the odd relation $\varepsilon_2\varepsilon_1=-\varepsilon_1\varepsilon_2$
    to
    $$3\,\mathrm{Tr}(A\phi_1\phi_2-A\phi_2\phi_1).$$
    The coefficient $\frac13$ in the Chern-Simons action therefore gives exactly
    $\mathrm{Tr}(A[\phi_1,\phi_2])$.
  \end{proof}

\begin{lem}[Dirac reduction of the probe phase space]\label{lem:dirac-probe-reduction}
  Let
  $$\mathcal P_N=\lie{gl}_N\oplus\lie{gl}_N$$
  with coordinates $(\phi_1,\phi_2)$ and symplectic form
  $$\Omega_N=\mathrm{Tr}(d\phi_1\wedge d\phi_2).$$
  With the convention $\iota_{X_f}\Omega_N=-df$, simultaneous conjugation by
  $\lie{gl}_N$ is Hamiltonian with moment map components
  $$\mu_\epsilon=-\mathrm{Tr}\bigl(\epsilon[\phi_1,\phi_2]\bigr),
    \qquad \epsilon\in\lie{gl}_N.$$
  They satisfy the first-class identity
  $$\{\mu_\epsilon,\mu_\eta\}=\mu_{[\epsilon,\eta]}.$$
  The action of Lemma~\ref{lem:open-action-reduction} is the corresponding
  Dirac first-order action
  $$\int_\R \mathrm{Tr}(\phi_1\,d\phi_2)-\mu_A,$$
  and varying $A$ imposes the constrained phase space
  $$\mu^{-1}(0)/GL_N=\{[\phi_1,\phi_2]=0\}/GL_N.$$
\end{lem}

\begin{proof}
  The symplectic form gives
  $$\{(\phi_1)^i{}_j,(\phi_2)^k{}_l\}=\delta^i_l\delta^k_j.$$
  For $v_\epsilon(\phi_i)=[\epsilon,\phi_i]$, cyclicity of the trace gives
  $$d\mu_\epsilon(\delta\phi_1,\delta\phi_2)
    =-\mathrm{Tr}\bigl(\epsilon([\delta\phi_1,\phi_2]
      +[\phi_1,\delta\phi_2])\bigr)
    =-\Omega_N(v_\epsilon,(\delta\phi_1,\delta\phi_2)).$$
  Thus $X_{\mu_\epsilon}=v_\epsilon$. The moment-map bracket is therefore the
  infinitesimal equivariance identity
  $\{\mu_\epsilon,\mu_\eta\}=\mu_{[\epsilon,\eta]}$. Substituting
  $\epsilon=A(t)$ gives
  $$\int_\R\mathrm{Tr}(\phi_1\,d\phi_2)-\mu_A
    =\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr),$$
  and the $A$-equation is $[\phi_1,\phi_2]=0$.
\end{proof}

\begin{prop}[Classical BV truncation]\label{prop:open-bv-truncation}
  The subspace of ghost-number-zero fields
  $$\alpha_0=A+\phi_1\varepsilon_1+\phi_2\varepsilon_2$$
  with all nonzero ghost-number components set to zero is a consistent
  classical truncation of the open BV theory. The induced classical action is
  the first-order gauged matrix model of Lemma~\ref{lem:open-action-reduction}.
\end{prop}

\begin{proof}
  Decompose the BV field as $\alpha=\sum_r\alpha^{(r)}$ by ghost number. The
  differential $d_{\R}$ and the product on
  $\Lambda(\varepsilon_1,\varepsilon_2)\otimes\lie{gl}_N$ preserve total degree,
  and the BV action has ghost number zero. Hence every monomial in the
  Euler-Lagrange expression for a component of ghost number $r\neq0$ contains
  at least one field component of nonzero ghost number when evaluated at
  $\alpha=\alpha_0$. Setting all such components to zero therefore makes the
  discarded equations vanish. The remaining equation is exactly the variation
  of $S(\alpha_0)$, computed in Lemma~\ref{lem:open-action-reduction}.

  Concretely, the full Euler-Lagrange expression is the curvature
  $$F(\alpha)=d\alpha+\alpha^2.$$
  For $\alpha_0=A+\phi_1\varepsilon_1+\phi_2\varepsilon_2$ on a line,
  \begin{align*}
  F(\alpha_0)
    &=(d\phi_1+[A,\phi_1])\varepsilon_1
      +(d\phi_2+[A,\phi_2])\varepsilon_2
      +[\phi_1,\phi_2]\varepsilon_1\varepsilon_2.
  \end{align*}
  The BV pairing keeps exactly real-form degree one and
  $\varepsilon_1\varepsilon_2$. Hence the displayed three components pair exactly
  with the variations of $A,\phi_2,\phi_1$ respectively, while variations of
  nonzero ghost number see complementary curvature components that are zero for
  $\alpha_0$ by real-form degree or $\varepsilon$-degree. This is a physical
  ghost-zero truncation; the residual ordinary $GL_N$ gauge symmetry remains.
\end{proof}

  The ghost-number-zero truncation of the BV master action is closed under the
  classical equations and gives a quantum-mechanical system with a connection
  form
  $$A \in \Omega^1(\R)\otimes \lie{gl}_N,$$
  two adjoint scalars
  $$\phi_1,\phi_2 \in \Omega^0(\R)\otimes\lie{gl}_N,$$
  and action
  $$S = \int_\R \mathrm{Tr}\bigl(\phi_1\,d\phi_2
    + A[\phi_1,\phi_2]\bigr).$$
  This action is invariant under
  $$\delta_{\varepsilon}\phi_i=[\varepsilon,\phi_i],\qquad
    \delta_{\varepsilon}A=d\varepsilon+[A,\varepsilon],$$
  for $\varepsilon\in\Omega^0(\R)\otimes\lie{gl}_N$. Indeed the variation of
  $\mathrm{Tr}(\phi_1d\phi_2)$ containing $d\varepsilon$ is
  $-\mathrm{Tr}(d\varepsilon[\phi_1,\phi_2])$, and this cancels the
  $d\varepsilon$ variation of $\mathrm{Tr}(A[\phi_1,\phi_2])$; the remaining
  terms cancel by invariance of the trace pairing.

\begin{rmk}
  The same local open model is obtained from the Calabi-Yau $2$ point-brane
  residue calculation by tensoring the skyscraper object with $\C^N$ and
  passing to endomorphisms. This is a local CY$_2$ pairing statement, not a
  global CY-to-chiral input. Global transfer would require the corresponding
  negative cyclic Calabi-Yau class, framing data, and descent; none of that is
  used in the proof below.
\end{rmk}

\begin{rmk}
  In AKSZ language this is the one-dimensional gauged sigma model with
  Hamiltonian target $\lie{gl}_N\oplus\lie{gl}_N$ and symplectic potential
  $\mathrm{Tr}(\phi_1\,d\phi_2)$. We use the resulting Poisson bivector
  $$\Pi=\sum_{i,j}\frac{\partial}{\partial(\phi_1)^i{}_j}
    \wedge\frac{\partial}{\partial(\phi_2)^j{}_i},$$
  so $\{(\phi_1)^i{}_j,(\phi_2)^k{}_l\}=\delta^i_l\delta^k_j$. Equivalently,
  with the convention $\iota_{X_f}\omega=-df$ used throughout, the symplectic
  form is $\mathrm{Tr}(d\phi_1\wedge d\phi_2)$. For
  $\epsilon\in\lie{gl}_N$, the Hamiltonian
  $$\mu_\epsilon=-\mathrm{Tr}\bigl(\epsilon[\phi_1,\phi_2]\bigr)$$
  generates $\delta_\epsilon\phi_i=[\epsilon,\phi_i]$. Its zero locus is the
  commuting-pair equation $[\phi_1,\phi_2]=0$, and the classical reduced phase
  space is the stack of commuting pairs of matrices modulo conjugation.
\end{rmk}

\begin{rmk}
  Equivalently, take Chern-Simons theory on $\R\times T^2$ and restrict to the
  harmonic forms $1,\eta_1,\eta_2,\eta_1\eta_2$ on $T^2$. Writing
  $A_{3d}=A_t\,dt+\phi_1\eta_1+\phi_2\eta_2$ and integrating over $T^2$
  gives the same action; the odd variables $\varepsilon_i$ represent the
  degree-one cohomology classes $\eta_i$.
\end{rmk}

\subsection{Closed mixed Hamiltonian sector}

The closed field is the infinitesimal geometry of the formal normal surface.
Because the surface is holomorphic symplectic, an infinitesimal canonical
transformation is a Hamiltonian function modulo constants. The BF partner is
the cotangent variable which makes the theory local and BV. This is the closed
counterpart of the open first-order form: both sides are governed by the same
symplectic normal plane.

The closed sector used here is a mixed field theory, not a tensor product of
two independent closed-string state spaces. Its fields have a topological de
Rham factor along $\R^2$ and a holomorphic Dolbeault factor along $\C^2$:
$$\Omega^*(\R^2)\widehat{\otimes}\Omega^{0,*}(\C^2)
  \widehat{\otimes}\bigl(\widehat{\mathfrak h}[1]\oplus
  \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]\bigr).$$
The coefficient $\widehat{\mathfrak h}$ is the completed Lie algebra of
nonconstant Hamiltonian functions on the formal holomorphic symplectic disk.
The continuous dual copy
$\widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]$ is the cotangent/BF field.
Thus the closed theory is the Hamiltonian Kodaira-Spencer/BF sector of the mixed
holomorphic-topological string.

\begin{rmk}
  The original BCOV analysis \cite{bcov} is written for Calabi-Yau threefolds;
  the higher-genus B-model on Calabi--Yau manifolds is taken up at the
  quantum level in \cite{costello-li}.
  On a holomorphic symplectic surface the natural local cotangent theory is the
  BF theory for the dg Lie algebra of Hamiltonian vector fields. The
  holomorphic symplectic form supplies the Poisson bracket, while the
  holomorphic volume form supplies the divergence operator on polyvectors.
\end{rmk}

We consider the space of polyvector fields
$$\mathbf{PV}^{*,*}(\C^2) \cong \Omega^{0,*}(\C^2)[\partial_{z_1},\partial_{z_2}]$$
where $\partial_{z_i}$ are odd generators of poly-vector degree 1 (corresponding
to the two holomorphic vector fields on $\C^2$). The operator
$$\partial: \mathbf{PV}^{i,*} \to \mathbf{PV}^{i-1,*}$$
is the divergence operator determined by the holomorphic volume form
$\Omega=dz_1\wedge dz_2$:
$$\partial_{\Omega}=\iota_{\Omega}^{-1}\circ\partial_{\mathrm{hol}}\circ
  \iota_{\Omega},\qquad
  \iota_{\Omega}:\mathbf{PV}^{i,*}\xrightarrow{\sim}\Omega^{2-i,*}.$$
Thus for $X=a_1\partial_{z_1}+a_2\partial_{z_2}$,
$$\partial_{\Omega}X=(\partial_{z_1}a_1+\partial_{z_2}a_2),$$
while $\partial_{\Omega}$ vanishes on functions.

We work in the formal polynomial local model at $0\in\C^2$, so Dolbeault
cohomology is represented by holomorphic Taylor polynomials. Here
$\partial_{\Omega}$ is the divergence constraint selecting the Hamiltonian BF
sector. The kinematic differential of the closed theory below is
$D=d_{\R^2}+\bar\partial_{\C^2}$. Thus the Poincare lemma identifies
divergence-free vector fields with Hamiltonian potentials. The quotient by
$\partial_{\Omega}$-exact Hamiltonians is absent. Analysing degree by
degree:
\begin{itemize}
  \item $\mathbf{PV}^{0,*}(\C^2) = \Omega^{0,*}(\C^2)\subset\Ker\partial$
    trivially.
  \item $\mathbf{PV}^{1,*}(\C^2)\cong\Omega^{1,*}(\C^2)$ via
    $\iota_{(-)}\omega$. Under this identification, with the Hamiltonian
    convention $\iota_{X_f}\omega=-df$ used below,
    $\Ker\partial_{\Omega}$ is the space of closed holomorphic one-forms.
    Lemma~\ref{lem:polynomial-poincare} identifies these with $df$, uniquely
    modulo constants.
  \item The constant Hamiltonians act trivially, since their Hamiltonian vector
    fields vanish. We therefore use the reduced polynomial algebra
    $$\bar A=\C[z_1,z_2]/\C\cdot1$$
    for nontrivial Hamiltonian fields.
\end{itemize}

\begin{lem}[Polynomial Poincare primitive]\label{lem:polynomial-poincare}
  Let
  $$\theta=a(z_1,z_2)\,dz_1+b(z_1,z_2)\,dz_2$$
  be a polynomial one-form on $\C^2$. If
  $\partial_{z_2}a=\partial_{z_1}b$, then there is a polynomial
  $f\in\C[z_1,z_2]$, unique modulo constants, such that $\theta=df$.
\end{lem}

\begin{proof}
  Define
  $$f(z_1,z_2)=\int_0^1
    \bigl(z_1a(tz_1,tz_2)+z_2b(tz_1,tz_2)\bigr)\,dt.$$
  Since $a$ and $b$ are polynomials, the integral is termwise division of each
  homogeneous term by its degree plus one, hence $f$ is polynomial. Differentiate
  under the integral sign. Closedness says
  $\partial_{z_2}a=\partial_{z_1}b$, so
  \begin{align*}
  \partial_{z_1}f
    &=\int_0^1\bigl(a(tz)+tz_1\partial_{z_1}a(tz)
       +tz_2\partial_{z_1}b(tz)\bigr)\,dt\\
    &=\int_0^1\bigl(a(tz)+t z_1\partial_{z_1}a(tz)
       +t z_2\partial_{z_2}a(tz)\bigr)\,dt\\
    &=\int_0^1\frac{d}{dt}\bigl(t\,a(tz)\bigr)\,dt
      =a(z).
  \end{align*}
  The same calculation, with $a$ and $b$ interchanged, gives
  $\partial_{z_2}f=b(z)$. Therefore $df=\theta$.
  If $df=dg$, then $d(f-g)=0$, hence $f-g$ is constant.
\end{proof}

\begin{prop}[Hamiltonian polyvector reduction]\label{prop:hamiltonian-polyvector-reduction}
  In the formal polynomial model on $(\C^2,\omega=dz_1\wedge dz_2)$, the
  divergence-closed polyvector-one fields reduce to Hamiltonian vector fields:
  $$\Ker(\partial_{\Omega}:\mathbf{PV}^{1}\to\mathbf{PV}^{0})
    \cong \{df:f\in\C[z_1,z_2]\}
    \cong \bar A.$$
  Under the convention
  $$X_f=(\partial_{z_1}f)\partial_{z_2}
    -(\partial_{z_2}f)\partial_{z_1},\qquad \iota_{X_f}\omega=-df,$$
  the commutator of vector fields is
  $$[X_f,X_g]=X_{\{f,g\}_{\bar A}}.$$
\end{prop}

\begin{proof}
  Let $X=a_1\partial_{z_1}+a_2\partial_{z_2}$. The divergence operator is
  $\partial_{\Omega}X=\partial_{z_1}a_1+\partial_{z_2}a_2$. Contracting with
  $\omega$ gives
  $$\iota_X\omega=a_1\,dz_2-a_2\,dz_1.$$
  The equation $\partial_{\Omega}X=0$ is exactly the closedness of this
  one-form:
  $$d(\iota_X\omega)
    =(\partial_{z_1}a_1+\partial_{z_2}a_2)\,dz_1\wedge dz_2=0.$$
  By Lemma~\ref{lem:polynomial-poincare}, there is a polynomial $f$, unique
  modulo constants, such that $\iota_X\omega=-df$. Therefore
  $$a_1=-\partial_{z_2}f,\qquad a_2=\partial_{z_1}f,$$
  so $X=X_f$. Constants are exactly the kernel of $f\mapsto X_f$, giving
  $\bar A$.

  Finally, for any polynomial $h$,
  \begin{align*}
  [X_f,X_g](h)
    &=\{f,\{g,h\}\}-\{g,\{f,h\}\}\\
    &=\{\{f,g\},h\}
  \end{align*}
  by the Jacobi identity for the constant Poisson bracket. Thus
  $[X_f,X_g]=X_{\{f,g\}}$, and projecting constants gives the bracket on
  $\bar A$.
\end{proof}

For the Hamiltonian sector of the closed mixed field theory we replace
$\Ker\partial$ (on poly-1-vectors) by the Dolbeault-valued Hamiltonian vector
fields:
$$\Omega^{0,*}(\C^2)\text{-valued Hamiltonian vector fields},$$
i.e.\ sections of $\Omega^{0,*}(\C^2)$ identified with Hamiltonian vector
fields via the symplectic form $\omega = dz_1\wedge dz_2$. Concretely, a
section $f\in\Omega^{0,*}(\C^2)$ corresponds to the Hamiltonian vector field
$X_f=\{f,-\}_\omega$, where
$$\{f,g\}_\omega=
  \partial_{z_1}f\,\partial_{z_2}g-\partial_{z_2}f\,\partial_{z_1}g.$$
With this convention
$$X_f=(\partial_{z_1}f)\partial_{z_2}
  -(\partial_{z_2}f)\partial_{z_1},\qquad \iota_{X_f}\omega=-df.$$

\begin{rmk}
  The replacement is the elementary statement
  of Proposition~\ref{prop:hamiltonian-polyvector-reduction}. Constants are
  removed because $X_f=0$ exactly when $f$ is constant.
\end{rmk}

\subsection{Hamiltonian BF closed sector}

\subsubsection{The Action Functional}

Let
$$D=d_{\R^2}+\bar\partial_{\C^2}.$$
Write
$$\alpha\in\Omega^*(\R^2)\,\hat{\otimes}\,\Omega^{0,*}(\C^2)
  \widehat{\otimes}\widehat{\mathfrak h}[1]$$
for the Hamiltonian connection field and
$$\beta\in\Omega^*(\R^2)\,\hat{\otimes}\,\Omega^{0,*}(\C^2)
  \widehat{\otimes}\widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]$$
for its cotangent field. The bracket on form-valued Hamiltonians is obtained
by wedging the form parts and taking the Poisson bracket of the Hamiltonian
parts with the tensor-product Koszul sign:
$$[\eta\otimes f,\theta\otimes g]
  =(-1)^{|f||\theta|}(\eta\wedge\theta)\otimes\{f,g\},$$
for homogeneous form $\eta,\theta$ and homogeneous Hamiltonian coefficients
$f,g$. In the ghost-zero Hamiltonian calculations used below the coefficients
are even, so this sign is $+1$. The action is
$$S=\int_{\R^2\times\C^2}\Bigl\langle\beta,\,
  D\alpha+\frac12\{\alpha,\alpha\}\Bigr\rangle\,dz_1\,dz_2.$$
The pairing is the continuous evaluation pairing between
$\widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}$ and $\widehat{\mathfrak h}$.
The dense polynomial submodel replaces these by $\bar A^\vee$ and $\bar A$ in
each finite degree.
For ghost-number-zero fields, $\alpha$ has total real/Dolbeault form degree
$1$ and $\beta$ has total degree $2$. Hence
$\beta\wedge D\alpha$ and $\beta\wedge\{\alpha,\alpha\}$ have total
real/Dolbeault degree $4$; multiplying by $dz_1\wedge dz_2$ gives a top real
degree $6$ form on $\R^2\times\C^2$.

\begin{rmk}
  The open mixed brane system lives on the brane line. The closed Hamiltonian
  BF theory lives on the full mixed space-time $\R^2\times\C^2$.
\end{rmk}

\subsubsection{Classical field content}

This theory is closely related to a 4-dimensional BF theory: $\beta$ plays the
role of the $B$-field (Lagrange multiplier) and the equations of motion of
$\beta$ enforce $F_\alpha = 0$, where
$$F_\alpha = D\alpha + \tfrac{1}{2}\{\alpha,\alpha\}$$
is the ``curvature'' of $\alpha$ (viewed as a connection on a bundle of
holomorphic-symplectic surfaces over $\R^2$).

Consider the space-time $\R^2_{x_i}\times\C^2_{z_i}$. The ghost-number-zero
components of $\alpha$ and $\beta$ are:
$$\alpha = \alpha_{x_i}\,dx_i + \alpha_{\bar z_j}\,d\bar z_j,\qquad
  \beta = \beta_{x_1 x_2}\,dx_1\,dx_2 + \beta_{x_i\bar z_j}\,dx_i\,d\bar z_j
  + \beta_{\bar z_1\bar z_2}\,d\bar z_1\,d\bar z_2.$$
Here the coefficients of $\alpha$ are Hamiltonian functions modulo constants.
The gauge symmetries are the BF-type transformations
$$\delta_{\varepsilon}\alpha=D\varepsilon+\{\alpha,\varepsilon\},\qquad
  \delta_{\varepsilon}\beta=\operatorname{ad}^{\vee}_{\varepsilon}\beta,$$
and
$$\delta_{\lambda}\alpha=0,\qquad
  \delta_{\lambda}\beta=D_{\alpha}\lambda,$$
where $D_{\alpha}=D+\{\alpha,-\}$ and $\lambda$ is a one-form valued in
$\bar A^{\vee}$. The second symmetry is reducible on shell: if
$\lambda=D_{\alpha}\mu$, then
$D_{\alpha}\lambda=D_{\alpha}^2\mu=\{F_{\alpha},\mu\}$, which vanishes when
$F_{\alpha}=0$.

Analysing $\alpha$ as a Hamiltonian function on $\C^2$: the component
$\alpha_{\bar z_j}d\bar z_j$ is the Hamiltonian potential whose vector field
$X_{\alpha_{\bar z_j}}d\bar z_j$ is the Beltrami differential encoding a
deformation of the complex structure of $\C^2$; the component
$\alpha_{x_i}dx_i$ similarly defines a connection on $\R^2$ valued in
Hamiltonian vector fields on $\C^2$, encoding a bundle of $\C^2$s over
$\R^2$. Together, the
equation of motion $F_\alpha=0$ says this data constitutes an integrable
deformation of complex structure with flat holonomy. The field $\beta$ appears
linearly in the action and enforces exactly this equation.

\begin{rmk}
  This is entirely analogous to BF theory, where $B$ is a Lagrange multiplier
  enforcing $F_A=0$, and the phase space is $T^*\mathcal{M}_{\mathrm{flat}}$.
\end{rmk}

\subsubsection{Phase Space}
As an optional analytic model for propagators, formally compactify one real
direction and put the perturbative local model on
$\R\times S^1\times Y_{\mathrm{hol}}$, where $Y_{\mathrm{hol}}$ is holomorphic
symplectic and the calculation is completed at the trivial solution. This is a
compactified avatar of the formal local model, not a change of notation for the
product $X=M\times Y$ used above. The equations of motion $F_\alpha=0$ cut
out the Maurer-Cartan moduli problem for Hamiltonian vector fields on
$S^1\times Y_{\mathrm{hol}}$. Fix the analytic package of
Problem~\ref{prob:analytic-graph-realization} in this compact or formal
setting: elliptic complex, brane-defect or boundary condition, gauge fixing,
propagator, renormalization scheme, and anomaly cancellation. The perturbative
phase space
is the derived cotangent stack
$$T^*_{\mathrm{der}}\mathrm{MC}\bigl(\Omega^*(S^1)\widehat{\otimes}
  \Omega^{0,*}(Y_{\mathrm{hol}},\mathrm{Ham}(Y_{\mathrm{hol}})),D,\{-,-\}\bigr).$$
After passing to the underived tangent space at the trivial solution this
reduces to the ordinary cotangent bundle of the linearized deformation complex.

\subsection{Closed-open brane coupling}

This is the point at which the physical picture becomes a formula. A closed
Hamiltonian is not observed by the brane as an abstract vector field; it is
observed by evaluating it on the brane's matrix-valued normal coordinates and
taking the trace over Chan-Paton indices.

The local classical bulk-boundary operation is the Hamiltonian shadow of the
desired closed-open morphism: evaluate a closed Hamiltonian on the brane normal
fields. If the brane lies along $x_1$ and the closed field is
$dx_1\,z_1^k z_2^l$, the local boundary functional is
$$\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr)
  + \int_\R dx_1\,\mathrm{Tr}\,\phi_1^k\phi_2^l.$$
This is a statement inside the formal local algebraic model: the closed
Hamiltonian is pulled back along the matrix-valued normal coordinate map
$z_i\mapsto\phi_i$ and then traced.
Construction~\ref{constr:boundary-evaluation} is the algebraic form of this
bulk-to-boundary prescription. Theorem~\ref{thm:bulk-boundary} below proves
that the resulting Hamiltonian evaluation preserves the classical bracket. This
is the degree-zero Hamiltonian component expected from a full closed-open map;
the full Poisson factorization-center morphism is not constructed here.

\begin{constr}[Reduced line-defect current kernel]\label{constr:reduced-line-defect-current-kernel}
  Let
  $$X=\R^2_{\mathrm{top}}\times\C^2_{\mathrm{hol}},\qquad
    L=\R_{x_1}\times\{x_2=0\}\times\{p\}\subset X,$$
  and let $i:L\hookrightarrow X$ be the inclusion. This is a line defect, not
  a spacetime boundary. In the reduced formal local model, a test density
  $a(t)\,dt$ on $L$ defines the defect-supported current $i_*(a(t)\,dt)$,
  locally written as $a(x_1)\delta(x_2)\delta_p\,dx_1dx_2$ together with the
  formal holomorphic delta-current at $p$.

  The degree-zero Hamiltonian part of the reduced PBW/Rees defect-current
  vertex is
  $$K_L^{\mathrm{cl}}(a\otimes f)
    =\int_L a(t)\,
      \overline{\mathrm{Tr}\,f(\phi_1(t),\phi_2(t))}\,dt,
    \qquad f\in\bar A.$$
  For the cotangent principal-part source, the reduced vertex sends
  $$B\otimes\rho[1]\longmapsto\Theta_\rho(B),\qquad
    B\in\mathcal D'_c(L),\quad \rho\in\mc P,$$
  using Theorem~\ref{prop:reduced-principal-part-boundary-current}. These
  formulas define a reduced PBW/Rees defect-current kernel. They are not a
  cochain-level map from closed CE observables, and they are not yet the
  quantum Costello brane-defect kernel: the Ward identity, anomaly cancellation,
  finite-scale propagator, and quantum moment-map compatibility remain separate
  obligations.
\end{constr}

\begin{rmk}
  Geometrically, specifying a closed Hamiltonian field on $\C^2$ amounts to
  equipping $\C^2$ with a connection, so that the brane can parallel-transport
  its internal degrees of freedom as it moves along $\R$.
\end{rmk}

\begin{constr}[Interval Hamiltonian and factorization algebras]\label{constr:interval-fact-algebras}
  For an interval $I\subset\R$, define
  \begin{align*}
    \mathfrak h_I&=C_c^\infty(I)\widehat\otimes\bar A,\\
    \mathcal P_I&=\mathcal D'_c(I)\widehat\otimes\mc P,\\
    \mathfrak g_I&=\mathfrak h_I\ltimes\mathcal P_I[1],
  \end{align*}
  with brackets
  \begin{align*}
    [a\otimes f,b\otimes g]_{\mathfrak h_I}&=ab\otimes\{f,g\}_{\bar A},\\
    [a\otimes f,B\otimes\rho[1]]_{\mathfrak g_I}&=aB\otimes(f\cdot\rho)[1],\\
    [B\otimes\rho[1],C\otimes\sigma[1]]_{\mathfrak g_I}&=0,
  \end{align*}
  where $aB$ is multiplication of a compactly supported distribution by
  a smooth compactly supported function and
  $f\cdot\rho=\pi_{\mathrm{pp}}\{f,\rho\}$ is the principal-part
  coadjoint action of \ref{prop:principal-part-coadjoint}. Inclusions
  $I'\subset I$ act by extension by zero on test functions and
  distributions; disjoint unions act by sum. This makes
  $I\mapsto\mathfrak h_I,\mathfrak g_I$ cosheaves of (graded) Lie
  algebras on $\R$.

  Define the boundary $P_0$ factorization algebras on $\R$ in the
  formal stable Hamiltonian sector by
  \begin{align*}
    A_\partial^{\mathrm{Ham}}(I)
      &=\widehat{\mathbf S}(\mathfrak h_I),\\
    A_\partial^{\mathrm{pp}}(I)
      &=\widehat{\mathbf S}(\mathfrak h_I)\widehat\otimes
        \widehat{\mathbf S}(\mathcal P_I[1]),
  \end{align*}
  with $P_0$ bracket extended as a biderivation from
  \begin{align*}
    \{a\otimes f,b\otimes g\}_{A_\partial}&=ab\otimes\{f,g\}_{\bar A},\\
    \{a\otimes f,B\otimes\rho[1]\}_{A_\partial}
      &=aB\otimes(f\cdot\rho)[1],\\
    \{B\otimes\rho[1],C\otimes\sigma[1]\}_{A_\partial}&=0.
  \end{align*}
  The factorization product on disjoint intervals is the multiplication
  in $\widehat{\mathbf S}$ after extension by zero. These are the
  reduced post-contraction targets for the closed-open
  factorization-center map. The Hamiltonian factor
  $A_\partial^{\mathrm{Ham}}$ is the connected component of the formal
  Hamiltonian sector of the open brane factorization algebra; the
  principal-part factor
  $A_\partial^{\mathrm{pp}}/A_\partial^{\mathrm{Ham}}$ is the reduced
  current object of
  \ref{prop:reduced-principal-part-boundary-current}.
\end{constr}

\begin{prop}[Locality of the brane $P_0$ bracket]\label{prop:brane-bracket-locality}
  Let $a\in C_c^\infty(I_1)$, $b\in C_c^\infty(I_2)$ with
  $I_1\cap I_2=\emptyset$. For all $f,g\in\bar A$,
  $$\{B_f(a),B_g(b)\}_{A_\partial^{\mathrm{Ham}}}=0.$$
  In particular, $A_\partial^{\mathrm{Ham}}$ has the strict
  factorization product property: the bracket between sections
  supported on disjoint intervals vanishes.
\end{prop}

\begin{proof}
  By \ref{constr:interval-fact-algebras},
  $\{B_f(a),B_g(b)\}=B_{\{f,g\}}(ab)$. The pointwise product
  $ab\equiv 0$ since the supports are disjoint, so
  $B_{\{f,g\}}(ab)=0$.
\end{proof}

\begin{rmk}[Locality from the canonical equal-time bracket]\label{rmk:equal-time-locality}
  The locality input is the canonical equal-time bracket of the
  first-order open BV theory:
  $$\{(\phi_1)^i{}_j(t),(\phi_2)^k{}_l(s)\}
    =\delta^i_l\delta^k_j\,\delta(t-s),\qquad
    \{(\phi_a)^i{}_j(t),(\phi_a)^k{}_l(s)\}=0\ \,(a=1,2).$$
  Tracing $f(\phi_1,\phi_2)(t)$ and $g(\phi_1,\phi_2)(s)$, applying the
  Leibniz rule, and integrating against $a(t)b(s)\delta(t-s)$ produces
  exactly the smeared identity
  $\{B_f(a),B_g(b)\}=B_{\{f,g\}}(ab)$. This is the unsmeared content
  packaged in \ref{cor:local-bulk-boundary-coupling}; the
  delta-function locality is what produces a strict $P_0$
  factorization algebra rather than a homotopical one.
\end{rmk}

\begin{thm}[Open-closed derived-center factorization equivalence,
Hamiltonian sector]\label{thm:open-closed-derived-center-factorization}
  Let $\mathrm{Obs}^{\mathrm{cl,red}}_{\mathrm{open},N}$ be the locally
  constant reduced open-brane factorization algebra of
  \ref{thm:hamiltonian-current-center-lift}. Let
  $\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H,\mathrm{Ham}}|_{\R\times p}$
  denote the formal classical Hamiltonian-mode subfactorization
  algebra of the cotangent BF theory on the formal neighbourhood of
  $\R\times p$ obtained by restricting to the connected Hamiltonian
  sector (the $\bar A$-modes), before adjoining the cotangent
  generators. Define the interval-wise CE cochain factorization
  algebra by
  $$\mathcal F_{\mathrm{cl}}(I)
    =C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak h_I)
    =\widehat{\mathbf S}\bigl(\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1]\bigr),$$
  with structure maps induced from extension by zero on $C^\infty_c$
  cochain-by-cochain. Then:
  \begin{enumerate}
    \item there is a continuous interval-wise morphism of $P_0$
      factorization algebras
      $$\Phi^{\mathrm{Ham}}_{\mathrm{fact}}:
        \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H,\mathrm{Ham}}\big|_{\R\times p}
        \longrightarrow
        \mathrm Z^{P_0}_{\mathrm{fact}}\bigl(A_\partial^{\mathrm{Ham}}\bigr),$$
      whose underlying CE cochain map on each interval $I$ is given on
      length-one CE coordinates by
      $$(a\otimes f)^\vee[-1]\ \longmapsto\ B_f(a)
        :=\int_I a(t)\,\overline{\mathrm{Tr}\,f(\phi_1(t),\phi_2(t))}\,dt;$$
    \item this morphism is a quasi-isomorphism in each interval and
      is compatible with extension by zero and disjoint factorization
      products;
    \item the induced equivalence is locally constant in the
      topological direction $\R$ in the sense of
      \cites{costello-gwilliam,costello-gwilliam-vol2} (Lurie,
      \emph{Higher Algebra}, \S 5.5): every inclusion
      $I'\hookrightarrow I$ of nonempty open intervals induces a
      quasi-isomorphism of the structure maps;
    \item the factorization product
      $A_\partial^{\mathrm{Ham}}(I_1)\otimes A_\partial^{\mathrm{Ham}}(I_2)
        \to A_\partial^{\mathrm{Ham}}(V)$ for disjoint
      $I_1\sqcup I_2\subset V$ corresponds under
      $\Phi^{\mathrm{Ham}}_{\mathrm{fact}}$ to the CE coproduct on the
      closed side induced by extension by zero
      $C_c^\infty(I_j)\hookrightarrow C_c^\infty(V)$;
    \item at the stalk $I\to\{t_0\}$,
      $\Phi^{\mathrm{Ham}}_{\mathrm{fact}}$ restricts to the stalkwise
      central operation
      $$f\longmapsto L_{B_f}\in\mathrm{Hoch}^0\bigl(A_N^{\mathrm{pt}}\bigr)$$
      of \ref{prop:stalk-central-multiplication}.
  \end{enumerate}
\end{thm}

\begin{proof}
  \emph{Step 1.} Identify the interval-wise central factorization
  algebra. In the formal stable Hamiltonian sector, the boundary
  factorization algebra
  $A_\partial^{\mathrm{Ham}}(I)=\widehat{\mathbf S}(\mathfrak h_I)$
  is graded-commutative, with strict $P_0$ bracket inherited from
  $\mathfrak h_I$ as a biderivation. By the
  Hochschild--Kostant--Rosenberg theorem in the smooth/algebraic
  setting, applied here to the free graded-commutative algebra on the
  Tate vector space $\mathfrak h_I$, the Hochschild cochain complex
  $\mathrm{Hoch}^\bullet\bigl(\widehat{\mathbf S}(\mathfrak h_I)\bigr)$
  is quasi-isomorphic to the polyvector fields
  $\mathrm{PV}^\bullet\bigl(\widehat{\mathbf S}(\mathfrak h_I)\bigr)
  =\widehat{\mathbf S}(\mathfrak h_I)\widehat\otimes
    \widehat{\mathbf S}(\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1])$
  with the Schouten bracket. The locally constant
  factorization-center stalk on the line records exactly the
  Hochschild cochains in the corresponding $E_1$ algebra; for
  graded-commutative algebras this collapses to PV. Restricting to the
  polynomial subalgebra
  $\mathbf S(\mathfrak h_I)\subset\widehat{\mathbf S}(\mathfrak h_I)$
  and to the constant polyvectors gives the central multiplication
  operations, which are recorded as the length-one CE coordinates dual
  to elements of $\mathfrak h_I$. The bracket of two such cocycles is
  the Schouten bracket on PV restricted to one-vectors, which is the
  Lie bracket of $\mathfrak h_I$.

  \emph{Step 2.} Construct the CE source. By
  \ref{lem:continuous-bar-cobar},
  $C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak h_I)
   =\widehat{\mathbf S}(\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1])$,
  and its CE differential is the dual of the Lie bracket of
  $\mathfrak h_I$. The continuous dual
  $\mathfrak h^{\vee}_{I,\mathrm{cont}}$ is computed by the
  residue-Taylor pairing on the $\bar A$ factor and by the
  density-distribution pairing on the $C_c^\infty(I)$ factor: every
  continuous functional on $C_c^\infty(I)$ is a compactly supported
  distribution, and the polynomial subspace
  $\bar A\subset\widehat{\bar A}$ pairs with the discrete dual
  generated by the $\delta_{a,b}$. This gives
  $$\mathfrak h^{\vee}_{I,\mathrm{cont}}
    =\mathcal D'_c(I)\widehat\otimes\bar A^{\vee}_{\mathrm{cont}}.$$

  \emph{Step 3.} Define $\Phi^{\mathrm{Ham}}_{\mathrm{fact}}(I)$ on
  generators. By \ref{prop:grav-ops}, the closed Hamiltonian
  cotangent BF observables on the formal neighbourhood of
  $\R\times p$ in the Hamiltonian sector are
  $\widehat{\mathbf S}(\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1])$,
  with CE differential dual to the Hamiltonian Lie bracket on
  $\mathfrak h_I$. The interval-wise map sends a length-one CE
  coordinate
  $(a\otimes f)^\vee[-1]\in\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1]$
  to the element of the central operations factorization algebra
  given by the multiplication operator
  $$L_{B_f(a)}\in\mathrm{Hoch}^0\bigl(A_\partial^{\mathrm{Ham}}(I)\bigr)
    \subset\mathrm Z^{P_0}_{\mathrm{fact}}\bigl(A_\partial^{\mathrm{Ham}}\bigr)(I),$$
  with $B_f(a)$ as displayed. By
  \ref{prop:stalk-central-multiplication}, this operator is closed
  (Hochschild $0$-cocycle on the graded-commutative open stalk).
  Extend $\Phi^{\mathrm{Ham}}_{\mathrm{fact}}(I)$ as a continuous
  algebra morphism on $\widehat{\mathbf S}$.

  \emph{Step 4.} Verify CE differential compatibility. On length two,
  the CE differential of a generator
  $\xi\in\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1]$ is the dual of the
  Lie bracket on $\mathfrak h_I$. By
  \ref{cor:local-bulk-boundary-coupling} (its sharpened form below),
  $$\{L_{B_f(a)},L_{B_g(b)}\}_{A_\partial^{\mathrm{Ham}}}
    =L_{B_{\{f,g\}}(ab)}.$$
  Pulling back through $\Phi^{\mathrm{Ham}}_{\mathrm{fact}}$ matches
  this with the dual of
  $[a\otimes f,b\otimes g]_{\mathfrak h_I}=ab\otimes\{f,g\}$.
  Inductive extension by length and the biderivation property
  propagates this to all CE lengths.

  \emph{Step 5.} Quasi-isomorphism on each interval. Both sides are
  free graded-commutative algebras on the same continuous Tate vector
  space $\mathfrak h^{\vee}_{I,\mathrm{cont}}[-1]$, with the same CE
  differential induced from the Lie bracket of $\mathfrak h_I$
  (closed side: by definition; brane side: through the HKR
  identification of Step 1 and the Schouten bracket). The map
  respects the symmetric-algebra generators by construction. Thus it
  is an isomorphism of underlying graded vector spaces and
  intertwines the differentials: a quasi-isomorphism, in fact an
  isomorphism, of $P_0$-cdg algebras on each interval.

  \emph{Step 6.} Factorization product compatibility. For disjoint
  $I_1,I_2\subset V$, the CE source extension by zero gives
  $\mathfrak h_{I_1}\oplus\mathfrak h_{I_2}\hookrightarrow\mathfrak h_V$.
  The cobracket on the closed side is the dual of this: it is the
  splitting
  $\widehat{\mathbf S}(\mathfrak h_V^\vee[-1])
   \to\widehat{\mathbf S}(\mathfrak h_{I_1}^\vee[-1])\widehat\otimes
   \widehat{\mathbf S}(\mathfrak h_{I_2}^\vee[-1])$
  obtained from the dual surjection
  $\mathfrak h_V^\vee\twoheadrightarrow
  \mathfrak h_{I_1}^\vee\oplus\mathfrak h_{I_2}^\vee$. On the brane
  side,
  $A_\partial^{\mathrm{Ham}}(I_1)\otimes A_\partial^{\mathrm{Ham}}(I_2)
  \to A_\partial^{\mathrm{Ham}}(V)$ is the multiplication map under
  the inclusion of
  $\mathfrak h_{I_1}\oplus\mathfrak h_{I_2}\hookrightarrow\mathfrak h_V$.
  By \ref{prop:brane-bracket-locality}, the bracket between the two
  factors vanishes on disjoint supports, so the product is strictly
  multiplicative. The induced map between central-operation
  factorization algebras is the corresponding tensor product of
  multiplication operators. This is exactly the dual of the CE-source
  extension by zero. Therefore the diagram
  $$\begin{array}{ccc}
    \mathcal F_{\mathrm{cl}}(I_1)\otimes\mathcal F_{\mathrm{cl}}(I_2)
      &\xrightarrow{\Phi(I_1)\otimes\Phi(I_2)}
      & \mathrm Z^{P_0}_{\mathrm{fact}}(A_\partial^{\mathrm{Ham}})(I_1)
        \otimes\mathrm Z^{P_0}_{\mathrm{fact}}(A_\partial^{\mathrm{Ham}})(I_2)\\
    \uparrow & & \downarrow\\
    \mathcal F_{\mathrm{cl}}(V)
      &\xrightarrow{\Phi(V)}
      & \mathrm Z^{P_0}_{\mathrm{fact}}(A_\partial^{\mathrm{Ham}})(V)
  \end{array}$$
  commutes after vertical reversal of the left arrow (CE coproduct =
  dual of inclusion).

  \emph{Step 7.} Locally constant structure. By
  \ref{lem:derivative-jets} the de Rham contraction in $t$ kills all
  positive jets in $C^\infty_c(I)$, leaving values at points. The
  translation vector field $\partial_t$ is $Q$-exact through
  $[d_\R,\iota_{\partial_t}]=\partial_t$. Hence the structure maps
  for inclusions of intervals are quasi-isomorphisms on both sides;
  the $E_1$-equivalent associative algebra structure is the
  underlying graded-commutative product on the stalk, equipped with
  the strict $P_0$ bracket of \ref{constr:interval-fact-algebras}.

  \emph{Step 8.} Stalk recovery. As $I$ shrinks to a point
  $t_0\in\R$, $C^\infty_c(I)$ contracts onto evaluation at $t_0$ in
  cohomology (\ref{lem:derivative-jets}). The image of a length-one
  CE coordinate becomes the multiplication operator $L_{B_f}$ at the
  stalk, recovering \ref{prop:stalk-central-multiplication}.
\end{proof}

\begin{rmk}[Locally constant equivalence and $E_1$-algebra translation]\label{rmk:E1-translation}
  In the locally constant setting on $\R$, factorization algebras are
  equivalent to homotopy associative algebras up to translation
  invariance \cites{costello-gwilliam,costello-gwilliam-vol2} (Lurie,
  \emph{Higher Algebra}, \S 5.5.4). The Hochschild cochain complex of
  the $E_1$ algebra computes the factorization-center stalk. For
  graded-commutative $E_1$ algebras (which the open Hamiltonian stalk
  is, in the reduced model), the Hochschild cochain complex is
  quasi-isomorphic to polyvector fields by HKR, and its strict $P_0$
  subalgebra of multiplication operators with constant differential
  is the polynomial Hamiltonian sector
  $\widehat{\mathbf S}(\mathfrak h_I)\widehat\otimes
  \widehat{\mathbf S}(\mathfrak h_I^\vee[-1])$. The CE source
  identification of
  \ref{thm:open-closed-derived-center-factorization} is exactly the
  closed dual of this PV picture in the connected Hamiltonian sector.
\end{rmk}

For a factorization algebra $\mc A$ on the line, write
$\mathrm Z_{\mathrm{fact}}(\mc A)$ for the factorization algebra of $E_1$
central operations. In the locally constant one-dimensional case its stalk is
the Hochschild cochain complex of the corresponding $E_1$ algebra. The notation
$\mathrm Z^{P_0}_{\mathrm{fact}}(\mc A)$ means the same central operations with
the additional compatibility homotopies for the classical Poisson/BV bracket.
The proposition below records the degree-zero current shadow as a
corollary of
\ref{thm:open-closed-derived-center-factorization}.

\begin{prop}[Healed Hamiltonian-current central operation]\label{thm:hamiltonian-current-center-lift}
  \ref{thm:open-closed-derived-center-factorization} restricted to the
  length-one CE component on each interval recovers the degree-zero
  Hamiltonian current shadow: the assignment
  $$\Phi_{I,N}(a\otimes f)(u)=B_f(a)\cdot u
    =\Bigl(\int_I a(t)\,
      \overline{\mathrm{Tr}\,f(\phi_1(t),\phi_2(t))}\,dt\Bigr)u$$
  is a Hochschild $0$-cocycle in $\mathrm Z_{\mathrm{fact}}
  (\mathrm{Obs}^{\mathrm{cl,red}}_{\mathrm{open},N})(I)$, the assignments
  are compatible with interval inclusions and disjoint factorization
  products, and the induced operations satisfy
  $$\{\Phi(a\otimes f),\Phi(b\otimes g)\}_{\mathrm{open}}
    =\Phi(ab\otimes\{f,g\}_{\bar A}).$$
  The earlier degree-zero current shadow is therefore the length-one
  shadow of the present quasi-isomorphism, not a tautology of graded
  commutativity: its content is the strict $P_0$ identity, which is
  one of the structure equations defining
  $\Phi^{\mathrm{Ham}}_{\mathrm{fact}}$ of
  \ref{thm:open-closed-derived-center-factorization}.
\end{prop}

\begin{proof}
  In the reduced open model $Q\phi_1=Q\phi_2=0$. Hence
  $\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}$ is $Q$-closed for every
  Hamiltonian $f$, and the compactly supported integral is $Q$-closed.
  Since the reduced open observable algebra is graded-commutative,
  multiplication by this closed element is a Hochschild $0$-cocycle;
  this is the interval-wise version of
  \ref{prop:stalk-central-multiplication}. Extension by zero of the
  test function is compatible with restriction to a larger interval.
  For disjoint intervals \ref{prop:brane-bracket-locality} gives
  vanishing of the $P_0$ bracket between the two factors, so the
  factorization product of two such operations is the strict
  multiplication by $I_\partial(a,f)I_\partial(b,g)$; this is the
  multiplicative extension from $\mathfrak h_I$ to
  $A_\partial^{\mathrm{Ham}}(I)=\widehat{\mathbf S}(\mathfrak h_I)$, not
  the linear current bracket.

  The Poisson statement is local on the line. For compactly supported
  test functions $a,b$,
  \ref{cor:local-bulk-boundary-coupling} (the strict $P_0$ identity
  on the brane factorization algebra) gives
  $$\{I_\partial(a,f),I_\partial(b,g)\}_{\mathrm{open}}
    =I_\partial(ab,\{f,g\}_{\bar A}).$$
  Passing to the connected stable Hamiltonian quotient removes only
  the scalar Hamiltonian line, which is central for the bracket. Thus
  the current bracket is preserved. Taking $a$ and $b$ supported in a
  small coordinate interval and then passing to the locally constant
  stalk recovers \ref{thm:bulk-boundary}.
\end{proof}

\begin{prop}[CE-source obstruction, reframed]\label{prop:ce-source-obstruction}
  Let $\mathfrak h$ be a perfect Lie algebra in $\Cat{TateVec}$
  (i.e.\ $[\mathfrak h,\mathfrak h]=\mathfrak h$). Then no length-one CE
  coordinate $c^I$ dual to a Hamiltonian generator $H_I\in\mathfrak h$
  is closed under $d_{\mathrm{CE}}$:
  $$d_{\mathrm{CE}}c^K=-\tfrac12\,C^K_{IJ}\,c^Ic^J\neq 0.$$
  Equivalently, $H^1(\mathfrak h;\C)=0$.

  This obstruction is the structural reason that the boundary observable
  $O_I=J(H_I)\in A_\partial$ cannot be the image under $\Phi$ of $c^I$.
  Instead, under \ref{thm:open-closed-derived-center},
  $$O_I=\Phi(u_I),$$
  the image of the CE coordinate dual to the shifted cotangent generator
  $\eta_{\delta_I}\in\mathfrak h^\vee[1]$. The boundary observable lives
  in the cotangent direction of the CE cochain algebra, not in the
  Hamiltonian direction. Its CE differential is not zero but
  $d_{\mathrm{CE}}u_K=C^L_{KJ}u_Lc^J$, mapping under $\Phi$ to the
  Hamiltonian vector field $d_\pi O_K=C^L_{KJ}O_L\theta^J$ of $O_K$ in
  the Schouten algebra.

  This is exactly what a $P_0$-algebra map should produce: a function
  whose Schouten differential is its Hamiltonian vector field.
\end{prop}

\begin{proof}
  $\mathfrak h$ perfect means $C^K_{IJ}c^Ic^J\neq 0$ for some triple
  $(I,J,K)$ realizing a non-trivial bracket; $H^1$ vanishing follows.
  Identification $O_I=\Phi(u_I)$ is the content of
  \ref{cor:moment-map-shadow} combined with $\Phi(u_I)=O_I$ from
  \ref{thm:open-closed-derived-center}. Differentials match on
  generators by \ref{lem:linear-poisson-schouten}.
\end{proof}

\begin{rmk}\label{rmk:ce-source-obstruction-disk}
  The reduced Hamiltonian Lie algebra
  $\mathfrak h=\widehat A/\C\cdot 1=(z_1,z_2)\C[[z_1,z_2]]$ of the
  formal symplectic disk in dimension two is perfect: for every
  monomial one has, before quotienting constants,
  $z_1^az_2^b=\bigl\{z_1,\tfrac{1}{b+1}z_1^az_2^{b+1}\bigr\}$, so
  $[\mathfrak h,\mathfrak h]=\mathfrak h$. In particular
  $[H_{1,0},H_{m,n}]=n\,H_{m,n-1}$ and
  $[H_{0,1},H_{m,n}]=-m\,H_{m-1,n}$. The hypothesis of
  \ref{prop:ce-source-obstruction} is met. The CE-length-one cochain
  $\xi_{a,b}=c^{a,b}$ dual to $H_{a,b}=z_1^az_2^b$ is therefore not
  closed, and no closed CE cochain has linear Hamiltonian part
  $c^{a,b}$, recovering the earlier source-obstruction observation.
\end{rmk}

\begin{thm}[Reduced derived Poisson center]\label{thm:reduced-derived-poisson-center}
  Let
  $$\mathfrak h=\prod_{d\geq1}H_d,\qquad
    \mathfrak h^\vee_{\mathrm{cont}}=\bigoplus_{d\geq1}H_d^\vee$$
  be the product/direct-sum Tate Hamiltonian Lie algebra of the formal
  symplectic disk and its continuous dual. Put
  $$\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1].$$
  Let $A_\partial=\widehat{\mathbf S}(\mathfrak h)$ be the completed stable
  degree-zero Hamiltonian trace algebra, with generators $O_i$ corresponding to
  a homogeneous topological basis $H_i$ of $\mathfrak h$. If
  $$[H_i,H_j]=C_{ij}^{k}H_k,$$
  with the constant target projected out, equip $A_\partial$ with the linear
  Poisson bracket
  $$\{O_i,O_j\}_\partial=C_{ij}^{k}O_k.$$
  Let
  $$\operatorname{PV}_{\mathrm{cont}}(A_\partial)
    =
    A_\partial\widehat\otimes
    \widehat\Lambda(\mathfrak h^\vee_{\mathrm{cont}})$$
  be the completed algebra of continuous polyvectors, with odd generators
  $\theta_i$ dual to the coordinates $O_i$. The Poisson bivector is
  $$\pi_\partial=\frac12 C_{ij}^{k}O_k\,\theta_i\theta_j,$$
  and the Poisson differential is $d_\pi=[\pi_\partial,-]$ in the Schouten
  convention.

  If $c_i$ is the CE coordinate dual to $H_i\in\mathfrak h$ and $u_i$ is the CE
  coordinate dual to the shifted cotangent generator $\delta_i[1]\in
  \mathfrak h^\vee_{\mathrm{cont}}[1]$, then the assignment
  $$c_i\longmapsto\theta_i,\qquad u_i\longmapsto O_i$$
  extends to an isomorphism of completed graded-commutative dg algebras
  $$C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
    \xrightarrow{\ \sim\ }
    \bigl(\operatorname{PV}_{\mathrm{cont}}(A_\partial),d_\pi\bigr).$$
\end{thm}

\begin{proof}
  By the product/direct-sum convention already used in
  Proposition~\ref{prop:ce-koszul}, the continuous CE algebra of
  $\mathfrak g$ is freely generated, after completion, by the odd coordinates
  $c_i$ and the even coordinates $u_i$. The CE differential is dual to the
  brackets of $\mathfrak g$:
  $$d_{\mathrm{CE}}c_k=-\frac12 C_{ij}^{k}c_ic_j,\qquad
    d_{\mathrm{CE}}u_k=C_{kj}^{\ell}u_\ell c_j.$$
  The second formula is the coadjoint action of $\mathfrak h$ on
  $\mathfrak h^\vee_{\mathrm{cont}}[1]$ written on the dual coordinates.

  The linear Poisson bivector gives the Lichnerowicz differential
  \cite{lichnerowicz-poisson}
  $$d_\pi\theta_k=-\frac12 C_{ij}^{k}\theta_i\theta_j,\qquad
    d_\pi O_k=C_{kj}^{\ell}O_\ell\theta_j.$$
  Hence $c_i\mapsto\theta_i$ and $u_i\mapsto O_i$ intertwine the two
  differentials. The underlying completed graded-commutative algebras are
  freely generated by corresponding variables, so this is an isomorphism.

  Continuity is the same coefficient-finiteness used in
  Lemma~\ref{lem:continuous-bar-cobar}: for each fixed output coefficient in a
  bracket of Hamiltonians only finitely many homogeneous input-degree pairs
  contribute, and the coadjoint input has finite support in
  $\mathfrak h^\vee_{\mathrm{cont}}$. Thus the displayed sums define
  continuous derivations of the completed CE and polyvector algebras.
\end{proof}

\begin{rmk}
  The theorem is the reduced algebraic center calculation. It does not say that
  the scalar boundary function $O_f=\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}$
  is the image of the nonclosed CE coordinate $c_f$. It says that $O_f$ is the
  image of the CE coordinate $u_f$ dual to the shifted cotangent generator,
  while $c_f$ maps to the constant Hamiltonian vector-field operation
  $\theta_f$. This is why Proposition~\ref{prop:ce-source-obstruction} remains
  correct and why the full BV/factorization lift below has nontrivial content.
\end{rmk}

\begin{thm}[Open-closed derived center, cochain level]\label{thm:open-closed-derived-center}
  Let $\mathfrak h$ be any pro-finite-dimensional Lie algebra in
  $\Cat{TateVec}$ over $\C$, concentrated in degree zero, satisfying
  the Tate-conilpotency hypothesis of \ref{lem:continuous-bar-cobar}.
  Let $\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1]$
  be the shifted-cotangent extension. Let
  $A_\partial=\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)$ be the
  Tate-completed Kirillov--Poisson algebra of
  \ref{lem:linear-poisson-schouten}.

  Then there is a canonical isomorphism of completed dg
  graded-commutative $P_0$-algebras
  $$\Phi:C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
    \xrightarrow{\ \sim\ }
    \mathrm{PV}\bigl(A_\partial\bigr),$$
  determined on generators by
  $$\Phi(c^I)=\theta^I,\qquad \Phi(u_I)=O_I,$$
  where $c^I$ is the CE coordinate dual to $H_I\in\mathfrak h$ and
  $u_I$ is the CE coordinate dual to the shifted cotangent generator
  $\eta_{\delta_I}\in\mathfrak h^\vee[1]$.

  Moreover, $\mathrm{PV}(A_\partial)$ identifies with the derived
  $P_0$-factorization center of the constant factorization algebra
  $A_\partial$, so
  $$\Phi:C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
    \xrightarrow{\ \sim\ } Z^{P_0}_{\mathrm{fact}}(A_\partial)$$
  is the cochain-level open-closed derived center isomorphism in the
  formal/local sector.
\end{thm}

\begin{proof}
  \emph{Generators and free extension.} By
  \ref{lem:continuous-bar-cobar},
  $$C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)=
    \widehat{\mathbf S}_{\mathrm{Tate}}\bigl(
      (\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1])^\vee_{\mathrm{cont}}[-1]
    \bigr)
    \cong \widehat{\mathbf S}_{\mathrm{Tate}}\bigl(\{u_I\}\bigr)
    \widehat\otimes \widehat\Lambda\bigl(\{c^I\}\bigr),$$
  with $|u_I|=0$ and $|c^I|=1$. On the open side,
  $\mathrm{PV}(A_\partial)=\widehat{\mathbf S}_{\mathrm{Tate}}(\{O_I\})
  \widehat\otimes \widehat\Lambda(\{\theta^I\})$, with $|O_I|=0$ and
  $|\theta^I|=1$. The same generator data on both sides freely generate
  completed graded-commutative algebras in $\Cat{TateVec}$ of the same
  shape; the assignment $c^I\mapsto\theta^I$, $u_I\mapsto O_I$ extends
  uniquely to a continuous bijection of completed dg-commutative
  algebras.

  \emph{Cochain identity on generators.} The CE differential is
  $$d_{\mathrm{CE}}c^K=-\tfrac12 C^K_{IJ}c^Ic^J,\qquad
    d_{\mathrm{CE}}u_K=C^L_{KJ}u_L c^J.$$
  By \ref{lem:linear-poisson-schouten},
  $$d_\pi\theta^K=-\tfrac12 C^K_{IJ}\theta^I\theta^J,\qquad
    d_\pi O_K=C^L_{KJ}O_L\theta^J.$$
  Therefore
  $$\Phi(d_{\mathrm{CE}}c^K)=-\tfrac12 C^K_{IJ}\theta^I\theta^J
    =d_\pi\theta^K=d_\pi\Phi(c^K),$$
  $$\Phi(d_{\mathrm{CE}}u_K)=C^L_{KJ}O_L\theta^J=d_\pi O_K
    =d_\pi\Phi(u_K).$$

  \emph{Cochain identity on the full completed algebra.} Both
  $d_{\mathrm{CE}}$ and $d_\pi$ are degree-$1$ derivations of the
  completed graded-commutative algebra structures on each side. They
  satisfy the graded Leibniz rule with the same Koszul sign
  convention. $\Phi$ is an algebra homomorphism, so
  $$\Phi(d_{\mathrm{CE}}(xy))
    =\Phi\bigl((d_{\mathrm{CE}}x)y+(-1)^{|x|}x\,d_{\mathrm{CE}}y\bigr)
    =\Phi(d_{\mathrm{CE}}x)\Phi(y)+(-1)^{|x|}\Phi(x)\Phi(d_{\mathrm{CE}}y),$$
  while
  $$d_\pi\Phi(xy)=d_\pi\bigl(\Phi(x)\Phi(y)\bigr)
    =(d_\pi\Phi(x))\Phi(y)+(-1)^{|x|}\Phi(x)d_\pi\Phi(y).$$
  Generator-level agreement plus Leibniz/algebra-homomorphism gives
  agreement on every word in $\{c^I,u_J\}$ at fixed total length;
  Tate-completeness of both sides plus continuity of $d_{\mathrm{CE}},
  d_\pi,\Phi$ in the Tate filtration extends the equality to the
  completed algebras.

  \emph{Inverse.} The assignment $\theta^I\mapsto c^I$,
  $O_I\mapsto u_I$ extends to a continuous algebra homomorphism in the
  opposite direction. By the same Leibniz argument, it intertwines
  $d_\pi$ and $d_{\mathrm{CE}}$. The two compositions fix generators,
  hence fix the completed algebras. So $\Phi$ is an isomorphism of
  complete dg graded-commutative algebras.

  \emph{$P_0$-bracket compatibility.} The CE side carries the canonical
  $(-1)$-shifted Poisson structure on
  $C^\bullet_{\mathrm{CE},\mathrm{cont}}(T^*[1]\mathfrak h)$ with
  $$\{c^I,u_J\}_{\mathrm{CE}}=\delta^I_J,\quad
    \{c^I,c^J\}_{\mathrm{CE}}=0,\quad
    \{u_I,u_J\}_{\mathrm{CE}}=0.$$
  These are the standard Poisson brackets on the cochain algebra of a
  $(-1)$-shifted cotangent of a Lie algebra
  (cf.\ Costello--Gwilliam factorization-algebra conventions).
  The Schouten bracket on $\mathrm{PV}(A_\partial)$ satisfies
  $$[\theta^I,O_J]_S=\delta^I_J,\quad
    [\theta^I,\theta^J]_S=0,\quad
    [O_I,O_J]_S=0,$$
  the last because $O_I,O_J$ are functions on the formal affine space
  $\mathfrak h^\vee$ and the Schouten bracket of two functions is zero.
  Generator-level matching gives
  $\Phi\bigl(\{c^I,u_J\}_{\mathrm{CE}}\bigr)
  =\Phi(\delta^I_J)=\delta^I_J=[\theta^I,O_J]_S
  =[\Phi(c^I),\Phi(u_J)]_S$, and similarly for the other two pairs.
  Both brackets satisfy the graded Leibniz rule; bilinear extension on
  completed words gives compatibility on the full completed algebra.

  \emph{Identification with the derived $P_0$-factorization center.}
  For a Poisson algebra $A$ regarded as a constant
  $\R^d$-factorization algebra (or as a stalk of a locally constant
  factorization algebra), the derived $P_0$-factorization center is
  computed by the Poisson cochain complex $\mathrm{PV}(A)$ with the
  Lichnerowicz differential $[\pi,-]_S$. This is the local stalk
  version of the Poisson-CE identification of Cattaneo--Felder /
  Costello--Gwilliam (cf.~\cite{costello-gwilliam}, central operations
  for factorization algebras with Poisson bracket; the identification
  is local: at a point, the factorization-center is the Poisson-cochain
  complex). Therefore
  $\mathrm{PV}(A_\partial)\simeq Z^{P_0}_{\mathrm{fact}}(A_\partial)$
  as completed dg-commutative $P_0$-algebras, and $\Phi$ is the
  cochain-level open-closed derived center isomorphism in this local
  stalk sense.
\end{proof}

\begin{cor}[Moment-map shadow]\label{cor:moment-map-shadow}
  In the situation of \ref{thm:open-closed-derived-center}, the
  degree-zero specialization of $\Phi$ on the cotangent direction is
  the moment-map / Kirillov assignment
  $$J:\mathfrak h\longrightarrow A_\partial=
    \widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h),
    \qquad J(f)=O_f.$$
  The closed-side Lie bracket $\{f,g\}_{\mathfrak h}$ matches the
  Kirillov--Poisson bracket on $A_\partial$:
  $$\{J(f),J(g)\}_\partial=J\bigl(\{f,g\}_{\mathfrak h}\bigr).$$
\end{cor}

\begin{proof}
  $J$ is the restriction of $\Phi$ to the cotangent direction
  $u_I\mapsto O_I$ followed by linear extension along
  $\mathfrak h\hookrightarrow A_\partial$ (the canonical embedding of
  $\mathfrak h$ as the linear functions on $\mathfrak h^\vee$). Bracket
  compatibility is the $(c^J,u_K)$-versus-$(\theta^J,O_K)$ identity
  from \ref{thm:open-closed-derived-center} read off in degree zero.
  Equivalently, this is the standard Kirillov--Kostant--Souriau theorem
  for linear Poisson structures.
\end{proof}

\begin{cor}[Derived center, formal symplectic disk]\label{cor:derived-center-formal-disk}
  Let $\mathfrak h=\widehat A/\C\cdot 1=(z_1,z_2)\C[[z_1,z_2]]$ be the
  reduced Hamiltonian Lie algebra of the formal symplectic disk on
  $\C^2$, with bracket
  $\{f,g\}=\partial_{z_1}f\,\partial_{z_2}g-\partial_{z_2}f\,\partial_{z_1}g$
  modulo constants. Choose the Taylor basis $H_{a,b}=z_1^az_2^b$ for
  $a,b\geq 0$, $a+b>0$. Structure constants:
  $$[H_{a,b},H_{c,d}]=(ad-bc)\,H_{a+c-1,b+d-1},$$
  with the convention that $H_{m,n}=0$ if $\min(m,n)<0$ or $m+n=0$.

  Set $A_\partial=\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)$,
  with linear coordinates $O_{a,b}$ on $\mathfrak h^\vee$ and
  Kirillov--Poisson bracket
  $\{O_{a,b},O_{c,d}\}_\partial=(ad-bc)O_{a+c-1,b+d-1}$.
  \ref{thm:open-closed-derived-center} gives the cochain-level
  derived-center isomorphism
  $$\Phi:C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak h\ltimes
    \mathfrak h^\vee_{\mathrm{cont}}[1])\xrightarrow{\ \sim\ }
    \mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr),
    \qquad c^{a,b}\mapsto\theta^{a,b},\quad u_{a,b}\mapsto O_{a,b}.$$
  Its moment-map shadow is the boundary evaluation map
  $J(f)=O_f=\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}$ of
  \ref{thm:bulk-boundary} after identifying $A_\partial$ with the
  stable connected scalar-reduced Hamiltonian trace algebra of
  \ref{prop:brane-ops}.
\end{cor}

\begin{proof}
  The structure constants are an instance of
  \ref{prop:hamiltonian-polyvector-reduction} read on monomials.
  Apply \ref{thm:open-closed-derived-center} to this $\mathfrak h$
  (perfect; pro-finite-dimensional in Taylor filtration;
  Tate-conilpotent; see \ref{rmk:ce-source-obstruction-disk}). The
  moment-map shadow follows from \ref{cor:moment-map-shadow} together
  with \ref{thm:bulk-boundary}.
\end{proof}

\begin{ex}[Low-degree monomial verification]\label{ex:low-degree-phi}
  We verify $\Phi$ on small monomials of the formal symplectic disk.

  \begin{itemize}
    \item \emph{Degree-1 generators.} Take $H_{1,0}=z_1$,
      $H_{0,1}=z_2$. The bracket
      $[H_{1,0},H_{0,1}]=1\cdot 1-0\cdot 0=1$ lifts to the constant
      $H_{0,0}$, which is set to zero in $\mathfrak h$. Hence
      $C^{0,0}_{(1,0),(0,1)}=0$ in $\mathfrak h$. Consequently
      $d_{\mathrm{CE}}u_{0,0}$ is not present (no such generator); the
      $u_{0,0}$ degree of freedom does not appear, consistent with
      constants being removed.

    \item \emph{Degree-2 calculation.} Take $H_{2,0}=z_1^2$,
      $H_{0,2}=z_2^2$. The bracket
      $\{z_1^2,z_2^2\}=2z_1\cdot 2z_2-0\cdot 0=4z_1z_2=4H_{1,1}$, so
      $C^{1,1}_{(2,0),(0,2)}=4$ and the antisymmetric companion is
      $C^{1,1}_{(0,2),(2,0)}=-4$. The cochain identity reads
      $$d_{\mathrm{CE}}u_{1,1}=4\,u_{2,0}\,c^{0,2}-4\,u_{0,2}\,c^{2,0}+
        \cdots,$$
      where $\cdots$ denotes terms from other index triples
      $(K,J,L)$ with $K=(1,1)$. Each such term
      $C^L_{(1,1),J}\,u_L\,c^J$ arises from
      $\{H_{1,1},H_J\}=\sum_L C^L_{(1,1),J}\,H_L$. For example,
      $\{H_{1,1},H_{1,0}\}=\partial_{z_1}(z_1z_2)\cdot 0-
      \partial_{z_2}(z_1z_2)\cdot 1=-z_1=-H_{1,0}$, so
      $C^{1,0}_{(1,1),(1,0)}=-1$, contributing $-u_{1,0}\,c^{1,0}$ to
      $d_{\mathrm{CE}}u_{1,1}$. On the open/PV side,
      $$d_\pi O_{1,1}=4\,O_{2,0}\,\theta^{0,2}-4\,O_{0,2}\,\theta^{2,0}
        -O_{1,0}\,\theta^{1,0}+O_{0,1}\,\theta^{0,1}+\cdots,$$
      the same expression with $u\to O,c\to\theta$. Hence
      $\Phi(d_{\mathrm{CE}}u_{1,1})=d_\pi\Phi(u_{1,1})$. The script
      \texttt{scripts/check\_moyal\_coefficients.py} verifies the same
      structure-constant input on every monomial pair with exponents
      up to $6$ via the first-order Moyal coefficient $kn-lm$ at
      $\hbar^1$, which equals $C^K_{IJ}$ for these indices.

    \item \emph{Higher-order word.} For $K=(1,1)$, $J=(1,0)$,
      $J'=(0,1)$, the cochain element $u_{1,1}c^{1,0}c^{0,1}$ has
      degree $0+1+1=2$. Its CE differential, by graded Leibniz, is
      $$d_{\mathrm{CE}}\bigl(u_{1,1}c^{1,0}c^{0,1}\bigr)
        =(d_{\mathrm{CE}}u_{1,1})c^{1,0}c^{0,1}
        -u_{1,1}(d_{\mathrm{CE}}c^{1,0})c^{0,1}
        +u_{1,1}c^{1,0}(d_{\mathrm{CE}}c^{0,1}),$$
      with each summand applying the generator formulas above. The
      same word on the PV side is $O_{1,1}\theta^{1,0}\theta^{0,1}$,
      and $d_\pi$ applied with the same Leibniz convention produces
      the corresponding triple sum with $u\to O$ and $c\to\theta$.
      Term-by-term equality follows from the generator identities; the
      full word equality is the algebra-homomorphism Leibniz argument
      from \ref{thm:open-closed-derived-center}.
  \end{itemize}
\end{ex}

\begin{constr}[Compact current PBW/Rees source]\label{constr:compact-current-pbw-rees-source}
  Let $\mc P$ denote the principal-part module
  $$\mc P=\bigoplus_{\substack{a,b\geq0\\ a+b>0}}\C\,\rho_{a,b},\qquad
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2,$$
  identified with $\mathfrak h^\vee_{\mathrm{cont}}$ by the residue pairing
  of Proposition~\ref{prop:principal-part-coadjoint}. Put
  $$\mathfrak g_{\mathrm{pp}}=\mathfrak h\ltimes\mc P[1],$$
  with zero differential and bracket
  $$[f,g]=\{f,g\},\qquad [f,\rho[1]]=(f\cdot\rho)[1],\qquad
    [\rho[1],\sigma[1]]=0,$$
  where $f\cdot\rho=\pi_{\mathrm{pp}}\{f,\rho\}$. On monomials this action is
  $$z_1^pz_2^q\cdot\rho_{a,b}
    =-(pb-qa+p-q)\rho_{a-p+1,b-q+1},$$
  with negative-index targets zero.

  For an interval $I\subset\R$, define the compactly supported current Lie
  algebra
  $$\mathfrak J_{\mathfrak g}(I)
    =C_c^\infty(I)\widehat\otimes\mathfrak g_{\mathrm{pp}},\qquad
    [\alpha\otimes x,\beta\otimes y]
      =\alpha\beta\otimes[x,y].$$
  Its PBW/Rees algebra is
  $$U_\hbar\bigl(\mathfrak J_{\mathfrak g}(I)\bigr)
    =\widehat T\bigl(\mathfrak J_{\mathfrak g}(I)\bigr)[[\hbar]]
      \big/
      \langle xy-(-1)^{|x||y|}yx-\hbar[x,y]\rangle.$$
  The PBW filtration is the tensor-word filtration. Its special fibre is
  $$U_\hbar\bigl(\mathfrak J_{\mathfrak g}(I)\bigr)/(\hbar)
    \cong \widehat{\mathbf S}\bigl(\mathfrak J_{\mathfrak g}(I)\bigr),$$
  equipped with the semiclassical $P_0$ bracket
  $$\{\bar X,\bar Y\}_{P_0}
    =\bigl(\hbar^{-1}(XY-(-1)^{|X||Y|}YX)\bigr)\bmod\hbar.$$
  This is the PBW/Koszul-dual source for Hamiltonian and principal-part modes.
  It is not a closed CE cochain algebra map; the CE comparison must be made
  separately by bar-cobar twisting or by a completed pairing.
\end{constr}

\begin{prob}[PBW-source $P_0$ center action and CE comparison]\label{prob:pbw-p0-center-action}
  Construct a filtered factorization-center action of the compactly
  supported current PBW/Rees source
  $U_\hbar(\mathfrak J_{\mathfrak g})$ of
  Construction~\ref{constr:compact-current-pbw-rees-source}. The target cannot
  be the polynomial open observable algebra alone if the cotangent generators
  are included; it must use the enlarged principal-part boundary object of
  Theorem~\ref{prop:reduced-principal-part-boundary-current}. In the
  classical special fibre the action must send
  $$f\longmapsto B_f=\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)},\qquad
    \rho_{a,b}[1]\longmapsto\Theta_{a,b},$$
  and satisfy the stalkwise bracket identities
  $$\{B_f,B_g\}_{\mathrm{open}}=B_{\{f,g\}},\qquad
    \{B_f,\Theta_\rho\}_{\mathrm{open}}=\Theta_{f\cdot\rho},\qquad
    \{\Theta_\rho,\Theta_\sigma\}_{\mathrm{open}}=0.$$
  This special-fibre statement is the natural $P_0$ theorem. A strict action
  of the full filtered Rees algebra on the same commutative reduced target is
  not a consequence of these identities: in the source
  $$XY-(-1)^{|X||Y|}YX=\hbar[X,Y],$$
  while multiplication operators on a commutative classical target commute.
  Thus the Rees-level theorem requires either a deformed boundary target or an
  explicit homotopical quantization of the central operations.
  The target data must include differential compatibility, factorization
  centrality homotopies, coherent $P_0$ bracket homotopies, and
  compact-support naturality for interval inclusions and disjoint unions before
  the de Rham contraction.

  Separately compare this PBW/Koszul-dual source with the closed CE observable
  algebra by an explicit twisting or pairing construction. Without this
  comparison, the result is a PBW/Koszul-dual boundary action, not a
  cochain-level map from closed CE observables.
\end{prob}

\begin{prob}[Unreduced Tate-coefficient cotangent lift]\label{prob:formal-factorization-center}
  This is the single residual of the umbrella theorem
  \ref{thm:main-local}. Construct a Tate or weighted-coefficient
  extension of the BV heat-kernel calculus on $\R^2\times\C^2$ in
  which:
  \begin{enumerate}
    \item the formal Casimir
      $C_{\mathfrak h}=\sum_{d\geq 1}\sum_i e_{d,i}\otimes e^i_d$
      converges as an element of
      $\widehat{\mathfrak h}\,\widehat\otimes\,
      \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}$;
    \item the Costello propagator $P_{\epsilon,L}$ extends to that
      coefficient category;
    \item the unreduced principal-part current sub-factorization
      algebra
      $\widetilde{\mathrm{Obs}}^{\mathrm{cl,pp}}_{\partial,N}(I)
      =\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},N}(I)\,\widehat\otimes\,
      \widehat{\mathbf S}\bigl(\mc M^{\mathrm{pp,unred}}_\partial(I)\bigr)$
      admits a chain-level primitive projection $\pi_{\mathrm{prim}}$
      with verified $Q$-compatibility, factorization compatibility, and
      $P_0$-bracket homotopies;
    \item statement~(d) of \ref{thm:main-local} lifts to the
      unreduced factorization-algebra model and statement~(e) extends
      to the cotangent (one-antifield) sector at all orders in $\hbar$.
  \end{enumerate}

  Equivalently, lift the cochain-level
  \ref{thm:open-closed-derived-center} and the Hamiltonian-sector
  factorization-algebra
  \ref{thm:open-closed-derived-center-factorization} to a
  cochain-level morphism of factorization algebras
  $$\Phi_{\mathrm{cl}}:
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H}\big|_{\R\times p}
    \longrightarrow
    \mathrm Z^{P_0}_{\mathrm{fact}}\bigl(\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},N}\bigr)$$
  on the unreduced (cotangent-included) sector, with all $P_0$-center
  homotopies, factorization centrality homotopies, the stable
  connected quotient, and a boundary realization of the shifted
  cotangent generators. Any global version must additionally pass
  through the local-Hamiltonian descent and period obstruction of
  \ref{prop:formal-local-global-restriction}; a stalkwise formal
  disk map is not a Weiss/Ran descent theorem for factorization
  centers.

  Two routes are named, neither yet executed.
  \begin{itemize}
    \item \emph{Route R1: weighted Tate completion.} Replace the
      direct sum $\bigoplus_{d\geq 1}H_d^{\vee}$ by a weighted Tate
      completion in which the Casimir converges. The
      $\mathfrak m$-adic completion fails by the finite-window
      obstruction; a candidate is a graded-Mittag-Leffler completion
      controlled by a polynomial weight in the degree filtration,
      checked compatible with the Costello RG flow at every order.
    \item \emph{Route R2: nilpotent truncation.} Restrict to the
      smaller Lie sector $\mathfrak m^2/\mathfrak m^{N+1}$ or analogous
      nilpotent truncation, declaring that translations and the
      constant-Hamiltonian $\hbar$-normalization have been removed
      (the Costello--Li $\mathfrak{gl}(N\mid N)$ precedent). This
      loses the fully stable connected statement on $\mathfrak h$ but
      recovers a meaningful nilpotent sector unconditionally.
  \end{itemize}

  The deciding evidence to close: either (R1) yields a
  Tate-coefficient category with the displayed Casimir convergence
  and BV propagator extension, or (R2) gives an explicit obstruction
  class for the unreduced cotangent lift (which would itself be a
  major theorem and would not invalidate the reduced umbrella
  \ref{thm:main-local}, parts (a)--(f)).

  The residual is identified across four independent obstruction
  routes as the same obstruction. The cotangent direction
  $\mathfrak h^{\vee}_{\mathrm{cont}}[1]$ supports the
  deformation-correct realization $\mc P$ at the cochain level; fails
  to admit a polynomial sub-bimodule realization in any
  locally-nilpotent category; admits a factorization-algebra
  realization at the reduced post-contraction level; and obstructs
  the unreduced lift at the analytic level. The umbrella theorem is
  unconditional in parts (a), (b), (c), (e) on the degree-zero
  Hamiltonian sector, and (f); part~(d) is unconditional at the
  reduced post-contraction level and conditional on this problem for
  the unreduced extension; part~(e) is unconditional on the
  degree-zero Hamiltonian sector at all orders in $\hbar$ and
  conditional on this problem for the descendant (one-antifield)
  sector.
\end{prob}

\begin{rmk}[The residual is conditional, the umbrella is not]
  \ref{thm:main-local} is unconditional in parts (a), (b), (c),
  (e) (degree zero), (f). Part (d) is unconditional at the reduced
  post-contraction level and conditional on
  \ref{prob:formal-factorization-center} for the unreduced
  factorization-algebra extension. Part (e) is unconditional on the
  degree-zero Hamiltonian sector at all orders in $\hbar$ and
  conditional on the same residual for the descendant (one-antifield)
  sector. Cross-volume comparisons (Vol III CY-to-chiral, Igusa
  $\Delta_5$ / BKM, twisted-M-theory universality) are frontier
  obligations recorded in the convention contract appendix; they are
  outside the dependency closure of the present local theorem.
\end{rmk}

\begin{rmk}[Weiss/Ran descent firewall]\label{rmk:weiss-ran-descent-firewall}
  A global closed-open map is not obtained by choosing Darboux coordinates at
  each point and gluing the resulting stalk maps. The obstruction lives in the
  Weiss/Ran total complex
  $$\operatorname{Tot} C^\bullet_{\mathrm{WR}}
    \left(\operatorname{Ran}(L);
    \underline{\operatorname{RHom}}\left(
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H},
    Z^{P_0}_{\mathrm{fact}}(\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}})
    \right)\right).$$
  Vanishing of the local Hamiltonian period class is only the first condition.
  One must also prove source comparison, cotangent boundary realization, all
  $P_0$-center homotopies, and factorization descent. Until then the
  Hamiltonian boundary map, the $\Theta$-currents, and the PBW/Rees action are
  formal local or reduced-current statements.
\end{rmk}

\subsection{Operators in the open brane gauge theory and the large N limit}

The local-operator calculation is performed in the reduced BV model with
fields $\phi_1,\phi_2$ and the antifield $\psi=A^*$ for the Lagrange
multiplier $A$. We take $GL_N$-invariants in characteristic zero, so the
Chevalley part of the gauge BRST differential acts trivially on trace
functions by cyclicity.

The gauge field has one algebraic job: it imposes the moment-map equation
$[\phi_1,\phi_2]=0$. In BV language this equation is imposed by the Koszul
differential $Q\psi=[\phi_1,\phi_2]$. This is why the stable trace algebra
starts noncommutative, as cyclic words in two matrices, and then collapses in
cohomology to commutative monomials on the formal symplectic plane.

\begin{constr}[The reduced BV algebra at the insertion point]\label{constr:reduced-bv-algebra}
  At a fixed point of the brane line, introduce three matrix variables
  $$\phi_1,\phi_2\in\lie{gl}_N,\qquad \psi\in\lie{gl}_N[1].$$
  The reduced local polynomial algebra is
  $$\mc R_N=\C[(\phi_1)^i{}_j,(\phi_2)^i{}_j]
    \otimes\Lambda\bigl((\psi)^i{}_j\bigr).$$
  Its BRST differential is the derivation determined on generators by
  $$Q(\phi_1)^i{}_j=0,\qquad Q(\phi_2)^i{}_j=0,\qquad
    Q(\psi)^i{}_j=([\phi_1,\phi_2])^i{}_j.$$
  This formula is the algebraic shadow of the $A$-equation of motion:
  varying
  $$\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr)$$
  with respect to $A$ gives $[\phi_1,\phi_2]=0$, and the antifield $\psi=A^*$
  records that equation as a Koszul differential.
\end{constr}

\begin{lem}[De Rham jets]\label{lem:derivative-jets}
  Positive jets in the topological direction vanish in local
  operator cohomology. Equivalently, every cohomology class has a representative
  determined by the values of the fields and antifields at the insertion point.
\end{lem}

\begin{proof}
  For a coordinate $t$ on the line, the de Rham part of the BRST operator is
  $d_{\R}$. On the jet algebra one has the contraction homotopy
  $[d_{\R},\iota_{\partial_t}]=\partial_t$. Hence a local expression containing
  a positive $t$-derivative is cohomologous to zero after applying the usual
  Euler homotopy on jet degree. This kills topological-direction jets and leaves
  the holomorphic $z_i$-derivatives used later on the closed side.
\end{proof}

\begin{prop}[Stable trace invariants]\label{prop:stable-trace-invariants}
  Let $F=\C\langle x_1,x_2\rangle$ and let $\mathrm{Cyc}(F)=F/[F,F]$ be the
  vector space of cyclic words. For each $N$, $GL_N$ acts on
  $\lie{gl}_N^2$ by simultaneous conjugation. The degreewise stable invariant
  algebra
  $$\C[\lie{gl}_\infty^2]^{GL_\infty}_{\mathrm{st}}
    :=\bigoplus_{d\geq0}\varprojlim_N
      \bigl(\C[\lie{gl}_N^2]^{GL_N}\bigr)_d$$
  with respect to block-restriction maps in each word-degree
  is the free commutative algebra generated by the nonempty cyclic words:
  $$\C[\lie{gl}_\infty^2]^{GL_\infty}_{\mathrm{st}}
    \cong\mathbf S\bigl(\mathrm{Cyc}(F)_{\mathrm{nonempty}}\bigr),$$
  where a cyclic word $w$ maps to the trace function
  $(\phi_1,\phi_2)\mapsto\mathrm{Tr}\,w(\phi_1,\phi_2)$.
  More precisely, in total positive word-degree $d$ this map is an isomorphism
  for every $N\geq d$, after omitting the scalar empty trace as a primitive
  generator.
\end{prop}

\begin{proof}
  Procesi--Razmyslov invariant theory \cites{procesi,razmyslov} gives two
  inputs. First, $\C[\lie{gl}_N^2]^{GL_N}$ is generated by trace functions of
  words in the two generic matrices. Second, all polynomial relations among
  these trace functions are consequences of the fundamental trace identities
  of matrix size $N$; in particular every homogeneous trace relation has total
  word-degree at least $N+1$. Fix a total word-degree $d$. For every
  $N\geq d$ the degree-$d$ relations are exactly cyclicity of the trace.
  Passing degree by degree to the stable inverse limit removes
  all finite-$N$ trace identities. The surviving identification is
  $\mathrm{Tr}(uv)=\mathrm{Tr}(vu)$. This is exactly the symmetric algebra on
  cyclic words.

\end{proof}

\begin{lem}[Stable marked trace invariants]\label{lem:stable-marked-traces}
  In the stable invariant theory used below, the primitive part linear or
  quadratic in an odd marked matrix $\psi$ is obtained from the corresponding
  even three-matrix trace invariant by polarization and skew-symmetrisation in
  the marked letters. The only stable single-trace relation is graded cyclicity:
  moving one $\psi$ through the trace has sign $+1$, while moving one $\psi$
  past another $\psi$ gives a minus sign.
\end{lem}

\begin{proof}
  Apply Proposition~\ref{prop:stable-trace-invariants} to three even generic
  matrices and take the homogeneous summand linear, respectively quadratic, in
  the third matrix. The Procesi--Razmyslov trace identities have no stable
  relations in the fixed total word-degree once $N$ is large enough. Declaring
  the marked matrix odd is the usual super-polarization: the linear part is
  unchanged, and the quadratic part is projected to the alternating component
  under exchange of the two marked occurrences. The trace relation therefore
  becomes exactly graded cyclicity. These are the signs used in the finite
  complex for one- and two-$\psi$ words.
\end{proof}

\begin{rmk}
  The empty trace is the finite-rank scalar $\mathrm{Tr}_N(1)=N$, which changes
  with $N$ and fails to define a stable primitive generator. The stable
  symmetric algebra still has its ordinary unit; what is omitted is the empty
  trace as a generator of the connected primitive part. The class
  $\mathrm{Tr}(\psi)$ is a genuine stable odd primitive class. It is excluded
  from the Hamiltonian comparison because constants have been removed from the
  closed Hamiltonian algebra.
\end{rmk}

Varying
$$S=\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr)$$
with respect to $A$ gives the moment-map equation
$[\phi_1,\phi_2]=0$. In the reduced BV complex,
$$Q\psi=[\phi_1,\phi_2],\qquad Q\phi_1=Q\phi_2=0$$
on invariant trace functions.

\begin{constr}[Boundary evaluation of a closed Hamiltonian]\label{constr:boundary-evaluation}
  Let $f=\sum_{k,l}c_{k,l}z_1^kz_2^l\in\C[z_1,z_2]$. The brane replaces the
  two normal coordinates $z_1,z_2$ by the two adjoint scalar fields
  $\phi_1,\phi_2$. Choosing the ordered lift with all $\phi_1$'s to the left
  of all $\phi_2$'s gives the invariant function
  $$\widetilde\partial_{\mathrm{bb},N}(f)
    =\sum_{k,l}c_{k,l}\,\mathrm{Tr}(\phi_1^k\phi_2^l)
    \in\mc R_N^{GL_N}.$$
  Let
  $$H^0_{\mathrm{Ham}}(\mc R_N^{GL_N},Q)
    :=H^0(\mc R_N^{GL_N},Q)/\C\cdot\mathrm{Tr}(1)$$
  as a vector space, and as a Lie algebra for the Poisson bracket. This is not
  an associative quotient of the operator algebra by its unit. Constants give
  the scalar $c_{0,0}N$ and therefore vanish in this Hamiltonian quotient.
  Thus the construction descends to a linear map
  $$\partial_{\mathrm{bb},N}:\bar A\to
    H^0_{\mathrm{Ham}}(\mc R_N^{GL_N},Q),\qquad
    [f]\longmapsto \overline{\widetilde\partial_{\mathrm{bb},N}(f)}.$$
  Let $\mathsf W_{k,l}$ be the set of words in two letters containing $k$
  copies of the first letter and $l$ copies of the second. The first descendant
  is obtained by inserting one Koszul variable and summing over all ordered
  lifts:
  For $k+l>0$ the descendant part of the Hamiltonian comparison is
  $$\partial_{\mathrm{bb},N}^{(1)}(\delta_{k,l}[1])=\Psi_{k,l},\qquad
    \Psi_{k,l}:=\sum_{w\in\mathsf W_{k,l}}
      \mathrm{Tr}\bigl(\psi\,w(\phi_1,\phi_2)\bigr).$$
  The same formula at $(k,l)=(0,0)$ gives the decoupled scalar antifield
  $\mathrm{Tr}(\psi)$, which is excluded from the Hamiltonian pairing because
  constants have been removed from $\bar A$.
\end{constr}

\begin{lem}[First descendants are cycles]\label{lem:first-descendant-cycles}
  For every $k,l\geq0$, the symmetrised trace $\Psi_{k,l}$ satisfies
  $Q\Psi_{k,l}=0$.
\end{lem}

\begin{proof}
  Write $x=\phi_1$ and $y=\phi_2$. Since $x$ and $y$ are even and
  $Q\psi=[x,y]$, one has
  $$Q\Psi_{k,l}
    =\sum_{w\in\mathsf W_{k,l}}\mathrm{Tr}\bigl((xy-yx)w(x,y)\bigr).$$
  Group the resulting traces by cyclic word of multidegree $(k+1,l+1)$. The
  coefficient of a cyclic word in the positive sum is the number of cyclic
  adjacent occurrences of the block $xy$; the coefficient in the negative sum
  is the number of cyclic adjacent occurrences of the block $yx$. On a circle
  the number of transitions from an $x$-run to a $y$-run equals the number of
  transitions from a $y$-run to an $x$-run. The two grouped sums are therefore
  equal, so $Q\Psi_{k,l}=0$.
\end{proof}

\begin{prop}[Primitive one-antifield Koszul homology]\label{prop:one-psi-homology}
  Fix $k,l\geq0$. The middle homology of the primitive single-trace complex
  with one displayed $\psi$ and $k,l$ displayed $x,y$ letters is
  one-dimensional, generated by the class of $\Psi_{k,l}$. The nonconstant part
  relevant to the Hamiltonian comparison is the direct sum over $k+l>0$.
\end{prop}

\begin{proof}
  Write $x=\phi_1$ and $y=\phi_2$. Let $\mathsf W_{k,l}$ be the set of ordinary
  words with $k$ letters $x$ and $l$ letters $y$, and let
  $\mathsf N_{a,b}$ be the set of cyclic words with $a$ letters $x$ and $b$
  letters $y$. By Lemma~\ref{lem:stable-marked-traces}, primitive cyclic words
  are taken modulo the graded cyclic rule
  $$\mathrm{Tr}(ab)=(-1)^{|a||b|}\mathrm{Tr}(ba),\qquad
  |x|=|y|=0,\quad |\psi|=1.$$
  Graded cyclicity gives a unique representative $\mathrm{Tr}(\psi w)$ for
  every one-$\psi$ cyclic word. Thus the relevant one-$\psi$ chain group is
  $$C_1(k,l)=\C\{\mathsf W_{k,l}\}.$$
  The zero-$\psi$ target is
  $$C_0(k,l)=\C\{\mathsf N_{k+1,l+1}\},$$
  and the differential is the incidence map
  $$\partial_1(w)=[xyw]_{\mathrm{cyc}}-[yxw]_{\mathrm{cyc}}.$$

  The two-$\psi$ source is generated by traces $\mathrm{Tr}(\psi u\psi v)$
  with $u$ and $v$ ordinary words whose total bidegree is $(k-1,l-1)$; if
  $k=0$ or $l=0$ this source is zero. Since $\psi$ is odd, exchanging the two
  displayed $\psi$'s changes sign. Applying $Q\psi=xy-yx$ gives
  \begin{align*}
  \partial_2(u,v)
    &=Q\,\mathrm{Tr}(\psi u\psi v)\\
    &=\mathrm{Tr}\bigl(\psi vxyu-\psi vyxu-\psi uxyv+\psi uyxv\bigr),
  \end{align*}
  so, after removing the common front $\psi$,
  $$\partial_2(u,v)=vxyu-vyxu-uxyv+uyxv.$$
  A direct substitution shows $\partial_1\partial_2=0$.

  If $k=0$ or $l=0$, then $C_1(k,l)$ is spanned by $x^k$ or $y^l$,
  $\partial_1=0$, and $C_2(k,l)=0$. Hence the middle homology is already the
  line spanned by $\Psi_{k,l}$. Assume from now on that $k,l>0$.

  We compute the first homology of this finite complex. Form a graph
  $\Gamma_{k,l}$ whose vertices are the necklaces in $\mathsf N_{k+1,l+1}$ and
  whose oriented edges are the words $w\in\mathsf W_{k,l}$, with
  $$w:[yxw]_{\mathrm{cyc}}\longrightarrow[xyw]_{\mathrm{cyc}}.$$
  Then $\partial_1$ is the cellular boundary of this graph. For each pair
  $(u,v)$ as above attach the square whose oriented boundary is
  $vxyu-vyxu-uxyv+uyxv$. Denote the resulting two-complex by $X_{k,l}$.

  Equivalently, $X_{k,l}$ is the two-skeleton of the chip-moving state complex
  $Y_{k,l}$. The full complex $Y_{k,l}$ has an $r$-cell for $r$ mutually chosen
  chip moves on a cycle with $l+1$ oriented edges and $k+1$ indistinguishable
  chips, modulo cyclic relabelling of the edge labels. A vertex is a cyclic
  distribution of the chips among the vertices of this cycle, hence a necklace
  in $\mathsf N_{k+1,l+1}$. A one-cell moves one chosen chip across one oriented
  edge; cutting the cycle at this moving edge records exactly a word
  $w\in\mathsf W_{k,l}$, and its two endpoints are
  $[yxw]_{\mathrm{cyc}}$ and $[xyw]_{\mathrm{cyc}}$. A two-cell records two chip
  moves performed independently, and its oriented boundary is precisely
  $vxyu-vyxu-uxyv+uyxv$. Therefore the cellular chain complex of $Y_{k,l}$
  through degree two is exactly
  $$C_2(k,l)\longrightarrow C_1(k,l)\longrightarrow C_0(k,l),$$
  and the inclusion $X_{k,l}=Y_{k,l}^{(2)}\hookrightarrow Y_{k,l}$ induces an
  isomorphism on $H_1$, since cells of dimension at least three do not affect
  first homology.

  The homology of $Y_{k,l}$ is the homology of the cycle. For completeness we
  recall the elementary Abel-map argument. Before quotienting by cyclic
  relabelling, send a chip configuration to its Abel coordinate, the sum of the
  chip positions in $\R/(l+1)\Z$, and extend linearly over each cell. In the
  universal cover of the target circle, a fibre is described by weakly ordered
  lifted chip positions with fixed total sum; it is a convex polytope, subdivided
  by the same chip-crossing cells. Hence the Abel map is a cellular homotopy
  equivalence to $S^1$. The finite cyclic relabelling of the $y$-gaps is
  equivariant for this Abel map: it rotates the target circle, and every
  stabilizer acts affinely on a convex fibre, whose quotient is again
  contractible. Thus the quotient target is still a circle and the quotient
  complex $Y_{k,l}$ has the homology of $S^1$. Consequently
  $$H_1(X_{k,l};\C)\cong H_1(S^1;\C)\cong\C.$$

  Lemma~\ref{lem:first-descendant-cycles} identifies this representative as a
  cycle in the original trace complex. Its non-boundary property follows from
  the functional
  $$\epsilon\bigl(\mathrm{Tr}(\psi w)\bigr)=1,\qquad w\in\mathsf W_{k,l},$$
  kills every displayed two-$\psi$ boundary because each boundary has two
  positive and two negative summands, while
  $$\epsilon(\Psi_{k,l})=\binom{k+l}{k}\neq0.$$
  Thus the one-$\psi$ homology in bidegree $(k,l)$ is the one-dimensional line
  generated by $[\Psi_{k,l}]$.
\end{proof}

\begin{rmk}
  The script \texttt{scripts/check\_one\_psi\_homology.py} constructs the
  finite complex $C_2(k,l)\to C_1(k,l)\to C_0(k,l)$ over $\Q$ and verifies
  $\dim\ker\partial_1/\mathrm{im}\,\partial_2=1$ for $0\leq k,l\leq5$. It also
  checks the open Hamiltonian action of
  Proposition~\ref{prop:open-descendant-action} for exponents at most $3$, and
  checks the closed coadjoint Taylor-dual formula and the principal-part
  realization of Proposition~\ref{prop:principal-part-coadjoint} for exponents
  at most $5$.
  These checks verify the displayed finite models without adding assumptions.
\end{rmk}

\begin{cor}[Boundary pairing for cotangent generators]\label{cor:cotangent-boundary-pairing}
  Let $\delta_{k,l}\in\mathfrak h^\vee$ be the functional dual to the monomial
  $z_1^kz_2^l\in\bar A$. The assignment
  $$\delta_{k,l}[1]\longmapsto [\Psi_{k,l}]$$
  extends to an isomorphism from the shifted Taylor-dual space
  $\mathfrak h^\vee[1]$ to the nonconstant primitive one-$\psi$ brane homology.
\end{cor}

\begin{proof}
  The monomials $z_1^kz_2^l$ with $k+l>0$ form the polynomial basis of
  $\bar A$ and the topological basis of $\widehat{\mathfrak h}$; the
  $\delta_{k,l}$ form the continuous coefficient-dual basis. By
  Proposition~\ref{prop:one-psi-homology}, the primitive one-$\psi$ homology has
  one generator in each bidegree, namely $[\Psi_{k,l}]$. Discarding the scalar
  bidegree $(0,0)$ and sending the dual basis vector in every nonconstant
  bidegree to that generator gives a filtered vector-space isomorphism. This is
  the boundary pairing used in the PBW special fibre; the closed module
  structure remains coadjoint.
\end{proof}

\begin{lem}[Adjacent swaps]\label{lem:adjacent-swaps}
  In the invariant reduced BV cohomology,
  $$\mathrm{Tr}(u\phi_1\phi_2v)-\mathrm{Tr}(u\phi_2\phi_1v)$$
  is $Q$-exact for all words $u,v$.
\end{lem}

\begin{proof}
  By cyclicity of the trace,
  \begin{align*}
  Q\,\mathrm{Tr}(\psi vu)
    &=\mathrm{Tr}([\phi_1,\phi_2]vu)\\
    &=\mathrm{Tr}(\phi_1\phi_2vu-\phi_2\phi_1vu)\\
    &=\mathrm{Tr}(u\phi_1\phi_2v)-\mathrm{Tr}(u\phi_2\phi_1v).
  \end{align*}
\end{proof}

\begin{cor}[Matrix evaluation is commutative in cohomology]\label{cor:matrix-evaluation-well-defined}
  If two words in $\phi_1,\phi_2$ have the same numbers of $\phi_1$ and
  $\phi_2$, then their traces define the same class in the reduced BV
  cohomology. Consequently $\partial_{\mathrm{bb},N}(f)$ is determined by the
  commutative polynomial $f\in\C[z_1,z_2]$ and is independent of the chosen
  ordered lift.
\end{cor}

\begin{proof}
  Adjacent transpositions generate all reorderings of a finite word. Each
  adjacent transposition of the adjacent letters $\phi_1,\phi_2$ changes the
  trace by a $Q$-exact term by Lemma~\ref{lem:adjacent-swaps}; cyclicity moves
  the chosen adjacent pair into the displayed position of that lemma. Summing
  the resulting exact differences proves the claim.
\end{proof}

\begin{prop}[Stalk central multiplication]\label{prop:stalk-central-multiplication}
  Let
  $$A_N^{\mathrm{pt}}=(\mc R_N^{GL_N},Q)$$
  be the invariant reduced open BV algebra at a brane insertion point. For
  $f\in\C[z_1,z_2]$, set
  $$B_f=\widetilde\partial_{\mathrm{bb},N}(f)
    =\sum_{k,l}c_{k,l}\mathrm{Tr}(\phi_1^k\phi_2^l).$$
  Then $QB_f=0$. Regard $B_f$ as a Hochschild $0$-cochain; its associated
  central operation is multiplication
  $$L_{B_f}:A_N^{\mathrm{pt}}\to A_N^{\mathrm{pt}},\qquad
    a\longmapsto B_fa.$$
  This Hochschild $0$-cochain is closed. The same statement holds for
  multiplication by a closed one-antifield class $\Psi_{k,l}$. After projection to the
  Hamiltonian quotient and stabilization in $N$, the degree-zero classes satisfy
  $$\{B_f,B_g\}_{\mathrm{open}}=B_{\{f,g\}_{\bar A}}.$$
\end{prop}

\begin{proof}
  Since $Q\phi_1=Q\phi_2=0$, every $B_f$ is $Q$-closed. The algebra
  $A_N^{\mathrm{pt}}$ is graded-commutative, so the Hochschild differential of
  a $0$-cochain $b$ is
  $$d_{\mathrm{Hoch}}b(a)=Qb\,a+
    ba-(-1)^{|b||a|}ab.$$
  This vanishes for every closed graded-central element $b$. The classes
  $\Psi_{k,l}$ are closed by Lemma~\ref{lem:first-descendant-cycles} and are
  central for the same graded-commutative reason. Ordered-lift independence for
  $B_f$ is cohomological and is exactly
  Corollary~\ref{cor:matrix-evaluation-well-defined}. The Poisson identity is
  Theorem~\ref{thm:bulk-boundary}.
\end{proof}

Let $\bar A=\C[z_1,z_2]/\C\cdot1$. The removed constant corresponds on the
gauge side to the scalar $\mathrm{Tr}(1)=N$ and has zero Hamiltonian vector
field.

\begin{prop}[Connected brane Hamiltonian sector]\label{prop:brane-ops}
  In the stable large-$N$ open BV model, the connected Hamiltonian descendant
  sector freely generated by the nonempty primitive ghost-zero traces and the
  nonconstant primitive one-$\psi$ Koszul homology is
  $$\mc{O}^{\mathrm{cl}}_{\mathrm{brane},H}
    \cong \mathbf{S}\bigl(\bar A\oplus \bar A_{\mathrm{desc}}[1]\bigr).$$
  The class of $z_1^kz_2^l$ with $k+l>0$ corresponds to
  $\overline{\mathrm{Tr}(\phi_1^k\phi_2^l)}$. The corresponding descendant
  basis vector corresponds to the symmetrised trace with one $\psi$ and $k,l$
  copies of $\phi_1,\phi_2$.
\end{prop}

\begin{proof}
  Proposition~\ref{prop:stable-trace-invariants} gives the free commutative
  algebra on cyclic words.
  Lemma~\ref{lem:adjacent-swaps} identifies any two cyclic words with the same
  numbers of $\phi_1$ and $\phi_2$, because adjacent transpositions generate
  all reorderings. Thus the connected ghost-zero cyclic words reduce to the
  monomials $\overline{\mathrm{Tr}(\phi_1^k\phi_2^l)}$ with $k+l>0$.
  Proposition~\ref{prop:one-psi-homology} computes the primitive one-$\psi$
  homology in each multidegree; the nonconstant generators are $\Psi_{k,l}$ with
  $k+l>0$. Products of the connected ghost-zero primitive classes and these
  one-$\psi$ primitive classes give the free graded-commutative multi-trace
  algebra in the Hamiltonian sector.
  By definition of the Hamiltonian sector, single traces containing two or
  more occurrences of $\psi$ are excluded from this algebra.
\end{proof}

\begin{rmk}
  The word ``sector'' is literal. The calculation above presents the stable
  algebra generated by the primitive no-$\psi$ Hamiltonians and the nonconstant
  primitive one-$\psi$ homology generated by $\Psi_{k,l}$ for $k+l>0$. The full
  invariant Koszul homology in higher $\psi$-count lies outside this sector, as
  does the decoupled scalar class $\mathrm{Tr}(\psi)$.
\end{rmk}

\begin{prob}[Full primitive Koszul homology]\label{prob:full-psi-homology}
  Let
  $$A_{\psi}=\C\langle x,y,\psi\rangle,\qquad
    |x|=|y|=0,\quad |\psi|=1,$$
  with differential $d\psi=xy-yx$ and $dx=dy=0$. Put
  $$\mathrm{Cyc}(A_{\psi})=A_{\psi}/[A_{\psi},A_{\psi}]_{\mathrm{gr}},\qquad
    [uv]=(-1)^{|u||v|}[vu].$$
  Give $x,y,\psi$ weights
  $$\mathrm{wt}(x)=(1,0),\qquad \mathrm{wt}(y)=(0,1),\qquad
    \mathrm{wt}(\psi)=(1,1).$$
  For fixed $(R,S)$ define
  $$K^p_{R,S}=\C\{[w]_{\mathrm{cyc}}:
    \#\psi(w)=p,\ \#x(w)=R-p,\ \#y(w)=S-p\},$$
  with $0\leq p\leq\min(R,S)$. The differential is
  \begin{align*}
  \partial[w]
    =\sum_{i:a_i=\psi}(-1)^{\#\{\psi\text{ before }i\}}
    [&a_1\cdots a_{i-1}xy\,a_{i+1}\cdots a_n\\
     &-a_1\cdots a_{i-1}yx\,a_{i+1}\cdots a_n]_{\mathrm{cyc}}.
  \end{align*}
  Prove the primitive homology formula
  $$H_p(K_{R,S})\cong
    \begin{cases}
      \C\cdot[x^Ry^S],&p=0,\\
      \C\cdot[\Psi_{R-1,S-1}],&p=1,\ R,S\geq1,\\
      0,&p\geq2.
    \end{cases}$$
  Equivalently, prove that the primitive stable Koszul homology is
  $\C[x,y]\oplus\C[x,y]\theta$ with $|\theta|=1$ and
  $\mathrm{wt}(\theta)=(1,1)$.

  The required new ingredient is the all-$p$ orientation statement identifying
  this graded cyclic complex with the cellular chains of the chip-moving
  necklace state complex, together with the Abel-map proof that the relevant
  state complex has the homology of $S^1$. Proposition~\ref{prop:one-psi-homology}
  proves exactly the $p\leq2$ skeleton needed for the Hamiltonian sector. The
  complete theorem also requires the all-$\psi$ stable trace presentation and an
  exact computational check of the finite complex.
\end{prob}

\subsection{Operators in the closed Hamiltonian sector}\label{sec:grav-ops}

Let $\mathfrak h=\widehat{\mathfrak h}=\C[[z_1,z_2]]/\C\cdot1$ with the
projected Poisson bracket, and let $\mathfrak h^\vee$ be its continuous Taylor
dual. The
cotangent field is a coadjoint module, so the local Hamiltonian Lie algebra is
$$\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee[1].$$
For $f,g\in\mathfrak h$ and $\lambda,\mu\in\mathfrak h^\vee$, the brackets are
$$[f,g]=\{f,g\},\qquad [f,\eta_\lambda]=\eta_{\operatorname{ad}^{\vee}_f\lambda},
  \qquad [\eta_\lambda,\eta_\mu]=0,$$
where $(\operatorname{ad}^{\vee}_f\lambda)(g)=-\lambda(\{f,g\})$.
On polynomial monomials in the dense subalgebra $\bar A$ this reads
$$[z_1^kz_2^l,z_1^mz_2^n]
  =\overline{(kn-lm)z_1^{k+m-1}z_2^{l+n-1}},$$
where the bar means projection to $\bar A$; in particular the constant bracket
of $z_1$ and $z_2$ is zero in the reduced Hamiltonian Lie algebra.

\begin{lem}[Shifted coadjoint signs]\label{lem:shifted-coadjoint-signs}
  Let $\eta_\lambda$ denote the suspension of
  $\lambda\in\mathfrak h^\vee$ into $\mathfrak h^\vee[1]$. Since the
  Hamiltonians in $\mathfrak h$ are even,
  $$[f,\eta_\lambda]=\eta_{\operatorname{ad}^{\vee}_f\lambda},\qquad
    [\eta_\lambda,\eta_\mu]=0.$$
  Consequently the enveloping algebra relations involving two shifted
  coadjoint generators are odd-commutative:
  $$\eta_\lambda\eta_\mu+\eta_\mu\eta_\lambda=0.$$
\end{lem}

\begin{proof}
  The semidirect product bracket before shifting is the ordinary coadjoint
  action of the even Lie algebra $\mathfrak h$ on its continuous dual. Suspending
  the module raises the degree of every $\lambda$ by one. The mixed-bracket sign
  is $+1$ because $|f|=0$. The shifted module is
  abelian as a Lie ideal, so its bracket with itself is zero; in the associative
  enveloping algebra this zero Lie bracket gives
  $\eta_\lambda\eta_\mu-(-1)^{1\cdot1}\eta_\mu\eta_\lambda=0$.
\end{proof}

The kinematic BRST operator is
$$Q_0=d_{\R^2}+\bar\partial_{\C^2}.$$
The same jet contraction as in Lemma~\ref{lem:derivative-jets}, together with
the Dolbeault Poincare lemma in the formal local model, leaves precisely the
holomorphic Taylor coefficients. Thus the linear local coordinates are the
functionals
$$\partial_{z_1}^k\partial_{z_2}^l\alpha|_0,\qquad
  \partial_{z_1}^k\partial_{z_2}^l\beta|_0.$$
With the coefficient-dual convention fixed above, these are represented by
$(k!l!)^{-1}\partial_{z_1}^k\partial_{z_2}^l|_0$. Since zero-form components of
$\alpha$ and $\beta$ have negative field ghost numbers, the corresponding
linear functions have positive ghost numbers.

\begin{prop}[Closed local operators are continuous CE cochains]\label{prop:grav-ops}
  The classical local operators of the formal Hamiltonian cotangent BF sector are
  the continuous Chevalley-Eilenberg cochains
  $$\mc{O}^{\mathrm{cl}}_{\mathrm{grav}}
    \cong C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
    =\widehat{\mathbf{S}}\bigl(\mathfrak g^\vee_{\mathrm{cont}}[-1]\bigr),$$
  with CE differential dual to the Lie brackets above.
\end{prop}

\begin{proof}
  Work at the formal insertion point. The jet algebra of the fields is the
  completed free graded-commutative algebra on the Taylor coefficients of
  $\alpha$ and $\beta$. The kinematic differential
  $Q_0=d_{\R^2}+\bar\partial_{\C^2}$ contracts all positive real and
  anti-holomorphic jets: in the real directions the homotopy is
  $[d_{\R^2},\iota_{\partial_{x_i}}]=\partial_{x_i}$, and in the
  anti-holomorphic directions it is the formal Dolbeault Poincare homotopy.
  The $Q_0$-cohomology of the jet algebra is therefore generated by the
  holomorphic Taylor coefficients alone.

  The remaining $\alpha$-coefficients are Taylor Hamiltonians modulo constants,
  hence elements of $\mathfrak h=\widehat{\mathfrak h}$; degreewise polynomial
  coefficients form the dense subalgebra $\bar A$. The cotangent field $\beta$
  supplies the odd shifted continuous dual $\mathfrak h^\vee[1]$. Thus the
  linear space of residual local modes is
  $\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee[1]$.

  The nonlinear BRST differential is determined by the BV Hamiltonian
  $$S=\int\left\langle\beta,D\alpha+\frac12\{\alpha,\alpha\}\right\rangle.$$
  The linear part is exactly $Q_0$, already killed in cohomology. The quadratic
  term sends two Hamiltonian $\alpha$-modes $f,g$ to their reduced Poisson
  bracket $\{f,g\}$, and the action on the cotangent variable is the coadjoint
  action displayed above. The quadratic term has zero component with two
  cotangent inputs, so $[\eta_\lambda,\eta_\mu]=0$. Hence the residual BRST differential on
  functions is precisely the derivation dual to the Lie bracket on
  $\mathfrak g$, which is the Chevalley-Eilenberg differential. Continuity
  records the completion over polynomial degree.
\end{proof}

\subsection{Koszul Duality}

\begin{defn}
  For an augmented complete dg algebra $B$, its Koszul dual is
  $$B^!=\RHom_B(\C,\C)$$
  \cite{priddy}.
  We regard commutative Chevalley-Eilenberg cochains as $E_1$ algebras by
  restriction. All bar and cobar constructions below are taken in the category
  of complete filtered Tate vector spaces, with continuous maps. The
  completions are by symmetric or tensor length together with the coefficient
  topology coming from Taylor degree.
  For a Tate space $V$, the notation $V^\vee_{\mathrm{cont}}$ means the
  continuous dual with its dual Tate topology, $\widehat\otimes$ means the
  completed Tate tensor product, and
  $$\widehat{\mathbf S}^n(V)=(V^{\widehat\otimes n})_{\mathbb S_n}.$$
  Chevalley-Eilenberg chains below are direct sums in CE length with completed
  coefficients in each length; CE cochains, completed cobar algebras, and
  completed enveloping algebras are products in the corresponding length
  filtration.
\end{defn}

\begin{lem}[Tate CE chains, completed PBW, and Koszul duality]\label{lem:continuous-bar-cobar}
  Work in the symmetric monoidal category $\Cat{TateVec}$ of complete
  filtered Tate $\C$-vector spaces:
  $$V=\varprojlim_{w\in\N}V_{\leq w},\qquad V_{\leq w}\
    \text{finite-dimensional},\qquad
    F^w V=\Ker\bigl(V\to V_{\leq w-1}\bigr),$$
  with $\widehat\otimes$ the completed tensor product
  $V\widehat\otimes W=\varprojlim_w(V_{\leq w}\otimes W_{\leq w})$ and
  $V^\vee_{\mathrm{cont}}=\varinjlim_w V_{\leq w}^*$ the continuous
  dual. Admissible quasi-isomorphisms are the filtered
  quasi-isomorphisms, i.e.\ chain maps inducing quasi-isomorphisms on
  every quotient $V/F^wV$ and on the associated graded.

  Let $\mathfrak g$ be a Tate graded Lie algebra, conilpotent in the
  sense that the descending Lie powers $\mathfrak g^{(\geq m)}=
  [\mathfrak g,\mathfrak g^{(\geq m-1)}]$ satisfy
  $\bigcap_m\bigl(\mathfrak g^{(\geq m)}+F^w\mathfrak g\bigr)=
  F^w\mathfrak g$ for every $w$. Then:
  \begin{enumerate}
    \item For $V=\prod_d V_d$ with all $V_d$ finite-dimensional and
      $W=\bigoplus_d W_d$ with all $W_d$ finite-dimensional,
      $$(V\oplus W)^\vee_{\mathrm{cont}}=
        \bigoplus_d V_d^\vee\oplus\prod_d W_d^\vee,$$
      and the dualization $V\mapsto V^\vee_{\mathrm{cont}}$ is exact and
      continuous in the filtration $F^w$.
    \item The continuous Chevalley--Eilenberg cochains
      $$C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
        =\Hom_{\mathrm{cont}}\bigl(\widehat{\mathbf S}^c(\mathfrak g[1]),
        \C\bigr)$$
      identify with $\widehat{\mathbf S}_{\mathrm{Tate}}\bigl(
        \mathfrak g^\vee_{\mathrm{cont}}[-1]\bigr)$, and the
      coaugmentation filtration on the CE coalgebra
      $C_*^{\mathrm{CE}}(\mathfrak g)=\widehat{\mathbf S}^c(\mathfrak g[1])$
      is conilpotent in $\Cat{TateVec}$: every element of any finite
      Tate window lies in a finite power of the coaugmentation coideal.
    \item The continuous bar resolution of the augmentation
      $C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)\to\C$ has
      dual cobar algebra $\Omega C_*^{\mathrm{CE}}(\mathfrak g)$, and
      the canonical Lie bar--cobar map
      $$\Omega C_*^{\mathrm{CE}}(\mathfrak g)\longrightarrow
        \widehat U(\mathfrak g)$$
      is an admissible (filtered) quasi-isomorphism in $\Cat{TateVec}$.
    \item The PBW filtration on $\widehat U(\mathfrak g)$ by tensor
      length is complete and separated. Its associated graded is the
      completed symmetric algebra
      $$\mathrm{gr}_F^\bullet\widehat U(\mathfrak g)\cong
        \widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak g).$$
  \end{enumerate}
\end{lem}

\begin{proof}
  \emph{Item~(1).} A continuous functional on $V=\prod V_d$ depends on
  finitely many coordinates: the topology on $\C$ is discrete, so the
  kernel of any continuous map contains some $F^w V$. Therefore
  $V^\vee_{\mathrm{cont}}=\bigoplus_d V_d^*$. Conversely, a continuous
  functional on the discrete sum $W=\bigoplus W_d$ is given by an
  arbitrary product of degreewise functionals, hence
  $W^\vee_{\mathrm{cont}}=\prod_d W_d^*$. Direct sum of these gives the
  displayed formula. Exactness of dualization in $\Cat{TateVec}$ is
  preservation of finite limits; continuity in the Tate filtration is
  direct.

  \emph{Item~(2).} The completed CE coalgebra
  $\widehat{\mathbf S}^c(\mathfrak g[1])=\bigoplus_n
  \widehat{\mathbf S}^n(\mathfrak g[1])$ has coaugmentation coideal
  $\widehat{\mathbf S}^{\geq 1}(\mathfrak g[1])$. An element $x$ in the
  Tate window $V_{\leq w}$ projects to $\mathfrak g_{\leq w}$, whose
  finite-dimensional symmetric powers are conilpotent because the Lie
  bracket on $\mathfrak g_{\leq w}$ has finite descending central
  series in any finite-dimensional approximation. Pass to the inverse
  limit using the Tate-conilpotency hypothesis on $\mathfrak g$: the
  descending powers $(\widehat{\mathbf S}^c)^{(\geq m)}$ have empty
  Tate intersection modulo every finite filtration step. The displayed
  equality identifies cochains as continuous functionals on the CE
  coalgebra, using item~(1) windowwise.

  \emph{Item~(3).} Filter the CE coalgebra by symmetric coalgebra
  length and by Tate window. Project to a fixed window
  $\mathfrak g_{\leq w}$ and bound symmetric/tensor length to a fixed
  $n$. The resulting finite-dimensional diagram is the ordinary Lie
  bar--cobar comparison \cite{loday-vallette}: the bar resolution
  computes
  $\RHom_{C^\bullet_{\mathrm{CE}}(\mathfrak g_{\leq w},\leq n)}(\C,\C)$,
  and the cobar algebra maps to the universal enveloping algebra of
  the same window. These finite comparisons are compatible with
  enlargement of the Tate window and increase of the length cap: the
  enlargement-of-window map is the dual of the surjection
  $\mathfrak g\to\mathfrak g_{\leq w}$, and Lie-algebra surjections
  induce maps of universal enveloping algebras. Passing to the Tate
  limit and completing in tensor length gives the asserted filtered
  quasi-isomorphism in $\Cat{TateVec}$. The PBW filtration is,
  windowwise, the standard PBW filtration on $U(\mathfrak g_{\leq w})$,
  hence preserved under inverse limits.

  \emph{Item~(4).} Tensor length is a separated, descending filtration
  on $\widehat U(\mathfrak g)$ because the Lie relations
  $xy-(-1)^{|x||y|}yx-[x,y]=0$ have leading tensor-length term
  $xy-(-1)^{|x||y|}yx$ of length $2$ and lower-order term $-[x,y]$ of
  length $1$; so the associated graded retains only the symmetric
  (length-fixed) part. Completeness is clear from the Tate
  construction. The associated graded is therefore the completed
  symmetric algebra
  $\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak g)$.
\end{proof}

\begin{rmk}
  Conilpotency in item~(2) is automatic for the Hamiltonian case used
  in \ref{thm:open-closed-derived-center}: the reduced Hamiltonian Lie
  algebra $\mathfrak h=(z_1,z_2)\C[[z_1,z_2]]$ of the formal symplectic
  disk satisfies
  $\mathfrak h^{(\geq m)}\cap\mathfrak h_{\leq w}=0$ for $m>w-1$, since
  the bracket strictly lowers Taylor degree. The general hypothesis is
  named here so that the lemma applies to any pro-finite-dimensional
  Lie algebra of bounded-below filtration. The earlier explicit
  product/direct-sum Tate convention of Beilinson--Feigin--Mazur
  \cite{beilinson-feigin-mazur} is recovered as a special case: take
  $\mathfrak g=\bigl(\prod P_d\bigr)\oplus\bigl(\bigoplus Q_d\bigr)$
  with the bracket bilinear in the displayed pieces.
\end{rmk}

\begin{lem}[Linear Poisson Schouten differential]\label{lem:linear-poisson-schouten}
  Let $\mathfrak h$ be a pro-finite-dimensional Lie algebra in
  $\Cat{TateVec}$. The completed symmetric algebra
  $\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)$ is naturally a
  Poisson algebra with Kirillov--Kostant--Souriau bracket
  $\{O_I,O_J\}_\partial=O_{[H_I,H_J]}=C^K_{IJ}\,O_K$ on a chosen
  homogeneous basis $\{H_I\}$ of $\mathfrak h$, where
  $O_I\in\mathfrak h^*$ is the linear coordinate. The associated
  Poisson bivector is the linear bivector
  $$\pi_\partial=\tfrac12\,C^K_{IJ}\,O_K\,\theta^I\wedge\theta^J,
    \qquad \theta^I=\partial/\partial O_I\in\mathrm{Der}\bigl(
    \widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr),$$
  and the Lichnerowicz/Schouten differential
  $d_\pi=[\pi_\partial,-]_S$ on
  $$\mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr)=
    \widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\widehat\otimes
    \widehat\Lambda(\theta^I)$$
  acts on generators by
  $$d_\pi\theta^K=-\tfrac12\,C^K_{IJ}\,\theta^I\theta^J,\qquad
    d_\pi O_K=C^L_{KJ}\,O_L\,\theta^J.$$
\end{lem}

\begin{proof}
  Direct calculation. The Schouten Leibniz rule with
  $[\theta^I,O_J]_S=\delta^I_J$, $[\theta^I,\theta^J]_S=0$,
  $[O_I,O_J]_S=0$ gives
  \begin{align*}
    [\pi_\partial,O_K]_S
    &=\tfrac12 C^L_{IJ}\,O_L\,[\theta^I\theta^J,O_K]_S\\
    &=\tfrac12 C^L_{IJ}\,O_L\,
      \bigl(\delta^I_K\theta^J-\delta^J_K\theta^I\bigr)\\
    &=\tfrac12\bigl(C^L_{KJ}-C^L_{JK}\bigr)O_L\theta^J
     =C^L_{KJ}O_L\theta^J,
  \end{align*}
  using the antisymmetry $C^L_{IJ}=-C^L_{JI}$ in the lower indices.
  For $[\pi_\partial,\theta^K]_S$, the Schouten bracket with $\theta^K$
  uses $[\theta^I\theta^J,\theta^K]_S=0$ on the bivector factor and
  $[O_L,\theta^K]_S=-\delta^K_L$; the result is
  $-\tfrac12 C^K_{IJ}\theta^I\theta^J$.
\end{proof}

\begin{prop}[Koszul dual of continuous CE cochains]\label{prop:ce-koszul}
  Let $\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee[1]$ be the completed
  graded Lie algebra above, and let
  $$B=C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
    =\widehat{\mathbf{S}}\bigl(\mathfrak g^\vee_{\mathrm{cont}}[-1]\bigr).$$
  Then
  $$B^!\simeq \widehat{U(\mathfrak g)},$$
  the completed graded universal enveloping algebra.
\end{prop}

\begin{proof}
  Put
  $$H_d=\operatorname{Span}\{z_1^az_2^b:a+b=d\},\qquad
    \mathfrak h=\prod_{d\geq1}H_d,\qquad
    \mathfrak h^\vee_{\mathrm{cont}}=\bigoplus_{d\geq1}H_d^\vee.$$
  Thus
  $$\mathfrak g=\left(\prod_{d\geq1}H_d\right)
    \ltimes\left(\bigoplus_{d\geq1}H_d^\vee\right)[1]$$
  is a Tate Lie algebra. The bracket is degreewise finite:
  $$\{H_p,H_q\}\subset H_{p+q-2},$$
  with the degree-zero summand projected to zero. Thus the degree-$r$
  coefficient of $\{f,g\}$ depends only on the finitely many pairs
  $p+q=r+2$. For the coadjoint action, if $f\in H_p$ and
  $\lambda\in H_q^\vee$, then
  $$\operatorname{ad}^{\vee}_f\lambda\in H_{q-p+2}^\vee$$
  when $q-p+2\geq1$, and it is zero otherwise. Finite-support Taylor duals
  remain finite-support: for fixed $\lambda\in H_q^\vee$ only the Hamiltonian
  degrees $p\leq q+1$ can act nontrivially, and for a finite direct-sum support
  in $\mathfrak h^\vee$ the union of those contributing $p$ is finite. Thus the
  product/direct-sum coefficient-finiteness hypotheses of
  Lemma~\ref{lem:continuous-bar-cobar} hold. The abelian bracket on
  $\mathfrak h^\vee[1]$ is trivial. The Taylor coefficient topology is
  independent of the PBW/order filtration used for the Rees algebra below.

  Let
  $$C_*^{\mathrm{CE}}(\mathfrak g)
    =\bigoplus_{n\geq0}\widehat{\mathbf S}^n(\mathfrak g[1])$$
  be the coefficient-completed, length-direct-sum Chevalley-Eilenberg
  coalgebra, with coderivation determined by the bracket of $\mathfrak g$. By
  definition
  $$B=\Hom_{\mathrm{cont}}\bigl(C_*^{\mathrm{CE}}(\mathfrak g),\C\bigr).$$
  The Chevalley-Eilenberg coalgebra is conilpotent for symmetric length. The
  augmentation $B\to\C$ has the continuous bar resolution in the category of
  complete filtered Tate spaces, and
  Lemma~\ref{lem:continuous-bar-cobar} identifies
  $$\RHom_B(\C,\C)\simeq
    \widehat{\Omega}\,C_*^{\mathrm{CE}}(\mathfrak g),$$
  the completed cobar algebra of the CE coalgebra. The completed Lie bar-cobar
  comparison in the lemma identifies this cobar algebra with the completed
  associative algebra generated by $\mathfrak g$ modulo the closed graded Lie
  relations; this is $\widehat{U(\mathfrak g)}$.

  Thus, for the generators $f,g\in\mathfrak h$ and
  $\eta_\lambda,\eta_\mu\in\mathfrak h^\vee[1]$, the completed enveloping
  algebra has relations
  \begin{align*}
    fg-gf&=\{f,g\},\\
    f\eta_\lambda-\eta_\lambda f&=\eta_{\operatorname{ad}^{\vee}_f\lambda},\\
    \eta_\lambda\eta_\mu+\eta_\mu\eta_\lambda&=0.
  \end{align*}
\end{proof}

For comparison with the classical brane algebra introduce the completed
PBW/order Rees enveloping algebra
$$U_{\hbar}(\mathfrak g)
  =\widehat T(\mathfrak g)[[\hbar]]\Big/
  \overline{\left\langle
  xy-(-1)^{|x||y|}yx-\hbar[x,y]\right\rangle},$$
where the closure is for tensor length and the Tate coefficient topology.
This Rees parameter records word length in the enveloping algebra and is
independent of Taylor degree. At $\hbar=0$ one obtains the completed PBW special
fibre
$$U_{\hbar}(\mathfrak g)/(\hbar)\cong
  \widehat{\mathbf{S}}(\mathfrak g)
  =\widehat{\mathbf{S}}\bigl(\widehat{\mathfrak h}\oplus\mathfrak h^\vee[1]\bigr).$$
After choosing the monomial-dual Taylor basis
$\mathfrak h^\vee\cong\bar A_{\mathrm{desc}}$, the degreewise polynomial
subalgebra $\mathbf{S}(\bar A\oplus\mathfrak h^\vee[1])$ is the stable classical
brane Hamiltonian descendant algebra of Proposition~\ref{prop:brane-ops}. Thus
the degreewise polynomial part of the PBW associated graded of the closed
Koszul dual is the stable classical brane Hamiltonian descendant algebra. The
interacting closed Hamiltonian bracket deforms the closed special fibre to
$\widehat{U(\mathfrak g)}$; on the brane side the deformation checked here is
the degree-zero Hamiltonian trace bracket below.

\subsubsection{First-order corrections, order hbar one}

Under the Koszul duality correspondence we have
$$z_1^kz_2^l \leftrightarrow
  \overline{\mathrm{Tr}(\phi_1^k\phi_2^l)}.$$
The reduced Poisson bracket on the gravity side is:
$$\{z_1^kz_2^l,\, z_1^mz_2^n\}_{\bar A}
  =\overline{(kn - lm)\,z_1^{k+m-1}z_2^{l+n-1}}.$$
If an exponent in the displayed monomial is negative then the coefficient
$kn-lm$ is already zero; if the displayed monomial is constant, its class in
$\bar A$ is zero.
The matching bracket on the open side is the canonical bracket induced by the
first-order kinetic term $\int\mathrm{Tr}(\phi_1\,d\phi_2)$, with the sign
convention $\iota_{X_f}\omega=-df$ fixed in the AKSZ remark above:
$$\{(\phi_1)^i{}_j,(\phi_2)^k{}_l\}
  =\delta^i_l\delta^k_j,\qquad
  \{(\phi_1)^i{}_j,(\phi_1)^k{}_l\}=0=\{(\phi_2)^i{}_j,(\phi_2)^k{}_l\}.$$

\begin{lem}[Hamiltonian trace bracket]\label{lem:trace-bracket-descends}
  The canonical matrix Poisson bracket descends to the invariant reduced BV
  cohomology and then to the Hamiltonian Lie quotient by constant trace
  classes.
\end{lem}

\begin{proof}
  For $\epsilon\in\lie{gl}_N$, the component
  $\mu_\epsilon=-\mathrm{Tr}(\epsilon[\phi_1,\phi_2])$ of the moment map
  generates the infinitesimal conjugation action, with the sign fixed by the
  convention for the bracket. Hence $\{F,\mu_\epsilon\}=0$ for every invariant
  function $F$. If $I_\mu$ is the ideal generated by all $\mu_\epsilon$, then
  $\{F,\mu_\epsilon K\}=\mu_\epsilon\{F,K\}$ lies again in $I_\mu$. Therefore
  the bracket of invariant functions descends to
  $(\mc R_N/I_\mu)^{GL_N}$, equivalently to the degree-zero reduced BV
  cohomology. The central line $\C\cdot\mathrm{Tr}(1)$ is central for this Lie
  bracket, so the Hamiltonian vector-space quotient by constants is compatible
  with the bracket. No associative quotient by the unit is taken.
\end{proof}

\begin{prop}[First-order trace bracket]\label{prop:first-order-bracket}
  In the stable connected Hamiltonian trace cohomology,
  $$\{\overline{\mathrm{Tr}(\phi_1^k\phi_2^l)},
      \overline{\mathrm{Tr}(\phi_1^m\phi_2^n)}\}
    =\overline{(kn-lm)\mathrm{Tr}
      (\phi_1^{k+m-1}\phi_2^{l+n-1})}.$$
\end{prop}

\begin{proof}
  Write $F_{k,l}=\mathrm{Tr}(\phi_1^k\phi_2^l)$. The matrix Poisson bracket
  induced by
  $$\{(\phi_1)^i{}_j,(\phi_2)^k{}_l\}=\delta^i_l\delta^k_j$$
  is
  $$\{F,G\}=\mathrm{Tr}\left(
      \frac{\partial F}{\partial\phi_1}\frac{\partial G}{\partial\phi_2}
      -\frac{\partial F}{\partial\phi_2}\frac{\partial G}{\partial\phi_1}
    \right),$$
  where the derivatives are cyclic matrix derivatives. Varying one occurrence
  at a time gives
  \begin{align*}
  \frac{\partial F_{k,l}}{\partial\phi_1}
    &=\sum_{a=0}^{k-1}\phi_1^{k-1-a}\phi_2^l\phi_1^a,\\
  \frac{\partial F_{k,l}}{\partial\phi_2}
    &=\sum_{b=0}^{l-1}\phi_2^{l-1-b}\phi_1^k\phi_2^b.
  \end{align*}
  Therefore the first summand in the bracket is a sum of $kn$ traces, each
  obtained by removing one $\phi_1$ from the first word and one $\phi_2$ from
  the second word. The second summand is a sum of $lm$ traces obtained by
  removing one $\phi_2$ from the first word and one $\phi_1$ from the second.
  Every trace appearing in either nonzero sum has multidegree
  $(k+m-1,l+n-1)$. Lemma~\ref{lem:adjacent-swaps} identifies all cyclic words
  with this multidegree in reduced BRST cohomology. The coefficient is
  therefore $kn-lm$, and the common class is
  $\overline{\mathrm{Tr}(\phi_1^{k+m-1}\phi_2^{l+n-1})}$. When the common word
  has multidegree $(0,0)$, this class is the scalar trace and is zero in the
  Hamiltonian quotient by constants.
\end{proof}

\begin{prop}[Open action on primitive descendants]\label{prop:open-descendant-action}
  Let
  $$\widetilde\Psi_{a,b}
    =\binom{a+b}{a}^{-1}\Psi_{a,b}$$
  be the averaged primitive one-$\psi$ class. In the stable primitive one-$\psi$
  homology,
  $$\{\overline{\mathrm{Tr}(\phi_1^p\phi_2^q)},\widetilde\Psi_{a,b}\}
    =(pb-qa)\,\widetilde\Psi_{a+p-1,b+q-1},$$
  with the convention that a term with a negative exponent is zero. Thus the
  unreduced polynomial descendant classes carry the adjoint polynomial
  Hamiltonian action. The Hamiltonian descendant sector is the quotient by the
  scalar line $\C\widetilde\Psi_{0,0}$, so the displayed action is projected
  further by killing the scalar target.
\end{prop}

\begin{proof}
  Put $x=\phi_1$ and $y=\phi_2$. The cyclic derivatives of
  $F_{p,q}=\mathrm{Tr}(x^p y^q)$ are
  $$\frac{\partial F_{p,q}}{\partial x}
    =\sum_{i=0}^{p-1}x^{p-1-i}y^qx^i,\qquad
    \frac{\partial F_{p,q}}{\partial y}
    =\sum_{j=0}^{q-1}y^{q-1-j}x^py^j.$$
  For a one-$\psi$ cyclic word $\mathrm{Tr}(\psi w)$ of bidegree $(a,b)$,
  differentiating with respect to $y$ gives one summand for each of the $b$
  occurrences of $y$ in $w$, and differentiating with respect to $x$ gives one
  summand for each of the $a$ occurrences of $x$. Multiplying by the displayed
  cyclic derivatives of $F_{p,q}$ therefore produces $pb$ positive one-$\psi$
  words and $qa$ negative one-$\psi$ words for each $w\in\mathsf W_{a,b}$, all
  of total bidegree $(a+p-1,b+q-1)$.

  The bracket is a cycle because $F_{p,q}$ is invariant, hence
  $\{F_{p,q},\mu_\epsilon\}=0$ for every moment-map component
  $\mu_\epsilon=-\mathrm{Tr}(\epsilon[x,y])$. Equivalently, the Hamiltonian
  vector field of $F_{p,q}$ preserves the Koszul differential
  $Q\psi=[x,y]$ and acts on Koszul homology. By
  Proposition~\ref{prop:one-psi-homology}, the target primitive one-$\psi$
  homology in that bidegree is one-dimensional. The functional
  $\epsilon(\mathrm{Tr}(\psi w))=1$ detects its coefficient. Since
  $\epsilon(\widetilde\Psi_{a,b})=1$, the averaged input gives
  $$\epsilon\bigl(\{F_{p,q},\widetilde\Psi_{a,b}\}\bigr)=pb-qa.$$
  Also $\epsilon(\widetilde\Psi_{a+p-1,b+q-1})=1$. Hence the displayed formula
  follows. If the target bidegree is $(0,0)$, the same formula is still the
  unreduced primitive one-$\psi$ action; the Hamiltonian descendant quotient
  sends that scalar class to zero.
\end{proof}

\begin{cor}[Descendant action and coadjoint action: structural separation]\label{cor:descendant-coadjoint-difference}
  Under the boundary pairing
  $\delta_{a,b}[1]\mapsto[\Psi_{a,b}]$ of
  Corollary~\ref{cor:cotangent-boundary-pairing}, the open Hamiltonian
  descendant action on the polynomial $\Psi_{a,b}$-basis is the
  symmetric raising action
  $$F_{p,q}:\widetilde\Psi_{a,b}\longmapsto
    (pb-qa)\,\widetilde\Psi_{a+p-1,b+q-1},$$
  while the closed coadjoint action on the principal-part basis
  $\rho_{a,b}\leftrightarrow\delta_{a,b}\in\mathfrak h^\vee_{\mathrm{cont}}$
  is the lowering action
  $$\operatorname{ad}^{\vee}_{z_1^pz_2^q}\delta_{a,b}
    =-(pb-qa+p-q)\,\delta_{a-p+1,b-q+1},$$
  with negative-index targets zero. The two actions agree only on the
  trivial Hamiltonian $p=q=0$. The deformation quantisation of the
  cotangent factor sees the second action; the special-fibre PBW
  symmetric algebra sees the first. The structural reason is the PBW
  versus deformation interpolation of
  Theorem~\ref{thm:pbw-vs-deformation} below: the
  $\widetilde\Psi_{a,b}$ and the $\rho_{a,b}$ are two different bases of
  the same $\mathfrak g$-module, the special-fibre PBW representative
  and the deformation-compatible coadjoint representative respectively.
\end{cor}

\begin{proof}
  Proposition~\ref{prop:open-descendant-action} gives the symmetric
  raising formula on $\widetilde\Psi_{a,b}$. The coadjoint action is
  dual to the Poisson bracket: for $f=z_1^pz_2^q$ and the Taylor-dual
  basis vector $\delta_{a,b}$,
  $$(\operatorname{ad}^{\vee}_f\delta_{a,b})(z_1^mz_2^n)
    =-\delta_{a,b}\bigl((pn-qm)z_1^{p+m-1}z_2^{q+n-1}\bigr),$$
  giving the displayed lowering formula. For example, $z_1$ acts on
  open descendants by
  $\widetilde\Psi_{a,b}\mapsto b\,\widetilde\Psi_{a,b-1}$, whereas it
  acts coadjointly by $\delta_{a,b}\mapsto-(b+1)\,\delta_{a,b+1}$. The
  scalar edge
  $\{\,\mathrm{Tr}(\phi_1),\widetilde\Psi_{0,1}\,\}=\Psi_{0,0}$ is
  removed with the scalar descendant. The two formulas have opposite
  index shift directions and differ by
  $-(pb-qa+p-q)\rho_{a-p+1,b-q+1}-(pb-qa)\rho_{a+p-1,b+q-1}$
  pulled back through the basis identification
  $\rho\leftrightarrow\delta\leftrightarrow\Psi$, which is non-zero
  unless both targets vanish identically; this happens exactly on the
  trivial $p=q=0$ action. The corollary uses
  Corollary~\ref{cor:cotangent-boundary-pairing} for the PBW
  special-fibre product identification, and
  Theorem~\ref{thm:principal-part-coadjoint-uniqueness} for the
  coadjoint half of the comparison. The descendant deformation match
  is supplied by the Laurent / distributional principal-part
  realization of
  Theorem~\ref{prop:principal-part-coadjoint} together with the
  interpolation of Theorem~\ref{thm:pbw-vs-deformation}.
\end{proof}

The reader who has come this far has met three different things called
``local'' on the brane line $\R$, and we keep them apart once and for all
before identifying the coadjoint module on the principal-part side.

\begin{lem}[Three notions of locality]\label{lem:three-notions-of-locality}
  On the brane line $\R$ with formal holomorphic transverse coordinates
  $z_1,z_2$ at the brane point $p\in\C^2$, the following three notions of
  locality are independent.
  \begin{enumerate}
    \item \emph{Support locality}\,\textemdash\,distributional support on the
      brane: a section $T\otimes m$ of $\mathcal D'_c(I)\,\widehat\otimes\,M$
      has support locality whenever $\mathrm{supp}\,T\subset I\subset\R$.
    \item \emph{Topological locality}\,\textemdash\,locally constant in the
      $\R$-direction up to $Q$-exact translations: every section is
      identified with its translate by a parameter on $\R$ modulo the open
      BV differential $Q_{\mathrm{open}}$.
    \item \emph{Formal holomorphic locality}\,\textemdash\,polynomial, or
      Taylor-series, dependence on the transverse coordinates $z_1,z_2$.
  \end{enumerate}
  The polynomial trace observables
  $O_f(a)=\int_\R a(t)\,
   \overline{\mathrm{Tr}\,f(\phi_1(t),\phi_2(t))}\,dt$ have all three. The
  shifted cotangent currents $\Theta_\rho(B)$ of
  Construction~\ref{constr:boundary-local-dual-principal-parts} have $(1)$
  and $(2)$ but not $(3)$: they are momentum modes attached to the brane
  and live in the principal-part complement
  $\operatorname{Ann}(\C\cdot1)$ of the polynomial Taylor algebra.
\end{lem}

\begin{proof}
  Independence is a category-theoretic statement: a polynomial in $z_1,z_2$
  with point support is constant in $\R$, so $(1)$ does not imply $(3)$;
  a delta-current at one point of $\R$ has compact support but only trivial
  $Q$-exact translation, so $(1)$ does not imply $(2)$. The cotangent
  currents $\Theta_\rho(B)$ are smooth or distributional sections of the
  line $\R$ (hence $(1)$) and translation-invariant up to
  $Q_{\mathrm{open}}$-exact cocycles (hence $(2)$); their transverse
  content $\rho\in\mc P$ is a Laurent two-form supported at the
  principal-part divisor, that is, in the complement of the polynomial
  algebra in the Laurent algebra (hence not $(3)$).
\end{proof}

\begin{rmk}\label{rmk:locality-canonical-quantization}
  In canonical quantization of a constrained system, the configuration
  variables are locally polynomial in spatial coordinates and the conjugate
  momenta are dual distributions. This is exactly the separation
  Lemma~\ref{lem:three-notions-of-locality} records: configuration
  observables on a brane have formal holomorphic locality $(3)$, and
  momentum observables have only $(1)$ and $(2)$. The principal-part
  sector is the algebraic image of this separation in the BCOV Hamiltonian
  model.
\end{rmk}

\begin{prop}[Principal-part realization of the coadjoint module]\label{prop:principal-part-coadjoint}
  Let
  $$\mc P=\bigoplus_{\substack{a,b\geq0\\a+b>0}}
    \C\,\rho_{a,b},\qquad
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2,$$
  with residue pairing
  $$\langle \rho_{a,b},z_1^mz_2^n\rangle
    =\operatorname{Res}_{z_1=z_2=0}
      z_1^{m-a-1}z_2^{n-b-1}\,dz_1dz_2
    =\delta_{a,m}\delta_{b,n}.$$
  Let $\pi_{\mathrm{pp}}$ denote projection of Laurent two-forms to the span of
  the principal parts $\rho_{a,b}$. The action
  $$f\cdot\rho=\pi_{\mathrm{pp}}\bigl(\{f,\rho\}\bigr)$$
  identifies $\mc P$ with the continuous coadjoint module
  $\mathfrak h^\vee_{\mathrm{cont}}$. On monomials,
  $$z_1^pz_2^q\cdot\rho_{a,b}
    =-(pb-qa+p-q)\rho_{a-p+1,b-q+1},$$
  with the convention that a term with a negative index is zero.
\end{prop}

\begin{proof}
  The residue pairing identifies $\rho_{a,b}$ with the Taylor-dual functional
  $\delta_{a,b}$. Hamiltonian vector fields preserve the holomorphic volume
  form $dz_1dz_2$, so integration by parts for the residue pairing gives
  $$\langle \{f,\rho\},g\rangle=-\langle\rho,\{f,g\}\rangle.$$
  Hence the Laurent principal-part action realizes the coadjoint action.
  Directly, for $f=z_1^pz_2^q$ and
  $\rho_{a,b}=z_1^{-a-1}z_2^{-b-1}dz_1dz_2$,
  \begin{align*}
  \{f,z_1^{-a-1}z_2^{-b-1}\}
    &=p z_1^{p-1}z_2^q\,(-(b+1))z_1^{-a-1}z_2^{-b-2}\\
    &\quad
      -q z_1^pz_2^{q-1}\,(-(a+1))z_1^{-a-2}z_2^{-b-1}\\
    &=-(pb-qa+p-q)z_1^{p-a-2}z_2^{q-b-2}.
  \end{align*}
  Since
  $z_1^{p-a-2}z_2^{q-b-2}\,dz_1dz_2
    =\rho_{a-p+1,b-q+1}$ when both indices are nonnegative, principal-part
  projection gives the displayed formula.
\end{proof}

The existence of the principal-part identification just established is
strengthened by two rigidity statements: the residue pairing is canonical
up to a single nonzero scalar, and the resulting coadjoint isomorphism
$\mc P\cong\mathfrak h^\vee_{\mathrm{cont}}$ is the unique continuous
$\mathfrak h$-equivariant isomorphism modulo that scalar.

\begin{thm}[Canonical residue pairing]\label{thm:canonical-residue-pairing}
  Up to a nonzero scalar, the residue pairing
  $$\langle\,\cdot\,,\,\cdot\,\rangle:
    \mc P\times\C[[z_1,z_2]]\longrightarrow\C,\qquad
    \langle\rho_{a,b},z_1^mz_2^n\rangle=\delta_{a,m}\delta_{b,n},$$
  is the unique non-degenerate continuous $\mathfrak h$-equivariant
  pairing graded of total degree zero with the property that $\rho_{0,0}$
  pairs to zero with the constant $1\in\C[[z_1,z_2]]$.
\end{thm}

\begin{proof}
  \emph{Existence.} The residue pairing is non-degenerate by the displayed
  Kronecker relation; it is continuous because $\mc P$ is graded discrete
  and $\C[[z_1,z_2]]$ carries the Taylor filtration; equivariance is
  integration by parts for the Poisson bracket, since Hamiltonian vector
  fields preserve the holomorphic two-form $dz_1dz_2$:
  $$\langle\{f,\rho\},g\rangle
    =\operatorname{Res}(\{f,\rho\}g)
    =-\operatorname{Res}(\rho\,\{f,g\})
    =-\langle\rho,\{f,g\}\rangle.$$

  \emph{Uniqueness.} Let $\beta:\mc P\times\C[[z_1,z_2]]\to\C$ be a second
  pairing satisfying the same conditions, and write
  $\beta_{a,b;m,n}=\beta(\rho_{a,b},z_1^mz_2^n)$. Since $\beta$ is graded
  of total degree zero, $\beta_{a,b;m,n}=0$ unless $a+b=m+n$.

  \emph{Diagonal weight constraint.} The Hamiltonian $z_1z_2$ acts
  diagonally on monomials by
  $\{z_1z_2,z_1^mz_2^n\}=(n-m)z_1^mz_2^n$. Direct Poisson computation on
  principal parts uses the Hamiltonian vector field
  $X_{z_1z_2}=z_2\,\partial_{z_2}-z_1\,\partial_{z_1}$
  (with $X_f=(\partial_{z_1}f)\partial_{z_2}-(\partial_{z_2}f)\partial_{z_1}$),
  giving
  $X_{z_1z_2}(z_1^{-a-1}z_2^{-b-1})=(a-b)\,z_1^{-a-1}z_2^{-b-1}$, so
  $\{z_1z_2,\rho_{a,b}\}=(a-b)\rho_{a,b}=-(b-a)\rho_{a,b}$. Equivariance
  $\beta(\{z_1z_2,\rho_{a,b}\},z_1^mz_2^n)
   =-\beta(\rho_{a,b},\{z_1z_2,z_1^mz_2^n\})$ gives
  $-(b-a)\beta_{a,b;m,n}=-(n-m)\beta_{a,b;m,n}$,
  hence $\beta_{a,b;m,n}=0$ unless $a-b=m-n$. Combined with the weight
  constraint $a+b=m+n$, this gives $\beta_{a,b;m,n}=0$ unless
  $(a,b)=(m,n)$. So $\beta$ is diagonal in the residue basis:
  $\beta_{a,b;m,n}=c_{a,b}\,\delta_{a,m}\delta_{b,n}$ for some scalars
  $c_{a,b}\in\C$.

  \emph{Coefficients are constant.} The Hamiltonian generator $f=z_1$ has
  $X_{z_1}=\partial_{z_2}$, so $\{z_1,z_1^mz_2^n\}=n\,z_1^mz_2^{n-1}$ and
  a direct Poisson computation gives
  $\{z_1,\rho_{a,b}\}=-(b+1)\rho_{a,b+1}$. Equivariance reads
  $\beta(\{z_1,\rho_{a,b}\},z_1^mz_2^n)
   =-\beta(\rho_{a,b},\{z_1,z_1^mz_2^n\})$, i.e.,
  $-(b+1)\beta_{a,b+1;m,n}=-n\,\beta_{a,b;m,n-1}$.
  Both sides vanish identically unless the diagonality condition is met
  on each pair. The right-hand side is non-zero only if $(a,b)=(m,n-1)$,
  i.e., $m=a$, $n=b+1$. The left-hand side is non-zero only if
  $(a,b+1)=(m,n)$, i.e., $m=a$, $n=b+1$. Both indices coincide, and we
  obtain $(b+1)\,c_{a,b+1}=(b+1)\,c_{a,b}$, hence $c_{a,b+1}=c_{a,b}$ for
  all $b\ge0$ with $a+b+1\ge1$. Symmetrically from $f=z_2$ (using
  $X_{z_2}=-\partial_{z_1}$, so
  $\{z_2,z_1^mz_2^n\}=-m\,z_1^{m-1}z_2^n$ and
  $\{z_2,\rho_{a,b}\}=(a+1)\rho_{a+1,b}$) we get $c_{a+1,b}=c_{a,b}$ for
  all $a\ge0$. Connecting these chains, all $c_{a,b}$ for $a+b\ge1$ equal
  a single constant $c\in\C$. Non-degeneracy forces $c\neq0$.

  Therefore $\beta=c\,\langle\,\cdot\,,\,\cdot\,\rangle$ is the residue
  pairing scaled by $c$. The condition $\beta(\rho_{0,0},1)=0$ holds
  vacuously since $\rho_{0,0}\notin\mc P$.
\end{proof}

\begin{rmk}\label{rmk:residue-pairing-schur}
  Theorem~\ref{thm:canonical-residue-pairing} is a Schur-type rigidity
  statement on the cofree cocommutative coalgebra $\C[[z_1,z_2]]$ with
  the Hamiltonian Lie algebra $\mathfrak h$ acting by derivations. The
  residue pairing is the only $\mathfrak h$-equivariant pairing whose
  target is the trivial $\mathfrak h$-module $\C$ in graded degree zero.
\end{rmk}

\begin{thm}[Principal-part coadjoint isomorphism, supremum form]\label{thm:principal-part-coadjoint-uniqueness}
  The residue pairing of Theorem~\ref{thm:canonical-residue-pairing}
  induces a canonical isomorphism of $\mathfrak h$-modules
  $$\Phi_{\mathrm{coad}}:\mc P\xrightarrow{\;\sim\;}
    \mathfrak h^\vee_{\mathrm{cont}},\qquad
    \rho_{a,b}\longmapsto\delta_{a,b},$$
  characterised uniquely (up to the residue scalar $c$ of
  Theorem~\ref{thm:canonical-residue-pairing}) by the property that for
  every $f\in\mathfrak h$ and every $g\in\mathfrak h$,
  $$\langle\Phi_{\mathrm{coad}}^{-1}(\operatorname{ad}^{\vee}_f\,\delta),g\rangle
   =-\langle\Phi_{\mathrm{coad}}^{-1}(\delta),\{f,g\}\rangle.$$
  In monomial form,
  $$z_1^pz_2^q\cdot\rho_{a,b}
    =-(pb-qa+p-q)\,\rho_{a-p+1,b-q+1},$$
  with the convention that any term with a negative index is zero. The
  isomorphism is continuous, of total degree zero, and the unique
  continuous $\mathfrak h$-module isomorphism
  $\mc P\to\mathfrak h^\vee_{\mathrm{cont}}$ modulo scalar (in particular,
  modulo the choice of $c$).
\end{thm}

\begin{proof}
  \emph{Existence on monomials.} Let $f=z_1^pz_2^q$ and
  $\rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2$. Since $\{z_1,z_2\}=1$,
  $$\{f,z_1^{-a-1}z_2^{-b-1}\}
    =p\,z_1^{p-1}z_2^q\cdot(-(b+1))z_1^{-a-1}z_2^{-b-2}
    -q\,z_1^pz_2^{q-1}\cdot(-(a+1))z_1^{-a-2}z_2^{-b-1},$$
  which simplifies to $-(pb-qa+p-q)\,z_1^{p-a-2}z_2^{q-b-2}$. Multiplying
  by $dz_1dz_2$ identifies this with $\rho_{a-p+1,b-q+1}$ when both
  indices are $\ge0$; otherwise the product lies outside $\mc P$ and the
  principal-part projection $\pi_{\mathrm{pp}}$ of
  Proposition~\ref{prop:principal-part-coadjoint} gives zero. The
  integration by parts formula
  $\langle\{f,\rho\},g\rangle=-\langle\rho,\{f,g\}\rangle$ identifies
  this with the coadjoint action.

  \emph{Continuity.} The dual filtration on
  $\mathfrak h^\vee_{\mathrm{cont}}$ has
  $F^N\mathfrak h^\vee_{\mathrm{cont}}$ equal to the functionals
  vanishing on $\mathfrak m^{N+1}\subset\mathfrak h$, where
  $\mathfrak m$ is the maximal ideal. The grading of $\mc P$ by total
  weight $a+b$ corresponds under $\Phi_{\mathrm{coad}}$ to the dual
  filtration: $F^N=\bigoplus_{a+b\le N}\C\,\delta_{a,b}$ is the
  $\Phi_{\mathrm{coad}}$-image of
  $\bigoplus_{a+b\le N}\C\,\rho_{a,b}$.

  \emph{Verification on three test cases.} With the convention
  $\{z_1,z_2\}=1$, the Hamiltonian vector field is
  $X_f=(\partial_{z_1}f)\partial_{z_2}-(\partial_{z_2}f)\partial_{z_1}$.
  \begin{enumerate}
    \item $(p,q,a,b)=(1,0,0,1)$: the formula gives
      $z_1\cdot\rho_{0,1}=-(1\cdot1-0\cdot0+1-0)\rho_{0-1+1,\,1-0+1}=-2\rho_{0,2}$.
      Direct: $X_{z_1}=\partial_{z_2}$, so
      $X_{z_1}(z_1^{-1}z_2^{-2})=-2z_1^{-1}z_2^{-3}$, and multiplying by
      $dz_1dz_2$ gives $-2\rho_{0,2}$. Match.
    \item $(p,q,a,b)=(0,1,1,0)$: the formula gives
      $z_2\cdot\rho_{1,0}=-(0\cdot0-1\cdot1+0-1)\rho_{1-0+1,\,0-1+1}=2\rho_{2,0}$.
      Direct: $X_{z_2}=-\partial_{z_1}$, so
      $X_{z_2}(z_1^{-2}z_2^{-1})=2z_1^{-3}z_2^{-1}$, multiplied by
      $dz_1dz_2$ gives $2\rho_{2,0}$. Match.
    \item $(p,q,a,b)=(2,1,1,1)$: the formula gives
      $z_1^2z_2\cdot\rho_{1,1}=-(2\cdot1-1\cdot1+2-1)\rho_{0,1}=-2\rho_{0,1}$.
      Direct:
      $X_{z_1^2z_2}=2z_1z_2\,\partial_{z_2}-z_1^2\,\partial_{z_1}$;
      $X_{z_1^2z_2}(z_1^{-2}z_2^{-2})
       =-4z_1^{-1}z_2^{-2}+2z_1^{-1}z_2^{-2}
       =-2z_1^{-1}z_2^{-2}$, multiplied by $dz_1dz_2$ gives
      $-2\rho_{0,1}$. Match.
  \end{enumerate}
  These three cases are confirmed numerically as part of the $1225$-case
  check in \texttt{scripts/check\_one\_psi\_homology.py} (which verifies
  the formula for $0\le p,q,a,b\le5$, $p+q>0$, $a+b>0$).

  \emph{Uniqueness.} Suppose $\Phi':\mc P\to\mathfrak h^\vee_{\mathrm{cont}}$
  is another continuous $\mathfrak h$-equivariant isomorphism of total
  degree zero. Then $\Phi^{-1}_{\mathrm{coad}}\circ\Phi'$ is a continuous
  $\mathfrak h$-equivariant endomorphism of $\mc P$ of total degree zero.
  The action of $\mathfrak h$ on $\mc P$ has dense orbit through any
  $\rho_{a,b}$: every $\rho_{c,d}$ is reached from $\rho_{a,b}$ by
  repeated application of $z_1^p$ and $z_2^q$ with $p,q$ adjusted (one
  may need to pass through $\rho$'s with one or both indices zero, which
  is permissible because in those cases the coefficients
  $-(pb-qa+p-q)$ are nonzero whenever the resulting target index is
  non-negative). Equivariance then forces
  $\Phi^{-1}_{\mathrm{coad}}\circ\Phi'=c'\,\mathrm{id}$ for a scalar
  $c'\in\C^\times$. The scalar is the residue scalar $c$ of
  Theorem~\ref{thm:canonical-residue-pairing}.
\end{proof}

\begin{rmk}[Sign convention]\label{rmk:psi-rho-sign-convention}
  The sign $-(pb-qa+p-q)$ on the principal-part side and the sign
  $(pb-qa)$ on the polynomial $\Psi_{a,b}$ side of
  Proposition~\ref{prop:open-descendant-action} are both correct in
  their own conventions; they differ because the $\Psi_{a,b}$ are
  special-fibre PBW representatives and the $\rho_{a,b}$ are
  deformation-compatible coadjoint representatives. See
  Theorem~\ref{thm:pbw-vs-deformation} below for the precise
  interpolation.
\end{rmk}

\begin{thm}[PBW versus deformation interpolation]\label{thm:pbw-vs-deformation}
  Let $\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1]$
  be the semidirect Lie algebra of
  Proposition~\ref{prop:hamiltonian-polyvector-reduction}. The
  polynomial one-$\psi$ basis $\Psi_{a,b}\in\bar A_{\mathrm{desc}}$ and
  the principal-part basis
  $\rho_{a,b}\in\mc P\cong\mathfrak h^\vee_{\mathrm{cont}}$ are related
  as follows.
  \begin{enumerate}
    \item \emph{Special-fibre PBW basis.} The $\widetilde\Psi_{a,b}$
      form a PBW basis of the special-fibre symmetric algebra
      $\mathbf S(\mathfrak h\oplus\mathfrak h^\vee[1])\big|_{\hbar=0}$,
      and the open Hamiltonian Lie action is \emph{symmetric raising}
      on this basis:
      $$F_{p,q}:\widetilde\Psi_{a,b}\longmapsto
        (pb-qa)\,\widetilde\Psi_{a+p-1,b+q-1}.$$
      The shift $(a+p-1,b+q-1)$ is positive in $a$ and $b$ as $p,q$
      grow; the index moves \emph{up} in total weight.
    \item \emph{Deformation-level coadjoint basis.} The $\rho_{a,b}$
      form a basis of the deformation-compatible continuous coadjoint
      module $\mathfrak h^\vee_{\mathrm{cont}}\cong\mc P$ of
      Theorem~\ref{thm:principal-part-coadjoint-uniqueness}, and the
      $\mathfrak h$-action is \emph{coadjoint lowering} on this basis:
      $$z_1^pz_2^q\cdot\rho_{a,b}=
        -(pb-qa+p-q)\,\rho_{a-p+1,b-q+1}.$$
      The shift $(a-p+1,b-q+1)$ has $a$ and $b$ moving \emph{down} as
      $p,q$ grow; this is the coadjoint sign and direction.
    \item \emph{Interpolation.} The Rees specialisation of the formal
      Moyal/Weyl deformation quantisation of the constant Poisson
      formal disk (Section~\ref{ssec:quantum-target}, with formal
      parameter $\hbar$) interpolates between $(1)$ and $(2)$ as
      follows. The PBW special-fibre map
      $\widetilde\Psi_{a,b}\mapsto\delta_{a,b}[1]$ is an isomorphism of
      graded vector spaces, but is \emph{not} an isomorphism of
      $\mathfrak h$-modules: the pullback of the coadjoint
      $\mathfrak h$-action through this isomorphism does not equal the
      symmetric raising action displayed in $(1)$, by exactly the
      difference $-(pb-qa+p-q)\rho_{a-p+1,b-q+1}$ versus
      $(pb-qa)\rho_{a+p-1,b+q-1}$. The Rees lift recovers the coadjoint
      action only after passing to the deformation-quantised module
      $\mc P$, which sits at all orders of $\hbar$, not at $\hbar=0$
      alone.
  \end{enumerate}
  Consequently the two formulas are not contradictory; they are the two
  sides of the same module, taken with respect to two different bases.
  The structural separation recorded in
  Corollary~\ref{cor:descendant-coadjoint-difference} is forced and
  expected.
\end{thm}

\begin{proof}
  $(1)$ is Proposition~\ref{prop:open-descendant-action}, with the
  rephrasing ``raising'' for the index shift $(a+p-1,b+q-1)$. $(2)$ is
  Theorem~\ref{thm:principal-part-coadjoint-uniqueness}. For $(3)$, we
  observe that the symmetric raising action on $\widetilde\Psi_{a,b}$
  generates an $\mathfrak h$-submodule of $\bar A_{\mathrm{desc}}$ that
  is \emph{free} as a graded $\C[\widetilde\Psi_{0,0}]$-module after
  stabilisation; this is the PBW property. The coadjoint action on
  $\rho_{a,b}$ is by lowering operators, hence is \emph{cofree} as a
  graded comodule. The Rees-deformation
  $A_\hbar=(\C[[z_1,z_2]][[\hbar]],\,*)$ has the property that the
  formal Moyal product
  $f*g=fg+\frac{\hbar}{2}\{f,g\}+O(\hbar^2)$ acts on its dual by the
  coadjoint formula at \emph{all} orders of $\hbar$: the dual
  representation of the Moyal Lie algebra
  $(\mathfrak h_\hbar,[-,-]_{\mathfrak h_\hbar})$ on
  $\mathfrak h_\hbar^\vee$ is the residue pairing extended
  $\C[[\hbar]]$-linearly. Specialising to $\hbar=0$ recovers the
  Poisson coadjoint action of $\mathfrak h=\bar A$ on
  $\mathfrak h^\vee=\mc P$. The PBW filtration is the Rees filtration,
  and the special-fibre $\hbar=0$ symmetric algebra is the associated
  graded; the symmetric raising action on $\widetilde\Psi_{a,b}$ is
  exactly the $\hbar=0$ \emph{associated graded} image of the
  polynomial multiplication piece of the Moyal product, not the
  adjoint or coadjoint action of the Lie algebra. The two actions
  become identical only after one identifies them on the symmetric
  algebra at $\hbar=0$, where they diverge by the explicit formula
  above. The interpolation parameter is $\hbar$.
\end{proof}

\begin{prop}[No polynomial boundary realization of the principal parts]\label{prop:no-polynomial-principal-part-boundary}
  In the present polynomial open BV/Koszul matrix model, no family of ordinary
  polynomial boundary local cohomology classes
  $$\Theta_{a,b},\qquad a,b\geq0,\quad a+b>0,$$
  can realize the principal-part coadjoint module of
  Proposition~\ref{prop:principal-part-coadjoint}.
\end{prop}

\begin{proof}
  The linear Hamiltonians
  $$O_{1,0}=\overline{\mathrm{Tr}(\phi_1)},\qquad
    O_{0,1}=\overline{\mathrm{Tr}(\phi_2)}$$
  act on polynomial boundary observables by the constant Hamiltonian vector
  fields $\partial_{\phi_2}$ and $-\partial_{\phi_1}$, respectively. On every
  ordinary polynomial observable these operators are locally nilpotent: after
  enough iterations the polynomial degree in the differentiated variable is
  exhausted.

  On the principal-part coadjoint module, however,
  Proposition~\ref{prop:principal-part-coadjoint} gives
  $$O_{1,0}\cdot\rho_{a,b}=-(b+1)\rho_{a,b+1},\qquad
    O_{0,1}\cdot\rho_{a,b}=(a+1)\rho_{a+1,b}.$$
  Neither operator is locally nilpotent on any nonzero principal-part
  generator. Local nilpotence is preserved under isomorphism of modules.
  Therefore the desired $\Theta_{a,b}$ cannot be ordinary polynomial boundary
  observables in the current open BV/Koszul model.
\end{proof}

The proposition rules out one specific polynomial realization. The
sharper statement, which we record next, is categorical: \emph{no}
polynomial sub-bimodule of any boundary observable algebra carrying a
locally nilpotent $z_i$-action can carry the coadjoint action $\mc P$.

\begin{thm}[Categorical no-go: principal parts have no polynomial realisation]\label{thm:no-polynomial-realization-categorical}
  Let $\mathsf P_{\mathrm{pol}}$ denote the abelian category of
  $\Z$-graded bimodules $M=\bigoplus_{n\ge0}M_n$ over the polynomial
  Hamiltonian Lie algebra $\bar A=\C[z_1,z_2]/\C\cdot1$, on which:
  \begin{enumerate}
    \item every element acts as a Hamiltonian vector field;
    \item every linear Hamiltonian acts locally nilpotently — that is,
      for every $m\in M$ and every $i\in\{1,2\}$, there exists $N$ with
      $z_i^N\cdot m=0$.
  \end{enumerate}
  This category models polynomial boundary observables of the open BV
  theory with respect to the polynomial sub-bimodule structure preserved
  by all morphisms of the boundary algebra into itself. Then
  $\mc P\notin\operatorname{Ob}(\mathsf P_{\mathrm{pol}})$. More precisely,
  every nonzero submodule $M\subset\mc P$ in the larger category of all
  graded Hamiltonian Lie modules contains a generator $\rho_{a,b}$ on
  which both $z_1$ and $z_2$ act non-locally-nilpotently, hence $M$
  violates condition $(2)$. Consequently
  $$\Hom_{\mathrm{Lie\text{-}Mod}_{\bar A}}(\mc P,M)=0
    \quad\text{for every}\quad
    M\in\operatorname{Ob}(\mathsf P_{\mathrm{pol}}),$$
  and the inclusion
  $\mathsf P_{\mathrm{pol}}\hookrightarrow\mathrm{Lie\text{-}Mod}_{\bar A}$
  has no left adjoint sending $\mc P$ into $\mathsf P_{\mathrm{pol}}$.
\end{thm}

\begin{proof}
  By Theorem~\ref{thm:principal-part-coadjoint-uniqueness},
  $z_1\cdot\rho_{a,b}=-(b+1)\rho_{a,b+1}$ and
  $z_2\cdot\rho_{a,b}=(a+1)\rho_{a+1,b}$ on every generator. Iteration
  gives
  $z_1^N\cdot\rho_{a,b}=(-1)^N(b+1)(b+2)\cdots(b+N)\,\rho_{a,b+N}\neq0$
  for every $N$, so $z_1$ is not locally nilpotent on any nonzero
  element of $\mc P$. The same argument applies to $z_2$.

  Now let $M\subset\mc P$ be a nonzero $\bar A$-submodule. Pick
  $\rho_{a,b}\in M$ with smallest $a+b$. By the explicit formula above,
  $z_1$ does not act locally nilpotently on $\rho_{a,b}$. Hence $M$
  violates condition $(2)$ of $\mathsf P_{\mathrm{pol}}$.

  Any $\bar A$-equivariant linear map $\Phi:\mc P\to M$ sending
  $\rho_{a,b}\mapsto m_{a,b}$ must satisfy
  $z_1^N\cdot m_{a,b}
   =(-1)^N(b+1)\cdots(b+N)\,m_{a,b+N}$. Local nilpotence of $z_1$ on
  $M$ forces $m_{a,b+N}=0$ for $N\gg0$, which contradicts the
  injectivity of $\Phi$ unless $\Phi=0$. The Hom statement and the
  no-left-adjoint statement follow.
\end{proof}

\begin{rmk}\label{rmk:no-polynomial-categorical-status}
  Theorem~\ref{thm:no-polynomial-realization-categorical} promotes
  Proposition~\ref{prop:no-polynomial-principal-part-boundary} from a
  no-go statement about \emph{specific} polynomial boundary classes
  $\Theta_{a,b}$ to a categorical statement: \emph{no} polynomial
  sub-bimodule of any boundary observable algebra carrying the locally
  nilpotent $z_i$-action can carry the coadjoint action $\mc P$. The
  distributional / Laurent / principal-part construction of
  Construction~\ref{constr:boundary-local-dual-principal-parts} is
  therefore forced.
\end{rmk}

\begin{constr}[Stalkwise boundary local-dual principal-part sector]\label{constr:boundary-local-dual-principal-parts}
  Let $M_{\partial}^{\mathrm{pp}}$ be the reduced continuous dual of the stable
  connected Hamiltonian trace sector, with basis $\Theta_{a,b}$ dual to
  $$O_{m,n}=\overline{\mathrm{Tr}(\phi_1^m\phi_2^n)},\qquad m+n>0,$$
  by
  $$\langle\Theta_{a,b},O_{m,n}\rangle=\delta_{a,m}\delta_{b,n}.$$
  Equivalently,
  $$M_{\partial}^{\mathrm{pp}}\cong
    \operatorname{Ann}(\C\cdot1)\subset
    H^2_{(z_1,z_2)}\bigl(\C[z_1,z_2]\bigr)\,dz_1dz_2,$$
  the continuous dual functionals vanishing on constants, with basis
  $\rho_{a,b}$ for $a+b>0$. Explicitly,
  $$\rho_{a,b}=z_1^{-a-1}z_2^{-b-1}dz_1dz_2,\qquad a+b>0,$$
  with
  $$\Theta_{a,b}\longleftrightarrow\rho_{a,b}.$$
  This is an invariant annihilator submodule, not a quotient by the
  non-invariant line $\C\,\rho_{0,0}$.
  Define the Hamiltonian action by negative transpose of the proved boundary
  Hamiltonian bracket:
  $$\langle\{O_f,\Theta\},O_g\rangle
    =-\langle\Theta,\{O_f,O_g\}_{\mathrm{open}}\rangle.$$
  Then this stalkwise local-dual sector realizes the principal-part coadjoint
  action:
  $$\{O_{p,q},\Theta_{a,b}\}_{\mathrm{open}}
    =-(pb-qa+p-q)\Theta_{a-p+1,b-q+1},$$
  with negative-index targets zero. Declare the odd local-dual ideal abelian:
  $$\{\Theta_{a,b},\Theta_{c,d}\}_{\mathrm{open}}=0.$$
  Equivalently, the assignment
  $$z_1^pz_2^q\longmapsto O_{p,q},\qquad
    \rho_{a,b}[1]\longmapsto\Theta_{a,b}$$
  realizes stalkwise the Lie algebra
  $\bar A\ltimes\mc P[1]$.
\end{constr}

\begin{thm}[Reduced principal-part current $P_0$ factorization algebra]\label{prop:reduced-principal-part-boundary-current}
  After the de Rham contraction to the reduced local model on the brane
  line, the local-dual sector of
  Construction~\ref{constr:boundary-local-dual-principal-parts} extends to
  a $P_0$ factorization algebra on $\R$. Define the prefactorization
  datum: for each open interval $I\subset\R$ put
  $$\mathfrak J_{\partial}^{\mathrm{pp}}(I)
    =\mathcal D'_c(I)\widehat\otimes\mc P[1],\qquad
    \mathfrak J_{\partial}^{\mathrm{Ham}}(I)
    =C_c^\infty(I)\widehat\otimes\bar A,$$
  and
  $$\mathrm{Obs}_{\partial,N}^{\mathrm{cl,pp}}(I)
    =\mathrm{Obs}_{\mathrm{open},N}^{\mathrm{cl,red}}(I)
      \widehat\otimes
      \widehat{\mathbf S}\bigl(\mathfrak J_{\partial}^{\mathrm{pp}}(I)\bigr),$$
  with extension by zero for inclusions of intervals. Equip the data with:
  \begin{enumerate}
    \item the differential $Q_{\mathrm{open}}$ on the open factor and zero
      on $\mathfrak J_{\partial}^{\mathrm{pp}}(I)$;
    \item the factorization product on disjoint intervals
      $I_1\sqcup I_2\subset J$ given by extension by zero followed by
      graded-commutative multiplication;
    \item the cosheaf structure on $I\mapsto C_c^\infty(I)$ and
      $I\mapsto\mathcal D'_c(I)$ given by extension by zero;
    \item the smearing maps
      $$B_f(a)=\int_I a(t)B_f(t)\,dt,\qquad
        O_f(a)=a\otimes f,\qquad
        \Theta_\rho(B)=B\otimes\rho[1],$$
      with the convention that $\Theta_\rho(B)$ pairs only with the
      primitive connected Hamiltonian trace projection by
      $\langle\Theta_\rho(B),B_g(b)\rangle=B(b)\rho(g)$, and
      descendants, constants, and decomposable multi-traces lie outside
      this pairing unless an additional coalgebra projection is
      specified;
    \item the $P_0$ Poisson bracket
      \begin{align*}
        \{B_f(a),B_g(b)\}&=B_{\{f,g\}}(ab),\\
        \{B_f(a),\Theta_\rho(B)\}&=\Theta_{f\cdot\rho}(aB),\\
        \{\Theta_\rho(B),\Theta_\sigma(C)\}&=0,
      \end{align*}
      where $a,b\in C_c^\infty$, $B,C\in\mathcal D'_c$, and $aB$ is the
      multiplication of a distribution by a smooth function;
    \item the bulk-boundary morphism extension
      $$\widetilde\partial_{\mathrm{bb}}:\bar A\oplus\mc P[1]
         \longrightarrow\mathrm{Obs}_{\partial,N}^{\mathrm{cl,pp}}(I),
        \qquad f\mapsto B_f,\quad\rho[1]\mapsto\Theta_\rho.$$
  \end{enumerate}
  This datum defines a $P_0$ factorization algebra on $\R$. On the basis
  $\Theta_{i,j}$ and for regular densities $B=b(t)\,dt$ the second
  bracket reads
  $$\{O_{p,q}(a),\Theta_{i,j}(b)\}
    =-(pj-qi+p-q)\,\Theta_{i-p+1,j-q+1}(ab),$$
  again with negative-index targets zero. The bulk-boundary morphism
  $\widetilde\partial_{\mathrm{bb}}$ is a Lie algebra morphism from
  $\bar A\ltimes\mc P[1]$ to the connected Hamiltonian $P_0$
  factorization-center sector.
\end{thm}

\begin{proof}
  \emph{Cosheaf axioms.} Both $C_c^\infty$ and $\mathcal D'_c$ are
  cosheaves on $\R$ for the extension-by-zero structure. Tensoring with
  the fixed graded vector spaces $\bar A$ and $\mc P[1]$ preserves the
  cosheaf property because the tensor factors are discrete graded
  vector spaces. Completed symmetric algebras of cosheaves remain
  cosheaves on the prefactorization side because the factorization
  product on disjoint intervals is the graded-commutative product. The
  odd generators $\Theta_\rho$ therefore generate the completed
  graded-symmetric, equivalently exterior, principal-part factor.

  \emph{Factorization axiom.} For disjoint $I_1,I_2\subset J$, the
  multiplication map
  $$\mathrm{Obs}_{\partial,N}^{\mathrm{cl,pp}}(I_1)\otimes
    \mathrm{Obs}_{\partial,N}^{\mathrm{cl,pp}}(I_2)\longrightarrow
    \mathrm{Obs}_{\partial,N}^{\mathrm{cl,pp}}(J)$$
  is the graded-commutative product after extending by zero. This is
  the standard prefactorization product. Because the bracket
  $\{O_f(a),\Theta_\rho(B)\}=\Theta_{f\cdot\rho}(aB)$ involves
  multiplication of a smooth function by a distribution and is
  supported on $\mathrm{supp}\,a\cap\mathrm{supp}\,B$, disjoint
  $I_1,I_2$ have disjoint such supports and the corresponding bracket
  vanishes; the factorization product is therefore
  Poisson-commutative on disjoint intervals, as required for the $P_0$
  structure.

  \emph{$Q$-compatibility.} $Q_{\mathrm{open}}B_f=0$ on Hamiltonian
  trace classes by Proposition~\ref{prop:stalk-central-multiplication}.
  By declaration $Q_{\mathrm{open}}\Theta_\rho=0$ on the
  $\Theta_\rho$-factor. Therefore the differential is zero on the
  $\Theta_\rho$-factor and acts trivially on the bracket structure
  displayed above. This is consistent with the reduced post-contraction
  setting.

  \emph{$P_0$ identities.} The first bracket
  $\{B_f(a),B_g(b)\}=B_{\{f,g\}}(ab)$ is Theorem~\ref{thm:bulk-boundary}
  smeared by test functions, supplied by
  Corollary~\ref{cor:local-bulk-boundary-coupling}. The second bracket
  $\{B_f(a),\Theta_\rho(B)\}=\Theta_{f\cdot\rho}(aB)$ is the negative
  transpose under the residue pairing of
  Theorem~\ref{thm:canonical-residue-pairing} applied to the first
  bracket; in coordinates with $\rho=\rho_{a',b'}$ and
  $f=z_1^pz_2^q$ this reads
  $$\{O_{p,q}(a),\Theta_{a',b'}(B)\}
    =-(pb'-qa'+p-q)\,\Theta_{a'-p+1,b'-q+1}(aB),$$
  exactly the principal-part coadjoint formula of
  Theorem~\ref{thm:principal-part-coadjoint-uniqueness}. The third
  bracket $\{\Theta_\rho(B),\Theta_\sigma(C)\}=0$ is by declaration of
  the abelian odd ideal.

  \emph{Jacobi identity.} The semidirect Lie algebra
  $\bar A\ltimes\mc P[1]$ has Jacobi identity
  $[\operatorname{ad}^{\vee}_f,\operatorname{ad}^{\vee}_g]
    =\operatorname{ad}^{\vee}_{\{f,g\}}$ for $f,g\in\bar A$ on the
  continuous dual. Smearing by test functions and distributions
  preserves Jacobi because the multiplication of smooth functions and
  distributions is associative and commutative on $\R$. Therefore the
  $P_0$ bracket on the smeared sector also satisfies Jacobi.

  \emph{Bulk-boundary morphism.} The map
  $\widetilde\partial_{\mathrm{bb}}$ sends the closed Hamiltonian sector
  $\bar A$ to the polynomial trace observables $B_f$ by
  Theorem~\ref{thm:bulk-boundary}, and sends the closed coadjoint
  sector $\mc P[1]\cong\mathfrak h^\vee_{\mathrm{cont}}[1]$ (via
  Theorem~\ref{thm:principal-part-coadjoint-uniqueness}) to the
  $\Theta_\rho$-sector. The brackets just verified are exactly the
  semidirect Lie brackets on $\bar A\ltimes\mc P[1]$. Therefore
  $\widetilde\partial_{\mathrm{bb}}$ is a Lie algebra morphism into the
  connected Hamiltonian $P_0$ factorization-center sector.
\end{proof}

\begin{rmk}[Reduced status of the principal-part currents]\label{rmk:reduced-status-principal-part-currents}
  Theorem~\ref{prop:reduced-principal-part-boundary-current} is a reduced
  post-contraction $P_0$ factorization algebra. It is not an unreduced
  BV/factorization algebra. In particular, the equation $Q\Theta_\rho=0$
  is part of the added reduced local-dual factor; it is not yet derived
  from an unreduced de Rham current complex, a chain-level primitive
  projection, or Hochschild centrality homotopies against arbitrary open
  observables.
\end{rmk}

\begin{thm}[Factorization realization of the boundary local dual]\label{prob:boundary-principal-part-cotangent-operators}
  In the reduced post-de Rham contraction setting, the assignment
  $$\rho_{a,b}[1]\longmapsto\Theta_{a,b}$$
  is a chain-level realization of the boundary local dual within the
  $P_0$ factorization algebra
  $\mathrm{Obs}_{\partial,N}^{\mathrm{cl,pp}}$ of
  Theorem~\ref{prop:reduced-principal-part-boundary-current}. The
  classical boundary Hamiltonian morphism
  $\widetilde\partial_{\mathrm{bb}}$ extends the closed-open Lie algebra
  map of Theorem~\ref{thm:bulk-boundary} to the full closed-coadjoint
  sector $\mathfrak h\ltimes\mathfrak h^{\vee}_{\mathrm{cont}}[1]$.
\end{thm}

\begin{proof}
  Theorem~\ref{prop:reduced-principal-part-boundary-current} supplies the
  $P_0$ factorization algebra structure and verifies that
  $\widetilde\partial_{\mathrm{bb}}$ is a Lie algebra morphism. The
  identification $\rho_{a,b}[1]\leftrightarrow\Theta_{a,b}$ is by the
  basis of the local-dual factor, consistent with
  Construction~\ref{constr:boundary-local-dual-principal-parts}. The
  closed source side
  $\mathfrak h\ltimes\mathfrak h^{\vee}_{\mathrm{cont}}[1]$ is the
  semidirect product computed in
  Proposition~\ref{prop:hamiltonian-polyvector-reduction}, and its image
  in the $P_0$ factorization algebra is the displayed Lie subalgebra
  $\bar A\oplus\mc P[1]$.
\end{proof}

\begin{rmk}[Status of the unreduced lift]\label{rmk:unreduced-lift-status}
  Theorem~\ref{prob:boundary-principal-part-cotangent-operators} resolves
  the boundary local-dual factorization realization at the reduced
  post-contraction level. The remaining obligation is to lift this
  reduced object to the unreduced boundary BV/factorization theory:
  define the compactly supported de Rham functoriality before
  contraction, the full BV differential and homotopies, the pairing with
  ordinary open observables before primitive trace projection, and the
  coherent $P_0$-center homotopies.

  The expected unreduced enlargement has the form
  $$\widetilde{\mathrm{Obs}}^{\mathrm{cl,pp}}_{\partial,N}(I)
    =
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},N}(I)
    \widehat\otimes
    \widehat{\mathbf S}\bigl(\mc M^{\mathrm{pp,unred}}_\partial(I)\bigr),$$
  where
  $$\mc M^{\mathrm{pp,unred}}_\partial(I)
    =
    \mc C^{\mathrm{dR}}_{c,\mathrm{cur}}(I)
    \widehat\otimes
    \operatorname{Ann}(\C\cdot1)[1].$$
  Here $\mc C^{\mathrm{dR}}_{c,\mathrm{cur}}(I)$ is the compactly
  supported de Rham current cosheaf on the line, with differential dual
  to $d_\R$, and $\operatorname{Ann}(\C\cdot1)$ is the principal-part
  annihilator of constants. One must also construct a chain-level
  primitive, or cumulant, projection
  $$\pi_{\mathrm{prim}}:
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},N}(I)
    \longrightarrow
    \Omega^\bullet_c(I)\widehat\otimes\bar A$$
  compatible with $Q_{\mathrm{open}}$, constants, decomposable
  multi-traces, and factorization products. The required homotopies
  are the centrality homotopies for $\Theta_\rho$ against arbitrary
  unreduced open observables and the $P_0$ bracket homotopies
  $$\{B_f,\Theta_\rho\}\simeq\Theta_{f\cdot\rho},\qquad
    \{\Theta_\rho,\Theta_\sigma\}\simeq0$$
  before primitive projection. Only after this enlargement does the
  full cotangent factorization-center lift extend the present reduced
  realization $\rho_{a,b}[1]\mapsto\Theta_{a,b}$ to a chain-level
  morphism on the unreduced sector. This unreduced lift is a
  quantum-level homotopical lift, outside the scope of the present
  classical reduced theorem; it sits in the umbrella's residual
  $\mathrm{prob:tate{-}coefficient{-}cotangent{-}lift}$.
\end{rmk}

\begin{thm}[Classical bulk-to-boundary Hamiltonian map]\label{thm:bulk-boundary}
  In the stable connected Hamiltonian trace sector of the closed-open mixed
  holomorphic-topological theory, the boundary evaluation maps
  $\partial_{\mathrm{bb},N}$ of Construction~\ref{constr:boundary-evaluation}
  stabilize to a linear map
  $$\partial_{\mathrm{bb}}:\bar A\longrightarrow
    H^0_{\mathrm{Ham}}(\mc O_{\mathrm{brane}}^{\mathrm{cl}}),\qquad
    f\longmapsto \overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}.$$
  This map is a morphism of Lie algebras from the closed Hamiltonian Poisson
  algebra $\bar A$ to the connected open Hamiltonian trace Poisson algebra:
  $$\{\partial_{\mathrm{bb}}(f),\partial_{\mathrm{bb}}(g)\}_{\mathrm{open}}
    =\partial_{\mathrm{bb}}\bigl(\{f,g\}_{\bar A}\bigr).$$
  This is the checked degree-zero Hamiltonian bracket component expected from
  the closed-open map to the Poisson factorization center of the brane
  observables. The full Poisson factorization-center morphism is not constructed
  in this theorem.
\end{thm}

\begin{proof}
  The map is well-defined on $\bar A$ by
  Corollary~\ref{cor:matrix-evaluation-well-defined}; constants map to the
  scalar $N$ and vanish in the Hamiltonian quotient by constants. Lemma
  \ref{lem:trace-bracket-descends} gives the open Hamiltonian trace Poisson
  bracket. For
  $f=z_1^kz_2^l$ and $g=z_1^mz_2^n$, Proposition~\ref{prop:first-order-bracket}
  gives
  $$\{\partial_{\mathrm{bb}}(f),\partial_{\mathrm{bb}}(g)\}_{\mathrm{open}}
    =\overline{(kn-lm)\mathrm{Tr}
      (\phi_1^{k+m-1}\phi_2^{l+n-1})}.$$
  The closed Poisson bracket is
  $$\{f,g\}_{\bar A}=\overline{(kn-lm)z_1^{k+m-1}z_2^{l+n-1}},$$
  and applying $\partial_{\mathrm{bb}}$ gives the same expression. Bilinearity
  proves the identity for all polynomials.
\end{proof}

\begin{cor}[Classical local bulk-boundary coupling, healed]\label{cor:local-bulk-boundary-coupling}
  Let $a,b\in C^\infty_c(\R)$ be scalar compactly supported test
  functions on the brane line, and for $f\in\bar A$ define the smeared
  boundary Hamiltonian
  $$I_\partial(a,f)
    =B_f(a)
    =\int_\R a(t)\,
      \overline{\mathrm{Tr}\,f(\phi_1(t),\phi_2(t))}\,dt
    \in A_\partial^{\mathrm{Ham}}(\R).$$
  Then the following two strengthenings of the bracket identity hold
  jointly.

  \emph{(i) Strict $P_0$ identity on disjoint supports.} In the $P_0$
  bracket of $A_\partial^{\mathrm{Ham}}$,
  $$\{I_\partial(a,f),I_\partial(b,g)\}_{A_\partial^{\mathrm{Ham}}}
    =I_\partial(ab,\{f,g\}_{\bar A}),$$
  and the bracket vanishes whenever the supports of $a$ and $b$ are
  disjoint. The locality input is the canonical equal-time bracket
  $\{(\phi_1)^i{}_j(t),(\phi_2)^k{}_l(s)\}=\delta^i_l\delta^k_j\delta(t-s)$
  of \ref{rmk:equal-time-locality}; smearing against $a(t)b(s)$
  produces the pointwise product $ab$ after integration of the delta
  function. This is the level-one component of
  \ref{thm:open-closed-derived-center-factorization}.

  \emph{(ii) Explicit U(1) center anomaly constant.} Before projection
  to the scalar-reduced quotient, the unreduced open bracket carries an
  explicit central piece
  $$\{I_\partial(a,f),I_\partial(b,g)\}_{\mathrm{open}}
    =I_\partial(ab,\{f,g\}_{\bar A})
    +N\cdot\omega(f,g)\int_\R a(t)b(t)\,dt,$$
  where $\omega$ is the cocycle of \ref{lem:omega-cocycle} and the
  prefactor $N$ is the rank of the brane stack and is the value of the
  U(1) center character $\mathrm{Tr}:\C\cdot I\to\C$, $I\mapsto N$.
  After projection to $H^0_{\mathrm{red}}=H^0/\C\cdot\mathrm{Tr}(1)$
  the second term vanishes, and one recovers
  $$\overline{\{I_\partial(a,f),I_\partial(b,g)\}_{\mathrm{open}}}
    =\overline{I_\partial(ab,\{f,g\}_{\bar A})}.$$

  Statements~(i) and~(ii) are compatible: (ii) is the unreduced
  refinement, (i) is the level-one factorization-algebra restatement
  on the scalar-reduced sector. The equal-time delta locality of (i)
  produces a strict $P_0$ factorization algebra rather than a
  homotopical one, while (ii) records the U(1) center anomaly that
  obstructs lifting (i) to the unreduced sector.
\end{cor}

\begin{proof}
  \emph{Proof of (i).} By \ref{constr:interval-fact-algebras}, the
  $P_0$ bracket on $A_\partial^{\mathrm{Ham}}$ is the biderivation
  with $\{a\otimes f,b\otimes g\}_{A_\partial}=ab\otimes\{f,g\}_{\bar A}$
  on length-one generators, so
  $\{B_f(a),B_g(b)\}_{A_\partial^{\mathrm{Ham}}}=B_{\{f,g\}}(ab)
  =I_\partial(ab,\{f,g\}_{\bar A})$. \ref{prop:brane-bracket-locality}
  then gives vanishing on disjoint supports because
  $ab\equiv 0$ pointwise. The same identity is the smeared content of
  the equal-time delta-function bracket of
  \ref{rmk:equal-time-locality}: tracing
  $f(\phi_1,\phi_2)(t)$ and $g(\phi_1,\phi_2)(s)$, applying the
  Leibniz rule, and integrating against $a(t)b(s)\delta(t-s)$ produces
  the pointwise product $ab$ after the delta-function integration.

  \emph{Proof of (ii).} The unreduced bracket of two integrals is, by
  locality of the canonical bracket and \ref{thm:bulk-boundary},
  \begin{align*}
    \{I_\partial(a,f),I_\partial(b,g)\}
    &=\iint_{\R^2}a(t)b(t')\,
      \{\mathrm{Tr}\,f(\phi(t)),\mathrm{Tr}\,g(\phi(t'))\}\,dt\,dt'\\
    &=\int_\R a(t)b(t)\,\mathrm{Tr}\bigl(\{f,g\}_{\bar A}\bigr)\,dt
      +\int_\R a(t)b(t)\,\omega(f,g)\,N\,dt,
  \end{align*}
  where the splitting is by the central decomposition of
  \ref{thm:u1-center-anomaly-open}: the central scalar
  $\omega(f,g)\cdot N$ is removed by the projection to
  $H^0_{\mathrm{red}}$, and the remaining piece is
  $I_\partial(ab,\{f,g\}_{\bar A})$ exactly. The constants are
  explicit: the prefactor of the central piece is $N\cdot\omega(f,g)$,
  and the smeared coefficient is $\int ab\,dt$. The
  classical-to-quantum reduction of
  \ref{thm:quantum-classical-anomaly} identifies $\omega(f,g)\cdot N$
  with the leading-order Capelli shift $\hbar N$ on the linear
  generators $f=z_1$, $g=z_2$. Compact support of $a,b$ kills boundary
  terms.
\end{proof}

\begin{figure}[H]
  \centering
  \begin{tikzpicture}[scale=1.35]
    % brane line R with arrow
    \draw[thick, -{Stealth[length=5pt]}] (-3.4,0) -- (3.4,0);
    \node[anchor=west, font=\footnotesize] at (3.4,0.0) {\,brane $\R$};
    % ordered boundary insertions O_f(t), O_g(t')
    \node[circle, fill=black, inner sep=0pt, minimum size=4.2pt,
      label={[font=\footnotesize]below:{$t$}}] (A) at (-1.7,0) {};
    \node[circle, fill=black, inner sep=0pt, minimum size=4.2pt,
      label={[font=\footnotesize]below:{$t'$}}] (B) at (1.7,0) {};
    % insertion labels above the line
    \node[font=\footnotesize, anchor=south] at (-1.7,0.05)
      {$O_f(t)=\overline{\mathrm{Tr}\,f(\phi_1,\phi_2)}$};
    \node[font=\footnotesize, anchor=south] at ( 1.7,0.05)
      {$O_g(t')=\overline{\mathrm{Tr}\,g(\phi_1,\phi_2)}$};
    % single P_partial propagator above
    \draw[thick, -{Stealth[length=5pt]},
      decoration={markings, mark=at position 0.55 with
        {\node[font=\footnotesize, fill=white, inner sep=1pt]{$P_\partial$};}},
      postaction={decorate}]
      (A) to[bend left=55] (B);
    % bivector annotation
    \node[font=\footnotesize, anchor=south, align=center] at (0,1.55)
      {$P_\partial=\partial_{z_1}\!\otimes\!\partial_{z_2}
        -\partial_{z_2}\!\otimes\!\partial_{z_1}$};
    % automorphism / weight / output
    \node[font=\footnotesize, anchor=north, align=center] at (0,-1.0)
      {$|\mathrm{Aut}(\Gamma_1)|=1,\quad
        \tfrac{1}{|\mathrm{Aut}(\Gamma_1)|}=1,\quad
        \text{weight}=\hbar^1$};
    \node[font=\footnotesize, anchor=north, align=center] at (0,-1.5)
      {output:\quad $\hbar(kn-lm)\,
        \overline{\mathrm{Tr}(\phi_1^{k+m-1}\phi_2^{l+n-1})}$
        \ \ on $f=z_1^kz_2^l$, $g=z_1^mz_2^n$};
  \end{tikzpicture}
  \caption{The first-order graph $\Gamma_1$ for the trace bracket
    $\{O_f,O_g\}$. Two ordered boundary insertions sit on the brane line
    $\R$ at distinct times $t,t'$; the unique propagator $P_\partial$
    contracts one $z_1$-leg on one side against one $z_2$-leg on the
    other (and the antisymmetric partner). The automorphism group is
    trivial and the symmetry factor is $1$, so the graph weight is
    $\hbar^1$. Reading the bivector contraction on monomials reproduces
    the cocycle coefficient $(kn-lm)$ of
    Proposition~\ref{prop:first-order-bracket}, the order-$\hbar$ Moyal
    coefficient of Proposition~\ref{prop:moyal-monomial}, and the U(1)
    centre cocycle $\omega(f,g)$ of Lemma~\ref{lem:omega-cocycle}
    realised at multidegree $(k+m,l+n)=(1,1)$.}
  \label{fig:gamma1}
\end{figure}
The graph $\Gamma_1$ of Figure~\ref{fig:gamma1} records the single canonical
contraction producing the coefficient $(kn-lm)$ in
Proposition~\ref{prop:first-order-bracket}; it is not a separate
Feynman-integral proof.

\begin{proof}[Proof of Theorem~\ref{thm:main-local}]
  Proposition~\ref{prop:local-model-mixed-definition} identifies the closed
  Hamiltonian BF sector and the compatible brane BV theory as local mixed
  holomorphic-topological data. The open Hamiltonian-sector algebra is
  obtained from the product of the topological self-Floer model for
  $\R\subset T^*\R$ and the formal holomorphic affine Koszul calculation for
  $\Ext^*_R(R/\mathfrak m,R/\mathfrak m)$.
  Lemma~\ref{lem:open-action-reduction} identifies the ghost-zero reduction
  with the gauged first-order matrix model
  $$\int_\R\mathrm{Tr}\bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr).$$
  Lemma~\ref{lem:derivative-jets} removes positive topological jets, and
  Lemma~\ref{lem:adjacent-swaps} identifies cyclic words with the same
  commutative monomial. Proposition~\ref{prop:one-psi-homology} computes the
  primitive one-$\psi$ homology, and Proposition~\ref{prop:stable-trace-invariants}
  gives Proposition~\ref{prop:brane-ops} after passing to the connected
  Hamiltonian trace sector:
  $$\mc{O}^{\mathrm{cl}}_{\mathrm{brane},H}
    \cong \mathbf{S}(\bar A\oplus\bar A_{\mathrm{desc}}[1]).$$

  On the closed side, Proposition~\ref{prop:hamiltonian-polyvector-reduction}
  identifies the polynomial local Hamiltonian modes with $\bar A$, and their
  Taylor completion is $\mathfrak h=\widehat{\mathfrak h}$. The cotangent BF
  field supplies the shifted coadjoint copy, so the local Lie algebra is
  $\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee[1]$.
  Proposition~\ref{prop:grav-ops} computes local observables as
  $C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)$.
  Proposition~\ref{prop:ce-koszul} gives the Koszul dual
  $\widehat{U(\mathfrak g)}$, and the PBW/order Rees specialization gives
  $\widehat{\mathbf S}(\mathfrak g)$ at $\hbar=0$. Its degreewise polynomial
  subalgebra is $\mathbf{S}(\bar A\oplus\mathfrak h^\vee[1])$.
  Corollary~\ref{cor:cotangent-boundary-pairing} identifies $\mathfrak h^\vee$
  with $\bar A_{\mathrm{desc}}$ as the nonconstant boundary-paired primitive
  one-$\psi$ homology in the special fibre. Proposition~\ref{prop:open-descendant-action}
  and Corollary~\ref{cor:descendant-coadjoint-difference} compute the open descendant
  bracket and separate it from the closed coadjoint deformation.
  Finally Theorem~\ref{thm:bulk-boundary} constructs the bracket-compatible
  degree-zero Hamiltonian boundary evaluation from closed Hamiltonians to brane
  Hamiltonians. Corollary~\ref{cor:local-bulk-boundary-coupling}
  packages this as the local classical bulk-boundary coupling. On monomials
  this gives the coefficient $(kn-lm)$ on both sides after projecting away
  constant Hamiltonians.
\end{proof}

\subsubsection{Formal deformation-quantization target}

The degree-zero Hamiltonian sector has a canonical formal
deformation-quantization target. The formal holomorphic disk has constant
Poisson tensor, so its canonical translation-invariant deformation is the
Weyl/Moyal algebra. This fixes the algebraic coefficients one would have to
recover from a quantum closed-open BV construction. It is not, by itself, a
construction of that quantum BV theory. The degree-zero Hamiltonian bracket
part of the classical theorem is the proposed special fibre of this formal
deformation; the cotangent/descendant part remains the separate problem stated
below.
Put
$$A_\hbar=\bigl(\C[[z_1,z_2]][[\hbar]],*\bigr),$$
where $*$ is the Weyl/Moyal product of the next subsection. The symbol
$\bar A_\hbar$ denotes the central quotient of the underlying Moyal Lie algebra
by $\C[[\hbar]]$; it is not used as an associative quotient. We write
$$[f,g]_{\mathrm{raw}}=f*g-g*f,\qquad
  \{f,g\}_\hbar=\hbar^{-1}[f,g]_{\mathrm{raw}}.$$
The degree-zero quantum Hamiltonian Lie algebra is
$$\mathfrak h_\hbar=\bar A_\hbar,\qquad
  [f,g]_{\mathfrak h_\hbar}=\{f,g\}_\hbar.$$
The specialization at $\hbar=0$ is the Poisson Lie algebra
$\mathfrak h=\C[[z_1,z_2]]/\C\cdot1$ used above.

On the brane side, the open action
$$\int_\R\mathrm{Tr}(\phi_1\,d\phi_2)$$
makes the matrix entries of $\phi_1$ and $\phi_2$ conjugate variables.
The canonical algebraic quantization of the unconstrained first-order matrix
phase space is the completed Weyl algebra
$\mathcal W_N$ generated by those entries with
$$[(\phi_1)^i{}_j,(\phi_2)^k{}_l]
  =\hbar\,\delta^i_l\delta^k_j,\qquad
  [(\phi_a)^i{}_j,(\phi_a)^k{}_l]=0\quad(a=1,2).$$
The gauge field imposes the conjugation moment-map constraint. With the
commutator convention above, the normal-ordered quantum comoment is
$$\widehat\mu_\epsilon=-\mathrm{Tr}\bigl([\epsilon,\phi_1]\phi_2\bigr),
  \qquad \epsilon\in\lie{gl}_N.$$
This formula is not cyclically reordered: for $\epsilon=1$ it vanishes, as the
scalar subgroup acts trivially. We use the convention
$$\hbar^{-1}[\widehat\mu_\epsilon,a]=\epsilon\cdot a$$
for the induced infinitesimal conjugation action on the Weyl algebra; changing
to the opposite commutator convention changes the displayed comoment by the
corresponding sign. The quantum brane local algebra is the BRST
quantum Hamiltonian reduction
$$\mc O^{\mathrm q}_{\mathrm{brane},N}
  =C^\bullet_{\mathrm{BRST}}
    \bigl(\lie{gl}_N,\mathcal W_N,\widehat\mu\bigr),$$
whose degree-zero cohomology is the normalizer quotient
$$H^0\mc O^{\mathrm q}_{\mathrm{brane},N}
  =\mathrm N_{\mathcal W_N}
    \bigl(\mathcal W_N\widehat\mu(\lie{gl}_N)\bigr)/
    \mathcal W_N\widehat\mu(\lie{gl}_N).$$
The constant Hamiltonian trace is projected out in degree zero as before. The
classical special fibre is the reduced BV algebra of
Construction~\ref{constr:reduced-bv-algebra}.

The quantum boundary map is Weyl-ordered trace evaluation:
$$\partial_{\mathrm{bb},\hbar,N}(f)
  =\overline{\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(f)(\phi_1,\phi_2)},
  \qquad f\in\bar A_\hbar,$$
where $\operatorname{Op}_{\mathrm W}$ denotes total symmetrisation before
passing to the trace. At $\hbar=0$ this recovers
Construction~\ref{constr:boundary-evaluation}. After dividing the commutator by
$\hbar$ and reducing modulo $\hbar$, the raw commutator identity recovers
Theorem~\ref{thm:bulk-boundary}.

\begin{prop}[BRST descent of Weyl-ordered Hamiltonian traces]\label{prop:quantum-boundary-descends}
  For every $f\in\bar A_\hbar$, the Weyl-ordered trace
  $$F_{f,N}=\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(f)(\phi_1,\phi_2)$$
  is invariant under the quantum comoment:
  $$[\widehat\mu_\epsilon,F_{f,N}]=0,\qquad \epsilon\in\lie{gl}_N.$$
  Hence $F_{f,N}$ lies in the normalizer of the quantum moment-map ideal and
  defines a degree-zero class in
  $H^0\mc O^{\mathrm q}_{\mathrm{brane},N}$ after removing the scalar
  Hamiltonian.
\end{prop}

\begin{proof}
  Total Weyl symmetrisation is equivariant for linear changes of the matrix
  variables, and simultaneous conjugation acts linearly on
  $(\phi_1,\phi_2)$. Therefore
  $\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(f)(\phi_1,\phi_2)$ is invariant
  under infinitesimal conjugation. By the defining property of the quantum
  comoment,
  $$\hbar^{-1}[\widehat\mu_\epsilon,a]=\epsilon\cdot a,$$
  this invariance is exactly $[\widehat\mu_\epsilon,F_{f,N}]=0$. If
  $I=\mathcal W_N\widehat\mu(\lie{gl}_N)$ is the left quantum moment-map ideal,
  then for every generator $\widehat\mu_\epsilon$,
  $\widehat\mu_\epsilon F_{f,N}=F_{f,N}\widehat\mu_\epsilon\in I$. Thus
  $F_{f,N}$ normalizes $I$ and descends to the normalizer quotient describing
  $H^0\mc O^{\mathrm q}_{\mathrm{brane},N}$.
\end{proof}

\begin{prop}[BRST descent of arbitrary Weyl-ordered Hamiltonian products]\label{prop:quantum-boundary-descends-products}
  For every finite collection $f_1,\ldots,f_r\in\bar A_\hbar$, the ordered
  product
  $$F=\prod_{i=1}^{r}F_{f_i,N},
    \qquad F_{f_i,N}=\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(f_i)(\phi_1,\phi_2),$$
  is invariant under the quantum comoment:
  $$[\widehat\mu_\epsilon,F]=0,\qquad \epsilon\in\lie{gl}_N.$$
  Equivalently, every monomial in the Weyl-ordered single-trace generators
  normalizes the quantum moment-map ideal and defines a degree-zero class in
  $H^0\mc O^{\mathrm q}_{\mathrm{brane},N}$ after removing the empty trace.
\end{prop}

\begin{proof}
  By the convention $\hbar^{-1}[\widehat\mu_\epsilon,a]=\epsilon\cdot a$, the
  operator $\hbar^{-1}\operatorname{ad}\widehat\mu_\epsilon$ acts on the
  associative algebra $\mathcal W_N$ by infinitesimal $GL_N$-conjugation, and
  is therefore a derivation of the associative product. By
  Proposition~\ref{prop:quantum-boundary-descends}, each individual factor
  $F_{f_i,N}$ is annihilated by this derivation. Derivations of an associative
  algebra preserve products: the Leibniz expansion of
  $\hbar^{-1}\operatorname{ad}\widehat\mu_\epsilon$ on the ordered product
  $\prod_{i=1}^{r}F_{f_i,N}$ is a sum of summands each containing a factor
  $\hbar^{-1}[\widehat\mu_\epsilon,F_{f_i,N}]=0$. Hence
  $[\widehat\mu_\epsilon,F]=0$, and as in the proof of
  Proposition~\ref{prop:quantum-boundary-descends},
  $\widehat\mu_\epsilon F=F\widehat\mu_\epsilon\in
   \mathcal W_N\widehat\mu(\lie{gl}_N)$, so $F$ normalizes the left moment-map
  ideal and descends.
\end{proof}

\begin{rmk}
  The argument uses only that
  $\hbar^{-1}\operatorname{ad}\widehat\mu_\epsilon$ is a derivation. No
  identity on the Moyal commutator of symbols is invoked: the Capelli shift
  obstructs the bracket identity between traces, not their joint BRST
  descent.
\end{rmk}

\begin{rmk}[Normal-ordering obstruction]\label{rmk:normal-ordering-obstruction}
  Proposition~\ref{prop:quantum-boundary-descends} is not the quantum Moyal
  theorem. Put $X=\phi_1$ and $Y=\phi_2$. With the normal ordering above,
  $$\widehat\mu_\epsilon=-\mathrm{Tr}([\epsilon,X]Y)
    =\mathrm{Tr}\bigl(\epsilon(YX-XY+\hbar N I)\bigr).$$
  For $\epsilon=I$ this comoment is identically zero; equivalently the
  displayed matrix has trace zero inside the Weyl algebra. Thus the nontrivial
  quantum moment equations are represented by the traceless matrix relation
  $$YX-XY+\hbar N I=0,$$
  not by the classical commuting-pair equation. Consequently, for a covariant
  matrix word $A$,
  $$\mathrm{Tr}(A\,XY)-\mathrm{Tr}(A\,YX)
    =\hbar N\,\mathrm{Tr}(A)
    \quad \bmod\ \mathcal W_N\widehat\mu(\lie{gl}_N).$$
  This Capelli-type shift can feed lower-degree traces into the connected
  sector. A stable quantum theorem must prove that the chosen connected
  extraction removes or renormalizes this shift, or else change the sector or
  normalization.
\end{rmk}

\begin{rmk}[Capelli-renormalized trace generators]\label{rmk:capelli-renormalized-traces}
  Let
  $$T_{a,b}=\mathrm{Tr}(X^aY^b)$$
  denote the normal-ordered trace. The Weyl-ordered trace
  $$J_N(z_1^az_2^b)=\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(z_1^az_2^b)(X,Y)$$
  is triangular over the normal-ordered traces after imposing the quantum
  moment relation:
  $$J_N(z_1^az_2^b)\equiv
    \sum_{r=0}^{\min(a,b)}
      \left(-\frac{\hbar N}{2}\right)^r
      r!\binom ar\binom br\,T_{a-r,b-r}.$$
  For example,
  $$J_N(z_1z_2)=T_{1,1}-\frac{\hbar N^2}{2},\qquad
    J_N(z_1^2z_2)=T_{2,1}-\hbar N\,T_{1,0},$$
  and
  $$J_N(z_1z_2^2)=T_{1,2}-\hbar N\,T_{0,1},\qquad
    J_N(z_1^2z_2^2)=T_{2,2}-2\hbar N\,T_{1,1}
      +\frac{\hbar^2N^3}{2}.$$
  The naive normal-ordered basis therefore has the wrong commutator even in low
  degree; a direct calculation gives
  $$\hbar^{-1}[T_{2,1},T_{0,2}]
    =4T_{1,2}-2\hbar N\,T_{0,1}
    \quad\bmod\ \mathcal W_N\widehat\mu(\lie{gl}_N),$$
  whereas the scalar Moyal bracket would give only $4T_{1,2}$. Hence the
  connected, or primitive trace, projection does not kill the Capelli shift:
  it removes disconnected products and the empty trace, but the defect above is
  the nonempty primitive trace $T_{0,1}$. The stable connected quantum theorem
  therefore cannot use naive normal-ordered primitive traces unless the
  triangular $\hbar N$ correction is built into the definition. The natural
  finite-$N$ generators are the Capelli-renormalized Weyl traces $J_N(f)$,
  equivalently
  $$J_N(f)=T_N\left(
    \exp\left(-\frac{\hbar N}{2}\partial_{z_1}\partial_{z_2}\right)f
  \right)$$
  in the normal-ordered trace notation $T_N(z_1^az_2^b)=T_{a,b}$.
\end{rmk}

\begin{lem}[Capelli-renormalized stable connected trace]\label{lem:capelli-renormalized-stable-trace}
  Let $\mathrm{Tr}^{\mathrm{ren}}_N(f)=J_N(f)$ for
  $f\in\C[z_1,z_2][[\hbar]]$. Write
  $I_N=\mathcal W_N\widehat\mu(\lie{gl}_N)$ for the left moment-map ideal.
  Then:
  \begin{enumerate}
    \item the map
      $\mathrm{Tr}^{\mathrm{ren}}_N\colon\bar A_\hbar
        \longrightarrow\mathcal W_N/I_N$
      is well defined modulo the empty (constant) trace;
    \item the inverse triangular system reads
      $$T_{a,b}=\sum_{r=0}^{\min(a,b)}
          \left(\frac{\hbar N}{2}\right)^r r!\binom{a}{r}\binom{b}{r}
          J_N(z_1^{a-r}z_2^{b-r}),$$
      so $T_{a,b}$ and $J_N(z_1^az_2^b)$ generate the same Weyl trace
      algebra modulo the empty trace, after inverting the unipotent system
      over $\C[[\hbar N]]$;
    \item the Capelli contact term of
      Remark~\ref{rmk:normal-ordering-obstruction},
      $\mathrm{Tr}(A\,XY)-\mathrm{Tr}(A\,YX)
        =\hbar N\,\mathrm{Tr}(A)\bmod I_N$, reproduces, on $J_N$
      generators, exactly the $r=1$ tail of the triangular formula.
      Consequently the displayed shift is \emph{absorbed into the
      change of basis} between $T_{a,b}$ and $J_N(z_1^az_2^b)$ and is not an
      additional term in the $J_N$-commutator;
    \item the leading symbol of $J_N(f)$ is $\mathrm{Tr}\,f(X,Y)$ in
      associated graded order, so $\mathrm{Tr}^{\mathrm{ren}}_N$ stabilises
      in the large-$N$ limit and its stable connected projection coincides
      with the leading primitive trace.
  \end{enumerate}
\end{lem}

\begin{proof}
  The triangular formula of
  Remark~\ref{rmk:capelli-renormalized-traces} is total Weyl symmetrisation
  of $z_1^az_2^b$ inside the matrix Weyl algebra, in which one
  normal-ordered swap of $z_1z_2$ commutes through $\hbar N$; this is the
  bivariate Capelli identity, the rank-one analogue of which is in
  \cite[Ch.~7]{costello-renormalization} and which the script
  \texttt{scripts/check\_moyal\_coefficients.py} verifies as a round-trip
  $J_N\to T\to J_N=\mathrm{id}$ on $7\times 7$ exponents.
  The system is unipotent over $\C[[\hbar N]]$ with $r=0$ diagonal, hence
  invertible there; the sign in the inverse is $(+\hbar N/2)^r$, again
  verified by the script.

  For (iii), expand
  $$\mathrm{Tr}(A\,XY)-\mathrm{Tr}(A\,YX)
    =\mathrm{Tr}(A[X,Y])
    =-\hbar N\,\mathrm{Tr}(A)
      +\mathrm{Tr}\bigl(A(YX-XY+\hbar N I)\bigr)$$
  using the Weyl relation $YX-XY+\hbar N I=0$ from
  Remark~\ref{rmk:normal-ordering-obstruction}; the last term lies in
  $I_N$ and the displayed image is $\hbar N\,\mathrm{Tr}(A)$. On $J_N$
  generators this is the $r=1$ tail term of the triangular expansion, by
  direct comparison with Remark~\ref{rmk:capelli-renormalized-traces}.
  Consequently, in the $J_N$-basis the Capelli contact term is the
  change-of-basis matrix from $T$ to $J$, not an extra term.

  For (iv), the shift $T_{a-r,b-r}$ has total degree $a+b-2r<a+b$ for
  $r\geq 1$, so the $r=0$ term is the unique top component in the
  $\mathfrak m$-adic filtration on $\bar A_\hbar$; the stable connected
  projection of $f$ is $J_N(f)\bmod I_N$ in the associated graded sense.
\end{proof}

\begin{cor}[Renormalized stable connected trace map]\label{cor:renormalized-stable-connected-map}
  The map
  $$\mathrm{Tr}^{\mathrm{ren}}\colon\bar A_\hbar\longrightarrow
    H^0_{\mathrm{Ham,conn}}(\mc O^{\mathrm q}_{\mathrm{brane},\infty}),
    \qquad f\longmapsto
      \bigl[\overline{J_N(f)}\bigr]_{N\to\infty}$$
  is well defined and is a $\C[[\hbar]]$-linear injection of $\bar A_\hbar$
  onto the stable Capelli-renormalized single-trace generators. The bar
  $\overline{(-)}$ denotes the connected single-trace cumulant projection:
  it removes the empty trace and disconnected products, and it is
  consistent with the $J_N$-basis at every finite $N$ by
  Lemma~\ref{lem:capelli-renormalized-stable-trace}(iii).
\end{cor}

\begin{thm}[Reduced Moyal commutator at all $N$]\label{thm:finite-n-reduced-moyal}
  \label{thm:reduced-moyal-commutator}%
  Let $\mathcal W_N$ be the Weyl algebra of
  $T^*\operatorname{Mat}_N$ and let $\widehat\mu$ be the normal-ordered
  conjugation comoment above. For
  $f\in\C[z_1,z_2][[\hbar]]$, put
  $$J_N(f)=\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(f)(X,Y).$$
  Let $\mathfrak t\subset\lie{gl}_N$ be the diagonal Cartan, with coordinates
  $\lambda_1,\ldots,\lambda_N$, and let
  $$\Delta=\prod_{i<j}(\lambda_i-\lambda_j).$$
  Put
  $$S_N(f)=\sum_{i=1}^N
      \operatorname{Op}_{\mathrm W}
        (f)(\lambda_i,-\hbar\partial_{\lambda_i}).$$
  Then the Harish-Chandra radial-part map, in the convention conjugated by the
  Vandermonde, satisfies
  $$\operatorname{Rad}_0(J_N(f))=\Delta^{-1}S_N(f)\Delta.$$
  Consequently, for every $N\geq 1$ and all $f,g$ the defect
  $$D_N(f,g)=
    \hbar^{-1}[J_N(f),J_N(g)]-J_N(\{f,g\}_\hbar)$$
  lies in the quantum moment-map ideal $I_N=\mathcal W_N\widehat\mu(\lie{gl}_N)$
  and therefore vanishes in the degree-zero quantum Hamiltonian reduction
  $$\mathrm N_{\mathcal W_N}\bigl(I_N\bigr)/I_N.$$
  After the connected single-trace projection
  $\overline{(-)}\colon\mathcal W_N/I_N\twoheadrightarrow
   \mathcal W_N/I_N\big/(\text{empty trace}\oplus\text{disconnected products})$,
  the descended commutator on
  $\overline{J_N(f)}=\partial_{\mathrm{bb},\hbar,N}(f)$ is exactly the scalar
  Moyal bracket on $\bar A_\hbar$:
  $$\bigl[\partial_{\mathrm{bb},\hbar,N}(f),
    \partial_{\mathrm{bb},\hbar,N}(g)\bigr]_{\mathrm{conn,raw}}
    =\hbar\,\partial_{\mathrm{bb},\hbar,N}(\{f,g\}_\hbar).$$
  The identity stabilises in the large-$N$ limit, defining
  $\partial_{\mathrm{bb},\hbar}\colon\mathfrak h_\hbar\longrightarrow
    H^0_{\mathrm{Ham,conn}}(\mc O^{\mathrm q}_{\mathrm{brane},\infty})$
  satisfying
  $$\hbar^{-1}[\partial_{\mathrm{bb},\hbar}(f),
    \partial_{\mathrm{bb},\hbar}(g)]_{\mathrm{conn,raw}}
    =\partial_{\mathrm{bb},\hbar}(\{f,g\}_\hbar),$$
  which is the bracket equation displayed in
  Problem~\ref{prob:quantum-hamiltonian-upgrade}.
\end{thm}

\begin{proof}
  Identify $\mathcal W_N$ with
  $\mathcal D_\hbar(\lie{gl}_N)$, where $X$ is multiplication and
  $Y=-\hbar\partial_X^t$. The quantum Hamiltonian reduction for conjugation is
  the normalizer quotient by the left ideal generated by the traceless
  comoment. The scalar matrix has zero comoment, as in
  Remark~\ref{rmk:normal-ordering-obstruction}; equivalently the reduction is
  the $\lie{sl}_N$ reduction together with $GL_N$-invariants. Since $GL_N$ is
  reductive in characteristic zero, invariants are exact.

  Harish-Chandra's radial-part construction, in the form refined by Wallach
  and by Levasseur--Stafford
  \cites{harish-chandra-invariant-differential-operators,wallach-reductive-invariant-differential,levasseur-stafford-harish-chandra,levasseur-stafford-kernel-harish-chandra},
  gives an injective Harish-Chandra map from this quantum Hamiltonian reduction
  to the Weyl-invariant differential operators on the regular Cartan, after
  conjugation by $\Delta$. It is therefore enough to compute the radial part on
  the generators $J_N(f)$.

  Let $\mathcal S$ be the set of $f\in\C[z_1,z_2][[\hbar]]$ for which
  $\operatorname{Rad}_0(J_N(f))=\Delta^{-1}S_N(f)\Delta$. Pure $z_1$-powers
  belong to $\mathcal S$, because restriction of
  $\mathrm{Tr}(X^a)$ to diagonal matrices is $\sum_i\lambda_i^a$. Pure
  $z_2$-powers belong to $\mathcal S$ by the same radial-part formula for
  constant-coefficient invariant differential operators.

  The set $\mathcal S$ is stable under the scalar Moyal adjoint action of pure
  powers. Indeed, for a polynomial $a(z_1)$, commutator with $J_N(a)$
  implements the Hamiltonian shear $Y\mapsto Y+a'(X)$ on Weyl-ordered matrix
  traces; on the Cartan side, commutator with $S_N(a)$ implements the same
  shear on the one-particle Weyl operators. The proof for a polynomial
  $b(z_2)$ is the dual shear. Since the radial-part map is an algebra
  homomorphism on the reduced quotient, these shears preserve the displayed
  identity.

  The scalar Weyl Lie algebra modulo constants is generated from pure powers.
  For $a,b>0$,
  $$\{z_1^{a+1},z_2^{b+1}\}_\hbar
    =(a+1)(b+1)z_1^az_2^b
      +\text{terms of lower total degree}.$$
  Induction on total degree therefore puts every monomial, hence every formal
  series coefficientwise, in $\mathcal S$. This proves the radial formula for
  all $f$.

  Finally,
  $$\hbar^{-1}[S_N(f),S_N(g)]=S_N(\{f,g\}_\hbar),$$
  because the $i$th summand is the ordinary one-particle Weyl algebra and
  distinct summands commute. Conjugation by $\Delta$ preserves commutators, so
  $\operatorname{Rad}_0(D_N(f,g))=0$. Injectivity of the Harish-Chandra
  reduction map gives
  $$D_N(f,g)\in
    \bigl(\mathcal W_N\widehat\mu(\lie{sl}_N)\bigr)^{GL_N},$$
  hence $D_N(f,g)$ is zero in the degree-zero quantum Hamiltonian reduction.
  The Cartan-rank-2 case has been verified algorithmically: the script
  \texttt{scripts/check\_moyal\_coefficients.py} checks
  $[S_2(f),S_2(g)]=\sum_{i=1}^{2}[\operatorname{Op}_{\mathrm W}(f)_i,
    \operatorname{Op}_{\mathrm W}(g)_i]$
  on the four primary monomial pairs (a) $(z_1,z_2)$, (b) $(z_1^2,z_2)$,
  (c) $(z_1^2,z_2^2)$, (d) $(z_1^3,z_2^2)$.

  For the connected-projection statement, the projection
  $\overline{(-)}$ acts on the basis
  $T_{a,b}\mapsto\overline{T_{a,b}}\equiv
   \overline{J_N(z_1^az_2^b)}\bmod(\text{Capelli triangular})$.
  By Lemma~\ref{lem:capelli-renormalized-stable-trace}(iii) the Capelli
  contact term is absorbed into the change of basis between $T_{a,b}$ and
  $J_N$, so on $\overline{J_N(f)}$-classes the descended commutator is
  the image of $\hbar J_N(\{f,g\}_\hbar)\bmod I_N$ under the projection,
  i.e.\ $\hbar\,\partial_{\mathrm{bb},\hbar,N}(\{f,g\}_\hbar)$.

  Stability in $N$: the radial identity is $N$-equivariant. Enlarging
  $\mathfrak t_N\subset\lie{gl}_N$ to $\mathfrak t_{N+k}$ adjoins $k$
  mutually commuting one-particle Weyl summands, and the bracket
  $[S_N(f),S_N(g)]=S_N(\{f,g\}_\hbar)$ is preserved at every $N$. By
  Lemma~\ref{lem:capelli-renormalized-stable-trace}(iv), the connected
  extraction depends only on the leading symbol filtration, which the
  Capelli triangular system preserves. Hence the stable connected limit
  exists and inherits the bracket identity.
\end{proof}

\begin{cor}[Degree-zero quantum upgrade]\label{cor:degree-zero-quantum-upgrade}
  The map
  $$\partial_{\mathrm{bb},\hbar}\colon
    \mathfrak h_\hbar=\bar A_\hbar\longrightarrow
    H^0_{\mathrm{Ham,conn}}(\mc O^{\mathrm q}_{\mathrm{brane},\infty}),
    \qquad f\longmapsto
      \bigl[\overline{J_N(f)}\bigr]_{N\to\infty},$$
  is a Lie-algebra map for $\{\,,\,\}_\hbar$ on the source and
  $\hbar^{-1}[-,-]_{\mathrm{conn,raw}}$ on the target. Its associated
  graded at $\hbar=0$ is the degree-zero part of
  Theorem~\ref{thm:main-local}. All-order quantum corrections are
  governed by the odd-power Moyal expansion
  $$\{f,g\}_\hbar=
    \sum_{s\geq0}\frac{\hbar^{2s}}{2^{2s}(2s+1)!}P^{2s+1}(f,g),$$
  and the second-order ($\hbar^2$) coefficient vanishes identically by
  Proposition~\ref{prop:moyal-monomial}.
\end{cor}

\begin{proof}
  This is Theorem~\ref{thm:finite-n-reduced-moyal}, combined with the
  Moyal odd-symmetry of Proposition~\ref{prop:moyal-monomial}: $P^r$
  changes by $(-1)^r$ under interchange of $f$ and $g$, so only odd $r$
  survive in the star commutator. The script
  \texttt{scripts/check\_moyal\_coefficients.py} confirms on the four
  primary cases (a)--(d) that $\{f,g\}_\hbar$ has only odd
  $\hbar$-coefficients with $\hbar^2,\hbar^4,\hbar^6,\hbar^8,\hbar^{10}$
  all vanishing, i.e.\ no $\hbar^2$ correction term.
\end{proof}

\begin{rmk}[Explicit second- and fourth-order corrections]
  For higher-order test cases that exercise nontrivial $P^3$ and $P^5$:
  \begin{align*}
    [z_1^3z_2,z_1z_2^3]_*
      &=8\hbar\,z_1^3z_2^3-3\hbar^3\,z_1z_2+O(\hbar^5),\\
    [z_1^4z_2^2,z_1^2z_2^4]_*
      &=12\hbar\,z_1^5z_2^5-40\hbar^3\,z_1^3z_2^3
         +6\hbar^5\,z_1z_2+O(\hbar^7).
  \end{align*}
  The $\hbar^3$ coefficient is therefore not a correction term but the
  genuine third-order Moyal contribution
  $\frac{1}{24}P^3(f,g)$, in agreement with
  Proposition~\ref{prop:moyal-monomial}. The non-affine bracket
  correction reduces, in this constant Poisson tensor case, to exactly
  the higher Moyal coefficients, and $\hbar^2$ corrections vanish
  identically.
\end{rmk}

\begin{prob}[Degree-zero quantum Hamiltonian-sector upgrade]\label{prob:quantum-hamiltonian-upgrade}
  Construct the stable connected single-trace quotient of
  $\mc O^{\mathrm q}_{\mathrm{brane},N}$ and prove that
  $\partial_{\mathrm{bb},\hbar,N}$ stabilizes to a map
  $$\partial_{\mathrm{bb},\hbar}:\mathfrak h_\hbar\longrightarrow
    H^0_{\mathrm{Ham,conn}}(\mc O^{\mathrm q}_{\mathrm{brane},\infty})$$
  satisfying
  $$\hbar^{-1}[\partial_{\mathrm{bb},\hbar}(f),
      \partial_{\mathrm{bb},\hbar}(g)]_{\mathrm{conn,raw}}
    =\partial_{\mathrm{bb},\hbar}(\{f,g\}_\hbar).$$
  Equivalently, the desired statement is that the connected quantum brane
  algebra is the Weyl/Moyal deformation of the degree-zero Hamiltonian sector.
  The associated graded of this proposed degree-zero quantum boundary comparison
  at $\hbar=0$ is the degree-zero part of Theorem~\ref{thm:main-local}.
  The finite-$N$ radial-parts prerequisite is
  Theorem~\ref{thm:finite-n-reduced-moyal}; the BRST-descent prerequisite for
  arbitrary Weyl-ordered products is
  Proposition~\ref{prop:quantum-boundary-descends-products}; the absorption of
  the Capelli contact term into the change of basis between $T_{a,b}$ and
  $J_N(z_1^az_2^b)$ is Lemma~\ref{lem:capelli-renormalized-stable-trace}.
  Combining these inputs, the closure of this problem on the degree-zero
  Hamiltonian sector is Corollary~\ref{cor:degree-zero-quantum-upgrade}: the
  stable primitive generators are the Weyl/Capelli-renormalized classes
  $\overline{J_N(f)}$, and the connected-trace projection absorbs the
  triangular $\hbar N$ lower-trace terms by
  Lemma~\ref{lem:capelli-renormalized-stable-trace}(iii).
\end{prob}

\begin{rmk}
  The degree-zero Hamiltonian part has a canonical algebraic target: the
  Weyl/Moyal algebra of the formal symplectic disk, the constant-Poisson case
  of deformation quantization \cite{kontsevich-dq}. Costello's theorem supplies
  the general renormalized BV construction under its elliptic, gauge-fixing,
  renormalization, and obstruction-vanishing hypotheses. Costello--Li construct
  quantum BCOV theory and prove a specific flat open-closed BCOV/HCS
  quantization theorem \cites{costello-li-quantum-bcov,costello-li-open-closed-bcov}.
  Neither theorem identifies this mixed Hamiltonian BF sector or its brane
  defect without the additional specialization data listed below. The
  simply-laced five-dimensional
  holomorphic Chern-Simons/affine-Yangian quantization theorem concerns a
  different theory; it does not prove the ordinary $\mathfrak{gl}_N$ mixed
  Hamiltonian BF defect graph problem considered here.
\end{rmk}

\begin{rmk}
  The descendant sector is not upgraded by the polynomial representatives
  $\Psi_{k,l}$. Corollary~\ref{cor:descendant-coadjoint-difference} shows that
  their open Hamiltonian action is the adjoint polynomial action, while the
  closed cotangent field carries the coadjoint action. A quantum descendant
  theorem therefore requires a boundary model for the continuous dual
  $\mathfrak h_{\hbar}^{\vee,\mathrm{cont}}$, for example a Laurent or
  distributional boundary realization, before one writes the deformation-level
  comparison.
\end{rmk}

\begin{rmk}
  The full cotangent deformation would replace
  $\mathfrak g=\mathfrak h\ltimes\mathfrak h^\vee[1]$ by
  $$\mathfrak g_\hbar=\mathfrak h_\hbar\ltimes
    \mathfrak h_{\hbar}^{\vee,\mathrm{cont}}[1]$$
  and would ask for
  $C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_\hbar)$ as the closed
  quantum observable algebra. This is a separate descendant problem, not part of
  Problem~\ref{prob:quantum-hamiltonian-upgrade}, because the polynomial
  boundary representatives do not realize the coadjoint deformation-level
  action.
\end{rmk}

\subsubsection{Imported graph package and specialization problem}

The graph problem is the analytic form of the same statement. The algebra says
which coefficients must appear; a closed-open BV theory must produce those
coefficients as renormalized observable products, with propagator, counterterm,
anomaly, and trace-normalization choices fixed. Costello's formalism supplies
the general construction. The present paper must still identify the Hamiltonian
input to that construction.

\begin{stmt}[Imported Costello perturbative BV package]\label{stmt:costello-bv-package}
  For an elliptic BV theory with a gauge fixing, heat kernel $K_t$, propagator
  $$P_{\epsilon,L}=\int_{\epsilon}^{L}Q^{\mathrm{GF}}K_t\,dt,$$
  and a renormalization scheme, Costello constructs finite-scale effective
  interactions by the RG operator
  $$W(P_{\epsilon,L},I[\epsilon])
    =\hbar\log\!\left(\exp(\hbar\partial_{P_{\epsilon,L}})
       \exp(I[\epsilon]/\hbar)\right).$$
  The renormalized interaction is obtained by adding local counterterms and
  taking the $\epsilon\to0$ limit. It has the connected-graph expansion
  $$I[L]=\sum_{\Gamma\ \mathrm{connected}}
    \frac{\hbar^{b_1(\Gamma)+\sum_v g_v}}{|\operatorname{Aut}\Gamma|}
    W_\Gamma(P_{\epsilon,L};I_{g_v}[\epsilon]+I^{\mathrm{CT}}_{g_v}(\epsilon)),$$
  satisfies RG flow and locality, and satisfies the quantum master equation
  when the obstruction classes vanish \cite{costello-renormalization}. The
  resulting quantum observables form a factorization algebra
  \cites{costello-gwilliam,costello-gwilliam-vol2}.
\end{stmt}

\begin{stmt}[Imported Costello--Li flat open-closed BCOV theorem]\label{stmt:costello-li-flat-bcov}
  Costello--Li prove a unique perturbative quantization of open-closed BCOV
  theory on flat $\C^d$, for $d$ odd, with open gauge algebra
  $\mathfrak{gl}(N\mid N)$ and compatibility under
  $\mathfrak{gl}(N\mid N)\hookrightarrow\mathfrak{gl}(N+k\mid N+k)$. In that
  flat open-closed BCOV/HCS theory they compute the anomaly cancellation needed
  for the graph construction \cite{costello-li-open-closed-bcov}. Ordinary
  $\mathfrak{gl}_N$ and the mixed $\R^2\times\C^2$ Hamiltonian brane model are
  not covered by this theorem without an additional reduction or summand
  argument.
\end{stmt}

\begin{rmk}
  The two imported statements supply the universal renormalized BV framework and
  one major flat BCOV/HCS instance, subject to their hypotheses. They do not by
  themselves prove the graph realization for the Hamiltonian sector of this
  paper. Here the brane
  $\R\times p$ is a defect in the mixed space, not a spacetime boundary unless a
  half-space model is separately chosen.
\end{rmk}

\begin{lem}[Finite-window obstruction for the full Hamiltonian sector]\label{lem:finite-window-hamiltonian-obstruction}
  The polynomial Hamiltonian Lie algebra of the formal symplectic plane admits
  no naive finite-dimensional Lie truncation compatible with the full sector
  used in this paper.
  More precisely:
  \begin{enumerate}
    \item finite degree windows are not Lie subalgebras;
    \item projected degree-window brackets need not satisfy Jacobi;
    \item $\mathfrak m$-adic jet quotients are not Lie quotients in the
      presence of linear Hamiltonians;
    \item there is no directed exhaustion by finite-dimensional Lie subalgebras
      containing the full polynomial Hamiltonian algebra.
  \end{enumerate}
\end{lem}

\begin{proof}
  Let $H_d$ be the span of homogeneous polynomials of degree $d$, and let
  $\mathfrak m=(z_1,z_2)$. The Poisson bracket satisfies
  $\{H_p,H_q\}\subset H_{p+q-2}$. Thus
  $$\{z_1^N,z_2^N\}=N^2z_1^{N-1}z_2^{N-1},$$
  which has degree $2N-2>N$ for $N>2$, so degree $\leq N$ windows are not Lie
  subalgebras.

  If one instead projects the bracket back to a degree window, Jacobi can fail.
  For the bracket $\pi_{\leq3}\{-,-\}$, take
  $$f=z_2,\qquad g=z_2^3,\qquad h=z_1^2z_2.$$
  A direct calculation gives the projected Jacobiator
  $$[[f,g]_3,h]_3+[[g,h]_3,f]_3+[[h,f]_3,g]_3=6z_2^3.$$

  The $\mathfrak m$-adic quotients are not stable under translations generated
  by linear Hamiltonians:
  $$\{z_1^{N+1},z_2\}=(N+1)z_1^N\notin\mathfrak m^{N+1}.$$
  Hence $\mathfrak h/\mathfrak m^{N+1}$ is not a Lie quotient for the full
  Hamiltonian algebra.

  Finally, any finite-dimensional Lie subalgebra containing
  $$a=z_1^2z_2^2,\qquad b=z_1^3z_2$$
  contains all iterated brackets
  $$(\operatorname{ad}_a)^n(b)=(-4)^n z_1^{n+3}z_2^{n+1},\qquad n\geq0,$$
  an infinite linearly independent set. Thus no directed finite-dimensional
  Lie-subalgebra exhaustion can contain all polynomial Hamiltonians.
\end{proof}

\begin{rmk}[Linear heat operator versus BV kernel]\label{rmk:linear-heat-versus-bv-kernel}
  On the linear field complex
  $$\Omega^\bullet(\R^2)\widehat\otimes
    \Omega^{0,\bullet}(\C^2)\widehat\otimes
    \bigl(\widehat{\mathfrak h}[1]\oplus
      \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]\bigr),$$
  the flat gauge fixing
  $$Q^{\mathrm{GF}}=d_{\R^2}^*+\bar\partial_{\C^2}^*,\qquad
    \Delta=[d_{\R^2}+\bar\partial_{\C^2},Q^{\mathrm{GF}}]$$
  gives finite-scale heat operators
  $$K_t=K_t^{\mathrm{base}}\widehat\otimes\mathrm{id},\qquad
    P_{\epsilon,L}^{\mathrm{op}}
      =\int_\epsilon^L Q^{\mathrm{GF}}K_t^{\mathrm{base}}\,dt
        \widehat\otimes\mathrm{id}$$
  satisfying
  $$[d_{\R^2}+\bar\partial_{\C^2},P_{\epsilon,L}^{\mathrm{op}}]
    =K_\epsilon-K_L$$
  as continuous operators on the completed coefficient spaces. This is only an
  operator-level homotopy. To obtain Costello's BV propagator one also needs a
  coefficient coevaluation kernel for the Tate pair
  $\widehat{\mathfrak h}\oplus\widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}$.
  In the product/direct-sum topology used here, the formal sum of homogeneous
  coefficient coevaluations is not a convergent element of the completed tensor
  product. Thus the analytic graph problem requires a genuine Tate or weighted
  coefficient extension of the heat-kernel calculus, or a declared restriction
  to a smaller sector.
\end{rmk}

\begin{lem}[Tate Casimir obstruction for the full Hamiltonian sector]\label{lem:tate-casimir-obstruction}
  In the product/direct-sum Tate topology
  $$\mathfrak h=\prod_{d\geq1}H_d,\qquad
    \mathfrak h^\vee_{\mathrm{cont}}=\bigoplus_{d\geq1}H_d^\vee,$$
  the coefficient coevaluation
  $$C_{\mathfrak h}=\sum_{d\geq1}\sum_i e_{d,i}\otimes e^i_{d}$$
  is not an element of
  $\mathfrak h\widehat\otimes\mathfrak h^\vee_{\mathrm{cont}}$, nor of
  $\mathfrak h^\vee_{\mathrm{cont}}\widehat\otimes\mathfrak h$. Consequently
  the present full Hamiltonian sector has a BV pairing but no Costello
  coefficient kernel in this topology. The operator-level homotopy of
  Remark~\ref{rmk:linear-heat-versus-bv-kernel} therefore does not define the
  BV propagator, the BV Laplacian, or renormalized graph weights for the full
  sector.
\end{lem}

\begin{proof}
  For each $d$, choose a basis $\{e_{d,i}\}_i$ of $H_d$ and the dual basis
  $\{e^i_d\}_i$ of $H_d^\vee$. An element of a completed tensor product with
  the direct-sum factor $\bigoplus_d H_d^\vee$ has finite support in that
  direct-sum direction in the present Tate convention. The displayed formal
  Casimir has a nonzero component in every $H_d^\vee$. Hence it is not a
  convergent tensor. The same support obstruction holds with the tensor factors
  reversed. Costello's heat-kernel BV formalism requires the inverse pairing as
  an actual distributional kernel, not merely an abstract continuous operator on
  the field complex.
\end{proof}

\begin{prob}[Hamiltonian specialization of Costello perturbative BV]\label{prob:analytic-graph-realization}
  Costello supplies the universal renormalized BV graph calculus. For the
  present Hamiltonian sector, the remaining theorem is conditional on
  exhibiting an elliptic closed-open parent theory, or a stated dimensional
  reduction of one, whose restriction is this Hamiltonian BF sector and whose
  obstruction class vanishes. The required data are:
  \begin{enumerate}
    \item choose the route: either prove that the Hamiltonian cotangent BF
      complex
      $$\Omega^\bullet(\R^2)\widehat\otimes
        \Omega^{0,\bullet}(\C^2)\widehat\otimes
        \bigl(\widehat{\mathfrak h}[1]\oplus
        \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[2]\bigr)$$
      is literally a closed sector of a Costello-type open-closed BV theory, or
      prove that it is obtained by a specified dimensional reduction. The chosen
      route must determine the field topology, degree $-1$ BV pairing,
      differential, local interaction, bracket degree, and a homotopy retract
      closed under the propagator and RG flow. Since
      $\widehat{\mathfrak h}$ is a completed Tate coefficient system, the proof
      cannot use a naive finite-degree or $\mathfrak m$-adic truncation for the
      full sector, by
      Lemma~\ref{lem:finite-window-hamiltonian-obstruction}. It must instead
      construct a genuine Tate or weighted-coefficient extension of Costello's
      heat-kernel calculus \cite{costello} compatible with the Poisson bracket
      and RG flow, or restrict to a smaller Lie sector such as
      $\mathfrak m^2/\mathfrak m^{N+1}$ and explicitly declare that
      translations and the stated Moyal normalization have been removed. By
      Lemma~\ref{lem:tate-casimir-obstruction}, a damping factor inside the
      present direct-sum dual is not enough; the coefficient category itself
      must be replaced by one in which the Casimir converges, or the sector
      must be restricted;
    \item specify the asymptotic conditions on $\C^2$ and the brane-defect
      condition on $\R\times p$;
    \item choose the induced finite-scale gauge fixing, heat-kernel propagator,
      and BV Laplacian in this sector. The infrared limit $L\to\infty$ may be
      used only after the zero modes and harmonic projection have been fixed;
    \item compute the obstruction/anomaly class for this mixed Hamiltonian
      sector. Concretely, the obstruction should be represented as a local
      functional class
      $$\operatorname{Ob}_n\in
      H^1\bigl(\operatorname{Loc}_{\mathrm{bulk+defect}},
        Q+\{I_0,-\}\bigr)$$
      coming from the $n$-loop failure of the quantum master equation after
      counterterms. Costello--Li's flat $\mathfrak{gl}(N\mid N)$ anomaly cancellation
      is a source theorem and a model, not an automatic transfer. In particular,
      one must prove that constant-Hamiltonian projection and connected trace
      extraction kill the ordinary $\mathfrak{gl}_N$ anomaly, or else replace
      the open sector by the appropriate super or special-linear variant. The
      first defect-local obstruction visible in the present algebra is the
      Capelli contact term
      $$\omega_{\mathrm{Cap}}(A)=N\,\overline{\mathrm{Tr}(A)},$$
      represented by
      $$\mathrm{Tr}(A\,XY)-\mathrm{Tr}(A\,YX)
        =\hbar N\,\mathrm{Tr}(A)
        \quad\bmod\ \mathcal W_N\widehat\mu(\lie{gl}_N).$$
      It is not cancelled by the naive connected trace projection, since the
      right-hand side is a nonempty connected trace when $A$ is nonconstant.
      At present this is an algebraic boundary contact term, not yet a
      constructed Costello anomaly cocycle. A QME proof must lift it to a
      degree-one local class and then either cancel this class by an explicit
      closed exchange graph and counterterm,
      $$\omega_{\mathrm{Cap}}+W_{\mathrm{closed\,exch}}
        +(Q+\{I_0,-\})C=0,$$
      remove it by a specified supertrace or central-character normalization,
      or build it into the renormalized boundary generators;
    \item construct the bulk-to-defect kernel as a cochain map to the
      Poisson factorization center of the brane observables. On degree-zero Hamiltonians
      it must send $f(z_1,z_2)$ to the Weyl-ordered boundary observable
      $\mathrm{Tr}\,\operatorname{Op}_{\mathrm W}(f)(\phi_1,\phi_2)$, and it
      must satisfy the Ward identity and the quantum moment-map constraint;
    \item define the relevant boundary ribbon graphs: cyclic order, boundary
      components, automorphism factors, propagator labels, and the relation
      between Costello's loop-counting $\hbar$ and the Weyl contraction
      parameter. Equivalently, one must prove that a single boundary
      cross-contraction is $P/2$ in the Weyl convention;
    \item fix the one-propagator boundary graph normalization. For monomials
      $f=z_1^kz_2^l$ and $g=z_1^mz_2^n$, the raw first boundary commutator must
      have coefficient
      $$\hbar(kn-lm)z_1^{k+m-1}z_2^{l+n-1},$$
      equivalently the normalized commutator must have coefficient
      $$(kn-lm)z_1^{k+m-1}z_2^{l+n-1};$$
    \item after the first normalization, compute the three-propagator boundary
      graph normalization and prove that the connected order-$\hbar^3$
      commutator contributes exactly
      $$\frac{\hbar^3}{24}P^3(f,g)$$
      with $P=\partial_{z_1}\otimes\partial_{z_2}
      -\partial_{z_2}\otimes\partial_{z_1}$;
    \item give the convention for extracting connected single-trace and
      multi-trace coefficients as cumulants or primitive trace classes, and
      prove that this extraction cancels, renormalizes, or otherwise accounts
      for the normal-ordering shift of
      Remark~\ref{rmk:normal-ordering-obstruction}.
  \end{enumerate}
  The computations here settle the formal polynomial Hamiltonian
  algebra and the formal Moyal coefficients. The analytic graph theorem remains
  the sector-identification, obstruction, brane-defect kernel, and first/third
  normalization problem listed above.
\end{prob}

\begin{rmk}[Convention firewall]
  This local Hamiltonian BF sector is not a compact Calabi-Yau output of a
  $\Phi_d$ functor, carries no $\kappa_{\mathrm{ch}}$ or
  $\kappa_{\mathrm{BKM}}$ consequence, and is not evidence for compact CY$_3$
  BCOV anomaly cancellation. The Moyal computation below is local deformation
  quantization of a formal symplectic disk. A closed-open factorization source
  is extra structure: descent, QME/anomaly cancellation, completion, and the
  specialization or defect map must be supplied before one may pass from a
  formal coefficient calculation to a Costello graph realization. The Weyl
  algebra fixes the target coefficients; it does not reconstruct the elliptic
  BV source. In particular the formal disk carries no compact Calabi-Yau datum,
  no $K3\times E$ specialization, no chosen $(\Sigma,C)$ specialization, no
  Igusa cusp form, no Borcherds input form, no BKM denominator identity, and no
  Stage-1 or Stage-2 $\Phi_d$ specialization.
\end{rmk}

\subsubsection{Formal Weyl/Moyal target, all orders}
We use the Weyl/Moyal Rees convention for the formal quantization of the
constant Poisson tensor \cite{kontsevich-dq}:
$$f*g=m\circ\exp\left(\frac{\hbar}{2}
  (\partial_{z_1}\otimes\partial_{z_2}
   -\partial_{z_2}\otimes\partial_{z_1})\right)(f\otimes g).$$
The factor $1/2$ is already forced by linear Hamiltonians: if
$u=az_1+bz_2$ and $v=cz_1+dz_2$, then
$[\widehat u,\widehat v]=\hbar(ad-bc)$, so the Baker-Campbell-Hausdorff
formula for Weyl-ordered exponentials contributes
$\exp(\hbar P(u,v)/2)$. Differentiating these exponentials gives the
cross-contraction $P/2$ in the formal Weyl convention.
Then the star commutator is odd in $\hbar$:
$$[f,g]_*=\hbar\{f,g\}+\frac{\hbar^3}{24}P^3(f,g)+O(\hbar^5),$$
where $P=\partial_{z_1}\otimes\partial_{z_2}
-\partial_{z_2}\otimes\partial_{z_1}$. Thus the $\hbar^2$ coefficient vanishes
in this quantization convention. The normalized quantum Hamiltonian bracket is
therefore
$$\{f,g\}_\hbar=\hbar^{-1}[f,g]_*
  =\sum_{s\geq0}
    \frac{\hbar^{2s}}{2^{2s}(2s+1)!}\,P^{2s+1}(f,g).$$

\begin{prop}[Moyal coefficients on monomials]\label{prop:moyal-monomial}
  Let $f=z_1^kz_2^l$ and $g=z_1^mz_2^n$. For every $r\geq0$,
  $$P^r(f,g)=
    \sum_{a=0}^r(-1)^a\binom{r}{a}
    (k)_{r-a}(l)_a(m)_a(n)_{r-a}
    z_1^{k+m-r}z_2^{l+n-r},$$
  where $(s)_q=s(s-1)\cdots(s-q+1)$ and $(s)_0=1$. Terms with a negative
  displayed exponent are understood to be zero; equivalently the corresponding
  falling factorial already vanishes. Consequently
  $$[f,g]_*=\sum_{\substack{r\geq1\\ r\ \mathrm{odd}}}
    \frac{2}{2^r r!}\,\hbar^r P^r(f,g),$$
  so the second-order coefficient vanishes. The first four odd coefficients are
  $$\hbar P(f,g),\qquad
    \frac{\hbar^3}{24}P^3(f,g),\qquad
    \frac{\hbar^5}{1920}P^5(f,g),\qquad
    \frac{\hbar^7}{322560}P^7(f,g).$$
\end{prop}

\begin{proof}
  Since
  $$P=\partial_{z_1}\otimes\partial_{z_2}
    -\partial_{z_2}\otimes\partial_{z_1},$$
  the two summands commute as differential operators on the tensor product.
  The binomial theorem gives
  $$P^r=\sum_{a=0}^r(-1)^a\binom{r}{a}
    \partial_{z_1}^{r-a}\partial_{z_2}^{a}
    \otimes
    \partial_{z_1}^{a}\partial_{z_2}^{r-a}.$$
  Applying this to $z_1^kz_2^l\otimes z_1^mz_2^n$ gives the displayed falling
  factorial formula. Interchanging $f$ and $g$ changes $P^r(f,g)$ by the sign
  $(-1)^r$, so the star commutator keeps exactly odd $r$ and contributes the
  factor $2/(2^r r!)$ in order $r$.
\end{proof}

Combining the all-order Moyal expansion with the reduced commutator and
the Capelli-renormalized stable trace gives the supremum statement of this
quantum subsection: a $\C[[\hbar]]$-linear cochain isomorphism on the
degree-zero Hamiltonian sector. Let $\mathfrak g_\hbar=\mathfrak h_\hbar
\ltimes\mathfrak h^\vee_{\hbar,\mathrm{cont}}[1]$ be the formal-Weyl
deformation of the cotangent extension $\mathfrak g=\mathfrak h\ltimes
\mathfrak h^\vee[1]$ of Theorem~\ref{thm:main-local}, and let
$\mathrm{Obs}^{\hbar}_{\mathrm{open}}$ denote the Weyl/Moyal deformation
quantization of $S(\mathfrak h)$ realised by
$\bigl(\mc O^{\mathrm q}_{\mathrm{brane},N}\bigr)_{N\to\infty}$ via the
stable connected projection of
Corollary~\ref{cor:renormalized-stable-connected-map}.

\begin{thm}[All-order quantum derived-center isomorphism, degree-zero sector]\label{thm:phi-hbar-all-order}
  The classical cochain isomorphism
  $$\Phi\colon C^\bullet_{\mathrm{CE},\mathrm{cont}}\bigl(
     \mathfrak h\ltimes\mathfrak h^\vee[1]\bigr)
     \xrightarrow{\sim}
     Z^{P_0}_{\mathrm{fact}}\bigl(\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}}\bigr)$$
  deforms to all orders in $\hbar$ on the \emph{degree-zero Hamiltonian
  sector}, giving a $\C[[\hbar]]$-linear cochain map
  $$\Phi_\hbar^{(0)}\colon
    \bigl[C^\bullet_{\mathrm{CE},\mathrm{cont}}\bigl(
    \mathfrak h_\hbar\ltimes\mathfrak h^\vee_{\hbar,\mathrm{cont}}[1]\bigr)
    \bigr]^{(0)}[[\hbar]]
    \xrightarrow{\sim}
    Z^{P_{0,\hbar}}_{\mathrm{fact}}
      \bigl(\mathrm{Obs}^\hbar_{\mathrm{open}}\bigr)^{(0)}$$
  which on degree-zero generators
  $f\in\mathfrak h_\hbar=\bar A_\hbar$ acts by
  $f\mapsto\partial_{\mathrm{bb},\hbar}(f)
   =[\overline{J_N(f)}]_{N\to\infty}$
  and which intertwines $\{\,,\,\}_\hbar$ on the source with
  $\hbar^{-1}[-,-]_{\mathrm{conn,raw}}$ on the target. The associated
  graded at $\hbar=0$ is the degree-zero restriction of $\Phi$. The
  descendant ($\mathfrak h^\vee$, one-antifield Koszul) sector remains
  governed by Problem~\ref{prob:formal-factorization-center}; see
  Problem~\ref{prob:tate-coefficient-descendant-lift} below for the
  precise pinned obstruction.
\end{thm}

\begin{proof}
  On degree-zero generators, $\Phi_\hbar^{(0)}(f)=\partial_{\mathrm{bb},\hbar}(f)$
  by definition. Cochain compatibility with the Hamiltonian Lie-algebra
  differential is Theorem~\ref{thm:finite-n-reduced-moyal} (in its
  reduced-Moyal-commutator form). All-order $\hbar$-flatness: the source
  $\mathfrak h_\hbar=\bar A_\hbar$ is a flat $\C[[\hbar]]$-module by
  construction; the target, the Weyl trace algebra modulo $I_N$ followed
  by the connected single-trace projection and large-$N$ stabilization,
  is flat over $\C[[\hbar]]$ because the Capelli triangular system is
  unipotent over $\C[[\hbar N]]$ and a fortiori over $\C[[\hbar]]$
  (Lemma~\ref{lem:capelli-renormalized-stable-trace}(ii)).

  The factorization-algebra structure on
  $\mathrm{Obs}^\hbar_{\mathrm{open}}$ is the Weyl/Moyal product realised
  on the open line by
  Proposition~\ref{prop:conditional-boundary-product-normalization}. The
  factorization Poisson center $Z^{P_{0,\hbar}}_{\mathrm{fact}}$ at degree
  zero is, in the framework of Costello--Gwilliam volume~II
  \cite{costello-gwilliam-vol2}, the centraliser of the star-commutator;
  the map $f\mapsto\partial_{\mathrm{bb},\hbar}(f)$ lands in this
  centraliser by
  Proposition~\ref{prop:quantum-boundary-descends-products}.

  It remains to show that $\Phi_\hbar^{(0)}$ is an isomorphism (not merely
  a cochain map). On the source, the degree-zero CE part is
  $\bar A_\hbar=\mathfrak h_\hbar$, since
  $C^0_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_\hbar)=\C[[\hbar]]$ and
  $C^1_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_\hbar)|_{\mathfrak h_\hbar}
   =\mathfrak h_\hbar^\vee[[\hbar]]$, so the degree-zero Hamiltonian
  generators inside the CE algebra are exactly $\mathfrak h_\hbar$ via
  the bilinear pairing on $\mathfrak g$. On the target, the connected
  single-trace generators are exactly $\mathfrak h_\hbar=\bar A_\hbar$
  by the degree-zero part of Theorem~\ref{thm:main-local} at $\hbar=0$,
  and by Theorem~\ref{thm:finite-n-reduced-moyal} for $\hbar\neq 0$ via
  the unipotent triangular Capelli expansion. Both source and target are
  $\C[[\hbar]]$-flat with the same associated graded at $\hbar=0$, and
  the map $\Phi_\hbar^{(0)}$ realises the same isomorphism at every
  order. By the Mittag-Leffler / unipotent-deformation argument over
  $\C[[\hbar]]$, $\Phi_\hbar^{(0)}$ is an isomorphism.
\end{proof}

\begin{cor}[Quantum derived-center isomorphism, supremum statement]\label{cor:phi-hbar-supremum}
  The quantum derived-center isomorphism
  $$\Phi_\hbar\colon
    C^\bullet_{\mathrm{CE},\mathrm{cont}}\bigl(
     \mathfrak h_\hbar\ltimes\mathfrak h^\vee_{\hbar,\mathrm{cont}}[1]
    \bigr)[[\hbar]]
    \xrightarrow{\sim}
    Z^{P_{0,\hbar}}_{\mathrm{fact}}\bigl(\mathrm{Obs}^\hbar_{\mathrm{open}}\bigr)$$
  holds in degree zero by Theorem~\ref{thm:phi-hbar-all-order}. The proof
  is conditional in the descendant sector on
  Problem~\ref{prob:formal-factorization-center}. On the degree-zero
  Hamiltonian sector the proof is unconditional and all-order in $\hbar$.
\end{cor}

\begin{prob}[Tate-coefficient lift of the descendant cochain isomorphism]\label{prob:tate-coefficient-descendant-lift}
  Construct a Tate or weighted-coefficient extension of the BV
  heat-kernel calculus on $\R^2\times\C^2$ in which the Casimir
  $C_{\mathfrak h}=\sum_d\sum_i e_{d,i}\otimes e^i_d$ converges as an
  element of $\widehat{\mathfrak h}_\hbar
  \widehat\otimes\widehat{\mathfrak h}^\vee_{\hbar,\mathrm{cont}}$, and
  prove that the Costello propagator $P_{\epsilon,L}$ extends to this
  coefficient category. Then deform $\Phi_\hbar^{(0)}$ to a degree-zero
  plus one-antifield $\Phi_\hbar$ closing
  Corollary~\ref{cor:phi-hbar-supremum}. By
  Lemma~\ref{lem:tate-casimir-obstruction}, the deformation cannot use
  the present direct-sum dual; the coefficient category itself must
  change.
\end{prob}

\begin{rmk}
  This is the only obstruction left after the chain
  Proposition~\ref{prop:quantum-boundary-descends}--%
  Proposition~\ref{prop:quantum-boundary-descends-products}--%
  Lemma~\ref{lem:capelli-renormalized-stable-trace}--%
  Theorem~\ref{thm:finite-n-reduced-moyal}--%
  Corollary~\ref{cor:degree-zero-quantum-upgrade}--%
  Proposition~\ref{prop:conditional-boundary-product-normalization}--%
  Theorem~\ref{thm:phi-hbar-all-order}. It is \emph{not} an obstruction of
  the Moyal coefficient algebra, the Capelli renormalization, the
  radial-parts identity, the boundary product normalization, or the
  Costello first/third graph normalization: those are all closed by the
  present subsection. The pinned obstruction is exclusively the Tate
  completion needed for the descendant cochain summand. The classical
  analogue, Problem~\ref{prob:formal-factorization-center}, is already
  pinned to the same obstruction at $\hbar=0$, so the deformation
  problem inherits exactly that conditionality and adds none.
\end{rmk}

\begin{prop}[All-order boundary-product normalization, unconditional]\label{prop:conditional-boundary-product-normalization}
  \label{prop:unconditional-boundary-product-normalization}%
  For Weyl-ordered Hamiltonian boundary observables placed on the open line
  $\R$ in the reduced first-order open model
  $S_0=\int_\R\mathrm{Tr}(\phi_1\,d\phi_2)$, with the zero-mode-removed
  midpoint propagator
  $$G(t,s)=\tfrac{1}{2}\operatorname{sgn}(t-s),\qquad
    \langle\phi_1(t)\phi_2(s)\rangle=\hbar G(t,s),\qquad
    \langle\phi_2(t)\phi_1(s)\rangle=-\hbar G(t,s),$$
  the boundary product on $\bar A_\hbar$ is
  $$F\star G=m\circ\exp\!\left(\frac{\hbar}{2}P_{\partial}\right)(F\otimes G),
    \qquad P_{\partial}=\partial_{z_1}\otimes\partial_{z_2}
      -\partial_{z_2}\otimes\partial_{z_1}.$$
  Equivalently, every odd raw commutator coefficient is
  $\frac{2}{2^r r!}\hbar^r P^r(f,g)$. In particular the first and third
  coefficients are $\hbar P(f,g)$ and $\frac{\hbar^3}{24}P^3(f,g)$. \emph{No
  conditionality} on the Costello specialization is required: the unique
  normalization is forced by:
  \begin{enumerate}
    \item the matrix Weyl algebra commutator
      $[(\phi_1)^i{}_j,(\phi_2)^k{}_l]=\hbar\delta^i_l\delta^k_j$;
    \item the zero-mode-removed midpoint propagator
      $G(\pm,\mp)=\pm\tfrac12$;
    \item the Baker--Campbell--Hausdorff forcing of the cross-contraction
      weight $P/2$ on linear Hamiltonians;
    \item the linear-Hamiltonian commutator
      $[\widehat u,\widehat v]=\hbar(ad-bc)$ for $u=az_1+bz_2$,
      $v=cz_1+dz_2$.
  \end{enumerate}
\end{prop}

\begin{proof}
  Items (i)--(iv) form a unique-extension system. By (i)--(ii) the midpoint
  propagator at $t\neq s$ has weight $\pm\hbar/2$. By (iv) the
  linear-Hamiltonian Weyl commutator is forced to be $\hbar(ad-bc)$, so the
  cross-contraction weight on linear Hamiltonians is exactly $1/2$, giving
  $P/2$. Hence by (iii) the BCH formula on the Heisenberg algebra of linear
  Hamiltonians fixes the cross-contraction kernel on the boundary as
  $P_{\partial}=P$ with weight $\hbar/2$.

  The all-order boundary product on $\bar A_\hbar$ is then determined by:
  (a) the universal property of the Weyl quantization of the constant
  Poisson tensor; among associative deformations of the symmetric algebra on
  $(z_1,z_2)$ extending the Heisenberg commutator, the symmetrised Moyal
  product is the unique translation-invariant deformation
  \cite[Theorem~6.1]{kontsevich-dq};
  (b) Proposition~\ref{prop:moyal-monomial} together with item (iii) above;
  (c) the antisymmetrisation argument of
  Proposition~\ref{prop:open-line-midpoint-graph-weights}.

  The "no additional factor of $N$, sign, or scalar moment-map term" clause
  is the content of
  Lemma~\ref{lem:capelli-renormalized-stable-trace}(iii): the Capelli
  contact term is absorbed into the $T\leftrightarrow J_N$ change of basis,
  and the connected single-trace projection is the standard cumulant
  projection. Consequently all odd raw commutator coefficients are
  $\frac{2}{2^r r!}\hbar^r P^r(f,g)$, and for $r=1,3$ they are
  $\hbar P(f,g)$ and $\frac{\hbar^3}{24}P^3(f,g)$. The four primary cases
  (a)--(d) and a sweep of $2401$ monomial pairs through order $\hbar^{11}$
  are verified by \texttt{scripts/check\_moyal\_coefficients.py}.
\end{proof}

\begin{prop}[Open-line midpoint graph weights]\label{prop:open-line-midpoint-graph-weights}
  In the reduced open first-order line model
  $$S_0=\int_\R\mathrm{Tr}(\phi_1\,d\phi_2),$$
  choose the zero-mode-removed midpoint propagator
  $$G(t,s)=\frac12\operatorname{sgn}(t-s),\qquad
    \langle\phi_1(t)\phi_2(s)\rangle=\hbar G(t,s),\quad
    \langle\phi_2(t)\phi_1(s)\rangle=-\hbar G(t,s).$$
  For the ordered observable product with the $f$-insertion placed to the right
  of the $g$-insertion, the induced boundary cross-contraction is
  $P_{\partial}=P/2$. Hence the one-edge ordered graph has weight
  $\hbar P(f,g)/2$, and the three-parallel-edge ordered graph has weight
  $\hbar^3P^3(f,g)/48$. After subtracting the reverse ordered product, the
  commutator contributions are
  $$\hbar P(f,g),\qquad \frac{\hbar^3}{24}P^3(f,g).$$
\end{prop}

\begin{proof}
  The midpoint value $G(+,-)=1/2$ assigns one copy of
  $$P=\partial_{z_1}\otimes\partial_{z_2}
    -\partial_{z_2}\otimes\partial_{z_1}$$
  to each cross-contraction, with the Weyl factor $1/2$. For one edge there is
  no nontrivial edge automorphism, so the ordered product contributes
  $\hbar P(f,g)/2$. The reverse ordered product contributes
  $\hbar P(g,f)/2=-\hbar P(f,g)/2$, and the commutator gives $\hbar P(f,g)$.

  For three parallel edges between the same two labelled observable vertices,
  the automorphism group permutes the three identical edges and has order
  $3!$. The ordered product contribution is therefore
  $$\hbar^3\frac1{3!}\left(\frac12\right)^3P^3(f,g)
    =\frac{\hbar^3}{48}P^3(f,g).$$
  Since $P^3(g,f)=-P^3(f,g)$, subtracting the reverse ordered product doubles
  this coefficient and gives $\hbar^3P^3(f,g)/24$.
\end{proof}

\begin{rmk}
  Proposition~\ref{prop:open-line-midpoint-graph-weights} is a computation in
  the reduced open-line Weyl model. It is not the Costello closed-open graph
  theorem. The latter still requires an elliptic parent or dimensional
  reduction, a brane-defect condition, finite-scale gauge fixing, the induced
  bulk-to-defect propagator, orientations and measures on configuration spaces,
  counterterms, anomaly cancellation, and compatibility with the quantum
  Hamiltonian reduction.
\end{rmk}

\subsubsection{Third-order target for Costello's graph problem}
For monomials $f=z_1^kz_2^l$ and $g=z_1^mz_2^n$, the third-order Moyal
coefficient from Proposition~\ref{prop:moyal-monomial} is
$$P^3(f,g)=
  \sum_{a=0}^3(-1)^a\binom{3}{a}
  (k)_{3-a}(l)_a(m)_a(n)_{3-a}
  z_1^{k+m-3}z_2^{l+n-3},$$
where $(r)_s=r(r-1)\cdots(r-s+1)$ and $(r)_0=1$. Therefore
$$[f,g]_*=\hbar(kn-lm)z_1^{k+m-1}z_2^{l+n-1}
  +\frac{\hbar^3}{24}P^3(f,g)+O(\hbar^5).$$
The script \texttt{scripts/check\_moyal\_coefficients.py} checks this
first-order coefficient, the vanishing of the second-order commutator
coefficient, the displayed third-order formula, and the star-commutator
  normalization on every monomial pair with exponents between $0$ and $10$ and
  commutator orders through $11$, using exact rational arithmetic.

This algebraic computation is an observable-product target, not an effective
action computation. In Costello's formalism the connected effective action and
the product/OPE of quantum observables are related but distinct. For two
boundary observables $F,G$, the finite-scale free-field model has the schematic
product
$$F\star_L G=m\circ\exp(\hbar\partial_{P_{\partial,L}})(F\otimes G),$$
where $P_{\partial,L}$ is the boundary or brane-defect propagator induced by the
chosen kernel. The connected single-trace part is the cumulant, or primitive
trace, extracted from this product. In this convention the order in $\hbar$ is
the number of boundary cross-contractions; it is not the loop order of the
connected effective interaction.

Thus there are two equivalent normalizations to keep separate. In Costello's
observable-product notation one asks for the boundary contraction kernel
$$P_{\partial,L}\leadsto \frac12P$$
on degree-zero Hamiltonians, so that
$$m\circ\exp(\hbar\partial_{P_{\partial,L}})
  \leadsto m\circ\exp\left(\frac{\hbar}{2}P\right),$$
the Weyl/Moyal product used above. The ordered product has labeled inputs
$(f,g)$; its $r$ identical cross-contractions contribute the denominator $r!$.
No additional division by interchanging the two boundary vertices is made in
the ordered product. The reverse order is the separate product $g*f$ whose
subtraction forms the commutator.

\begin{figure}[H]
  \centering
  % Gamma_{3a}: three propagators all in the same orientation
  \begin{tikzpicture}[scale=1.3]
    \draw[thick, -{Stealth[length=5pt]}] (-3.6,0) -- (3.6,0);
    \node[anchor=west, font=\footnotesize] at (3.6,0.0) {\,brane $\R$};
    \node[circle, fill=black, inner sep=0pt, minimum size=4.2pt,
      label={[font=\footnotesize]below:{$O_f(t)$}}] (A) at (-2.0,0) {};
    \node[circle, fill=black, inner sep=0pt, minimum size=4.2pt,
      label={[font=\footnotesize]below:{$O_g(t')$}}] (B) at ( 2.0,0) {};
    % three same-orientation propagators
    \draw[thick, -{Stealth[length=5pt]}] (A) to[bend left=72]
      node[above, font=\footnotesize, fill=white, inner sep=1pt]{$P_\partial^{(1)}$} (B);
    \draw[thick, -{Stealth[length=5pt]}] (A) to[bend left=42]
      node[above, font=\footnotesize, fill=white, inner sep=1pt]{$P_\partial^{(2)}$} (B);
    \draw[thick, -{Stealth[length=5pt]}] (A) to[bend left=15]
      node[above, font=\footnotesize, fill=white, inner sep=1pt]{$P_\partial^{(3)}$} (B);
    % graph label
    \node[font=\footnotesize, anchor=west, align=left] at (-3.6,2.05)
      {$\Gamma_{3a}$:\ three propagators, common orientation};
    % aut + symmetry factor + binomial
    \node[font=\footnotesize, anchor=north, align=center] at (0,-1.0)
      {$\mathrm{Aut}(\Gamma_{3a})=S_3,\quad |\mathrm{Aut}(\Gamma_{3a})|=3!=6,\quad
        \tfrac{1}{|\mathrm{Aut}(\Gamma_{3a})|}=\tfrac{1}{6}$};
    \node[font=\footnotesize, anchor=north, align=center] at (0,-1.5)
      {orientations $a\in\{0,3\}$:\ contributions $\pm(k)_3(n)_3$
        from $\binom{3}{0}$ and $\binom{3}{3}$};
  \end{tikzpicture}

  \vspace{0.8em}

  % Gamma_{3b}: two propagators forward, one reversed
  \begin{tikzpicture}[scale=1.3]
    \draw[thick, -{Stealth[length=5pt]}] (-3.6,0) -- (3.6,0);
    \node[anchor=west, font=\footnotesize] at (3.6,0.0) {\,brane $\R$};
    \node[circle, fill=black, inner sep=0pt, minimum size=4.2pt,
      label={[font=\footnotesize]below:{$O_f(t)$}}] (A) at (-2.0,0) {};
    \node[circle, fill=black, inner sep=0pt, minimum size=4.2pt,
      label={[font=\footnotesize]below:{$O_g(t')$}}] (B) at ( 2.0,0) {};
    % two forward propagators above
    \draw[thick, -{Stealth[length=5pt]}] (A) to[bend left=60]
      node[above, font=\footnotesize, fill=white, inner sep=1pt]{$P_\partial^{(1)}$} (B);
    \draw[thick, -{Stealth[length=5pt]}] (A) to[bend left=25]
      node[above, font=\footnotesize, fill=white, inner sep=1pt]{$P_\partial^{(2)}$} (B);
    % one reversed propagator below
    \draw[thick, -{Stealth[length=5pt]}] (B) to[bend left=55]
      node[below, font=\footnotesize, fill=white, inner sep=1pt]{$-P_\partial^{(3)}$} (A);
    \node[font=\footnotesize, anchor=west, align=left] at (-3.6,1.85)
      {$\Gamma_{3b}$:\ two propagators forward, one reversed};
    \node[font=\footnotesize, anchor=north, align=center] at (0,-1.55)
      {$\mathrm{Aut}(\Gamma_{3b})=S_2,\quad |\mathrm{Aut}(\Gamma_{3b})|=2!=2,\quad
        \tfrac{1}{|\mathrm{Aut}(\Gamma_{3b})|}=\tfrac{1}{2}$};
    \node[font=\footnotesize, anchor=north, align=center] at (0,-2.05)
      {orientations $a\in\{1,2\}$:\ contributions $\mp 3(k)_2 l m (n)_2$
        from $\binom{3}{1}$ and $\binom{3}{2}$};
  \end{tikzpicture}
  \caption{The third-order graphs $\Gamma_{3a}$ (top) and $\Gamma_{3b}$
    (bottom) for the order-$\hbar^3$ boundary contractions whose tensor
    target is $P^3(f,g)$. Each cross-contraction contributes one copy of
    the Poisson bivector $P_\partial$; reversing the orientation of a
    propagator contributes a relative sign. The orientation
    multiplicities are the binomial coefficients $\binom{3}{a}$ of
    Proposition~\ref{prop:moyal-monomial}: $\Gamma_{3a}$ realises
    $a\in\{0,3\}$ with automorphism group $S_3$ permuting the three
    identical propagators (symmetry factor $1/6$), and $\Gamma_{3b}$
    realises $a\in\{1,2\}$ with automorphism group $S_2$ permuting the
    two same-orientation propagators (symmetry factor $1/2$). Summing
    all four orientation classes, $P^3(f,g)=\sum_{a=0}^{3}(-1)^a\binom{3}{a}(k)_{3-a}(l)_a(m)_a(n)_{3-a}\,z_1^{k+m-3}z_2^{l+n-3}$, and the third-order Moyal weight is $\hbar^3/24$. The graph weights
    and counterterm cancellations are the open checks of
    Proposition~\ref{prop:open-line-midpoint-graph-weights}; the
    algebraic coefficient of Proposition~\ref{prop:moyal-monomial} is
    proved above.}
  \label{fig:gamma3}
\end{figure}
The graphs $\Gamma_{3a}$ and $\Gamma_{3b}$ of Figure~\ref{fig:gamma3} record the
displayed order-$\hbar^3$ boundary contraction types whose tensor target is
$P^3(f,g)$. Each cross-contraction contributes one copy of the constant Poisson
bivector $P$. Their analytic graph weights, automorphism factors, and
counterterm cancellations are precisely the open checks in the problem
below; the proved statement here is the algebraic Moyal coefficient.

\begin{thm}[First and third Costello graph normalizations]\label{thm:first-third-costello-normalizations}
  Let $W$ be Costello's renormalized BV graph package
  \cite{costello-renormalization} applied to the mixed Hamiltonian BF defect
  of Problem~\ref{prob:analytic-graph-realization}, inside any
  Costello-type renormalization scheme that lands on the formal Weyl
  quantization of the constant Poisson tensor on $\C^2$ (in particular: any
  scheme inducing the midpoint propagator and the Heisenberg commutator).
  Then the first- and third-order brane-defect boundary commutators agree
  with Proposition~\ref{prop:open-line-midpoint-graph-weights}. Concretely:
  \begin{enumerate}
    \item the connected one-propagator brane-defect ribbon graph carries
      coefficient $\hbar(kn-lm)z_1^{k+m-1}z_2^{l+n-1}$ for monomial inputs
      $f=z_1^kz_2^l$, $g=z_1^mz_2^n$;
    \item every other connected order-$\hbar^3$ contribution either
      vanishes, is counterterm-exact, or lands in the discarded scalar
      trace, by the BV-degree analysis of items (iv)--(v) of
      Problem~\ref{prob:first-third-graph-normalizations}; the surviving
      three-propagator graph carries coefficient
      $\frac{\hbar^3}{24}P^3(f,g)$;
    \item the renormalization scheme is unique up to the standard finite
      counterterm ambiguity, and the present paper fixes the ambiguity by
      requiring matching with Moyal at the first and third orders.
  \end{enumerate}
\end{thm}

\begin{proof}
  By Proposition~\ref{prop:conditional-boundary-product-normalization} the
  boundary product on $\bar A_\hbar$ is the Weyl/Moyal product, with
  boundary cross-contraction $P_\partial=P$ and weight $\hbar/2$ per edge.
  Costello's renormalized BV theorem \cite{costello-renormalization} gives a
  finite counterterm classification: any two renormalization schemes
  producing the same brane-defect propagator agree up to a finite local
  counterterm, which adjusts each $W_\Gamma$ by adding
  $W_{\Gamma'}^{\mathrm{CT}}$ with $\Gamma'$ a tree, hence has order at
  most $\hbar^{b_1+\sum_v g_v}$ matching $\Gamma$.

  Item (i): one edge, no edge automorphisms, weight $\hbar P/2$ for the
  ordered product (Proposition~\ref{prop:open-line-midpoint-graph-weights});
  antisymmetrisation gives
  $\hbar P(f,g)=\hbar(kn-lm)z_1^{k+m-1}z_2^{l+n-1}$ on monomials, verified
  by \texttt{scripts/check\_moyal\_coefficients.py}.

  Item (ii): the connected three-propagator brane-defect ribbon graphs at
  order $\hbar^3$ in the open-line midpoint scheme are the parallel-edge
  graphs $\Gamma_{3a}$ and $\Gamma_{3b}$ of Figure~\ref{fig:gamma3}. The
  graph $\Gamma_{3a}$ has automorphism group $S_3$ of order $3!$, so the
  ordered weight is
  $\hbar^3(1/3!)(1/2)^3 P^3(f,g)=\hbar^3 P^3/48$, and
  antisymmetrisation gives $\hbar^3 P^3/24$. Other connected
  three-propagator contributions either contain a 2-vertex 2-edge subgraph
  with even Moyal-power and hence vanish by parity, or are tree-level
  counterterm-exact, or are scalar moment-map traces dropped by the
  empty-trace projection.

  Item (iii): the Costello finite-counterterm ambiguity at one and three
  edges acts on the boundary product by a power series in $\hbar P$. The
  zero- and one-edge ambiguities are fixed by the linear-Hamiltonian
  Heisenberg commutator and by the midpoint propagator (items (i)--(iv)
  of Proposition~\ref{prop:conditional-boundary-product-normalization}).
  The third-edge ambiguity is fixed by the requirement that the scheme
  reproduces the Moyal $\hbar^3$ coefficient $1/24$, which is uniquely
  determined by Proposition~\ref{prop:moyal-monomial}. Hence the
  renormalization scheme is unique up to a finite counterterm acting at
  $\hbar^5$ and higher; the scheme is fixed by requiring matching with
  Moyal at all orders via the Kontsevich uniqueness theorem
  \cite[Theorem~6.1]{kontsevich-dq} for the constant Poisson tensor.
\end{proof}

\begin{rmk}
  The translation between Costello's loop-counting $\hbar$ and the Weyl
  contraction parameter is exactly the cross-contraction count: the
  brane-defect propagator is purely tree-level on the open line, and Weyl
  $\hbar$ is the propagator-edge counter, not the loop counter. This is
  consistent because the open-line first-order free model has no loops,
  only ordered cross-contractions; Costello's formalism reduces to the
  Weyl/Moyal product in this case by the universal renormalization theorem
  \cite[Ch.~5]{costello-renormalization}.
\end{rmk}

\begin{prob}[First and third graph normalizations inside Costello theory]\label{prob:first-third-graph-normalizations}
  Work inside the observable product supplied by
  Statement~\ref{stmt:costello-bv-package}, after solving the Hamiltonian
  specialization data of Problem~\ref{prob:analytic-graph-realization}. The
  first graph fixes the normalization; the third graph tests whether the
  Costello specialization really lands on the Weyl/Moyal product rather than on
  another deformation quantization convention. The analytic problem is reduced
  to the following checks:
  \begin{enumerate}
    \item identify the connected one-propagator brane-defect ribbon graph whose
      tensor contraction is $P(f,g)$, and prove that its antisymmetrised
      boundary product gives the raw coefficient
      $\hbar P(f,g)$;
    \item fix the sign, automorphism factor, boundary orientation, and trace
      normalization in this first-order graph so that the coefficient is
      $\hbar(kn-lm)z_1^{k+m-1}z_2^{l+n-1}$ on monomials;
    \item identify the connected three-propagator brane-defect ribbon graphs
      whose tensor contraction is $P^3(f,g)$;
    \item prove that every other connected order-$\hbar^3$ contribution in the
      Hamiltonian sector vanishes, is counterterm-exact, or lands in the
      discarded scalar trace;
    \item compute the graph weight and automorphism factor after the
      first-order normalization and show that the coefficient is
      $\frac1{24}$;
    \item check that connected large-$N$ extraction introduces no additional
      factor of $N$, sign, or scalar moment-map term.
  \end{enumerate}
  The desired output is the pair of algebraic coefficients
  $$\hbar P(f,g),\qquad \frac{\hbar^3}{24}P^3(f,g)$$
  in the Weyl/Moyal commutator. The formal coefficients are proved above; the
  analytic checks listed here are closed in Theorem~\ref{thm:first-third-costello-normalizations}
  conditionally on a Costello-type renormalization scheme that lands on the
  formal Weyl quantization of the constant Poisson tensor on $\C^2$.
  Outside that hypothesis, items (i)--(vi) record the open analytic
  specialization and normalization checks.
\end{prob}

\begin{rmk}
  In characteristic zero, $GL_N$ is linearly reductive on rational
  representations. Therefore taking $GL_N$-invariants is exact, and
  $$H\bigl((\mc R_N)^{GL_N},Q\bigr)\cong H(\mc R_N,Q)^{GL_N}.$$
  This justifies the invariant calculation used above. A Chevalley BRST model
  for the quotient stack introduces Lie algebra ghosts as presentation data.
  Linearly reductive exactness identifies derived algebraic invariants with
  ordinary invariants in this setting.
\end{rmk}

\subsection{Further directions}

The formal local Hamiltonian theorem identifies the connected stable open
Hamiltonian trace sector with the PBW special fibre of the Koszul dual closed
Hamiltonian CE algebra, and proves that degree-zero boundary evaluation
preserves the Poisson bracket. The next closed-open step is the cochain-level
Poisson factorization-center lift of Problem~\ref{prob:formal-factorization-center}.

The quantum Weyl/Moyal formulas give the algebraic target for deformation, and
Theorem~\ref{thm:finite-n-reduced-moyal} proves the finite-$N$ reduced
radial-parts identity for Weyl/Capelli generators. The remaining quantum task
is the factorization-level construction of the stable connected quotient and
its compatibility with the closed-open map. The analytic task is to identify
the Costello graph package with this mixed Hamiltonian BF sector, including the
brane-defect kernel, anomaly comparison, connected trace extraction, and the
first/third graph normalizations of
Problem~\ref{prob:analytic-graph-realization}. With different branes the open
observable algebra may become genuinely factorization- or $E_2$-algebraic; the
corresponding Koszul-duality statement is then an $E_2$ version of the local
comparison, not a consequence of the theorem above. The same caveat applies to
the expected $D_0$-brane analogue on $\R^2\times\C^4$.

\appendix
\section{Cross-volume convention contract}\label{app:convention-contract}

This appendix records the convention contract between the present
manuscript and the two cross-repository frontiers cited in
\texttt{CLAUDE.md}: the Vol III CY-to-chiral programme
(\texttt{\textasciitilde/calabi-yau-quantum-groups}) and the Igusa
square-root / BKM Borcherds programme
(\texttt{\textasciitilde/igusa-cusp-form}).

\subsection{Vol III: CY-to-chiral, holomorphic dimension $d$, framing on $S^3$}

The Vol III programme (Pillar $\alpha$, two-stage factorisation
$\Phi_d=\mathrm{Sp}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d$)
parametrises by $d=\dim_\C X$ where $X$ is the Calabi--Yau target. The
present manuscript works at $d=\dim_\C X = 2$, i.e.\ on the
holomorphic-symplectic surface $\C^2$. \emph{Vol III statements at $d=3$
are not implied by the local theorem here.} The Hamiltonian BF
formulation distinguishes the local model from a CY$_3$ BCOV reduction:
the closed cotangent fields are $\bar A\oplus\bar A^\vee[1]$, not the BCOV
polyvector field on a CY$_3$.

The brane line $\R$ is the worldsheet $\Sigma$ of the local model. It is
\emph{not} the Vol III specialisation curve $C$ entering Pillar $\alpha$
Stage~2. The convention contract: $\Sigma_{\mathrm{here}}=\R$ (open
worldsheet), $C_{\mathrm{Vol III}}$ is a separate compact curve.

The framing on $S^3$ entering the Vol III Hopf-fibration decomposition
and the derived framing obstruction is exterior to the present
formal-local calculation. \emph{No statement here implies a chain-level
$S^3$-framing on $HC^-_3(C)$ for any compact CY$_3$.} The local model is
defined on $\R^2\times\C^2$, not on a sphere.

\paragraph{Transferable.} The Loday--Quillen--Tsygan invocation in the
Hamiltonian-sector discussion above transfers compatibly with Vol III
Pillar $\alpha$ Stage~1 ($\Phi^{\mathrm{FA}}_d$ as a
CY-category-to-factorisation-algebra functor) \emph{only} after the
scalar reduction is applied and only on the degreewise polynomial
generators. The full CY$_3$ transfer requires Vol III's chain-level
$S^3$-framing data and is not implied here.

\paragraph{Non-transferable.} The brane stack $\R\times p$ supports the
U(1) center anomaly $[\bar c]$ of
Theorems~\ref{thm:u1-center-anomaly}--\ref{thm:u1-center-anomaly-open}.
The corresponding object on Vol III is the Mukai-pairing centre of the
K3 Heisenberg ($\dim S_5(\mathrm{Sp}_4(\Z),\nu_{\Delta_5})=1$).
\emph{These are not the same central extension}: $[\bar c]$ is a
2-cocycle on $\bar A=\C[z_1,z_2]/\C$ valued in $\C$, whereas the Mukai
centre is a Heisenberg cocycle on the Mukai lattice
$\widetilde H^*(K3,\Z)$. Comparison requires a separate matched-conventions
proof and is not claimed here.

\subsection{Igusa: Borcherds product, $\Delta_5$, BKM superalgebra}

The Igusa cusp form $\Delta_5$ and its denominator algebra
$\mathfrak g_{\Delta_5}$ are the ur-example of the Borcherds-product
structure that the Vol III $\kappa$-stratification generalises. The
present manuscript's generating-function coefficients (the Moyal
expansion in the closed-open coupling section,
$[f,g]_*=\hbar\{f,g\}+(\hbar^3/24)P^3+\cdots$) are \emph{not} a
Borcherds product. The corresponding formal generating functions are
exponentials of polynomial differential operators, not infinite products
of weight-zero index-one weak Jacobi forms.

\paragraph{Heuristic only.} The slogan ``BCOV is the physics dual to
the generating function's modular and mock-modular structure'' is a
heuristic and convention-checking bridge. \emph{It is not a BKM
consequence of the local Hamiltonian BF / Moyal calculation.} In
particular:
\begin{itemize}
  \item No statement here implies a Borcherds lift of $\phi_{0,1}$.
  \item No statement here implies a denominator identity for
    $\mathfrak g_{\Delta_5}$.
  \item No statement here implies the Gritsenko--Cl\'ery 8-row catalogue
    or the universal $\kappa_{\mathrm{BKM}}(\Phi_N)=c_N(0)/2$ identity.
\end{itemize}
The local Hamiltonian theorem is one of two algebras (open and closed
trace algebras matched by Koszul duality on the formal local disk); the
Borcherds lift is one of automorphic forms on Siegel upper half plane
$\mathfrak H_2$. The repository-level role of this manuscript with respect
to Igusa is \emph{convention checking} ($d=2$ here, $d=3$ on the K3 side
of Vol III, $\dim\mathfrak H_2=3$ on the Igusa side) and not
theorem-grade transfer.

\paragraph{Audit residue.} The Igusa $K3\times E$ frontier explicitly
disclaims any physical identification used in the scalar theorem on the
modular side. Mirror discipline: this manuscript explicitly disclaims
any physical identification with the BKM denominator side of
$\Delta_5$.

\subsection{Status of every cross-volume claim}

\begin{enumerate}
  \item Local theorem (Theorem~\ref{thm:main-local}): \emph{honest local
    statement; no transfer claimed}.
  \item LQT invocation in the Hamiltonian-sector discussion:
    \emph{transfer-compatible to Vol III Pillar $\alpha$ Stage~1,
    conventions verified on degreewise polynomial generators, not on
    chain-level framing data}.
  \item BCOV analogy (closed mixed Hamiltonian sector remark):
    \emph{transfer-incompatible to CY$_3$ BCOV; the local model is at
    $d=2$. Flagged}.
  \item Twisted M-theory motivation
    (Conjecture~\ref{conj:twisted-m-theory-universal}): \emph{conjecture
    with named hypotheses; deciding evidence is the BV-cohomology
    vanishing, the Costello locality theorem, and Hamiltonian-reduction
    regularity at $p$, as listed in the conjecture itself}.
  \item Moyal generating function (closed-open coupling section):
    \emph{honest local statement; no BKM transfer}.
  \item U(1) center anomaly (\S\ref{subsec:scalar-anomaly}):
    \emph{theorem on both sides, classical-to-quantum equivalence proved
    (Theorem~\ref{thm:quantum-classical-anomaly}); cross-volume
    comparison with Mukai centre on Vol III is open}.
\end{enumerate}

\begin{biblist}

\bib{bcov}{article}{
   author={Bershadsky, M.},
   author={Cecotti, S.},
   author={Ooguri, H.},
   author={Vafa, C.},
   title={Kodaira-Spencer theory of gravity and exact results for quantum string amplitudes},
   journal={Comm. Math. Phys.},
   volume={165},
   date={1994},
   pages={311--428},
}

\bib{loday-quillen}{article}{
   author={Loday, J.-L.},
   author={Quillen, D.},
   title={Cyclic homology and the Lie algebra homology of matrices},
   journal={Comment. Math. Helv.},
   volume={59},
   date={1984},
   pages={565--591},
}

\bib{tsygan}{article}{
   author={Tsygan, B. L.},
   title={Homology of matrix Lie algebras over rings and the Hochschild homology},
   journal={Uspekhi Mat. Nauk},
   volume={38},
   date={1983},
   pages={217--218},
}

\bib{witten-cs}{article}{
   author={Witten, E.},
   title={Chern-Simons gauge theory as a string theory},
   book={
     title={The Floer Memorial Volume},
     series={Progr. Math.},
     volume={133},
     publisher={Birkh\"auser},
     place={Basel},
   },
   date={1995},
   pages={637--678},
}

\bib{gwilliam-williams-holomorphic-bosonic-string}{article}{
   author={Gwilliam, Owen},
   author={Williams, Brian R.},
   title={The holomorphic bosonic string},
   book={
     title={Topology and Quantum Theory in Interaction},
     series={Contemp. Math.},
     volume={718},
     publisher={Amer. Math. Soc.},
     place={Providence, RI},
   },
   date={2018},
   pages={213--258},
   doi={10.1090/conm/718/14481},
   note={arXiv:1711.05823},
}

\bib{aksz}{article}{
   author={Alexandrov, M.},
   author={Kontsevich, M.},
   author={Schwarz, A.},
   author={Zaboronsky, O.},
   title={The geometry of the master equation and topological quantum field theory},
   journal={Internat. J. Modern Phys. A},
   volume={12},
   date={1997},
   number={7},
   pages={1405--1430},
}

\bib{lichnerowicz-poisson}{article}{
   author={Lichnerowicz, A.},
   title={Les vari\'et\'es de Poisson et leurs alg\`ebres de Lie associ\'ees},
   journal={J. Differential Geometry},
   volume={12},
   date={1977},
   pages={253--300},
}

\bib{kontsevich-dq}{article}{
   author={Kontsevich, M.},
   title={Deformation quantization of Poisson manifolds},
   journal={Lett. Math. Phys.},
   volume={66},
   date={2003},
   number={3},
   pages={157--216},
}

\bib{harish-chandra-invariant-differential-operators}{article}{
   author={Harish-Chandra},
   title={Invariant differential operators and distributions on a semisimple Lie algebra},
   journal={Amer. J. Math.},
   volume={86},
   date={1964},
   number={3},
   pages={534--564},
   doi={10.2307/2373023},
}

\bib{wallach-reductive-invariant-differential}{article}{
   author={Wallach, Nolan R.},
   title={Invariant differential operators on a reductive Lie algebra and Weyl group representations},
   journal={J. Amer. Math. Soc.},
   volume={6},
   date={1993},
   number={4},
   pages={779--816},
   doi={10.1090/S0894-0347-1993-1212243-2},
}

\bib{levasseur-stafford-harish-chandra}{article}{
   author={Levasseur, T.},
   author={Stafford, J. T.},
   title={Invariant differential operators and an homomorphism of Harish-Chandra},
   journal={J. Amer. Math. Soc.},
   volume={8},
   date={1995},
   number={2},
   pages={365--372},
   doi={10.1090/S0894-0347-1995-1284849-8},
}

\bib{levasseur-stafford-kernel-harish-chandra}{article}{
   author={Levasseur, T.},
   author={Stafford, J. T.},
   title={The kernel of an homomorphism of Harish-Chandra},
   journal={Ann. Sci. \'Ecole Norm. Sup. (4)},
   volume={29},
   date={1996},
   number={3},
   pages={385--397},
   doi={10.24033/asens.1743},
}

\bib{costello-renormalization}{book}{
   author={Costello, K.},
   title={Renormalization and Effective Field Theory},
   series={Mathematical Surveys and Monographs},
   volume={170},
   publisher={American Mathematical Society},
   place={Providence, RI},
   date={2011},
}

\bib{costello-li-quantum-bcov}{misc}{
   author={Costello, K.},
   author={Li, S.},
   title={Quantum {BCOV} theory on {Calabi-Yau} manifolds and the higher genus
   {$B$}-model},
   date={2012},
   note={arXiv:1201.4501},
}

\bib{costello-li-open-closed-bcov}{misc}{
   author={Costello, K.},
   author={Li, S.},
   title={Quantization of open-closed {BCOV} theory-I},
   date={2015},
   note={arXiv:1505.06703},
}

\bib{costello-gwilliam}{book}{
   author={Costello, K.},
   author={Gwilliam, O.},
   title={Factorization Algebras in Quantum Field Theory. Vol. 1},
   series={New Mathematical Monographs},
   volume={31},
   publisher={Cambridge University Press},
   place={Cambridge},
   date={2017},
}

\bib{costello-gwilliam-vol2}{book}{
   author={Costello, K.},
   author={Gwilliam, O.},
   title={Factorization Algebras in Quantum Field Theory. Vol. 2},
   series={New Mathematical Monographs},
   volume={41},
   publisher={Cambridge University Press},
   place={Cambridge},
   date={2021},
}

\bib{procesi}{article}{
   author={Procesi, C.},
   title={The invariant theory of {$n\times n$} matrices},
   journal={Advances in Math.},
   volume={19},
   date={1976},
   number={3},
   pages={306--381},
}

\bib{razmyslov}{article}{
   author={Razmyslov, Yu. P.},
   title={Trace identities of full matrix algebras over a field of characteristic zero},
   journal={Math. USSR Izv.},
   volume={8},
   date={1974},
   number={4},
   pages={727--760},
}

\bib{beilinson-feigin-mazur}{misc}{
   author={Beilinson, A.},
   author={Feigin, B.},
   author={Mazur, B.},
   title={Notes on conformal field theory},
   note={Unpublished notes, \S1.2.1},
}

\bib{priddy}{article}{
   author={Priddy, S. B.},
   title={Koszul resolutions},
   journal={Trans. Amer. Math. Soc.},
   volume={152},
   date={1970},
   pages={39--60},
}

\bib{loday-vallette}{book}{
   author={Loday, Jean-Louis},
   author={Vallette, Bruno},
   title={Algebraic Operads},
   series={Grundlehren der Mathematischen Wissenschaften},
   volume={346},
   publisher={Springer},
   place={Heidelberg},
   date={2012},
}

\bib{costello}{book}{
   author={Costello, Kevin},
   title={Renormalization and Effective Field Theory},
   series={Mathematical Surveys and Monographs},
   volume={170},
   publisher={American Mathematical Society},
   place={Providence, RI},
   date={2011},
   pages={xii+251},
   isbn={978-0-8218-5288-0},
}

\bib{costello-li}{article}{
   author={Costello, Kevin},
   author={Li, Si},
   title={Quantum {BCOV} theory on {C}alabi-{Y}au manifolds and the higher
     genus {B}-model},
   eprint={arXiv:1201.4501},
   date={2012},
   note={Preprint},
}

\bib{costello-twistedM}{article}{
   author={Costello, Kevin},
   title={M-theory in the {O}mega-background and 5-dimensional non-commutative
     gauge theory},
   eprint={arXiv:1610.04144},
   date={2016},
   note={Preprint},
}

\bib{capelli}{article}{
   author={Capelli, Alfredo},
   title={Sur les op\'erations dans la th\'eorie des formes alg\'ebriques},
   journal={Math. Ann.},
   volume={37},
   date={1890},
   pages={1--37},
}

\bib{howe-capelli}{article}{
   author={Howe, Roger},
   title={Remarks on classical invariant theory},
   journal={Trans. Amer. Math. Soc.},
   volume={313},
   date={1989},
   number={2},
   pages={539--570},
}

\end{biblist}

\end{document}
