\section{Admissibility criteria and obstruction complexes}\label{sec:open-obligations}

The coordinate CE/PV theorem and staged admissibility programme is
governed by constructions, hypotheses, and obstruction complexes.  Each
item below is either a construction already used in the local theorem, an
admissibility criterion for a frontier extension, or an obstruction complex
whose vanishing is the exact condition for the next theorem.

External compact Calabi--Yau, CoHA, quintic, OSV/GV, Abel--Jacobi, MNOP,
Igusa, BKM, and global BCOV material is not a core local obligation.  It
is a comparison surface only, and it cannot support the local QME, Ext,
cyclic, Weyl/Moyal, radial-parts, or kernel theorems without a separate
matched-conventions theorem and a vanishing obstruction vector.

\begin{enumerate}
  \item \emph{Finite cotangent CE/PV data.}
  The finite model is attached to a finite-dimensional Lie algebra
  \(\mathfrak l\), its ordinary dual \(\mathfrak l^\vee\), and the
  cotangent Lie algebra
  \[
    \mathfrak g_{\mathfrak l}
    =\mathfrak l\ltimes \mathfrak l^\vee[1].
  \]
  The finite comparison is
  \[
    \Phi_{\mathfrak l}\colon
    C^\bullet_{\mathrm{CE}}(\mathfrak g_{\mathfrak l})
    \xrightarrow{\sim}
    \mathrm{PV}(\mathbf S(\mathfrak l)),
    \qquad c\mapsto\theta,\quad u\mapsto O .
  \]

  \item \emph{Completed formal-disk CE/PV admissibility.}
  The comparison for
  \(\mathfrak h=\C[[z_1,z_2]]/\C\cdot1\) and
  \(\mathfrak g=\mathfrak h\ltimes
  \mathfrak h^\vee_{\mathrm{cont}}[1]\) is accepted first as a pro
  coordinate-window CE/PV comparison.  It becomes a completed bracketed
  statement only after a bracket-admissible realization \(B\subset
  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) has a
  specified complete Hausdorff topology, continuous inclusion in the
  coordinate product, continuous multiplication, continuous
  \(d_\pi^{\mathrm{coord}}\), a continuous closed coordinate contraction
  bracket, and the transported continuous source structure on
  \(\Phi_{\mathrm{coord}}^{-1}(B)\).  Boundary Hamiltonian uses also
  require \(B\) to contain the relevant \(O_f\)'s and
  \(d_\pi^{\mathrm{coord}}O_f\)'s.  It becomes a kernel statement only
  after a kernel-admissible datum \((B,\mathcal K_B)\) is supplied, so that
  the diagonal tensor
  \[
    \Theta_B=\sum_I H_I\otimes\theta^I+\sum_I\eta^I\otimes O_I
  \]
  converges in \(\mathcal K_B\) and satisfies
  \[
    d\Theta_B+\frac12[\Theta_B,\Theta_B]=0.
  \]
  The admissible formal-local interface datum is
  \[
    \mathfrak U_{\mathfrak h}
    =(\Phi_{\mathrm{coord}},\{\Phi^B_{P_0}\}_B,\{\Theta_B\}_B).
  \]
  It is not a categorical universal object unless a category of
  admissible completions and a universal property are supplied.
  The
  coordinate obstruction terms are
  \[
    \begin{aligned}
    \mathfrak o^{\mathrm{br}}_{M,N}(x,y)
      ={}&\pi_{M,N}[x,y]_M-[\pi_{M,N}x,\pi_{M,N}y]_N,
    \end{aligned}
  \]
  \[
    \begin{aligned}
    \mathfrak o^{\mathrm{coad}}_{M,N}(x,\lambda)
      ={}&\pi^\vee_{M,N}(x\cdot_M\lambda)\\
       &-(\pi_{M,N}x)\cdot_N(\pi^\vee_{M,N}\lambda),
    \end{aligned}
  \]
  Their vanishing gives the pro coordinate-window comparison
	  \[
	    \Phi_{\mathrm{coord}}\colon
	    C^\bullet_{\mathrm{CE},\mathrm{coord}}(\mathfrak g)
	    \xrightarrow{\sim}
	    \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}}).
	  \]
  On a bracket-admissible \(B\) the restricted map
  \[
    \Phi^B_{P_0}\colon
    \Phi_{\mathrm{coord}}^{-1}(B)\xrightarrow{\sim}B
  \]
  is the corresponding completed \(P_0\)-comparison.
  The Casimir transition term
  \[
    \mathfrak o^{\mathrm{Cas}}_{M,N}
      =(\pi_{M,N}\otimes\pi^\vee_{M,N})C_M-C_N
  \]
  diagnoses the failure of a strict global kernel, propagator, endpoint,
  ambient-product bracket, and bar-cobar/enveloping comparison in the unweighted
  product/direct-sum topology.  It is not an additional hypothesis for
  each coordinate-window CE/PV identity.

  \item \emph{Admissible Tate bar-cobar/Quillen envelope.}
  For an admissible Tate replacement
  \(\mathfrak g_{\mathrm{adm}}\), put
  \[
    B_{\mathrm{adm}}=
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{adm}}).
  \]
  The admissible Koszul duality theorem in the envelope is
  \[
    B_{\mathrm{adm}}^!\simeq
    \widehat U(\mathfrak g_{\mathrm{adm}}),
  \]
  together with the bar-cobar Quillen equivalence under lower-central
  Tate-pronilpotence, PBW completeness, and the completed symmetric
  associated graded.  The acceptance datum lives in a chosen admissible
  finite-window model envelope, not in raw Tate vector spaces.  Failure is
  the obstruction vector
  \[
    \mathcal O_{\mathrm{AdmTate}}
    =
    (\mathcal O_{\mathrm{win}},
     \mathcal O_{\mathrm{top}},
     \mathcal O_{\mathrm{conilp}},
     \mathcal O_{\mathrm{MC}},
     \mathcal O_{\mathrm{cobar}},
     \mathcal O_{\mathrm{PBW}},
     \mathcal O_{P_0},
     \mathcal O_{\mathrm{cyc}}),
  \]
  where \(\mathcal O_{\mathrm{win}}\) contains the bracket, coadjoint,
  and Casimir transition defects; \(\mathcal O_{\mathrm{top}}\) contains
  Milnor/Roos \(\varprojlim^1\) terms; \(\mathcal O_{\mathrm{conilp}}\)
  records CE-length and lower-central separatedness defects;
  \(\mathcal O_{\mathrm{MC}}\) is the twisting-cochain curvature;
  \(\mathcal O_{\mathrm{cobar}}\) is the associated-graded cone plus
  tower defect; \(\mathcal O_{\mathrm{PBW}}\) is the PBW
  separatedness/associated-graded defect; \(\mathcal O_{P_0}\) is
  bracket-admissibility and transferred-model failure; and
  \(\mathcal O_{\mathrm{cyc}}\) is the cyclic trace compatibility
  obstruction.

  \item \emph{Finite-window dg LQT comparison.}
  The repaired finite-window comparison uses the quotient dg algebra
  \(A_{\psi,K}=A_\psi/F^{>K}A_\psi\), with \(F^{>K}\) the two-sided
  dg ideal generated by words of total Koszul weight \(>K\) for
  \[
    \operatorname{wt}(x)=(1,0),\qquad
    \operatorname{wt}(y)=(0,1),\qquad
    \operatorname{wt}(\psi)=(1,1).
  \]
  On the stable single-cycle image of the trace-cycle map
  \[
    \Theta_{N,K,L}\colon CC_{\mathrm{red},\le L}(A_{\psi,K})[1]
    \to
    C_{*,\le L}^{\mathrm{CE}}(\mathfrak{gl}_N(A_{\psi,K}))^{GL_N},
  \]
  the finite-window map is
  \(\lambda_{\mathrm{LQT},K,L}
  =\Theta_{N,K,L}^{-1}P_{1\mathrm{cyc}}\).
  The theorem-grade projection is the stable block-sum Hopf Eulerian
  idempotent
  \[
    P_{1\mathrm{cyc}}
    =
    \log^*(\operatorname{id})
    =
    \sum_{m=1}^{L}\frac{(-1)^{m-1}}{m}
    (\operatorname{id}-u\epsilon)^{*m}.
  \]
  This closes only after the stable range
  \(N\geq\max(K,L+2)\), or \(N\geq W+2\) under one bound, controls both
  Koszul weight and CE length.  Under one bound \(W\), the notations
  \(A_{\psi,W}\), \(\Theta_{N,W}\), and \(\lambda_{\mathrm{LQT},W}\) are
  abbreviations for \(K,L\le W\).  This projection also requires the
  scalar-Koszul chain quotient to kill
  \(\Theta_1(\psi)\mapsto\Theta_1(xy-yx)\).  The unqualified primitive
  formula is obstructed by
  \[
    \mathcal O_{\mathrm{LQT},K,L}
    =
    (\mathcal O_{\mathrm{win}},
     \mathcal O_{\mathrm{Prim}},
     \mathcal O_{\mathrm{stab}},
     \mathcal O_{\mathrm{scalar}},
     \mathcal O_{\mathrm{CC}},
     \mathcal O_{\mathrm{Roos}}).
  \]
  The raw same-rank operation that keeps one-cycle tensors and deletes
  fixed-rank multicycles is not a chain map:
  \(d_{\mathrm{CE}}(\Theta_1(a)\wedge\Theta_1(b))\) has a single-cycle
  commutator component, while deletion before the differential gives
  zero.  The finite-rank bridge must use separated-block stabilization:
  with \(B(K,L)=\max(K,L+2)\) and \(M=L\,B(K,L)\),
  \(\beta_{M,K,L}\) is the normalized signed average over injections into
  the \(L\) labeled diagonal blocks, \(\alpha_{M,K,L}\) forgets block
  labels, \(\alpha_{M,K,L}\beta_{M,K,L}=\operatorname{id}\), and the
  strict separated-block idempotent is
  \[
    P^{\mathrm{sep}}_{M,K,L}
    =
    \beta_{M,K,L}P_{1\mathrm{cyc}}\alpha_{M,K,L}.
  \]
  The same-rank bridge is obstructed by
  \[
    \Gamma_N=d_{\mathrm{same}}F_N-F_Nd_{\oplus},
    \qquad
    \Gamma_N(\Theta_1^N(a)\wedge\Theta_1^N(b))
    =
    \pm\Theta_1^N(ab-(-1)^{|a||b|}ba).
  \]

  \item \emph{Reduced CE/PV central-operation generator map.}
  The reduced formal central-operation map is determined on CE/PV
  generators by
  \[
    c^I\mapsto\theta^I,\qquad u_I\mapsto O_I .
  \]
  The boundary Hamiltonian observable is sourced by the shifted
  cotangent coordinate \(u_I\).  This type check is part of the theorem:
  \(c^I\) gives the vector-field operation, while \(u_I\) gives the
  Hamiltonian boundary coordinate.

  \item \emph{Constructed chiral algebra interface.}
  A constructed curve chiral algebra can enter the local mixed HT
  manuscript only through an interface
  \[
    \mathfrak I_{\mathrm{ch}}
    =
    (\mathcal R_{\C\times\R},
     \mathcal F_{\mathrm{red}},
     V_{\mathrm{red}},
     Q_{\mathrm{BRST}},
     \mathbf 1,T,Y,\operatorname{wt},
     \zeta_\hbar,H_{\mathrm{anom}}),
  \]
  not as the native \(\C^2\) holomorphic \(E_2\) object.  The reduction
  \(\mathcal R_{\C\times\R}\) must retain the \(z_2\)-mode or full
  two-index principal-part coefficient system; otherwise the
  Hamiltonian bracket, Moyal bivector, scalar cocycle, and second matrix
  brane coordinate are destroyed.  The exact admission obstruction is
  \[
    \operatorname{Ob}_{\mathfrak I_{\mathrm{ch}}}
    =
    (\operatorname{Ob}_{\mathrm{red}},
     \operatorname{Ob}_{\mathrm{vert}},
     \operatorname{Ob}_{\mathrm{Zhu}},
     \operatorname{Ob}_{\mathrm{nat}}),
  \]
  whose entries measure the retained-mode pushforward and anomaly
  transport, the finite Laurent/OPE and BRST vertex package, the
  zero-mode/Zhu multiplicativity, Capelli shift, and completed stable
  Hochschild/HKR/CE-PV comparison, and the comparison back to
  \(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}\).

  \item \emph{Matlis/local-cohomology cotangent source.}
  The continuous cotangent module is
  \[
    \mathcal P=
    \operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
    \subset H^2_{\mathfrak m}(\C[[z_1,z_2]])\,dz_1dz_2,
  \]
  with basis
  \[
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}dz_1dz_2,\qquad a+b>0.
  \]
  The coadjoint action is
  \[
    z_1^p z_2^q\cdot\rho_{a,b}
    =
    -(pb-qa+p-q)\rho_{a-p+1,b-q+1}.
  \]

  \item \emph{BMK one-pair pro-Matlis retract and native all-window
  obstruction.}
  The positive all-window datum presently constructed is one-pair and
  analytic:
  \[
    \bar\partial H_\chi^0+H_\chi^0\bar\partial
    =
    \operatorname{id}-I_{\mathrm{an}}P_{\mathrm{an}},
    \qquad
    P_{\Pi}^{\mathrm{an}}=\tau P_{\mathrm{an}},
    \qquad
    \pi_NP_{\Pi}^{\mathrm{an}}=p_N .
  \]
  It is not a native support-local factorization-current transfer.  The
  strict native all-window current theorem is exactly the vanishing, or
  constructive replacement in a changed habitat, of
  \[
    \operatorname{Ob}^{\Pi}_{\mathrm{BM}}
    =
    (\operatorname{ob}_{\oplus},
     \operatorname{ob}_{I_\Pi},
     \operatorname{ob}_{\mathfrak h,\Pi},
     \operatorname{ob}_{\mathrm{collar},\Pi},
     \operatorname{ob}_{3,\Pi},
     \operatorname{ob}_{\mathrm{unif},\Pi}).
  \]
  Here \(\operatorname{ob}_{\oplus}\) is the failure of all moments to
  land in the direct-sum Matlis module; \(\operatorname{ob}_{I_\Pi}\) is
  the nonexistence of a compact-current section of the pro-product tower;
  and \(\operatorname{ob}_{\mathfrak h,\Pi}\) is the failure of the full
  formal Hamiltonian action on that target, detected by the divergent
  \(\rho_{0,1}\)-coefficient for
  \(f=\sum_{p\ge2}z_1^p\) acting on
  \(\lambda=\sum_{p\ge2}\rho_{p-1,0}\).  The first, second, third, and
  sixth entries are nonzero in the native current/product topology; the
  collar and ternary entries are exact primitive construction targets.

  \item \emph{Primitive higher-\(\psi\) Hamiltonian extraction.}
  The full primitive Koszul complex for \(Q\psi=[x,y]\) extracts the
  Hamiltonian sectors:
  nonconstant \(H_0\) classes, primitive one-\(\psi\) classes
  \(\Psi_{a,b}\), and no primitive \(p\ge2\) homology.  The one-\(\psi\)
  action is
  \[
    \{\overline{\operatorname{Tr}(\phi_1^p\phi_2^q)},
      \widetilde\Psi_{a,b}\}
    =(pb-qa)\widetilde\Psi_{a+p-1,b+q-1},
  \]
  with negative targets zero and scalar targets killed in the
  Hamiltonian quotient.

  \item \emph{Principal-part versus polynomial-descendant criterion.}
  The polynomial one-\(\psi\) and principal-part modules have opposite
  linear-Hamiltonian behavior:
  \[
    \{O_{1,0},\widetilde\Psi_{a,b}\}
      =b\,\widetilde\Psi_{a,b-1},
    \qquad
    \{O_{0,1},\widetilde\Psi_{a,b}\}
      =-a\,\widetilde\Psi_{a-1,b},
  \]
  while
  \[
    z_1\cdot\rho_{a,b}=-(b+1)\rho_{a,b+1},
    \qquad
    z_2\cdot\rho_{a,b}=(a+1)\rho_{a+1,b}.
  \]
  This local-nilpotence obstruction is the necessary condition for any
  proposed polynomial realization of \(\mathcal P\): it must change the
  target, the action, or the category.

  \item \emph{\(\mathcal D_\hbar\) Fourier--Rees bridge.}
  With
  \[
    \begin{aligned}
    \mathcal D_\hbar
    ={}&
    \C[[\hbar]]
      \langle z_1,z_2,\partial_1,\partial_2\rangle\\
    &/
      ([\partial_i,z_j]=\hbar\delta_{ij}),
    \end{aligned}
  \]
  the Fourier delta module
  \(\Delta^{\mathsf F}_\hbar=\mathcal D_\hbar/(z_1,z_2)\) gives
  \[
    z_1^az_2^b\mapsto
    \partial_1^a\partial_2^be_0
    \mapsto
    (-1)^{a+b}\hbar^{a+b}a!b!\rho_{a,b}.
  \]
  Before \(\hbar\) is inverted, the image is the Rees sublattice
  \(\bigoplus\hbar^{a+b}\C[[\hbar]]\rho_{a,b}\).  The same-action
  obstruction forbids a flat Rees family that identifies polynomial
  one-\(\psi\) descendants with \(\mathcal P\) as modules for the
  original Hamiltonian action.

  \item \emph{One-antifield Moyal target.}
  The reduced distributional principal-part target has bracket
  \[
    \{B_f(a),\Theta_\rho(B)\}_\hbar
      =
      \Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}(aB),
    \qquad
    \{\Theta_\rho(B),\Theta_\sigma(C)\}_\hbar=0.
  \]
  A strict quantum descendant lift of the classical label shadow is
  excluded by the leading-term calculation
  \[
    z_1\cdot_0\widetilde\Psi_{1,0}=0,\qquad
    z_1\cdot\rho_{1,0}=-\rho_{1,1}.
  \]

  \item \emph{Weighted finite-window regulator independence.}
  A regulator-admissible sector is a strict Mittag-Leffler family on
  finite windows with graphwise bounded Hamiltonian and cotangent legs.
  For admissible weights \(w,w'\), diagonal transports
  \(R^{w_0}_{w,w'}\) identify the local-functional complexes and carry
  the obstruction class
  \[
    \mathrm{Ob}_w\in
    H^1_{\mathrm{adm}}(\mathcal O_{\mathrm{loc}}(\mathcal E_w),
      Q+\{I_0^w,-\})
  \]
  to \(\mathrm{Ob}_{w'}\).  Thus QME vanishing is invariant under
  admissible finite-window weight.

  \item \emph{Endpoint admissibility.}
  An endpoint for \(w_q(d)=q^d\) is accepted by conditions (E1)--(E5):
  strict Mittag-Leffler quotients, a coefficient kernel projecting to
  every finite Casimir, transport of differential, bracket, coadjoint
  action, propagator, interaction, counterterms, and the generator map
  \(c\mapsto\theta,\ u\mapsto O\), admissible filtered cohomology, and
  RG preservation.  The endpoint obstruction tuple is
  \[
    \mathfrak o_{\mathrm{BV,end}}
    =
    (\mathfrak o_{\mathrm{Cas}},
     \mathfrak o_{\mathrm{def}},
     \mathfrak o_{\mathrm{RG}},
     \mathfrak o_{\mathrm{QME}}).
  \]
  The strict product/direct-sum pair fails the criterion because no
  tensor \(K\) projects to all finite Casimirs
  \(C^M_{\mathfrak h}\).

  \item \emph{Mixed brane-defect QME complex.}
  The local-functional obstruction lives in
  \[
    H^1\bigl(\mathcal O_{\mathrm{loc}}(\mathcal E_w),
      Q+\{I_0,-\}\bigr).
  \]
  Its scalar component is computed by
  \[
    \begin{aligned}
    \{I_\partial(a,f),I_\partial(b,g)\}_{\mathrm{open}}
    ={}&
    I_\partial(ab,\{f,g\}_{\bar A})\\
    &+N\,\omega(f,g)\int_\R a(t)b(t)\,dt ,
    \end{aligned}
  \]
  or, in Weyl normalization,
  \[
    \begin{aligned}
    \operatorname{Tr}(A\,XY)-\operatorname{Tr}(A\,YX)
      ={}&\hbar N\,\operatorname{Tr}(A)\\
      &\quad\bmod\ \mathcal W_N\widehat\mu(\lie{sl}_N).
    \end{aligned}
  \]
	  The brane stack is still ordinary \(\mathfrak{gl}_N\), but the quantum
	  moment-map ideal is traceless after the scalar comoment vanishes.
  With the central ghost \(\gamma_{\mathbf 1}\), the representative is
  \[
    \operatorname{Ob}_{\mathrm{sc}}
    =
    \hbar N\,\omega(f,g)
    \int_\R a(t)b(t)\gamma_{\mathbf 1}(t)\,dt .
  \]
	  A scalar-reduced ordinary \(\mathfrak{gl}_N\) lift requires
	  \(W_{\mathrm{ext}}\) with leading class
	  \[
	    [w_{\mathrm{ext}}]=-\hbar N[\bar c]
	    \qquad\text{in }H^2_{\mathrm{Lie}}(\bar A;\C)[[\hbar]].
	  \]
	  Alternatively, the unreduced central-character source and the opposite
	  central extension
	  \(\bar A^{\mathrm{cl}}_{-\hbar N\bar c}\) absorb the scalar symbol
	  before it becomes a reduced-source obstruction, while a
	  Casimir-balanced supertrace model makes the scalar representative
	  zero.  In the opposite branch
	  \(J_{\mathrm{op}}=-k^\vee\) satisfies
	  \(d_{\mathrm{CE}}J_{\mathrm{op}}=-\hbar N\bar c\); forgetting the
	  central line restores the class \(\hbar N[\bar c]\) on \(\bar A\).
	  The finite-window algebraic repair obtained by adjoining a
	  defect-supported central closed source line is a legitimate changed
	  branch: with generator \(e_M\) and
	  \[
	    \Xi^{\mathrm{alg},\mathrm{sc}}_M(e_M)
	    =
	    -\hbar N\,\bar c_M
	  \]
	  on the scalar-contact line, one may take \(W_M=e_M\) and \(C_M=0\),
	  so that
	  \(\beta^{\mathrm{sc}}_M=\beta^{\mathrm{sc}}_{\mathrm{cl}}
	  =\mu^{\mathrm{sc}}_{\mathrm{cl}}
	  =\lambda^{\mathrm{sc}}_C=0\) in that enlarged algebraic cone.  This
	  is not yet a Costello-local closed-exchange theorem.  Without a
	  closed field, bulk-to-defect propagator, locality/support rule,
	  scalar-contact chain projection on the original ordinary complex,
	  and compatible finite-window/Roos representatives, the original
	  scalar-reduced branch remains blocked first by
	  \[
	    o_{\sigma,M}^{(1),\mathrm{sc}}
	    =
	    \hbar N[\bar c_M]\neq0,
	  \]
	  and then, for any supplied genuine closed-exchange tower, by
	  \[
	    \beta^{\mathrm{sc}}_M,\quad
	    \beta^{\mathrm{sc}}_{\mathrm{cl}},\quad
	    \mu^{\mathrm{sc}}_{\mathrm{cl}},\quad
	    \lambda^{\mathrm{sc}}_C .
	  \]

  \item \emph{Componentwise quantum coefficient surface and non-scalar
  obstruction complex.}
  The componentwise theorem datum is
  \[
    \mathfrak S_{\hbar,w}(I)
      =
      \mathcal K_{\mathrm{BV}}^w
      \times\{0_{\mathrm{sc}}\}
      \times A^{\mathrm{pp},w}_{\partial,\hbar}(I)
      \times T_{\mathrm{Ham},\hbar}.
  \]
  Here \(\mathcal K_{\mathrm{BV}}^w\) is the weighted
  coefficient-kernel datum, \(0_{\mathrm{sc}}\) is the balanced
  supertrace scalar QME representative, \(A^{\mathrm{pp},w}_{\partial,\hbar}(I)\)
  is the reduced weighted Moyal principal-part current target, and
  \(T_{\mathrm{Ham},\hbar}\) is the degree-zero Hamiltonian trace target
  governed by the radial/Weyl dual-potential decorated-Stokes gate.  The
  present theorem
  includes the algebraic Moyal coefficients, the Capelli scalar-contact
  relation, the all-edge PBW telescoping theorem for
  \((2,b)\) and \((a,2)\), and finite normal-form certificates for the
  balanced diagonal through \((6,6)\), all non-edge bidegrees of total
  degree at most \(13\), and the total-degree \(14\) cases
  \[
    (3,11),(11,3),(4,10),(10,4),(5,9),(9,5).
  \]
  The remaining all-interior theorem is not an external slogan:
  it is the vanishing of the dual-potential obstruction
  \[
    \Omega^{\mathrm{rad}}_{a,b}
    =
    [(T_{a,b},E^+_{a,b})]\in\operatorname{coker}B_{a,b},
  \]
  equivalently the decorated PBW Stokes condition
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\) for every bidegree.  Failure is
  exactly a signed row \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\).
  The reduced Moyal current brackets are
  \[
    \{B_f(a),B_g(b)\}_\hbar
      =B_{\{f,g\}_\hbar}(ab),\qquad
    \{B_f(a),\Theta_\rho(B)\}_\hbar
      =
      \Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}(aB),
  \]
  \[
    \{\Theta_\rho(B),\Theta_\sigma(C)\}_\hbar=0,
  \]
  with the full Moyal coadjoint action on the weighted continuous
  coefficient module.  This is a proved componentwise target surface,
  not a Costello graph/QME construction.

  The next theorem obligation is the constructive non-scalar
  Costello/QME problem.  For each finite window one must first supply a
  codimension-two closed marked Costello list
  \(\mathcal G_M^{\mathrm{mk}}\), with every field-differential, BV-edge,
  collision/contact, counterterm, and CE-source face carrying its output
  graph, coefficient, marker transport, incidence sign, and lower-window
  truncation.  Missing any one of these entries means that the marked
  graph differential and the Hom-valued Bianchi identity have not been
  constructed.

  The target complex is the completed local-functional complex
  \[
    \mathfrak Q^\bullet_{\mathcal G,M}(I)
      =
    \left(
      \mathcal O_{\mathrm{loc},\mathcal G,M}^{\mathrm{bd}}\bigl(
        \mathcal E^M_w|_I;\,
        A^{\mathrm{pp},w,M}_{\partial,\hbar}(I)\bigr),
      d_M=Q+\{I^w_{0,M},-\}_{\hbar,M}
    \right),
  \]
  complete for the \(\hbar\)-adic, scalar-contact, and finite-window
  filtrations.  The Hom kernel complex is
  \[
    \mathbf K^\bullet_{\mathcal G,M}(I)
      =
    \operatorname{Hom}_{\mathrm{cont}}\!
    \left(C^\bullet_{\mathrm{lab}}(\mathcal G_M),
      \mathfrak Q^\bullet_{\mathcal G,M}(I)\right),
  \]
  with
  \[
    d_{\mathbf K,M}T
      =
    d_MT-(-1)^{|T|}T\,d_{\mathrm{CE}},
    \qquad
    \operatorname{Curv}_{\mathbf K,M}(\kappa)
      =
    d_{\mathbf K,M}\kappa+\frac12[\kappa,\kappa]_{\mathbf K,M}.
  \]
  The source-face term \(-\kappa d_{\mathrm{CE}}\) is therefore part of
  the QME row calculation, not a later convention.

  The bulk-to-defect kernel is a continuous current-valued cochain
  candidate
  \[
    \kappa_{\hbar,w,I}\colon
    C^\bullet_{\mathrm{CE},\mathrm{cont}}
    (\mathfrak g^{w,\mathrm{cur}}_{\hbar,I})
      \longrightarrow
    \mathfrak Q^\bullet_{\mathcal G,M}(I),
  \]
  where the current source is either restricted to regular compactly
  supported densities, placed in the sign-conic finite-scaling habitats
  \(\mathcal D'_{c,\Lambda_\pm,\mathrm{fs}}(I)\) for ordinary
  collision-conormal graph kernels, or equipped with the graphwise
  wavefront/counterterm relation
  \(\mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)\).  Its zero-edge values
  are fixed by the coefficient theorem,
  \[
    u_{a(t)dt\otimes f}\mapsto \iota_I(B^{w,M}_f(a)),
    \qquad
    c_{B,\rho}\mapsto\iota_I(\Theta^{w,M}_\rho(B)),
  \]
  while the positive-edge values must be actual renormalized graph
  weights
  \[
    K^M_\Gamma=W^{R,M}_{\Gamma,L,w}(B^\Gamma_\bullet).
  \]
  The exact current-kernel obstruction is the curvature class in
  \(H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})\); Costello's
  general BV/RG formalism supplies the habitat, not these local
  Hamiltonian current weights.

  Before this class is defined, choose a complete
  \(d_{\mathrm{QME}}\)-stable scalar-contact filtration and a filtered
  chain projection
  \[
    \widehat\sigma_{\mathrm{sc},M}\colon
    \mathfrak Q^\bullet_{\mathcal G,M}(I)
      \longrightarrow
    C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]]
  \]
  whose associated graded is the scalar-symbol projection.  In the
  balanced supertrace branch the scalar-lift tower
  \(o_{\sigma,w}^{(r)}(I)\) of
  Lemma~\ref{lem:filtered-scalar-projection-obstruction} must vanish
  before the reduced non-scalar complex is formed.  Then
  \(\mathcal Q^\bullet_{w,M}(I)=\ker\widehat\sigma_{\mathrm{sc},M}\)
  is the finite-window non-scalar complex, and the remaining class
  \[
    [\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]
      \in
    H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})
  \]
  must be killed.

  At order \(n\), after lower counterterms \(C_{<n,M}\) have been chosen,
  the mandatory marked row types are
  \[
    R^{\mathrm{row}}_{d\Gamma,M}
      =
    \varepsilon_\Gamma d_MK^M_\Gamma,\qquad
    R^{\mathrm{row}}_{\mathrm{CE}(\Gamma,\nu),M}
      =
    -\varepsilon^{\mathrm{CE}}_{\Gamma,\nu}K^M_\Gamma(\zeta_{M,\nu}),
  \]
  \[
    R^{\mathrm{row}}_{b(\Gamma_1,\Gamma_2),M}
      =
    \frac12\varepsilon_{\Gamma_1,\Gamma_2}
    \{K^M_{\Gamma_1},K^M_{\Gamma_2}\}_{\hbar,M},
  \]
  together with the homogeneous lower-counterterm contribution
  \[
    [\hbar^n]\left(
      d_MC_{<n,M}
      +\frac12\{C_{<n,M},C_{<n,M}\}_{\hbar,M}
    \right).
  \]
  Their scalar row sum must vanish before non-scalar cohomology is
  tested.  If it vanishes, the residual
  \(R^{\mathrm{ns}}_{n,M}\in\mathcal Q^1_{w,M}(I)\) represents
  \(\mathfrak o^{\mathrm{ns}}_{n,M}\).

  Choose row coordinates \(\rho^M_i\) and degree-zero primitive
  candidates \(\eta^M_j\):
  \[
    R^{\mathrm{ns}}_{n,M}=\sum_i r^M_i\rho^M_i,\qquad
    d_{\mathrm{ns},M}\eta^M_j=\sum_iA^M_{ij}\rho^M_i .
  \]
  A fixed-window counterterm exists exactly when the row equation
  \[
    A^Mc=-r^M
  \]
  is solvable.  Failure is certified by a left-cokernel functional
  \[
    \ell A^M=0,\qquad \ell(r^M)\ne0 .
  \]
  Windowwise solutions form an inverse-limit theorem only after row and
  primitive transports satisfy
  \[
    T^{M,N}r^M=r^N,\qquad
    T^{M,N}A^M=A^NP^{M,N},
  \]
  and the Roos primitive class
  \[
    [P^{M,N}c_M-c_N]\in H^0(\mathcal Q^\bullet_{w,N}(I))
  \]
  vanishes.  For larger graph packages the transition matrices
  \(u^{M,N}\) for seed rows, \(v^{M,N}\) for CE-source faces,
  \(q^{M,N}\) for bracket rows, and \(P^{M,N}\) for primitives are
  construction data.  The order-\(n\) obstruction vector is
  \[
    \mathfrak O^{\mathrm{ns}}_n
      =
    \bigl(([\mathfrak o^{\mathrm{ns}}_{n,M}])_M,\lambda_n\bigr),
  \]
  as in Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.  Thus
  changing admissible weight or passing to a finite window is not itself
  a cancellation mechanism.

	  A closed-exchange repair is extra cochain data.  It consists of a
	  strict Mittag--Leffler tower of closed-exchange local-functional
	  complexes
	  \[
	    \mathcal X^\bullet_{w,M}(I)
	  \]
	  and compatible cochain maps
	  \[
	    \Xi_M\colon
	    \mathcal X^\bullet_{w,M}(I)
	      \longrightarrow
	    \mathcal Q^\bullet_{w,M}(I),
	    \qquad
	    \pi_{M,N}\Xi_M=\Xi_N\pi_{M,N},
	    \qquad
	    R^M_{w,w'}\Xi_M=\Xi'_M R^M_{w,w'} .
	  \]
	  The complex \(\mathcal X^\bullet_{w,M}(I)\) must encode the closed
	  propagator, bulk-to-defect restriction, wavefront/locality rule, and
	  Costello counterterm support.  At the first non-scalar order the
	  branch equation is
	  \[
	    \mathfrak o^{\mathrm{ns}}_{n_0,M}
	      +\Xi_M(W_{n_0,M})
	      +d_M C_{n_0,M}=0,
	    \qquad
	    W_{n_0,M}\in Z^1(\mathcal X^\bullet_{w,M}(I)),\quad
	    C_{n_0,M}\in\mathcal Q^0_{w,M}(I).
	  \]
	  The finite-window branch is theorem-grade exactly in the following
	  sense.  For a fixed \(M\), such \(W_{n_0,M}\) and \(C_{n_0,M}\) exist
	  if and only if
	  \[
	    [\mathfrak o^{\mathrm{ns}}_{n_0,M}]
	      \in
	    -\,\operatorname{im}
	    \Bigl(
	      H^1(\Xi_M)\colon
	      H^1(\mathcal X^\bullet_{w,M}(I))
	      \to
	      H^1(\mathcal Q^\bullet_{w,M}(I))
	    \Bigr).
	  \]
	  In the compatible finite-window inverse limit this becomes the
	  closed-exchange branch class
	  \[
	    \beta^{\mathrm{cl}}_{n_0}
	      =
	      \bigl([\mathfrak o^{\mathrm{ns}}_{n_0,M}]\bigr)_M
	      \quad\text{in}\quad
	      \operatorname{coker}\!\left(
	        \varprojlim_M H^1(\mathcal X^\bullet_{w,M}(I))
	        \xrightarrow{\ \varprojlim H^1(\Xi_M)\ }
	        \varprojlim_M H^1(\mathcal Q^\bullet_{w,M}(I))
	      \right),
	  \]
	  together with a closed-exchange representative-compatibility class
	  \[
	    \mu^{\mathrm{cl}}_{n_0}
	      \in
	      \varprojlim\nolimits^1_M
	      H^0(\mathcal X^\bullet_{w,M}(I))
	  \]
	  and the usual counterterm primitive-compatibility class
	  \[
	    \lambda^{\mathrm{cl}}_{n_0}
	      \in
	      \varprojlim\nolimits^1_M
	      H^0(\mathcal Q^\bullet_{w,M}(I)).
	  \]
	  Vanishing of these three classes is equivalent to a compatible
	  closed-exchange kernel plus local counterterm killing the first
	  non-scalar residual.  The proof is the elementary cohomology
	  calculation: the displayed equation implies
	  \([\mathfrak o^{\mathrm{ns}}_{n_0,M}]
	  =-H^1(\Xi_M)[W_{n_0,M}]\); conversely that equality supplies a
	  windowwise closed-exchange class and a primitive \(C_{n_0,M}\).  The
	  inverse-limit obstruction to choosing the closed-exchange cocycles
	  compatibly is \(\mu^{\mathrm{cl}}_{n_0}\), and the obstruction to
	  choosing the counterterm primitives compatibly is
	  \(\lambda^{\mathrm{cl}}_{n_0}\).  A counterterm-only branch is the special
	  case \(\mathcal X^\bullet_{w,M}(I)=0\).  What remains open is not a
	  scalar QME objection, but the construction of \(\mathcal X^\bullet\),
	  \(\Xi\), and a class \([W]\) mapping to
	  \(-[\mathfrak o^{\mathrm{ns}}_{n_0}]\).

  The first certified larger-row test is the \(\theta_3\) row.  In the
  one-row finite-window package currently supplied by the graph-array
  calculation, the non-scalar scalar-zero subcomplex is
  \[
    \mathcal Q^0_{\theta_3,M}=0,\qquad
    \mathcal Q^1_{\theta_3,M}
      =\C\mathsf E_{\theta_3,M},\qquad d_M=0,
  \]
  with residual
  \[
    \mathfrak o^{\mathrm{ns}}_{\theta_3,M}
      =\mathsf E_{\theta_3,M},\qquad
    \ell_{\theta_3}(\mathsf E_{\theta_3,M})=1 .
  \]
  Thus the present one-row datum proves
  \([\mathsf E_{\theta_3,M}]\ne0\) in the supplied subcomplex.
  Admissibility repair does not weaken the non-scalar QME theorem; it identifies the
  exact additional construction that would make the stronger theorem true.
  The row is killed precisely by one of the following three pieces of
  added mathematics, with finite-window and weight compatibilities:
  \[
    \text{source ancestor:}\quad
    d_{\mathrm{CE}}\eta_{\theta_3,M}=\zeta_{M,\nu_3},\qquad
    C^{\mathrm{CE}}_{\theta_3,M}=K^M_{\Theta_3}(\eta_{\theta_3,M}),
  \]
  together with the Hom-valued Bianchi identity giving
  \(d_M C^{\mathrm{CE}}_{\theta_3,M}=-\mathsf E_{\theta_3,M}\);
  or
  \[
    \text{local counterterm:}\quad
    C^{\mathrm{ct}}_{\theta_3,M}\in\mathcal Q^0_{w,M}(I),\qquad
    d_M C^{\mathrm{ct}}_{\theta_3,M}=-\mathsf E_{\theta_3,M},
  \]
  with \(\widehat\sigma_{\mathrm{sc},M}(C^{\mathrm{ct}}_{\theta_3,M})=0\);
  or a complete companion-face table whose differential changes the
  row residual from \(\mathsf E_{\theta_3,M}\) to zero.  In all three
  cases the tower obstruction
  \[
    [\pi_{M,N}C_{\theta_3,M}-C_{\theta_3,N}]
      \in H^0(\mathcal Q^\bullet_{w,N}(I))
  \]
  must vanish in the Roos \(\varprojlim^1\)-class.  A name
  \(C_{\theta_3}\) without its local-functional formula, CE ancestor, or
  companion-face differential is not a counterterm.
  The currently tested finite routes are obstructed.  The source
  obstruction is sharper than the degree-\(\le3\) test.  In the ordinary
  pure two-\(u\) CE source envelope, in every finite Hamiltonian degree,
  the covector
  \[
    q_{2u}
    =
    e^*_{((H_{0,1},H_{2,0}),c_{\rho_{2,1}})}
    -\frac12
    e^*_{((H_{0,1},H_{0,1}),c_{\rho_{0,2}})}
  \]
  satisfies
  \[
    q_{2u}d_{\mathrm{CE}}=0,\qquad
    q_{2u}(\zeta_{M,\nu_3})=1.
  \]
  Hence no ordinary pure two-\(u\) degree enlargement supplies a CE
  ancestor for \(\zeta_{M,\nu_3}\).  This is an exact obstruction theorem
  for that source envelope only; it is not a global no-go for
  scalar-zero local counterterms, marked source extensions, or
  Hom-valued companion rows.  The tested eight-face companion expression
  has
  coordinate row
  \[
    (2,-2,3,2,-1,1,-2,-3)
  \]
  on
  \[
    E_{\nu_{02}},E_{\nu_{20}},E_{\nu_{03}},
    E_{\nu_{12}^{(1)}},E_{\nu_{12}^{(2)}},
    E_{\theta_3},E_{\nu_{21}^{(2)}},E_{\nu_{30}},
  \]
  and diagonal transport to \(N=2\) leaves
  \(2E^2_{\nu_{02}}-2E^2_{\nu_{20}}\).  The same eight-face row has
  \(q_{2u}\)-value zero, so it cannot be reused as the missing marked
  source column.  The lower-window functional
  \(\lambda^{(2)}_{\nu_{02}}=\frac12(E^2_{\nu_{02}})^*\) detects the
  transported residual.  A repair must therefore supply exact data not
  present in the tested package: a counterterm column
  \(A^M_{\theta_3,C}=-1\) with
  \(d_MC^{\mathrm{ct}}_{\theta_3,M}=-\mathsf E_{\theta_3,M}\),
  scalar-zero value, and zero Roos class; or a marked source generator
  \(\eta^{\mathrm{mark}}_{\theta_3,M}\) outside the ordinary pure
  two-\(u\) algebra, with a boundary column of \(q_{2u}\)-value \(1\),
  codimension-two closure, Hom-valued Bianchi cancellation, scalar-zero
  value, and compatible transport; or a marked companion relation
  \(R^{\mathrm{cand}}_{\Theta_3,M}=0\) together with lower-window
  transport \(v^{M,N}R^{\mathrm{cand}}_{\Theta_3,M}=0\), including the
  \(N=2\) relation killing
  \(2E^2_{\nu_{02}}-2E^2_{\nu_{20}}\) by a derived non-diagonal
  transport, lower primitive, or relation
  \(E^2_{\nu_{02}}=E^2_{\nu_{20}}\).  The canonical source-coordinate
  lower primitive candidate is
  \[
    \zeta^0_2=u_{a,H_{1,0}}u_{b,H_{0,1}},\qquad
    D^2_{02,20}=K^2_{\Theta_3}(\zeta^0_2),
    \qquad
    d_{\mathrm{CE}}\zeta^0_2
    =
    2\zeta_{\nu_{02}}-2\zeta_{\nu_{20}}.
  \]
  This is source exactness.  In the local-functional complex
  \[
    d_{\mathrm{ns},2}D^2_{02,20}
    =
    -2E^2_{\nu_{02}}+2E^2_{\nu_{20}}
    +\mathfrak b^2_{02,20},
  \]
  where
  \[
    \mathfrak b^2_{02,20}
    =
    d_{\mathrm{ns},2}K^2_{\Theta_3}(\zeta^0_2)
    -
    K^2_{\Theta_3}(d_{\mathrm{CE}}\zeta^0_2).
  \]
  In the Bianchi-exposed lower basis
  \((E^2_{\nu_{02}},E^2_{\nu_{20}},\mathfrak b^2_{02,20})\), the column
  and residual are
  \[
    A_D^2=(-2,2,1)^T,\qquad r_2=(2,-2,0)^T .
  \]
  The cokernel
  \[
    \widetilde\lambda_{02,\mathfrak b}
    =
    \frac12(E^2_{\nu_{02}})^*
    +(\mathfrak b^2_{02,20})^*
  \]
  kills \(A_D^2\) and evaluates to \(1\) on \(r_2\).  The source
  primitive becomes a genuine local-functional primitive only after
  \(\mathfrak b^2_{02,20}\) is killed, or after adding a scalar-zero local
  counterterm \(B^2_{02,20}\) with
  \(d_{\mathrm{ns},2}B^2_{02,20}=-\mathfrak b^2_{02,20}\), locality or
  wavefront admissibility, and compatible transport.  The current
  finite-row habitat contains no such \(B^2_{02,20}\): the desired target
  \((0,0,-1)^T\) is not in the image of \(A_D^2\), because
  \[
    \widetilde\lambda_{02,\mathfrak b}A_D^2=0,\qquad
    \widetilde\lambda_{02,\mathfrak b}((0,0,-1)^T)=-1 .
  \]
  The next construction target is therefore a genuine scalar-zero
  local-functional column \(A_B^2=(0,0,-1)^T\), not a relabelling of the
  source primitive.  In a tower the named Bianchi transport cocycle is
  \[
    \Delta^1_{M,N}
    =
    -\pi_{M,N}\mathfrak b^M+\mathfrak b^N .
  \]
  A compatible family \(B^M\) would kill it by
  \[
    \Delta^1_{M,N}
    =
    d_{\mathrm{ns},N}(\pi_{M,N}B^M-B^N).
  \]
  Thus the tower must first kill the \(H^1\) class of
  \(\Delta^1_{M,N}\); after a choice of primitive, it must also kill the
  resulting secondary \(\varprojlim^1H^0\) class.  The tested finite
  routes do not close the row.

  \item \emph{Unreduced factorization-current lift.}
	  The unreduced cotangent lift is a datum:
	  distributional principal-part boundary fields, product centrality
	  homotopies, \(P_0\)-bracket homotopies, a coefficient kernel, a
	  brane-defect propagator, and a QME solution.  Polynomial boundary
	  representatives are ruled out by the local-nilpotence theorem; the
	  accepted target is the principal-part current sector; the centrality
	  homotopies must be supplied as additional unreduced lift data.  In
	  convolution form an unreduced coupling
	  \[
	    \kappa\colon C^\bullet_{\mathrm{CE}}(\mathfrak g)
	    \longrightarrow Z^{P_0}_{\mathrm{fact}}(A_{\mathrm{BV}})
	  \]
	  must first satisfy
	  \[
	    \operatorname{Curv}(\kappa)
	    =d\kappa+\frac12[\kappa,\kappa]=0,
	  \]
		  and then pass the descent and QME tests.  A chain-level
		  normal-ordering lift is separate data: either a cut-dependent
		  no-\(\psi\) straightening as in
		  Theorem~\ref{thm:normal-ordering-straightening-homotopy}, or a
		  genuinely larger target retaining the descendant module together with
		  maps \(N,i,H\) satisfying the relevant deformation of
		  \(QH+HQ=\mathrm{id}-iN\).  Only in such a larger target could one
		  attempt to form a correction.  After matching the bracket convention of
		  Construction~\ref{constr:boundary-local-dual-principal-parts}, the
		  defect
		  \[
		    \{O_f,\Theta_\rho\}-\Theta_{f\cdot\rho}
		  \]
		  would have to be \(Q\)-exact; no fixed formula for that homotopy is
		  asserted before the target and signs are constructed.
  Until these maps are constructed in the chosen target, the
  principal-part cotangent lift is an obligation rather than a theorem.
  Moreover, the explicit normal-ordering straightening now proved in the
  body is only the cut-dependent no-\(\psi\) calculation.  A full cyclic
  contraction with \(N\) killing all one-\(\psi\) descendants is
  impossible by Lemma~\ref{lem:no-full-cyclic-normal-ordering-contraction};
  any genuine unreduced lift must retain those descendant classes or
  replace the target by a larger homotopy-coherent object.

  \item \emph{Stratified brane prefactorization and module datum.}
  Let
  \[
    X=\R_t\times\R_s\times\C^2_{z_1,z_2},\qquad
    L=\R_t\times\{s=z_1=z_2=0\}.
  \]
  For a finite normal/Hamiltonian window \((N,M)\), let
  \(\mathsf X_{N,M}\) be the set of nonzero moving characters occurring
  in that window, containing the relevant characters
  \[
    n\epsilon_s+a\epsilon_1+b\epsilon_2,\qquad
    n\epsilon_s-a\epsilon_1-b\epsilon_2 .
  \]
  The coefficient ring for the equivariant obligation is
  \[
    R_\Omega^{N,M}
    =
    \C[\epsilon_s,\epsilon_1,\epsilon_2,\hbar_\omega]
    [\chi^{-1}\mid \chi\in\mathsf X_{N,M}].
  \]
  On the self-dual branch one first imposes
  \(\epsilon_1+\epsilon_2=0\), then inverts only the surviving nonzero
  characters; resonant summands stay in \(\operatorname{pr}_{\chi=0}\).
  A field-valued theorem may replace this by a declared \(K_\Omega\), but
  not by an undeclared Laurent field in the three weights.
  The brane theorem datum is not an ordinary bulk factorization algebra
  with a boundary algebra added afterwards.  The stronger datum is a
  stratified prefactorization algebra on the pair \((X,L)\),
  \[
    \mathcal F^{\mathrm{str}}_{\Omega,N}\colon
    \operatorname{Disk}^{\mathrm{str}}_{X,L}
      \longrightarrow
    \operatorname{Ch}_{R_\Omega^{N,M}[[\hbar_{\mathrm{QME}}]]},
  \]
  where \(\operatorname{Disk}^{\mathrm{str}}_{X,L}\) contains bulk
  mixed holomorphic-topological disks in \(X\setminus L\), brane intervals
  in \(L\), and collars meeting the lower stratum.  Its missing values
  are part of the data:
  \[
    \mathcal F^{\mathrm{str}}_{\Omega,N}(U\subset X\setminus L)
    =
    C^\bullet_{\mathrm{CE},\mathrm{cont}}
    \bigl(\mathfrak g^{\mathrm{mix}}_{\Omega,\hbar_\omega}(U)\bigr),
  \]
  \[
    \mathcal F^{\mathrm{str}}_{\Omega,N}(I\subset L)
    =
    A^q_{N,\Omega}(I)
    \quad\text{or}\quad
    A^{\mathrm{pp},w}_{\partial,\Omega,\hbar_{\mathrm{W}}}(I),
  \]
  together with a collar module
  \[
    \mathcal M_{\Omega,N}(U;I)
  \]
  carrying the bulk-to-brane structure maps.  The finite-\(N\) brane
  algebra branch is the equivariant quantum Hamiltonian reduction
  \[
    A^q_{N,\Omega}
    =
    \operatorname{Weyl}_{\hbar_{\mathrm{W}}}(\operatorname{Mat}_N^2)
    //_{\hbar_{\mathrm{W}}} GL_N,
    \qquad
    YX-XY+\hbar_{\mathrm{W}}N I=0,
  \]
  with \(w(X)=\epsilon_1\), \(w(Y)=\epsilon_2\), and
  \(w(\hbar_{\mathrm{W}})=\epsilon_1+\epsilon_2\).  The stable
  principal-part branch is the weighted current target already recorded
  above.  Choosing one branch, or constructing a comparison between them,
  is not optional notation; it is part of the stratified object.
  The three formal parameters remain separate:
  \[
    \hbar_{\mathrm{QME}},\qquad
    \hbar_{\mathrm{W}},\qquad
    \hbar_\omega .
  \]
  Here \(\hbar_{\mathrm{QME}}\) counts Costello/BV loop order,
  \(\hbar_{\mathrm{W}}\) deforms the Weyl/Moyal brane algebra, and
  \(\hbar_\omega\) scalarizes the equivariant Hamiltonian bracket.  A
  Weyl branch may impose \(\hbar_{\mathrm{W}}=\hbar_\omega\); no branch
  identifies either parameter with \(\hbar_{\mathrm{QME}}\) without a
  separate QME obstruction calculation.

  The required structure maps are the extension-by-zero products for
  mutually disjoint stratified disks, the collar restriction maps from
  bulk insertions to brane modules, and descent for stratified Weiss
  covers.  The first obstruction cochains are
  \[
    \delta_{\mathrm{pref}}\mu_{\mathrm{str}}
      =
      d\mu_{\mathrm{str}}
      -\mu_{\mathrm{str}}d,\qquad
    \delta_{\mathrm{assoc}}\mu_{\mathrm{str}}
      =
      \mu_{\mathrm{str}}(\mu_{\mathrm{str}}\otimes1)
      -\mu_{\mathrm{str}}(1\otimes\mu_{\mathrm{str}}),
  \]
  together with the descent defect
  \[
    \check C^p(\mathcal U;\mathcal F^q)
    =
    \prod_{i_0<\cdots<i_p}
    \mathcal F^q(U_{i_0}\cap\cdots\cap U_{i_p}),
    \qquad
    \mathbb D=\check\delta+(-1)^p d_{\mathcal F},
  \]
  and
  \[
    \delta_{\mathrm{Weiss}}(V,\mathcal U)
    =
    \operatorname{Cone}\left(
      \mathcal F^{\mathrm{str}}_{\Omega,N}(V)
      \to
      \operatorname{Tot}\check C^\bullet
      (\mathcal U;\mathcal F^{\mathrm{str}}_{\Omega,N})
    \right).
  \]
  A brane restriction of a closed insertion \(x\) must also come with
  product centrality and \(P_{0,\hbar_{\mathrm{QME}}}\)-bracket homotopies against
  arbitrary unreduced open observables \(a\):
  \[
    d_{\mathrm{QME}}H^{\mathrm{prod}}_{x,a}
      =
      \rho(x)a-(-1)^{|x||a|}a\rho(x),
  \]
  \[
    d_{\mathrm{QME}}H^{P_0}_{x,a}
      =
      \{\rho(x),a\}_{P_{0,\hbar_{\mathrm{QME}}}}
      -\rho_{\mathrm{mod}}(x;a),
  \]
  where \(\rho_{\mathrm{mod}}\) is the closed-induced brane module
  operation to be constructed, with compatibility under interval
  inclusions, disjoint products,
  finite-window projections, and weight transports.  These homotopies are
  not supplied by the reduced current brackets
  \(\{B_f(a),B_g(b)\}_{\hbar_{\mathrm{W}}}\) and
  \(\{B_f(a),\Theta_\rho(B)\}_{\hbar_{\mathrm{W}}}\).

  At a finite marked window the centrality obstruction is the Hom-curvature
  row, for
  \(x,y\in\{u_{a(t)dt\otimes f},c_{B,\rho}\}\),
  \[
  \begin{aligned}
    R^{\mathrm{cent}}_{x,y,M}
      ={}&
      \sum_{\Gamma\in\mathsf A^{d}_{x,y,M}}
        \varepsilon_\Gamma d_MK^M_\Gamma
      -\sum_{\Gamma\in\mathsf A^{\mathrm{CE}}_{x,y,M}}
        \varepsilon^{\mathrm{CE}}_\Gamma
        K^M_\Gamma(\zeta_{\Gamma,x,y})\\
      &+\frac12
      \sum_{(\Gamma_1,\Gamma_2)\in\mathsf A^{\mathrm{br}}_{x,y,M}}
        \varepsilon_{\Gamma_1,\Gamma_2}
        \{K^M_{\Gamma_1},K^M_{\Gamma_2}\}_{\hbar_{\mathrm{QME}},M}
      +R^{\mathrm{ct}}_{x,y,M}.
  \end{aligned}
  \]
  Only after
  \(\widehat\sigma_{\mathrm{sc},M}(R^{\mathrm{cent}}_{x,y,M})=0\)
  does this row define a non-scalar class
  \[
    \mathfrak o^{\mathrm{cent}}_{x,y,M}
      \in
    H^{|x|+|y|}(\mathcal Q^\bullet_{w,M}(I)).
  \]
  A product or \(P_0\)-centrality homotopy is then an explicit primitive
  row
  \[
    H^M_{x,y}\in\mathcal Q^{|x|+|y|-1}_{w,M}(I),
    \qquad
    R^{\mathrm{cent}}_{x,y,M}+d_MH^M_{x,y}=0,
  \]
  compatible with interval inclusions, finite-window projections, and
  admissible-weight transports.  The corresponding
  \(\varprojlim^1 H^{|x|+|y|-1}\)-class is part of the centrality
  obstruction, not a consequence of scalar-shadow vanishing.

  In the normal \(\Omega\)-branch the same row is formed over
  \(R_\Omega^{N,M}[[\hbar_{\mathrm{QME}}]]\) with \(d_{M,\Omega}\) and the
  \(\Omega\)-equivariant bracket.  The primitive must be basic:
  \[
    R^{\mathrm{cent}}_{x,y,\Omega,M}
      +d_{M,\Omega}H^\Omega_{x,y,M}=0,\qquad
    L_{V_\Omega}H^\Omega_{x,y,M}=0.
  \]
  If a primitive is chosen before passing to \(T_\Omega\)-invariants, the
  secondary class
  \[
    [L_{V_\Omega}H_{x,y,\Omega,M}]
      \in
    H^{|x|+|y|}
      (\mathcal Q^\bullet_{w,\Omega,M}(I),d_{\mathrm{ns},\Omega,M})
  \]
  must vanish before the homotopy is a \(Q_\Omega\)-homotopy.

  The brane-defect Costello QME condition is the same curvature equation
  as the non-scalar lift, now required as a natural transformation of
  the stratified prefactorization object:
  \[
    \operatorname{Curv}(K_{\Omega,N})
      =
      d_{\mathrm{QME}}K_{\Omega,N}
      +\frac12[K_{\Omega,N},K_{\Omega,N}]_{\hbar_{\mathrm{QME}}}=0.
  \]
  The Omega coefficient ring, normal weights, and notation gate supply
  only the habitat for this equation.  They do not prove the
  brane-defect QME.
  Its obstruction vector is
  \[
    \operatorname{Ob}^{\mathrm{int}}_{\mathrm{str},\Omega,N}
    =
    (\delta_{\mathrm{pref}},
     \delta_{\mathrm{assoc}},
     \delta_{\mathrm{Weiss}}^{\check C/R},
     \operatorname{ob}_{\mathrm{collar}},
     \operatorname{ob}^{\mathrm{prod}}_{\mathrm{cent}},
     \operatorname{ob}^{P_0}_{\mathrm{cent}},
     \operatorname{ob}^{\mathrm{bd}}_{\mathrm{QME}},
     \operatorname{ob}_{\Omega\mathrm{-basic}},
     \operatorname{ob}_{\mathrm{tr}\mathrm{-top}}).
  \]
  where
  \[
    \delta_{\mathrm{Weiss}}^{\check C/R}
    =
    \left(
      \{H^\bullet(\Delta^{N,M}_{V,\mathcal U})\}_{V,\mathcal U,N,M},
      \mathfrak w^{\check C/R}_{V,\Omega,N,M}
    \right).
  \]
  This is the internal vector.  The source-primary class
  \(\operatorname{ob}^{\mathrm{src}}_{\mathrm{CFG}}\) is external.  A
  Costello, Costello--Francis--Gwilliam, or stratified-homology analogy
  enters the stable core only after a source fixture identifies the source
  theorem, verifies its hypotheses, and supplies a matched-conventions
  morphism to the local mixed HT pair \((X,L)\).  Without that fixture it is
  motivation, not theorem support.

  \item \emph{Trace-state functional and physical large-\(N\) surface.}
  A protected brane trace is not produced by the algebraic stable trace
  theorem alone.  The stronger theorem requires a continuous state
  \[
    \omega_{N,\Omega}\colon
    \int_{L\subset X}\mathcal F^{\mathrm{str}}_{\Omega,N}
    \longrightarrow
    R_\Omega^{N,M}[[\hbar_{\mathrm{QME}}]]
  \]
  on the stratified factorization homology of the chosen brane module.
  The finite-\(N\) input is a state on the quantum Hamiltonian reduction
  \(A^q_{N,\Omega}\); the stable branch must specify the map from
  \(A^{\mathrm{pp},w}_{\partial,\Omega,\hbar_{\mathrm{W}}}\) to the same state target.
  The trace datum is
  \[
    \mathfrak T_{\Omega,N}
    =
    (\omega_{N,\Omega},
     \nu_{\Omega,N},
     \mathcal T_\Omega,
     \kappa_{\Omega,N},
     C_{\Omega,N},
     H^{\mathrm{prod}},
     H^{P_0}),
  \]
  where \(\nu_{\Omega,N}\) fixes trace, \(N\), the parameters
  \(\hbar_{\mathrm{QME}},\hbar_{\mathrm{W}},\hbar_\omega\), and the
  residue/Euler normalization branch; \(\mathcal T_\Omega\) is the
  topology in which \(N\to\infty\) asymptotics are asserted;
  \(\kappa_{\Omega,N}\) and \(C_{\Omega,N}\) are the brane-defect kernel
  and counterterms; and \(H^{\mathrm{prod}},H^{P_0}\) are the centrality
  homotopies above.  The normal Euler denominator is
  \[
    e_{T_\Omega}(N_LX)^{-1}
      =
      (\epsilon_s\epsilon_1\epsilon_2)^{-1}.
  \]
  The normalization must decide among
  \[
    \nu_\Omega^{\mathrm{res}}=1,\qquad
    \nu_\Omega^{\mathrm{Eu}}
      =
      \sigma_s(\epsilon_s\epsilon_1\epsilon_2)^{-1},
  \]
  or an explicitly named Euler-rescaled residue convention
  \[
    \nu_\Omega^{\mathrm{Eres}}
      =
      \sigma_s(\epsilon_s\epsilon_1\epsilon_2)^{-1}.
  \]
  Thus the Euler factor is built into \(\omega_{N,\Omega}\), into
  \(\nu_\Omega^{\mathrm{Eres}}\), or left external.  Plain residue
  normalization never contains the Euler denominator silently.

  The Ward identities are part of the theorem, not a consequence of the
  word trace:
  \[
    \omega_{N,\Omega}(d_{\mathrm{QME}}F)=0,\qquad
    \omega_{N,\Omega}(Q_\Omega F)=0,
  \]
  \[
    \omega_{N,\Omega}(\widehat\mu(\xi)F)=0,\qquad
    \omega_{N,\Omega}(\operatorname{Curv}(K_{\Omega,N})\,F)=0,
  \]
  whenever the expressions are defined in the chosen brane-defect
  local-functional complex.  These identities require the scalar
  anomaly branch, the non-scalar QME class, and the centrality
  homotopies to have been solved or absorbed by an explicitly named
  source replacement.  They are not consequences of \(R_\Omega^{N,M}\)
  localization.

  Connected large-\(N\) cumulants are then defined by
  \[
    \langle F_1,\ldots,F_k\rangle^{c}_{N,\Omega}
      =
      [t_1\cdots t_k]\,
      \log\omega_{N,\Omega}
      \left(\exp\Bigl(\sum_i t_iF_i\Bigr)\right),
  \]
  after finite-\(N\) trace identities and the empty-trace scalar have
  been treated in the normalization \(\nu_{\Omega,N}\).  A physical
  large-\(N\) theorem is the asymptotic statement, in
  \(\mathcal T_\Omega\),
  \[
    \langle F_1,\ldots,F_k\rangle^{c}_{N,\Omega}
      \sim
      \sum_{g\ge0}
      N^{2-2g-k}F^{\Omega}_{g;k}(F_1,\ldots,F_k),
  \]
  or the same formula with a different explicitly chosen
  \(\hbar_{\mathrm{QME}},\hbar_{\mathrm{W}},\hbar_\omega,N\)-scaling.
  The algebraic degreewise stable trace theorem
  supplies candidate primitive generators only; it does not choose
  \(\omega_{N,\Omega}\), \(\nu_{\Omega,N}\), \(\mathcal T_\Omega\), or
  the Ward identities.

  The trace obstruction vector is
  \[
    \operatorname{Ob}_{\mathrm{tr},\Omega}
    =
    (\operatorname{ob}_{\mathrm{state}},
     \operatorname{ob}_{\mathrm{norm}},
     \operatorname{ob}_{\mathrm{Ward}},
     \operatorname{ob}_{\mathrm{cum}},
     \operatorname{ob}_{\mathrm{conv}},
     \operatorname{ob}_{\mathrm{QME}},
     \operatorname{ob}_{\mathrm{src}}).
  \]
  Vanishing means that the state exists, the normalization is fixed, the
  QME and moment-map Ward identities hold, connected cumulants are
  defined in the chosen topology, the large-\(N\) expansion converges
  asymptotically there, and all external factorization-homology or
  Costello analogies have been audited against primary sources and
  matched to this local brane model.

  \item \emph{Radial/Weyl finite certificates and the
  dual-potential decorated-Stokes gate.}
  The ordinary Weyl-trace part of the degree-zero Hamiltonian trace
  target is no longer a bare external input.  The formal Moyal
  coefficients and the Capelli scalar-contact relation are proved
  algebraically, and the quantum shear primitive has a finite
  obstruction complex.  In bidegree \((a,b)\) let
  \[
    R^{\mathrm{free}}_{a,b}
      =
      \mathcal N_{\mathrm{free}}(E_{a,b,N})
      -
      \mathcal N_{\mathrm{free}}
      \left(\sum_W c^{\mathrm{cl}}_W\operatorname{Tr}(WM)\right)
  \]
  be the free normal-form residual after the classical cyclic lift.  The
  theorem-grade obstruction is the dual-potential class
  \[
    B_{a,b}(W)=(\partial W,C^+_{a,b}(W)),\qquad
    \eta_{a,b}=(T_{a,b},E^+_{a,b}),
  \]
  \[
    \Omega^{\mathrm{rad}}_{a,b}
    =
    [\eta_{a,b}]\in\operatorname{coker}B_{a,b}.
  \]
  The bidegree closes exactly when
  \(\Omega^{\mathrm{rad}}_{a,b}=0\).  After fixing a classical lift, the
  free normal-diagram model is the subordinate map
  \[
    \mathcal C_{a,b}\colon
    \ker\partial\longrightarrow\mathsf{Diag}_{a,b},
  \]
  and a displayed certificate is an explicit
  \(K_{a,b}\in\ker\partial\) with
  \(\mathcal C_{a,b}(K_{a,b})=R^{\mathrm{free}}_{a,b}\).  This is a
  normal-diagram presentation of the same obstruction, not the final
  theorem surface.

  Proposition~\ref{prop:app-edge-pbw-telescoping} proves zero obstruction
  for the edge families \((2,b)\) and \((b,2)\) for all \(b\).  The
  finite certificates additionally give zero obstruction for the balanced
  diagonal through \((6,6)\), for all non-edge bidegrees of total degree
  at most \(12\), and for the total-degree \(13\) interior cases
  \[
    (3,10),(10,3),(4,9),(9,4),(5,8),(8,5),(6,7),(7,6).
  \]
  The total-degree \(14\) certificates also close
  \[
    (3,11),(11,3),(4,10),(10,4),(5,9),(9,5).
  \]
  The first undecided total-degree \(14\) systems are
  \[
    (6,8),(8,6),(7,7).
  \]
  In the current basis these are timeout/frontier computations: the
  ordinary cyclic boundary equation closes, and no signed obstruction row
  is known.  The balanced cases \((5,5)\) and \((6,6)\) require nonzero
  corrections with \(16\) and \(54\) terms respectively; a nonzero
  correction is not a nonzero obstruction.

  The all-bidegree theorem is therefore
  \(\Omega^{\mathrm{rad}}_{a,b}=0\) for every bidegree.  The ordinary
  square-cell necklace cycle mechanism supplies
  \(\ker\partial=\operatorname{im}\partial_2\) in the relevant quotient,
  so this is equivalently the decorated PBW Stokes equation
  \[
    D^\square_{a,b}H_{a,b}=R^{\mathrm{free}}_{a,b},
    \qquad
    D^\square_{a,b}=C^+_{a,b}\partial_2 .
  \]
  A functorial splitting of the family \(\mathcal C_{a,b}\), or an
  associated-graded Hodge homotopy on the decorated two-colour necklace
  incidence graph with edges
  \[
    [WXY]\longrightarrow[WYX].
  \]
  is one construction route to this Stokes identity.  A finite table,
  even a long one, is evidence for the mechanism but not the theorem.
  Conversely, an obstruction row for the free model may be written as a
  decorated harmonic projection
  \[
    \Pi^{\mathrm{harm}}_{a,b}R^{\mathrm{free}}_{a,b},
  \]
  or, in the older free-complex shadow, a functional
  \(\lambda_{a,b}\) with
  \(\lambda_{a,b}\mathcal C_{a,b}=0\) and
  \(\lambda_{a,b}(R^{\mathrm{free}}_{a,b})\ne0\); in the theorem-grade
  dual-potential system, failure is exactly a signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \[
    \lambda(E^+_{a,b})-\phi(T_{a,b})\ne0.
  \]
  Admissibility repair asks first for the decorated Stokes identity, or
  equivalently the dual-potential identity
  \(\lambda(E^+_{a,b})=\phi(T_{a,b})\) for every such row; only a
  violating row proves that the stronger radial/Weyl theorem fails.  The
  ordinary square-cell necklace cycle mechanism is now proved; the
  missing theorem is the decorated PBW Stokes identity for
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\).

  \item \emph{Moyal and graph normalization.}
  The Weyl/Moyal convention is
  \[
    \begin{aligned}
    f*g
    ={}&m\circ\exp\Bigl(\frac{\hbar}{2}
    (\partial_{z_1}\otimes\partial_{z_2}\\
    &\qquad\qquad
     -\partial_{z_2}\otimes\partial_{z_1})\Bigr)(f\otimes g).
    \end{aligned}
  \]
  The normalized bracket is
  \[
    \{f,g\}_\hbar
    =\sum_{s\ge0}
      \frac{\hbar^{2s}}{2^{2s}(2s+1)!}P^{2s+1}(f,g).
  \]
  The first and third raw commutator weights are \(1\) and \(1/24\);
  any Costello realization must reproduce these coefficients after its
  sign, orientation, automorphism, and counterterm conventions are fixed.
  These coefficients are necessary tests for a Costello realization, not
  sufficient data for analytic BV/QME existence.

  \item \emph{Global and cross-volume descent.}
  A target theorem supplies a matched-conventions datum
  \[
    \begin{aligned}
    \mathfrak C_{\mathrm{tar}}
    ={}&(d,Y,\eta,(\Sigma_{d-1},C),L,\tau,\lambda,\mathfrak f,\Lambda,\\
    &\hbar_{\mathrm{tar}},\mathcal O_{\mathrm{tar}},
      \chi_{\mathrm{cl}},\chi_{\mathrm{op}},\chi_{\mathrm{anom}},\\
    &\mathcal K_{\mathrm{obs}}).
    \end{aligned}
  \]
  Its admissibility vector is
  \[
    \begin{aligned}
    \operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}}
    ={}&
    (\operatorname{per}_{\mathrm{tar}},
     \operatorname{ob}_{\mathrm{WR}},
     \operatorname{ob}_{\mathrm{anom}},
     \operatorname{ob}_{\mathrm{QME}},\\
    &\operatorname{ob}_{\mathrm{conv}},
     \operatorname{ob}_{\mathrm{hyp}},
     \operatorname{ob}_{6r},
     \operatorname{ob}_{\mathrm{MD}}).
    \end{aligned}
  \]
  Here \(\operatorname{ob}_{\mathrm{conv}}\) records convergence of the
  transported obstruction tower, \(\operatorname{ob}_{\mathrm{hyp}}\)
  records hyperdescent and the absence of hidden \(\varprojlim^1\)
  defects, and \(\operatorname{ob}_{6r}\) records any asserted
  six-relation factorization constraint.  A CoHA, compact BCOV, quintic,
  OSV/GV, Abel--Jacobi, MNOP/chiral-volume, Vol III, Igusa/BKM, or
  sister-volume theorem may use the formal-local theorem only after the
  target supplies this vanishing obstruction vector, chosen
  null-homotopies, and comparison morphisms identifying its formal
  restriction with the local Hamiltonian BF/Moyal normalization.  The
  transfer theorem is target data, not a consequence of the formal disk.
  Missing source fixtures in those external lanes are not core local
  proof obligations and do not supply theorem support for the local QME,
  Ext, cyclic, Weyl/Moyal, radial-parts, or kernel theorem data.
\end{enumerate}
