\section{Three principles and the admissibility discipline}\label{sec:three-principles}

After the symplectic primitive, scalar quotient, and residue
normalization are fixed, the formal-local CE/PV theory and its
admissible Koszul-duality enhancement are
organized by three source principles.  Each is physical in origin; each
enters as algebraic theorem data.  Together they specify
the open brane complex, the closed Hamiltonian BF complex, the
formal CE/PV source-to-boundary coordinate map, the Tate coefficient envelope, the current lift
datum, and the obstruction complexes controlling global use.  A separate
admissibility discipline governs repairs: a failed strong sentence is
not replaced by a weak true slogan, but by the strongest true theorem
obtained after adding the missing object, topology, kernel, homotopy,
counterterm, finite-window row, or obstruction class.

\subsection{Dirac: a brane stack is a constrained probe}

Fix the formal holomorphic symplectic disk
\[
  \widehat{\C^2}_0=\operatorname{Spf}\C[[z_1,z_2]],
  \qquad \omega=dz_1\wedge dz_2.
\]
A stack of \(N\) branes supported on the topological line probes this
disk by replacing the normal coordinates by matrices
\[
  z_1\rightsquigarrow\phi_1,\qquad
  z_2\rightsquigarrow\phi_2,\qquad
  \phi_i\in\mathfrak{gl}_N .
\]
The pulled-back symplectic form is
\[
  \Omega_N=\operatorname{Tr}(d\phi_1\wedge d\phi_2),
\]
with primitive \(\operatorname{Tr}(\phi_1\,d\phi_2)\). Change of basis
in the probe stack is gauge. Its moment map is
\[
  \mu(\epsilon)=-\operatorname{Tr}(\epsilon[\phi_1,\phi_2]),
  \qquad \epsilon\in\mathfrak{gl}_N .
\]
Dirac reduction therefore imposes the first-class constraint
\[
  [\phi_1,\phi_2]=0.
\]
After the primitive \(\operatorname{Tr}(\phi_1\,d\phi_2)\) and moment
map convention have been fixed, the corresponding first-order
world-line action is
\[
  S_\partial
  =\int_\R\operatorname{Tr}
    \bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr).
\]
In BV form the constraint is the Koszul differential
\[
  Q\psi=[\phi_1,\phi_2],\qquad Q\phi_1=Q\phi_2=0,
\]
where \(\psi=A^*\). Thus the open algebra is not postulated as a
trace algebra. It is the algebra of gauge-invariant functions on the
derived commuting-pair locus. Lemma~\ref{lem:dirac-probe-reduction}
and Proposition~\ref{prop:open-bv-truncation} give the formal proof.

\subsection{Witten convention: closed fields target central operations}

Witten's open string field theory supplies the cyclic open-field-theory
source convention.  A closed insertion approaching a brane gives an
operation on compatible boundary observables.  In a topological
direction the algebraic target for such an operation is centrality up to
derived Poisson homotopies.  The formal-local target is therefore
\[
  Z^{P_0}_{\mathrm{red,Ham}}(\mathrm{Obs}_{\mathrm{open}}),
\]
not \(\mathrm{Obs}_{\mathrm{open}}\) itself.  The reduced Hamiltonian
sector supplies the cochain CE/PV theorem; the unreduced
factorization-current theorem is formulated by adding the boundary
representatives, centrality homotopies, coefficient kernel, and QME
solution demanded by that target.

For the formal symplectic disk the infinitesimal closed symmetries are
Hamiltonian vector fields. Constants generate the zero vector field,
so the Hamiltonian Lie algebra is
\[
  \mathfrak h=\C[[z_1,z_2]]/\C\cdot1,
  \qquad
  \{f,g\}
  =\partial_{z_1}f\,\partial_{z_2}g
   -\partial_{z_2}f\,\partial_{z_1}g .
\]
In the local model the closed BV algebra of canonical transformations is
the shifted cotangent theory
\[
  \mathfrak g
  =\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1].
\]
The finite-window and coordinate-completed CE/PV theorem is the
cochain identity
\[
  C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
  \cong
  \mathrm{PV}_{\mathrm{coord}}
  \bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr),
\]
with generator dictionary
\[
  c^I\mapsto\theta^I,\qquad u_I\mapsto O_I .
\]
The \(Z^{P_0}_{\mathrm{red,Ham}}\) interpretation is made only after
imposing the finite-window or mixed/weighted continuity condition that
makes the bracket continuous; it is not a statement about the full
ambient product completion.
The boundary Hamiltonian observable is the image of the shifted
cotangent coordinate \(u_I\). It is not the image of the Hamiltonian
ghost coordinate \(c^I\). This distinction is the type check behind
the factorization-current theorem.  At the unreduced BV level the same
type check defines the theorem datum: boundary representatives for
\(u_I\), product centrality homotopies, \(P_0\)-bracket homotopies,
coefficient kernel, and mixed brane-defect QME solution.

The polynomial category is eliminated by a local-nilpotence criterion.
In the polynomial unreduced BV/Koszul category the linear Hamiltonians
act by constant translations of \(\phi_2\) and \(\phi_1\), hence
locally nilpotently on every finite polynomial observable and on its
\(Q\)-cohomology. The principal-part cotangent module has the opposite
behavior:
\[
  z_1^r\cdot\rho_{a,b}
  =(-1)^r(b+1)\cdots(b+r)\rho_{a,b+r}\neq0,
  \qquad r\geq1,
\]
and similarly for \(z_2\). Thus a same-action unreduced lift cannot be
hidden inside polynomial one-\(\psi\) representatives. The boundary
target is therefore the distributional principal-part current sector,
with its centrality homotopies stated as theorem data.

The QME obstruction has an independent scalar component. With the
Capelli/Weyl convention used below,
\[
  \operatorname{Tr}(A\,XY)-\operatorname{Tr}(A\,YX)
  =\hbar N\,\operatorname{Tr}(A)
  \quad\bmod\ \mathcal W_N\widehat\mu(\lie{gl}_N).
\]
After inserting the central boundary ghost
\(\gamma_{\mathbf 1}\), \(|\gamma_{\mathbf 1}|=1\), the scalar contact
contributes
\[
  \operatorname{Ob}_{\mathrm{sc}}
  =
  \hbar N\,\omega(f,g)
  \int_\R a(t)b(t)\gamma_{\mathbf 1}(t)\,dt .
\]
  Its associated graded class is \(\hbar N[\bar c]\). The reduced
  Hamiltonian source has no constant Hamiltonian line on which the
  primitive \(\eta(f)=-[f]_0\) could live.  A fixed scalar-reduced
  ordinary \(\mathfrak{gl}_N\) lift therefore requires a closed-exchange
  contribution \(W_{\mathrm{ext}}\) whose leading class satisfies
  \[
    [w_{\mathrm{ext}}]=-\hbar N[\bar c]
    \qquad\text{in }H^2_{\mathrm{Lie}}(\bar A,\C).
  \]
  Alternatively, the unreduced central-character source absorbs the
  scalar symbol before scalar reduction, while a Casimir-balanced
  supertrace model makes the scalar representative zero.
  The obstruction complex controls any further mechanism by the same
  degree-one class.

\subsection{Grothendieck: cotangent modes are residue currents}

The continuous dual of functions on a formal disk is not another copy
of polynomial functions. It is the local-cohomology module of residue
currents. For
\[
  R=\C[[z_1,z_2]],\qquad \mathfrak m=(z_1,z_2),
\]
the Matlis dualizing module is
\[
  H^2_{\mathfrak m}(R)\,dz_1dz_2
  =
  \bigoplus_{a,b\geq0}
  \C\,z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2 .
\]
After removing the scalar Hamiltonian, the cotangent module is
\[
  \mathcal P
  =
  \operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
  =
  \bigoplus_{a+b>0}\C\,\rho_{a,b},
  \qquad
  \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2 .
\]
The residue pairing
\[
  \langle\rho_{a,b},z_1^m z_2^n\rangle
  =
  \operatorname{Res}_{0}
  z_1^{m-a-1}z_2^{n-b-1}\,dz_1dz_2
  =
  \delta_{a,m}\delta_{b,n}
\]
identifies \(\mathfrak h^\vee_{\mathrm{cont}}\) with \(\mathcal P\).
The coadjoint action is the principal-part formula
\[
  z_1^p z_2^q\cdot\rho_{a,b}
  =
  -(pb-qa+p-q)\rho_{a-p+1,b-q+1}.
\]
This is the cotangent sector used by the closed theory. The
one-\(\psi\) open classes \(\Psi_{a,b}\) carry the same labels but a
different \(\mathfrak h\)-module structure. They form a PBW
special-fibre shadow; they do not realize the principal-part module.
The no-go theorem
\ref{thm:no-polynomial-realization-categorical} records the formal
obstruction.

\subsection{Admissibility discipline: repair by construction}

Every frontier statement in this manuscript is read with its repair datum.
Suppose a proposed theorem \(T\) fails in the currently displayed
habitat.  The admissible repair is not the largest harmless weakening of
\(T\).  It is the smallest enlargement of the mathematical habitat in
which the intended mechanism is a theorem, or else the exact obstruction
proving that no such enlargement of the prescribed type can work.
Thus a failed theorem surface is not a stable status.  It must be
reconstituted until it is either a proved theorem with all missing data
supplied, or a proved obstruction theorem naming the cohomology class,
cokernel functional, Roos class, finite-window matrix row, graph
incidence table, or source fixture that prevents the original statement.

Concretely, a failed bracket statement demands the missing continuous
bracket habitat, scalar quotient, line-valued parameter, or weight
character; a failed kernel statement demands the missing convergence
topology, diagonal tensor, Bochner--Martinelli homotopy, finite-window
transport, or source-face table; a failed QME statement demands the
filtered local-functional complex, scalar-contact projection,
bulk-to-defect kernel, counterterm primitive, centrality homotopies, and
the non-scalar obstruction class.  If any of these data are unavailable,
the manuscript records the precise class or construction problem rather
than demoting the theorem into analogy.

Thus the current non-scalar QME surface is not the vague assertion that
``the QME is open''.  It is the finite-window criterion in
\(\mathfrak Q^\bullet_{w,\partial,\hbar}(I)\): the scalar-contact lift
must exist, the reduced class in
\[
  H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})
\]
must vanish, and each row must pass the matrix equation
\[
  A^M c^M=-r^M
\]
with Roos-compatible primitives.  The first exposed larger row is
\(\theta_3\).  In the supplied one-row complex
\[
  \mathcal Q^0_{\theta_3,M}=0,\qquad
  \mathcal Q^1_{\theta_3,M}=\C\mathsf E_{\theta_3,M},
\]
the covector \(\ell_{\theta_3}(\mathsf E_{\theta_3,M})=1\) is an exact
obstruction.  Admissibility repair therefore asks for a CE ancestor, a
scalar-zero Costello counterterm primitive, or a complete companion-face
table whose differential or signed CE boundary kills
\(\mathsf E_{\theta_3,M}\).  Merely naming \(C_{\theta_3}\) is not
mathematics.

The same discipline governs the radial/Weyl input.  The finite
normal-form certificates are not discarded because they stop before the
all-bidegree theorem, and they are not inflated into that theorem either.
They define the stronger true target: construct a functorial splitting
of the free normal-diagram correction maps
\[
  \mathcal C_{a,b}\colon
  \ker\partial\longrightarrow\mathsf{Diag}_{a,b},
\]
or prove a left-cokernel functional detecting a genuine obstruction.
Likewise the native chiral object is not weakened to a curve vertex
algebra; it remains the \(\C^2\) holomorphic factorization algebra, with
curve/Zhu structures admitted only after the controlled
\(\C\times\R\) reduction retaining the \(z_2\)-mode or principal-part
system.

\subsection{Deduction of the local theorem}

The three principles have disjoint jobs in the formal-local theorem.

\begin{enumerate}
  \item Dirac determines the open BV complex and the stable trace
  observables.
  \item Witten's source convention motivates the source-to-boundary target as a
  derived \(P_0\)-centre; the local CE/PV theorem supplies the proof in
  the reduced Hamiltonian sector.
  \item Grothendieck determines the continuous cotangent coefficients
  and separates principal parts from polynomial descendants.
\end{enumerate}

The resulting theorem decomposes into independent
component theorems: the Dirac probe theorem; the stable trace and
one-\(\psi\) calculation; the CE/PV central-operation theorem; the Matlis
principal-part theorem; the brane-line factorization-current theorem;
the reduced principal-part defect-current theorem; the degree-zero
Moyal/Weyl quantum theorem; and the scalar \(U(1)\) anomaly theorem.
The frontier components are theorem data: the admissible and endpoint
Tate envelope, the unreduced cotangent factorization-centre morphism,
the one-antifield quantum lift, the Costello brane-defect QME
realization, and matched-conventions global descent.  Each is governed
by the obstruction complex displayed in
Section~\ref{sec:open-obligations}.
