% !TEX root = main.tex
%
% Cross-volume matched conventions and obstruction complexes.
%
% This appendix gives the exact convention data and obstruction classes
% needed to use the local Hamiltonian theorem inside a global or
% cross-volume theorem.

\section{Cross-volume matched conventions and obstruction complexes}\label{app:convention-contract}

The theorem is local on
\[
  \R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}
  =
  \R_{\mathrm{brane}}\times\R_{\mathrm{top,normal}}
  \times\widehat{\C^2}_{0,\mathrm{hol}},
\]
with brane line \(\R_{\mathrm{brane}}\times\{0\}\times\{0\}\). Its
closed sector is Hamiltonian BF theory on the formal
holomorphic-symplectic disk together with the topological directions, and
its open sector is the Dirac brane probe on the brane line. The statement
is at \(d=\dim_\C Y=2\) in the holomorphic factor and uses the brane line
\(\R_{\mathrm{brane}}\) as its one-dimensional factorization direction.

This appendix states the transfer problem in theorem form.  The local
result contributes a \(d=2\) formal-disk convention base for the
universal Koszul-duality programme.  A global or cross-volume theorem
using it is an accepted universal target exactly when it gives a target
convention datum, comparison morphisms, and null-homotopies for the
named obstruction classes.

\begin{defn}[Local Hamiltonian convention base]\label{defn:local-hamiltonian-convention-base}
  The local theorem supplies the convention base
  \[
  \mathfrak C_{\mathrm{loc}}^{(2)}=
  \bigl(
    d=2,\,
    \R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}},\,
    \R_{\mathrm{brane}},\,
    \widehat{\mathfrak h},\,
    \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}[1],\,
    \Ext^*(\mc O_0,\mc O_0),\,
    [\bar c],\,
    \hbar_{\mathrm{Weyl}},\,
    \Phi^{\mathrm{Ham}}_{\mathrm{fact}}
  \bigr),
  \]
  where
  \(\widehat{\mathfrak h}=\C[[z_1,z_2]]/\C\cdot 1\).  The base includes
  the brane-line factorization convention, the scalar quotient, and the
  reduced degree-zero Capelli/Moyal normalization.
\end{defn}

\begin{lem}[Formal-disk universal acceptance criterion]\label{lem:no-formal-disk-transfer}
  The formal-disk theorem gives universal Koszul-duality target data for
  a proposed global or cross-volume target \(\mathfrak T\) exactly after
  the target supplies a matched-conventions datum
  \(\mathfrak C_{\mathrm{tar}}\) and a null-homotopy of the acceptance
  class
  \[
  \operatorname{Ob}_{\mathrm{UKD}}(\mathfrak T)
  =
  \left(
    \operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}},
    \operatorname{Ob}_{\mathrm{glob}},
    \operatorname{ob}_{6r},
    \operatorname{ob}_{\mathrm{MD}}
  \right),
  \]
  with the entries omitted only when the corresponding structure is not
  asserted by \(\mathfrak T\).  The accepted morphism has formal stalk
  \[
    \chi_{\mathrm{op}}^{-1}
    \Phi^{\mathrm{Ham}}_{\mathrm{fact}}
    \chi_{\mathrm{cl}}.
  \]
\end{lem}

\begin{proof}
  The local input consists of the formal Hamiltonian algebra
  \(\C[[z_1,z_2]]/\C\), its continuous cotangent extension, the point
  brane Ext algebra, the brane-line factorization-current convention,
  the scalar quotient, and the Capelli/Weyl normalization.  These data
  are invariant under the formal Darboux germ.  Compact topology, a
  negative-cyclic Calabi--Yau class, a worldsheet or specialization
  curve, an \(S^3\) framing, a global BV propagator, the holomorphic
  anomaly equation, Borcherds input data, a Weyl chamber, a compact Hall
  orientation, and a compact chiral-homology object therefore enter as
  components of \(\mathfrak C_{\mathrm{tar}}\), not as consequences of the
  formal germ.  The four displayed components record exactly the target
  convention, global descent, six-relation mixed-factorization, and
  mixed-Dunn acceptance tests.  Vanishing with null-homotopies is the
  universal acceptance datum; a nonzero component is the corresponding
  obstruction class.
\end{proof}

\begin{defn}[Matched-conventions theorem datum]\label{defn:matched-conventions-theorem-datum}
  A matched-conventions theorem datum is a tuple
  \[
  \mathfrak C_{\mathrm{tar}}=
  \bigl(
    d,Y,\eta,(\Sigma_{d-1},C),L,\tau,\lambda,\mathfrak f,\Lambda,
    \hbar_{\mathrm{tar}},\mc O_{\mathrm{tar}},
    \chi_{\mathrm{cl}},\chi_{\mathrm{op}},\chi_{\mathrm{anom}},
    \mc K_{\mathrm{obs}},\mathfrak K_{\mathrm{KD}},\Theta_{\mathrm{KD}}
  \bigr)
  \]
  with the following meaning.  Here \(d=\dim_\C Y\);
  \(\eta\) is the negative-cyclic Calabi--Yau class, holomorphic volume
  form, or holomorphic-symplectic form used by the target theory;
  \((\Sigma_{d-1},C)\) is the worldsheet or factorization-homology
  specialization when a \(\Phi_d\)-type theorem is asserted; \(L\) is the
  brane or boundary condition; \(\tau\) is the trace pairing and scalar
  quotient; \(\lambda\) is the anomaly normalization; \(\mathfrak f\) is the
  framing datum, including an \(S^3\)-framing for compact CY\(_3\)
  statements; \(\Lambda\) is the coefficient topology; \(\hbar_{\mathrm{tar}}\)
  is the deformation parameter; \(\mc O_{\mathrm{tar}}\) is the QME or
  obstruction hypothesis; \(\chi_{\mathrm{cl}}\), \(\chi_{\mathrm{op}}\),
  and \(\chi_{\mathrm{anom}}\) are the closed-field, open-field, and anomaly
  comparison morphisms from the target formal restriction to
  \(\mathfrak C_{\mathrm{loc}}^{(2)}\); and
  \(\mc K_{\mathrm{obs}}\) is the obstruction complex in which descent,
  QME, and operadic coherence are solved;
  \(\mathfrak K_{\mathrm{KD}}\) is the filtered dg Lie algebra governing
  the target universal Koszul-duality Maurer--Cartan problem; and
  \(\Theta_{\mathrm{KD}}\) is the transported local closed-open
  Maurer--Cartan element whose curvature is the target acceptance class.
\end{defn}

\begin{defn}[Compact Hamiltonian period complex]\label{defn:compact-hamiltonian-period-complex}
  Let \((X,\omega)\) be a compact connected holomorphic-symplectic
  surface.  For a holomorphic symplectic vector field \(v\), set
  \[
    \alpha_v=-\iota_v\omega\in H^0(X,\Omega^1_{X,\mathrm{cl}}).
  \]
  Choose a Stein cover \(\mathfrak U=\{U_i\}\) and local holomorphic
  primitives \(h_i\in\mc O_X(U_i)\) with \(dh_i=\alpha_v|_{U_i}\).
  The differences \(h_i-h_j\in\C\) define a Cech cocycle, and its class
  \[
    \operatorname{per}_X(v)=
    [\,h_i-h_j\,]\in H^1(X,\C_X)
  \]
  is the Hamiltonian period obstruction.  Equivalently, it is the
  connecting image of \(\alpha_v\) for the holomorphic de Rham exact
  sequence
  \[
    0\longrightarrow\C_X\longrightarrow\mc O_X
      \xrightarrow{d}\Omega^1_{X,\mathrm{cl}}\longrightarrow0.
  \]
\end{defn}

\begin{defn}[Global Hamiltonian descent complex]\label{defn:global-hamiltonian-descent-complex}
  Let \(L\) be the brane locus in a proposed global target and suppose
  that formal Darboux charts have produced local Hamiltonian maps
  \(\Phi_U\) on a Weiss/Ran cover of \(L\).  The descent target for these
  maps is the total complex
  \[
  \mathfrak G_{\mathrm{WR}}(L)=
  \operatorname{Tot} C^\bullet_{\mathrm{WR}}\!\left(
    \operatorname{Ran}(L);
    \underline{\operatorname{RHom}}\left(
      \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H},
      \mathrm Z^{P_0}_{\mathrm{fact}}
        (\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}})
    \right)\right).
  \]
  The degree-zero Cech-Weiss cochain \(\Phi_{\mathrm{loc}}=\{\Phi_U\}\)
  has first descent obstruction
  \[
    \operatorname{ob}^{(1)}_{\mathrm{WR}}(\Phi_{\mathrm{loc}})
      =[d_{\mathrm{WR}}\Phi_{\mathrm{loc}}]
      \in H^1(\mathfrak G_{\mathrm{WR}}(L)).
  \]
  After choosing a filtration by number of factorization collisions and
  cotangent insertions, the higher coherence obstructions live in
  \[
    \operatorname{ob}^{(r)}_{\mathrm{WR}}(\Phi_{\mathrm{loc}})
      \in
      H^{r+1}\!\left(
        \operatorname{gr}^r\mathfrak G_{\mathrm{WR}}(L)
      \right),
      \qquad r\ge 1.
  \]
  Vanishing of all these classes, together with chosen null-homotopies, is
  the exact assertion that the local Darboux maps descend to a global
  factorization-centre morphism.
\end{defn}

\begin{thm}[Formal local-to-global Hamiltonian descent theorem data]\label{thm:global-descent-criterion}
  Let \((X,\omega)\) be a compact connected holomorphic-symplectic
  surface and \(L\subset X\) a brane locus for which the formal local
  Hamiltonian theorem is applied along Darboux charts.  Fix the finite
  collection of locally Hamiltonian symplectic vector fields and local
  Darboux Hamiltonians used by the construction.  The following data are
  equivalent.
  \begin{enumerate}[label=(\roman*)]
    \item A global Hamiltonian universal Koszul-duality descent datum:
      a closed-open morphism
      \[
        \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H}\big|_L
          \longrightarrow
        \mathrm Z^{P_0}_{\mathrm{fact}}
          (\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}})
      \]
      whose Darboux restrictions are the local maps
      \(\Phi_{\mathrm{loc}}\), together with its interval,
      Weiss/Ran, scalar, and connected-stable coherence homotopies.
    \item Vanishing of the obstruction vector
      \[
      \operatorname{Ob}_{\mathrm{glob}}(X,L,\Phi_{\mathrm{loc}})
      =
      \left(
        \{\operatorname{per}_X(v)\}_v,\,
        \operatorname{ob}_{\mathrm{scal}},\,
        \operatorname{ob}^{(1)}_{\mathrm{WR}}(\Phi_{\mathrm{loc}}),\,
        \{\operatorname{ob}^{(r)}_{\mathrm{WR}}(\Phi_{\mathrm{loc}})\}_{r\ge1}
      \right)
      \]
      with null-homotopies compatible with disjoint unions, interval
      inclusions, cotangent boundary realization, \(P_0\)-centrality, and
      the stable connected quotient.
  \end{enumerate}
  The morphism in (i) is the global accepted Koszul-duality surface
  \[
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H}\big|_L
      \longrightarrow
    \mathrm Z^{P_0}_{\mathrm{fact}}
      (\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open}})
  \]
  and the entries in (ii) are:
  \begin{enumerate}[label=(\alph*)]
    \item every locally Hamiltonian symplectic vector field used by the
      construction has period class
      \[
        \operatorname{per}_X(v)=
        \delta(-\iota_v\omega)\in H^1(X,\C_X)
      \]
      equal to zero;
    \item the first Weiss/Ran class
      \(\operatorname{ob}^{(1)}_{\mathrm{WR}}\) vanishes;
    \item all higher coherence classes
      \(\operatorname{ob}^{(r)}_{\mathrm{WR}}\), \(r\ge1\), vanish after
      the cotangent boundary realization and \(P_0\)-centrality homotopies
      have been fixed;
    \item the scalar anomaly class agrees with the local class
      \([\bar c]\).
  \end{enumerate}
  When these conditions hold, the local Darboux maps glue, uniquely up to
  the corresponding contractible space of choices, to the displayed
  global Hamiltonian factorization-centre morphism.  When one component
  is nonzero, that component is the exact universal descent obstruction.

  On a compact connected \(X\) the period condition is sharp:
  \[
    \operatorname{per}_X(v)=0
    \quad\Longleftrightarrow\quad
    \alpha_v=0
    \quad\Longleftrightarrow\quad
    v=0 .
  \]
  Thus a nonzero global holomorphic symplectic vector field on a compact
  surface, for example a translation on an abelian surface, has nonzero
  \(\operatorname{per}_X(v)\) and is rejected by the global Hamiltonian
  acceptance criterion.
\end{thm}

\begin{proof}
  The period calculation is Definition~\ref{defn:compact-hamiltonian-period-complex}.
  If \(\operatorname{per}_X(v)=0\), the local primitives \(h_i\) can be
  modified by constants and glued to a global holomorphic function
  \(h\) with \(dh=-\iota_v\omega\).  Since \(X\) is compact and
  connected, \(H^0(X,\mc O_X)=\C\), hence \(dh=0\).  Therefore
  \(\iota_v\omega=0\), and nondegeneracy of \(\omega\) gives \(v=0\).
  The converse is immediate.  This proves the sharp compact-surface
  obstruction: \(\operatorname{per}_X(v)\) is the exact class preventing
  formal local Hamiltonians from becoming nonzero compact global
  Hamiltonians by descent alone.

  Once local primitives and Darboux charts are fixed, the remaining
  problem is ordinary descent for morphisms of factorization objects.  On
  double overlaps the failure of the local maps to agree is
  \(d_{\mathrm{WR}}\Phi_{\mathrm{loc}}\), hence the first obstruction is
  the displayed class in \(H^1(\mathfrak G_{\mathrm{WR}}(L))\).  If it
  vanishes, a first homotopy can be chosen.  The obstruction to making
  those homotopies coherent on higher overlaps and higher collision
  strata is computed by the associated graded pieces of the same filtered
  total complex, giving the classes
  \(\operatorname{ob}^{(r)}_{\mathrm{WR}}\).  This is the standard
  obstruction theory for a Maurer--Cartan element in a filtered dg Lie
  algebra of descent data.  Scalar compatibility is separate because the
  local theorem has already quotiented by the distinguished scalar line.
  If all classes vanish and null-homotopies have been chosen, the
  Maurer--Cartan element is gauge equivalent to a global descent datum,
  which is exactly the displayed morphism.
\end{proof}

\begin{thm}[Matched-conventions universal transfer theorem]\label{thm:matched-conventions-transfer}
  Let \(\mathfrak C_{\mathrm{tar}}\) be a matched-conventions datum and
  suppose that its comparison morphisms identify the formal restriction of
  the target closed and open theories with
  \(\mathfrak C_{\mathrm{loc}}^{(2)}\):
  \[
    \chi_{\mathrm{cl}}\colon
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},\mathrm{tar}}\big|_{\widehat p}
      \xrightarrow{\simeq}
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H},
    \qquad
    \chi_{\mathrm{op}}\colon
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},\mathrm{tar}}\big|_{\R_{\mathrm{brane}}}
      \xrightarrow{\simeq}
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},H}.
  \]
  Assume that \(\chi_{\mathrm{anom}}\) sends the target scalar anomaly to
  \([\bar c]\), that the target period classes specified by
  \(\mc K_{\mathrm{obs}}\) vanish for the locally Hamiltonian fields used
  by the comparison, that the Weiss/Ran obstructions in
  \(\mathfrak G_{\mathrm{WR}}(L)\) vanish with chosen null-homotopies, and
  that the QME obstruction specified by \(\mc O_{\mathrm{tar}}\) vanishes.
  If \(\mathfrak C_{\mathrm{tar}}\) also asserts a mixed topological-holomorphic
  operadic comparison, assume the map \(\delta_{m,n}\) satisfies
  Theorem~\ref{thm:mixed-dunn-criterion}.
  Equivalently, assume the target obstruction vector
  \[
  \operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}}
  =
  \left(
    \operatorname{per}_{\mathrm{tar}},\,
    \operatorname{ob}_{\mathrm{WR}},\,
    \operatorname{ob}_{\mathrm{anom}},\,
    \operatorname{ob}_{\mathrm{QME}},\,
    \operatorname{ob}_{\mathrm{MD}}
  \right)
  \]
  is zero, with \(\operatorname{ob}_{\mathrm{MD}}\) omitted only when no
  mixed topological-holomorphic operad is part of the target datum.
  Let
  \[
    \operatorname{Ob}_{\mathrm{UKD}}(\mathfrak C_{\mathrm{tar}})
      =
    \left(
      \operatorname{Ob}_{\mathfrak C_{\mathrm{tar}}},
      [d\Theta_{\mathrm{KD}}+\frac12[\Theta_{\mathrm{KD}},\Theta_{\mathrm{KD}}]]
    \right)
    \in
    H^1(\mc K_{\mathrm{obs}})
      \oplus H^1(\mathfrak K_{\mathrm{KD}})
  \]
  be the universal Koszul-duality acceptance class of the transported
  closed-open Maurer--Cartan element.

  If \(\operatorname{Ob}_{\mathrm{UKD}}(\mathfrak C_{\mathrm{tar}})=0\)
  and a null-homotopy of this class has been chosen, then the local
  Hamiltonian theorem determines an accepted target
  factorization-centre morphism
  \[
    \Phi_{\mathfrak C_{\mathrm{tar}}}\colon
    \mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},\mathrm{tar}}\big|_L
      \longrightarrow
    \mathrm Z^{P_0}_{\mathrm{fact}}
      (\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{open},\mathrm{tar}})
  \]
  whose formal restriction at \(p\) is
  \[
    \chi_{\mathrm{op}}^{-1}\,
    \Phi^{\mathrm{Ham}}_{\mathrm{fact}}\,
    \chi_{\mathrm{cl}}.
  \]
  If a specialization functor
  \(\mathrm{Sp}_{\Sigma_{d-1},C}\) is part of
  \(\mathfrak C_{\mathrm{tar}}\), the specialized morphism is
  \(\mathrm{Sp}_{\Sigma_{d-1},C}(\Phi_{\mathfrak C_{\mathrm{tar}}})\).
  If the acceptance class is nonzero, that class is the obstruction to
  accepting the target theorem in the universal Koszul-duality programme.
\end{thm}

\begin{proof}
  The comparison morphisms transport the local closed-open map to each
  Darboux chart of the target.  Anomaly compatibility identifies the scalar
  quotient with the local class \([\bar c]\), so the transported bracket and
  connected-trace normalization agree with the Hamiltonian theorem.  The
  vanishing of the target period classes gives Hamiltonian primitives for
  the local symplectic vector fields in every chart where the Hamiltonian
  model is used, and the vanishing of the Weiss/Ran classes in
  \(\mathfrak G_{\mathrm{WR}}(L)\) glues the local maps with coherent
  factorization homotopies by
  Theorem~\ref{thm:global-descent-criterion}.  The QME obstruction
  vanishing upgrades the classical comparison to the target quantum
  normalization specified by \(\mc O_{\mathrm{tar}}\).  When a mixed
  topological-holomorphic operad is present, the mixed-Dunn criterion gives
  the required equivalence of algebra categories before applying
  specialization.  The displayed formula is the definition of the glued map
  on the formal stalk.  The remaining Maurer--Cartan curvature is exactly
  \(d\Theta_{\mathrm{KD}}+\frac12[\Theta_{\mathrm{KD}},\Theta_{\mathrm{KD}}]\);
  a chosen null-homotopy makes the transported local datum a global
  universal Koszul-duality datum.  Descent gives the global morphism.
\end{proof}

\begin{defn}[Functor of points of mixed six-relation factorization]\label{defn:mixed-dunn-fact6r-datum}
  Let \(M\) be a real \(m\)-manifold and \(Y\) a complex \(n\)-fold.  For
  an Artinian commutative dg algebra \(R\), an \(R\)-point of
  \(\mathrm{Fact}^{6r}_{\mathrm{mix}}(M,Y)\) is a datum
  \[
    \mathcal A_R=
    (A_R,\mu_R,\ell_R,\bar\partial_R,\mathsf W_R,\mathsf R_R,\iota_R)
  \]
  on product disks \(D\times B\subset M\times Y\), where \(D\) is a
  real disk and \(B\) is a holomorphic polydisk:
  \begin{enumerate}[label=(\roman*)]
    \item \(A_R(D\times B)\) is a nilcomplete \(R\)-linear cochain
      complex, functorial for inclusions of product disks;
    \item \(\mu_R\) gives factorization products for pairwise disjoint
      finite families of product disks;
    \item \(\ell_R\) gives local-constancy homotopies for inclusions of
      real disks in the \(M\)-direction;
    \item \(\bar\partial_R\) gives Dolbeault null-homotopies for
      anti-holomorphic translations in the \(Y\)-direction;
    \item \(\mathsf W_R\) gives Weiss descent in the real direction;
    \item \(\mathsf R_R\) gives Ran descent in the holomorphic direction;
    \item \(\iota_R\) gives the interchange homotopies between real
      collision products and holomorphic factorization products.
  \end{enumerate}
  These data are required to satisfy six relations.  Put
  \[
  \mathsf{Rel}^{6r}(\mathcal A_R)=
  \bigl(
    \operatorname{Assoc}(\mu_R),\,
    \operatorname{LC}(\ell_R),\,
    \bar\partial_R^2,\,
    d_{\mathrm{WR}}\mathsf W_R,\,
    d_{\mathrm{Ran}}\mathsf R_R,\,
    \operatorname{Int}(\iota_R)
  \bigr).
  \]
  An \(R\)-point is precisely a seven-tuple with
  \(\mathsf{Rel}^{6r}(\mathcal A_R)=0\): associativity of \(\mu_R\),
  homotopy invariance for \(\ell_R\), Dolbeault closedness for
  \(\bar\partial_R\), Weiss cocycle descent for \(\mathsf W_R\), Ran
  cocycle descent for \(\mathsf R_R\), and the mixed interchange
  identity for \(\iota_R\).  A \(k\)-simplex of the
  derived functor of points is the same datum over
  \(R\otimes\Omega^\bullet(\Delta^k)\).  Base change in \(R\) defines
  the functor
  \[
    \mathrm{Fact}^{6r}_{\mathrm{mix}}(M,Y)\colon
    \mathrm{dgArt}_\C\longrightarrow\mathrm{sSet}.
  \]

  This functor is the mixed factorization surface used by the universal
  Koszul-duality programme.  Its acceptance condition is the equation
  \(\mathsf{Rel}^{6r}=0\) together with coherent
  null-homotopies in square-zero families.  For a partial lift
  \(\widetilde{\mathcal A}_{R'}\) over a square-zero extension
  \(R'\twoheadrightarrow R\) with kernel \(I\), the six-relation
  obstruction is
  \[
    \operatorname{ob}_{6r}(\widetilde{\mathcal A}_{R'})
      =
    [\,\mathsf{Rel}^{6r}(\widetilde{\mathcal A}_{R'})\,]
      \in
    H^2\!\left(
      \operatorname{Der}^{\mathrm{fact,mix}}(\mathcal A_R)\otimes_R I
    \right).
  \]

  A mixed-Dunn comparison is a morphism of cofibrant operadic models
  \[
    \delta_{m,n}\colon
    \mathbb E_m^{\mathrm{top}}\otimes\mathbb E_n^{\mathrm{hol}}
      \longrightarrow
    \mathbb E_{m,n}^{\mathrm{mix}}
  \]
  whose induced algebra functor realizes this functor of points.
\end{defn}

\begin{prop}[Recognition and tangent complex for mixed six-relation factorization]\label{prop:fact6r-functor-of-points-recognition}
  Let \(\mathcal A_R\) be an \(R\)-point of
  \(\mathrm{Fact}^{6r}_{\mathrm{mix}}(M,Y)\).  Then \(\mathcal A_R\)
  determines a mixed factorization object on
  \(\operatorname{Ran}(M\times Y)\), locally constant in the
  \(M\)-directions and holomorphic in the \(Y\)-directions.  Conversely,
  restriction to product disks sends every such mixed factorization
  object to an \(R\)-point of
  \(\mathrm{Fact}^{6r}_{\mathrm{mix}}(M,Y)\).

  If \(R'\twoheadrightarrow R\) is a square-zero extension with kernel
  \(I\), the obstruction to lifting \(\mathcal A_R\) to an
  \(R'\)-point is the six-relation class
  \(\operatorname{ob}_{6r}\), lying in
  \[
    H^2\!\left(
      \operatorname{Der}^{\mathrm{fact,mix}}(\mathcal A_R)
      \otimes_R I
    \right),
  \]
  and the space of lifts, when nonempty, is a torsor under
  \[
    H^1\!\left(
      \operatorname{Der}^{\mathrm{fact,mix}}(\mathcal A_R)
      \otimes_R I
    \right).
  \]
\end{prop}

\begin{proof}
  Product disks form a basis for the mixed Weiss/Ran topology on
  \(M\times Y\).  The factorization products \(\mu_R\) define the
  multiplication on disjoint configurations.  The homotopies
  \(\ell_R\) and \(\bar\partial_R\) impose the two directional
  invariance conditions.  The descent systems \(\mathsf W_R\) and
  \(\mathsf R_R\) glue the basis values to the mixed Ran object, and
  \(\iota_R\) is exactly the compatibility between the two collision
  operations.  Nilcompleteness over \(R\) identifies this glued object
  with the derived functor of points.  Restricting a mixed
  factorization object to product disks recovers the seven pieces of
  data and the six relations.

  For a square-zero extension \(R'\to R\), deforming the seven
  structure maps while preserving the six relations is the
  Maurer--Cartan lifting problem in the dg Lie algebra of mixed
  factorization derivations
  \(\operatorname{Der}^{\mathrm{fact,mix}}(\mathcal A_R)\otimes_R I\).
  The curvature of a partial lift is the degree-two component of
  \(\mathsf{Rel}^{6r}\) for the lifted seven-tuple; its cohomology class
  is precisely \(\operatorname{ob}_{6r}\) and is independent of choices.
  If this class vanishes, the remaining choices form the usual
  \(H^1\)-torsor.  This proves the positive recognition criterion for the
  mixed surface: a target supplies a universal Koszul-duality
  factorization surface exactly by giving an \(R\)-point and killing the
  six-relation obstruction tower in square-zero thickenings.
\end{proof}

\begin{defn}[Mixed-Dunn obstruction complex]\label{defn:mixed-dunn-obstruction-complex}
  The deformation complex of the candidate operad map
  \(\delta_{m,n}\) is
  \[
    \mathfrak D_{\mathrm{MD}}(m,n)=
    \operatorname{Cone}\!\left(
      C^\bullet_{\mathrm{Operad}}\!
        (\mathbb E_{m,n}^{\mathrm{mix}},\mathbb E_{m,n}^{\mathrm{mix}})
      \longrightarrow
      C^\bullet_{\mathrm{Operad}}\!
        (\mathbb E_m^{\mathrm{top}}\otimes\mathbb E_n^{\mathrm{hol}},
         \mathbb E_{m,n}^{\mathrm{mix}})
    \right)[-1].
  \]
  After a cofibrant filtration of the source operad has been chosen, the
  mixed-Dunn curvature is
  \[
    F_{\delta}=d\delta+\frac12[\delta,\delta]
      \in Z^1(\mathfrak D_{\mathrm{MD}}(m,n)).
  \]
  Its class
  \[
    \operatorname{ob}_{\mathrm{MD}}(\delta_{m,n})
      =[F_\delta]\in H^1(\mathfrak D_{\mathrm{MD}}(m,n))
  \]
  measures the simultaneous failure of the topological \(E_m\)
  operations, the holomorphic \(E_n\) operations, and the mixed
  interchange law to assemble into a strict operadic comparison.  Higher
  rectification obstructions lie in
  \(H^{r+1}(\operatorname{gr}^r\mathfrak D_{\mathrm{MD}}(m,n))\).
\end{defn}

\begin{thm}[Mixed-Dunn universal acceptance criterion]\label{thm:mixed-dunn-criterion}
  Let \(\delta_{m,n}\) be a morphism between cofibrant operadic models as
  in Definition~\ref{defn:mixed-dunn-fact6r-datum}, equipped with a
  complete exhaustive cofibrant filtration for which the obstruction
  tower below converges and has no hidden \(\varprojlim^1\) defect.  The mixed-Dunn
  surface is accepted by the universal Koszul-duality programme exactly
  under the following equivalent conditions.
  \begin{enumerate}[label=(\roman*)]
    \item \(\delta_{m,n}\) rectifies to a weak equivalence of operads and
      induces an equivalence
      \[
        \operatorname{Alg}_{\mathbb E_{m,n}^{\mathrm{mix}}}
          \simeq
        \operatorname{Alg}_{\mathbb E_m^{\mathrm{top}}\otimes
          \mathbb E_n^{\mathrm{hol}}}
      \]
      on the homotopy categories of algebras, with
      \(\mathrm{Fact}^{6r}_{\mathrm{mix}}(M,Y)\) represented by the
      tensor product of the topological and holomorphic structures.
    \item The aritywise homology map of \(\delta_{m,n}\) is an
      isomorphism, the primary class
      \(\operatorname{ob}_{\mathrm{MD}}(\delta_{m,n})\) vanishes, and
      every higher class in
      \(H^{r+1}(\operatorname{gr}^r\mathfrak D_{\mathrm{MD}}(m,n))\)
      vanishes with chosen null-homotopies compatible with operadic
      composition.
  \end{enumerate}
  When these classes do not vanish, their ordered tuple is the exact
  mixed-Dunn acceptance obstruction.
\end{thm}

\begin{proof}
  A weak equivalence between cofibrant operads induces a Quillen
  equivalence on their algebra categories
  \cite{lurie-ha}*{Thm.~A.3.7.5}.  This proves that (i) implies the
  aritywise homology isomorphism and that the curvature classes in
  \(\mathfrak D_{\mathrm{MD}}(m,n)\) vanish.

  Conversely, suppose (ii) holds.  The complete exhaustive cofibrant
  filtration reduces rectification of \(\delta_{m,n}\) to a convergent
  tower of lifting problems.  The
  primary curvature \(F_\delta\) is the obstruction at the first stage;
  the associated-graded obstruction groups record the successive
  failures of operadic composition, Beilinson--Drinfeld holomorphic
  compatibility, and the topological-holomorphic interchange law.  By
  hypothesis each obstruction class is zero and a compatible
  null-homotopy has been chosen, so the tower has a rectified operad map.
  The aritywise homology isomorphism makes the rectified map a weak
  equivalence.  Applying the cofibrant-operad Quillen-equivalence theorem
  gives (i), and Proposition~\ref{prop:fact6r-functor-of-points-recognition}
  identifies the resulting algebra objects with the displayed functor of
  points.
\end{proof}

\begin{cor}[Matched-conventions factorization]\label{cor:matched-conventions-factorization}
  Every target theorem using the local Hamiltonian BF/Moyal theorem through
  a matched-conventions datum \(\mathfrak C_{\mathrm{tar}}\) factors through
  the morphism
  \[
    \Phi_{\mathfrak C_{\mathrm{tar}}}=
    \chi_{\mathrm{op}}^{-1}\,
    \Phi^{\mathrm{Ham}}_{\mathrm{fact}}\,
    \chi_{\mathrm{cl}}
  \]
  constructed in Theorem~\ref{thm:matched-conventions-transfer}, followed
  by the target's own specialization, compactification, or automorphic
  construction.
\end{cor}

\begin{proof}
  Theorem~\ref{thm:matched-conventions-transfer} constructs the only map
  whose formal stalk is obtained from the local theorem and the comparison
  morphisms \(\chi_{\mathrm{cl}}\), \(\chi_{\mathrm{op}}\).  Any subsequent
  operation belongs to the target datum: specialization along
  \((\Sigma_{d-1},C)\), compact BV integration, or the Borcherds
  automorphic construction.  Thus the local theorem enters the target proof
  through the displayed factorization.
\end{proof}

\begin{cor}[Universal Koszul target acceptance criterion]\label{cor:target-obstruction-criterion}
  A compact BCOV, Vol III CY-to-chiral, Igusa/BKM, or other
  cross-volume theorem is accepted as a universal Koszul-duality target of
  the local Hamiltonian BF/Moyal theorem exactly by a datum
  \(\mathfrak C_{\mathrm{tar}}\) with
  \[
    \operatorname{Ob}_{\mathrm{UKD}}(\mathfrak C_{\mathrm{tar}})=0
  \]
  and chosen null-homotopies for all components of the obstruction tower.
  The accepted theorem-data include the formal stalk
  \[
    \chi_{\mathrm{op}}^{-1}\,
    \Phi^{\mathrm{Ham}}_{\mathrm{fact}}\,
    \chi_{\mathrm{cl}},
  \]
  the global descent datum, the QME/anomaly null-homotopies, and any
  mixed-Dunn or six-relation factorization null-homotopies asserted by
  the target.  If one component is absent or nonzero, the exact residual
  is the corresponding component of
  \(\operatorname{Ob}_{\mathrm{UKD}}(\mathfrak C_{\mathrm{tar}})\);
  no compact CY\(_3\), global BCOV, Vol III, Igusa, or BKM conclusion is
  accepted without killing that class.
\end{cor}

\begin{proof}
  Theorem~\ref{thm:matched-conventions-transfer} constructs the accepted
  target morphism after the target datum has been fixed and the universal
  Koszul-duality acceptance class has been null-homotoped.  The class
  contains the period, descent, anomaly, QME, six-relation, and
  mixed-Dunn components.  Lemma~\ref{lem:no-formal-disk-transfer}
  identifies these components as target theorem data rather than
  consequences of the formal disk.  Therefore a nonzero component is the
  named obstruction class, and a zero component with a null-homotopy is
  exactly the accepted theorem datum.
\end{proof}

\begin{defn}[Named target convention data]\label{rmk:matched-conventions-templates}
  The cross-volume targets require the following matched-conventions data.
  \begin{enumerate}[label=(\roman*)]
    \item \emph{Vol III CY-to-chiral datum.}
      \[
      \mathfrak C_{\mathrm{CY\to ch}}=
      \bigl(d,Y,\eta_{\mathrm{CY}}\in HC^-_d(Y),
      (\Sigma_{d-1},C),\Phi^{\mathrm{FA}}_d,
	      \mathrm{Sp}_{\Sigma_{d-1},C},\kappa_{\mathrm{cat}},
      \tau,\mathfrak f,\mc O_{\mathrm{QME}},
      \mathfrak K_{\mathrm{KD}},
      \operatorname{Ob}_{\mathrm{UKD}}\bigr).
      \]
      The comparison map from \(\mathfrak C_{\mathrm{loc}}^{(2)}\) is the
      formal \(d=2\) Darboux normalization at the chosen brane point.
      The Vol III convention is the two-stage factorization
      \[
        \Phi_d=\mathrm{Sp}_{\Sigma_{d-1},C}\circ\Phi^{\mathrm{FA}}_d .
      \]
	      For a compact CY\(_3\) target the total-space
	      \(\kappa_{\mathrm{cat}}\) is the Hodge supertrace
	      \(\sum_q(-1)^qh^{0,q}(Y)\); in particular
	      \(\kappa_{\mathrm{cat}}(K3\times E)=0\).  This component is
	      distinct from any Heisenberg, BKM, or fibre normalization in
	      Vol III.  Any BKM weight comparison is therefore a separate
	      component of
      \(\operatorname{Ob}_{\mathrm{UKD}}\), not a consequence of the
      unqualified total-space supertrace.
    \item \emph{Compact BCOV datum.}
      \[
      \mathfrak C_{\mathrm{BCOV}}=
      \bigl(Y^3,\Omega_Y,\mathrm{PV}^{*,*}(Y)[[t]],Q_{\mathrm{BCOV}},
      P_{\mathrm{prop}},L,\mathfrak f_{S^3},
      I_{\mathrm{ct}},\mc O_{\mathrm{HAE}},
      \mathfrak K_{\mathrm{KD}},
      \operatorname{Ob}_{\mathrm{UKD}}\bigr).
      \]
      Here \(P_{\mathrm{prop}}\) is the global gauge-fixed propagator,
      \(I_{\mathrm{ct}}\) is the counterterm scheme, and
      \(\mc O_{\mathrm{HAE}}\) is the holomorphic-anomaly/QME obstruction
      complex.
    \item \emph{Igusa/BKM datum.}
      \[
      \mathfrak C_{\mathrm{BKM}}=
      \bigl(\varphi_{\mathrm{Jac}},\Lambda_{\mathrm{Borch}},
      W,\rho,\mathrm{ch}_{\mathrm{Hall}},\ell_{\mathrm{or}},
      \pi_{\mathrm{prim}},\kappa_{\mathrm{BKM}},
      \tau_{\mathrm{DT/PT/OP}},
      \operatorname{Ob}_{\mathrm{UKD}}\bigr).
      \]
      The entries are the Jacobi or modular input, Borcherds lattice, Weyl
      chamber, character, Hall or chiral source, orientation line, primitive
      recognition map, and scalar DT/PT/OP normalization.
      In the \(\Delta_5\) row the matched constants are
      \[
        D_5=64^{-1}\Delta_5,\qquad
        \operatorname{den}(\mathfrak g_{\Delta_5})
          =64^{-1}\Delta_5(2Z),
      \]
      \[
        \kappa_{\mathrm{BKM}}(\Phi_1)=c_1(0)/2=10/2=5,\qquad
        Z^X_{\mathrm{OP}}=-4096\,\Delta_5^{-2}.
      \]
      The orientation comparison
      \(\epsilon_o=\nu_{\Delta_5}\), compact Hall constants, and
      primitive BKM recognition are target obstructions; they are not
      supplied by the local \(d=2\) Hamiltonian theorem.
    \item \emph{Global Hamiltonian descent datum.}
      \[
      \mathfrak C_{\mathrm{glob}}=
      \bigl(L,\mc H_X=\mc O_X/\C_X,
      \operatorname{per}(v)=\delta(-\iota_v\omega),
      \mathfrak G_{\mathrm{WR}}(L),
      \{\operatorname{ob}^{(r)}_{\mathrm{WR}}\}_{r\ge1},
      h_{\mathrm{cent}},\operatorname{Ob}_{\mathrm{glob}},
      \Theta_{\mathrm{KD}}\bigr).
      \]
      The vanishing condition is the one in
      Theorem~\ref{thm:global-descent-criterion}; its output is the
      global universal Koszul-duality descent surface.
    \item \emph{Mixed-Dunn datum.}
      \[
      \mathfrak C_{\mathrm{MD}}=
      \bigl(\mathbb E_m^{\mathrm{top}},\mathbb E_n^{\mathrm{hol}},
      \mathbb E_{m,n}^{\mathrm{mix}},
      \mathrm{Fact}^{6r}_{\mathrm{mix}},
      \mathsf{Rel}^{6r},\delta_{m,n},
      \operatorname{ob}_{6r},
      \mathfrak D_{\mathrm{MD}}(m,n),
      \operatorname{ob}_{\mathrm{MD}}\bigr).
      \]
      The vanishing condition is the simultaneous six-relation and
      rectification condition in
      Proposition~\ref{prop:fact6r-functor-of-points-recognition} and
      Theorem~\ref{thm:mixed-dunn-criterion}.
  \end{enumerate}
\end{defn}

% --- End of appendix.
