% !TEX root = main.tex
%
% Lower-central Tate-pronilpotent bar-cobar Quillen equivalence.
%
% Relative model-categorical promotion of the cochain-level Tate
% bar-cobar identity of \ref{lem:continuous-bar-cobar}.  The Quillen
% statements below live in the admissible bounded-below
% Mittag-Leffler Tate envelope fixed in
% \ref{stmt:tate-model-envelope}.  They do not assert a model
% structure on every raw Tate vector space and do not solve the
% analytic Casimir / heat-kernel residual.
%
% We use
% Loday-Vallette \emph{Algebraic Operads} (2012) Ch. 11-13 sign and
% suspension conventions. The Tate categorical machinery is
% Costello-Gwilliam Vol. I \S\S 6.1, 6.4, 7.2 (factorization
% algebra, local constancy, extension-from-a-basis vocabulary)
% combined with Hinich \emph{Homological algebra of homotopy
% algebras} (1997) \S 2 transfer theorem.
%
% Sign conventions: Koszul. Suspension
% $s\colon V\to V[1]$ shifts homological degree up by one. The bar
% and cobar functors satisfy
%   $\mathrm{Bar}(A)=T^c(s\overline A),\quad
%    \Omega(C)=T(s^{-1}\overline C)$,
% with differentials assembled from $d_A,m_A,\Delta_C,d_C$ in the
% standard Loday-Vallette sign (\S 2.2.6, \S 11.1).

\subsection[Tate Quillen equivalence and the infinity-categorical upgrade]{Tate Quillen equivalence and the $\infty$-categorical
upgrade of the cochain bar-cobar identity}\label{sec:tate-quillen}

\subsubsection{Categorical home}

Let $\Cat{TateVec}$ be the closed symmetric monoidal category of
complete filtered Tate $\C$-vector spaces of \alpharef. The
filtration on every object is taken \emph{complete and Hausdorff}:
$V=\varprojlim_w V_{\leq w}$ and $\bigcap_w F^w V=0$. Concrete
morphisms are filtration-preserving continuous chain maps. The
working ambient category is the bounded-below filtered subcategory
$\Cat{TateChain}_{\geq 0}$ of non-negatively filtered chain
complexes in $\Cat{TateVec}$, large enough to contain every CE
  chain coalgebra and completed enveloping algebra used here.  The
  exact completion used below is constructed first.  The
  model-categorical statements add transfer, smallness, and monoid
  hypotheses to this exact Mittag-Leffler habitat; they are not
  statements about the raw category of all Tate spaces.

\begin{defn}[Strict finite-window Mittag-Leffler Tate habitat]
\label{defn:strict-ml-tate-habitat}
  Let \(\Cat{MLTateChain}_{\geq0}^{\mathrm{str}}\) be the category whose
  objects are inverse systems
  \[
    V=(V_{\leq M},\pi^V_{M,N})_{M\geq N\geq1}
  \]
  of bounded-below finite-dimensional chain complexes over \(\C\), with
  degreewise surjective transition maps.  The represented complete
  object is
  \[
    |V|=\varprojlim_MV_{\leq M},\qquad
    F^M|V|=\ker(|V|\to V_{\leq M-1}).
  \]
  Morphisms are compatible families of chain maps
  \(f_{\leq M}\colon V_{\leq M}\to W_{\leq M}\).  The completed tensor
  product is defined on paired windows by
  \[
    V\widehat\otimes_{\mathrm{ML}}W
      =
    \left(
      V_{\leq M}\otimes W_{\leq M}
    \right)_{M\geq1},
  \]
  with the induced surjective transition maps, and
  \[
    |V\widehat\otimes_{\mathrm{ML}}W|
      =
    \varprojlim_M(V_{\leq M}\otimes W_{\leq M}).
  \]
  The continuous dual attached to this strict tower is
  \[
    V^\vee_{\mathrm{ML}}=\varinjlim_MV_{\leq M}^\vee .
  \]
  A morphism is an admissible filtered weak equivalence when each
  \(f_{\leq M}\) and the induced associated-graded map are
  quasi-isomorphisms.

  The only universal property asserted for this habitat is the ordinary
  inverse-limit one: a compatible family \(x_M\in V_{\leq M}\) determines
  a unique element \(x\in |V|\), and every map out of a test strict tower
  is exactly a compatible family of finite-window maps.  No initial or
  terminal property among all completions of a Tate vector space is
  asserted.
\end{defn}

\begin{prop}[Exactness and kernels in the strict ML habitat]
\label{prop:strict-ml-habitat-exactness}
  In \(\Cat{MLTateChain}_{\geq0}^{\mathrm{str}}\):
  \begin{enumerate}[label=(\roman*)]
    \item the filtration on \(|V|\) is complete and Hausdorff;
    \item inverse limits of strict surjective towers are exact, so
      \(H^\bullet(|V|)=\varprojlim_MH^\bullet(V_{\leq M})\) and
      \(\varprojlim^1_MH^{\bullet-1}(V_{\leq M})=0\);
    \item completed tensor products and continuous duals are computed by
      the displayed finite-window formulas;
    \item if \(H=(H_{\leq M})\) and \(D=(D_{\leq M})\) are paired strict
      ML systems and finite tensors
      \(C_M\in H_{\leq M}\otimes D_{\leq M}\) are compatible under
      transition, then
      \[
        C=\varprojlim_MC_M
          \in |H|\widehat\otimes_{\mathrm{ML}}|D|
      \]
      exists and is the unique strict ML kernel with those finite-window
      projections.
  \end{enumerate}
\end{prop}

\begin{proof}
  Completeness is the definition of \(|V|\) as an inverse limit; the
  intersection of the kernels \(F^M|V|\) is zero because an element whose
  image vanishes in every finite quotient is the zero compatible family.
  Surjectivity of the transition maps gives the Mittag-Leffler condition.
  The Milnor exact sequence then has zero \(\varprojlim^1\)-term, proving
  exactness and the cohomology formula.  The tensor and dual formulas are
  definitions inside the strict habitat and are finite-dimensional on each
  window.  Finally, a compatible tensor family \((C_M)_M\) is precisely an
  element of the inverse limit
  \(\varprojlim_M(H_{\leq M}\otimes D_{\leq M})\), which is the completed
  tensor product by definition.  The uniqueness is the inverse-limit
  universal property of Definition~\ref{defn:strict-ml-tate-habitat}.
\end{proof}

\begin{stmt}[Admissible Tate model envelope]\label{stmt:tate-model-envelope}
  An admissible Tate model envelope is a bounded-below, locally
  presentable symmetric monoidal model category
  \(\Cat{TateChain}_{\geq0}^{\mathrm{adm}}\) equipped with a fully
  faithful exact symmetric-monoidal embedding of the strict habitat
  \[
    \Cat{MLTateChain}_{\geq0}^{\mathrm{str}}
      \hookrightarrow
    \Cat{TateChain}_{\geq0}^{\mathrm{adm}},
  \]
  and containing the CE chains, completed enveloping algebras, completed
  symmetric algebras, and finite-window inverse systems used in this
  manuscript.  Weak equivalences are admissible filtered
  quasi-isomorphisms: quasi-isomorphisms on every finite quotient and on
  associated graded.  The tensor product restricts to
  \(\widehat\otimes_{\mathrm{ML}}\) on strict Mittag-Leffler systems, and
  filtered inverse limits with surjective transition maps are exact by
  Proposition~\ref{prop:strict-ml-habitat-exactness}.  The additional
  hypotheses are transfer and smallness for the bar-cobar adjunction, the
  monoid axiom for completed tensor products, and compatibility of
  \(\widehat\otimes\) with the finite-window model structures.  All
  Quillen statements below are relative to such an envelope.
\end{stmt}

\begin{lem}[Mittag-Leffler dictionary for closed Tate windows]
\label{lem:tate-mittag-leffler-dictionary}
  Let
  \[
    \{V_{\leq M}\}_{M\geq1}
    \quad\text{and}\quad
    \{W_{\leq M}\}_{M\geq1}
  \]
  be inverse systems of finite-dimensional complexes with surjective
  transition maps, and put
  \[
    V=\varprojlim_MV_{\leq M},\qquad
    W=\varprojlim_MW_{\leq M}.
  \]
  In the strict ML habitat, and hence in any admissible envelope
  containing it, the following assertions hold:
  \begin{enumerate}[label=(\roman*)]
    \item \(\varprojlim\) is exact on these systems, so
      \(H^\bullet(V)=\varprojlim_MH^\bullet(V_{\leq M})\);
    \item continuous dualization changes the inverse system into the
      direct system of finite duals:
      \(V^\vee_{\mathrm{cont}}=\varinjlim_MV_{\leq M}^\vee\);
    \item completed tensor products are computed windowwise:
      \(V\widehat\otimes W
        =\varprojlim_M(V_{\leq M}\otimes W_{\leq M})\) whenever the
      transition maps are the paired finite-window truncations;
    \item a map \(f\colon V\to W\) is an admissible filtered
      quasi-isomorphism iff each finite-window map
      \(f_{\leq M}\colon V_{\leq M}\to W_{\leq M}\) is a
      quasi-isomorphism and the induced associated-graded maps are
      quasi-isomorphisms.
  \end{enumerate}
\end{lem}

\begin{proof}
  Surjectivity of the transition maps gives the Mittag-Leffler
  condition, hence \(\varprojlim^1=0\).  The cohomology assertion is
  the standard Milnor exact sequence with the \(\varprojlim^1\)-term
  killed.  Continuous linear functionals on \(V\) factor through a
  finite quotient \(V_{\leq M}\), giving the displayed direct limit of
  duals.  The completed tensor product in
  Definition~\ref{defn:strict-ml-tate-habitat} is defined by the same
  finite-window inverse system, so item (iii) is tautological inside the
  strict habitat.  Item (iv) is the definition of weak equivalence in
  Definition~\ref{defn:strict-ml-tate-habitat} and
  Statement~\ref{stmt:tate-model-envelope}.
\end{proof}

\begin{defn}[Closed-window obstruction terms]
\label{defn:closed-window-obstruction-terms}
  Let \(\mathfrak h=\varprojlim_M\mathfrak h_{\leq M}\) be a complete
  filtered Lie algebra with finite-dimensional windows and surjective
  transition maps \(\pi_{M,N}\).  Write
  \(D_{\leq M}\) for a finite dual module paired with
  \(\mathfrak h_{\leq M}\), with surjective transition maps
  \(\pi^\vee_{M,N}\), and put
  \(D_{\mathrm{cont}}=\varprojlim_MD_{\leq M}\).  For \(M\geq N\)
  define:
  \[
    \mathfrak o^{\mathrm{br}}_{M,N}(x,y)
      =\pi_{M,N}[x,y]_M-[\pi_{M,N}x,\pi_{M,N}y]_N,
  \]
  \[
    \mathfrak o^{\mathrm{coad}}_{M,N}(x,\lambda)
      =\pi^\vee_{M,N}(x\cdot_M\lambda)
       -(\pi_{M,N}x)\cdot_N(\pi^\vee_{M,N}\lambda),
  \]
  and
  \[
    \mathfrak o^{\mathrm{Cas}}_{M,N}
      =(\pi_{M,N}\otimes\pi^\vee_{M,N})C_M-C_N .
  \]
  The closed window system is \emph{cochain-CE/PV-admissible} if
  \(\mathfrak o^{\mathrm{br}}\) and \(\mathfrak o^{\mathrm{coad}}\)
  vanish for all \(M\geq N\).  It is
  \emph{kernel-admissible} only after the additional Casimir term
  \(\mathfrak o^{\mathrm{Cas}}\) vanishes in the chosen completed tensor
  category.  The Casimir condition is not part of the coordinate CE/PV
  cochain identity.
\end{defn}

\begin{lem}[Closed CE/PV finite-window compatibility and variance boundary]
\label{lem:closed-ce-pv-window-limit}
  Assume the closed window system of
  Definition~\ref{defn:closed-window-obstruction-terms} is
  cochain-CE/PV-admissible and each finite window has the finite cotangent
  CE/PV identity
  \[
    \Phi_M\colon
    C^\bullet_{\mathrm{CE}}\bigl(\mathfrak h_{\leq M}\ltimes
      D_{\leq M}[1]\bigr)
    \xrightarrow{\sim}
    \mathrm{PV}\bigl(\mathbf S(\mathfrak h_{\leq M})\bigr).
  \]
  Then the \(\Phi_M\) are compatible as finite coordinate tests under the
  contravariant CE pullbacks and the corresponding PV coordinate maps.
  They do not by themselves form an inverse system of dg cochain
  projections.  A completed admissible filtered quasi-isomorphism
  \[
    \Phi\colon
    C^\bullet_{\mathrm{CE},\mathrm{cont}}
      \bigl(\mathfrak h\ltimes D_{\mathrm{cont}}[1]\bigr)
    \xrightarrow{\sim}
    \mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr)
  \]
  follows only after one supplies either a chain-side inverse limit with
  exact continuous dualization or a topology whose cochain transition maps
  are dg maps.  If the kernel-admissible Casimir condition is also
  supplied, the same finite windows carry compatible \(P_0\)-pairings and
  kernels in that chosen tensor category.
\end{lem}

\begin{proof}
  The finite map \(\Phi_M\) is determined on generators by
  \(c\mapsto\theta\) and \(u\mapsto O\).  Vanishing of
  \(\mathfrak o^{\mathrm{br}}_{M,N}\) says the CE differential on the
  Hamiltonian ghosts commutes with transition maps.  Vanishing of
  \(\mathfrak o^{\mathrm{coad}}_{M,N}\) says the cotangent-coordinate
  part of the CE differential, and equivalently the Lichnerowicz
  differential on \(O\)-coordinates, commutes with transition maps.
  Therefore the finite squares with \(\Phi_M\) and \(\Phi_N\) commute in
  the variance appropriate to cochains.  A quotient
  \(\mathfrak h_{\leq M}\twoheadrightarrow\mathfrak h_{\leq N}\) induces
  CE cochain maps by pullback, not by projection from \(M\) to \(N\).
  Thus inverse-limit language on cochains requires the additional
  continuous-dualization or topology hypothesis stated above.  Vanishing
  of \(\mathfrak o^{\mathrm{Cas}}_{M,N}\) is the separate statement that
  the finite \(P_0\)-brackets and BV coefficient pairings are compatible
  under transition in the chosen kernel-admissible tensor category.
\end{proof}

\subsubsection{Direct admissibility recognition}

\begin{defn}[Open-side twisting cochain datum]
\label{defn:universal-open-side-twisting-cochain}
  Fix a candidate admissible filtered-cobar datum
  \[
    \mathfrak h=\varprojlim_M\mathfrak h_{\leq M},\qquad
    D=\varinjlim_M\mathfrak h_{\leq M}^{\vee},\qquad
    \mathfrak g=\mathfrak h\ltimes D[1],
  \]
  a complete augmented filtered open \(A_\infty\)-algebra
  \(A_{\mathrm{op}}\), and the completed CE/PV target
  \[
    B_{\mathrm{cl}}
      =
      C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
      \cong
      \mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{coord}}(\mathfrak h)\bigr).
  \]
  Put \(C_{\mathrm{op}}=\mathrm{Bar}(A_{\mathrm{op}})\), with reduced bar
  differential \(b_{\mathrm{op}}\), coproduct \(\Delta\), and iterated
  reduced coproducts \(\Delta^{(r)}\).  The bar coalgebra is required to
  be locally conilpotent in the completed sense: for every finite output
  window of \(B_{\mathrm{cl}}\) and every finite coaugmentation stage of
  \(C_{\mathrm{op}}\), the iterated reduced coproducts \(\Delta^{(r)}\)
  vanish for all sufficiently large \(r\).  Equivalently, the
  conilpotence obstruction in
  Definition~\ref{defn:universal-koszul-obstruction-complex} is zero.
  Without this condition the Maurer--Cartan curvature below is not a
  continuous map and no twisting-cochain datum has been constructed.

  An open-side twisting cochain is a continuous degree-one map
  \[
    \tau\colon C_{\mathrm{op}}\longrightarrow B_{\mathrm{cl}}
  \]
  vanishing on the coaugmentation and satisfying the Maurer--Cartan
  equation
  \[
    d_{B_{\mathrm{cl}}}\tau+\tau b_{\mathrm{op}}
      +\sum_{r\geq2}
        m_r^{B_{\mathrm{cl}}}\bigl(\tau^{\otimes r}\bigr)
        \Delta^{(r)}
      =0 .
  \]
  For the dg \(P_0\)-algebra \(B_{\mathrm{cl}}\), the higher
  multiplications vanish and this reads
  \[
    d_{B_{\mathrm{cl}}}\tau+\tau b_{\mathrm{op}}
      +\mu_{B_{\mathrm{cl}}}(\tau\otimes\tau)\Delta=0 .
  \]
  Equivalently,
  \[
    d_{\mathrm{conv}}\tau+\frac12[\tau,\tau]_{\mathrm{conv}}=0,\qquad
    d_{\mathrm{conv}}f=d_{B_{\mathrm{cl}}}f
      -(-1)^{|f|}f\,b_{\mathrm{op}},
  \]
  in the continuous convolution dg Lie algebra
  \(\Hom_{\mathrm{cont}}(C_{\mathrm{op}},B_{\mathrm{cl}})\).

  The twisting cochain induces the completed cobar morphism
  \[
    \kappa_\tau\colon
    \Omega C_{\mathrm{op}}
    \longrightarrow B_{\mathrm{cl}}.
  \]
  Its associated-graded symbol is the map
  \[
    \operatorname{gr}\kappa_\tau\colon
    \operatorname{gr}\Omega\mathrm{Bar}(A_{\mathrm{op}})
    \longrightarrow
    \operatorname{gr}B_{\mathrm{cl}}.
  \]
  In the Hamiltonian trace presentation the required linear symbol is
  \[
    \operatorname{gr}\kappa_\tau(B_f)=O_f,\qquad
    \operatorname{gr}\kappa_\tau(\Theta_{\rho_{a,b}})=\theta^{a,b},
  \]
  after the scalar trace is removed and the cotangent generator is read
  in the principal-part local-dual basis.
\end{defn}

\begin{defn}[Open-side Koszul obstruction complex]
\label{defn:universal-koszul-obstruction-complex}
  In the notation of
  Definition~\ref{defn:universal-open-side-twisting-cochain}, put
  \(D_{\leq M}=\mathfrak h_{\leq M}^\vee\),
  \(\mathrm{PV}_{\leq M}=\mathrm{PV}(\mathbf S(\mathfrak h_{\leq M}))\),
  and \(B_{\mathrm{cl},\leq M}\) for the corresponding finite CE/PV
  window.  The obstruction datum is
  \[
    \mathcal O_{\mathrm{Kos}}(\mathfrak h,D,A_{\mathrm{op}},\tau)
      =
      \mathcal O_{\mathrm{win}}
      \oplus
      \mathcal O_{\mathrm{top}}
      \oplus
      \mathcal O_{\mathrm{conilp}}
      \oplus
      \mathcal O_{\mathrm{MC}}(\tau)
      \oplus
      \mathcal O_{\mathrm{cobar}}(\tau).
  \]
  The window and conilpotence summands are degree-zero:
  \[
    \mathcal O_{\mathrm{win}}
      =
      \prod_{M\geq N}
      \left(
        \Hom(\Lambda^2\mathfrak h_{\leq M},\mathfrak h_{\leq N})
        \oplus
        \Hom(\mathfrak h_{\leq M}\otimes D_{\leq M},D_{\leq N})
      \right)
      \oplus
      Q_{\mathrm{Cas}},
  \]
  where
  \[
    Q_{\mathrm{Cas}}
      =
      \frac{\varprojlim_M(\mathfrak h_{\leq M}\otimes D_{\leq M})}
           {\operatorname{im}(\mathfrak h\widehat\otimes D)} .
  \]
  The distinguished window class is
  \[
    \omega_{\mathrm{win}}
      =
      \bigl(
        \mathfrak o^{\mathrm{br}}_{M,N},
        \mathfrak o^{\mathrm{coad}}_{M,N},
        [(C_{\leq M})_M]
      \bigr),
  \]
  where the first two terms are those of
  Definition~\ref{defn:closed-window-obstruction-terms} and the last
  term is the compatible finite-window Casimir family modulo strict
  completed tensors.  The topology summand is
  \[
    \mathcal O_{\mathrm{top}}^n
      =
      \varprojlim\nolimits^1_M
        H^{n-1}\!\left(C^\bullet_{\mathrm{CE}}(\mathfrak g_{\leq M})\right)
      \oplus
      \varprojlim\nolimits^1_M
        H^{n-1}\!\left(\mathrm{PV}_{\leq M}\right).
  \]
  The conilpotence summand is
  \[
    \mathcal O_{\mathrm{conilp}}
      =
      \left(
        C_*^{\mathrm{CE}}(\mathfrak g)/
        \bigcup_rF^{(r)}_{\mathrm{coaug}}
          C_*^{\mathrm{CE}}(\mathfrak g)
      \right)
      \oplus
      \bigcap_{r\geq1}\mathfrak g^{(r)}.
  \]

  The Maurer--Cartan summand is the explicit curvature
  \[
    \mathcal O_{\mathrm{MC}}(\tau)
      =
      \operatorname{MC}(\tau)
      =
      d_{\mathrm{conv}}\tau+\frac12[\tau,\tau]_{\mathrm{conv}}
      \in
      \Hom^2_{\mathrm{cont}}(C_{\mathrm{op}},B_{\mathrm{cl}}).
  \]
  The cobar obstruction complex is
  \[
    \mathcal O_{\mathrm{cobar}}(\tau)
      =
      \operatorname{Cone}(\operatorname{gr}\kappa_\tau)
      \oplus
      \bigoplus_n
      \varprojlim\nolimits^1_M
        H^{n-1}\!\left((\Omega C_{\mathrm{op}})_{\leq M}\right)[-n]
      \oplus
      \bigoplus_n
      \varprojlim\nolimits^1_M
        H^{n-1}\!\left(B_{\mathrm{cl},\leq M}\right)[-n].
  \]
\end{defn}

\begin{thm}[Filtered-cobar admissibility criterion]
\label{thm:universal-filtered-cobar-recognition}
  Fix a candidate datum as in
  Definitions~\ref{defn:universal-open-side-twisting-cochain} and
  \ref{defn:universal-koszul-obstruction-complex}.  Assume the
  filtrations on \(\Omega C_{\mathrm{op}}\) and \(B_{\mathrm{cl}}\) are
  bounded below, complete, separated, and strongly convergent, with
  finite-dimensional associated graded pieces in every total degree.
  Assume moreover that the local conilpotence condition in
  Definition~\ref{defn:universal-open-side-twisting-cochain} holds and
  continuous dualization is exact on the finite-window towers.
  Then the following conditions are equivalent.
  \begin{enumerate}[label=(A\arabic*)]
    \item The datum is accepted: the generator substitution
      \(c\mapsto\theta,\ u\mapsto O\) is the completed CE/PV identity,
      \(\tau\) is a twisting cochain, and
      \[
        \kappa_\tau\colon
        \Omega\mathrm{Bar}(A_{\mathrm{op}})
        \longrightarrow B_{\mathrm{cl}}
      \]
      is an admissible filtered quasi-isomorphism with the linear symbol
      of Definition~\ref{defn:universal-open-side-twisting-cochain}.
    \item The obstruction equations are exact:
      \[
        \omega_{\mathrm{win}}=0,\qquad
        \mathcal O_{\mathrm{conilp}}=0,\qquad
        \mathcal O_{\mathrm{MC}}(\tau)=0,\qquad
        H^\bullet\!\left(
          \mathcal O_{\mathrm{top}}
          \oplus
          \mathcal O_{\mathrm{cobar}}(\tau)
        \right)=0 .
      \]
  \end{enumerate}
  When these equivalent conditions hold,
  \[
    B_{\mathrm{cl}}
      \simeq
    A_{\mathrm{op}}
  \]
  in the homotopy category of complete augmented filtered
  \(A_\infty\)-algebras.  If the CE coalgebra is also used as the closed
  Koszul source, exact continuous duality identifies the dual form as
  \[
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
      \simeq
    A_{\mathrm{op}}^!
  \]
  precisely when the CE-side cobar map
  \(\Omega C_*^{\mathrm{CE}}(\mathfrak g)\to A_{\mathrm{op}}\) has the
  same exact associated-graded cone and \(\varprojlim^1\) obstruction.
\end{thm}

\begin{proof}
  The equality \(\omega_{\mathrm{win}}=0\) is equivalent to strict
  finite-window compatibility of the CE differential and the Schouten
  differential, with \(P_0\)-pairings added only in the
  kernel-admissible tensor category; this is exactly
  Lemma~\ref{lem:closed-ce-pv-window-limit} and
  Theorem~\ref{thm:universal-formal-local-ce-pv-recognition}.  The
  vanishing of \(\mathcal O_{\mathrm{top}}\) is the Milnor and variance
  condition identifying cohomology of the completed CE/PV objects with
  the admissible finite-window calculation.

  The local conilpotence hypothesis makes the Maurer--Cartan sum finite
  on each finite output window, hence a continuous curvature.  The
  equation \(\mathcal O_{\mathrm{MC}}(\tau)=0\) is then the
  Maurer--Cartan equation in the continuous convolution dg Lie algebra.
  It is equivalent to the statement that the adjoint map
  \(\kappa_\tau\) commutes with the completed cobar differential and the
  \(A_\infty\)-operations.  Without this equality there is no morphism
  to test.

  After the Maurer--Cartan equation holds, filter
  \(\Omega C_{\mathrm{op}}\) and \(B_{\mathrm{cl}}\) by tensor length
  and by the finite coordinate windows.  The mapping-cone summand in
  \(\mathcal O_{\mathrm{cobar}}(\tau)\) is acyclic exactly when
  \(\operatorname{gr}\kappa_\tau\) is a quasi-isomorphism.  The two
  \(\varprojlim^1\)-summands are exactly the Milnor defects for the
  completed source and target towers.  Strong convergence and
  completeness then make the spectral-sequence comparison theorem
  equivalent to admissible filtered quasi-isomorphism of
  \(\kappa_\tau\).  Necessity follows from the definition of admissible
  filtered quasi-isomorphism in the envelope: it is detected on the
  associated graded and on the exact finite-window towers.

  The bar-cobar counit
  \(\Omega\mathrm{Bar}(A_{\mathrm{op}})\to A_{\mathrm{op}}\) is an
  admissible filtered quasi-isomorphism under the same boundedness and
  convergence hypotheses.  Composing its inverse in the homotopy
  category with \(\kappa_\tau\) gives
  \(A_{\mathrm{op}}\simeq B_{\mathrm{cl}}\).  The final statement is the
  same argument applied to the CE coalgebra
  \(C_*^{\mathrm{CE}}(\mathfrak g)\), followed by exact continuous
  dualization.
\end{proof}

\begin{defn}[Tate cofibrantly generated model structure in the envelope]
  \label{defn:tate-model}
  Define generating cofibrations $I$ and acyclic cofibrations $J$
  by
  $$I=\bigl\{F^w S^{n-1}\hookrightarrow F^w D^n
       \mid n\in\Z_{\geq 0},\ w\in\N\bigr\},\qquad
    J=\bigl\{0\hookrightarrow F^w D^n
       \mid n\in\Z_{\geq 0},\ w\in\N\bigr\},$$
  where $S^{n-1},D^n$ are the standard sphere and disk chain
  complexes in $\Cat{Vec}$ and the Tate window $F^w(-)$ takes the
  $w$-th piece of the filtration. A morphism $f\colon V\to W$ in
  $\Cat{TateChain}_{\geq 0}^{\mathrm{adm}}$ is:
  \begin{enumerate}
    \item a \emph{weak equivalence} if it is an admissible filtered
      quasi-isomorphism in the sense of \alpharef:
      a quasi-isomorphism on every quotient $V/F^wV\to W/F^wW$ and
      on the associated graded;
    \item a \emph{cofibration} if it is in the class generated by
      $I$ under transfinite composition, retracts, and pushouts;
    \item a \emph{fibration} if it has the right lifting property
      against $J$.
  \end{enumerate}
\end{defn}

\begin{thm}[Admissible-envelope model-structure existence criterion]
  \label{thm:tate-model-structure}
  Under Statement~\ref{stmt:tate-model-envelope}, the triple
  \(\bigl(\Cat{TateChain}_{\geq 0}^{\mathrm{adm}},I,J\bigr)\)
  is a cofibrantly generated model category. The class of weak equivalences is
  closed under retracts and satisfies the two-out-of-three
  property; cofibrations and fibrations form complementary lifting
  classes; the small-object argument terminates after countably
  many steps because every Tate window is finite-dimensional and
  every generating cofibration changes only one window.
\end{thm}

\begin{proof}
  Quillen's small-object argument (\cite{quillen-htpy}*{\S II.3})
  applies in the admissible envelope once the following are
  verified:
  \begin{enumerate}[label=(\roman*)]
    \item $I$ and $J$ permit the small-object argument:
      the domains and codomains of the generating maps are small
      with respect to relative $I$-cell complexes because each
      generator lives in one finite-dimensional Tate window
      $V_{\leq w}$, hence is $\aleph_0$-small in the admissible
      envelope.
    \item Every map in $J$-cell is a weak equivalence: pushouts of
      acyclic generating cofibrations are levelwise acyclic by
      finite-dimensional standard chain-complex theory in each
      window, and the filtered colimit of windowwise acyclic
      cofibrations is acyclic by Mittag-Leffler exactness in the
      Tate filtration (\alpharef\ item~1).
    \item Every map with the right lifting property against $I$ is
      a trivial fibration: standard, levelwise.
  \end{enumerate}
  The two-out-of-three property for filtered quasi-isomorphisms
  follows from the long exact sequence of the filtration: a
  composite $V\to W\to U$ has filtered $E_1$-page agreeing with
  the composite of $E_1$-pages of $V\to W$ and $W\to U$ in each
  window, so two-out-of-three on each window propagates to the
  global filtered class. This proves the model structure in the
  chosen envelope only. No assertion is made for arbitrary unbounded
  Tate complexes outside it.
\end{proof}

\begin{lem}[Tail quotient obstruction invisible to finite-window weak equivalence]
\label{lem:tate-envelope-tail-boundary}
  Let \(\{V_d\}_{d\geq1}\) be nonzero finite-dimensional vector
  spaces with zero differential, and put
  \[
    V_{\oplus}=\bigoplus_{d\geq1}V_d,\qquad
    V_{\Pi}=\prod_{d\geq1}V_d .
  \]
  Filter both complexes by degree tails.  The inclusion
  \(V_{\oplus}\hookrightarrow V_{\Pi}\) is an admissible filtered weak
  equivalence in the sense of
  Statement~\ref{stmt:tate-model-envelope}: it is an isomorphism on
  every finite quotient and on associated graded pieces.  It is not an
  ordinary quasi-isomorphism of chain complexes.  Its cofiber has
  \[
    H^0(V_{\Pi}/V_{\oplus})=V_{\Pi}/V_{\oplus}\neq0 .
  \]
\end{lem}

\begin{proof}
  The quotient by the tail \(d>w_0\) is
  \[
    V_{\oplus}/\bigoplus_{d>w_0}V_d
      \cong \bigoplus_{d\leq w_0}V_d
      \cong \prod_{d\leq w_0}V_d
      \cong V_{\Pi}/\prod_{d>w_0}V_d .
  \]
  Thus the inclusion is an isomorphism on every finite quotient.  The
  associated graded in degree \(d\) is \(V_d\) on both sides, so the
  associated graded map is also an isomorphism.  This is precisely an
  admissible filtered weak equivalence.

  Since the differential is zero, ordinary cohomology is the underlying
  vector space.  A sequence with one nonzero component in every degree
  defines a nonzero class of \(V_{\Pi}/V_{\oplus}\).  Hence the cofiber
  has nonzero \(H^0\), and the inclusion is not an ordinary
  quasi-isomorphism.
\end{proof}

\begin{rmk}[Boundedness restriction is harmless]
  Restriction to $\Cat{TateChain}_{\geq 0}^{\mathrm{adm}}$ avoids inverse-limit
  pathologies in unbounded filtrations. Every CE coalgebra
  $C_*^{\mathrm{CE}}(\mathfrak g)$ and every completed enveloping
  algebra $\widehat U(\mathfrak g)$ that appears here is
  non-negatively filtered (CE length and PBW length are
  $\geq 0$). A model structure on the raw unbounded category
  $\Cat{TateChain}$ would require the Spaltenstein semi-model
  modification (\cite{lurie-ha}*{\S 7.5}) and is not needed for
  the application here.
\end{rmk}

\subsubsection{Operad-algebra transfer}

Let $\mathrm{Lie}_{\Cat{TateVec}}$ be the Lie operad in
$\Cat{TateVec}$, regarded as a $\Sigma$-cofibrant $\Sigma$-module
(by the standard Koszul resolution of the $\Sigma$-cofibrant
replacement), and similarly $\mathrm{Ass}^+_{\Cat{TateVec}}$ for
augmented associative. A $\mathrm{Lie}_{\Cat{TateVec}}$-algebra is
a Tate Lie algebra in $\Cat{TateVec}$; an
$\mathrm{Ass}^+_{\Cat{TateVec}}$-algebra is a Tate complete
augmented associative algebra. Write
$$\mathrm{TateLie}=\mathrm{Lie}_{\Cat{TateVec}}\text{-alg}_{\geq 0},
  \qquad \mathrm{TateAssocAlg}^+=
  \mathrm{Ass}^+_{\Cat{TateVec}}\text{-alg}_{\geq 0}$$
in $\Cat{TateChain}_{\geq 0}^{\mathrm{adm}}$.

\begin{lem}[Transferred model structures on Tate operad-algebras]
  \label{lem:transferred-model}
  In the admissible envelope, the free-forget adjunction
  $\mathrm{Free}_{\mathcal P}\dashv\mathrm{Forget}$ for
  $\mathcal P\in\{\mathrm{Lie}_{\Cat{TateVec}},
  \mathrm{Ass}^+_{\Cat{TateVec}}\}$ transfers the cofibrantly
  generated model structure of \ref{thm:tate-model-structure} to
  $\mathcal P\text{-alg}_{\geq 0}$ in the sense of
  Hinich~\cite{hinich-htpy-alg}*{\S 2.2}: the weak equivalences and
  fibrations in $\mathcal P\text{-alg}_{\geq 0}$ are the maps
  whose underlying chain map in
  $\Cat{TateChain}_{\geq 0}^{\mathrm{adm}}$ is one,
  and the cofibrations are determined by lifting.
\end{lem}

\begin{proof}
  Hinich's transfer theorem requires:
  \begin{enumerate}[label=(\arabic*)]
    \item a path object on every algebra of the form
      $\mathrm{Free}_{\mathcal P}(F^w D^n)$;
    \item that pushouts along generating acyclic cofibrations be
      weak equivalences.
  \end{enumerate}
  Item~(1) follows because $\mathcal P=\mathrm{Lie}$ or
  $\mathrm{Ass}^+$ is a $\Sigma$-cofibrant operad in
  $\Cat{TateVec}$; the path object is constructed from the
  cylinder object on chain complexes via the Berger-Moerdijk
  path-functor lift~\cite{berger-moerdijk-axiomatic}, valid
  whenever the operad is admissible and the ambient category is
  cofibrantly generated and proper. Item~(2) follows because
  $\mathcal P$ acts levelwise on each Tate window, and the windowwise
  finite-dimensional pushout is a quasi-isomorphism by
  Schwede-Shipley \cite{schwede-shipley-monoid}*{Lemma 2.3}.
  Filtered-colimit assembly preserves quasi-isomorphism by
  Mittag-Leffler exactness (\alpharef\ item~1).
\end{proof}

The dual coalgebra side requires more care: Hinich's transfer
applies to algebra categories, not coalgebra categories, because
the cofree coalgebra functor is not a left adjoint in general.
The substitute is the Aubry-Lemaire-Smirnov \cite{loday-vallette}
\S 11.4 model structure on conilpotent dg coalgebras transferred
through the bar-cobar adjunction itself.

\begin{defn}[Conilpotent Tate coalgebras]\label{defn:tate-conilp-coalg}
  Let
  $$\begin{aligned}
  \mathrm{TateConilpCoAlg}
  =\bigl\{\,(C,\Delta_C,d_C)\,:\,&
  C\in\Cat{TateChain}_{\geq 0}^{\mathrm{adm}},\\
  &\Delta_C\colon C\to C\widehat\otimes C
    \text{ continuous coproduct},\\
  &\text{coaugmentation filtration exhaustive}\,\bigr\}.
  \end{aligned}$$
  with morphisms continuous coalgebra maps. Conilpotency means
  the coaugmentation filtration $F^{(n)}_{\mathrm{coaug}}C=
  \ker(\overline\Delta^{(n)})$ is exhaustive: $C=\bigcup_n
  F^{(n)}_{\mathrm{coaug}}C$.
\end{defn}

\begin{lem}[Transferred model structure on Tate conilpotent
  coalgebras]\label{lem:tate-conilp-model}
  $\mathrm{TateConilpCoAlg}$ admits, in the admissible envelope, a
  model structure with
  \begin{itemize}
    \item weak equivalences = maps $f\colon C\to C'$ such that
      $\Omega(f)\colon\Omega(C)\to\Omega(C')$ is a weak
      equivalence in $\mathrm{TateAssocAlg}^+$
      (\ref{lem:transferred-model});
    \item cofibrations = monomorphisms of underlying filtered
      chain complexes;
    \item fibrations = right lifting against acyclic cofibrations.
  \end{itemize}
  Equivalently, this is the Lefevre-Hasegawa
  \cite{lefevre-hasegawa}*{Th.~1.3.1.2} transferred model structure
  in the admissible Tate envelope.
\end{lem}

\begin{proof}
  Lefevre-Hasegawa, with proof sketched in Loday-Vallette
  \S 11.4.10, constructs the conilpotent-coalgebra transferred
  model structure in the symmetric monoidal category of $\Q$- or
  $\C$-vector spaces. The proof passes through the cobar-bar
  adjunction $\Omega\colon\mathrm{ConilpCoAlg}\rightleftarrows
  \mathrm{AugAssocAlg}\colon\mathrm{Bar}$ and uses that
  \begin{enumerate}[label=(\roman*)]
    \item $\Omega$ takes coalgebra cofibrations (= mono with
      filtered cokernel) to algebra cofibrations;
    \item $\Omega$ inverts coalgebra weak equivalences;
    \item the unit $\eta_C\colon C\to\mathrm{Bar}\,\Omega(C)$ is a
      weak equivalence for every conilpotent dg coalgebra.
  \end{enumerate}
  Items~(i)-(iii) are checked windowwise (each Tate window is
  finite-dimensional, so the standard Lefevre-Hasegawa proof
  applies) and assemble by the transfer, smallness, monoid, completed
  tensor, and Mittag-Leffler exactness hypotheses built into
  Statement~\ref{stmt:tate-model-envelope}. The unit
  weak-equivalence~(iii) is precisely \alpharef\ item~3
  (admissible filtered qiso) inside that envelope.
\end{proof}

\subsubsection{Bar-cobar Quillen equivalence in the admissible envelope}

\begin{thm}[Tate bar-cobar Quillen equivalence in the admissible envelope]
  \label{thm:tate-bar-cobar-quillen}
  The bar-cobar adjunction
  $$\Omega\colon\mathrm{TateConilpCoAlg}\rightleftarrows
    \mathrm{TateAssocAlg}^+\colon\mathrm{Bar}$$
  is a Quillen equivalence with respect to the admissible-envelope
  model structures
  of \ref{lem:transferred-model} and \ref{lem:tate-conilp-model}.
  In particular:
  \begin{enumerate}
    \item $\Omega$ is left Quillen: it preserves cofibrations and
      acyclic cofibrations.
    \item $\mathrm{Bar}$ is right Quillen: it preserves
      fibrations and acyclic fibrations.
    \item For every cofibrant conilpotent coalgebra $C$ and every
      fibrant augmented associative algebra $A$, the unit
      $\eta_C\colon C\to\mathrm{Bar}\,\Omega(C)$ and the counit
      $\varepsilon_A\colon\Omega\,\mathrm{Bar}(A)\to A$ are weak
      equivalences.
    \item The induced derived adjunction
      $L\Omega\colon\mathrm{Ho}(\mathrm{TateConilpCoAlg})
      \rightleftarrows\mathrm{Ho}(\mathrm{TateAssocAlg}^+)\colon
      R\,\mathrm{Bar}$ is an equivalence of homotopy categories.
  \end{enumerate}
\end{thm}

\begin{proof}
  Items~(1) and~(2) are immediate from
  \ref{lem:tate-conilp-model}: weak equivalences in
  $\mathrm{TateConilpCoAlg}$ are defined as maps whose $\Omega$
  is a weak equivalence, and fibrations on the coalgebra side are
  defined by lifting.

  For item~(3), the unit $\eta_C$: filter both sides by symmetric
  / tensor length on the underlying $\Cat{TateVec}$ object, plus
  the Tate window filtration $F^w$. The associated graded gives,
  windowwise, a finite-dimensional dg coalgebra and the standard
  bar-cobar resolution
  $C^{\mathrm{gr}}\to\mathrm{Bar}\,\Omega(C^{\mathrm{gr}})$. By
  Loday-Vallette \cite{loday-vallette}*{\S 2.2.5, \S 11.1.5}, this
  is a quasi-isomorphism on each window. Conilpotency
  (\ref{defn:tate-conilp-coalg}) ensures the coaugmentation
  filtration on $C$ is exhaustive and Hausdorff, so the abutment
  of the spectral sequence of the filtration computes the global
  qiso. Mittag-Leffler exactness in the Tate filtration
  (\alpharef\ item~1) lifts the windowwise qiso to a global
  filtered qiso.

  For the counit
  \(\varepsilon_A\colon\Omega\,\mathrm{Bar}(A)\to A\), filter both
  sides by augmentation/tensor length and by the Tate window.  On every
  finite window and every finite length cap this is the ordinary
  bar-cobar counit for an augmented dg associative algebra over
  \(\C\), hence a quasi-isomorphism by the standard normalized bar
  resolution \cite{loday-vallette}*{\S 2.2.5, \S 11.1.5}.  The
  filtrations are bounded below, complete, and Hausdorff in the
  admissible envelope, so the spectral sequence comparison and
  Mittag-Leffler exactness lift the windowwise quasi-isomorphism to the
  completed Tate object.

  In the Lie specialization \(A=\widehat U(\mathfrak g)\), the same
  counit can also be read through the PBW filtration:
  \(\mathrm{gr}_{\mathrm{PBW}}\widehat U(\mathfrak g)\cong
  \widehat S_{\mathrm{Tate}}(\mathfrak g)\), and the associated graded
  comparison is the symmetric Koszul resolution of
  Loday-Vallette \cite{loday-vallette}*{\S 3.4.13}.  This is the
  closed-side PBW form used later, but the Quillen counit above is the
  associative bar-cobar counit for general \(A\).

  Item~(4) is formal from~(1)-(3) by Quillen's adjoint-functor
  theorem (\cite{hovey}*{Th.~1.3.10}).
\end{proof}

\subsubsection[Promotion to the associated infinity-categories]{Promotion to the associated $\infty$-categories}

\begin{cor}[Infinity-categorical Tate bar-cobar equivalence]
  \label{cor:tate-bar-cobar-infinity}
  Apply the Dwyer-Kan / Hammock-localization functor to the
  Quillen equivalence of \ref{thm:tate-bar-cobar-quillen}:
  $$N_\Delta\bigl(\mathrm{TateConilpCoAlg}^{\mathrm{cf}},W\bigr)
    \simeq
    N_\Delta\bigl(\mathrm{TateAssocAlg}^{+,\mathrm{cf}},W\bigr)$$
  as the $\infty$-categories associated to the admissible model
  envelope in the sense of Lurie's
  \emph{Higher Algebra} \S A.3, where $\mathrm{cf}$ denotes the
  full subcategory of cofibrant-fibrant objects and $W$ is the
  class of weak equivalences. The equivalence is induced by
  $L\Omega$ and $R\,\mathrm{Bar}$ at the cofibrant-fibrant level.
  Presentability is an attribute of the chosen locally presentable
  envelope, not of the raw Tate category.
\end{cor}

\begin{proof}
  Lurie \cite{lurie-ha}*{A.3.7.6, A.3.7.10}: a Quillen equivalence
  of model categories induces an equivalence of associated
  $\infty$-categories. The presentability of both sides, inside the
  envelope, is
  inherited from the cofibrant generation of the model structures
  (\ref{thm:tate-model-structure}, \ref{lem:transferred-model},
  \ref{lem:tate-conilp-model}) by Lurie A.2.6.8.
\end{proof}

\subsubsection{Identification with the Lie operadic Koszul duality}

The Quillen equivalence of \ref{thm:tate-bar-cobar-quillen} is
\emph{associative} bar-cobar. Specialization to the Lie operad
gives the cochain-level equivalence used in the CE/PV theorem.

\begin{cor}[Tate Lie bar-cobar / CE Koszul duality]
  \label{cor:tate-lie-bar-cobar}
  For $\mathfrak g$ a lower-central Tate-pronilpotent graded Lie algebra in the
  sense of \alpharef, the bar-cobar Quillen equivalence applied
  to $A=\widehat U(\mathfrak g)\in\mathrm{TateAssocAlg}^+$ yields
  the equivalence in the homotopy category
  $$L\Omega\bigl(C_*^{\mathrm{CE}}(\mathfrak g)\bigr)
    \xrightarrow{\sim}\widehat U(\mathfrak g),\qquad
    R\,\mathrm{Bar}\bigl(\widehat U(\mathfrak g)\bigr)
    \xrightarrow{\sim}C_*^{\mathrm{CE}}(\mathfrak g),$$
  and hence, after continuous dualization, a Lie-Koszul-dual equivalence
  of cochain algebras
  $$C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
    \simeq\bigl(\widehat U(\mathfrak g)\bigr)^!$$
  in the corresponding homotopy category of complete augmented
  Tate algebras.

  Inside the admissible envelope, by the symmetric-monoidal-functoriality of the bar-cobar
  Quillen equivalence \cite{loday-vallette}*{\S 13.2} and Lurie
  \cite{lurie-ha}*{\S 5.5}, this lifts to an equivalence of
  symmetric monoidal $\infty$-categories,
  $$N_\Delta\bigl(\mathrm{TateConilpCoAlg}_{\mathrm{Lie}}^{\mathrm{cf}},
    W\bigr)\simeq
    N_\Delta\bigl(\mathrm{TateAssocAlg}_{\mathrm{Lie}}^{+,\mathrm{cf}},
    W\bigr)$$
  in the framework of Lurie \emph{Higher Algebra} \S 5.5
  (locally constant factorization algebras over $\R$, applied
  pointwise on the line; or directly the formal-disk version).
\end{cor}

\begin{proof}
  Apply \ref{thm:tate-bar-cobar-quillen} to the
  Lie-operadic Koszul-dual pair $(\mathrm{Lie},\mathrm{CoComm})$
  in $\Cat{TateVec}$. Loday-Vallette \cite{loday-vallette}*{Th.~13.4.6}
  identifies the operadic bar-cobar with the Lie-bar-cobar of
  CE chains and completed enveloping algebra. The
  symmetric-monoidal extension is direct because the operad
  $\mathrm{Lie}$ is a symmetric-monoidal Hopf operad in
  $\Cat{Vec}$, and base change to $\Cat{TateVec}$ via the strong
  symmetric-monoidal functor $\Cat{Vec}\to\Cat{TateVec}$
  preserves operadic Koszul duality
  (\cite{loday-vallette}*{\S 13.5}).
\end{proof}

\begin{lem}[Closed-side Tate formalism package]
\label{lem:closed-tate-koszul-formalism}
  Let \(\mathfrak h=\varprojlim_M\mathfrak h_{\leq M}\) be a closed
  Hamiltonian Tate Lie algebra whose finite windows are
  cochain-CE/PV-admissible, and kernel-admissible when a \(P_0\) kernel is
  used, in the sense of
  Definition~\ref{defn:closed-window-obstruction-terms}.  Assume:
  \begin{enumerate}[label=(K\arabic*)]
    \item the shifted cotangent extension
      \(\mathfrak g=\mathfrak h\ltimes D_{\mathrm{cont}}[1]\) is an
      object of \(\Cat{TateChain}_{\geq0}^{\mathrm{adm}}\);
    \item the CE coalgebra \(C_*^{\mathrm{CE}}(\mathfrak g)\) is
      conilpotent for the coaugmentation filtration;
    \item the completed enveloping algebra
      \(\widehat U(\mathfrak g)=\varprojlim_M\widehat U(\mathfrak g_{\leq M})\)
      is complete and separated for the PBW filtration;
    \item the finite-window PBW associated graded maps assemble to
      \[
        \mathrm{gr}_{\mathrm{PBW}}\widehat U(\mathfrak g)
          \cong
        \widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak g).
      \]
  \end{enumerate}
  Then the closed-side formalism has two compatible outputs:
  \[
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)
      \xrightarrow{\ \Phi\ }
    \mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(\mathfrak h)\bigr)
  \]
  is the admissible completed CE/PV identity obtained from the
  finite-window family of Lemma~\ref{lem:closed-ce-pv-window-limit}
  together with the exact continuous-dualization and variance data in
  (K1)--(K4), and
  \[
    L\Omega C_*^{\mathrm{CE}}(\mathfrak g)
      \simeq \widehat U(\mathfrak g),\qquad
    R\,\mathrm{Bar}\,\widehat U(\mathfrak g)
      \simeq C_*^{\mathrm{CE}}(\mathfrak g)
  \]
  is the Tate Lie bar-cobar / CE Koszul duality of
  Corollary~\ref{cor:tate-lie-bar-cobar}.  The two outputs are
  compatible with the same finite-window transition maps.
\end{lem}

\begin{proof}
  The first output is Lemma~\ref{lem:closed-ce-pv-window-limit} plus the
  exact continuous-dualization and variance hypotheses included above.
  The obstruction terms \(\mathfrak o^{\mathrm{br}}\) and
  \(\mathfrak o^{\mathrm{coad}}\) are the cochain CE/PV transition
  obstructions; \(\mathfrak o^{\mathrm{Cas}}\) is the additional
  kernel/\(P_0\)-pairing obstruction.  Their vanishing does not by itself
  make \(\Phi=\varprojlim_M\Phi_M\) a cochain inverse limit; the
  admissible envelope supplies that extra datum.

  For the Koszul output, hypotheses (K1)--(K4) put
  \(C_*^{\mathrm{CE}}(\mathfrak g)\) and
  \(\widehat U(\mathfrak g)\) in the admissible model envelope with
  complete filtrations.  Conilpotency is the coalgebra hypothesis
  needed for \(\mathrm{Bar}\,\Omega\), and PBW completeness identifies
  the associated graded of the enveloping algebra with the completed
  symmetric algebra.  Corollary~\ref{cor:tate-lie-bar-cobar} therefore
  applies.  Both constructions are obtained by first applying the
  finite-dimensional CE/PV and bar-cobar statements on
  \(\mathfrak g_{\leq M}\), then passing through the same
  Mittag-Leffler inverse limit; hence the transition maps are the same.
\end{proof}

\subsubsection{Application to the local component theorems}

\begin{thm}[Admissible-envelope module reconstruction from the CE/PV identity]
\label{thm:admissible-envelope-module-reconstruction}
  Let $\mathfrak h_{\mathrm{adm}}$ be a pro-finite-dimensional Lie algebra in
  $\Cat{TateVec}$ whose shifted-cotangent extension
  $\mathfrak g_{\mathrm{adm}}
  =\mathfrak h_{\mathrm{adm}}\ltimes
  \mathfrak h_{\mathrm{adm},\mathrm{cont}}^\vee[1]$
  satisfies the lower-central Tate-pronilpotent admissible-envelope hypotheses of
  \ref{thm:tate-bar-cobar-quillen}.  Assume further that:
  \begin{enumerate}[label=(M\arabic*)]
    \item the strict cochain map
  $$\Phi\colon C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{adm}})
    \longrightarrow \mathrm{PV}\bigl(
    \widehat S_{\mathrm{Tate}}(\mathfrak h_{\mathrm{adm}})\bigr)$$
      is the admissible CE/PV quasi-isomorphism obtained from the
      finite-window family of Lemma~\ref{lem:closed-ce-pv-window-limit}
      after the required variance and exact continuous-dualization data
      are supplied;
    \item the completed dg \(P_0\)-algebras on both sides lie in an
      admissible transferred \(P_0\)-algebra model structure inside
      \(\Cat{TateChain}_{\geq0}^{\mathrm{adm}}\), with weak
      equivalences detected on underlying admissible filtered
      quasi-isomorphisms;
    \item the module categories are formed in the same locally
      presentable monoidal envelope, and the two algebras are replaced by
      cofibrant-fibrant representatives when needed.
  \end{enumerate}
  Then \(\Phi\) induces an equivalence, inside that admissible Tate
  model envelope, of module $\infty$-categories over the two identified
  completed dg \(P_0\)-algebras
  $$\widetilde\Phi\colon
    N_\Delta\bigl(C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{adm}})
      \text{-mod},W\bigr)
    \xrightarrow{\sim}
    N_\Delta\bigl(\mathrm{PV}\bigl(\widehat S_{\mathrm{Tate}}(\mathfrak h_{\mathrm{adm}})
      \bigr)\text{-mod},W\bigr)$$
	  in the framework of Lurie's \emph{Higher Algebra} \S 5.5.  This is
	  a reconstruction criterion from a strict CE/PV weak equivalence in an
	  already fixed admissible \(P_0\)-algebra envelope.  It is not a
	  construction of a completed dg \(P_0\) model structure and not a
	  factorization-centre theorem for the full untruncated formal
	  Hamiltonian algebra. The equivalence itself is the
	  admissible-envelope algebraic one.
\end{thm}

\begin{proof}
  Assumption (M1) gives a strict admissible filtered quasi-isomorphism of
  completed dg \(P_0\)-algebras.  The strictness is the generator-level
  identity \(c\mapsto\theta,\ u\mapsto O\), together with
  \(d_\pi\Phi=\Phi d_{\mathrm{CE}}\) and bracket compatibility from the
  finite-window CE/PV calculation.

  By (M2), this strict weak equivalence is a weak equivalence in the
  transferred \(P_0\)-algebra model structure.  Replace the two
  \(P_0\)-algebras by cofibrant-fibrant representatives if necessary.
  Extension and restriction of scalars along a weak equivalence of
  admissible algebra objects give a Quillen equivalence of module model
  categories; this is the standard Schwede--Shipley/Lurie mechanism
  for module categories over weakly equivalent algebra objects
  \cite{schwede-shipley-monoid} and
  \cite{lurie-ha}*{Th.~7.1.4.6}.  Applying
  Dwyer--Kan localization gives the displayed equivalence of module
  \(\infty\)-categories.

  Functoriality in the Lie algebra gives interval-wise compatibility for
  admissible interval objects
  \(\mathfrak h_{\mathrm{adm},I}=
  \Omega^\bullet_c(I)\otimes\mathfrak h_{\mathrm{adm}}\) when these
  interval objects remain in the same admissible envelope.  This is
  interval-wise categorical compatibility, not an independent Weiss
  descent theorem and not an unreduced open-BV centrality theorem.
\end{proof}

\begin{rmk}[Relation to Lurie's higher-algebraic Koszul
  duality]
  \label{rmk:lurie-koszul}
  Lurie \cite{lurie-ha}*{\S 5.5.5} constructs a higher-algebraic
  Koszul duality between augmented $\infty$-operad-algebras and
  their Koszul-dual coalgebras. For the operad
  $\mathrm{Lie}_{\Cat{TateVec}}$, Koszul self-duality (with
  shift) gives the equivalence of \ref{cor:tate-lie-bar-cobar}
  in the lower-central Tate-pronilpotent setting used here. The advantage of the model-
  categorical proof is concrete: weak equivalences are spelled
  out in terms of admissible filtered qiso of \alpharef, not
  abstractly via the Hammock localization. The two constructions
  agree by Lurie A.3.7 plus the Hinich transfer of
  \ref{lem:transferred-model}.
\end{rmk}

\subsubsection{Compatibility with the descendant residual}

The Tate Quillen equivalence of \ref{thm:tate-bar-cobar-quillen}
operates on the bar-cobar duality between $\widehat U(\mathfrak g)$
and $C_*^{\mathrm{CE}}(\mathfrak g)$. It does not directly use
the Casimir element
$C_{\mathfrak h}=\sum_d e_{d,i}\otimes e_d^{i,\vee}$
of \alpharef\ or its convergence in the Tate completion.

\begin{prop}[Bar-cobar conilpotence separated from Casimir convergence]
  \label{prop:quillen-vs-casimir}
  The Quillen equivalence of \ref{thm:tate-bar-cobar-quillen}
  and the resulting $\infty$-categorical equivalence of
  \ref{thm:admissible-envelope-module-reconstruction}, when their
  admissible-envelope hypotheses hold, are independent
  of the convergence of the Tate Casimir element. The cochain
  complexes $C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)$
  and $\mathrm{PV}\bigl(\widehat S_{\mathrm{Tate}}(\mathfrak h)
  \bigr)$ are equivalent in the model category of
  \ref{lem:transferred-model} only after the same conilpotent
  admissibility hypotheses are imposed. Casimir convergence is not one
  of those hypotheses; conilpotence is.
\end{prop}

\begin{proof}
  The bar-cobar comparison uses
  $\widehat S^c(\mathfrak g[1])$ and $T(\mathfrak g)$ as
  underlying graded objects. Both are well-defined and conilpotent
  in the admissible envelope under \alpharef\ items~1, 2 (continuous
  dual exact, conilpotent CE coalgebra). The formal Casimir
  \(\sum_d e_{d,i}\otimes e_d^{i,\vee}\) is a kernel hypothesis only when
  it converges in the chosen coefficient category; in the strict
  product/direct-sum Tate endpoint it is precisely the obstruction
  isolated in Lemma~\ref{lem:tate-casimir-obstruction}.  Such a kernel is
  required for the Costello \cite{costello-renormalization} heat-kernel
  propagator construction at the analytic /
  factorization-algebra-with-non-strict-bracket level. It is \emph{not}
  required for the algebraic bar-cobar comparison.

  Therefore the cochain-level $\Phi$ promotes, in the admissible
  model envelope and only there, to an $\infty$-categorical equivalence. What
  remains outside this algebraic promotion is
  the Weiss-cosheaf upgrade and the heat-kernel quantum lift,
  flagged in \ref{prop:weiss-cosheaf-residual} below.
\end{proof}

\begin{prop}[No universal strict product/direct-sum kernel habitat]
\label{prop:no-universal-strict-kernel-habitat}
  Let \(\mathcal C_{\mathrm{ker}}\) be the category whose objects are
  complete coefficient pairs \((H,D)\), equipped with finite quotients
  \((H_{\leq M},D_{\leq M})\), compatible transition maps, and a tensor
  \(K\in H\widehat\otimes D\) whose image in
  \(H_{\leq M}\otimes D_{\leq M}\) is the finite Casimir \(C_M\) for
  every \(M\).  Morphisms preserve the finite quotients and carry \(K\)
  to \(K'\).  The original strict product/direct-sum pair
  \[
    H_\Pi=\prod_{d\geq1}H_d,\qquad
    D_\oplus=\bigoplus_{d\geq1}H_d^\vee
  \]
  is not an object of \(\mathcal C_{\mathrm{ker}}\).  More strongly, no
  object of \(\mathcal C_{\mathrm{ker}}\) can map to the strict pair by a
  morphism inducing the identity on every finite window.

  Hence the strict product/direct-sum pair has no initial, terminal, or
  representing universal property for kernel-admissible completions.  A
  weighted product completion is a constructed regulator habitat, not a
  universal endpoint for tail-sensitive ordinary cohomology classes.
\end{prop}

\begin{proof}
  If the strict pair were an object, it would contain a tensor
  \(K\in H_\Pi\widehat\otimes D_\oplus\) whose image in every finite
  window is \(C_M\).  If a kernel-admissible object mapped to the strict
  pair by a finite-window identity morphism, the image of its kernel
  would give the same forbidden tensor.  But \(D_\oplus\) has finite
  support in the degree direction, while the compatible family
  \((C_M)_M\) has a nonzero \(H_d^\vee\)-component for every \(d\).
  This is exactly the support obstruction of
  Theorem~\ref{thm:strict-unweighted-no-go}.  Therefore the strict pair
  is outside \(\mathcal C_{\mathrm{ker}}\), and no universal property
  through it is available.
\end{proof}

\begin{prop}[Residual Weiss-cosheaf condition]
  \label{prop:weiss-cosheaf-residual}
  The $\infty$-categorical equivalence of
  \ref{thm:admissible-envelope-module-reconstruction} on stalks and on
  the locally-constant interval-factorization $\mathcal F_{\mathrm{cl}}$
  of \ref{thm:hamiltonian-current-factorization} does not,
  by itself, give the Weiss-cosheaf condition for the
  \emph{unreduced} factorization algebra
  $\mathrm{Obs}^{\mathrm{cl}}_{\mathrm{closed},H}$ on $\R^2\times\C^2$.
  The Weiss / descent condition for an unreduced factorization
  algebra on a higher-dimensional manifold requires checking
  \v{C}ech descent for Weiss covers, which is a separate
  cosheaf-theoretic statement.  Costello-Gwilliam Vol.~I
  \S\S 6.1, 6.5, 7.2 provide the published factorization,
  cosheaf, and basis-extension vocabulary; no theorem from those
  sections is used here to close the unreduced descent obligation.  The
  admissible Tate Quillen-equivalence promotion closes the cochain-level
  $\infty$-categorical promotion; the Weiss upgrade is recorded as the standing residual on the
  unreduced-factorization side of the local theorem.
\end{prop}

\begin{proof}
  Lurie \cite{lurie-ha}*{\S 5.5.4}, with the same terminology as
  Costello-Gwilliam \cite{costello-gwilliam}*{Vol.~I \S 6.4}: a locally constant factorization
  algebra on $\R$ determines an $E_1$-algebra up to the standard
  contractible choice; the
  Quillen equivalence of \ref{thm:tate-bar-cobar-quillen}
  realizes this. On a higher-dimensional manifold, the Weiss
  cover $\{U_\alpha\}$ has structure-map descent independent of
  the algebraic bar-cobar; in particular the heat-kernel
  propagator on $\R^2\times\C^2$ enters the analytic check.
  Without that propagator the bar-cobar identity is consistent
  but does not trivialize Weiss descent.
\end{proof}

\subsubsection{Summary diagram}

\begin{equation*}
  \begin{array}{@{}c@{\;}c@{\;}c@{}}
    \begin{gathered}
      \alpharef\\
      \text{(filtered qiso of cochain complexes)}
    \end{gathered}
    &
    \xrightarrow{\text{admissible Tate promotion}} &
    \begin{gathered}
      \text{Quillen equivalence}\\
      \text{of model cats}
    \end{gathered} \\
    \downarrow & & \downarrow \\
    \text{cochain identity }\Phi\,d_{\mathrm{CE}}=d_\pi\,\Phi &
    \xrightarrow{\text{Lurie A.3.7}} &
    \text{equivalence of }\infty\text{-cats}\\
    & & \downarrow\text{Lurie 5.5} \\
    & &
    \text{equivalence in admissible }\infty\text{-cats of}\\
    & & \text{completed dg }P_0\text{-algebras}
  \end{array}
\end{equation*}

The chain on the left is $\Phi$ as a strict cochain map.
The chain on the right is the admissible Tate promotion: model-categorical,
then $\infty$-categorical, then $P_0$-algebra-categorical.
The promotion does not depend on the Tate Casimir convergence
(\ref{prop:quillen-vs-casimir}); the Weiss-cosheaf descent on the
unreduced factorization algebra is a separate residual
(\ref{prop:weiss-cosheaf-residual}).
