% Endpoint coefficient criterion for Costello--Li BV-cohomology input.
% The fragment separates the published Costello--Li hypotheses from the
% mixed R^2 x C^2 brane-defect coefficient problem and records the exact
% obstruction tuple for an endpoint-admissible module.
%
% Records: (i) the precise Costello--Li hypotheses; (ii) the local
% hypothesis-separation against the R^2 x C^2 brane R x p, gl_N gauge
% setup studied here; (iii) the coefficient endpoint criterion; (iv) the
% obstruction tuple whose vanishing is necessary and sufficient for the
% endpoint construction.

\section*{BV-cohomology vanishing and the unreduced cotangent lift}

\subsection*{Costello--Li 2012 hypotheses, restated}

\begin{stmt}[Costello--Li 2012 BCOV package,
   restated]\label{stmt:costello-li-2012-restated}
  Let $X$ be a compact Calabi--Yau manifold of complex dimension $d$,
  with holomorphic volume form $\Omega$. Let $\mathrm{PV}(X)[[t]]$ be
  the polyvector field complex with the Tate parameter $t$ (the
  worldsheet $S^1$ rotation), with differential
  $Q=\bar\partial+t\,\partial_\Omega$ and $(-1)$-shifted symplectic
  pairing
  $$\langle \alpha,\beta\rangle
    =\int_X (\alpha\wedge\beta)\big|_{\mathrm{PV}^{d,d}}\cdot\Omega^2.$$
  The classical BCOV interaction $I_{\mathrm{BCOV}}$ is the cubic
  vertex on $\mathrm{PV}(X)[[t]]$ supplied by
  \cite{costello-li-quantum-bcov}.  The source package supplies the
  generalized classical BCOV complex, its local-functional obstruction
  complex, and the renormalization framework in which quantization
  obstructions are stated.  The quantization vanishing theorems used as
  primary-source precedent here are only those with their own stated
  hypotheses.  No general all-dimensional compact-Calabi--Yau theorem
  is imported saying that every
  higher-loop obstruction vanishes in the mixed brane-defect sector.
\end{stmt}

The 2015 sequel \cite{costello-li-open-closed-bcov} extends to
open-closed BCOV with open gauge data $\lie{gl}(N\mid N)$, anomaly
cancellation by the supertrace, on flat $\mathbb C^d$, $d$ odd. That
is the precedent for defects in the Costello--Li line, but on
$\mathbb C^d$, not on $\R^2\times\C^2$ with topological factor.

\subsection*{Applicability check on \texorpdfstring{$\R^2\times\C^2$}{R2 x C2}
   with brane \texorpdfstring{$L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}$}{L} and \texorpdfstring{$\lie{gl}_N$}{gl\_N}}

\begin{prop}[Costello--Li 2012 hypothesis separation for the local
   model]\label{prop:costello-li-2012-hypothesis-separation}
  The hypotheses of \ref{stmt:costello-li-2012-restated} differ from
  the formal local model on $\R^2\times\C^2$ with brane
  \(L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}\)
  and gauge data $\lie{gl}_N$ along five independent axes.

  \begin{enumerate}
    \item[(S1)] \emph{Compact-Hodge input.} The 2012 compact
      Hodge-theoretic input does not apply directly to the formal
      \(\C^2\) jet model.  The 2015 theorem shows that flat
      non-compact geometry can be admissible under its own odd-dimensional
      \(\mathfrak{gl}(N\mid N)\) hypotheses; those are not the mixed
      topological-holomorphic defect hypotheses used here.
    \item[(S2)] \emph{Topological--holomorphic mixing.} The local
      theory has a topological factor $\R^2$ (de~Rham) crossed with
      a holomorphic factor $\C^2$ (Dolbeault). Costello--Li 2012 is
      pure BCOV/HCS on a single holomorphic Calabi--Yau; there is no
      pure BCOV statement covering the mixed kinematics. The
      protected sector of twisted M-theory \cite{costello-twistedM}
      has the right shape as motivation, but no theorem from that source
      is used here without a separate local anchor, and Costello--Li 2012
      is not stated for it.
    \item[(S3)] \emph{Brane defect.} The brane \(L\) is
      one-real-dimensional in the topological direction and
      point-supported in the holomorphic direction. Costello--Li
      2012 has no brane sector. Costello--Li 2015
      \cite{costello-li-open-closed-bcov} has a brane sector but on
      flat $\C^d$ (not $\R^2\times\C^2$) with $\lie{gl}(N\mid N)$
      open gauge data.
    \item[(S4)] \emph{Gauge data.} Ordinary $\lie{gl}_N$ is not
      $\lie{gl}(N\mid N)$. Costello--Li 2015 cancel the U(1) center
      anomaly by the supertrace; this cancellation is unavailable for
      ordinary $\lie{gl}_N$. The U(1) center class $[\bar c]$ in
      part~(f) of \ref{thm:main-local} is the local trace-line avatar of
      that Costello--Li anomaly, not a graph-level identification with it.
    \item[(S5)] \emph{Tate direction.} Costello--Li's $t$-Tate
      completion is along the worldsheet $S^1$ rotation, not along
      the coefficient system. The Tate completion required by
      \ref{prob:formal-factorization-center} is along the
      \emph{coefficient} direction
      $\widehat{\mathfrak h}\,\widehat\otimes\,
      \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}$ in which the
      Casimir
      $C_{\mathfrak h}=\sum_{d\geq 1}\sum_i e_{d,i}\otimes e^i_d$
      must converge. By \ref{lem:tate-casimir-obstruction}, the
      direct-sum dual fixed in the parent calculation obstructs
      convergence, and the coefficient category itself must change.
      Costello--Li provide no convergence theorem in this direction.
  \end{enumerate}

  Hypothesis (S5) is the coefficient endpoint obstruction: even if
  (S1)--(S4) were supplied by an Omega-background or twisted M-theory
  extension, the coefficient-system Tate completion would still be
  unprovided.
\end{prop}

\begin{proof}
  Each clause is a direct comparison of the hypotheses of
  \ref{stmt:costello-li-2012-restated} (and its 2015 sequel) with
  the data of \ref{thm:main-local} and the topology declared in
  the linear-heat / coefficient-Casimir analysis
  (\ref{rmk:linear-heat-versus-bv-kernel},
  \ref{lem:tate-casimir-obstruction}). The non-compactness of
  $\C^2$ blocks the harmonic-projection step in Costello--Li's
  one-loop anomaly cancellation; the topological factor $\R^2$ is
  not BCOV kinematics; the brane \(L\) is a topological
  line transverse to a holomorphic point, not an open boundary on a
  flat $\C^d$; ordinary $\lie{gl}_N$ lacks the Costello--Li
  supertrace cancellation (whose local trace-line avatar here is the
  class $[\bar c]$ of part~(f)); and the worldsheet-$t$ Tate completion
  is orthogonal to the coefficient-Casimir Tate direction.
\end{proof}

\begin{cor}[Costello--Li input and the unreduced coefficient endpoint]
\label{cor:costello-li-input-coefficient-endpoint}
  The Costello--Li 2012 BCOV package supplies a pure closed BCOV
  template.  The unreduced Tate-coefficient cotangent lift
  for the present brane-defect model additionally requires the endpoint
  coefficient data of
  Definition~\ref{defn:endpoint-admissible-coefficient-module}.  The
  independent chain-level route
  \ref{thm:chain-level-primitive-projection} closes the classical
  primitive indecomposable shadow without analytic input.  The
  unreduced cotangent factorization-centre morphism and the
  quantum one-antifield extension of part~(e) require the
  weighted coefficient category and the mixed brane-defect
  locality/QME input isolated in
  Problem~\ref{prob:weighted-rg-locality} and
  \ref{thm:hadamard-mittag-leffler}.
\end{cor}

\begin{proof}
  By Proposition~\ref{prop:costello-li-2012-hypothesis-separation}, the
  BCOV package of \cite{costello-li-quantum-bcov} is stated
  for different geometric and coefficient data.  Its conclusion, in the
  form used here as source precedent, contains
  neither the coefficient-system Tate completion in which the Casimir
  converges nor a brane-defect extension of the propagator.  The closures
  cited in the statement supply the classical chain-level lift and the
  weighted finite-scale coefficient kernel by other routes.  The endpoint
  data remain exactly those listed in
  Definition~\ref{defn:endpoint-admissible-coefficient-module}.
\end{proof}

\begin{thm}[Costello--Li endpoint coefficient criterion]
\label{thm:costello-li-no-coefficient-endpoint}
  The Costello--Li 2012 BCOV package
  \cite{costello-li-quantum-bcov} and its 2015 open-closed extension
  \cite{costello-li-open-closed-bcov}, in the forms cited above, can
  yield an endpoint-admissible coefficient module for
  Definition~\ref{defn:endpoint-admissible-coefficient-module} only after
  three independent data are added:
  \[
  \begin{gathered}
    \text{(E2) coefficient Casimir kernel},\\
    \text{(E3) mixed brane-defect transport},\\
    \text{(E5) endpoint RG preservation}.
  \end{gathered}
  \]
  Here (E1) and (E4) are the inherited finite-window and Mittag--Leffler
  envelope conditions of
  Definition~\ref{defn:endpoint-admissible-coefficient-module}.  A
  quantum endpoint additionally requires vanishing of the separate QME
  component \(\mathfrak o_{\mathrm{QME}}\) in
  Definition~\ref{defn:bv-endpoint-obstruction-tuple}.
\end{thm}

\begin{proof}
  An endpoint-admissible coefficient module requires a coefficient
  kernel
  \(C_\ast\in\mathfrak h_\ast\widehat\otimes D_\ast\) whose projection
  to every finite Hamiltonian window is the finite Casimir, together
  with mixed brane-defect transport of the bracket, propagator,
  interaction, counterterms, and RG recursion.  By
  Proposition~\ref{prop:costello-li-2012-hypothesis-separation}, the cited
  Costello--Li theorems are pure closed BCOV statements on the
  polyvector \(t\)-Tate direction, with a separate
  \(\mathfrak{gl}(N\mid N)\) open-closed setting in the sequel.  Their
  stated data are orthogonal to the coefficient pair
  \(\widehat{\mathfrak h}\widehat\otimes
  \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}\), its Casimir kernel,
  and the topological line defect with ordinary \(\mathfrak{gl}_N\)
  boundary observables.  Thus the endpoint conditions (E2), (E3), and
  (E5) of
  Definition~\ref{defn:endpoint-admissible-coefficient-module} are not
  consequences of the cited theorems.
\end{proof}

\begin{defn}[BV endpoint obstruction tuple]
\label{defn:bv-endpoint-obstruction-tuple}
  For the mixed local geometry
  \(\R^2\times\C^2\) with brane
  \(L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}\), the obstruction
  tuple for a BV-cohomology vanishing theorem to construct an
  endpoint-admissible coefficient module is
  \[
    \mathfrak o_{\mathrm{BV,end}}
      =\bigl(
        \mathfrak o_{\mathrm{Cas}},
        \mathfrak o_{\mathrm{def}},
        \mathfrak o_{\mathrm{RG}},
        \mathfrak o_{\mathrm{QME}}
       \bigr).
  \]
  Its components are:
  \begin{enumerate}[label=(O\arabic*)]
    \item \(\mathfrak o_{\mathrm{Cas}}\): the class of the compatible
      finite Casimirs
      \((C^M_{\mathfrak h})_{M\geq1}\) in the quotient by actual
      coefficient kernels
      \(\mathfrak h_\ast\widehat\otimes D_\ast\);
    \item \(\mathfrak o_{\mathrm{def}}\): the obstruction to extending
      the bulk propagator and bracket transport to the topological line
      defect with ordinary \(\lie{gl}_N\) open observables;
    \item \(\mathfrak o_{\mathrm{RG}}\): the obstruction to preserving
      the same strict finite-window Mittag-Leffler tower under
      Costello's recursion \(W(P_{\epsilon,L},I)\);
    \item \(\mathfrak o_{\mathrm{QME}}\): the mixed brane-defect local
      functional class in
      \[
        H^1\bigl(\mathcal O_{\mathrm{loc}}(\mathcal E_\ast),
          Q+\{I_\ast,-\}\bigr)
      \]
      produced by the quantum master equation at the endpoint.
  \end{enumerate}
\end{defn}

\begin{prop}[Endpoint construction is equivalent to vanishing of the tuple]
\label{prop:bv-endpoint-obstruction-tuple}
  A Costello--Li type BV-cohomology theorem closes the coefficient
  endpoint for this local brane-defect problem only if all four
  components of
  \(\mathfrak o_{\mathrm{BV,end}}\) vanish and a compatible choice of
  primitives is made.  Under such a choice, the endpoint satisfies
  Definition~\ref{defn:endpoint-admissible-coefficient-module}; conversely
  an endpoint-admissible coefficient module kills
  \(\mathfrak o_{\mathrm{Cas}}\), \(\mathfrak o_{\mathrm{def}}\), and
  \(\mathfrak o_{\mathrm{RG}}\), and the QME solution kills
  \(\mathfrak o_{\mathrm{QME}}\).
\end{prop}

\begin{proof}
  Definition~\ref{defn:endpoint-admissible-coefficient-module}(E2) is
  precisely the existence of an actual coefficient kernel whose
  finite-window projections are the \(C^M_{\mathfrak h}\); this is the
  vanishing of \(\mathfrak o_{\mathrm{Cas}}\).  Condition (E3) requires
  transport of bracket, propagator contraction, interaction, and
  counterterm representatives through the brane-defect geometry; this
  is exactly \(\mathfrak o_{\mathrm{def}}=0\) together with the chosen
  transport primitives.  Condition (E5) is
  \(\mathfrak o_{\mathrm{RG}}=0\).  The endpoint QME is the vanishing of
  the displayed degree-one local-functional class
  \(\mathfrak o_{\mathrm{QME}}\).  These conditions are also necessary:
  a nonzero component removes one of the endpoint data just listed.
\end{proof}

\subsection*{Costello--Li extension criterion}

\begin{thm}[Costello--Li extension criterion for the mixed coefficient endpoint]\label{thm:t4-four-missing}
  Any Costello--Li type theorem that proves an endpoint-admissible
  coefficient module for the setup here must supply the following four
  components simultaneously:
  \begin{enumerate}
    \item \emph{Non-compact / Omega-background BV-cohomology
      vanishing.} A version of \ref{stmt:costello-li-2012-restated}
      on $\R^2\times\C^2$, either via a separately anchored
      Omega-background route or via a compactification with Lagrangian
      boundary at infinity.
    \item \emph{Topological--holomorphic mixed kinematics.} The
      vanishing must hold on the kinematic differential
      $D=d_{\R^2}+\bar\partial_{\C^2}$, with the linearized
      complex of \ref{rmk:linear-heat-versus-bv-kernel}, and on
      the Hamiltonian sector with cotangent $[1]$ extension.
    \item \emph{Brane-defect extension.} The vanishing must allow
      the transverse one-real-dimensional defect \(L\) on
      which open gauge data $\lie{gl}_N$ live; not the flat-$\C^d$
      $\lie{gl}(N\mid N)$ setup of
      \cite{costello-li-open-closed-bcov}. It must also decide the
      scalar contact class of
      Theorem~\ref{thm:app-scalar-contact-qme-class}: closed
      exchange cancellation, supertrace removal, central-character
      normalization, or renormalized boundary generators.
    \item \emph{Coefficient-system Tate completion.} The
      coefficient direction
      $\widehat{\mathfrak h}\,\widehat\otimes\,
      \widehat{\mathfrak h}^{\vee}_{\mathrm{cont}}$ must support the
      Casimir as a convergent kernel. By
      \ref{lem:tate-casimir-obstruction} this is a category-level
      change, not a damping factor.
  \end{enumerate}
  These four inputs are the coefficient package of
  \ref{prob:formal-factorization-center}.  They are the necessary data
  for turning the Costello--Li convention template into the mixed
  brane-defect coefficient theorem used here.
\end{thm}

\begin{proof}
  Component (1) supplies the compactness/Hodge-theoretic replacement
  needed in (S1).  Component (2) supplies the mixed
  topological--holomorphic complex required by (S2).  Component (3)
  supplies the line-defect transport and ordinary \(\lie{gl}_N\) scalar
  anomaly decision required by (S3)--(S4).  Component (4) is precisely
  condition (E2) of
  Definition~\ref{defn:endpoint-admissible-coefficient-module}; together
  with the transport and RG requirements in (E3) and (E5), it is the
  coefficient endpoint datum.  Proposition~\ref{prop:bv-endpoint-obstruction-tuple}
  identifies these requirements with vanishing of the obstruction tuple.
\end{proof}

\begin{rmk}[External comparison boundary]\label{rmk:t4-external-comparison-boundary}
  The local Hamiltonian BF sector here supplies the formal-disk
  coefficient normalization.  Compact Calabi--Yau outputs of a
  \(\Phi_d\) functor, \(\kappa_{\mathrm{ch}}\) or
  \(\kappa_{\mathrm{BKM}}\) consequences, compact
  \(\mathrm{CY}_3\) BCOV anomaly cancellation, the Vol~III
  CY-to-chiral frontier, and the Igusa \(\Delta_5\) /
  Borcherds--BKM frontier require their own comparison data.
  Costello--Li 2012 supplies the convention template used to state the
  coefficient problem for the unreduced cotangent lift.
\end{rmk}
