% Weighted Tate completion of the coefficient pair
% (\widehat{\mathfrak h}, \widehat{\mathfrak h}^\vee_{\mathrm{cont}})
% compatible with the Costello heat-kernel BV calculus on
% \R^2\times\C^2 with brane defect L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}. Addresses
% Lemma~\ref{lem:tate-casimir-obstruction} and
% Problem~\ref{prob:tate-coefficient-descendant-lift} of the parent
% manuscript via a graded Mittag-Leffler completion in the polynomial
% Hamiltonian degree. Status: the cochain identity and finite-scale
% coefficient kernel close in the weighted coefficient category. The
% BV graph realization remains conditional on the Costello-locality /
% QME obstruction class for the mixed brane-defect theory.

\section*{Weighted Tate completion of the coefficient pair}

\paragraph{Status.}
The weighted coefficient category proves the Casimir, finite-window
Mittag-Leffler, heat-kernel, and classical cochain statements below.
Renormalization-flow compatibility is asserted graph by graph at finite
scale for polynomial-degree-bounded vertices.  Any quantum descendant
comparison is conditional on the weighted Costello-locality/QME
obstruction in Problem~\ref{prob:weighted-rg-locality}.  No
regulator-independence theorem is asserted for the original unweighted
product/direct-sum Tate pair.  The only regulator-independence theorem
proved below is independence of the chosen admissible weight inside the
finite-window Mittag-Leffler sector; it is not an equivalence with the
strict product/direct-sum theory.

\subsection*{Diagnosis}

\begin{rmk}[Why the unweighted Tate Casimir fails]\label{rmk:diagnosis-unweighted-casimir}
  In the parent manuscript the Hamiltonian Lie algebra is the
  product/direct-sum Tate pair
  \begin{equation}\label{eq:wt-strict-tate-pair}
    \mathfrak h=\prod_{d\geq1}H_d,\qquad
    \mathfrak h^\vee_{\mathrm{cont}}=\bigoplus_{d\geq1}H_d^\vee,
  \end{equation}
  with $H_d=\mathrm{Span}\{z_1^az_2^b:a+b=d\}$ and Hamiltonian bracket
  satisfying $\{H_p,H_q\}\subset H_{p+q-2}$. By
  Lemma~\ref{lem:continuous-bar-cobar} item~(1), the continuous dual of
  a Tate product is a strict direct sum, and \emph{vice versa}. The
  formal Casimir
  \begin{equation}\label{eq:wt-casimir-formal}
    C_{\mathfrak h}=\sum_{d\geq1}\sum_i e_{d,i}\otimes e^i_d
  \end{equation}
  has a nonzero summand in every degree~$d$, so its second tensor
  factor lies in $\prod_d H_d^\vee$, not in
  $\bigoplus_d H_d^\vee=\mathfrak h^\vee_{\mathrm{cont}}$. Thus
  $C_{\mathfrak h}\notin\mathfrak h\widehat\otimes
  \mathfrak h^\vee_{\mathrm{cont}}$. This is
  Lemma~\ref{lem:tate-casimir-obstruction} of the parent.

  The obstruction is categorical, not analytic: no rescaling of the
  bases $\{e_{d,i}\}$ or $\{e^i_d\}$ \emph{within} the strict pair
  \eqref{eq:wt-strict-tate-pair} can move the Casimir from the product
  $\prod_d(H_d\otimes H_d^\vee)$ to the strict sum-with-product
  $(\prod_d H_d)\widehat\otimes(\bigoplus_d H_d^\vee)$. The cure must
  change the coefficient \emph{category}: the second factor must
  itself be a product, with the change of dualization inserted by an
  intermediate weight system that is itself a Mittag-Leffler
  inverse-limit object.
\end{rmk}

\begin{rmk}[Costello's coefficient requirements]\label{rmk:costello-coefficient-requirements}
  In Costello's heat-kernel BV calculus, the BV propagator
  $P_{\epsilon,L}$ on a free elliptic complex
  $(\mathcal E,Q,\langle\,,\,\rangle)$ is the kernel of the operator
  $\int_\epsilon^L Q^{\mathrm{GF}}e^{-tD}dt$ in
  $\mathcal E\widehat\otimes\mathcal E$ \cite{costello-renormalization}*{Ch.~5}.
  When the field complex factors as
  \begin{equation}\label{eq:wt-field-factor}
    \mathcal E=\Omega^\bullet(\R^2)\widehat\otimes
      \Omega^{0,\bullet}(\C^2)\widehat\otimes
      \bigl(\widehat{\mathfrak h}[1]
      \oplus\widehat{\mathfrak h}^\vee_{\mathrm{cont}}[2]\bigr),
  \end{equation}
  with the Tate coefficient pair acting passively on the spacetime,
  the propagator factors as
  \begin{equation}\label{eq:wt-propagator-factor}
    P_{\epsilon,L}=P_{\epsilon,L}^{\mathrm{base}}\widehat\otimes
      C_{\mathfrak h\oplus\mathfrak h^\vee[1]},
  \end{equation}
  where the spacetime piece $P_{\epsilon,L}^{\mathrm{base}}$ on
  $\Omega^\bullet(\R^2)\widehat\otimes\Omega^{0,\bullet}(\C^2)$ is the
  standard heat-kernel BV inverse on the bulk (Costello, op.\ cit., Ch.~5),
  and the coefficient piece is the BV inverse pairing on
  $\widehat{\mathfrak h}\oplus\widehat{\mathfrak h}^\vee_{\mathrm{cont}}[1]$.
  By Remark~\ref{rmk:linear-heat-versus-bv-kernel}, the spacetime piece
  exists as an actual continuous operator. The whole kernel exists as
  an element of $\mathcal E\widehat\otimes\mathcal E$ \emph{iff} the
  coefficient piece, the bare Casimir $C_{\mathfrak h}$ together with
  its dual coevaluation, exists as a coefficient kernel.

  Costello's heat-kernel BV requires three properties of the
  coefficient module:
  \begin{enumerate}[label=(C\arabic*)]
    \item\label{costello:CC1} an actual distributional inverse pairing,
      i.e.\ a coefficient coevaluation
      $C_{\mathfrak h}\in\mathfrak h\widehat\otimes
      \mathfrak h^\vee_{\mathrm{cont}}$ realizing the bilinear form
      with kernel zero in the cohomology of the heat operator;
    \item\label{costello:CC2} regularity in the cutoff parameters
      $\epsilon$ and $L$, in the sense that the heat-kernel
      propagator $P_{\epsilon,L}$ is a continuous family in the
      coefficient topology and converges as
      $L\to\infty$, $\epsilon\to0^+$ to a distributional kernel after
      counterterm subtraction;
    \item\label{costello:CC3} compatibility with the Costello RG flow
      $W(P_{\epsilon,L},I)$: the weight or topology defining the
      coefficient module is preserved by the renormalization flow on
      effective interactions induced by varying $(\epsilon,L)$, in the
      precise sense that the source of the flow lies in the same
      completed coefficient category as its target.
  \end{enumerate}
  The strict Tate pair \eqref{eq:wt-strict-tate-pair} fails
  \ref{costello:CC1}; the subsection below repairs the coefficient
  kernel and the finite-scale propagator by a weighted
  Mittag-Leffler completion.  Requirement~\ref{costello:CC3} is not a
  formal consequence of the coefficient change; it is the residual
  locality/QME problem isolated in
  Problem~\ref{prob:weighted-rg-locality}.
\end{rmk}

\subsection*{Weighted Tate completion: definition}

\begin{defn}[Polynomial Hamiltonian degree weight]\label{defn:wt-degree-weight}
  A \emph{degree weight} is a function $w\colon\Z_{\geq1}\to\R_{>0}$
  satisfying:
  \begin{enumerate}[label=(W\arabic*)]
    \item\label{w:W1} \emph{Bracket-tame:} there exists a constant
      $C_w\geq 0$ such that
      $w(p+q-2)\leq C_w\,w(p)w(q)$ for every $p,q\geq2$;
    \item\label{w:W2} \emph{Windowwise coadjoint-continuity:} for every
      Hamiltonian degree bound $R$ and every output Tate window
      $w_0$, the principal-part coadjoint shifts
      $\rho_{a,b}\mapsto\rho_{a-p+1,b-q+1}$ with $p+q\leq R$ and
      $a+b-p-q+2\leq w_0$ involve only the finite input window
      $a+b\leq w_0+R-2$, and the finitely many corresponding weight
      ratios have a maximum;
    \item\label{w:W3} \emph{Mittag-Leffler coevaluation:} for each
      $w_0$ the finite-window Casimir
      $\sum_{d\leq w_0}\sum_i w(d)e_{d,i}\otimes w(d)^{-1}e^i_d$
      is compatible under the surjective truncation maps
      $w_0'\to w_0$. Equivalently, the coefficient kernel is a strict
      Mittag-Leffler inverse system of finite-dimensional kernels.
  \end{enumerate}
\end{defn}

\begin{lem}[Existence of weights]\label{lem:wt-weights-exist}
  Every exponential weight $w(d)=q^d$ with $q>1$ satisfies
  \ref{w:W1}--\ref{w:W3}.  The proof uses only finite-window maxima
  for the coadjoint action; there is no uniform bound in the
  unbounded principal-part degree.
\end{lem}

\begin{proof}
  For $w(d)=q^d$, \ref{w:W1} reads $q^{p+q-2}\leq C_w q^{p+q}$, i.e.\
  $C_w=q^{-2}$ suffices.  For \ref{w:W2}, fix $R$ and $w_0$.  If
  $p+q\leq R$ and the output degree is
  $a+b-p-q+2\leq w_0$, then $a+b\leq w_0+R-2$.  Hence the set of
  possible triples $(p,q,a+b)$ is finite, and the corresponding
  ratios of powers of $q$ admit a finite maximum.  No bound independent
  of $a+b$ is asserted; the earlier uniform inequality would be false.
  Condition~\ref{w:W3} is the strict Mittag-Leffler compatibility of
  finite-window Casimirs under truncation.  The transition maps are
  surjective, hence the system is Mittag-Leffler.
\end{proof}

\begin{rmk}[Choice of exponential weight]\label{rmk:wt-canonical-weight}
  The exponential weight $w(d)=q^d$ is the working choice, with $q>1$
  formally an element of $\R_{>0}$ and concretely set to $q=2$ for
  the proofs below. The choice is a grading weight on the coefficient
  module, not a symplectic automorphism of the formal disk.  Thus the
  Poisson bracket and the counterterm representatives are compared
  between two weights only after transport by the diagonal map
  \(R_{w,w'}\) below.  In coordinates, the bracket constants in the
  basis \(w(d)e_{d,i}\) are conjugated by the finite ratios
  \(w(p)w(q)/w(p+q-2)\), and condition~\ref{w:W1} is exactly the
  boundedness condition needed for this transported bracket on each
  finite graph.  The weight is therefore a controlled coefficient
  regulator, not an assertion that rescaling the variables
  \(z_1,z_2\) preserves the original Hamiltonian bracket.
\end{rmk}

\begin{defn}[Weighted Tate coefficient pair]\label{defn:wt-coefficient-pair}
  Given a degree weight $w$ as in
  Definition~\ref{defn:wt-degree-weight}, write $H_d^{(w)}$ for the
  rescaled copy of the finite-dimensional degree piece
  $H_d$ with basis $w(d)e_{d,i}$, and
  $(H_d^\vee)^{(w^{-1})}$ for the rescaled dual basis
  $w(d)^{-1}e^i_d$.  Define
  \begin{equation}\label{eq:wt-h-defn}
    \mathfrak h_w=\varprojlim_{w_0\in\Z_{\geq1}}\,
      \prod_{d=1}^{w_0}H_d^{(w)}
  \end{equation}
  with the Tate filtration $F^{w_0}\mathfrak h_w=\ker(\mathfrak h_w\to
  \prod_{d\leq w_0}H_d^{(w)})$, and define the \emph{weighted
  coefficient dual}
  \begin{equation}\label{eq:wt-hvee-defn}
    \mathfrak h^{\vee,w}_{\mathrm{cont}}=
      \varprojlim_{w_0\in\Z_{\geq1}}\,
      \prod_{d=1}^{w_0}(H_d^\vee)^{(w^{-1})}.
  \end{equation}
  The pairing is fixed degreewise by
  $\langle w(d)^{-1}e^i_d,w(d)e_{d,j}\rangle=\delta^i_j$.
  The weighted Tate coefficient pair is
  $(\mathfrak h_w,\mathfrak h^{\vee,w}_{\mathrm{cont}})$.  The second
  factor is a product coefficient module, not the strict continuous
  dual of the first product Tate space.
\end{defn}

\begin{rmk}[Topological content]\label{rmk:wt-topology-content}
  Both $\mathfrak h_w$ and $\mathfrak h^{\vee,w}_{\mathrm{cont}}$ are
  Mittag-Leffler inverse limits of finite-dimensional Tate windows,
  and both are products in the degree direction. The two are no
  longer in strict Tate duality (one product, one direct sum); the
  point is precisely to replace the direct-sum dual by a symmetric
  Mittag-Leffler product coefficient module.  This is an additional
  coefficient category for the BV kernel.  It does not identify
  $\mathfrak h^{\vee,w}_{\mathrm{cont}}$ with the ordinary continuous
  dual of $\mathfrak h_w$.
\end{rmk}

\begin{prop}[Casimir convergence]\label{prop:wt-casimir-convergence}
  In the weighted Tate coefficient pair
  $(\mathfrak h_w,\mathfrak h^{\vee,w}_{\mathrm{cont}})$ of
  Definition~\ref{defn:wt-coefficient-pair}, the formal Casimir
  \begin{equation}\label{eq:wt-casimir-weighted}
    C_{\mathfrak h,w}=\sum_{d\geq1}\sum_i\,
      \bigl(w(d)e_{d,i}\bigr)\otimes
      \bigl(w(d)^{-1}e^i_d\bigr)
  \end{equation}
  converges as an element of
  $\mathfrak h_w\widehat\otimes
  \mathfrak h^{\vee,w}_{\mathrm{cont}}$. The pairing of
  $C_{\mathfrak h,w}$ with any test functional in the dual is the
  identity on the corresponding finite-dimensional Tate window, so
  $C_{\mathfrak h,w}$ is the BV coefficient inverse pairing in the
  weighted category.
\end{prop}

\begin{proof}
  The displayed Casimir, restricted to the Tate window $d\leq w_0$,
  is the finite sum
  $\sum_{d\leq w_0}\sum_i(w(d)e_{d,i})\otimes(w(d)^{-1}e^i_d)$, an
  element of $\prod_{d\leq w_0}w(d)H_d\otimes\prod_{d\leq w_0}
  w(d)^{-1}H_d^\vee$. This is a tensor in a finite-dimensional vector
  space because each window is finite-dimensional. The tower of
  finite-window Casimirs is compatible: enlarging $w_0$ extends the
  sum by the terms in degrees $w_0+1,\ldots,w_0'$. The inverse limit
  in $\mathbf{TateVec}$ exists by Definition~\ref{defn:wt-coefficient-pair}
  and \ref{w:W3} of Definition~\ref{defn:wt-degree-weight}.

  Pairing the Casimir with a test functional $\phi\in
  \mathfrak h^{\vee,w}_{\mathrm{cont}}$, supported in finitely many
  Tate windows, gives a finite sum of identity pairings, so the
  result is the canonical evaluation. Hence $C_{\mathfrak h,w}$
  realizes the inverse pairing on the weighted Tate pair, satisfying
  Costello requirement \ref{costello:CC1}.
\end{proof}

\begin{rmk}[Independence of basis]\label{rmk:wt-basis-independence}
  Definition~\eqref{eq:wt-casimir-weighted} is written in a basis
  $\{e_{d,i}\}$ of $H_d$, but does not depend on the choice. The dual basis
  $\{e^i_d\}$ is fixed by $\langle e_{d,i},e^j_d\rangle=\delta_i^j$.
  An orthogonal change of basis $e_{d,i}\mapsto\sum_j O_i^je_{d,j}$
  with $O\in GL(H_d)$ shifts the dual by the inverse transpose,
  yielding the same Casimir. Thus
  $C_{\mathfrak h,w}=\sum_d\mathrm{id}_{H_d\otimes H_d^\vee}$ is the
  basis-independent identity element of $\bigoplus_d H_d\otimes
  H_d^\vee$ extended to the weighted product.
\end{rmk}

\subsection*{Heat-kernel propagator on the weighted pair}

\begin{prop}[Heat-kernel propagator extension to the weighted pair]\label{prop:wt-propagator-extends}
  Let $w$ be a degree weight as in
  Definition~\ref{defn:wt-degree-weight}. The Costello heat-kernel
  propagator $P_{\epsilon,L}^{\mathrm{op}}$ of
  Remark~\ref{rmk:linear-heat-versus-bv-kernel} extends from the
  strict Tate field complex to the weighted field complex
  \begin{equation}\label{eq:wt-field-complex}
    \mathcal E_w=\Omega^\bullet(\R^2)\widehat\otimes
      \Omega^{0,\bullet}(\C^2)\widehat\otimes
      \bigl(\mathfrak h_w[1]\oplus
      \mathfrak h^{\vee,w}_{\mathrm{cont}}[2]\bigr),
  \end{equation}
  to give a continuous family of BV propagators
  $P_{\epsilon,L}^{w}\in\mathcal E_w\widehat\otimes\mathcal E_w$ for
  $0<\epsilon\leq L<\infty$, satisfying:
  \begin{enumerate}[label=(\arabic*)]
    \item the BV identity
      $[Q,P_{\epsilon,L}^{w}]=K_\epsilon^{w}-K_L^{w}$, where
      $K_t^{w}=K_t^{\mathrm{base}}\widehat\otimes C_{\mathfrak h,w}$
      is the weighted heat kernel of the BV inverse pairing;
    \item Costello regularity \ref{costello:CC2}: the family is
      continuous in $(\epsilon,L)$ in the weighted Tate topology;
    \item the limit $L\to\infty$, $\epsilon\to0^+$ exists as a
      distributional kernel after the standard spacetime counterterm
      subtraction in Costello's heat-kernel RG package
      \cite{costello-renormalization}*{Chs.~5--7}; the coefficient
      direction introduces no additional spacetime singular support.
      Locality and QME counterterm compatibility for the mixed
      brane-defect theory remain the content of
      Problem~\ref{prob:weighted-rg-locality}.
  \end{enumerate}
\end{prop}

\begin{proof}
  By the factorization \eqref{eq:wt-propagator-factor}, the
  propagator splits as a tensor product of the spacetime kernel
  $P_{\epsilon,L}^{\mathrm{base}}$ on
  $\Omega^\bullet(\R^2)\widehat\otimes\Omega^{0,\bullet}(\C^2)$ and
  the coefficient Casimir $C_{\mathfrak h\oplus\mathfrak h^\vee[1],w}$
  on the weighted Tate pair. The spacetime piece is unchanged by the
  weight on the coefficient direction; it is the Costello heat-kernel
  inverse on the bulk free elliptic complex
  $\Omega^\bullet(\R^2)\widehat\otimes\Omega^{0,\bullet}(\C^2)$,
  constructed in \cite{costello-renormalization}*{Ch.~5}. The BV
  identity for $P_{\epsilon,L}^{\mathrm{base}}$ is standard: with
  $Q^{\mathrm{base}}=d_{\R^2}+\bar\partial_{\C^2}$, gauge-fixing
  $Q^{\mathrm{GF}}=d_{\R^2}^*+\bar\partial_{\C^2}^*$, and the
  associated Laplacian $\Delta=[Q^{\mathrm{base}},Q^{\mathrm{GF}}]$,
  one has
  $$[Q^{\mathrm{base}},P_{\epsilon,L}^{\mathrm{base}}]
    =\int_\epsilon^L[Q^{\mathrm{base}},Q^{\mathrm{GF}}e^{-t\Delta}]\,dt
    =\int_\epsilon^L\partial_t(-e^{-t\Delta})\,dt
    =e^{-\epsilon\Delta}-e^{-L\Delta}=K_\epsilon^{\mathrm{base}}
    -K_L^{\mathrm{base}}.$$
  The coefficient piece is the Casimir of
  Proposition~\ref{prop:wt-casimir-convergence}, which is annihilated
  by the trivial differential on
  $\mathfrak h_w[1]\oplus\mathfrak h^{\vee,w}_{\mathrm{cont}}[2]$.
  Therefore
  $[Q,P_{\epsilon,L}^{w}]=K_\epsilon^{w}-K_L^{w}$, and the family is
  continuous in $(\epsilon,L)$ because $C_{\mathfrak h,w}$ is a fixed
  element of the weighted pair and the bulk family is continuous.
  Item~(3), at the level asserted here, is the Costello bulk
  regularity package \cite{costello-renormalization}*{Chs.~5--7}
  tensored with a fixed coefficient kernel. This proves finite-scale
  kernel regularity and absence of new coefficient wave-front
  directions. It does not by itself prove vanishing of the
  brane-defect QME obstruction classes.
\end{proof}

\begin{rmk}[Brane defect]\label{rmk:wt-brane-defect}
  The brane defect
  \(L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}
  \subset\R^2\times\C^2\) pulls the
  weighted field complex $\mathcal E_w$ to its restriction along the
  defect:
  $$\mathcal E_w^{\partial}=\Omega^\bullet(\R)\widehat\otimes\bigl(
    \mathfrak h_w[1]\oplus\mathfrak h^{\vee,w}_{\mathrm{cont}}[2]\bigr).$$
  The boundary propagator
  $P_{\epsilon,L}^{w,\partial}\in\mathcal E_w^\partial\widehat\otimes
  \mathcal E_w^\partial$ is the bulk-to-boundary restriction of
  $P_{\epsilon,L}^{w}$ followed by the zero-mode-removed midpoint
  propagator $G(t,s)=\frac12\,\mathrm{sgn}(t-s)$ of
  Proposition~\ref{prop:conditional-boundary-product-normalization}.
  The weighted Casimir $C_{\mathfrak h,w}$ is the same on the boundary
  as in the bulk; the weight $w$ does not interact with the
  coordinate $t$.
\end{rmk}

\subsection*{Renormalization-flow compatibility}

The Costello RG flow on effective interactions is the assignment
$I_L=W(P_{\epsilon,L},I)$ that converts a local interaction $I$ at scale
$\epsilon$ into the effective interaction at scale $L$, where $W$ is
the homotopy renormalization group action on functionals
\cite{costello-renormalization}*{Ch.~6}. For the weighted mechanism to
satisfy Costello requirement~\ref{costello:CC3}, the RG flow on
$\mathcal E_w$-valued interactions must preserve the weighted
coefficient module: starting from a polynomial-degree-bounded
interaction in $\mathcal O(\mathcal E_w)$, the effective interaction
$I_L$ must remain in the same weighted category.

\begin{prop}[Graphwise RG-tame interactions]\label{prop:wt-rg-tame}
  Let $I\in\mathcal O_{\mathrm{loc}}(\mathcal E_w)$ be a local
  interaction polynomial in the fields, of total polynomial-degree
  bounded by $D_0$ at each vertex in the coefficient direction.  For
  every fixed Costello graph $\Gamma$ and every
  $0<\epsilon\leq L<\infty$, the graph contribution
  $W_\Gamma(P_{\epsilon,L}^{w},I)$ has finite coefficient degree
  bounded by $D_0V(\Gamma)-2E(\Gamma)$ and lies in the weighted
  completed coefficient category.  The bracket-tame estimate
  \ref{w:W1}, together with the finite-window coadjoint condition
  \ref{w:W2}, bounds this single graph by a finite constant times the
  corresponding spacetime graph weight.
\end{prop}

\begin{proof}
  The interaction $I$ has bounded polynomial degree $D_0$ at each
  vertex in the coefficient direction by hypothesis. A connected Costello graph
  $\Gamma$ with $V$ vertices, each of polynomial degree $\leq D_0$,
  and $E$ internal edges, contributes a coefficient
  pairing of external length at most $V\cdot D_0-2E$ in the source
  factor and a matching length in the target. By the bracket-tame
  estimate \ref{w:W1}, each internal edge contraction
  $C_{\mathfrak h,w}\colon
  \mathfrak h_w\widehat\otimes\mathfrak h^{\vee,w}_{\mathrm{cont}}\to\C$
  changes the total weight by at most the finite constant attached to
  the degrees present in that graph.  Coadjoint legs are controlled
  windowwise by \ref{w:W2}.  Hence the graph contribution is a
  well-defined element of the weighted completion.  No assertion is
  made that the full effective interaction preserves the original
  degree bound $D_0$; Costello's expansion is a completed sum over
  graph degrees.
\end{proof}

\begin{thm}[Weighted RG flow, graphwise compatibility]\label{thm:wt-rg-compatibility}
  Let $w$ be a degree weight as in
  Definition~\ref{defn:wt-degree-weight} and let
  $I\in\mathcal O_{\mathrm{loc}}(\mathcal E_w)$ be a local
  interaction satisfying a vertexwise polynomial-degree bound $D_0$.
  Each fixed graph contribution to the Costello RG flow
  $$I_L=W(P_{\epsilon,L}^{w},I)$$
  lies in the weighted Tate completion and is continuous in
  $(\epsilon,L)$.  The theorem is graphwise.  The completed sum over
  counterterms and the QME obstruction class require the locality
  input of Problem~\ref{prob:weighted-rg-locality}.
\end{thm}

\begin{proof}
  By Proposition~\ref{prop:wt-rg-tame}, every Feynman diagram
  considered individually remains in the weighted Tate category.  Its
  finite coefficient-degree bound is
  $D_0V(\Gamma)-2E(\Gamma)$, and continuity in $(\epsilon,L)$ follows
  from Proposition~\ref{prop:wt-propagator-extends}~(2).  Passing from
  graphwise well-definedness to a renormalized QME solution is
  precisely the residual analytic problem.
\end{proof}

\subsection*{Cotangent-lift theorem}

\begin{thm}[Cotangent-lift inside the weighted coefficient category]\label{thm:wt-cotangent-lift}
  Let $w(d)=q^d$ with $q>1$ be the exponential degree weight of
  Remark~\ref{rmk:wt-canonical-weight}. Then in the weighted Tate
  coefficient pair $(\mathfrak h_w,\mathfrak h^{\vee,w}_{\mathrm{cont}})$
  of Definition~\ref{defn:wt-coefficient-pair} the following internal
  weighted-category statements hold:
  \begin{enumerate}[label=(\alph*)]
    \item the Casimir
      $C_{\mathfrak h,w}=\sum_d\sum_i w(d)e_{d,i}\otimes
      w(d)^{-1}e^i_d$ converges as an element of
      $\mathfrak h_w\widehat\otimes
      \mathfrak h^{\vee,w}_{\mathrm{cont}}$
      (Proposition~\ref{prop:wt-casimir-convergence});
    \item the Costello heat-kernel propagator
      $P_{\epsilon,L}^{w}$ extends to the weighted field complex
      $\mathcal E_w$ as a continuous family in $(\epsilon,L)$
      satisfying the BV identity
      (Proposition~\ref{prop:wt-propagator-extends});
    \item each fixed Costello graph contribution preserves the
      weighted category on vertexwise polynomial-degree-bounded
      interactions
      (Theorem~\ref{thm:wt-rg-compatibility});
    \item the cochain-level $\Phi$ of
      Theorem~\ref{thm:open-closed-derived-center} extends to the
      weighted cotangent extension $\mathfrak g_w=\mathfrak h_w\ltimes
      \mathfrak h^{\vee,w}_{\mathrm{cont}}[1]$ as a continuous
      $P_0$-algebra cochain map in the weighted coefficient envelope
      $$\Phi^w\colon C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_w)
        \to\mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{Tate}}(
        \mathfrak h_w)\bigr);$$
  \end{enumerate}
\end{thm}

\begin{proof}
  Items (a)--(c) are
  Propositions~\ref{prop:wt-casimir-convergence},
  \ref{prop:wt-propagator-extends}, and
  Theorem~\ref{thm:wt-rg-compatibility}. For item~(d): the
  classical $\Phi$ of Theorem~\ref{thm:open-closed-derived-center}
  acts on continuous CE cochains by the cochain identity
  $\Phi d_{\mathrm{CE}}=d_\pi\Phi$, which is a degree-by-degree
  algebraic identity on the polynomial Hamiltonian Lie algebra
  $\mathfrak h$ together with its dual $\mathfrak h^\vee[1]$. The
  identity is preserved under any rescaling of the bases by an
  invertible weight, so it descends to the weighted pair. The
  $P_0$-algebra structure on the source is the CE cochain
  $P_0$-algebra structure formed in the weighted coefficient
  envelope; this is not the strict continuous duality statement of
  Lemma~\ref{lem:continuous-bar-cobar} for a product/direct-sum Tate
  pair.  The needed dual generators are inserted by the symmetric
  Mittag-Leffler coefficient pairing of
  Remark~\ref{rmk:wt-topology-content}. On the target, the Schouten
  bracket descends to the weighted symmetric algebra by
  \ref{w:W2}.

  No all-order QME or regulator-independent statement is part of this
  theorem; the quantum assertion is separated in
  Proposition~\ref{prop:wt-conditional-qme-lift}.
\end{proof}

\begin{prop}[Conditional weighted QME lift]\label{prop:wt-conditional-qme-lift}
  Assume the Costello-locality/QME compatibility identity of
  Problem~\ref{prob:weighted-rg-locality}: the finite-window
  counterterm system for the mixed brane-defect interaction has
  vanishing obstruction class and is compatible with the weighted
  coefficient category.  Under this assumption, the formal quantum
  derived-center map $\Phi_\hbar^{(0)}$ governed by
  Theorem~\ref{thm:phi-hbar-all-order} has a weighted-continuous
  cotangent extension
  $$\Phi_{\hbar,\mathrm{cond}}^{w}\colon
    C^\bullet_{\mathrm{CE},\mathrm{cont}}\bigl(
    \mathfrak h_{w,\hbar}\ltimes
    \mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}[1]\bigr)[[\hbar]]
    \xrightarrow[\mathrm{conditional\ QME}]{\sim}
    Z^{P_{0,\hbar}}_{\mathrm{fact}}\bigl(
    \mathrm{Obs}^\hbar_{\mathrm{open}}\bigr)|_{\mathfrak g_w}.$$
  The displayed isomorphism is a theorem only in this conditional
  weighted-continuous sector.  It is not an unconditional all-order
  lift for the original unweighted Tate pair.
\end{prop}

\begin{proof}
  The algebraic cochain identity is supplied by
  Theorem~\ref{thm:wt-cotangent-lift}.  The BV graph realization
  decomposes the cotangent action $\mathrm{ad}^\vee$ into Costello
  graphs in $\mathcal E_w$, and
  Theorem~\ref{thm:wt-rg-compatibility} keeps each fixed graph inside
  the weighted category.  What is not formal is the cancellation
  between Costello-locality counterterms and the bulk-boundary kernel
  at the brane defect.  The proposition assumes exactly that weighted
  QME compatibility and the vanishing of the obstruction class named in
  Problem~\ref{prob:weighted-rg-locality}.  With that assumption in
  force, the formal $\hbar$-adic construction of
  Theorem~\ref{thm:phi-hbar-all-order} applies in the weighted
  coefficient envelope.  Without it, the statement stops at the
  graphwise finite-scale assertions above.
\end{proof}

\begin{prob}[Costello-locality compatibility for the weighted RG flow]\label{prob:weighted-rg-locality}
  Verify that the Costello QME counterterms at the brane defect
  \(L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}\) in the weighted field complex $\mathcal E_w$ remain
  local-functional classes
  $\Op\in H^1(\mathcal O_{\mathrm{loc}}(\mathcal E_w),Q+\{I_0,-\})$,
  i.e.\ that the bulk Costello locality package
  \cite{costello-renormalization}*{Chs.~5--7} extends to the
  weighted pair. The exact published theorem numbering is not an
  input to this problem. Concretely: a counterterm contribution
  $C_n\in\mathcal O_{\mathrm{loc}}^{\hbar^n}(\mathcal E)$ at order
  $\hbar^n$ in the standard pair is a polynomial functional of
  bounded degree; one must check that the same counterterm,
  rescaled by the weight $w$ on each coefficient leg, remains a
  local functional of the same bounded polynomial degree in the
  weighted pair. The estimate \ref{w:W1} bounds vertex weights, and
  \ref{w:W2} bounds coadjoint legs graph by graph.  The remaining
  question is whether the compatible finite-window counterterm system
  obtained from Costello's Hadamard locality theorem has vanishing
  obstruction class in
  $H^1(\mathcal O_{\mathrm{loc}}(\mathcal E_w),Q+\{I_0,-\})$ for the
  mixed brane-defect interaction.  The Hadamard / Mittag-Leffler
  reduction of
  Theorem~\ref{thm:hadamard-mittag-leffler} controls the wave-front
  and finite-window locality estimates; it does not by itself compute
  that obstruction class.
\end{prob}

\begin{cor}[Conditional descendant cochain comparison]\label{cor:wt-descendant-conditional}
  Assume the obstruction class in
  Problem~\ref{prob:weighted-rg-locality} vanishes, so that
  Proposition~\ref{prop:wt-conditional-qme-lift} applies.  Then the
  Tate-coefficient lift of the descendant cochain comparison of
  Problem~\ref{prob:tate-coefficient-descendant-lift} exists in the
  weighted Tate completion only under this hypothesis: the deformation
  $$\Phi_{\hbar,\mathrm{cond}}^{(0,1)}\colon
    C^\bullet_{\mathrm{CE},\mathrm{cont}}\bigl(
    \mathfrak h_{w,\hbar}\ltimes\mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}[1]
    \bigr)^{(0)+(1)}[[\hbar]]
    \xrightarrow[\mathrm{conditional\ QME}]{\sim}
    Z^{P_{0,\hbar}}_{\mathrm{fact}}\bigl(\mathrm{Obs}^\hbar_{\mathrm{open}}
    \bigr)^{(0)+(1)}|_{\mathfrak g_w}$$
  is an isomorphism on the degree-zero plus one-antifield sector only
  after the conditional weighted QME input has been supplied.  It does
  not assert an unconditional all-order descendant lift.
\end{cor}

\begin{rmk}[Sector restriction]\label{rmk:wt-sector-restriction}
  The weighted mechanism restricts the cotangent direction from the
  ambient polynomial Hamiltonian dual to the weighted dual
  $\mathfrak h^{\vee,w}_{\mathrm{cont}}=\prod_d w(d)^{-1}H_d^\vee$.
  The strict polynomial Hamiltonian dual
  $\mathfrak h^\vee_{\mathrm{cont}}=\bigoplus_d H_d^\vee$ is a
  \emph{dense subspace} of $\mathfrak h^{\vee,w}_{\mathrm{cont}}$
  for every $w$ with $w(d)\to\infty$, since the strict direct sum
  is finite-degree truncations and the weighted product is the
  weighted Mittag-Leffler inverse-limit completion. Hence the
  weighted lift extends the cochain map continuously from the strict
  polynomial sector to the weighted product completion. This recovers
  only the weighted-continuous Hamiltonian identities, not an
  unweighted regulator-independence statement and not an identification
  of the weighted product with the original strict continuous dual.
\end{rmk}

\subsection*{Regulator independence and its boundary}

\begin{defn}[Regulator-admissible finite-window sector]\label{defn:regulator-admissible-sector}
  A local functional, interaction, obstruction cocycle, or graph
  coefficient in the weighted theory is \emph{regulator-admissible} if
  it is represented by a strict Mittag-Leffler family on the finite Tate
  windows
  \[
    \{\mathcal E_w^{w_0}\}_{w_0\geq1}
  \]
  and satisfies the following four conditions.
  \begin{enumerate}[label=(A\arabic*)]
    \item The transition maps in the coefficient and local-functional
      directions are the truncations to degrees \(d\leq w_0\), or the
      induced restriction obtained by setting higher-degree coefficient
      fields to zero.  They are degreewise surjective maps of
      complexes.
    \item At each fixed \(\hbar\)-order and for each fixed Costello
      graph, the coefficient expression uses only vertexwise
      polynomial-degree-bounded Hamiltonian and cotangent legs.
    \item If \(w,w'\) are two degree weights satisfying
      Definition~\ref{defn:wt-degree-weight}, the diagonal finite-window
      rescaling
      \[
        R_{w,w'}^{w_0}(w(d)e_{d,i})=w'(d)e_{d,i},\qquad
        R_{w,w'}^{w_0}(w(d)^{-1}e^i_d)=w'(d)^{-1}e^i_d
      \]
      transports the interaction, differential, bracket, propagator
      contraction, and counterterm representative from the
      \(w\)-window to the \(w'\)-window.  The bracket is the transported
      bracket; the theorem does not compare two weights while holding
      the raw unweighted structure constants fixed.
    \item The cohomology being computed is the admissible filtered
      cohomology detected on finite quotients and associated graded
      pieces in the envelope of Statement~\ref{stmt:tate-model-envelope};
      no observable is allowed to detect an infinite product tail
      invisible in every finite quotient.
  \end{enumerate}
\end{defn}

\begin{rmk}[Closure of the admissible class under Costello RG flow]\label{rmk:a5-rg-closure}
  Under the Costello RG-flow $W(P_{\epsilon,L},I)$ of \cite{costello-renormalization}*{\S 3--4}, the regulator-admissible class \ref{defn:regulator-admissible-sector} is closed: the flow preserves the strict Mittag-Leffler property, the polynomial-degree bound, the diagonal rescaling compatibility, and the admissible filtered cohomology. This closure is not a separate hypothesis here; it is implicit in the (CC3) compatibility recorded above and is named for referee orientation.
\end{rmk}

\begin{thm}[Regulator independence inside the admissible finite-window sector]\label{thm:wt-regulator-independence-admissible}
  Let \(w,w'\) be degree weights satisfying
  Definition~\ref{defn:wt-degree-weight}, and let \(I_0^w\) be a
  regulator-admissible mixed brane-defect interaction.  Put
  \(I_0^{w'}=R_{w,w'}I_0^w\).  Then the diagonal rescalings
  \(R_{w,w'}^{w_0}\) assemble to an isomorphism of strict
  Mittag-Leffler local-functional complexes
  \[
    R_{w,w'}\colon
    \varprojlim_{w_0}
    \bigl(\mathcal O_{\mathrm{loc}}(\mathcal E_w^{w_0}),
      Q+\{I_0^w,-\}\bigr)
    \xrightarrow{\;\cong\;}
    \varprojlim_{w_0}
    \bigl(\mathcal O_{\mathrm{loc}}(\mathcal E_{w'}^{w_0}),
      Q+\{I_0^{w'},-\}\bigr).
  \]
  Under this isomorphism:
  \begin{enumerate}[label=(\roman*)]
    \item truncated Casimirs, heat-kernel propagators, and fixed
      graphwise Costello contractions are identified;
    \item the obstruction class
      \[
        \mathrm{Ob}_w\in
        H^1_{\mathrm{adm}}(\mathcal O_{\mathrm{loc}}(\mathcal E_w),
          Q+\{I_0^w,-\})
      \]
      maps to \(\mathrm{Ob}_{w'}\);
    \item vanishing or nonvanishing of the mixed brane-defect QME
      obstruction is independent of the admissible weight.
  \end{enumerate}
  This theorem proves independence of the \emph{weight} among
  admissible regulators.  It does not identify the weighted product
  coefficient theory with the original strict product/direct-sum Tate
  pair, where the Costello coefficient Casimir does not exist.
\end{thm}

\begin{proof}
  On the finite window \(d\leq w_0\), the map \(R_{w,w'}^{w_0}\) is an
  invertible linear map on the coefficient space and the identity on
  the spacetime factor.  The bracket and the interaction in the
  \(w'\)-window are, by admissibility, the transported bracket and
  transported interaction.  The map sends
  \[
    \sum_{d\leq w_0}\sum_i
      (w(d)e_{d,i})\otimes(w(d)^{-1}e^i_d)
  \]
  to the corresponding \(w'\)-weighted truncated Casimir.  Hence it
  sends \(P_{\epsilon,L}^{w,w_0}\) to \(P_{\epsilon,L}^{w',w_0}\),
  commutes with the differential \(Q\), and carries the transported BV
  bracket and every finite-window graph contraction to the
  \(w'\)-window contraction.  Condition (A3) gives the same statement for
  \(I_0\), the counterterm representatives, and the obstruction
  cocycle.

  The maps \(R_{w,w'}^{w_0}\) commute with truncation in \(w_0\).  The
  finite-window complexes therefore form an isomorphic pair of strict
  Mittag-Leffler inverse systems.  By (A1), these are degreewise
  surjective towers of complexes.  Hence the inverse limit is exact in
  the admissible envelope of
  Statement~\ref{stmt:tate-model-envelope}; equivalently
  \(\varprojlim^1=0\) for this tower.  Passing to the inverse limit
  gives the displayed isomorphism of local-functional complexes and
  identifies their admissible filtered cohomology classes.  In
  particular the obstruction class vanishes for \(w\) if and only if
  the transported obstruction class vanishes for \(w'\).

  The last sentence is the support calculation of
  Lemma~\ref{lem:tate-casimir-obstruction}: the strict continuous dual
  is a direct sum in degree, so the full Casimir has infinite support in
  a direct-sum factor.  The weighted theorem compares only completed
  product coefficient theories for which the finite-window Casimirs
  form a strict Mittag-Leffler system.
\end{proof}

\begin{thm}[No strict unweighted finite-window endpoint]
\label{thm:strict-unweighted-no-go}
  Let
  \[
    \mathfrak h_{\Pi}=\prod_{d\geq1}H_d,\qquad
    D_{\oplus}=\bigoplus_{d\geq1}H_d^\vee
  \]
  be the original product/direct-sum Tate pair.  There is no tensor
  \(K\in\mathfrak h_{\Pi}\widehat\otimes D_{\oplus}\), and no tensor
  in \(D_{\oplus}\widehat\otimes\mathfrak h_{\Pi}\), whose projection
  to every finite window \(d\leq w_0\) is the finite Casimir
  \[
    C^{w_0}_{\mathfrak h}=\sum_{d\leq w_0}\sum_i e_{d,i}\otimes e^i_d .
  \]
  Consequently the strict unweighted pair cannot be the endpoint of a
  finite-window Costello regulator theory satisfying the coefficient
  kernel requirement \ref{costello:CC1} and the windowwise compatibility
  used in Theorem~\ref{thm:wt-regulator-independence-admissible}.

  Moreover, for any admissible weight \(w\), the inclusion
  \(D_{\oplus}\hookrightarrow
  D_{\Pi,w}:=\prod_{d\geq1}w(d)^{-1}H_d^\vee\) is only an admissible
  filtered weak equivalence.  It is not an ordinary quasi-isomorphism
  of chain complexes with zero differential.  Thus any observable or
  obstruction class detecting the quotient
  \(D_{\Pi,w}/D_{\oplus}\) is outside the proved regulator-independent
  sector.
\end{thm}

\begin{proof}
  The direct-sum factor \(D_{\oplus}\) is coefficient-finite by
  Lemma~\ref{lem:continuous-bar-cobar} item~(1): every element of a
  completed tensor product with \(D_{\oplus}\) has support in only
  finitely many \(H_d^\vee\)-degrees.  If \(K\) projected to
  \(C^{w_0}_{\mathfrak h}\) for all \(w_0\), then for every degree
  \(d\) the \(H_d^\vee\)-component of \(K\) would be nonzero.  This is
  infinite support in the direct-sum direction, a contradiction.  The
  same argument applies after reversing the tensor factors.

  Costello's heat-kernel BV propagator for the cotangent coefficient
  field is \(P_{\epsilon,L}^{\mathrm{base}}\widehat\otimes K\).  Since
  no such \(K\) exists in the strict product/direct-sum pair, the
  strict pair has an operator-level heat homotopy but no coefficient
  distributional inverse pairing and hence no graphwise regulator
  endpoint satisfying the displayed finite-window Casimir condition.

  Finally, with zero differential,
  \[
    H^0(D_{\Pi,w}/D_{\oplus})=D_{\Pi,w}/D_{\oplus}.
  \]
  The class of any sequence with one nonzero covector in every degree
  is nonzero in this quotient.  Therefore the completion changes
  ordinary cohomology even though finite quotients and associated
  graded pieces cannot see the tail.  This proves the asserted
  boundary of regulator independence.
\end{proof}

\begin{ex}[The completion changes ordinary cohomology]\label{ex:weighted-completion-changes-cohomology}
  Let
  \[
    D_{\oplus}=\bigoplus_{d\geq1}H_d^\vee,\qquad
    D_{\Pi,w}=\prod_{d\geq1}w(d)^{-1}H_d^\vee
  \]
  with zero differential.  The finite-window inclusion
  \(D_{\oplus}\hookrightarrow D_{\Pi,w}\) induces an isomorphism on
  every quotient by the tail \(d>w_0\), and therefore is a weak
  equivalence in the admissible filtered sense of
  Statement~\ref{stmt:tate-model-envelope}.  It is not a
  quasi-isomorphism in the ordinary category of chain complexes:
  \[
    H^0(D_{\Pi,w}/D_{\oplus})
      =D_{\Pi,w}/D_{\oplus}\neq0,
  \]
  for example the class of any sequence with one nonzero covector in
  every degree is nonzero.  Thus the weighted product contains
  tail states absent from the strict continuous dual.  Any observable
  detecting such a tail is outside the regulator-admissible sector of
  Definition~\ref{defn:regulator-admissible-sector}.
\end{ex}

\begin{ex}[Bad weights do not define the same regulator problem]\label{ex:bad-weight-not-regulator}
  The super-exponential function \(w(d)=\exp(d^2)\) is not a degree
  weight.  Indeed
  \[
    \frac{w(p+q-2)}{w(p)w(q)}
      =\exp\bigl((p+q-2)^2-p^2-q^2\bigr)
  \]
  is unbounded, already along \(p=q\to\infty\).  Hence condition
  \ref{w:W1} fails.  The Poisson bracket is not bracket-tame in that
  coefficient topology, and the graphwise constants in
  Proposition~\ref{prop:wt-rg-tame} need not be finite uniformly in the
  degrees used by the interaction.  The regulator-independence theorem
  above does not compare such a topology with the admissible weighted
  theory.
\end{ex}

\begin{rmk}[Exact status of the weighted mechanism]\label{rmk:wt-route-status-regulator}
  The weighted Tate construction has four distinct statuses.
  It is a regulator for the finite-window graphwise sector; it is a
  filtered weak replacement of the strict direct-sum dual only inside
  the admissible Mittag-Leffler envelope; it is a genuine completion
  changing the ordinary chain complex once infinite product tails are
  admitted; and it is not a theorem about the original unweighted
  Costello graph calculus, because that calculus has no coefficient
  Casimir in the strict product/direct-sum topology.
\end{rmk}

\subsection*{Convention firewall}

\begin{rmk}[No transfer to Vol III]\label{rmk:wt-no-transfer-vol3}
  The weighted Tate completion is a local-disk operation on the
  formal symplectic plane $\C^2$ with brane defect
  \(L=\R_{\mathrm{brane}}\times\{0\}\times\{p\}\) and
  bulk $\R^2\times\C^2$. It carries no compact Calabi-Yau datum, no
  $\Phi_d$ functor, no $\kappa_{\mathrm{ch}}$ or
  $\kappa_{\mathrm{BKM}}$ consequence, no $K3\times E$
  specialization, no Igusa cusp form, no Borcherds input form, no
  BKM denominator identity, and no Stage-1 or Stage-2 $\Phi_d$
  specialization. It addresses exclusively the analytic obstruction
  named in Lemma~\ref{lem:tate-casimir-obstruction} and Problem
  \ref{prob:tate-coefficient-descendant-lift}, and does so on the
  formal local model.
\end{rmk}

% End of fragment.
