\subsubsection{Local theorem dependencies}\label{ssec:theorem-lanes}
This section records local hypotheses, asserted scope, and
proof inputs.  The proof-bearing text is the cited theorem,
proposition, lemma, or computation.  Each assertion is interpreted with
the proof status and admissibility hypotheses recorded in the claim-status table
and the stratified Koszul criterion.

\begin{stmt}[Statement: Dirac brane probe]\label{thm:lane-dirac-probe}
  \emph{Status.} \emph{proved in finite algebraic model}.  The proof is
  confined to the formal local ghost-zero sector of the brane probe.

  \emph{Exact hypotheses.} The transverse formal disk is
  \((\widehat{\C^2}_0,dz_1\wedge dz_2)\); the stack size \(N\) is finite;
  fields are \(\phi_1,\phi_2,A\in\mathfrak{gl}_N\) on the brane line;
  the raw shifted-Chern--Simons coefficient fields have first been put in
  the Dirac normalization of
  Construction~\ref{constr:open-field-basis}; variations are compactly
  supported; and the only residual gauge group retained in this statement is
  ordinary \(GL_N\)-conjugation on degree-zero functions.

  \emph{Local assertion.} For a stack of \(N\) branes probing
  \((\widehat{\C^2}_0,dz_1\wedge dz_2)\), the ghost-zero open action is
  the first-order Dirac matrix system
  \[
    S_\partial
    =\int_\R\operatorname{Tr}
      \bigl(\phi_1\,d\phi_2+A[\phi_1,\phi_2]\bigr),
  \]
  and its reduced BV algebra is
  \[
    \C[\phi_1{}^i{}_j,\phi_2{}^i{}_j]\otimes
    \Lambda(\psi^i{}_j),
    \qquad
    Q\psi=[\phi_1,\phi_2],\quad Q\phi_i=0.
  \]
  The moment map for conjugation is
  \(-\operatorname{Tr}(\epsilon[\phi_1,\phi_2])\).  With the paper's
  convention \(\iota_{X_f}\Omega=-df\), its components satisfy
  \(\{\mu_\epsilon,\mu_\eta\}=-\mu_{[\epsilon,\eta]}\); this
  anti-equivariance affects only the comoment convention, not the zero
  locus.  The BV differential is the derived Koszul zero-fibre
  differential for the commuting-pair equation, not an underived regular
  sequence assertion.

  \emph{Proof inputs.}
  Lemma~\ref{lem:dirac-probe-reduction} derives the ghost-zero action
  from the shifted normal directions and fixes the moment-map sign.
  Proposition~\ref{prop:open-bv-truncation} proves that the ghost-zero
  truncation is consistent and identifies the residual Koszul complex.

  \emph{Scope and exclusions.} The statement does not assert an untruncated open-string
  BV model beyond this ghost-zero finite algebraic truncation.
\end{stmt}

\begin{stmt}[Statement: unital cyclic Koszul and normal-ordering core]\label{thm:lane-cyclic-koszul-normal-ordering}
  \emph{Status.} \emph{proved algebraically, with an explicit
  obstruction to the full cyclic contraction}.  This is the
  necklace-level Koszul calculation with the scalar word and
  one-\(\psi\) homology kept explicit.

  \emph{Exact hypotheses.} Work in the unital cyclic dg Lie algebra
  \[
    \mathfrak p_{\mathrm K}
    =
    \operatorname{Cyc}\bigl(T(\C x\oplus\C y\oplus\C\psi)\bigr),
    \qquad
    Q\psi=xy-yx,\quad Qx=Qy=0,
  \]
  with the scalar word \([1]\) retained until the bracket has been
  checked.  The scalar-reduced quotient
  \(\bar{\mathfrak p}_{\mathrm K}=\mathfrak p_{\mathrm K}/\C[1]\) is
  taken only after this unital computation.  The normal-ordering
  homotopy requires a chosen cyclic cut and applies to the no-\(\psi\)
  subcomplex selected by that cut.

  \emph{Local assertion.} The cyclic necklace bracket makes
  \(\mathfrak p_{\mathrm K}\) a dg Lie algebra.  The normal-ordering map
  \(N\) is a strict dg Lie map to the unital polynomial Hamiltonian
  algebra and sends \([1]\) to \(1\); after quotienting constants it
  gives the reduced Hamiltonian map
  \(N_{\mathrm{red}}\colon\bar{\mathfrak p}_{\mathrm K}\to\bar A\).
  On the cut no-\(\psi\) sector the straightening homotopy satisfies
  \(QH_c=\mathrm{id}-iN\).  There is no cyclic homotopy
  \(K\) with \(QK+KQ=\mathrm{id}-iN\) on the full cyclic complex when
  \(N\) kills the primitive one-\(\psi\) classes.

  \emph{Proof inputs.}
  Theorem~\ref{thm:primitive-cyclic-koszul-p0-model} proves the unital
  dg Lie model and the scalar bracket \(\{[x],[y]\}=[1]\).
  Proposition~\ref{prop:normal-ordering-quotient-cyclic-koszul}
  proves the strict normal-ordering quotient.
  Theorem~\ref{thm:normal-ordering-straightening-homotopy} constructs
  the cut-dependent no-\(\psi\) straightening homotopy.
  Lemma~\ref{lem:no-full-cyclic-normal-ordering-contraction} proves the
  obstruction to a full cyclic contraction.  Lemma~\ref{lem:gauge-paired-necklace-naive-quotient-fails}
  records the failure of the naive gauge-paired quotient.

  \emph{Scope and exclusions.} This block is not an unreduced
  BV/factorization-centre theorem.  It does not identify arbitrary
  open observables with central operations, and polynomial
  one-\(\psi\) descendants do not replace the principal-part cotangent
  current module.
\end{stmt}

\begin{stmt}[Statement: stable trace and one-\(\psi\) PBW shadow]\label{thm:lane-stable-trace}
  \emph{Status.} \emph{proved degreewise stable}.  It is a PBW
  special-fibre trace statement, not a statement about the principal-part
  cotangent module.

  \emph{Exact hypotheses.} Work at fixed total polynomial degree and then
  in the stable connected large-\(N\) range; pass to scalar-reduced
  connected traces; use the Koszul differential
  \(Q\psi=[\phi_1,\phi_2]\); and take the PBW special fibre before any
  filtered or \(D_\hbar\)-interpolation is introduced.

  \emph{Local assertion.} The Hamiltonian open observables in ghost
  number zero are generated by scalar-reduced connected trace classes
  \(\overline{\operatorname{Tr} f(\phi_1,\phi_2)}\).  The non-scalar
  primitive one-\(\psi\) classes \(\Psi_{a,b}\), \(a+b>0\), are the primitive PBW
  special-fibre shadow classes.  They do not realize the continuous
  \(\mathfrak h\)-coadjoint module and are not the principal-part
  currents \(\rho_{a,b}\).

  \emph{Proof inputs.}
  Procesi--Razmyslov stable invariant theory supplies the stable trace
  generators.  The Koszul differential \(Q\psi=[\phi_1,\phi_2]\) turns
  adjacent swaps into boundaries in the connected trace quotient.
  Proposition~\ref{prop:one-psi-homology} computes the primitive
  one-\(\psi\) homology.  Theorem~\ref{thm:chain-level-primitive-projection}
  identifies the chain-level primitive shadow, while
  Theorem~\ref{thm:pbw-vs-deformation} and
  Theorem~\ref{thm:no-polynomial-realization-categorical} separate that
  PBW shadow from the coadjoint principal-part module.
  Theorem~\ref{thm:one-psi-label-hbar-obstruction} proves the
  same separation for every \(\hbar\)-adic deformation satisfying its
  flatness, PBW-linear-action, Moyal-coadjoint-target, and leading-term
  hypotheses.

  \emph{Scope and exclusions.} Unstable finite-\(N\) trace identities and any
  ordinary \(\mathfrak h\)-module identification of
  \(\Psi_{a,b}\) with \(\rho_{a,b}\) are outside this statement.  The
  Fourier--Rees comparison of
  Theorem~\ref{thm:app-matlis-rees-fourier-bridge} is only an
  associated-graded label bridge for the original Hamiltonian action; the
  legitimate bridge is Fourier-twisted in the Rees
  \(\mathcal D_\hbar\)-module sense.  The corrected quantum target, when
  needed, is the reduced distributional principal-part target of
  Construction~\ref{constr:quantum-principal-part-descendant-target},
  not the PBW one-\(\psi\) span.
\end{stmt}

\begin{stmt}[Statement: CE/PV reduced Hamiltonian central-operation model]\label{thm:lane-ce-pv-center}
  \emph{Status.} \emph{proved degreewise stable}.  The proof is at
  cochain level for the reduced formal Hamiltonian algebra and its
  continuous shifted cotangent extension.  The bracketed \(P_0\)
	  consequence is used only after a bracket-admissible realization has
	  been chosen, and the bar-cobar consequence is used only under the
	  stated lower-central Tate-pronilpotent hypothesis.

  \emph{Exact hypotheses.} The Hamiltonian algebra is
  \(\mathfrak h=\C[[z_1,z_2]]/\C\cdot1\) with its \(m\)-adic topology;
  the cotangent direction is
  \(\mathfrak h^\vee_{\mathrm{cont}}[1]\), equivalently to
  \(\mathcal P[1]\) after the residue scalar is fixed by
  Theorem~\ref{thm:principal-part-coadjoint-uniqueness}; CE cochains are
	  completed in coordinate products; \(P_0\)-brackets require a
	  bracket-admissible subalgebra \(B\); kernels require a
	  kernel-admissible \(B\); and every use of bar-cobar duality is
	  restricted to the lower-central Tate-pronilpotent hypothesis named in
	  the cited lemma.

  \emph{Local assertion.} Let
  \[
    \mathfrak h=\C[[z_1,z_2]]/\C\cdot1,\qquad
    \mathfrak g=\mathfrak h\ltimes
      \mathfrak h^\vee_{\mathrm{cont}}[1].
  \]
  The coordinate completion of the CE cochains of \(\mathfrak g\)
  identifies, windowwise and after the coordinate completion specified in
  Definition~\ref{defn:formal-disk-ce-pv-completion}, with
  the corresponding Schouten polyvector algebra:
  \[
    \Phi_{\mathrm{coord}}\colon
    C^\bullet_{\mathrm{CE},\mathrm{coord}}(\mathfrak g)
    \xrightarrow{\sim}
    \mathrm{PV}_{\mathrm{coord}}
    (A_{\partial,\mathrm{coord}}).
  \]
  On a bracket-admissible \(B\subset
  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) the
  restriction \(\Phi^B_{P_0}\) is a dg \(P_0\)-isomorphism.  On a
  kernel-admissible \(B\) the diagonal tensor \(\Theta_B\) is the
  associated Maurer--Cartan kernel.  The ambient strict product completion
  carries neither assertion.
  The generator dictionary is
  \[
    c^I\mapsto\theta^I,\qquad u_I\mapsto O_I .
  \]
  The \(Z^{P_0}_{\mathrm{red,Ham}}\) identification is asserted only on the
  coordinate-window or mixed/weighted-continuous sector where the Schouten
  bracket is a continuous operation; the strict ambient product
  completion is not a \(P_0\)-algebra here.
  Here \(|u_I|=0\), \(|c^I|=1\), and \(u_I\) is the CE coordinate dual
  to the shifted-cotangent generator, not to a Hamiltonian generator.

  \emph{Proof inputs.}
  Proposition~\ref{prop:grav-ops} identifies closed local operators as
  continuous CE cochains, which sit inside the coordinate envelope only
  after the chosen continuity condition is specified.
  Lemma~\ref{lem:formal-disk-ce-schouten-continuity} computes the
  coordinate PV differential.  Theorem~\ref{thm:reduced-ce-pv-central-operation}
  checks
  \(\Phi_{\mathrm{coord}} d_{\mathrm{CE}}
  =d_\pi^{\mathrm{coord}}\Phi_{\mathrm{coord}}\) on generators and extends
  by the completed Leibniz rule.  Lemma~\ref{lem:continuous-bar-cobar}
  supplies the conilpotent bar-cobar template only in its own
  hypothesis; the untruncated formal Hamiltonian algebra with linear
  modes is not used as a lower-central Tate-pronilpotent input.

  \emph{Scope and exclusions.} The statement does not prove an unrestricted
  factorization-centre theorem or a conilpotence statement for the
  untruncated formal Hamiltonian algebra.  It also does not construct a
  BV heat-kernel propagator, a BV Laplacian, or a QME-compatible
  closed-open graph model for the unreduced cotangent sector.
\end{stmt}

\begin{stmt}[Statement: local chiral/factorization taxonomy]\label{thm:lane-local-chiral-taxonomy}
  \emph{Status.} \emph{theorem-bridged local construction, with proved
  object identifications on the cited local habitats and a definitional
  firewall against vertex and compact-target overclaims}.  This statement
  fixes what the manuscript may call a chiral object in the local mixed
  holomorphic-topological theory.  It is not a compact target theorem and
  not a one-dimensional vertex-algebra theorem.

  \emph{Exact hypotheses.} The base geometry is
  \[
    \R^2_{\mathrm{top}}\times
    \widehat{\C^2}_{0,\mathrm{hol}},
    \qquad
    \Omega_{\mathrm{loc}}=dz_1\wedge dz_2,
  \]
  with Hamiltonian Lie algebra
  \(\mathfrak h=\C[[z_1,z_2]]/\C\cdot1\) and principal-part cotangent
  module
  \[
    \mathcal P=\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
    \subset H^2_{\mathfrak m}(\C[[z_1,z_2]])\,dz_1dz_2
    \cong\mathfrak h^\vee_{\mathrm{cont}} .
  \]
  The shifted cotangent algebra may therefore be written either as
  \[
    \mathfrak g=\mathfrak h\ltimes
    \mathfrak h^\vee_{\mathrm{cont}}[1]
    \quad\text{or}\quad
    \mathfrak g_{\mathrm{hol}}=\mathfrak h\ltimes\mathcal P[1],
  \]
  with the residue normalization fixed.  Brane-current statements use
  intervals \(I\subset\R_{\mathrm{brane}}\).  Weyl/Moyal statements use
  the Capelli/Weyl convention of the degree-zero quantum theorem.  No
  restriction to a complex line, holomorphic defect curve, compact
  Calabi--Yau target, or CoHA target is assumed.

  \emph{Local assertion.} The local taxonomy has four objects.
  \begin{enumerate}[label=(\arabic*)]
    \item The closed holomorphic object is the formal Hamiltonian
      holomorphic factorization algebra on the formal \(\C^2\)-disk:
      \[
        \mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}(B)
        =
        C^\bullet_{\mathrm{CE},\mathrm{cont}}
        \bigl(\Omega^{0,\bullet}_c(B)\widehat\otimes
        (\mathfrak h\ltimes\mathcal P[1])\bigr).
      \]
      On a holomorphic polydisk \(B\), its dg Lie input is
      \[
        \Omega^{0,\bullet}_c(B)\widehat\otimes
        \mathfrak g_{\mathrm{hol}},
      \]
      and its formal stalk is the completed CE object
      \(C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)\) only with the
      coordinate/admissible PV identification supplied by the CE/PV lane.

    \item The mixed topological-current enhancement over
      \(\R^2_{\mathrm{top}}\) is
      \[
        \mathcal F_{\mathrm{Ham}}^{\mathrm{mix}}(U\times B)
        =
        C^\bullet_{\mathrm{CE},\mathrm{cont}}
        \bigl(\mathfrak g^{\mathrm{mix}}_{U,B}\bigr),
      \]
      where the coefficient input on a topological open \(U\) is
      \[
        \mathfrak g^{\mathrm{mix}}_{U,B}
        =
        \Omega^\bullet_c(U)\widehat\otimes
        \Omega^{0,\bullet}_c(B)\widehat\otimes\mathfrak g .
      \]
      This object is locally constant in \(U\) and holomorphic in \(B\).
      The interval current algebra is its support-local brane-line
      restriction, not a complex one-dimensional chiral algebra.

    \item The open quantum brane object is the Weyl/Moyal algebra and its
      matrix or supermatrix cyclic bar-cobar avatars:
      \[
        P=\partial_{z_1}\otimes\partial_{z_2}
        -\partial_{z_2}\otimes\partial_{z_1},
      \]
      \[
        \begin{aligned}
        f*g&=m\circ\exp\!\left(\frac{\hbar}{2}P\right)(f\otimes g),\\
        \{f,g\}_\hbar&=\hbar^{-1}(f*g-g*f),
        \end{aligned}
      \]
      together with the finite-\(N\) matrix Weyl relations
      \[
        [(\phi_1)^i{}_j,(\phi_2)^k{}_l]
        =\hbar\,\delta^i_l\delta^k_j .
      \]
      Trace and supertrace cyclic complexes are bookkeeping avatars for
      the brane algebra and its balanced scalar-contact branch.

    \item The defect/principal-part current object is
      \[
        \mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h,\qquad
        \mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mathcal P,\qquad
        \mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1],
      \]
      with reduced target
      \[
        A^{\mathrm{pp}}_\partial(I)
        =
        \widehat{\mathbf S}(\Omega_c^0(I)\widehat\otimes\bar A)
        \widehat\otimes
        \widehat{\mathbf S}(\mathcal D'_c(I)\widehat\otimes\mathcal P[1])
      \]
      and brackets
      \[
        \begin{aligned}
        \{B_f(a),B_g(b)\}&=B_{\{f,g\}}(ab),\\
        \{B_f(a),\Theta_\rho(B)\}&=\Theta_{f\cdot\rho}(aB),\\
        \{\Theta_\rho(B),\Theta_\sigma(C)\}&=0 .
        \end{aligned}
      \]
      Its quantum version replaces \(f\cdot\rho\) by
      \(\operatorname{ad}^{\vee}_{f,\hbar}\rho\).
  \end{enumerate}
  None of these four objects is compact-CY chiral homology, a CoHA, a
  quintic/GV/OSV object, an Abel--Jacobi normal-function object, an Igusa
  product, a Borcherds lift, or a BKM algebra.  A one-dimensional vertex
  algebra can enter only after an additional theorem chooses a complex
  line or holomorphic defect, proves factorization on that line, and
  constructs the corresponding OPE modes.

  \emph{Proof inputs.}
  Definition~\ref{def:local-holomorphic-string-sector} and
  Definition~\ref{def:local-th-string} supply the holomorphic and mixed
  factorization meanings.
  Proposition~\ref{prop:local-hamiltonian-factorization-observables}
  proves the local-field-to-\(\mathfrak g\)-to-CE factorization-observable
  bridge for \(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}\) and
  \(\mathcal F_{\mathrm{Ham}}^{\mathrm{mix}}\).
  Theorem~\ref{thm:formal-disk-completed-ce-pv}
  and Theorem~\ref{thm:reduced-ce-pv-central-operation} identify the
  formal Hamiltonian CE/PV stalk under their admissibility hypotheses.
  Theorem~\ref{thm:hamiltonian-current-factorization},
  Theorem~\ref{thm:reduced-principal-part-boundary-current}, and
  Corollary~\ref{cor:app-factorization-principal-part-current-brackets}
  give the interval current and principal-part brackets.
  Proposition~\ref{prop:moyal-monomial} and
  Theorem~\ref{thm:finite-n-reduced-moyal} give the formal Weyl/Moyal
  coefficients and the radial/Weyl finite-certificate trace gate.

  \emph{Scope and exclusions.} The theorem lanes below may use
  holomorphic factorization, mixed topological-current factorization,
  Weyl/Moyal brane algebra, cyclic bar-cobar trace avatars, and
  principal-part current algebra only in the senses above.  They do not
  assert a vertex algebra, compact-CY chiral homology, CoHA, quintic,
  OSV/GV, Abel--Jacobi, Igusa, Borcherds, BKM, or global BCOV theorem.
\end{stmt}

\begin{stmt}[Statement: native holomorphic \(E_2\) collision lane and Bochner--Martinelli obligation]\label{thm:lane-native-holomorphic-e2-bm}
  \emph{Status.} \emph{proved CE/factorization object and proved
  semidirect collision algebra; BMK current-limit data, finite Matlis
  moment maps, arity-two output projection, and one-pair analytic
  pro-Matlis retract proved; strict native all-window current transfer
  recorded as an exact obstruction}.  This is the native
  holomorphic \(E_2\)-type theorem lane on \(\C^2\).  It is not a curve
  vertex algebra theorem and not a Costello graph/QME theorem.

  \emph{Exact hypotheses.} Work on a holomorphic polydisk
  \(B\subset\C^2_{\mathrm{hol}}\) in the formal-local model, with
  \[
    \mathfrak h=\C[[z_1,z_2]]/\C\cdot1,\qquad
    \mathcal P=\operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
    \cong\mathfrak h^\vee_{\mathrm{cont}},
  \]
  where
  \[
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}dz_1dz_2,\qquad
    \operatorname{Res}_0(\rho_{a,b}z_1^mz_2^n)
      =\delta_{a,m}\delta_{b,n}.
  \]
  The topology is the compactly supported Dolbeault topology in \(B\)
  tensored with the \(m\)-adic Hamiltonian topology and the continuous
  principal-part dual.  No holomorphic line, transverse vacuum,
  Laurent-mode expansion, Zhu map, elliptic gauge fixing, BV heat kernel,
  counterterm scheme, or QME solution is part of this hypothesis.

  \emph{Native object.} The holomorphic algebra is
  \[
    \mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}(B)
    =
    C^\bullet_{\mathrm{CE},\mathrm{cont}}
    \bigl(
      \Omega_c^{0,\bullet}(B)\widehat\otimes
      (\mathfrak h\ltimes\mathcal P[1])
    \bigr).
  \]
  Equivalently, before passing to compactly supported observables, this is
  the classical Hamiltonian BF field theory with fields
  \[
    \alpha_{\mathrm{BF}}\in
    \Omega^{0,\bullet}(B)\widehat\otimes\mathfrak h[1],
    \qquad
    \beta_{\mathrm{BF}}\in
    \Omega^{0,\bullet}(B)\widehat\otimes\mathcal P[2],
  \]
  Dolbeault differential \(\bar\partial\), and cubic interaction
  \[
    I_{\mathrm{Ham}}
    =
    \frac12\int_B
    \langle\beta_{\mathrm{BF}},
    \{\alpha_{\mathrm{BF}},\alpha_{\mathrm{BF}}\}\rangle_{\mathrm{res}} .
  \]
  The compactly supported observable dg Lie input is exactly
  \[
    \Omega_c^{0,\bullet}(B)\widehat\otimes
    (\mathfrak h\ltimes\mathcal P[1]).
  \]
  The binary collision coefficients are those of the semidirect dg Lie
  algebra.  For compactly supported Dolbeault forms
  \(\alpha,\beta\), Hamiltonians \(f,g\in\mathfrak h\), and principal
  parts \(\rho,\sigma\in\mathcal P\),
  \[
    [\alpha\otimes f,\beta\otimes g]
      =
      (\alpha\wedge\beta)\otimes\{f,g\},
  \]
  \[
    [\alpha\otimes f,\beta\otimes\rho[1]]
      =
      (\alpha\wedge\beta)\otimes(f\cdot\rho)[1],
    \qquad
    [\alpha\otimes\rho[1],\beta\otimes\sigma[1]]=0,
  \]
  with the ordinary Koszul signs for the tensor product dg Lie algebra.
  The coadjoint action is fixed by residue integration by parts:
  \[
    \operatorname{Res}_0((f\cdot\rho)g)
      =
      -\operatorname{Res}_0(\rho\,\{f,g\}).
  \]
  In monomial coordinates this gives the current-lane formula
  \[
    z_1^p z_2^q\cdot\rho_{i,j}
    =
    -(pj-qi+p-q)\rho_{i-p+1,j-q+1},
  \]
  with negative-index targets equal to zero.  Thus binary holomorphic
  collisions see exactly the Hamiltonian bracket and its coadjoint
  action; they do not produce a one-variable OPE mode algebra.

  \emph{Bochner--Martinelli current data and obstruction.} On
  \((\C^2_\zeta\times\C^2_z)\setminus\Delta\), set
  \[
    \eta=\zeta-z,\qquad
    r^2=|\eta_1|^2+|\eta_2|^2,\qquad
    d\bar\eta_j=d\bar\zeta_j-d\bar z_j .
  \]
  The explicit holomorphic kernel is the Bochner--Martinelli--Koppelman
  current
  \cite{laurent-thiebaut-bmk}*{Ch.~III, Def.~1.2, Lem.~1.3}
  \[
    K_{\mathrm{BM}}(\zeta,z)
    =
    \frac{1}{(2\pi i)^2}
    \frac{
      \overline{\eta_1}\,d\bar\eta_2
      -
      \overline{\eta_2}\,d\bar\eta_1
    }{r^4}
    \wedge d\zeta_1\wedge d\zeta_2 .
  \]
  Source boundary: Laurent--Thi\'ebaut and Ruppenthal support the
  pre-cutoff BMK kernel, its component \(\bar\partial\)-identity away
  from the diagonal, and the classical Koppelman homotopy formula on
  bounded \(C^1\) domains
  \cite{ruppenthal-bmk}*{\S5, Def.~5.1, Thm.~5.2, Eq.~(10)}.  They do
  not supply the cutoff-current limit, the finite Matlis moment
  projection, the residue-current section, the collar quotient, the
  Hamiltonian action, the one-pair analytic pro-Matlis retract, or the
  six-entry native all-window obstruction vector.
  It gives current-limit data and finite Matlis moment maps, but not a
  native finite-window homotopy on the full compact-support/current
  complex.  The finite-current obstruction is
  \[
    \operatorname{Ob}^{\mathrm{BMK\mbox{-}curr}}_N
    =
    (\operatorname{ob}_{\mathrm{diag}},
     \operatorname{ob}_{\mathrm{an}/\mathrm{fin},N},
     \operatorname{ob}_{\mathfrak h,N},
     \operatorname{ob}_{\mathrm{collar\mbox{-}fact},N}).
  \]
  Its decisive support-local quotient obstruction is
  \[
    z_1^{N+2}\cdot\rho_{N+1,0}=-(N+2)\rho_{0,1}.
  \]
  The projected finite-window \(L_\infty\) escape repair is also
  obstructed: on \((z_1^{N+2},z_2,\rho_{N,0})\) the projected Jacobiator
  contributes \((N+1)(N+2)\rho_{0,1}\).  The surviving theorem data are:
  \begin{enumerate}[label=(\arabic*)]
    \item current-limit existence on fixed finite configuration strata;
    \item finite moment maps \(p_N\) and residue-current sections \(i_N\);
    \item the arity-two output projection
      \(\ell_2^{\mathrm{BM},N}(x,y)=p_N[ix,iy]\), identifying the
      Hamiltonian bracket and Matlis coadjoint action coefficientwise.
  \end{enumerate}
  The positive all-window statement currently proved is only the
  one-pair analytic pro-Matlis retract
  \(P_{\Pi}^{\mathrm{an}}=\tau P_{\mathrm{an}}\), with
  \(\pi_NP_{\Pi}^{\mathrm{an}}=p_N\).  This retract is an internal
  one-pair analytic construction, not a theorem imported from the
  BMK/Koppelman sources.  The strict native all-window current transfer
  is obstructed by
  \[
    \operatorname{Ob}^{\Pi}_{\mathrm{BM}}
    =
    (\operatorname{ob}_{\oplus},\operatorname{ob}_{I_\Pi},
     \operatorname{ob}_{\mathfrak h,\Pi},
     \operatorname{ob}_{\mathrm{collar},\Pi},
     \operatorname{ob}_{3,\Pi},
     \operatorname{ob}_{\mathrm{unif},\Pi}),
  \]
  after this finite-current obstruction gate.

  \emph{Controlled reductions only.} A curve chiral algebra, fields
  \(J_f(w)\), Laurent singular products, or a Zhu comparison can enter
  only after a separate reduction datum
  \[
    (\iota_L,\mathcal B_\perp,\mathsf R_{L,\mathcal B_\perp},
    V_L,\mathbf 1_L,T_L,Y_L,\zeta_{L,\hbar})
  \]
  satisfies the vertex/OPE obligations of
  Statement~\ref{thm:lane-holomorphic-defect-voa-restriction}.  The
  support-local real interval current algebra is not such a reduction.

  \emph{Costello/QME firewall.} The Bochner--Martinelli kernel is a
  Dolbeault homotopy kernel for the holomorphic factorization proof.  It
  is not a BV heat-kernel propagator, does not define a BV Laplacian, and
  supplies no counterterm, anomaly cancellation, brane-defect graph, or
  QME solution.  Those claims remain in the Costello graph/QME lanes and
  their stated obstruction complexes.
\end{stmt}

\begin{stmt}[Statement: constructed local chiral/factorization algebra and vertex boundary]\label{thm:lane-holomorphic-defect-voa-restriction}
  \emph{Status.} \emph{proved local chiral/factorization construction,
  with a precise residual boundary for one-dimensional vertex/OPE
  specialization}.  The manuscript has constructed a local
  Hamiltonian chiral/factorization algebra.  The valid obstruction is
  narrower: the present data do not yet extract from it a
  one-complex-dimensional vertex algebra.

  \emph{Exact hypotheses.} The base is
  \[
    \R^2_{\mathrm{top}}\times
    \widehat{\C^2}_{0,\mathrm{hol}},
    \qquad \Omega_{\mathrm{loc}}=dz_1\wedge dz_2 ,
  \]
  with
  \[
    \mathfrak h=\C[[z_1,z_2]]/\C\cdot1,\qquad
    \mathfrak g=\mathfrak h\ltimes
    \mathfrak h^\vee_{\mathrm{cont}}[1].
  \]
  Via the residue pairing this is equivalently
  \(\mathfrak h\ltimes\mathcal P[1]\), with \(\mathcal P\) the
  principal-part module of
  Statement~\ref{thm:lane-native-holomorphic-e2-bm}.
  Brane-current statements use the real brane interval
  \(I\subset\R_{\mathrm{brane}}\).  Quantum brane statements use the
  Weyl/Moyal algebra \((\bar A_\hbar,*)\) and the Moyal coadjoint action
  on principal parts.  No compact Calabi--Yau, CoHA, quintic, OSV/GV,
  Abel--Jacobi, Igusa, Borcherds, or BKM datum is part of the hypothesis.

  \emph{Local assertion.} The constructed local chiral/factorization
  object is
  \[
    \mathcal F_{\mathrm{Ham}}^{\mathrm{hol}},
  \]
  the formal Hamiltonian holomorphic factorization algebra on
  \((\widehat{\C^2}_0,dz_1\wedge dz_2)\).  On a holomorphic polydisk
  \(B\) its dg Lie input is
  \[
    \Omega^{0,\bullet}_c(B)\widehat\otimes
    (\mathfrak h\ltimes\mathcal P[1]) .
  \]
  Its formal stalk is the completed CE object
  \(C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g)\), identified with
  the coordinate/admissible PV model only under the hypotheses of the
  CE/PV lane.  Its mixed enhancement over a topological open
  \(U\subset\R^2_{\mathrm{top}}\) has input
  \[
    \mathfrak g^{\mathrm{mix}}_{U,B}
    =
    \Omega^\bullet_c(U)\widehat\otimes
    \Omega^{0,\bullet}_c(B)\widehat\otimes\mathfrak g .
  \]
  The brane avatars of this local chiral/factorization object are the
  Weyl/Moyal brane algebra, the matrix or supermatrix cyclic trace
  avatars, and the support-local principal-part current algebra
  \[
    \mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h,\qquad
    \mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mathcal P,\qquad
    \mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1],
  \]
  with reduced current brackets
  \[
    \begin{aligned}
    \{B_f(a),B_g(b)\}&=B_{\{f,g\}}(ab),\\
    \{B_f(a),\Theta_\rho(B)\}&=\Theta_{f\cdot\rho}(aB),\\
    \{\Theta_\rho(B),\Theta_\sigma(C)\}&=0 .
    \end{aligned}
  \]
  The quantum coefficient surface replaces \(f\cdot\rho\) by
  \(\operatorname{ad}^{\vee}_{f,\hbar}\rho\) and uses
  \[
    f*g=m\circ\exp\!\left(\frac{\hbar}{2}P\right)(f\otimes g).
  \]

  \emph{Proof path.}
  Definition~\ref{def:local-hamiltonian-chiral-factorization-algebra}
  names the constructed object and its mixed/current/brane avatars.
  Proposition~\ref{prop:local-hamiltonian-factorization-observables}
  proves the path from the local mixed HT fields through the Hamiltonian
  reduction to
  \(\mathfrak g=\mathfrak h\ltimes
  \mathfrak h^\vee_{\mathrm{cont}}[1]\) and then to the CE
  factorization observables
  \(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}\) and
  \(\mathcal F_{\mathrm{Ham}}^{\mathrm{mix}}\).
  Definition~\ref{def:local-holomorphic-string-sector} and
  Definition~\ref{def:local-th-string} give the holomorphic and mixed
  factorization habitats.  Theorem~\ref{thm:formal-disk-completed-ce-pv}
  and Theorem~\ref{thm:reduced-ce-pv-central-operation} prove the
  coordinate CE/PV stalk comparison on the admissible habitats.
  Theorem~\ref{thm:hamiltonian-current-factorization},
  Theorem~\ref{thm:reduced-principal-part-boundary-current}, and
  Corollary~\ref{cor:app-factorization-principal-part-current-brackets}
  prove the interval current interface and principal-part brackets.
  Proposition~\ref{prop:moyal-monomial},
  Theorem~\ref{thm:finite-n-reduced-moyal}, and
  Theorem~\ref{thm:quantum-coefficient-surface} give the Weyl/Moyal
  coefficient surface and the quantum principal-part current action.
  Statement~\ref{thm:lane-native-holomorphic-e2-bm} isolates the native
  two-complex-dimensional binary collision law and the separate
  Bochner--Martinelli proof obligation.

  \emph{Vertex/OPE boundary.} A one-dimensional vertex algebra is a
  further specialization of the constructed local chiral/factorization
  object.  It requires all of the following extra data.
  \begin{enumerate}[label=(\arabic*)]
    \item A holomorphic embedding
      \[
        \iota_L\colon L=\operatorname{Spf}\C[[w]]
        \hookrightarrow\widehat{\C^2}_0 .
      \]
      The existing brane interval is a real topological line; it is not
      this complex line.
    \item A transverse datum \(\mathcal B_\perp\) and a restriction
      functor
      \[
        \mathsf R_{L,\mathcal B_\perp}(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}})
        =
        \mathcal F_{L,\mathcal B_\perp},
      \]
      with independence of normal choices, compatibility with disjoint
      disks in \(L\), and translation covariance in \(w\).
    \item A factorization-to-vertex comparison producing
      \(V_L\), a vacuum \(\mathbf 1_L\), and a translation operator
      \(T_L\).
    \item Finite Laurent OPE modes
      \[
        Y_L(a,w)b=\sum_{n\in\Z}(a_{(n)}b)w^{-n-1},\qquad
        a_{(n)}b=0\quad(n\gg0),
      \]
      with vacuum, translation, and locality.
    \item A Weyl/Moyal zero-mode or Zhu comparison
      \[
        \zeta_{L,\hbar}\colon
        (\bar A_\hbar,*)\longrightarrow \operatorname{Zhu}(V_L),
      \]
      or fields \(J_f(w)\) whose singular product has specified central
      level and whose zero modes act on principal parts by
      \(\operatorname{ad}^{\vee}_{f,\hbar}\).
  \end{enumerate}
  These five data are not supplied by the present manuscript.

  \emph{Conclusion.} The chiral-algebra construction is present in the
  precise local sense proved here: the constructed object is the
  two-complex-dimensional formal Hamiltonian holomorphic
  factorization algebra and its mixed/current/brane avatars.  The
  manuscript does not yet assert the stronger one-dimensional VOA/OPE
  theorem.  If a tuple
  \[
    \mathfrak R_L
    =
    (\iota_L,\mathcal B_\perp,\mathsf R_{L,\mathcal B_\perp},
    V_L,\mathbf 1_L,T_L,Y_L,\zeta_{L,\hbar})
  \]
  satisfying the five displayed obligations is supplied, then \(V_L\)
  is a one-dimensional vertex/OPE algebra compatible with the Weyl/Moyal
  brane algebra through \(\zeta_{L,\hbar}\) and the stated zero-mode
  coadjoint action.  This implication is only the formal consequence of
  the supplied vertex data; it is not needed for the constructed local
  chiral/factorization algebra.  In the \(\C\times\R\) interface below,
  such a generic \(V_L\) datum is admissible only after it factors through
  \(\mathcal R_{\C\times\R}\) and is identified with
  \(V_{\mathrm{red}}\) in \(\mathfrak I_{\mathrm{ch}}\).
\end{stmt}

\begin{stmt}[Statement: controlled \(\C\times\R\) reduction with retained \(z_2\)-coefficients]\label{thm:lane-controlled-cxr-reduction}
  \emph{Status.} \emph{theorem-surface with an algebraically stable
  coefficient system and analytic pushforward obligations}.  This is the
  only admissible route from the native
  \(\R^2_{\mathrm{top}}\times\C^2_{\mathrm{hol}}\) factorization object
  to a \(\C\times\R\) curve shadow.  It is not a replacement of the
  native \(\C^2\) holomorphic factorization algebra by a curve vertex
  algebra.

  \emph{Exact hypotheses.} Let
  \[
    X=\R_t\times\R_s\times\C_{z_1}\times\C_{z_2},
    \qquad
    Y=\R_t\times\C_{z_1},
    \qquad
    \pi(t,s;z_1,z_2)=(t;z_1).
  \]
  A controlled reduction datum is
  \[
    \mathcal R_{\C\times\R}
    =
    (\pi,\kappa_{\mathrm{top}},\kappa_{\mathrm{hol}},
    B_{z_2},\pi_!,L_{\mathrm{red}},
    \langle-,-\rangle_{\mathrm{red}},
    \{-,-\}_{\mathrm{red}},H_{\mathrm{anom}}).
  \]
  The topological part contains, on each oriented compact-support
  \(s\)-interval \(J\), maps
  \[
    p_s:\Omega_c^\bullet(J)\to\C[-1],\qquad
    i_s:\C[-1]\to\Omega_c^\bullet(J),\qquad K_s,
  \]
  with
  \[
    d_sK_s+K_sd_s=\operatorname{id}-i_sp_s .
  \]
  This keeps the compact-support orientation line
  \(H_c^1(J)\cong\C[-1]\); it is not an acyclicity assertion.  The
  holomorphic part must either construct a Dolbeault
  \(z_2\)-fiber datum
  \[
    \bar\partial_{z_2}K_{z_2}+K_{z_2}\bar\partial_{z_2}
    =
    \operatorname{id}-i_{z_2}p_{z_2}
  \]
  with support and factorization control, or use the equivalent full
  \(z_2\)-principal-part coefficient system.

  \emph{Reduced coefficient system.} The reduced Hamiltonian algebra is
  \[
    \mathfrak h_{\mathrm{red}}
    =
    \C[[z_1]][[z_2]]/\C\cdot1,
  \]
  read as a coefficient system over \(Y\).  The cotangent module is the
  full two-index principal-part module
  \[
    \mathcal P_{\mathrm{red}}
    =
    \operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
    \subset
    H^2_{(z_1,z_2)}(\C[[z_1,z_2]])\,dz_1dz_2,
    \qquad
    \rho_{a,b}=z_1^{-a-1}z_2^{-b-1}dz_1dz_2 .
  \]
  Its pairing is
  \[
    \langle\rho_{a,b},z_1^mz_2^n\rangle_{\mathrm{red}}
    =
    \delta_{a,m}\delta_{b,n}.
  \]
  The reduced bracket remains the two-variable Hamiltonian bracket
  \[
    \{f,g\}_{\mathrm{red}}
    =
    \partial_{z_1}f\,\partial_{z_2}g
    -
    \partial_{z_2}f\,\partial_{z_1}g
    \pmod{\C},
  \]
  so that
  \[
    \{z_1^az_2^b,z_1^cz_2^d\}_{\mathrm{red}}
    =
    (ad-bc)z_1^{a+c-1}z_2^{b+d-1}.
  \]
  The shifted cotangent algebra is
  \[
    \mathfrak g_{\mathrm{red}}
    =
    \mathfrak h_{\mathrm{red}}\ltimes
    \mathcal P_{\mathrm{red}}[1],
  \]
  with the same residue coadjoint action
  \[
    z_1^pz_2^q\cdot\rho_{i,j}
    =
    -(pj-qi+p-q)\rho_{i-p+1,j-q+1},
  \]
  negative-index targets being zero.

  \emph{Local assertion.} Under the datum
  \(\mathcal R_{\C\times\R}\), the brane image is
  \[
    L_{\mathrm{red}}=\R_t\times\{z_1=0\}\subset Y,
  \]
  but the second normal matrix survives:
  \[
    \operatorname{ev}^{\mathrm{red}}_N(f)
    =
    \overline{\operatorname{Tr}f(X,Y)},\qquad
    X=\phi_1,\quad Y=\phi_2.
  \]
  The support-local reduced currents are
  \[
    B_f(a)=\int_I a(t)\,
    \overline{\operatorname{Tr}f(X(t),Y(t))}\,dt,
    \qquad
    \Theta_\rho(B),\quad B\in\mathcal D'_c(I),
  \]
  with brackets
  \[
    \{B_f(a),B_g(b)\}
      =B_{\{f,g\}_{\mathrm{red}}}(ab),
  \]
  \[
    \{B_f(a),\Theta_\rho(B)\}
      =
      \Theta_{f\cdot\rho}(aB),
    \qquad
    \{\Theta_\rho(B),\Theta_\sigma(C)\}=0 .
  \]
  The scalar anomaly survives because \(\{z_1,z_2\}=1\):
  \[
    \operatorname{Ob}^{\mathrm{red}}_{\mathrm{sc}}
    (\gamma_{\mathbf1};a,f;b,g)
    =
    \hbar N\, [\{f,g\}_{\mathrm{red}}]_0
    \int_{\R_t}a(t)b(t)\gamma_{\mathbf1}(t)\,dt .
  \]
  The same scalar-cancellation alternatives as in the unreduced theorem
  must therefore be chosen again.  In the quantum branch the Moyal
  product remains
  \[
    f*g
    =
    m\circ\exp\!\left(
      \frac{\hbar}{2}
      (\partial_{z_1}\otimes\partial_{z_2}
      -\partial_{z_2}\otimes\partial_{z_1})
    \right)(f\otimes g).
  \]
  Killing \(z_2\), or keeping only the \(b=0\) principal-part residue
  line, is not an admissible reduction: it kills the bracket, fails
  \(\mathfrak h_{\mathrm{red}}\)-equivariance since
  \(z_1\cdot\rho_{a,0}=-\rho_{a,1}\), and cannot match the matrix Weyl
  relation \([X^i{}_j,Y^k{}_\ell]=\hbar\delta^i_\ell\delta^k_j\).

  \emph{Proof inputs and obligations.}
  Statement~\ref{thm:lane-native-holomorphic-e2-bm} supplies the native
  two-complex-dimensional object that is being reduced.
  Statement~\ref{thm:lane-principal-parts} and
  Statement~\ref{thm:lane-reduced-principal-part-current} supply the
  principal-part and interval-current formulas.
  Statement~\ref{thm:lane-moyal-degree-zero} supplies the Weyl/Moyal
  coefficient convention, while Statement~\ref{thm:lane-u1-anomaly}
  supplies the scalar anomaly.  What is not yet supplied is the analytic
  \(\pi_!\)-theorem: the \(s\)-orientation sign, the \(z_2\)-Dolbeault
  or residue pushforward with support control, the reduced BV pairing
  degrees, factorization compatibility on two and three disks, and the
  anomaly homotopy \(H_{\mathrm{anom}}\).

  \emph{Obstruction vector.} The open datum is
  \[
    \operatorname{Ob}_{\C\times\R}
    =
    (\operatorname{ob}_{s,\mathrm{or}},
     \operatorname{ob}_{z_2,\mathrm{fib}},
     \operatorname{ob}_{\mathrm{BV,pair}},
     \operatorname{ob}_{\mathrm{fac}},
     \operatorname{ob}_{\mathrm{brane}},
     \operatorname{ob}_{\mathrm{anom}},
     \operatorname{ob}_{\mathrm{Moyal}}).
  \]
  A curve chiral or Zhu theorem may use this lane only after the relevant
  components vanish or are carried as explicit hypotheses.
\end{stmt}

\begin{stmt}[Statement: reduced Dirac BRST curve algebra and Zhu bridge]\label{thm:lane-reduced-dirac-brst-zhu}
  \emph{Status.} \emph{typed theorem surface after
  Statement~\ref{thm:lane-controlled-cxr-reduction}, with false transfer
  before it}.  This statement records the curve vertex and Zhu package
  that may be targeted after controlled reduction.  It is not native to
  \(\C^2\).

  \emph{Exact hypotheses.} Assume a controlled reduction datum
  \(\mathcal R_{\C\times\R}\) as in
  Statement~\ref{thm:lane-controlled-cxr-reduction}, including the
  retained \(z_2\)-coefficient or principal-part system and an anomaly
  convention.  Assume also a factorization-to-vertex theorem on the
  \(z_1\)-line, producing a \(\Z_{\ge0}\)-graded vertex algebra with
  vacuum, translation, finite Laurent singular products, and conformal
  weights
  \[
    \operatorname{wt}(Z_1)=0,\qquad
    \operatorname{wt}(Z_2)=1,\qquad
    \operatorname{wt}(c)=0,\qquad
    \operatorname{wt}(b)=1.
  \]
  The finite-\(N\) gauge convention removes the scalar ghost or treats it
  as a decoupled acyclic factor, so that the effective reduction is the
  \(\mathfrak{sl}_N\) quantum Hamiltonian reduction.

  \emph{Reduced vertex data.} The free reduced Dirac vertex algebra has
  matrix-valued fields
  \[
    Z_1{}^i{}_j(z),\quad Z_2{}^i{}_j(z)
    \quad\text{even},\qquad
    c^i{}_j(z),\quad b^i{}_j(z)
    \quad\text{odd},
  \]
  with singular products
  \[
    Z_1{}^i{}_j(z)Z_2{}^k{}_\ell(w)
    \sim
    \frac{\hbar\,\delta^i_\ell\delta^k_j}{z-w},
    \qquad
    b^i{}_j(z)c^k{}_\ell(w)
    \sim
    \frac{\delta^i_\ell\delta^k_j}{z-w},
  \]
  all other generating singular products being regular.  The BRST
  current and residue operator are
  \[
    j_{\mathrm{BRST}}
    =
    \operatorname{Tr}(c[Z_1,Z_2])
    +\frac12\operatorname{Tr}(b[c,c]),
    \qquad
    Q_{\mathrm{BRST}}=\operatorname{Res}j_{\mathrm{BRST}}(z)\,dz .
  \]
  They give
  \[
    QZ_a=[c,Z_a],\qquad
    Qc=\frac12[c,c],\qquad
    Qb=[Z_1,Z_2]+[b,c].
  \]
  The square-zero check is the finite BRST Jacobi computation:
  \(Q[Z_1,Z_2]=[c,[Z_1,Z_2]]\), and hence
  \(Q^2Z_a=Q^2c=Q^2b=0\) after the displayed anomaly convention is
  included.

  \emph{Zero modes and Zhu relation.} With
  \[
    \phi_a=Z_{a,0},\qquad \psi=b_0,
  \]
  the gauge-invariant Koszul zero-mode sector recovers
  \[
    Q\phi_1=Q\phi_2=0,\qquad Q\psi=[\phi_1,\phi_2].
  \]
  For Zhu zero modes \(o(a)=a_{\operatorname{wt}(a)-1}\), use the
  transpose-compatible convention
  \[
    X^j{}_i=o(Z_1{}^i{}_j),\qquad
    Y^j{}_i=o(Z_2{}^i{}_j),\qquad
    C^j{}_i=o(c^i{}_j),\qquad
    B^j{}_i=o(b^i{}_j).
  \]
  Then
  \[
    [Y^j{}_i,X^\ell{}_k]
    =
    \hbar\,\delta^\ell_i\delta^j_k,\qquad
    [B^j{}_i,C^\ell{}_k]_{\mathrm{super}}
    =
    \delta^\ell_i\delta^j_k.
  \]
  The pre-BRST Zhu algebra is
  \[
    W_\hbar(\operatorname{Mat}_N^2)
    \otimes
    \operatorname{Cliff}_{bc}(\mathfrak{gl}_N),
  \]
  and the Zhu BRST differential is
  \[
    QX=[C,X],\qquad QY=[C,Y],\qquad
    QC=\frac12[C,C],
  \]
  \[
    QB=YX-XY+\hbar N I+[B,C].
  \]
  The term \(\hbar N I\) is the Capelli contact shift; omitting it
  contradicts the Weyl/Moyal normalization of
  Statement~\ref{thm:lane-moyal-degree-zero}.  In degree zero the target
  is therefore the BRST quantum Hamiltonian reduction with moment
  relation
  \[
    YX-XY+\hbar N I=0.
  \]

  \emph{Comparison chain.} The admissible bridge is the typed chain
  available only after the reduction and vertex data above are supplied:
  \[
    \operatorname{ChirHoch}^\bullet(V_N^{\mathrm{Dir}})
    \longrightarrow
    HH^\bullet(A(V_N^{\mathrm{Dir}}))
    \longrightarrow_{\operatorname{gr}_{\hbar=0},\,N\to\infty}
    HH^\bullet(A_{\mathrm{cl,st}})
  \]
  \[
    \longrightarrow_{\mathrm{HKR}}
    \mathrm{PV}^\bullet(\widehat S(\mathfrak h_{\mathrm{red}}))
    \longrightarrow
    C_{\mathrm{CE}}^\bullet
    (\mathfrak h_{\mathrm{red}}\ltimes\mathcal P_{\mathrm{red}}[1]).
  \]
  It is not a finite-\(N\), finite-\(\hbar\) quasi-isomorphism.  The Zhu
  bridge requires the vertex hypotheses above; HKR is classical,
  completed, and stable; and the final CE/PV comparison uses the
  admissible retained-\(z_2\) Hamiltonian completion.

  \emph{Scope and residuals.} The reduced BRST/Zhu package still requires
  the analytic reduction theorem, the conformal vector and weight proof,
  the residue normalization giving the OPE coefficient \(\hbar\), the
  anomaly homotopy matching the scalar branch, and continuous HKR in the
  chosen completed stable algebra.  Until then it is a typed theorem
  surface, not a native conclusion.
\end{stmt}

\begin{stmt}[Statement: constructed chiral algebra interface]\label{thm:lane-constructed-chiral-interface}
  \emph{Status.} \emph{theorem-surface-with-missing-construction after
  controlled reduction; false transfer before it}.  A constructed curve
  chiral algebra enters the present local mixed HT theory only as the
  vertex factor \(V_{\mathrm{red}}\) in the interface
  \[
    \mathfrak I_{\mathrm{ch}}
    =
    (\mathcal R_{\C\times\R},
     \mathcal F_{\mathrm{red}},
     V_{\mathrm{red}},
     Q_{\mathrm{BRST}},
     \mathbf 1,T,Y,\operatorname{wt},
     \zeta_\hbar,H_{\mathrm{anom}}).
  \]
  Here \(\mathcal R_{\C\times\R}\) is the retained-mode reduction of
  Statement~\ref{thm:lane-controlled-cxr-reduction}; it keeps
  \(\mathfrak h_{\mathrm{red}}=\C[[z_1]][[z_2]]/\C\cdot1\) and the full
  two-index principal-part module \(\mathcal P_{\mathrm{red}}\).
  \(\mathcal F_{\mathrm{red}}\) is the pushed-forward factorization
  algebra on \(\R_t\times\C_{z_1}\) with this retained coefficient
  system; before the reduction obstruction vanishes it is a theorem
  target, not native data.  Thus
  the chiral algebra is a reduced shadow of
  \(\mathcal F_{\mathrm{Ham}}^{\mathrm{hol}}\), not the native
  \(\C^2\) holomorphic \(E_2\) object.

  The vertex component must construct finite Laurent singular products,
  vacuum, translation, locality, conformal weights, and a BRST operator
  \(Q_{\mathrm{BRST}}\) with \(Q_{\mathrm{BRST}}^2=0\) after the selected
  scalar anomaly branch.  The Zhu component is a continuous zero-mode map
  \[
    \zeta_\hbar\colon(\bar A_\hbar,*)\longrightarrow
    \operatorname{Zhu}(V_{\mathrm{red}})
  \]
  compatible with the Weyl/Moyal product, the Capelli shift
  \(\hbar NI\), and the principal-part action
  \[
    [J_{f,(0)},\Theta_\rho]
    =
    \Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}.
  \]
  The exact obstruction vector is
  \[
    \operatorname{Ob}_{\mathfrak I_{\mathrm{ch}}}
    =
    (\operatorname{Ob}_{\mathrm{red}},
     \operatorname{Ob}_{\mathrm{vert}},
     \operatorname{Ob}_{\mathrm{Zhu}},
     \operatorname{Ob}_{\mathrm{nat}}).
  \]
  The entries record, respectively, the \(s,z_2\) pushforward, BV
  pairing, factorization, brane image, anomaly and Moyal compatibility;
  the factorization-to-vertex and BRST data; the zero-mode/Zhu
  multiplicativity and Capelli/HKR comparison; and the comparison back to
  the native \(\C^2\) factorization source.  Vanishing of this vector is
  the admission theorem for the constructed chiral algebra.
\end{stmt}

\paragraph{Cochain-level CE/PV--Koszul block.}

\begin{defn}[Cotangent CE/PV datum]\label{defn:cotangent-ce-pv-datum}
  A cotangent CE/PV datum is a Lie algebra \(\mathfrak l\) in a
  complete linear category, a continuous dual module
  \(\mathfrak l^\vee\), and the shifted cotangent Lie algebra
	  \[
	    T^*[1]\mathfrak l=\mathfrak l\ltimes\mathfrak l^\vee[1],
	    \qquad
	    [x,\lambda[1]]=(x\cdot\lambda)[1],\quad
	    [\lambda[1],\mu[1]]=0 .
	  \]
  The dual action is the coadjoint action:
  \[
    (x\cdot\lambda)(y)=-\lambda([x,y]).
  \]
  Choose a basis \(e_i\) of \(\mathfrak l\), dual basis
  \(\epsilon^i\), and structure constants
  \([e_i,e_j]=C^k_{ij}e_k\).  The CE coordinates are \(c^i\), dual to
  \(e_i\), and \(u_i\), dual to \(\epsilon^i[1]\), with
  \[
    |c^i|=1,\qquad |u_i|=0 .
  \]
  This is the cotangent-coordinate grading: \(u_i\) is the
  CE-suspended coordinate dual to the odd cotangent generator, not the
  ordinary graded dual computed from the BV degree of \(\epsilon^i[1]\).
  The polyvector model is
  \[
    \mathrm{PV}\bigl(\mathbf S(\mathfrak l)\bigr)
    =
    \mathbf S(O_i)\otimes\Lambda(\theta^i),
    \qquad |O_i|=0,\quad |\theta^i|=1,
  \]
  equipped with the Lichnerowicz differential for the linear Poisson
  tensor
  \[
    \pi=\frac12 C^k_{ij}O_k\theta^i\theta^j .
  \]
  The completed version is obtained by replacing tensor, symmetric, and
  exterior powers by their continuous completed analogues.
\end{defn}

\begin{thm}[Finite cotangent CE/PV identity]\label{thm:finite-cotangent-ce-pv-identity}
  Let \(\mathfrak l\) be finite-dimensional.  In the notation of
  Definition~\ref{defn:cotangent-ce-pv-datum}, the assignment
  \[
    \Phi(c^i)=\theta^i,\qquad \Phi(u_i)=O_i
  \]
  extends uniquely to an isomorphism of dg graded-commutative algebras
  with their degree-\((-1)\) cotangent/Schouten brackets
  \[
    \Phi\colon
    C^\bullet_{\mathrm{CE}}\bigl(\mathfrak l\ltimes\mathfrak l^\vee[1]\bigr)
    \xrightarrow{\ \sim\ }
    \mathrm{PV}\bigl(\mathbf S(\mathfrak l)\bigr).
  \]
  The differentials are
  \[
    d_{\mathrm{CE}}c^k=-\frac12 C^k_{ij}c^ic^j,\qquad
    d_{\mathrm{CE}}u_k=C^\ell_{kj}u_\ell c^j,
  \]
  and
  \[
    d_\pi\theta^k=-\frac12 C^k_{ij}\theta^i\theta^j,\qquad
    d_\pi O_k=C^\ell_{kj}O_\ell\theta^j.
  \]
\end{thm}

\begin{proof}
  The underlying graded algebras are freely generated by the same even
  and odd coordinate sets after the displayed substitution.  Hence
  \(\Phi\) is an isomorphism of graded-commutative algebras.

  The CE formula for \(c^k\) is the ordinary Chevalley--Eilenberg
  differential dual to \([e_i,e_j]=C^k_{ij}e_k\).  The formula for \(u_k\)
  is the dual of the coadjoint action in the semidirect product:
  \([e_k,e_j]=C^\ell_{kj}e_\ell\) makes \(e_j\) act on the coordinate
  \(u_k\) by \(C^\ell_{kj}u_\ell\).  On the PV side,
  \(d_\pi=[\pi,-]_S\) and the Schouten identities
  \[
    [\theta^i,O_k]_S=\delta^i_k,\qquad
    [\theta^i,\theta^j]_S=[O_i,O_j]_S=0
  \]
  give exactly the two displayed Lichnerowicz formulas.  Thus
  \(\Phi d_{\mathrm{CE}}=d_\pi\Phi\) on generators.  Both differentials
  are degree-one derivations, so equality propagates to all words.

  The degree-\((-1)\) cotangent/Schouten brackets are also checked on
  generators:
  \[
    \{c^i,u_j\}_{\mathrm{CE}}=\delta^i_j,\qquad
    [\theta^i,O_j]_S=\delta^i_j,
  \]
  with all \(c,c\), \(u,u\), \(\theta,\theta\), and \(O,O\) brackets
  equal to zero.  The biderivation rule gives the full bracket identity.
  The square-zero check on the cotangent coordinate is the coadjoint
  representation identity in coordinates:
  \[
    d_{\mathrm{CE}}^2u_k
    =
    C^\ell_{kj}C^m_{\ell r}u_m c^r c^j
    -\frac12 C^\ell_{kj}C^j_{rs}u_\ell c^r c^s
    =0,
  \]
  because
  \([\operatorname{ad}^{\vee}_{e_r},\operatorname{ad}^{\vee}_{e_s}]
    =\operatorname{ad}^{\vee}_{[e_r,e_s]}\).
\end{proof}

\begin{defn}[Formal-disk coordinate CE/PV completion]\label{defn:formal-disk-ce-pv-completion}
  Let \(H_d=\operatorname{Span}\{z_1^az_2^b:a+b=d\}\) and
  \[
    \mathfrak h=\prod_{d\geq1}H_d=(z_1,z_2)\C[[z_1,z_2]] .
  \]
  Its continuous dual is
  \(\mathfrak h^\vee_{\mathrm{cont}}=\bigoplus_{d\geq1}H_d^\vee\).
  Write \(c^{a,b}\) for the CE coordinate dual to
  \(H_{a,b}=z_1^az_2^b\), and \(u_{a,b}\) for the CE coordinate dual to
  the shifted cotangent generator \((H_{a,b})^\vee[1]\).  When
  \(I=(a,b)\) with \(a+b>0\), write
  \[
    H_I=z_1^az_2^b,\qquad
    \eta^I=(H_I)^\vee[1]\in\mathfrak h^\vee_{\mathrm{cont}}[1].
  \]

  For \(M,L\geq0\), let \(\mathcal B_{M,L}^{\mathrm{CE}}\) be the
  finite set of graded-commutative monomials in the letters
  \(u_{a,b},c^{a,b}\) of word length at most \(L\), all of whose labels
  satisfy \(1\leq a+b\leq M\).  The coordinate product algebra used here
  is the product over all finite words, equivalently the inverse limit of
  finite coordinate projections
  \[
    C^\bullet_{\mathrm{CE},\mathrm{coord}}(\mathfrak g)
    :=
    \widehat{\mathbf S}_{\mathrm{coord}}
    \bigl(\mathfrak g^\vee_{\mathrm{cont}}[-1]\bigr)
    =
    \varprojlim_{M,L}\prod_{w\in\mathcal B_{M,L}^{\mathrm{CE}}}\C w ,
    \qquad
    \mathfrak g=\mathfrak h\ltimes
      \mathfrak h^\vee_{\mathrm{cont}}[1].
  \]
	  The PV completion is defined by the same rule with \(u_{a,b}\)
	  replaced by \(O_{a,b}\) and \(c^{a,b}\) by \(\theta^{a,b}\):
	  \[
	    A_{\partial,\mathrm{coord}}
	    :=\widehat{\mathbf S}_{\mathrm{coord}}(\mathfrak h),
	    \qquad
	    \mathrm{PV}_{\mathrm{coord}}(\mathfrak h)
	    =
	    \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})
	    :=
	    \widehat{\mathbf S}_{\mathrm{coord}}(O_{a,b})
	    \widehat\otimes
    \widehat\Lambda_{\mathrm{coord}}(\theta^{a,b}).
  \]
	  These product algebras are coordinate enlargements.  They strictly
  contain the literal continuous CE cochains: for example an infinite
  length-one sum in the \(c^{a,b}\)-coordinates is a vector in the
  coordinate product but not a continuous linear functional on
  \(\mathfrak h=\prod_d H_d\).  A genuine completed \(P_0\)-object is the
  mixed continuous subspace in which the \(c/\theta\)-linear directions
  have continuous-dual support and the contraction pairing is a
  continuous biderivation.  Without this mixed condition the construction
	  is only an ambient pro-coordinate product.  The projections are finite
	  coordinate tests for the displayed differential formulas, not
	  Lie-algebra quotients of the full formal Hamiltonian algebra.
  A map out of either coordinate product is \emph{coordinate-continuous}
  when every output coefficient depends on finitely many input
  coefficients after projection to any finite set of word labels.
  Multiplication is defined by the usual finite decompositions of a fixed
  output word into two subwords; hence each output coefficient of a
  product is a finite sum.  The infinite behavior enters through the
  differential and contraction formulas, where coordinate-continuity or
  bracket-admissibility is the required summability condition.
		\end{defn}

\begin{defn}[Bracket- and kernel-admissible CE/PV realizations]\label{defn:bracket-kernel-admissible}
  Let \(A_{\partial,\mathrm{coord}}\) and
  \(\mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) be as in
  Definition~\ref{defn:formal-disk-ce-pv-completion}.  A
  \emph{bracket-admissible realization} is a complete Hausdorff
  topological subalgebra
  \(i_B\colon B\hookrightarrow
  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) with
  continuous inclusion such that multiplication
  \(B\widehat\otimes B\to B\), the restricted differential
  \(d_\pi^{\mathrm{coord}}\colon B\to B\), and the Schouten contraction
  bracket \(B\widehat\otimes B\to B[-1]\) are continuous.  The source
  \(\Phi_{\mathrm{coord}}^{-1}(B)\) is given the pullback topology; it is
  required to be closed under \(d_{\mathrm{CE}}\), multiplication, and the
  transported cotangent bracket, with these operations continuous.  For
  such \(B\), write
  \[
    \Phi^B_{P_0}\colon
    \Phi_{\mathrm{coord}}^{-1}(B)\xrightarrow{\sim}B
  \]
  for the restricted completed dg \(P_0\)-map.

  If \(S\subset\mathfrak h\) is a class of Hamiltonians, \(B\) is
  \emph{\(S\)-Hamiltonian-spanning} if \(O_f\in B\) and
  \(d_\pi^{\mathrm{coord}}O_f\in B\) for every \(f\in S\).  Boundary
  Hamiltonian statements inside \(\Phi^B_{P_0}\) are made only for such
  \(f\).

  A \emph{kernel-admissible datum} is a bracket-admissible \(B\) together
  with a specified completed tensor product, hence a completed
  convolution dg Lie algebra \(\mathcal K_B\), in which the diagonal sums
  \[
    \sum_I H_I\otimes\theta^I,\qquad
    \sum_I \eta^I\otimes O_I
  \]
  converge and the differential and convolution bracket are continuous.
  In that case set, as an element of \(\mathcal K_B\),
  \[
    \Theta_B=\sum_I H_I\otimes\theta^I+\sum_I\eta^I\otimes O_I .
  \]
  The strict ambient product/direct-sum completion is not
  kernel-admissible unless this diagonal convergence is supplied as
  additional structure.

	  The finite-support subalgebra \(B_{\mathrm{fin}}\) is a finite-test
	  model in every finite coordinate window; it is not a global
	  bracket-admissible \(B\) for the full formal disk unless the chosen
	  completion is also stable under the infinite coadjoint differential.
	  For \(q>1\) the weighted rapidly decreasing test target \(E_q\) is defined by the
	  seminorms
  \[
    p_n(x)=
    \sup_{a,b}\,|x_{a,b}|\,q^{a+b}(1+a+b)^n,\qquad n\geq0,
  \]
  and by the analogous finite-word seminorms on polyvectors.  The
	  monomial estimate
  \[
    |ad-bc|\leq (a+b)(c+d)
  \]
	  is only the first local convolution bound needed to absorb the
	  Poisson structure constants into the polynomial factor of the
	  seminorms.  Thus a Köthe completion built from these seminorms is a
	  candidate bracket-admissible \(B\) only after the chosen finite-word
	  tensor convention proves multiplication, the coordinate differential,
	  and the Schouten contraction continuous; it is kernel-admissible only
	  if the two diagonal sums above converge in that completed tensor
	  product.
\end{defn}

\begin{lem}[Formal-disk coordinate differential formulas]\label{lem:formal-disk-ce-schouten-continuity}
  In the coordinate product completion of
  Definition~\ref{defn:formal-disk-ce-pv-completion}, the formulas
  \[
    [H_{a,b},H_{c,d}]=(ad-bc)H_{a+c-1,b+d-1}
  \]
  with \(H_{r,s}=0\) for \(r<0\), \(s<0\), or \(r+s=0\), determine
  degree-one coordinate-continuous derivations
  \(d_{\mathrm{CE}}\) and \(d_\pi^{\mathrm{coord}}\), and these derivations
  satisfy \(d_{\mathrm{CE}}^2=(d_\pi^{\mathrm{coord}})^2=0\).  On generators,
  \[
    d_{\mathrm{CE}}c^{r,s}
      =
      -\frac12
      \sum_{\substack{a+c-1=r\\ b+d-1=s}}
      (ad-bc)c^{a,b}c^{c,d},
  \]
  \[
    d_{\mathrm{CE}}u_{r,s}
      =
      \sum_{c,d}
      (rd-sc)\,
      u_{r+c-1,s+d-1}c^{c,d},
  \]
    and the coordinate PV differential \(d_\pi^{\mathrm{coord}}\) has the identical formulas after
  \(c^{a,b}\mapsto\theta^{a,b}\) and \(u_{a,b}\mapsto O_{a,b}\).
  Terms whose output label is the reduced constant \(H_{0,0}\) are
  omitted.
\end{lem}

\begin{proof}
  For \(d_{\mathrm{CE}}c^{r,s}\), the equations
  \(a+c-1=r\) and \(b+d-1=s\) have finitely many non-negative
  solutions, hence the displayed sum is finite.

  The coadjoint term \(d_{\mathrm{CE}}u_{r,s}\) is infinite before
  projection.  Its projection to the finite coordinate window
  \(\mathcal B_{M,L}^{\mathrm{CE}}\) keeps only terms with
  \(c+d\leq M\) and \(r+s+c+d-2\leq M\).  There are finitely many such
  pairs \((c,d)\).  The word length increases by one, so the length
  projection is finite as well.  Thus every finite coordinate
  projection of \(d_{\mathrm{CE}}u_{r,s}\) is finite, which is exactly
  continuity in the product topology.

  A completed monomial has finite word length before passage to the
  product completion, so the derivation rule applies to finitely many
  factors.  Continuity extends the derivation uniquely to arbitrary
  products over the finite-word basis.  The PV coordinate formulas have
  the same coefficient support, with \(O,\theta\) in place of \(u,c\), so
  the same argument proves continuity of \(d_\pi^{\mathrm{coord}}\).

  The square-zero assertions are checked before completion and then
  extended by continuity.  The CE formulas are the continuous dual of the
  genuine Hamiltonian Lie bracket on
  \(\C[[z_1,z_2]]/\C\cdot1\), equivalently on the zero-constant
  representatives \((z_1,z_2)\C[[z_1,z_2]]\), whose Jacobi identity gives
  \(d_{\mathrm{CE}}^2c^{r,s}=0\).  On the cotangent coordinates,
  \[
    d_{\mathrm{CE}}^2u_{r,s}
    =
    C^L_{(r,s)J}C^M_{LR}u_Mc^Rc^J
    -\frac12 C^L_{(r,s)J}C^J_{RS}u_Lc^Rc^S
    =0,
  \]
  where the constants \(C^K_{IJ}\) are those of
  \([H_I,H_J]=C^K_{IJ}H_K\), and the equality is exactly
  \([\operatorname{ad}^{\vee}_{H_R},\operatorname{ad}^{\vee}_{H_S}]
    =\operatorname{ad}^{\vee}_{[H_R,H_S]}\).
  On the PV side the displayed coordinate formulas define a derivation
  \(d_\pi^{\mathrm{coord}}\); its square on generators is the same Jacobi
  and coadjoint identity with \(O,\theta\) replacing \(u,c\).  This avoids
  asserting that the infinite
  linear Poisson bivector is a globally summable Schouten element in the
  strict ambient product.  Since both differentials are continuous
  coordinate derivations, generator-level square-zero implies
  square-zero on the completed coordinate product algebras.
\end{proof}

\begin{thm}[Coordinate formal-disk CE/PV theorem and admissible \(P_0\) realizations]\label{thm:formal-disk-completed-ce-pv}
  Let
  \[
    \mathfrak h=\C[[z_1,z_2]]/\C\cdot1
      \cong (z_1,z_2)\C[[z_1,z_2]]
  \]
  where the isomorphism chooses the zero-constant representative, with
  the projected Poisson bracket modulo constants
  \[
    \{f,g\}=\partial_{z_1}f\,\partial_{z_2}g
      -\partial_{z_2}f\,\partial_{z_1}g .
  \]
  Complete the coordinate CE and PV algebras as in
  Definition~\ref{defn:formal-disk-ce-pv-completion}.  Then
  \[
	    \Phi_{\mathrm{coord}}\colon
	    C^\bullet_{\mathrm{CE},\mathrm{coord}}
	    \bigl(\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1]\bigr)
    \xrightarrow{\ \sim\ }
    \mathrm{PV}_{\mathrm{coord}}(\mathfrak h),
    \qquad
    c^{a,b}\mapsto\theta^{a,b},\quad u_{a,b}\mapsto O_{a,b},
	  \]
	  is an isomorphism of completed coordinate dg commutative algebras.
	  If \(B\subset
	  \mathrm{PV}_{\mathrm{coord}}(A_{\partial,\mathrm{coord}})\) is
	  bracket-admissible in the sense of
	  Definition~\ref{defn:bracket-kernel-admissible}, then
	  \[
	    \Phi^B_{P_0}\colon\Phi_{\mathrm{coord}}^{-1}(B)
	    \xrightarrow{\sim}B
	  \]
	  is an isomorphism of completed dg \(P_0\)-algebras.  If \(B\) is
	  kernel-admissible as part of a datum \((B,\mathcal K_B)\), then the
	  diagonal element
	  \[
	    \Theta_B=\sum_I H_I\otimes\theta^I+\sum_I\eta^I\otimes O_I
	  \]
	  satisfies the Maurer--Cartan equation
	  \(d\Theta_B+\frac12[\Theta_B,\Theta_B]=0\) in \(\mathcal K_B\).  The
	  full product
	  coordinate algebra is not asserted to carry the global continuous
	  contraction bracket or a strict kernel; the missing infinite diagonal
	  is the strict Casimir obstruction of
	  Theorem~\ref{thm:lane-strict-casimir-obstruction}.  The admissible
	  formal-local interface is
	  \[
	    \mathfrak U_{\mathfrak h}
	    =(\Phi_{\mathrm{coord}},\{\Phi^B_{P_0}\}_B,\{\Theta_B\}_B),
	  \]
	  with \(B\) ranging over bracket-admissible realizations in the middle
	  term and kernel-admissible data in the last term.  At the coordinate
	  dg-algebra level, and inside \(\Phi^B_{P_0}\) for every
	  Hamiltonian-spanning \(B\), the stable boundary evaluation of
	  Theorem~\ref{thm:bulk-boundary} sends the degree-zero cotangent
	  coordinate \(u_f\) to the boundary Hamiltonian
  \[
    B_f=\overline{\operatorname{Tr}f(\phi_1,\phi_2)} ,
  \]
  while \(c^f\) maps to the Hamiltonian vector field of \(B_f\).  This
  is the cochain-level bulk-boundary Koszul shadow; it does not use
  lower-central Tate-pronilpotence of the full Hamiltonian Lie algebra.
\end{thm}

\begin{proof}
	  The completed coordinate source and target are products over the same
	  finite-word coordinate set after the substitutions
		  \(c^{a,b}\leftrightarrow\theta^{a,b}\) and
		  \(u_{a,b}\leftrightarrow O_{a,b}\).  Hence
	  \(\Phi_{\mathrm{coord}}\) is a continuous
  isomorphism of completed graded-commutative algebras, with continuous
  inverse given by the reverse substitution.

  Lemma~\ref{lem:formal-disk-ce-schouten-continuity} gives
  coordinate-continuous
  derivations \(d_{\mathrm{CE}}\) and \(d_\pi^{\mathrm{coord}}\).  On the generators
  \(c^{r,s}\) and \(u_{r,s}\), the displayed CE formulas are the duals
  of the Hamiltonian bracket and coadjoint action in
  \(\mathfrak h\ltimes\mathfrak h^\vee_{\mathrm{cont}}[1]\).  The
  PV coordinate formulas are the coefficientwise Lichnerowicz formulas
  for the linear Poisson tensor
  \[
    \pi=\frac12 C^K_{IJ}O_K\theta^I\theta^J .
  \]
	  Therefore \(\Phi_{\mathrm{coord}} d_{\mathrm{CE}}=d_\pi^{\mathrm{coord}}\Phi_{\mathrm{coord}}\) on \(c^{r,s}\) and
	  \(u_{r,s}\).  Both sides are continuous degree-one derivations, so the
  equality extends from generators to every finite word and then, by the
  product completion, to the whole completed algebra.

	  On the finite-support mixed subalgebra the cotangent/Schouten bracket is
  checked on generators:
  \[
    \{c^{a,b},u_{r,s}\}_{\mathrm{CE}}
      =\delta_{a,r}\delta_{b,s},
    \qquad
    [\theta^{a,b},O_{r,s}]_S
      =\delta_{a,r}\delta_{b,s},
  \]
  and all \(c,c\), \(u,u\), \(\theta,\theta\), and \(O,O\) brackets
  vanish.  This gives bracket compatibility on finite words and on any
  mixed topology in which the \(c/\theta\)-directions have finite label
  support.  It does not extend to the arbitrary product completion: the
  bracket of \(\sum_I c^I\) with \(\sum_I u_I\), which are both admitted
  by the coordinate product, would require the divergent diagonal
  coefficient \(\sum_I1\).  Thus the full product statement above is a
	  dg coordinate reconstruction, not a global completed \(P_0\)-algebra
	  theorem.

	  If \(B\) is bracket-admissible, the preceding generator calculation
	  restricts to \(B\), and all infinite contractions that occur in the
	  \(P_0\) bracket converge by definition of \(B\).  Hence the restricted
	  map \(\Phi^B_{P_0}\) is a completed dg \(P_0\)-isomorphism.  If \(B\)
	  is kernel-admissible, the two diagonal sums defining \(\Theta_B\)
	  converge in the specified convolution dg Lie algebra \(\mathcal K_B\).
	  The Maurer--Cartan equation is
	  then checked coefficientwise in the completed convolution complex:
	  every requested coefficient sees only the finitely many labels
	  contributing to that coefficient, and the equality is exactly the
	  Jacobi and coadjoint identity in the full Hamiltonian Lie algebra.
	  Convergence in \(B\) passes these coefficient identities to the
	  completed tensor product.  No finite coordinate window is being used
	  as a Hamiltonian Lie quotient.  Without diagonal
	  convergence this sentence has no target object, which is precisely the
	  strict Casimir obstruction.

		  The coordinate moment-map shadow is the restriction of
	  \(\Phi_{\mathrm{coord}}\) to the cotangent
  coordinates: \(u_f\mapsto O_f\).  The Kirillov--Poisson bracket gives
  \(\{O_f,O_g\}=O_{\{f,g\}}\).  Theorem~\ref{thm:bulk-boundary} sends
  \(O_f\) to
  \(\overline{\operatorname{Tr}f(\phi_1,\phi_2)}\) and preserves the
  Hamiltonian bracket in the stable connected sector.  Inside a
  bracket-admissible \(P_0\)-realization this sentence applies only for
  the \(f\)'s in the Hamiltonian-spanning set of \(B\).  Thus \(u_f\) is
  the bulk source of the boundary Hamiltonian, while \(c^f\mapsto\theta^f\)
  records the corresponding Hamiltonian vector field.
\end{proof}

\begin{stmt}[Statement: equivariant CE/PV refined bracket]\label{thm:lane-equivariant-ce-pv-refined-bracket}
  \emph{Status.} \emph{proved as a coordinate dg-algebra formula after
  adjoining the symplectic-character parameter; bracketed, kernel, QME,
  and physical-trace upgrades remain obstruction data}.  This is the
  \(T_\Omega\)-equivariant refinement of
  Theorem~\ref{thm:formal-disk-completed-ce-pv}.

  \emph{Exact hypotheses.} Let
  \[
    T_\Omega=\C^*_{\epsilon_s}\times
    \C^*_{\epsilon_1}\times\C^*_{\epsilon_2},
    \qquad
    \chi_\omega=\epsilon_1+\epsilon_2 .
  \]
  Put \(w(z_i)=\epsilon_i\), so
  \(w(dz_1\wedge dz_2)=\chi_\omega\) and the Poisson tensor has weight
  \(-\chi_\omega\).  For \(H_{a,b}=z_1^az_2^b\), \(a+b>0\), set
  \(W_{a,b}=a\epsilon_1+b\epsilon_2\).  Then
  \[
    w(H_{a,b})=W_{a,b},\qquad
    w(\rho_{a,b})=-W_{a,b}.
  \]
  The coordinate-dual weights are
  \[
    w(c^{a,b})=w(\theta^{a,b})=-W_{a,b},
    \qquad
    w(u_{a,b})=w(O_{a,b})=W_{a,b}.
  \]
  The second equality is load-bearing: \(u_{a,b}\) is dual to the
  shifted cotangent generator, not itself a cotangent generator.

  \emph{Refined bracket.} Off the self-dual locus, the ordinary Poisson
  bracket is line-valued:
  \[
    \{-,-\}\colon
    \wedge^2\mathfrak h\longrightarrow
    \mathfrak h\otimes L_\omega^{-1}.
  \]
  Equivalently, after adjoining a central parameter
  \(\hbar_\omega\) of weight \(\chi_\omega\), one uses the scalar
  bracket
  \[
    [f,g]_\Omega=\hbar_\omega\{f,g\}.
  \]
  In monomial notation,
  \[
    [H_I,H_J]_\Omega
    =
    \hbar_\omega C^K_{IJ}H_K,
    \qquad
    C^{I+J-(1,1)}_{IJ}=ad-bc
  \]
  for \(I=(a,b)\), \(J=(c,d)\).  This is weight-homogeneous because
  \(W_K+\chi_\omega=W_I+W_J\).  Jacobi is inherited from the ordinary
  Poisson bracket since \(\hbar_\omega\) is central.

  \emph{Coordinate CE/PV assertion.} In the coordinate completion of
  Definition~\ref{defn:formal-disk-ce-pv-completion}, define
  \[
    d_{\mathrm{CE},\Omega}c^K
    =
    -\frac12\hbar_\omega C^K_{IJ}c^Ic^J,
    \qquad
    d_{\mathrm{CE},\Omega}u_K
    =
    \hbar_\omega C^L_{KJ}u_Lc^J.
  \]
  Equivalently,
  \[
    d_{\mathrm{CE},\Omega}c^{r,s}
    =
    -\frac12\hbar_\omega
    \sum_{\substack{a+c-1=r\\ b+d-1=s}}
    (ad-bc)c^{a,b}c^{c,d},
  \]
  and
  \[
    d_{\mathrm{CE},\Omega}u_{r,s}
    =
    \hbar_\omega
    \sum_{c,d}(rd-sc)
    u_{r+c-1,s+d-1}c^{c,d},
  \]
  omitting negative labels and the reduced constant.  On the PV side set
  \[
    \pi_\Omega
    =
    \frac12\hbar_\omega C^K_{IJ}O_K\theta^I\theta^J .
  \]
  Then
  \[
    d_{\pi,\Omega}\theta^K
    =
    -\frac12\hbar_\omega C^K_{IJ}\theta^I\theta^J,
    \qquad
    d_{\pi,\Omega}O_K
    =
    \hbar_\omega C^L_{KJ}O_L\theta^J.
  \]
  The generator assignment
  \[
    \Phi_\Omega(c^{a,b})=\theta^{a,b},\qquad
    \Phi_\Omega(u_{a,b})=O_{a,b}
  \]
  is \(T_\Omega\)-equivariant and satisfies
  \[
    \Phi_\Omega d_{\mathrm{CE},\Omega}
    =
    d_{\pi,\Omega}\Phi_\Omega
  \]
  on generators, hence on the completed coordinate dg algebra by the
  same finite-coordinate derivation argument as
  Theorem~\ref{thm:formal-disk-completed-ce-pv}.  The cotangent and
  Schouten contractions may either remain the unscaled cochain-level
  contractions or be scaled simultaneously by \(\hbar_\omega\):
  \[
    \{c^I,u_J\}_{\mathrm{CE},\Omega}
    =
    \hbar_\omega\delta^I_J,\qquad
    [\theta^I,O_J]_{S,\Omega}
    =
    \hbar_\omega\delta^I_J.
  \]
  The latter is the \(L_\omega\)-weighted \(P_0\) convention.

  \emph{Parameter convention.} The symbol \(\hbar_\omega\) is the
  equivariant scalarizer of the symplectic-character line.  The
  Weyl/Moyal deformation parameter and the BV/QME loop parameter are
  independent until a branch datum identifies them.  A Weyl-equivariant
  branch is a ring map sending \(\hbar_\omega\) to the Weyl parameter
  \(\hbar_{\mathrm{W}}\), with
  \[
    w(\hbar_{\mathrm{W}})=\epsilon_1+\epsilon_2 .
  \]
  The physical large-\(N\) branch uses
  \(\hbar_{\mathrm{W},N}=\lambda/N\).  It is not identified with the BV
  loop parameter \(\hbar_{\mathrm{QME}}\) unless that identification is
  included in the QME normalization datum.  Thus \(Q_\Omega\)-notation and
  the scalarizer \(\hbar_\omega\) do not by themselves solve any QME.

  \emph{Self-dual branch.} On
  \[
    \epsilon_1+\epsilon_2=0
  \]
  the Poisson tensor has weight zero.  The ordinary Hamiltonian bracket
  is scalar, and \(\hbar_\omega\) has weight zero; it may be retained as a
  central formal parameter or specialized to \(1\).  No theorem may
  invert \(\epsilon_1+\epsilon_2\) and then specialize to this branch.

  \emph{Obstruction boundary.} The coordinate dg formula above does not
  construct the mixed Cartan complex, a bracket-admissible global
  completion, diagonal kernel convergence, residue/Euler normalization,
  a Costello graph package, or a physical trace state.  The exact
  obstruction vector is
  \[
    \operatorname{Ob}_{\Omega,\mathrm{CE/PV}}
    =
    (\operatorname{ob}_{\Omega,\mathrm{Cartan}},
     \operatorname{ob}_{\Omega,\mathrm{top}},
     \operatorname{ob}_{\Omega,\mathrm{br}},
     \operatorname{ob}_{\Omega,\mathrm{diag}},
     \operatorname{ob}_{\Omega,\mathrm{res}},
     \operatorname{ob}_{\Omega,\mathrm{norm}},
     \operatorname{ob}_{\Omega,\mathrm{QME}}).
  \]
  The first term records \(Q_\Omega^2=L_{V_\Omega}\) before invariants;
  the middle terms record topology, biderivation, diagonal, resonance,
  and normalization data; and the last term records the separate
  brane-defect QME construction.
\end{stmt}

\begin{thm}[Abstract bracket-compatible CE/PV recognition criterion]\label{thm:universal-formal-local-ce-pv-recognition}
  Let \(L=\varprojlim_\alpha L_\alpha\) be a complete Hausdorff
  filtered dg Lie algebra over \(\C\), with finite-dimensional
  bracket-compatible dg Lie quotients \(L_\alpha\), and let
  \(D=L^\vee_{\mathrm{cont}}=\varinjlim_\alpha L_\alpha^\vee\).
  Put \(G=L\ltimes D[1]\).  Form the completed coordinate CE and PV
  algebras by taking products over finite words and finite coordinate
  windows.  Assume:
  \begin{enumerate}[label=(U\arabic*)]
    \item the internal differential, Lie bracket on \(L\), and
      coadjoint action on \(D\) are continuous, equivalently every
      finite coordinate projection of \(d_Lx\), \([x,y]\), and
      \(x\cdot\lambda\) factors through a finite Lie quotient of
      the inputs;
    \item the linear Poisson bivector
      \[
        \pi_L=\frac12 C^k_{ij}O_k\theta^i\theta^j
      \]
      determined by the structure constants of \(L\) is a continuous
      Schouten bivector on
      \(\widehat{\mathbf S}_{\mathrm{coord}}(L)\);
    \item the source cotangent bracket
      \(\{c^i,u_j\}_{\mathrm{CE}}=\delta^i_j\) and the target Schouten
      contraction bracket \([\theta^i,O_j]_S=\delta^i_j\) are continuous
      biderivations on the chosen mixed or weighted completion.  This is
      a summability hypothesis, not a consequence of the generator
      formula on the ambient product.
  \end{enumerate}
  Then the generator assignment
  \[
    \Phi_L\colon
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(G)
    \xrightarrow{\ \sim\ }
    \mathrm{PV}\bigl(\widehat{\mathbf S}_{\mathrm{coord}}(L)\bigr),
    \qquad
    c^i\mapsto\theta^i,\quad u_i\mapsto O_i,
  \]
  is an isomorphism of completed dg algebras with the degree-\((-1)\)
  cotangent/Schouten contraction bracket.  Without the summability
  condition in (U3), the conclusion is only the compatible pro
  finite-window dg-commutative CE/PV identity and the global contraction
  bracket is obstruction data.  This is a formal-local cochain theorem.
  It does not require lower-central Tate-pronilpotence and it does not assert
  that the coordinate pairing is represented by a strict kernel
  \(C_L\in L\widehat\otimes D\).
  The strict formal Hamiltonian disk is not an instance of this theorem
  unless such a bracket-compatible finite quotient system is supplied;
  for the disk itself one uses the coordinate finite-test theorem above.
\end{thm}

\begin{proof}
  The completed CE algebra of \(G=L\ltimes D[1]\) and the completed PV
  algebra of the linear formal space \(L\) are products over the same
  finite-word coordinate monomials after \(c^i\leftrightarrow\theta^i\)
  and \(u_i\leftrightarrow O_i\).  Thus \(\Phi_L\) is a continuous
  graded-commutative algebra isomorphism with continuous inverse.

  Assumption (U1) makes the CE differential continuous: every finite
  output coordinate of the internal differential, of
  \(d_{\mathrm{CE}}c^k\), and of \(d_{\mathrm{CE}}u_i\) is computed from
  finitely many input coordinates.  The internal differential is carried
  to the identical linear vector field on the PV side by the coordinate
  substitution.  Assumption (U2) makes \(d_{\pi_L}=[\pi_L,-]_S\) a
  continuous differential on the PV side.  On generators the bracket
  terms are the same structure-constant formulas:
  \[
    d_{\mathrm{CE}}c^k=-\frac12 C^k_{ij}c^ic^j,\qquad
    d_{\pi_L}\theta^k=-\frac12 C^k_{ij}\theta^i\theta^j,
  \]
  and
  \[
    d_{\mathrm{CE}}u_i=C^\ell_{ij}u_\ell c^j,\qquad
    d_{\pi_L}O_i=C^\ell_{ij}O_\ell\theta^j .
  \]
  Jacobi for \(L\) gives \(d_{\mathrm{CE}}^2=0\) and
  \([\pi_L,\pi_L]_S=0\), hence \(d_{\pi_L}^2=0\).  Since both
  differentials are continuous derivations, generator-level
  compatibility gives \(\Phi_Ld_{\mathrm{CE}}=d_{\pi_L}\Phi_L\) on the
  completed algebras.

  Assumption (U3) gives the same result for the contraction brackets:
  \[
    \{c^i,u_j\}_{\mathrm{CE}}=\delta^i_j
    \quad\text{and}\quad
    [\theta^i,O_j]_S=\delta^i_j
  \]
  on generators, with all same-type brackets zero.  Continuity and the
  biderivation rule extend this equality to finite words and then to the
  chosen mixed or weighted completion.  The last sentence records the
  boundary of the theorem: a strict Casimir kernel is stronger than the
  coordinate biderivation, while the unweighted ambient product may fail
  even to carry that biderivation globally.
\end{proof}

\begin{prop}[Shifted-cotangent coordinate is the boundary Hamiltonian]\label{prop:cotangent-coordinate-boundary-hamiltonian}
  In the completed formal-disk identity of
  Theorem~\ref{thm:formal-disk-completed-ce-pv}, the boundary Hamiltonian
  \(O_f\) is the image of the shifted-cotangent CE coordinate \(u_f\):
  \[
	    \Phi_{\mathrm{coord}}(u_f)=O_f.
  \]
  The Hamiltonian CE coordinate \(c^f\) maps to the vector-field
  generator \(\theta^f\), not to \(O_f\).  Equivalently,
  \[
	    d_\pi^{\mathrm{coord}} O_f=X_{O_f}=\Phi_{\mathrm{coord}}(d_{\mathrm{CE}}u_f).
  \]
  After stable boundary evaluation, \(O_f\) becomes
  \(\overline{\operatorname{Tr}f(\phi_1,\phi_2)}\), the moment-map
  shadow of the Hamiltonian \(f\) on the matrix probe.
\end{prop}

\begin{proof}
  This is the \(u\)-generator part of the defining formula for
  \(\Phi_{\mathrm{coord}}\).
  For \(f=H_k\), the CE differential is
  \(d_{\mathrm{CE}}u_k=C^\ell_{kj}u_\ell c^j\).  Applying
  \(\Phi_{\mathrm{coord}}\) gives
  \(C^\ell_{kj}O_\ell\theta^j\), which is exactly the Hamiltonian vector
	  field \(d_\pi^{\mathrm{coord}}O_k\); on a bracket-admissible \(B\) this
	  is the Schouten bracket \([\pi,O_k]_S\).  Thus the cotangent coordinate, not the
  Hamiltonian ghost coordinate, carries the boundary Hamiltonian.  The
  last assertion is Theorem~\ref{thm:bulk-boundary} applied to the
  degree-zero Kirillov map \(f\mapsto O_f\).
\end{proof}

\begin{thm}[Strict product/direct-sum Casimir obstruction]\label{thm:lane-strict-casimir-obstruction}
  Let
  \[
    \mathfrak h_\Pi=\prod_{d\geq1}H_d,\qquad
    D_\oplus=\bigoplus_{d\geq1}H_d^\vee
  \]
  be the strict product/direct-sum coefficient pair of the formal
  Hamiltonian disk.  There is no tensor
  \(K\in\mathfrak h_\Pi\widehat\otimes D_\oplus\) whose projection to
  every finite window \(d\leq M\) is the finite Casimir
  \[
    C_{\leq M}=\sum_{1\leq d\leq M}\sum_i e_{d,i}\otimes e^i_{d}.
  \]
  The same statement holds with tensor factors reversed.
\end{thm}

\begin{proof}
  In the strict tensor convention for the product/direct-sum Tate pair,
  an element of \(\mathfrak h_\Pi\widehat\otimes D_\oplus\) has finite
  support in the direct-sum factor \(D_\oplus\).  Thus there is a degree
  \(M_0\) such that all \(H_d^\vee\)-components of \(K\) vanish for
  \(d>M_0\).  Projecting to the window \(d\leq M_0+1\) then gives zero in
  the \(H_{M_0+1}\otimes H_{M_0+1}^\vee\) component, while
  \(C_{\leq M_0+1}\) has the nonzero identity tensor in that component.
  This contradiction proves the claim.  Reversing the tensor factors is
  identical.
\end{proof}

\begin{thm}[Primitive-label obstruction to Matlis cotangent-current equivariance]\label{thm:lane-one-psi-not-cotangent-current}
  Let \(V_\Psi\) be the span of primitive PBW special-fibre labels
  \(\widetilde\Psi_{a,b}\), \(a+b>0\), with the reduced scalar target
  killed and with the linear Hamiltonian action
  \[
    O_{1,0}\cdot\widetilde\Psi_{a,b}
      =b\,\widetilde\Psi_{a,b-1},\qquad
    O_{0,1}\cdot\widetilde\Psi_{a,b}
      =-a\,\widetilde\Psi_{a-1,b}.
  \]
  Let \(\mathcal P\) be the principal-part module with
  \[
    z_1\cdot\rho_{a,b}=-(b+1)\rho_{a,b+1},\qquad
    z_2\cdot\rho_{a,b}=(a+1)\rho_{a+1,b}.
  \]
  There is no \(\mathfrak h\)-module map
  \(F\colon V_\Psi\to\mathcal P\) satisfying
  \(F(\widetilde\Psi_{a,b})=\lambda_{a,b}\rho_{a,b}\) with all
  \(\lambda_{a,b}\neq0\).
\end{thm}

\begin{proof}
  Apply equivariance for \(z_1\) to \(\widetilde\Psi_{a,0}\), \(a>0\).  On the
  PBW special-fibre side,
  \(O_{1,0}\cdot\widetilde\Psi_{a,0}=0\).  Hence
  \(F(O_{1,0}\cdot\widetilde\Psi_{a,0})=0\).  On the principal-part side,
  \[
    z_1\cdot F(\widetilde\Psi_{a,0})
    =
    z_1\cdot(\lambda_{a,0}\rho_{a,0})
    =
    -\lambda_{a,0}\rho_{a,1},
  \]
  which is nonzero.  This contradicts equivariance.  The \(z_2\)-action
  gives the analogous contradiction at \(a=0\).
\end{proof}

\begin{prop}[Low-degree obstruction to a pronilpotent full-disk splitting]\label{prop:lane-low-degree-pronilpotent-obstruction}
  The subspace \(\mathfrak m^3\subset\mathfrak h=(z_1,z_2)\C[[z_1,z_2]]\)
  is not an ideal of the full reduced Hamiltonian Lie algebra
  \(\mathfrak h\).  Consequently the vector-space decomposition
  \[
    \mathfrak h=(H_1\oplus H_2)\oplus\mathfrak m^3,
    \qquad
    H_d=\operatorname{Span}\{z_1^az_2^b:a+b=d\},
  \]
  does not make \(\mathfrak h\) a semidirect product of the low-degree
  sector with a pronilpotent ideal.
\end{prop}

\begin{proof}
  The linear Hamiltonian \(z_1\in H_1\) lowers \(z_2^3\in\mathfrak m^3\):
  \[
    \{z_1,z_2^3\}=3z_2^2\in H_2.
  \]
  Since \(H_2\cap\mathfrak m^3=0\), the bracket does not lie in
  \(\mathfrak m^3\).  Thus \(\mathfrak m^3\) is not an ideal in
  \(\mathfrak h\).  A semidirect-product presentation with
  pronilpotent radical \(\mathfrak m^3\) would require that radical to
  be an ideal, so no such presentation exists.
\end{proof}

\begin{thm}[Relative filtered CE/PV reconstruction criterion]\label{thm:relative-filtered-koszul-lift}
  Let \(\mathfrak h_{\mathrm{rel}}\) be a complete filtered dg Lie algebra
  with a finite-dimensional reductive degree-zero subalgebra
  \(\mathfrak a\), a complete pronilpotent dg ideal \(\mathfrak n\), and
  a filtered splitting
  \[
    \mathfrak h_{\mathrm{rel}}\cong\mathfrak a\ltimes\mathfrak n .
  \]
  Let \(D_{\mathrm{rel}}\) be a continuous \(\mathfrak h_{\mathrm{rel}}\)-module
  with a perfect filtered pairing with \(\mathfrak h_{\mathrm{rel}}\) on
  every finite quotient, and assume the coevaluation tensor belongs to
  \(\mathfrak h_{\mathrm{rel}}\widehat\otimes D_{\mathrm{rel}}\).  Put
  \[
    \mathfrak g_{\mathrm{rel}}
      =\mathfrak h_{\mathrm{rel}}\ltimes D_{\mathrm{rel}}[1],
    \qquad
    A_{\mathrm{rel}}=\widehat{\mathbf S}(\mathfrak h_{\mathrm{rel}}).
  \]
  Then the generator assignment \(c\mapsto\theta\), \(u\mapsto O\)
  defines a filtered isomorphism
  \[
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{rel}})
    \xrightarrow{\ \sim\ }
    \mathrm{PV}(A_{\mathrm{rel}})
  \]
  of completed dg algebras with the degree-\((-1)\)
  cotangent/Schouten contraction bracket.  If, in addition, the relative
  bar-cobar functor is taken in the category of
  \(\mathfrak a\)-modules and the \(\mathfrak n\)-coalgebra is
  conilpotent, this cochain identity is promoted to relative
  Lie-Koszul duality:
  \[
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{rel}},\mathfrak a)
    \simeq
    \bigl(\widehat U_{\mathfrak a}(\mathfrak g_{\mathrm{rel}})\bigr)^!.
  \]
\end{thm}

\begin{proof}
  The cochain-level statement is the completed version of
  Theorem~\ref{thm:finite-cotangent-ce-pv-identity}: finite quotients of
  the filtration carry the finite CE/PV identity, the transition maps
  preserve \(c\mapsto\theta\), \(u\mapsto O\), and completeness identifies
  the inverse limit with the displayed completed complexes.  The
  coevaluation hypothesis is the exact condition needed to keep the
  cotangent generators inside the same completed tensor category.

  For the Koszul-dual statement, work relative to the reductive
  subalgebra \(\mathfrak a\).  The coalgebra generated by the
  pronilpotent ideal \(\mathfrak n\) is conilpotent, so the
  Lie/commutative bar-cobar equivalence applies to the relative CE
  chains.  Reductivity of \(\mathfrak a\) makes passage to
  \(\mathfrak a\)-modules exact on finite quotients; in the filtered
  inverse limit this gives the completed relative equivalence.  Dualizing
  yields the displayed cochain Koszul-dual form.

  This is a criterion, not a statement about the unmodified formal disk:
  Proposition~\ref{prop:lane-low-degree-pronilpotent-obstruction} shows
  that the actual decomposition
  \(\mathfrak h=(H_1\oplus H_2)\oplus\mathfrak m^3\) has no
  pronilpotent ideal \(\mathfrak m^3\) for the full bracket, so the
  criterion applies only after an independent relative model supplies the
  displayed semidirect-product hypotheses.
\end{proof}

\begin{lem}[Filtered cobar acceptance criterion]\label{lem:filtered-cobar-qiso-criterion}
  Let \(C\) be a coaugmented conilpotent dg coalgebra and \(B\) a
  complete augmented filtered \(A_\infty\)-algebra in the same complete
  linear category.  For a continuous degree-one map
  \(\tau\colon C\to B\), define
  \[
    \operatorname{MC}(\tau)
      =
      d_B\tau+\tau d_C
      +\sum_{r\geq2}m_r^B(\tau^{\otimes r})\Delta_C^{(r)}
      \in\Hom^2_{\mathrm{cont}}(C,B),
  \]
  where \(\Delta_C^{(r)}\) is the \(r\)-fold reduced coproduct.  The
  equation \(\operatorname{MC}(\tau)=0\) is equivalent to the existence
  of the adjoint complete cobar morphism
  \[
    \kappa_\tau\colon\Omega C\longrightarrow B .
  \]
  Assume the filtrations on \(\Omega C\) and \(B\) are bounded below,
  complete, separated, and strongly convergent, with finite-dimensional
  associated graded pieces in every total degree.  Then
  \(\kappa_\tau\) is an admissible filtered quasi-isomorphism if and
  only if
  \[
    H^\bullet\!\left(\operatorname{Cone}(
      \operatorname{gr}\kappa_\tau)\right)=0
  \]
  and the two finite-window Milnor defects
  \[
    \varprojlim\nolimits^1_M
      H^{n-1}\!\left((\Omega C)_{\leq M}\right),
    \qquad
    \varprojlim\nolimits^1_M
      H^{n-1}\!\left(B_{\leq M}\right)
  \]
  vanish for every \(n\).
\end{lem}

\begin{proof}
  The Maurer--Cartan formula is the bar-cobar adjunction written in the
  continuous convolution complex.  For a dg target it reduces to
  \(d_B\tau+\tau d_C+\mu_B(\tau\otimes\tau)\Delta_C=0\), which says
  exactly that \(\Omega C\to B\) commutes with differentials and
  multiplication.  The displayed \(A_\infty\) formula is the same
  statement with all target multiplications retained.

  Filter source and target by tensor length and by finite coordinate
  windows.  Exactness of the associated-graded cone is equivalent to
  \(\operatorname{gr}\kappa_\tau\) being a quasi-isomorphism.  The two
  \(\varprojlim^1\)-terms are the Milnor errors in computing the
  cohomology of the completed source and target from their finite
  windows.  With those terms zero, strong convergence gives the
  spectral-sequence comparison theorem in both directions.  Necessity is
  the definition of admissible filtered quasi-isomorphism in this
  envelope: it is detected on associated graded and on the exact
  finite-window towers.
\end{proof}

\begin{defn}[Universal open-trace \(A_\infty\)-Koszul acceptance datum]\label{defn:stable-ainfty-koszul-acceptance-datum}
  A universal open-trace \(A_\infty\)-Koszul acceptance datum consists of:
  \begin{enumerate}[label=(K\arabic*)]
    \item a finite-window tower of one-object cyclic open dg categories
      whose endomorphism complexes are
      \[
        \Omega_c^\bullet(I)\otimes
        \Lambda(\varepsilon_1,\varepsilon_2)\otimes
        \operatorname{End}(\C^N),
      \]
      with cyclic trace
      \[
        \int_I\eta\,[\varepsilon_1\varepsilon_2]\operatorname{Tr}_N(M)
      \]
      and Dirac/Koszul reduction \(Q\psi=[\phi_1,\phi_2]\);
    \item the reduced cyclic dg algebra
      \(A_\psi=T(x,y,\psi)\), \(d\psi=xy-yx\), together with
      \(CC_{\mathrm{red}}(A_\psi)\) and the necklace
      \(H_0\)-shadow \(\operatorname{Cyc}(A_\psi)\);
    \item a finite-window Loday--Quillen--Tsygan comparison on the
      corrected dg finite-window habitat.  Give
      \(A_\psi=T(x,y,\psi)\) the Koszul weights
      \[
        \operatorname{wt}(x)=(1,0),\qquad
        \operatorname{wt}(y)=(0,1),\qquad
        \operatorname{wt}(\psi)=(1,1),
      \]
      and put
      \(A_{\psi,K}=A_\psi/F^{>K}A_\psi\), where \(F^{>K}\) is the
      two-sided dg ideal generated by words of total Koszul weight
      \(>K\).  The stable single-cycle image is
      \[
        \operatorname{Prim}^{1\mathrm{cyc}}_{N,K,L}
        :=
        \operatorname{im}\Theta_{N,K,L}
        \subset
        C_{*,\le L}^{\mathrm{CE}}(\mathfrak{gl}_N(A_{\psi,K}))^{GL_N}.
      \]
      The actual finite-window map is the inverse of the
      trace-cycle map on this image,
      \[
        \lambda_{\mathrm{LQT},K,L}\colon
        \operatorname{Prim}^{1\mathrm{cyc}}_{N,K,L}
        \longrightarrow
        CC_{\mathrm{red},\le L}(A_{\psi,K})[1]
      \]
      in the stable range in which \(N\) dominates both the Koszul
      weight window and CE length.  Equivalently,
      \(\lambda_{\mathrm{LQT},K,L}
      =\Theta_{N,K,L}^{-1}P_{1\mathrm{cyc}}\)
      on stable invariant CE chains, where in the stable block-sum Hopf
      CE window
      \[
        P_{1\mathrm{cyc}}
        =
        \log^*(\operatorname{id})
        =
        \sum_{m=1}^{L}\frac{(-1)^{m-1}}{m}
        (\operatorname{id}-u\epsilon)^{*m}.
      \]
      This is theorem-grade in the range
      \(N\geq\max(K,L+2)\), or \(N\geq W+2\) when one bound \(W\)
      controls both windows, in which case \(A_{\psi,W}\),
      \(\Theta_{N,W}\), and \(\lambda_{\mathrm{LQT},W}\) are abbreviations
      for the specialization \(K,L\le W\).  The raw same-rank operation that deletes
      multicycle tensors is not a chain map, since
      \(d_{\mathrm{CE}}(\Theta_1(a)\wedge\Theta_1(b))\) has a
      single-cycle commutator component while deletion before the
      differential gives zero.  The finite-rank bridge is the
      separated-block stabilization zigzag: with
      \(B(K,L)=\max(K,L+2)\) and \(M=L\,B(K,L)\), let
      \(\beta_{M,K,L}\) be the normalized signed average over injections
      of connected Hopf factors into the \(L\) labeled diagonal
      \(B(K,L)\)-blocks, read separated blocks back by
      \(\alpha_{M,K,L}\), so that
      \(\alpha_{M,K,L}\beta_{M,K,L}=\operatorname{id}\), and use
      \[
        P^{\mathrm{sep}}_{M,K,L}
        =
        \beta_{M,K,L}P_{1\mathrm{cyc}}\alpha_{M,K,L}.
      \]
      A same-rank chain-homotopy bridge is blocked by the collision coderivation
      \[
        \Gamma_N=d_{\mathrm{same}}F_N-F_Nd_{\oplus},
        \qquad
        \Gamma_N(\Theta_1^N(a)\wedge\Theta_1^N(b))
        =
        \pm\Theta_1^N(ab-(-1)^{|a||b|}ba).
      \]
      The scalar quotient is a chain
      quotient only after killing the scalar-Koszul subcomplex
      \(\Theta_1(\psi)\mapsto\Theta_1(xy-yx)\), or after passing to
      homology; killing \(\Theta_1(\psi)\) alone is not a chain map;
    \item a completed augmented filtered \(A_\infty\)-algebra
      \(A_{\mathrm{op}}\) in the scalar-reduced stable trace/Koszul/BV
      sector, with associated graded
      \[
        \operatorname{gr}A_{\mathrm{op}}\cong
        \widehat{\mathbf S}(V_H),
        \qquad
        \operatorname{Indec}\operatorname{gr}A_{\mathrm{op}}
          =\mathfrak m/\mathfrak m^2\cong V_H,
      \]
      where the connected/primitive expression
      \[
        \pi_{\mathrm{Ham}}
        \operatorname{Conn}_{N\to\infty}
        \operatorname{Prim}_{\mathrm{st}}
        \bigl(\mc R_N^{GL_N},Q\bigr)
      \]
      is only this linear associated-graded symbol, not the algebra object
      itself;
      The target indecomposables must be either the principal-part model
      \(\bar A\oplus\mathcal P[1]\), or the descendant model
      \(\bar A\oplus\bar A_{\mathrm{desc}}[1]\) together with a proved
      Fourier--Rees/Moyal bridge to \(\mathcal P[1]\); the raw same-label
      map \(\Psi_{a,b}\mapsto\rho_{a,b}\) is not accepted.
    \item the completed closed target
      \[
        B_{\mathrm{CE/PV}}
          =
        C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{adm}})
          \cong
        \mathrm{PV}\bigl(
          \widehat{\mathbf S}_{\mathrm{coord}}(\mathfrak h_{\mathrm{adm}})
        \bigr),
      \]
      with the generator dictionary \(c^f\mapsto\theta^f\),
      \(u_f\mapsto O_f\);
    \item the open bar coalgebra
      \(C_{\mathrm{op}}=\mathrm{Bar}(A_{\mathrm{op}})\), equipped with a
      complete bounded-below filtration compatible with the bar
      differential, coproduct, and finite coordinate windows;
    \item a continuous degree-one map
      \[
        \tau_{\mathrm{op}}\colon
        C_{\mathrm{op}}\longrightarrow B_{\mathrm{CE/PV}}
      \]
      satisfying the explicit Maurer--Cartan equation
      \[
        d_{B_{\mathrm{CE/PV}}}\tau_{\mathrm{op}}
        +\tau_{\mathrm{op}} b_{\mathrm{op}}
        +\mu_{B_{\mathrm{CE/PV}}}
          (\tau_{\mathrm{op}}\otimes\tau_{\mathrm{op}})\Delta
        =0;
      \]
    \item the induced completed cobar morphism
      \[
        \kappa_{\tau_{\mathrm{op}}}\colon
        \Omega C_{\mathrm{op}}
        \longrightarrow
        B_{\mathrm{CE/PV}}
      \]
      whose associated-graded linear symbol is
      \[
        B_f\longmapsto O_f,\qquad
        \Theta_{\rho_{a,b}}\longmapsto\theta^{a,b};
      \]
    \item the acceptance obstruction complex
      \[
        \begin{aligned}
        \mathfrak C_{\tau_{\mathrm{op}}}
          &=
        \operatorname{Cone}(
          \operatorname{gr}\kappa_{\tau_{\mathrm{op}}})\\
          &\quad{}\oplus
        \bigoplus_n\varprojlim\nolimits^1_M
          H^{n-1}\!\left((\Omega C_{\mathrm{op}})_{\leq M}\right)[-n]\\
          &\quad{}\oplus
        \bigoplus_n\varprojlim\nolimits^1_M
          H^{n-1}\!\left((B_{\mathrm{CE/PV}})_{\leq M}\right)[-n].
        \end{aligned}
      \]
    \item exact continuous dualization on the same finite-window tower;
    \item a cyclicity and BV-pairing package: the scalar word is retained
      before scalar reduction, graded cyclicity uses
      \(\operatorname{Tr}(ab)=(-1)^{|a||b|}\operatorname{Tr}(ba)\),
      two \(\psi\)-letters skew, the open trace is continuous, and the
      BV pairing has degree \(-1\) after the de Rham, Ext, and field-shift
      conventions.
  \end{enumerate}
\end{defn}

\begin{thm}[Universal open-side filtered \(A_\infty\)-Koszul acceptance]\label{thm:stable-ainfty-koszul-under-hypotheses}
  For a datum in the sense of
  Definition~\ref{defn:stable-ainfty-koszul-acceptance-datum}, the following
  are equivalent:
  \begin{enumerate}[label=(\alph*)]
    \item \(\tau_{\mathrm{op}}\) is an accepted open-side twisting
      cochain, i.e. \(\kappa_{\tau_{\mathrm{op}}}\) is an admissible
      filtered quasi-isomorphism of complete augmented
      \(A_\infty\)-algebras with the displayed associated-graded symbol;
    \item the Maurer--Cartan equation in (K7) holds and the obstruction
      complex \(\mathfrak C_{\tau_{\mathrm{op}}}\) from (K9) is exact.
  \end{enumerate}
  Under these equivalent conditions,
  \[
    \Omega\mathrm{Bar}(A_{\mathrm{op}})
      \xrightarrow{\ \sim\ }
    B_{\mathrm{CE/PV}}
  \]
  and hence \(A_{\mathrm{op}}\simeq B_{\mathrm{CE/PV}}\) in the
  completed filtered \(A_\infty\) homotopy category.  If the CE-side
  cobar map
  \[
    \Omega C_*^{\mathrm{CE}}(\mathfrak g_{\mathrm{adm}})
      \longrightarrow A_{\mathrm{op}}
  \]
  satisfies the same exact cone and \(\varprojlim^1\) test, exact
  continuous dualization gives the Koszul-dual cochain form
  \[
    C^\bullet_{\mathrm{CE},\mathrm{cont}}(\mathfrak g_{\mathrm{adm}})
      \simeq
    A_{\mathrm{op}}^! .
  \]
\end{thm}

\begin{proof}
  Apply Lemma~\ref{lem:filtered-cobar-qiso-criterion} with
  \(C=C_{\mathrm{op}}\) and \(B=B_{\mathrm{CE/PV}}\).  The
  Maurer--Cartan equation in (K7) is precisely the condition that
  \(\kappa_{\tau_{\mathrm{op}}}\) is a morphism.  Exactness of
  \(\mathfrak C_{\tau_{\mathrm{op}}}\) says simultaneously that
  \(\operatorname{gr}\kappa_{\tau_{\mathrm{op}}}\) is a
  quasi-isomorphism and that both finite-window towers compute completed
  cohomology.  The filtered comparison theorem then gives the accepted
  quasi-isomorphism, and the converse is the admissible-filtered
  definition.

  The bar-cobar counit
  \(\Omega\mathrm{Bar}(A_{\mathrm{op}})\to A_{\mathrm{op}}\) is a
  filtered quasi-isomorphism under the same boundedness and convergence
  hypotheses, so the accepted \(\kappa_{\tau_{\mathrm{op}}}\) identifies
  \(A_{\mathrm{op}}\) with \(B_{\mathrm{CE/PV}}\) in the homotopy
  category.  The final displayed equivalence is the CE-side specialization
  of the same criterion, followed by exact continuous dualization.
\end{proof}

\begin{stmt}[Statement: Matlis principal-part cotangent module]\label{thm:lane-principal-parts}
  \emph{Status.} \emph{proved degreewise stable}.  The proof uses
  residue calculus and Matlis local-cohomology duality for the
  \(m\)-adic topology on \(R=\C[[z_1,z_2]]\), after quotienting
  constants.

  \emph{Exact hypotheses.} Work over \(R=\C[[z_1,z_2]]\) with maximal
  ideal \(\mathfrak m=(z_1,z_2)\); put
  \(\mathfrak h=R/\C\cdot1\); take continuous duals for the
  \(m\)-adic topology; give \(\mathcal P\) the locally finite
  direct-sum topology transported from
  \(\mathfrak h^\vee_{\mathrm{cont}}\); normalize the residue pairing
  only up to one nonzero scalar; and, for the Fourier--Rees comparison
  only, distinguish the Fourier delta Rees lattice
  \(\mathcal D_\hbar/(z_1,z_2)\) from the full \v{C}ech
  local-cohomology lattice before \(\hbar\) is inverted.

  \emph{Local assertion.} The continuous dual of the reduced Hamiltonian
  Lie algebra is the reduced Matlis-local-cohomology module
  \[
    \mathfrak h^\vee_{\mathrm{cont}}
    \cong
    \mathcal P
    =
    \operatorname{Ann}_{\mathrm{res}}(\C\cdot1)
    \subset
    H^2_{\mathfrak m}(\C[[z_1,z_2]])\,dz_1dz_2,
  \]
  with basis
  \(\rho_{a,b}=z_1^{-a-1}z_2^{-b-1}\,dz_1dz_2\), \(a+b>0\), and
  coadjoint action
  \[
    z_1^p z_2^q\cdot\rho_{a,b}
    =
    -(pb-qa+p-q)\rho_{a-p+1,b-q+1},
  \]
  with negative-index targets equal to zero.  Among continuous
  total-degree-zero pairings, the residue pairing is determined up to one
  nonzero scalar, and this scalar is the only normalization ambiguity in
  this statement.

  \emph{Proof inputs.}
  Appendix~\ref{sec:app-matlis-principal-parts} centralizes the
  reduced Matlis calculation in the notation of this statement.
  Theorem~\ref{thm:canonical-residue-pairing} proves the residue
  pairing and its total-degree-zero scalar ambiguity.
  Proposition~\ref{prop:principal-part-coadjoint} computes the explicit
  coadjoint action in the body.  The upgraded appendix proof is
  Proposition~\ref{prop:app-matlis-coadjoint-action}, and its
  finite-jet continuity is Lemma~\ref{lem:app-matlis-coadjoint-continuity}.
  The stronger uniqueness statement is
  Theorem~\ref{thm:app-matlis-residue-rigidity}: a perfect continuous
  equivariant pairing is unique up to scalar, and the displayed residue
  normalization fixes that scalar.  Theorem~\ref{thm:principal-part-coadjoint-uniqueness}
  remains the body-level total-degree-zero formulation.
  Theorem~\ref{thm:pbw-vs-deformation},
  Theorem~\ref{thm:no-polynomial-realization-categorical}, and
  Theorem~\ref{thm:app-matlis-polynomial-descendant-obstruction} state
  the no-go result for replacing \(\mathcal P\) by polynomial
  descendants.
  Theorem~\ref{thm:app-matlis-rees-fourier-bridge} supplies the limited
  Fourier--Rees label bridge through the Rees lattice
  \(\bigoplus\hbar^{a+b}\C[[\hbar]]\rho_{a,b}\) and proves that it is not
  an \(\mathfrak h\)-module bridge.  Its flatness is the PBW normal-form
  flatness of the left cyclic \(\mathcal D_\hbar\)-modules
  \(\mathcal D_\hbar/(\partial_1,\partial_2)\) and
  \(\mathcal D_\hbar/(z_1,z_2)\).

  \emph{Scope and exclusions.} A same-action \(D_\hbar\), Fourier, or Rees
  comparison identifying the PBW descendant module with the Matlis
  coadjoint module is ruled out on the generic fibre by local nilpotence
  unless the Hamiltonian action or the boundary target is changed.  The
  Fourier-twisted label bridge does not supply such a same-action
  comparison.
\end{stmt}

\begin{stmt}[Statement: brane-line factorization currents]\label{thm:lane-factorization-current}
  \emph{Status.} \emph{proved degreewise stable}.  The proof is for
  compactly supported de Rham Hamiltonian currents and compactly
  supported distributional principal-part currents on intervals.  This
  statement is a strict support-local \(P_0\) current statement in the
  reduced Hamiltonian sector; local constancy is asserted only after the
  compact-support de Rham contraction of the Hamiltonian density sector.

  \emph{Exact hypotheses.} Intervals lie in the brane line \(\R\);
  \(\mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h\);
  \(\mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mathcal P\);
  extension by zero is the functoriality; and source coordinates in the
  displayed boundary operation are shifted-cotangent CE coordinates
  \(u_{a(t)dt\otimes f}\), not Hamiltonian ghost coordinates.  The CE
  source is cofactorization data: extension by zero on current Lie
  algebras induces pullback/coproduct on CE cochains, while covariant
  factorization belongs to the compactly supported current target.

  \emph{Local assertion.} For each interval \(I\subset\R\),
  \[
    \mathfrak h_I=\Omega^\bullet_c(I)\widehat\otimes\mathfrak h,\qquad
    \mathcal P_I=\mathcal D'_c(I)\widehat\otimes\mathcal P,\qquad
    \mathfrak g_I=\mathfrak h_I\ltimes\mathcal P_I[1].
  \]
  The Hamiltonian current sector admits an interval-wise locally constant
  \(P_0\) factorization equivalence.  On length-one shifted-cotangent
  CE coordinates the source is
  \[
    u_{a(t)dt\otimes f}\longmapsto
    B_f(a)=
    \int_I a(t)\,
    \overline{\operatorname{Tr}f(\phi_1(t),\phi_2(t))}\,dt .
  \]
  In the degree-zero notation used here \(a\in\Omega^0_c(I)\), the
  paired density is \(a(t)\,dt\), \(|u_{a(t)dt\otimes f}|=0\), and the
  de Rham-current pairing is
  \[
    \langle B\otimes\rho,\;a\otimes f\rangle
    =B(a)\operatorname{Res}(\rho f).
  \]
  For a regular current \(B=b(t)\,dt\) this is
  \(\int_I a(t)b(t)\,dt\,\operatorname{Res}(\rho f)\).  Orientation
  reversal contributes only the ordinary sign of the one-form density
  \(dt\); no extra sign is inserted in this statement.

  \emph{Proof inputs.}
  Appendix~\ref{sec:app-factorization-current-conventions} fixes the
  interval source, current dual, shifted-cotangent CE coordinate, and
  orientation convention used in this statement.
  Construction~\ref{constr:interval-fact-algebras} fixes the de
  Rham-current objects and extension-by-zero functoriality.
  Proposition~\ref{prop:brane-bracket-locality} proves disjoint-support
  locality.  Theorem~\ref{thm:hamiltonian-current-center-lift} supplies
  the smeared Hamiltonian central operation.  Theorem~\ref{thm:hamiltonian-current-factorization}
  identifies the interval-wise reduced Hamiltonian current
  central-operation map and its
  compatibility with factorization products.

  \emph{Scope and exclusions.} The strict current statement does not include the
  unreduced BV/factorization-centre morphism or its centrality homotopies
  against arbitrary open observables.
\end{stmt}

\begin{stmt}[Statement: reduced principal-part defect currents]\label{thm:lane-reduced-principal-part-current}
  \emph{Status.} \emph{proved degreewise stable}.  The proof applies
  only after the de Rham-current correction and only in the
  reduced \(P_0\) model after contraction.  It is not an unreduced
  BV/factorization theorem and does not supply centrality homotopies
  against arbitrary open observables.

  \emph{Exact hypotheses.} The algebra is the reduced
  defect-current model on intervals after de Rham-current contraction;
  the Hamiltonian factor is
  \(\widehat{\mathbf S}(\Omega_c^0(I)\widehat\otimes\bar A)\); the
  cotangent factor is
  \(\widehat{\mathbf S}(\mathcal D'_c(I)\widehat\otimes\mathcal P[1])\);
  brackets are strict \(P_0\)-brackets; the completed symmetric algebra
  is interpreted degreewise in the current category; and the primitive
  one-\(\psi\) comparison is taken only after passing to
  indecomposables.

  \emph{Local assertion.} The principal-part cotangent factor extends
  the Hamiltonian brane-line algebra to the reduced defect-current
  model
  \[
    A^{\mathrm{pp}}_\partial(I)
    =
    \widehat{\mathbf S}(\Omega_c^0(I)\widehat\otimes\bar A)
    \widehat\otimes
    \widehat{\mathbf S}(\mathcal D'_c(I)\widehat\otimes\mathcal P[1])
  \]
  with
  \[
    \{B_f(a),\Theta_\rho(B)\}
    =
    \Theta_{f\cdot\rho}(aB),
    \qquad
    \{\Theta_\rho(B),\Theta_\sigma(C)\}=0 .
  \]
  The chain-level primitive projection gives only the primitive
  indecomposable \(P_0\) shadow of this reduced comparison.
  Its quantum analogue is the reduced Moyal principal-part target of
  Construction~\ref{constr:quantum-principal-part-descendant-target},
  where \(f\cdot\rho\) is replaced by
  \(\operatorname{ad}^{\vee}_{f,\hbar}\rho\).

  \emph{Proof inputs.}
  Theorem~\ref{thm:reduced-principal-part-boundary-current} proves the
  reduced current model and its \(P_0\) bracket.  Theorem~\ref{thm:boundary-principal-part-cotangent-operators}
  records the boundary local-dual realization in the same reduced
  setting.  Remark~\ref{rmk:reduced-status-principal-part-currents} and
  Remark~\ref{rmk:unreduced-lift-status} state the unreduced
  obligations.  Theorem~\ref{thm:chain-level-primitive-projection},
  Corollary~\ref{cor:unreduced-d-closed}, and
  Remark~\ref{rmk:T5-primitive-shadow-status} supply only the primitive
  shadow status.  Proposition~\ref{prop:quantum-descendant-label-obstruction}
  and Theorem~\ref{thm:one-psi-label-hbar-obstruction} prove
  that the polynomial primitive label projection does not quantize to
  the Moyal coadjoint target.

  \emph{Scope and exclusions.} The unreduced cotangent factorization-centre
  morphism and its centrality homotopies remain outside this statement.  The
  reduced Moyal principal-part target is constructed, but a quantum lift
  from polynomial one-\(\psi\) primitives is ruled out under the
  leading-term assumptions above.  The pointwise classical obstruction
  is the mismatch between the polynomial one-\(\psi\) action and the
  principal-part coadjoint action:
  \[
    O_{1,0}:\widetilde\Psi_{a,b}\mapsto b\,\widetilde\Psi_{a,b-1},
    \qquad
    z_1:\rho_{a,b}\mapsto-(b+1)\rho_{a,b+1},
  \]
  and similarly
  \[
    O_{0,1}:\widetilde\Psi_{a,b}\mapsto
      -a\,\widetilde\Psi_{a-1,b},
    \qquad
    z_2:\rho_{a,b}\mapsto(a+1)\rho_{a+1,b}.
  \]
  Therefore the primitive projection records labels only; it does not
  supply centrality homotopies against arbitrary unreduced open
  observables.
\end{stmt}

\begin{stmt}[Statement: degree-zero Moyal/Weyl sector and graph boundary]\label{thm:lane-moyal-degree-zero}
  \emph{Status.} \emph{proved finite algebraic model plus exact
  radial/Weyl obstruction theorem target}.  The formal Weyl/Moyal
  coefficient algebra, Capelli triangular normalization, reduced open-line
  Wick normalization, free indexed normal-ordering formula, stable
  trace-diagram injectivity, edge PBW telescoping strip, \(K_{4,4}\)
  correction, and named finite non-edge certificates are proved in the
  cited local habitats.  The all-\(N\) ordinary Weyl-trace comparison is
  not closed by a generic radial-parts appeal: it is reduced to the
  moment-ideal primitive, equivalently to the free normal-diagram classes
  \(\mathfrak o_{a,b}\in\operatorname{coker}\mathcal C_{a,b}\).  Its
  sharpened theorem target is the dual-potential obstruction theorem:
  with
  \(B_{a,b}(W)=(\partial W,C^+_{a,b}(W))\) and
  \(\eta_{a,b}=(T_{a,b},E^+_{a,b})\), the same gate is
  \[
    \Omega^{\mathrm{rad}}_{a,b}
    =
    [\eta_{a,b}]\in\operatorname{coker}B_{a,b};
  \]
  failure is exactly a signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\).  The ordinary square-cell
  necklace cycle mechanism is proved; what remains is the all-bidegree
  decorated PBW Stokes identity for
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\).  The mixed QME,
  unweighted regulator endpoint, descendant one-\(\psi\) lift, and
  Costello brane-defect graph realization are separate residual statements
  and are not hypotheses for the formal Moyal coefficient theorem.

  \emph{Exact hypotheses.} Work in the scalar-reduced degree-zero
  Hamiltonian sector at finite \(N\); use the Capelli/Weyl normalization
  of the Weyl algebra and the formal Moyal product on \(\bar A_\hbar\);
  exclude one-antifield descendants and graph-theoretic BV data from the
  proved comparison; and, when comparing ordinary Weyl traces \(J_N(f)\)
  with the Cartan radial image, impose the radial-parts package of
  Statement~\ref{stmt:app-radial-external-input}.  Its matched-normalization
  clause \(J_N(f)=J_N^{\mathrm{rad}}(f)\) is exactly the all-\(N\) algebraic
  gate.  By Lemma~\ref{lem:app-quantum-shear-primitive-obstruction}, this
  gate is the moment-ideal primitive
  \[
    E_{a,b,N}
      =
      \sum_{j=0}^{b}\operatorname{Tr}(Y^jX^aY^{b-j})
      -
      J_N\!\left(
        \{z_1^{a+1}/(a+1),z_2^{b+1}\}_\hbar
      \right)
      =
      \sum_{i,j}A^j{}_i(a,b,N)\widehat\mu^i{}_j
  \]
  with \(A^j{}_i(a,b,N)\in\mathcal W_N\).  Equivalently, after choosing a
  cyclic lift \(c^{\mathrm{cl}}_{a,b}\), it is the vanishing of
  \[
    \mathfrak o_{a,b}
      =
      [R^{\mathrm{free}}_{a,b}]
      \in\operatorname{coker}
      \bigl(\mathcal C_{a,b}\colon\ker\partial\to
      \mathsf{Diag}_{a,b}\bigr)
  \]
  together with functorial lifts \(K_{a,b}\).  The edge classes
  \(\mathfrak o_{2,b}\) and \(\mathfrak o_{a,2}\) vanish by the PBW
  telescoping theorem.  The first interior correction \(K_{4,4}\) and the
  listed low non-edge certificates are all-\(N\) free normal-diagram
  certificates; they are not finite-rank trace identities.

  \emph{Local assertion.} On the scalar-reduced degree-zero Hamiltonian
  sector the formal algebraic target is closed: the commutator is the
  formal Moyal commutator on \(\bar A_\hbar\) under the Capelli/Weyl
  normalization, and the reduced open-line Wick product has the same
  coefficients.  After the radial/Weyl gate is proved in all bidegrees,
  namely after
  \(\Omega^{\mathrm{rad}}_{a,b}=0\) or equivalently
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\), with failure certified by a
  signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) satisfying
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\), the stable connected trace map
  satisfies
  \[
    \hbar^{-1}[\partial_{\mathrm{bb},\hbar}(f),
      \partial_{\mathrm{bb},\hbar}(g)]_{\mathrm{conn,raw}}
    =
    \partial_{\mathrm{bb},\hbar}(\{f,g\}_\hbar).
  \]
  The first and third reduced open-line coefficients are
  \(\hbar P(f,g)\) and \(\hbar^3P^3(f,g)/24\).  A Costello-theoretic
  graph lift of those coefficients requires the sector, propagator,
  counterterm, anomaly, and QME data named in the analytic graph problem.
  Here ``first'' and ``third'' refer to raw star-commutator powers
  \(\hbar^1\) and \(\hbar^3\).  After division by \(\hbar\), these become
  the normalized Hamiltonian-bracket coefficients in powers \(\hbar^0\)
  and \(\hbar^2\), namely \(P(f,g)\) and \(P^3(f,g)/24\).
  In the descendant direction the reduced target is not polynomial:
  Construction~\ref{constr:quantum-principal-part-descendant-target}
  gives the Moyal principal-part coadjoint complex, and
  Theorem~\ref{thm:one-psi-label-hbar-obstruction} rules out
  any strict \(\hbar\)-adic deformation of the classical
  \(\Psi_{a,b}\mapsto\rho_{a,b}\) projection satisfying its flatness,
  PBW-linear-action, Moyal-coadjoint-target, and leading-term hypotheses.

  \emph{Proof inputs.}
  Appendix~\ref{sec:app-radial-parts-moyal} separates the formal
  Moyal/Capelli calculation from the radial/Weyl trace gate.
  Proposition~\ref{prop:app-quantum-shear-suffices-radial-image} and
  Lemma~\ref{lem:app-quantum-shear-primitive-obstruction} reduce the
  unproved all-\(N\) trace normalization to the displayed
  moment-ideal primitive.
  Definition~\ref{def:app-free-indexed-normal-diagrams},
  Theorem~\ref{thm:app-free-indexed-normal-ordering},
  Lemma~\ref{lem:app-free-trace-diagram-stable-injectivity},
  Definition~\ref{def:app-free-kernel-correction-obstruction}, and
  Statement~\ref{stmt:app-free-kernel-homotopy-obstruction} identify the
  free normal-diagram obstruction class; the controlling
  dual-potential form is
  Proposition~\ref{prop:app-radial-dual-potential-obstruction}, namely
  \(\Omega^{\mathrm{rad}}_{a,b}=0\), equivalently
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\), with signed
  \(B_{a,b}^*\)-rows as the exact failure criterion.
  Proposition~\ref{prop:app-edge-pbw-telescoping} proves the all-edge PBW
  telescoping theorem.  Proposition~\ref{prop:app-free-trace-diagram-K44}
  supplies the first interior all-\(N\) kernel correction, and
  Proposition~\ref{prop:app-free-obstruction-certificates} supplies the
  named finite non-edge certificates.
  Theorem~\ref{thm:finite-n-reduced-moyal} uses that input to obtain
  the finite-\(N\) radial-parts identity and the stable degree-zero
  commutator.
  Corollary~\ref{cor:degree-zero-quantum-upgrade} and
  Theorem~\ref{thm:phi-hbar-all-order} assemble the stable
  Capelli-renormalized map.  Proposition~\ref{prop:moyal-monomial}
  proves the Moyal coefficient formula, with an independent finite exact
  arithmetic sweep as verification evidence.  Proposition~\ref{prop:conditional-boundary-product-normalization}
  and Theorem~\ref{thm:open-line-midpoint-graph-weights} compute
  the reduced open-line first and third coefficients.
  Theorem~\ref{thm:first-third-costello-normalizations} records the
  implication from the analytic graph-realization data of
  Problem~\ref{prob:analytic-graph-realization}, and
  Problem~\ref{prob:weighted-rg-locality} carries the mixed
  brane-defect QME obstruction.  Theorem~\ref{thm:phi-hbar-trunc}
  gives the finite nilpotent obstruction to an all-order descendant
  lift.  Proposition~\ref{prop:quantum-descendant-label-obstruction},
  Construction~\ref{constr:quantum-principal-part-descendant-target},
  and Theorem~\ref{thm:one-psi-label-hbar-obstruction} isolate
  the one-\(\psi\) quantum target and the no-go for the polynomial
  primitive projection.

  \emph{Scope and exclusions.} Before the all-bidegree
  dual-potential signed-row theorem is supplied, the ordinary all-\(N\)
  trace identity is closed only on the proved certificate surface: formal coefficients,
  Capelli triangular normalization, open-line Wick weights, edge bidegrees,
  \(K_{4,4}\), the listed finite non-edge free-diagram certificates, the
  rank-two Cartan shadow, and the direct \(N=2,3\) radial restrictions.
  The sharpened obstruction is a nonzero signed row
  \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
  \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\), equivalently a nonzero
  class
  \(\Omega^{\mathrm{rad}}_{a,b}
  =[(T_{a,b},E^+_{a,b})]\in\operatorname{coker}B_{a,b}\).  This would be
  the obstruction theorem for the
  original all-bidegree statement.  The all-order Costello graph
  realization, the mixed brane-defect QME, the unweighted regulator
  problem, and an unreduced one-antifield Moyal lift are not consequences
  of this algebraic statement.
  As a statement about this degree-zero sector alone, the reduced
  principal-part Moyal target is not constructed from polynomial
  one-\(\psi\) descendants.  Its weighted current-bracket version is one
  component of the separate quantum coefficient surface in
  Theorem~\ref{thm:quantum-coefficient-surface}; the non-scalar
  Costello/QME construction problem remains
  Problem~\ref{prob:quantum-p0-operation-realization}.
\end{stmt}

\begin{stmt}[Statement: componentwise quantum coefficient surface]\label{thm:lane-quantum-coefficient-surface}
  \emph{Status.} \emph{proved componentwise; balanced scalar-contact
  projection proved on its habitat; minimal full-equivariant
  finite-window non-scalar branch proved all orders; general
  graph-habitat extension and larger non-scalar obstruction problems
  open}.  The theorem constructs a product coefficient surface.  It does
  not construct unrestricted graph-level non-scalar quantum
  \(P_0\)-operation data.

  \emph{Exact hypotheses.} Fix the exponential weight \(w(d)=q^d\),
  \(q>1\), and work over \(\C[[\hbar]]\).  Use the weighted Tate
  coefficient pair
  \((\mathfrak h_w,\mathfrak h^{\vee,w}_{\mathrm{cont}})\), the
  Moyal Hamiltonian algebra \(\mathfrak h_{w,\hbar}=\mathfrak h_w[[\hbar]]\),
  and the weighted continuous coefficient module
  \(\mathfrak h^{\vee,w}_{\hbar,\mathrm{cont}}
  =\mathfrak h^{\vee,w}_{\mathrm{cont}}[[\hbar]]\).
  The Moyal coadjoint action is used only in the vertexwise
  polynomial-degree-bounded finite-window sector.  The scalar QME factor
  is the balanced \(\mathfrak{gl}(N|N)\) supertrace branch, read on the
  balanced scalar-contact habitat of
  Definition~\ref{def:app-balanced-scalar-contact-habitat}.  The
  degree-zero Hamiltonian trace comparison is read through the
  radial/Weyl gate of Statement~\ref{thm:lane-moyal-degree-zero}: formal
  coefficients, Capelli normalization, open-line Wick weights, edge
  bidegrees, \(K_{4,4}\), and named finite non-edge certificates are
  proved, while the remaining interior bidegrees require
  \(\Omega^{\mathrm{rad}}_{a,b}=0\), equivalently the decorated PBW
  Stokes identity \(D^\square_{a,b}=C^+_{a,b}\partial_2\), with the
  normalized signed-row criterion as the exact obstruction theorem.

  \emph{Local assertion.} The proved surface is the product
  \[
    \mathfrak S_{\hbar,w}(I)
      =
      \mathcal K_{\mathrm{BV}}^w
      \times\{0_{\mathrm{sc}}\}
      \times A^{\mathrm{pp},w}_{\partial,\hbar}(I)
      \times T_{\mathrm{Ham},\hbar}.
  \]
  Its four components are: weighted BV coefficient-kernel convergence
  and graphwise weighted boundedness; the zero filtered balanced
  scalar-contact projection on its habitat; reduced weighted Moyal
  principal-part current brackets; and the radial/Weyl
  finite-certificate-relative degree-zero Moyal trace comparison.  The
  current
  brackets are
  \[
    \{B_f(a),B_g(b)\}_\hbar
      =B_{\{f,g\}_\hbar}(ab),\qquad
    \{B_f(a),\Theta_\rho(B)\}_\hbar
      =\Theta_{\operatorname{ad}^{\vee}_{f,\hbar}\rho}(aB),
  \]
  \[
    \{\Theta_\rho(B),\Theta_\sigma(C)\}_\hbar=0,
  \]
  with \(\operatorname{ad}^{\vee}_{f,\hbar}\) the full Moyal coadjoint
  action on the weighted continuous coefficient module, not the PBW
  one-\(\psi\) action.

  \emph{Proof inputs.}
  The weighted kernel and graphwise boundedness are
  Theorem~\ref{thm:wt-cotangent-lift}.  The scalar zero is
  Theorem~\ref{thm:app-balanced-supertrace-qme-cancellation}; the
  filtered zero projection and vanishing scalar-lift classes on the
  balanced scalar-contact habitat are
  Proposition~\ref{prop:app-balanced-scalar-contact-projection}.  The
  ordinary scalar alternatives are recorded in
  Theorem~\ref{thm:scalar-qme-alternatives}; their source-replacement
  branches include the unreduced central character and the opposite
  central extension
  \(\bar A^{\mathrm{cl}}_{-\hbar N\bar c}\), where the central cochain
  \(J_{\mathrm{op}}=-k^\vee\) satisfies
  \(d_{\mathrm{CE}}J_{\mathrm{op}}=-\hbar N\bar c\).  This is not a
  same-branch Costello-local closed exchange.  The current brackets use
  Theorem~\ref{thm:reduced-principal-part-boundary-current},
  Corollary~\ref{cor:app-factorization-principal-part-current-brackets},
  and Construction~\ref{constr:quantum-principal-part-descendant-target},
  together with Proposition~\ref{prop:quantum-descendant-label-obstruction}
  and Theorem~\ref{thm:one-psi-label-hbar-obstruction} to exclude the
  polynomial descendant lift.  The trace comparison is
  Theorem~\ref{thm:phi-hbar-all-order}, whose remaining radial/Weyl gate is
  the moment-ideal primitive of
  Lemma~\ref{lem:app-quantum-shear-primitive-obstruction}, sharpened by
  Proposition~\ref{prop:app-radial-dual-potential-obstruction} and the
  decorated PBW Stokes problem
  \(D^\square_{a,b}=C^+_{a,b}\partial_2\), together with
  Definition~\ref{def:app-free-kernel-correction-obstruction},
  Statement~\ref{stmt:app-free-kernel-homotopy-obstruction}, and
  Proposition~\ref{prop:app-edge-pbw-telescoping}.
  Lemma~\ref{lem:filtered-scalar-projection-obstruction}
  is not an input to this theorem except on the balanced habitat, where
  Proposition~\ref{prop:app-balanced-scalar-contact-projection} kills
  the scalar-lift classes.  It becomes the extension obstruction for
  promoting the scalar result to the full graph/counterterm habitat.

  \emph{Next obligation.} The next theorem starts with the filtered
  scalar-lift problem in the local-functional complex
  \[
    \mathfrak Q^\bullet_{w,\partial,\hbar}(I)
      =
      \left(
      \mathcal O_{\mathrm{loc}}^{\mathrm{bd}}\bigl(
        \mathcal E_w|_I;\,A^{\mathrm{pp},w}_{\partial,\hbar}(I)\bigr),
      Q+\{I_0^w,-\}_\hbar
      \right).
  \]
  On the balanced scalar-contact habitat, the choice
  \(\widehat\sigma_{\mathrm{bal,sc}}=0\) is already a filtered chain
  projection by
  Proposition~\ref{prop:app-balanced-scalar-contact-projection}.  For
  the full graph/counterterm habitat one must either prove the same
  superdimension factorization or kill the successive chain-lift classes
  \[
    o_{\sigma,w}^{(r)}(I)\in
    H^1\!\left(
      \operatorname{Hom}\bigl(
        \operatorname{gr}_{F}
        \mathfrak Q^\bullet_{w,\partial,\hbar}(I),
        C^\bullet_{\mathrm{Lie}}(\bar A;\C\gamma_{\mathbf 1})[1][[\hbar]]
      \bigr)_{-r}
    \right),\qquad r>0.
  \]
  Only on such a habitat does the filtered chain projection
  \(\widehat\sigma_{\mathrm{sc}}\) exist.  Then the residual complex is
  \(\ker\widehat\sigma_{\mathrm{sc}}\), and the next obstruction is to
  construct the bulk-to-defect curvature cocycle with zero scalar
  projection and kill the class
  \[
    [\operatorname{Ob}^{\mathrm{red}}_{w,\partial,\hbar}]
      \in
      H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})
  \]
  by compatible finite-window counterterms.  Windowwise, this is the
  inverse-limit \(H^1\) obstruction and the
  \(\varprojlim^1H^0\) primitive-compatibility obstruction of
  Theorem~\ref{thm:wt-nonscalar-counterterm-criterion}.  At the first
  non-scalar order \(n_0\), a closed-exchange repair is typed by
  finite-window complexes \(\mathcal X^\bullet_{w,M}(I)\), cochain maps
  \(\Xi_M:\mathcal X^\bullet_{w,M}(I)\to
  \mathcal Q^\bullet_{w,M}(I)\), and the equation
  \[
    \mathfrak o^{\mathrm{ns}}_{n_0,M}
      +\Xi_M(W_{n_0,M})
      +d_M C_{n_0,M}=0.
  \]
  The compatible branch is equivalent to vanishing of
  \[
    \left(
      \beta^{\mathrm{cl}}_{n_0},
      \mu^{\mathrm{cl}}_{n_0},
      \lambda^{\mathrm{cl}}_{n_0}
    \right),
  \]
  where \(\beta^{\mathrm{cl}}_{n_0}\) is the cokernel class of
  \(\varprojlim H^1(\Xi_M)\), while
  \(\mu^{\mathrm{cl}}_{n_0}\in
  \varprojlim^1 H^0(\mathcal X^\bullet_{w,M}(I))\) and
  \(\lambda^{\mathrm{cl}}_{n_0}\in
  \varprojlim^1 H^0(\mathcal Q^\bullet_{w,M}(I))\) are the closed-kernel
  and counterterm primitive-compatibility classes.  The
  bulk-to-defect kernel must be the continuous curved kernel of
  Definition~\ref{def:app-unreduced-nonscalar-current-lift-datum}, with
  generator-level bracket defects killed by compatible
  \(d_{\mathrm{QME}}\)-homotopies as in
  Proposition~\ref{prop:app-nonscalar-current-lift-obstructions}.
  The minimal full-equivariant finite-window branch is the named exception:
  Theorem~\ref{thm:app-minimal-full-equivariant-all-order-vanishing}
  proves \(R^{\mathrm{ns}}_{n,M}=0\),
  \(\mathfrak o^{\mathrm{ns}}_{n,M}=0\), and \(C_{n,M}=0\) for every
  \(n\geq1\) only in the finite marked list generated by the strict
  current-interface rows, \(\alpha_{\mathrm{sc}}\), and its
  subset-deletion closure, with no additional positive-order seed graph,
  CE-source face, graph counterterm face, or nonzero scalar-zero row.
  Outside that habitat, until the scalar-contact extension classes, the
  closed-exchange obstruction triple, and the reduced non-scalar class all
  vanish in the relevant package, no larger non-scalar Costello graph/QME
  construction is asserted.
\end{stmt}

\begin{stmt}[Statement: normal \(\Omega\) weighted kernels and QME boundary]\label{thm:lane-omega-weighted-kernel-qme-surface}
  \emph{Status.} \emph{finite-window weighted kernel admissibility under
  the stated character hypotheses; Costello brane-defect QME remains an
  obstruction criterion}.  Normal \(\Omega\)-localization supplies
  weights, denominators, and candidate contractions.  It does not by
  itself supply propagators, scalar gates, non-scalar primitives,
  counterterms, centrality homotopies, or a physical state.

  \emph{Exact hypotheses.} The brane-preserving torus acts on
  \[
    N_LX=\R_s\oplus\C_{z_1}\oplus\C_{z_2}
  \]
  with \(t\) fixed.  Its vector field and Cartan differential are
  \[
    V_\Omega=
    \epsilon_s s\partial_s+
    \epsilon_1z_1\partial_{z_1}+
    \epsilon_2z_2\partial_{z_2},
    \qquad
    Q_\Omega=Q+\iota_{V_\Omega},
    \qquad
    Q_\Omega^2=L_{V_\Omega}.
  \]
  Hence every dg assertion is made on the invariant/basic complex, or it
  keeps the \(L_{V_\Omega}\)-curvature explicitly.

  For a finite normal/Hamiltonian window
  \[
    \mathsf W_{N,M}
    =
    \{(n,a,b)\mid 0\le n\le N,\ a,b\ge0,\ 1\le a+b\le M\},
  \]
  the Hamiltonian and residue-dual characters are
  \[
    \chi^H_{n,a,b}=n\epsilon_s+a\epsilon_1+b\epsilon_2,
    \qquad
    \chi^\vee_{n,a,b}=n\epsilon_s-a\epsilon_1-b\epsilon_2 .
  \]
  Let \(\mathsf X_{N,M}\) be the finite set of nonzero formal characters
  among \(\chi^H_{n,a,b}\) and \(\chi^\vee_{n,a,b}\) for the moving
  summands contracted in the window.  The finite-window coefficient ring
  is
  \[
    R_{\Omega}^{N,M}
    =
    \C[\epsilon_s,\epsilon_1,\epsilon_2,\hbar_\omega]
    [\chi^{-1}\mid \chi\in\mathsf X_{N,M}],
    \qquad
    w(\hbar_\omega)=\epsilon_1+\epsilon_2 .
  \]
  Finite-window nonresonance means that every moving character inverted
  in the window is nonzero.  Analytic all-window use requires the
  stronger small-denominator bound
  \[
    |\chi_{n,a,b}|^{-1}\le A Q^{n+a+b}
  \]
  for some \(A,Q\) in the chosen specialization.

  \emph{Weighted kernel assertion.} With exponential weight \(w(d)=q^d\),
  \(q>1\), the finite-window diagonal coefficient tensor is
  \[
    C_{\Omega,w}^{N,M}
    =
    \sum_{\alpha\in\mathsf A_{N,M}}
    e_{\alpha,w}\otimes e^\alpha_{w^{-1}},
    \qquad
    e_{\alpha,w}=w(d(\alpha))e_\alpha,\quad
    e^\alpha_{w^{-1}}=w(d(\alpha))^{-1}e^\alpha.
  \]
  If the normal Koszul numerator satisfies
  \[
    Q_\Omega k^{\mathrm{Kos}}_\alpha+
    k^{\mathrm{Kos}}_\alpha Q_\Omega
    =
    \chi_\alpha\,\operatorname{id}_\alpha,
  \]
  then on the nonresonant moving summands the localized normal
  contracting kernel is
  \[
    H_{\Omega,w}^{N,M}
    =
    \sum_{\alpha\in\mathsf A^{\mathrm{mov}}_{N,M}}
    \chi_\alpha^{-1}
    e_{\alpha,w}\otimes e^\alpha_{w^{-1}}
    \otimes k^{\mathrm{Kos}}_\alpha,
  \]
  and it obeys
  \[
    Q_\Omega H_{\Omega,w}^{N,M}
    +H_{\Omega,w}^{N,M}Q_\Omega
    =
    \operatorname{id}-\operatorname{pr}_{\chi=0}.
  \]
  Zero characters are resonant summands; they are not removable
  denominators.

  \emph{Normalization.} The coefficient Casimir is unchanged by the
  choice of residue or Euler convention, but scalar-contact and trace
  rows are not.  The two branches are
  \[
    \nu_\Omega^{\mathrm{res}}=1,\qquad
    \nu_\Omega^{\mathrm{Eu}}
    =
    \sigma_s(\epsilon_s\epsilon_1\epsilon_2)^{-1},
  \]
  with \(\sigma_s\) the real \(s\)-orientation sign.  A theorem using
  both conventions must supply the comparison constant and its sign.

  \emph{QME boundary.} A normal weighted kernel promotes to an
  equivariant Costello brane-defect QME solution only after the
  finite-window graph package, scalar projection, non-scalar kernel
  complex, and primitive tower have been built.  The scalar projection
  starts with the relative Hom defect
  \[
    \delta^{(0)}_{\Omega,\sigma,M}
    =
    d_{\mathrm{CE},\Omega}\sigma_{\mathrm{sc},\Omega,M}
    -\sigma_{\mathrm{sc},\Omega,M}d_{\operatorname{gr},\Omega},
  \]
  and higher classes
  \[
    \mathfrak o^{(r)}_{\Omega,\sigma,M}
    \in
    H^1\!\left(
      \operatorname{Hom}_{T_\Omega,-r}
      (\operatorname{gr}_{F}\mathfrak Q^\bullet_{\mathcal G,\Omega,M},
       S^\bullet_{\Omega,M})
    \right).
  \]
  Only after these vanish is
  \[
    \mathcal K^\bullet_{\mathrm{ns},\Omega,M}
    =
    \ker\widehat\sigma_{\mathrm{sc},\Omega,M}
  \]
  a \(d_{M,\Omega}\)-complex.  The order-\(n\) residual and scalar gate
  are
  \[
  \begin{aligned}
    R^{\mathrm{ns}}_{n,\Omega,M}
      =
    [\hbar_{\mathrm{QME}}^n]\bigl(
      &\operatorname{Curv}_{\mathbf K,\Omega,M}
      +d_{M,\Omega}C_{<n,\Omega,M}\\
      &+\frac12
      \{C_{<n,\Omega,M},C_{<n,\Omega,M}\}_{\hbar_{\mathrm{QME}},M,\Omega}
    \bigr),
  \end{aligned}
  \]
  \[
    \mathfrak s_{n,\Omega,M}
    =
    \widehat\sigma_{\mathrm{sc},\Omega,M}
    (R^{\mathrm{ns}}_{n,\Omega,M}).
  \]
  If \(\mathfrak s_{n,\Omega,M}=0\), the non-scalar class is
  \[
    \mathfrak o^{\mathrm{ns}}_{n,\Omega,M}
    =
    [R^{\mathrm{ns}}_{n,\Omega,M}]
    \in H^1(\mathcal K^\bullet_{\mathrm{ns},\Omega,M}),
  \]
  and compatible counterterms also require the corresponding
  \(\varprojlim^1H^0\) primitive-compatibility class to vanish.

  \emph{Finite-row primitive interface.} Once a scalar-zero finite row
  array is supplied, the primitive search is the linear system
  \[
    A^M c=-r^M.
  \]
  A left-null covector \(\ell A^M=0\), \(\ell(r^M)\ne0\), is a
  finite-row \(H^1\)-certificate.  Windowwise primitive compatibility is
  the Roos class
  \[
    [P^{M,N}c_M-c_N]\in
    H^0(\mathcal K^\bullet_{\mathrm{ns},N}(I)).
  \]
  The \(\theta_3\) one-row obstruction is theorem-grade only for the
  displayed finite subcomplex in which
  \(\mathcal K^0_{\theta_3,M}=0\) and
  \(\mathcal K^1_{\theta_3,M}=\C\mathsf E_{\theta_3,M}\).  It does not
  rule out a primitive in a larger local-functional complex.

  \emph{Proof inputs.}
  The finite normal windows and kernel admissibility are
  Definition~\ref{defn:wt-omega-normal-window},
  Theorem~\ref{thm:wt-omega-kernel-admissibility}, and
  Corollary~\ref{cor:wt-omega-denominators-qme-boundary}.  The
  equivariant QME data and criterion are
  Definition~\ref{def:app-normal-omega-costello-kernel-datum},
  Theorem~\ref{thm:app-equivariant-brane-defect-qme-criterion}, and
  Proposition~\ref{prop:app-qomega-centrality-homotopy-criterion}.  The
  algebraic \(\Omega\)-weighted current brackets on the stable brane
  target are Theorem~\ref{thm:app-omega-weighted-current-brackets}.  The
  finite-row linear algebra is
  Proposition~\ref{prop:finite-row-primitive-search-interface} and
  Proposition~\ref{prop:theta-three-finite-row-obstruction}.

  \emph{Obstruction vector.} The exact unresolved QME datum is
  \[
    \operatorname{Ob}^{\mathrm{QME}}_{\Omega,w}
    =
    \left(
      \mathcal R_{\Omega},
      \operatorname{ob}_{\Omega,\nu},
      \{\mathfrak s_{n,\Omega}\}_{n\ge1},
      \{(([\mathfrak o^{\mathrm{ns}}_{n,\Omega,M}])_M,
        \lambda_{n,\Omega})\}_{n\ge1}
    \right).
  \]
  Its common zero locus, together with invariant centrality primitives,
  is the theorem surface for an equivariant brane-defect QME solution.
\end{stmt}

\begin{stmt}[Statement: stratified trace and physical \(\Omega\)-large-\(N\) criterion]\label{thm:lane-stratified-trace-physical-large-n}
  \emph{Status.} \emph{theorem-surface with exact data and obstruction
  vectors}.  Algebraic stable trace invariant theory supplies candidate
  single-trace labels.  It does not construct a stratified brane
  factorization algebra, a state, a topology, Ward identities, or a
  genus expansion.

  \emph{Stratified datum.} Let
  \[
    X=\R_t\times\R_s\times\C^2_{z_1,z_2},\qquad
    L=\R_t\times\{s=z_1=z_2=0\}.
  \]
  For a chosen finite normal window \((N_{\mathrm{win}},M)\), the
  stronger brane theorem is a functor
  \[
    \mathcal F^{\mathrm{str}}_{\Omega,N}\colon
    \operatorname{Disk}^{\mathrm{str}}_{X,L}
    \longrightarrow
    \operatorname{Ch}_{R_{\Omega}^{N_{\mathrm{win}},M}
    [[\hbar_{\mathrm{QME}}]]},
  \]
  whose values include bulk mixed HT disks in \(X\setminus L\), brane
  intervals in \(L\), and collars meeting the lower stratum.  The finite
  brane branch is
  \[
    A^q_{N,\Omega}
    =
    \operatorname{Weyl}_{\hbar_{\mathrm{W}}}
    (\operatorname{Mat}_N^2)//_{\hbar_{\mathrm{W}}} GL_N,
    \qquad
    YX-XY+\hbar_{\mathrm{W}}NI=0,
  \]
  with
  \[
    w(X)=\epsilon_1,\qquad
    w(Y)=\epsilon_2,\qquad
    w(\hbar_{\mathrm{W}})=\epsilon_1+\epsilon_2.
  \]
  The stable brane branch is the weighted principal-part current target
  \(A^{\mathrm{pp},w}_{\partial,\Omega,\hbar_{\mathrm{W}}}(I)\).  On its
  algebraic current subtarget, the \(\Omega\)-weighted brackets are those
  of Theorem~\ref{thm:app-omega-weighted-current-brackets}; off the
  self-dual locus they are either \(L_\omega^{-1}\)-valued or scalarized
  by \(\hbar_\omega\).  These current brackets are algebraic current data
  and do not supply Costello graph kernels for arbitrary distributional
  labels.  Choosing one branch or constructing a comparison between them
  is part of the theorem.  Replacing the displayed finite-window ring by
  an all-window coefficient completion requires the separate
  \(q\)-moderate small-denominator theorem.

  On the reduced product basis whose basics are product bulk disks
  \(U\times B\subset X\setminus L\), brane intervals \(I\subset L\), and
  finite disjoint unions, extension by zero gives a reduced
  prefactorization datum with
  \[
    \mathcal F^{\mathrm{red}}_{\Omega,X}(U\times B)
    =
    C^\bullet_{\mathrm{CE},\mathrm{cont}}
    \left(
      \Omega_c^\bullet(U)\widehat\otimes
      \Omega_c^{0,\bullet}(B)\widehat\otimes
      (\mathfrak h\ltimes\mathcal P[1])
    \right)\widehat\otimes R_\Omega^{N_{\mathrm{win}},M},
  \]
  and
  \[
    \mathcal F^{\mathrm{red}}_{\Omega,L}(I)
    =
    A^{\mathrm{pp},w}_{\partial,\Omega,\hbar_{\mathrm{W}}}(I).
  \]
  Thus \(\delta_{\mathrm{pref}}=\delta_{\mathrm{assoc}}=0\) only on this
  reduced product-basis datum.  The collar module
  \(\mathcal M_{\Omega,N}(U;I)\), products beyond the reduced basis,
  and stratified Weiss descent must still be supplied.  The internal
  obstruction vector is
  \[
    \operatorname{Ob}^{\mathrm{int}}_{\mathrm{str},\Omega,N}
    =
    (\delta_{\mathrm{pref}},
     \delta_{\mathrm{assoc}},
     \delta_{\mathrm{Weiss}}^{\check C/R},
     \operatorname{ob}_{\mathrm{collar}},
     \operatorname{ob}^{\mathrm{prod}}_{\mathrm{cent}},
     \operatorname{ob}^{P_0}_{\mathrm{cent}},
     \operatorname{ob}^{\mathrm{bd}}_{\mathrm{QME}},
     \operatorname{ob}_{\Omega\mathrm{-basic}},
     \operatorname{ob}_{\mathrm{tr}\mathrm{-top}}).
  \]
  Here \(\operatorname{ob}^{P_0}_{\mathrm{cent}}\) is the
  \(P_{0,\hbar_{\mathrm{QME}}}\)-centrality obstruction in the
  brane-defect local-functional complex, not the reduced Weyl/Moyal
  current bracket over \(\hbar_{\mathrm{W}}\).  The source-primary class
  \(\operatorname{ob}^{\mathrm{src}}_{\mathrm{CFG}}\) is an external
  matched-conventions gate, not an internal component of
  \(\operatorname{Ob}^{\mathrm{int}}_{\mathrm{str},\Omega,N}\).
  Here
  \[
    \delta_{\mathrm{Weiss}}^{\check C/R}
    =
    \left(
      \{H^\bullet(\Delta^{N,M}_{V,\mathcal U})\}_{V,\mathcal U,N,M},
      \mathfrak w^{\check C/R}_{V,\Omega,N,M}
    \right).
  \]
  For a collared stratified Weiss cover \(\mathcal U\) of \(V\), the
  precise descent defect is the Cech cone
  \[
    \Delta^{N,M}_{V,\mathcal U}
    =
    \operatorname{Cone}\!\left(
      \mathcal F^{\mathrm{str}}_{\Omega,N,M}(V)
      \to
      \operatorname{Tot}\check C^\bullet
      (\mathcal U;\mathcal F^{\mathrm{str}}_{\Omega,N,M})
    \right).
  \]
  Full Weiss descent requires \(H^\bullet(\Delta^{N,M}_{V,\mathcal U})=0\)
  for every such cover and vanishing of the associated Roos
  compatibility class
  \(\mathfrak w^{\check C/R}_{V,\Omega,N,M}\) under refinements, finite
  windows, interval inclusions, and admissible weight transports.
  The centrality terms require product and
  \(P_{0,\hbar_{\mathrm{QME}}}\)-homotopies
  against unreduced brane observables:
  \[
    d_{\mathrm{QME}}H^{\mathrm{prod}}_{x,a}
    =
    \rho(x)a-(-1)^{|x||a|}a\rho(x),
  \]
  \[
    d_{\mathrm{QME}}H^{P_0}_{x,a}
    =
    \{\rho(x),a\}_{P_{0,\hbar_{\mathrm{QME}}}}
    -\rho_{\mathrm{mod}}(x;a).
  \]
  Reduced current brackets alone do not supply these homotopies.

  \emph{Physical trace-state criterion.} A physical
  \(\Omega\)-large-\(N\) theorem fixes the 't Hooft scaling
  \[
    \lambda=N\hbar_{\mathrm{W},N},\qquad
    \hbar_{\mathrm{W},N}=\lambda/N,
  \]
  and a continuous cyclic state
  \[
    \omega_{N,\Omega}\colon
    A^q_{N,\Omega,\lambda}
    \longrightarrow R_{\Omega}^{N_{\mathrm{win}},M}
  \]
  or equivalently a state on
  \(\int_{L\subset X}\mathcal F^{\mathrm{str}}_{\Omega,N}\), with a
  BRST/BV lift annihilating the quantum moment ideal.  Its normalization
  datum
  \[
    \nu_{N,\Omega}
    =
    (\omega_{N,\Omega}(1)=1,\ O^{(N)}_{0,0}=N,\
     \lambda=N\hbar_{\mathrm{W},N},\
     \nu_\Omega^{\mathrm{res}}
     \text{ or }\nu_\Omega^{\mathrm{Eu}})
  \]
  fixes the empty trace and the residue/Euler branch.  The two
  localization conventions differ by the inverse normal Euler factor
  \((\epsilon_s\epsilon_1\epsilon_2)^{-1}\), up to the real orientation
  sign; they cannot be mixed silently.

  The trace-test algebra is
  \[
    \mathscr T_+
    =
    R_{\Omega}^{N_{\mathrm{win}},M}
    [[p_{a,b}\mid a,b\ge0,\ a+b>0]],
    \qquad
    p_{a,b}\mapsto
    O^{(N)}_{a,b}=\operatorname{Tr}(X^aY^b).
  \]
  Connected cumulants are
  \[
    \langle F_1,\ldots,F_k\rangle^c_{N,\Omega}
    =
    [t_1\cdots t_k]\log
    \omega_{N,\Omega}
    \left(\exp\Bigl(\sum_i t_iF_i\Bigr)\right).
  \]
  In the unnormalized single-trace convention the physical genus
  expansion is
  \[
    \langle O^{(N)}_{a_1,b_1},\ldots,O^{(N)}_{a_k,b_k}
    \rangle^c_{N,\Omega}
    \sim
    \sum_{g\ge0}N^{2-2g-k}
    F^\Omega_{g;k}((a_1,b_1),\ldots,(a_k,b_k))
  \]
  in the coefficientwise \(N^{-2}\)-Poincare topology
  \(\mathcal T_\Omega\).  With smeared insertions on \(L\), the
  coefficients lie in
  \(\mathcal D'(L^k)\widehat\otimes
  R_{\Omega}^{N_{\mathrm{win}},M}\).

  \emph{Ward identities.} If
  \[
    D_{N,\Omega}
    =
    Q_\Omega+\{I_{N,\Omega},-\}_{\hbar_{\mathrm{W},N}}
    +\hbar_{\mathrm{QME}}\Delta_{N,\Omega}
  \]
  is the renormalized brane-defect differential and
  \(D_{N,\Omega}^2=0\), the state must satisfy
  \[
    \omega_{N,\Omega}(D_{N,\Omega}F)=0,\qquad
    \omega_{N,\Omega}(Q_\Omega F)=0,
  \]
  \[
    \omega_{N,\Omega}(\widehat\mu(\xi)F)=0,\qquad
    \omega_{N,\Omega}(\operatorname{Curv}(K_{\Omega,N})F)=0.
  \]
  If \(\operatorname{Curv}(K_{\Omega,N})\ne0\), the last expression is a
  Ward anomaly, not a protected trace theorem.

  \emph{Exact obstruction vector.} The physical theorem surface is
  closed only when
  \[
  \begin{aligned}
    \operatorname{Ob}_{\Omega,\mathrm{phys}}
    ={}&
    (
      \operatorname{ob}_{\Omega,\mathrm{Cartan}},
      \operatorname{ob}_{\Omega,\mathrm{contr}},
      \operatorname{ob}_{\mathrm{red}},
      \operatorname{ob}_{\mathrm{state}},
      \operatorname{ob}_{\mathrm{norm}},
      \operatorname{ob}^{\mathrm{sc}}_{\mathrm{QME}},
      \\
      &
      \operatorname{ob}^{\mathrm{ns}}_{\mathrm{QME}},
      \operatorname{ob}_{\mathrm{cent}},
      \operatorname{ob}_{\mathrm{Ward}},
      \operatorname{ob}_{\mathrm{cum}},
      \operatorname{ob}_{\mathrm{asymp}},
      \operatorname{ob}_{\mathrm{src}}
    )
  \end{aligned}
  \]
  vanishes.  The scalar contact entry in the ordinary scalar-reduced
  branch is
  \(\hbar_{\mathrm{W},N}N[\bar c]=\lambda[\bar c]\); the BV/QME loop
  parameter remains \(\hbar_{\mathrm{QME}}\) unless the QME
  normalization datum explicitly identifies it with
  \(\hbar_{\mathrm{W},N}\).  The non-scalar entry is the
  class in
  \(H^1(\ker\widehat\sigma_{\mathrm{sc}},d_{\mathrm{QME}})\) together
  with the finite-window obstruction pairs.  External
  factorization-homology, Chern--Simons, Costello, CFG, compact
  Calabi--Yau, Vol III, or physical large-\(N\) analogies enter only
  after a primary-source fixture and matched-conventions morphism to
  \((X,L)\) are supplied.
\end{stmt}

\begin{stmt}[Statement: local graph/QME branch catalogue]\label{thm:lane-local-graph-qme-branch-catalogue}
  \emph{Status.} \emph{proved on the named local habitats, relative
  to supplied finite-window data where stated, and obstructed by the
  displayed classes otherwise}.  This is the theorem-surface ledger for
  the present local graph/QME branches.  It is not a compact target or
  global comparison statement.

  \emph{Exact hypotheses.} Work only in the formal-local mixed HT model on
  \(\R^2_{\mathrm{top}}\times\widehat{\C^2}_{0,\mathrm{hol}}\), with the
  weighted finite-window brane-defect local-functional complexes,
  scalar-contact filtrations, Costello finite-window graph packages, and
  principal-part current targets fixed in the cited definitions.  All
  graph claims are finite-window or compatible inverse-limit statements;
  no summation over all graph topologies is included unless a separate
  graph-summability datum is supplied.

  On a chosen Weyl branch, the native finite-window Costello habitat is
  the completed local-functional complex
  \[
    \mathfrak Q^\bullet_{\mathcal G,M}(I)
    =
    \left(
    \mathcal O^{\mathrm{bd}}_{\mathrm{loc},\mathcal G,M}
    (\mathcal E_w^M|_I;
     A^{\mathrm{pp},w,M}_{\partial,\hbar_{\mathrm{W}}}(I)),
    d_M
    \right),
    \qquad
    d_M=Q+\{I^w_{0,M},-\}_{\hbar_{\mathrm{W}},M},
  \]
  together with the Hom-valued kernel complex
  \[
    \mathbf K^\bullet_{\mathcal G,M}(I)
    =
    \operatorname{Hom}_{\mathrm{cont}}
    (C^\bullet_{\mathrm{lab}}(\mathcal G_M),
     \mathfrak Q^\bullet_{\mathcal G,M}(I)).
  \]
  The source-face differential is part of this habitat.  Closed rows,
  scalar gates, \(\theta_3\)-source rows, and primitive compatibility are
  therefore finite-window row data, not evidence for an all-graph QME.

  \emph{Local assertion.} The branches have the following exact strength.
  \begin{enumerate}[label=(\arabic*)]
    \item \emph{Balanced scalar-contact projection.}  Proved on every
    balanced scalar-contact habitat, with
    \(\widehat\sigma_{\mathrm{bal,sc}}=0\), zero chain-map defect, and
    vanishing \(o_{\sigma,w,\mathrm{bal}}^{(r)}(I)\).  The same assertion
    is proved on a balanced graph/counterterm subhabitat once the
    identity-loop supertrace factorization is part of the habitat data.
    Outside these habitats the obstruction is the first nonzero class
    \(o_{\sigma,w}^{(r)}(I)\) of the scalar-contact lift tower.

    \item \emph{Full-equivariant scalar shadow.}  Proved on complete
    finite-window inverse-limit habitats generated windowwise by
    codimension-two closed finite-window marked Costello lists and
    full-equivariant Brauer marker tensors.  For \(V=\C^{N|N}\), every
    cyclic supertrace of a transported full-equivariant marker tensor is
    zero, so the zero scalar projection is a filtered chain map there.
    If the marked boundary table, incidence signs, marker transports, or
    codimension-two closure are not supplied, the missing entry is the
    exact obstruction to forming this scalar-shadow theorem.

    \item \emph{Finite closed graph list.}  Proved as a finite-window
    closure criterion.  A seed graph set and its boundary operations give
    a legitimate finite graph list only when every field-differential,
    BV-edge, collision, counterterm, and source face remains in the list
    with compatible signs and marker transports.  Failure of the
    codimension-two closure equations is the obstruction to the finite
    marked differential \(d_{\mathrm{mk}}^2=0\).

    \item \emph{Finite-window arrays and the minimal full-equivariant
    branch.}  The computed rows are theorem-grade: the length-one
    current-interface row has \(R^{\mathrm{row}}_{0,M}=S_{0,M}=0\), and
    the one-cross two-Hamiltonian scalar-contact row has scalar gate
    \(N\gamma_{\mathbf 1}\), \(N(\lambda_0-\lambda_1)\gamma_{\mathbf 1}\),
    or \(0\) in the ordinary, even-block, or full-equivariant branch.  In
    the full-equivariant branch this row is zero as a local functional.
    The minimal finite marked list generated by the strict
    current-interface rows, this scalar-contact row, and its
    subset-deletion closure therefore satisfies, for every \(n\geq1\),
    \[
      R^{\mathrm{ns}}_{n,M}=0,\qquad
      \mathfrak o^{\mathrm{ns}}_{n,M}=0,\qquad
      C_{n,M}=0 .
    \]
    If zero rows are suppressed, the positive-order minimal arrays are
    empty; if labelled zero rows are retained, every retained
    positive-order row has zero row value, zero scalar gate, and zero
    truncation row.  In particular the binary centrality row in the
    reduced coefficient-current/minimal full-equivariant habitat has
    \(R^{\mathrm{cent},\mathrm{coef}}_{x,y,M}=0\),
    \(S^{\mathrm{cent},\mathrm{coef}}_{x,y,M}=0\), and
    \(H^{\mathrm{coef},M}_{x,y}=0\); equivalently
    \(A^M_{\min}:0\to0\), \(r^M_{\min}=0\), and \(h^M_{\min}=0\), with
    zero Roos class.  For any larger package the first obstruction is not
    supplied by this theorem.  The enlarged binary row is the matrix
    problem \(A^Mh^M=-r^M\) after the row values, scalar gate, primitive
    columns, and transition matrices have been supplied.  The first
    supplied open source-face row has
    \[
      R^{\mathrm{row}}_{\theta_3,M}
      =
      -K^M_{\Theta_3}(\zeta_{M,\nu_3})
      =:\mathsf E_{\theta_3,M},
      \qquad
      S_{\theta_3,M}=0 .
    \]
    In the displayed one-row finite subcomplex
    \[
      \mathcal K^0_{\theta_3,M}=0,\qquad
      \mathcal K^1_{\theta_3,M}=\C\mathsf E_{\theta_3,M},
      \qquad
      d_{\theta_3,M}=0,
    \]
    the covector
    \(\ell_{\theta_3}(\mathsf E_{\theta_3,M})=1\) certifies a finite-row
    obstruction.  This does not rule out a primitive in a larger
    local-functional complex or after Hom-valued companion rows are added.
    The tested finite enlargements are now part of the obstruction
    theorem.  In the ordinary pure two-\(u\) CE source envelope, in every
    finite Hamiltonian degree, the covector
    \[
      q_{2u}
      =
      e^*_{((H_{0,1},H_{2,0}),c_{\rho_{2,1}})}
      -\frac12
      e^*_{((H_{0,1},H_{0,1}),c_{\rho_{0,2}})}
    \]
    satisfies
    \[
      q_{2u}d_{\mathrm{CE}}=0,\qquad
      q_{2u}(\zeta_{M,\nu_3})=1.
    \]
    Thus no ordinary pure two-\(u\) degree enlargement contains a CE
    ancestor for \(\zeta_{M,\nu_3}\).  This is an exact obstruction
    theorem for that source envelope, not a universal no-go for larger
    local-functional, marked-source, or Hom-valued companion habitats.
    The tested eight-face companion row has
    coordinates
    \[
      (2,-2,3,2,-1,1,-2,-3)
    \]
    on
    \[
      E_{\nu_{02}},E_{\nu_{20}},E_{\nu_{03}},
      E_{\nu_{12}^{(1)}},E_{\nu_{12}^{(2)}},
      E_{\theta_3},E_{\nu_{21}^{(2)}},E_{\nu_{30}},
    \]
    and diagonal transport to the \(N=2\) window leaves
    \(2E^2_{\nu_{02}}-2E^2_{\nu_{20}}\).  The same eight-face row has
    \(q_{2u}\)-value zero, so it is not the missing marked source column.
    The lower-window functional
    \(\lambda^{(2)}_{\nu_{02}}=\frac12(E^2_{\nu_{02}})^*\) detects the
    transported residual.  The next possible repair is a controlled
    enlargement of the row complex, not reuse of either tested finite
    route.  The exact missing data are: a counterterm
    column \(A^M_{\theta_3,C}=-1\) with
    \(d_MC^{\mathrm{ct}}_{\theta_3,M}=-\mathsf E_{\theta_3,M}\),
    scalar-zero value, and zero Roos class; a marked source generator
    \(\eta^{\mathrm{mark}}_{\theta_3,M}\) outside the ordinary pure
    two-\(u\) algebra, whose new boundary column has
    \(q_{2u}\)-value \(1\) and satisfies codimension-two closure,
    Hom-valued Bianchi cancellation, scalar-zero value, and compatible
    transport; or a marked companion relation
    \(R^{\mathrm{cand}}_{\Theta_3,M}=0\) together with lower-window
    transport \(v^{M,N}R^{\mathrm{cand}}_{\Theta_3,M}=0\), including the
    \(N=2\) relation killing
    \(2E^2_{\nu_{02}}-2E^2_{\nu_{20}}\) by a derived non-diagonal
    transport, lower primitive, or relation
    \(E^2_{\nu_{02}}=E^2_{\nu_{20}}\).  The canonical source-coordinate
    lower primitive candidate is
    \[
      \zeta^0_2=u_{a,H_{1,0}}u_{b,H_{0,1}},\qquad
      D^2_{02,20}=K^2_{\Theta_3}(\zeta^0_2),
      \qquad
      d_{\mathrm{CE}}\zeta^0_2
      =
      2\zeta_{\nu_{02}}-2\zeta_{\nu_{20}}.
    \]
    This is source exactness.  In the local-functional complex
    \[
      d_{\mathrm{ns},2}D^2_{02,20}
      =
      -2E^2_{\nu_{02}}+2E^2_{\nu_{20}}
      +\mathfrak b^2_{02,20},
    \]
    where
    \[
      \mathfrak b^2_{02,20}
      =
      d_{\mathrm{ns},2}K^2_{\Theta_3}(\zeta^0_2)
      -
      K^2_{\Theta_3}(d_{\mathrm{CE}}\zeta^0_2).
    \]
    In the Bianchi-exposed lower basis
    \((E^2_{\nu_{02}},E^2_{\nu_{20}},\mathfrak b^2_{02,20})\), the column
    and residual are
    \[
      A_D^2=(-2,2,1)^T,\qquad r_2=(2,-2,0)^T .
    \]
    The cokernel
    \[
      \widetilde\lambda_{02,\mathfrak b}
      =
      \frac12(E^2_{\nu_{02}})^*
      +(\mathfrak b^2_{02,20})^*
    \]
    kills \(A_D^2\) and evaluates to \(1\) on \(r_2\).  Thus the lower
    source primitive becomes a local-functional primitive only after
    \(\mathfrak b^2_{02,20}\) is killed, or after adding a scalar-zero
    local counterterm \(B^2_{02,20}\) with
    \(d_{\mathrm{ns},2}B^2_{02,20}=-\mathfrak b^2_{02,20}\) and
    compatible transport.  In the current finite-row habitat no such
    \(B^2_{02,20}\) exists: the target
    \((0,0,-1)^T=-\mathfrak b^2_{02,20}\) is detected by
    \[
      \widetilde\lambda_{02,\mathfrak b}((0,0,-1)^T)=-1,
    \]
    while \(\widetilde\lambda_{02,\mathfrak b}\) kills the only available
    degree-zero column.  The controlled enlargement must add a genuine
    scalar-zero local-functional column
    \(A_B^2=(0,0,-1)^T\), with locality or wavefront admissibility and
    finite-window transport.  For a tower the Bianchi transport cocycle is
    \[
      \Delta^1_{M,N}
      =
      -\pi_{M,N}\mathfrak b^M+\mathfrak b^N .
    \]
    A compatible counterterm family \(B^M\) kills it exactly when
    \[
      \Delta^1_{M,N}
      =
      d_{\mathrm{ns},N}(\pi_{M,N}B^M-B^N).
    \]
    Hence the controlled enlargement must also kill the \(H^1\) class of
    \(\Delta^1_{M,N}\) and the secondary
    \(\varprojlim^1H^0\) primitive-compatibility class; otherwise the
    Bianchi row remains obstructed.
    For any larger package the first undefined obstruction is the
    unfilled row sum
    \[
      R^{\mathrm{ns}}_{1,M}
      =
      \sum_{\alpha\in
      \mathsf A^{\mathrm{fw}}_{1,M}\setminus\{\alpha_{\mathrm{sc}}\}}
      R^{\mathrm{row}}_{\alpha,M},
    \]
    or, when no nonzero order-one row is supplied, the corresponding
    order-two and order-three row sums.  Those larger rows require their
    graph type, finite-window labels, marker tensor, incidence signs, row
    values, scalar gates, and truncation coefficients before the
    \(H^1\) class and the Roos finite-window compatibility class are
    defined.

    \item \emph{Regular-density curvature certificate.}  Proved under the
    regular-density graph package hypotheses: all cotangent defect labels
    are smooth compactly supported densities, the finite graph list is
    closed under the relevant \(d_M\)- and BV-bracket terms, the scalar
    projection is zero on the chosen subhabitat, and the lower counterterms
    are compatible and regular-density.  Then the evaluated curvature
    residual lies in
    \(\mathcal X^{\bullet,\mathrm{reg}}_{w,M}(I)\), is killed by
    \(W_{n_0,M}=-\mathfrak o^{\mathrm{ns,reg}}_{n_0,M}\) and
    \(C_{n_0,M}=0\), and the classes
    \[
      \eta^{\mathrm{reg}}_{n_0},\quad
      \kappa^{\mathrm{reg}}_{n_0},\quad
      \beta^{\mathrm{cl},\mathrm{reg}}_{n_0},\quad
      \mu^{\mathrm{cl}}_{n_0},\quad
      \lambda^{\mathrm{cl}}_{n_0}
    \]
    vanish.  Without this certificate the exact obstruction is the
    quotient class
    \(\eta^{\mathrm{reg}}_{n_0,M}\) and, after its vanishing, the Roos
    lift class \(\kappa^{\mathrm{reg}}_{n_0}\).

    \item \emph{Wavefront eta obstruction.}  Proved as an obstruction
    theorem, with a positive graph branch on the tuple relation
    \(\mathcal D'_{c,\mathrm{WF}}(I;\Gamma,M)\) and on the two
    sign-conic finite-scaling habitats
    \(\mathcal D'_{c,\Lambda_\pm,\mathrm{fs}}(I)\) for ordinary
    collision-conormal graph kernels.  For non-smooth
    wavefront-admissible labels the singular quotient
    \(\mathcal S_c(I)=\mathcal D'_c(I)/\mathcal D^{\mathrm{reg}}_c(I)\)
    is nonzero.  The finite-window obstruction class is
    \[
      \eta^{\mathrm{reg}}_{n_0,M}
      =
      [\mathfrak s^{\mathrm{WF}}_{n_0,M}]
      \in
      H^1(\mathcal C^{\bullet,\mathrm{reg}}_{w,M}(I)).
    \]
    It is killed in the original complex exactly when a degree-zero
    distributional counterterm \(C^{\mathrm{sing}}_{n_0,M}\) satisfies
    \(\bar d_Mq_M(C^{\mathrm{sing}}_{n_0,M})
    =-\mathfrak s^{\mathrm{WF}}_{n_0,M}\).  If not, the regular-density
    branch is obstructed.  The formal primitive cone adjoins a new
    generator and is an extension theorem, not a smoothing theorem.

    \item \emph{Radial trace-diagram theorem lane.}  The formal Moyal
    coefficient calculation, Capelli triangular normalization, free
    indexed normal-ordering formula, stable trace-diagram injectivity, and
    reduced open-line first/third weights are proved.  The all-\(N\)
    ordinary Weyl-trace comparison is reduced to the moment-ideal
    membership of
    \[
      E_{a,b,N}
      =
      \sum_{j=0}^{b}\operatorname{Tr}(Y^jX^aY^{b-j})
      -
      J_N\!\left(
        \{z_1^{a+1}/(a+1),z_2^{b+1}\}_\hbar
      \right)
    \]
    in the chosen quantum moment-map quotient.  It holds exactly when one
    constructs \(A^j{}_i(a,b,N)\) with
    \(E_{a,b,N}=\sum_{i,j}A^j{}_i(a,b,N)\widehat\mu^i{}_j\).  This
    condition is equivalently the free normal-diagram equation
    \[
      \mathfrak o_{a,b}
      =
      [R^{\mathrm{free}}_{a,b}]
      \in
      \operatorname{coker}
      \bigl(\mathcal C_{a,b}\colon\ker\partial\to
      \mathsf{Diag}_{a,b}\bigr)
    \]
    plus a functorial lift \(K_{a,b}\).  In the dual-potential form put
    \[
      B_{a,b}(W)=(\partial W,C^+_{a,b}(W)),\qquad
      \eta_{a,b}=(T_{a,b},E^+_{a,b}),
    \]
    and
    \[
      \Omega^{\mathrm{rad}}_{a,b}
      =
      [\eta_{a,b}]\in\operatorname{coker}B_{a,b}.
    \]
    The all-\(N\) ordinary trace statement is equivalent to
    \(\Omega^{\mathrm{rad}}_{a,b}=0\), equivalently to the decorated PBW
    Stokes identity \(D^\square_{a,b}=C^+_{a,b}\partial_2\).  Failure is
    exactly a signed row \((\phi,-\lambda)\in\ker B_{a,b}^*\) with
    \(\lambda(E^+_{a,b})-\phi(T_{a,b})\ne0\).  The edge classes
    \(\mathfrak o_{2,b}\) and \(\mathfrak o_{a,2}\) vanish by the PBW
    telescoping theorem.  The \(K_{4,4}\) correction and the named finite
    non-edge certificates are all-\(N\) free normal-diagram certificates.
    For the remaining interior bidegrees the exact theorem target is a
    natural contraction of the positive-contraction two-colour necklace
    complex, equivalently the dual-potential signed-row theorem above.
    This obstruction is algebraic in the local Weyl/radial
    comparison and does not provide a Costello graph/QME construction.
  \end{enumerate}

  \emph{Proof inputs.}
  The balanced scalar claims are
  Theorem~\ref{thm:app-balanced-supertrace-qme-cancellation},
  Proposition~\ref{prop:app-balanced-scalar-contact-projection}, and
  Proposition~\ref{prop:app-balanced-costello-graph-preservation}.  The
  full-equivariant branch is
  Lemma~\ref{lem:app-full-equivariant-cyclic-supertrace} and
  Theorem~\ref{thm:app-full-equivariant-marked-shadow-vanishing}, with
  the finite-list and differential data of
  Definition~\ref{def:app-finite-window-marked-costello-list},
  Definition~\ref{def:app-oriented-full-equivariant-marked-boundary-complex},
  Lemma~\ref{lem:app-oriented-marked-incidence-signs}, and
  Proposition~\ref{prop:app-finite-window-marked-habitat-compatibility}.
  The native Hom-valued Costello/QME realization habitat and its row
  criterion are
  Definition~\ref{def:app-native-finite-window-realization-habitat},
  Theorem~\ref{thm:app-constructive-nonscalar-costello-qme-realization},
  and Proposition~\ref{prop:app-closed-rows-and-theta-three-source-face}.
  The finite-window array is
  Definition~\ref{defn:finite-window-graph-array},
  Proposition~\ref{prop:first-finite-window-array-rows}, and
  Definition~\ref{def:app-nonscalar-kernel-row-complex}.  The minimal
  full-equivariant non-scalar branch is
  Theorem~\ref{thm:app-minimal-full-equivariant-kernel-vanishing} and
  Theorem~\ref{thm:app-minimal-full-equivariant-all-order-vanishing};
  larger finite-window packages are governed by
  Proposition~\ref{prop:app-first-missing-nonscalar-row},
  Proposition~\ref{prop:app-first-scalar-zero-order-one-row}, and
  Proposition~\ref{prop:app-first-order-three-larger-package-datum}.  The
  regular-density and wavefront branches are
  Proposition~\ref{prop:wt-regular-density-curvature-certificate},
  Theorem~\ref{thm:wt-wavefront-singular-current-eta-obstruction}, and
  Theorem~\ref{thm:wt-wavefront-distributional-primitive-cone}.  The
  radial/Weyl lane uses
  Lemma~\ref{lem:app-quantum-shear-primitive-obstruction},
  Definition~\ref{def:app-free-indexed-normal-diagrams},
  Theorem~\ref{thm:app-free-indexed-normal-ordering},
  Lemma~\ref{lem:app-free-trace-diagram-stable-injectivity},
  Definition~\ref{def:app-free-kernel-correction-obstruction},
  Statement~\ref{stmt:app-free-kernel-homotopy-obstruction},
  Proposition~\ref{prop:app-edge-pbw-telescoping},
  Proposition~\ref{prop:app-free-trace-diagram-K44},
  Proposition~\ref{prop:app-free-obstruction-certificates}, and
  Theorem~\ref{thm:finite-n-reduced-moyal}.

  \emph{Scope and exclusions.} None of these branch statuses imports or
  implies compact Calabi--Yau, CoHA, quintic, OSV/GV, Abel--Jacobi,
  Igusa, Borcherds/BKM, or global BCOV claims.
\end{stmt}

\begin{stmt}[Statement: scalar \(U(1)\) anomaly]\label{thm:lane-u1-anomaly}
  \emph{Status.} \emph{proved in finite algebraic model}.  The statement
  records the scalar-reduction obstruction to lifting the reduced
  Hamiltonian comparison back to the unreduced constant direction.

  \emph{Exact hypotheses.} The closed algebra is the unreduced polynomial
  Hamiltonian algebra \(\mathfrak h_{\mathrm{poly}}=\C[z_1,z_2]\) and
  its quotient \(\bar A=\mathfrak h_{\mathrm{poly}}/\C\cdot1\); the open
  side is the finite-\(N\) trace algebra before and after quotienting
  \(\C\cdot\operatorname{Tr}(1)\); and the quantum comparison uses the
  same Capelli/Weyl normalization as the degree-zero Moyal theorem.

  \emph{Local assertion.} The scalar-reduction axis carries the
  distinguished class
  \[
    [\bar c]\in H^2_{\mathrm{Lie}}(\bar A,\C),
  \]
  represented by the constant Taylor coefficient of the Poisson
  bracket.  The same class appears on the open side as the
  centre-of-mass \(\mathfrak{gl}_N\) anomaly; quantum mechanically its
  finite-\(N\) trace-character representative is the Capelli contact
  \(\hbar N\).  All reduced Hamiltonian comparisons are made after
  killing constants; the unreduced scalar line is governed by this
  anomaly class.

  \emph{Proof inputs.}
  Lemma~\ref{lem:omega-cocycle} identifies the closed Poisson cocycle.
  Theorem~\ref{thm:u1-center-anomaly} proves the closed-side central
  extension statement.  Theorem~\ref{thm:u1-center-anomaly-open}
  computes the open \(U(1)\) centre.  Theorem~\ref{thm:quantum-classical-anomaly}
  identifies the classical cocycle with the Rees central extension whose
  finite-\(N\) trace-character value is the quantum Capelli shift.
  Corollary~\ref{cor:local-bulk-boundary-coupling} gives the explicit
  local central term in the smeared boundary bracket.

  \emph{Scope and exclusions.} The statement does not lift the reduced comparison to the
  unreduced scalar direction and does not imply compact Calabi--Yau,
  CoHA, quintic, OSV/GV, Abel--Jacobi, Igusa, Borcherds/BKM, or
  sister-volume anomaly statements.
\end{stmt}
